### 2018-04-30 WiL.tex
adding the WiL version

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
\documentclass[sigplan,10pt]{acmart}\settopmatter{}

%% Conference information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmConference[WiL'18]{Second Women in Logic (WiL) Workshop}
\acmYear{2018}
%\acmISBN{} % \acmISBN{978-x-xxxx-xxxx-x/YY/MM}
%\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
%\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2017}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%\citestyle{acmauthoryear}  %% For author/year citations
%\citestyle{acmnumeric}     %% For numeric citations
%\setcitestyle{nosort}      %% With 'acmnumeric', to disable automatic
                            %% sorting of references within a single citation;
                            %% e.g., \cite{Smith99,Carpenter05,Baker12}
                            %% rendered as [14,5,2] rather than [2,5,14].
%\setcitesyle{nocompress}   %% With 'acmnumeric', to disable automatic
                            %% compression of sequential references within a
                            %% single citation;
                            %% e.g., \cite{Baker12,Baker14,Baker16}
                            %% rendered as [2,3,4] rather than [2-4].

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from traditional SIGPLAN
%% proceedings format to PACMPL format must update the
%% '\documentclass' and topmatter commands above; see
%% 'acmart-pacmpl-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

%% Added Packages
\usepackage{virginialake}\vlnosmallleftlabels
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{color}
\floatstyle{boxed} 
\restylefloat{figure}
%\usepackage{colonequals}

%% Marianela's macros
\renewcommand{\G}{\mathcal{G}}
\newcommand{\Left}{\mathcal{L}}
\newcommand{\Right}{\mathcal{R}}

%Symbols for System labK
\newcommand{\id}{id^{lab}}
\newcommand{\tolab}{\top^{lab}}
\newcommand{\vlab}{\wedge^{lab}}
\newcommand{\olab}{\vlor^{lab}}
\newcommand{\blab}{\square^{lab}}
\newcommand{\dlab}{\lozenge^{lab}}

%Labelled proof system
\renewcommand{\toprule}{\G \Rightarrow \Right, x  \colon   \top}
\newcommand{\vlabr}{\G \Rightarrow \Right, x  \colon   A}
\newcommand{\vlabu}{\G \Rightarrow \Right, x  \colon   B}
\newcommand{\olabr}{\G \Rightarrow \Right, x  \colon   A, x  \colon   B}
\newcommand{\blabr}{\G \Rightarrow \Right, x  \colon   \square A}
\newcommand{\blabu}{\G, x$R$y \Rightarrow \Right, y  \colon   A}
\newcommand{\dlabr}{\G, x$R$y \Rightarrow \Right, x  \colon   \lozenge A}
\newcommand{\dlabu}{\G, x$R$y \Rightarrow \Right, x  \colon   \lozenge A, y  \colon}

%Symbols for system labIK
\newcommand{\botlab}{\bot_{L}^{lab}}
\newcommand{\toplab}{\top_{R}^{lab}}
\newcommand{\andleflab}{\wedge_{L}^{lab}}
\newcommand{\andriglab}{\wedge_{R}^{lab}}
\newcommand{\orleflab}{\vlor_{L}^{lab}}
\newcommand{\orriglabo}{\vlor_{R1}^{lab}}
\newcommand{\orriglabt}{\vlor_{R2}^{lab}}
\newcommand{\irlab}{\vljm_{R}^{lab}}
\newcommand{\illab}{\vljm_{L}^{lab}}
\newcommand{\dllab}{\lozenge_{L}^{lab}}
\newcommand{\drlab}{\lozenge_{R}^{lab}}
\newcommand{\bllab}{\square_{L}^{lab}}
\newcommand{\brlab}{\square_{R}^{lab}}

%Sumbols for System labheartIK
\newcommand{\gklmn}{\boxtimes_{gklmn}}
\newcommand{\ids}{id}
\newcommand{\idg}{id_{g}}
\newcommand{\refl}{refl}
\newcommand{\trans}{trans}
\newcommand{\cut}{cut}
\newcommand{\fone}{F1}
\newcommand{\ftwo}{F2}
\newcommand{\sbot}{\bot_{L}}
\newcommand{\Stop}{\top_{R}}
\newcommand{\svlef}{\wedge_{L}}
\newcommand{\svrig}{\wedge_{R}}
\newcommand{\solef}{\vlor_{L}}
\newcommand{\sorig}{\vlor_{R}}
\newcommand{\sorone}{\vlor_{R1}}
\newcommand{\sotwo}{\vlor_{R2}}
\newcommand{\sir}{\vljm_{R}}
\newcommand{\sil}{\vljm_{L}}
\newcommand{\sdl}{\lozenge_{L}}
\newcommand{\sdr}{\lozenge_{R}}
\newcommand{\sbl}{\square_{L}}
\newcommand{\sbr}{\square_{R}}
\newcommand{\smon}{mon_{L}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\Gone}{\mathcal{G}_{1}}
\newcommand{\Gtwo}{\mathcal{G}_{2}}
\newcommand{\Dw}{\mathcal{D}^{w}}
\newcommand{\Dwone}{\mathcal{D}_{1}^{w}}
\newcommand{\Dwtwo}{\mathcal{D}_{2}^{w}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Done}{\mathcal{D}_{1}}
\newcommand{\Dtwo}{\mathcal{D}_{2}}

%System LABIK
\newcommand{\conjrig}{\G, \Left \Rightarrow \Right, x \colon A}
\newcommand{\conjrigh}{\G, \Left \Rightarrow \Right, x  \colon B}
\newcommand{\conjlef}{\G, \Left, x  \colon  A, x \colon B \Rightarrow \Right}

%% Sonia's macros
\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
\newcommand{\lutz}[1]{{\color{green}[Lutz: #1]}}
\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}

%%% Systems
\newcommand*{\lab}{\mathsf{lab}}
\newcommand*{\IK}{\mathsf{IK}}

%%% Connectives
\newcommand*{\NOT}{\neg}
\newcommand*{\AND}{\mathbin{\wedge}}
\newcommand*{\TOP}{\mathord{\top}}
\newcommand*{\OR}{\mathbin{\vee}}
\newcommand*{\BOT}{\mathord{\bot}}
\newcommand*{\IMP}{\mathbin{\supset}}

\newcommand*{\BOX}{\mathord{\Box}}
\newcommand*{\DIA}{\mathord{\Diamond}}

\begin{document}

%% Title information
\title{Decomposing labelled proof theory\\for intuitionistic modal logic}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

%% Author with single affiliation.
\author{Sonia Marin}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
%  \department{Department1}              %% \department is recommended
  \institution{IT-Universitetet i K{\o}benhavn}            %% \institution is required
%  \streetaddress{Street1 Address1}
%  \city{City1}
%  \state{State1}
%  \postcode{Post-Code1}
  \country{Denmark}                    %% \country is recommended
}
%\email{first1.last1@inst1.edu}          %% \email is recommended

\author{Marianela Morales}
%\authornote{with author2 note}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%  \position{Position2a}
	%  \department{Department2a}             %% \department is recommended
	\institution{Universidad Nacional de C\'ordoba}           %% \institution is required
	%  \streetaddress{Street2a Address2a}
	%  \city{City2a}
	%  \state{State2a}
	%  \postcode{Post-Code2a}
	\country{Argentina}                   %% \country is recommended
}
%\email{first1.last1@inst1.edu}          %% \email is recommended

\author{Lutz Stra{\ss}burger}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position2a}
%  \department{Department2a}             %% \department is recommended
  \institution{Inria Saclay \& LIX} %, \'Ecole Polytechnique}           %% \institution is required
%  \streetaddress{Street2a Address2a}
%  \city{City2a}
%  \state{State2a}
%  \postcode{Post-Code2a}
  \country{France}                   %% \country is recommended
}
%\email{first2.last2@inst2a.com}         %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
We present a labelled deduction for intuitionistic modal logic that
comes with two relation symbols, one for the accessible world
relation associated with the Kripke semantics for modal logics, and
one for the preorder relation associated with the Kripke semantics
for intuitionistic logic. Thus, our labelled system is in close
correspondence to the birelational Kripke models.
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.
%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10011007.10011006.10011008</concept_id>
%<concept_desc>Software and its engineering~General programming languages</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%<concept>
%<concept_id>10003456.10003457.10003521.10003525</concept_id>
%<concept_desc>Social and professional topics~History of programming languages</concept_desc>
%<concept_significance>300</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}
%
%\ccsdesc[500]{Software and its engineering~General programming languages}
%\ccsdesc[300]{Social and professional topics~History of programming languages}
%% End of generated code

%% Keywords
%% comma separated list
%\keywords{Proof theory, Intuitionistic modal logic, Labelled sequents.}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}
%%One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged. Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.

\emph{Labelled deduction} has been proposed by Gabbay 
\todo{add reference}
in the 80’s as a unifying framework throughout proof theory in order to provide proof
systems for a wide range of logics. 
%
For modal logics it can take
the form of labelled natural deduction and labelled sequent systems as
used, for example, by Simpson~\cite{Simpson}, Vigano~\cite{Vigano} and
Negri~\cite{Negri}. 
%
These formalisms make explicit use not only of
labels, but also of relational atoms. 
%
To our knowledge, all labelled
systems proposed so far had only one relational symbol, 
\sonia{Incorrect. We even cite~\cite{Maffezioli} below}
either representing the \emph{accessible world relation $R$} (for modal
logics) or the \emph{future relation $\le$} (for intuitionistic
logic). 
%
In this short note we propose a system that unifies both, and
thus is able to use the full power of the bi-relational semantics for
intuitionistic modal logics.

\sonia{Removed paragraph. Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}
%For sequent systems for intuitionistic logics there is always a choice
%to be made: make the system \emph{single conclusion} following
%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
%variant because of the closer correspondence to the semantics. In that
%respect, our system is closer to~\cite{kuz:str} than
%to~\cite{Simpson} and~\cite{mar:str}.

\section{Preliminaries\todo{give a more informative title}}

\sonia{Removed the part on the classical labelled calculus. Don't think we need it in a short version.}
%%Labelled sequents are formed from by labelled formulas of the form $x \colon A$  and relational atoms of the form $x$R$y$, where $x$, $y$ range over a set of variables and $A$ is a modal formula. A one-sided labelled sequent is then of the form $\G \Rightarrow \Right$ where $\G$ denotes a set of relational atoms and $\Right$ a multiset of labelled formulas. A simple proof system for classical modal logic K can be obtained in this formalism (\textbf{Fig. 1}). 
%%
%%\begin{figure}[h]
%%\begin{center}
%%
%%$\vlderivation {\vlinf{\id}{}{\G \Rightarrow \Right, x: a, x: \vls-a}{}}$
%%\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$
%%
%%
%%$\vliinf{\vlab}{}{\G \Rightarrow \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
%%\hspace{7mm}$\vlinf{\olab}{}{\G \Rightarrow \Right, x \colon \vls[A.B]}{\olabr}$
%%
%%
%%$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
%%\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
%%
%%
%%\end{center}
%%\caption{System labK}
%%\end{figure}
%%These rule schemes can occur in different contexts and different calculi. The context that interests us is when it is applied to modal logic.
%%\\
%%
%%The idea to extend this system to another to capture intuitionistic modal logics allows us to study the Kripke semantics for this type of logics:

\sonia{Formulas need to be defined.

	The language of {intuitionisitic modal logic} is obtained from the one of intuitionistic propositional logic by adding the modal connectives $\BOX$ and $\DIA$. %, standing most generally for \emph{necessity} and \emph{possibility}.
	%
	Starting with a set $\mathcal{A}$ of atomic propositions denoted $a$, modal formulas are constructed from the following grammar:
	%
	$$
	A  ::=
	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
	$$
	%
	%We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.
}

The Kripke semantics for intuitionistic modal logic combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.

\begin{definition}
	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$: $R$ being the modal \emph{accessibility relation} and $\le$ a preorder, satisfying the following conditions:
	\begin{itemize}
		\item[(F1)] For all worlds $u, v, v'$, if $u$R$v$ and $v \le v'$, there exists a $u'$ such that $u \le u'$ and $u'$R$v'$.

		\item[(F2)] For all worlds $u', u, v$, if $u \le v$, there exists a $v'$ such that $u'$R$v'$ and $v\le v'$.
	\end{itemize}

\end{definition}

\begin{definition}
	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V: W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
	\begin{center}
		$w \le w'$ $\Rightarrow$ $V(w)$ $\subseteq$ $V(w')$
	\end{center}

\end{definition}

\vspace{4mm}

We write $w \Vdash a$ iff $a \in V(w)$ and we extend this relation to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:

$w \not\Vdash \bot$

$w \Vdash \vls(A.B)$ iff $w \Vdash A$ and $w \Vdash B$

$w \Vdash \vls[A.B]$ iff $w \Vdash A$ or $w \Vdash B$

$w \Vdash A \vljm B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$

$w \Vdash \square A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$

$w \Vdash \lozenge A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.

%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\

\begin{definition}
	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
\end{definition}

\begin{definition}
	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
\end{definition}

%\begin{figure}[h]
%\begin{center}
%$\vlderivation{\vlinf{\id}{}{\G, \Left, x \colon a \Rightarrow x \colon a }{}}$
%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\G, \Left, x\colon \bot \Rightarrow z\colon A}{}}$
%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\G, \Left \Rightarrow x \colon \top}{}}$
%
%\vspace{2mm}
%
%$\vlinf{\andleflab}{}{\G,\Left, x \colon \vls(A.B) \Rightarrow z \colon C}{\G, \Left, x\colon \vls(A.B,x \colon A, x \colon B \Rightarrow z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\G,\Left \Rightarrow x \colon \vls(A.B)}{\G, \Left \Rightarrow x \colon A}{\G, \Left \Rightarrow x \colon B}$
%
%\vspace{2mm}
%$\vliinf{\orleflab}{}{\G, \Left, x \colon \vls[A.B] \Rightarrow  \colon C}{\G, \Left, x \colon \vls[A.B], x \colon A \Rightarrow z \colon C}{\G, \Left, x \colon \vls[A.B], x   \colon   B \Rightarrow z \colon C}$
%
%\vspace{2mm}
%
%$\vlinf{\orriglabo}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\G, \Left \Rightarrow x   \colon   A}$
%\hspace{7mm}$\vlinf{\orriglabt}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\G, \Left \Rightarrow x \colon  B}$
%
%\vspace{2mm}
%
%$\vliinf{\illab}{}{\G, \Left, x \colon A \vljm B \Rightarrow z \colon C}{\G, \Left, x \colon A \vljm B \Rightarrow x \colon A}{\G, \Left, x \colon A \vljm B, x \colon B \Rightarrow z \colon C}$
%
%\vspace{2mm}
%
%$\vlinf{\irlab}{}{\G, \Left \Rightarrow x \colon A \vljm B}{\G, \Left, x \colon A \Rightarrow x \colon B}$
%
%\vspace{2mm}
%
% $\vlderivation {\vlinf{\bllab}{}{\G, x$R$y, \Left x \colon \square A \Rightarrow z \colon B}{\G, x$R$y, \Left, x \colon \square A, y \colon A \Rightarrow z \colon B}}$
%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\G, \Left \Rightarrow x \colon \square A}{\G, x$R$y, \Left \Rightarrow y \colon A}$
%
%\vspace{2mm}
%
%$\vlinf{\dllab}{$ $y$ fresh $}{\G, \Left, x \colon \lozenge A \Rightarrow z \colon B}{\G, x$R$y, \Left, x \colon \lozenge A, y \colon A \Rightarrow z \colon B}$
%\hspace{5mm}$\vlinf{\drlab}{}{\G, x$R$y, \Left,  \Rightarrow x \colon \lozenge A}{\G, x$R$y, \Left \Rightarrow y \colon A}$
%
%\end{center}
%\caption{System labIK}
%\end{figure}

\sonia{Removed the figure as it has nothing to do with the theorem. Fisher-Servi as well as Plotkin and Sterling only give Hilbert-style axiomatisations for the birelational models, no sequent calculi.
	Therefore, if we want to present this theorem, the axiomatisations also need to be introduced.}

\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]
	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
\end{theorem}

\section{Capturing intuitionistic modal logics with labels}

\sonia{I moved Simpson's system $\lab\IK$ here as we need to make explicit that we are aware of his approach and we propose something else.}
\begin{figure}%[h]

	\begin{center}

		$\vlderivation { \vlin {\ids}{}{\G, \Left, x \colon a \Rightarrow x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\G, \Left, x \colon \bot \Rightarrow z\colon A}{\vlhy {}}}$

		\vspace{3mm}

		$\vlderivation {\vlin {\svlef}{}{\G, \Left, x \colon \vls(A.B) \Rightarrow z \colon C}{\vlhy {\G, \Left, x \colon A, x \colon B \Rightarrow z \colon C}}}$
		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\G, \Left, \Rightarrow x \colon \vls(A.B)}{\vlhy {\G, \Left \Rightarrow x \colon A }}{\vlhy {\G, \Left \Rightarrow x \colon B}}}$

		\vspace{3mm}

		$\vlderivation {\vliin {\solef}{}{\G, \Left, x \colon \vls[A.B] \Rightarrow z \colon C}{\vlhy {\G, \Left, x \colon A \Rightarrow z \colon C}}{\vlhy {\G, \Left, x \colon B \Rightarrow z \colon C}}}$
		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlhy {\G, \Left \Rightarrow x \colon A}}}$
		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlhy {\G, \Left \Rightarrow x \colon B}}}$

		\vspace{3mm}

		$\vlderivation {\vliin{\sil}{}{\G, \Left, x \colon A \vljm B \Rightarrow z \colon C}{\vlhy {\G, \Left \Rightarrow x \colon A}}{\vlhy {\G, \Left, x \colon B \Rightarrow z \colon C}}}$
		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\G,  \Left, x \colon A \Rightarrow x \colon B}{\vlhy {\G, \Left, x \colon A \Rightarrow x \colon B}}}$

		\vspace{3mm}

		$\vlderivation { \vlin {\sbl}{}{\G, x$R$y, \Left, x \colon \square A \Rightarrow z\colon B}{\vlhy {\G, x$R$y, \Left, x \colon \square A, y \colon A \Rightarrow z\colon B}}}$
		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\G, \Left \Rightarrow x \colon \square A}{\vlhy {\G, x$R$y, \Left \Rightarrow y \colon A}}}$

		\vspace{3mm}

		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\G, \Left, x \colon \lozenge A \Rightarrow z \colon B}{\vlhy {\G, x$R$y, \Left, y \colon A \Rightarrow z \colon B}}}$
		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\G,x$R$y, \Left \Rightarrow x \colon \lozenge A}{\vlhy {\G, x$R$y, \Left \Rightarrow y \colon A }}}$

	\end{center}

	\caption{System $\lab\IK$}
	\label{fig:labIK}
\end{figure}

\todo{Some background needs to be added}
\begin{theorem}[Simpson~\cite{Simpson}]
	\label{thm:simpson-sound-compl}
	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
\end{theorem}

\begin{figure}%[h]
	\begin{center}

		%$\vlinf{\sbot}{}{\G,\Left, x \colon \bot \Rightarrow \Right}{}$
		%\hspace{7mm}$\vlinf{\ids}{}{\G, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$ \hspace{7mm}$\vlinf{\Stop}{}{\G, \Left \Rightarrow \Right, x \colon \top}{}$
		$\vlderivation{\vlinf{\id}{}{\G, \Left, x \colon a \Rightarrow x \colon a }{}}$
		\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\G, \Left, x\colon \bot \Rightarrow z\colon A}{}}$
		\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\G, \Left \Rightarrow x \colon \top}{}}$

		\vspace{4mm}

		$\vlinf{\svlef}{}{\G,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
		\hspace{7mm}$\vliinf{\svrig}{}{\G,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$

		\vspace{4mm}

		$\vliinf{\solef}{}{\G, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\G, \Left, x   \colon   A \Rightarrow \Right}{\G, \Left, x   \colon   B \Rightarrow \Right}$
		\hspace{7mm}$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$

		\vspace{4mm}

		$\vlinf{\sir}{$ $y$ fresh$}{\G, \Left \Rightarrow \Right, x \colon A \vljm B}{\G, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$

		\vspace{4mm}

		$\vliinf{\sil}{}{\G, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right}{\G, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right, y \colon A}{\G, \Left, x \le y, x \colon A \vljm B, y \colon B \Rightarrow \Right}$

		\vspace{4mm}

		$\vlderivation {\vlinf{\sbl}{}{\G, \Left, x \le y, y$R$z, x \colon \square A \Rightarrow \Right}{\G,\Left, x \le y, y$R$z, x \colon \square A, z \colon A \Rightarrow \Right}}$
		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\G, \Left \Rightarrow \Right, x \colon \square A}{\G, \Left, x \le y, y$R$z \Rightarrow \Right, z \colon A}$

		\vspace{4mm}

		$\vlinf{\sdl}{$ $y$ fresh $}{\G, \Left, x \colon \lozenge A \Rightarrow \Right}{\G, \Left, x$R$y, y \colon A \Rightarrow \Right}$
		\hspace{5mm}$\vlinf{\sdr}{}{\G, \Left, x$R$y \Rightarrow \Right, x \colon \lozenge A}{\G, \Left, x$R$y \Rightarrow \Right, x \colon \lozenge A, y \colon A}$

		\vspace{2mm}

		\vspace{2mm}

		$\vlinf{\refl}{}{\G, \Left \Rightarrow \Right}{\G, x\le x, \Left, \Right}$
		\hspace{7mm} $\vlinf{\trans}{}{\G, x \le y, y \le z, \Left \Rightarrow \Right}{\G, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$

		\vspace{2mm}

		$\vlinf{\fone}{$ $u$ fresh$}{\G, \Left, x$R$y, y \le z \Rightarrow \Right}{\G, \Left, x$R$y, y \le z, x \le u, u$R$z \Rightarrow \Right}$
		\hspace{3mm} $\vlinf{\ftwo}{u$ fresh$}{\G, \Left, x$R$y,x \le z \Rightarrow \Right}{\G, \Left, x$R$y, x \le z, y \le u, z$R$u \Rightarrow \Right }$

	\end{center}

	\caption{System $\lab\heartsuit\IK$}
	\label{fig:labHIK}
\end{figure}

Echoing the definition of bi-relational structures, another extension of labelled deduction to the intuitionistic setting would be to use two sorts of relational atoms, one for the modal relation $R$ and another one for the intuitionistic relation $\leq$. 
%
This is the approach developed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}. 
%
The idea is to extend labelled sequents with a preorder relation symbol in order to capture intuitionistic modal logics, that is to define intuitionistic labelled sequents from labelled formulas $x \colon A$, relational atoms $x$R$y$, and preorder atoms of the form $x \leq y$, where x, y range over a set of labels and A is an intuitionistic modal formula.

A two-sided intuitionistic labelled sequent would be of the form $\G, \Left \Rightarrow \Right$ where $\G$ denotes a set of relational and preorder atoms, and $\Left$ and $\Right$ are multiset of labelled formulas. 
%
We then obtain a proof system lab$\heartsuit$IK (\ref{fig:labHIK}) for intuitionistic modal logic in this formalism.
%
%As we mentioned, we obtain a proof system lab$\heartsuit$IK which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:

\begin{theorem}
	\label{thm:sound-compl}
	A formula $A$ is provable in the calculus $\lab\heartsuit\IK$ if and only if $A$ is valid in every bi-relational frame.
\end{theorem}

\sonia{Rewrote the last two paragraphs more succinctly. Should we say more?}

On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
%
On the other hand, we show that $\lab\heartsuit\IK$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.

%We show that each rule from our system is sound.
%
%We also present a syntactic completeness proof with respect the Hilbert system: we prove all Hilbert axioms using the rules from our system (i.e. proof of all propositional intuitionistic axioms, the five variants of k axiom from the intuitionistic syntax, simulate the necessitation rule and simulate modus ponens).
%
%We present a completeness proof for our system lab$\heartsuit$IK using the Simpson system. 
%
%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
%
%We show the proof by case analysis. 
%
%Most of the rules from Simpson system are the same as the rules in the system lab$\heartsuit$IK, then we prove for the rules that are different.

\begin{thebibliography}{4}
	\bibitem{Maffezioli}
	Paolo Maffezioli, Alberto Naibo, and Sara Negri. \emph{The Church-Fitch knowability paradox in the light of structural proof theory}. Synthese, 190(14):2677-2716, 2013.

	%	\bibitem{Fitch}
	%	Frederic B Fitch. \emph{Tree proofs in modal logic}. Journal of Symbolic Logic, 31(1):152, 1966.

	\bibitem{Negri}
	Sara Negri. \emph{Proof analysis in modal logics}. Journal of Philosophical Logic, 34:507-544, 2005.

	\bibitem{Simpson}
	Alex Simpson. \emph{The Proof Theory and Semantics of Intuitionistic Modal Logic}. PhD thesis, University of Edinburgh, 1994.

	\bibitem{Vigano}
	Luca Vigan\`o. \emph{Labelled Non-Classical Logic}. Kluwer Academic Publisher, 2000.

	%	\bibitem{Marin}
	%	Sonia Marin. \emph{Modal proof theory through a focused telescope}. PhD thesis, Université Paris-Saclay, 2017.

	\bibitem{Fischer}
	Gis\`ele Fischer-Servi.\emph{ Axiomatizations for some intuitionistic modal logics}. Rendiconti del Seminario Matematico dell’ Universit`a Politecnica di Torino, 42(3):179-194, 1984.

	\bibitem{Plotkin}
	Gordon D. Plotkin and Colin P. Stirling. \emph{A framework for intuitionistic modal logic}. In J. Y. Halpern, editor,1st Conference on Theoretical Aspects of Reasoning About Knowledge.
	Morgan Kaufmann, 1986.

	%	\bibitem{kuz:str}
	%	Roman Kuznets and Lutz Stra{\ss}burger. \emph{Maehara-style Modal Nested Calculi}. Research report, Inria RR-9123, 2017.

	%	\bibitem{mar:str}
	%	Sonia Marin and Lutz Stra{\ss}burger. \emph{Label-free Modular Systems for Classical and Intuitionistic Modal Logics}. In Advances in Modal Logics, 2014.

\end{thebibliography}

%% Acknowledgments
%\begin{acks}                            %% acks environment is optional
%                                        %% contents suppressed with 'anonymous'
%  %% Commands \grantsponsor{<sponsorID>}{<name>}{<url>} and
%  %% \grantnum[<url>]{<sponsorID>}{<number>} should be used to
%  %% acknowledge financial support and will be used by metadata
%  %% extraction tools.
%  This material is based upon work supported by the
%  \grantsponsor{GS100000001}{National Science
%    Foundation}{http://dx.doi.org/10.13039/100000001} under Grant
%  No.~\grantnum{GS100000001}{nnnnnnn} and Grant
%  No.~\grantnum{GS100000001}{mmmmmmm}.  Any opinions, findings, and
%  conclusions or recommendations expressed in this material are those
%  of the author and do not necessarily reflect the views of the
%  National Science Foundation.
%\end{acks}

%% Bibliography
%\bibliography{bibfile}

%% Appendix
%\appendix
%\section{Appendix}
%
%Text of appendix \ldots

\end{document}

### 2018-05-01 WiL.tex
adding content for the 5-page abstract

@@
 \usepackage{color}
+\usepackage{bm}
+
 \floatstyle{boxed} 
@@
 %\usepackage{colonequals}
+\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
 
@@
 \newcommand*{\DIA}{\mathord{\Diamond}}
+
+\newcommand*{\labels}[2]{{\color{blue}{#1}\:\colon}{#2}}
+\newcommand{\SEQ}{\Rightarrow}
+\newcommand*{\DD}{\mathcal{D}}
+\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+\newcommand*{\invr}[1]{#1^\bullet}
+\newcommand*{\rel}{R}
+\newcommand*{\rlabrn}[2][]  {\rn{#2}_{R#1}}%^\lab}}
+\newcommand*{\llabrn}[2][]  {\rn{#2}_{L#1}}%^\lab}}
 
@@
 
-\emph{Labelled deduction} has been proposed by Gabbay 
-\todo{add reference}
-in the 80’s as a unifying framework throughout proof theory in order to provide proof
+\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80's as a unifying framework throughout proof theory in order to provide proof
 systems for a wide range of logics. 
@@
 
-The Kripke semantics for intuitionistic modal logic combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
+\marianela{is this enough as an introduction of the axiomatisations to present the theorem 2.5?}
+
+The axiomatisation that is now generally accepted as intuitionistic modal logic denoted by IK was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi ~\cite{Fischer}, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic.
+It then was investigated in detail in ~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
+
+The Kripke semantics for IK was first defined by Fischer-Servi in ~\cite{Fischer}.
+This semantics for intuitionistic modal logic combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
 
 \begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$: $R$ being the modal \emph{accessibility relation} and $\le$ a preorder, satisfying the following conditions:
+	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$: $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
 	\begin{itemize}
@@
 %We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
+
+We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \vljm \bot$).
+
+From the monotonicity of the valuation function $V$ , we get a monotonicity property for the relation:
+\begin{proposition}(Monotonicity) 
+For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
+
+\end{proposition}
 
@@
 \sonia{I moved Simpson's system $\lab\IK$ here as we need to make explicit that we are aware of his approach and we propose something else.}
+
+Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
+This worked as well in the labelled setting as in the ordinary sequent case: we present Simpson's sequent system labIK (\ref{fig:labIK}) where intuitionistic labelled sequents are written $\G, \Left \SEQ z \colon C$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\G$.
+
 \begin{figure}%[h]
@@
 
-\todo{Some background needs to be added}
+\todo{Some background needs to be added} \marianela{what about the paragraph that I just added before?}
 \begin{theorem}[Simpson~\cite{Simpson}]
@@
 %
-We then obtain a proof system lab$\heartsuit$IK (\ref{fig:labHIK}) for intuitionistic modal logic in this formalism.
+We then obtain a proof system lab$\heartsuit$IK (\ref{fig:labHIK}) for intuitionistic modal logic in this formalism. \marianela{I can't put the figure 2 before this!!}
 %
@@
 On the other hand, we show that $\lab\heartsuit\IK$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
+\marianela{Sonia, what do you think about mention your result of completeness with cut elimination?}
+
+To show completeness wrt.~Simpson's $\lab\IK$ we obtain the proof for the next proposition:\marianela{I do not know if it is a good idea to add this but...}
+
+\begin{proposition}
+	\begin{enumerate}
+		\item\label{StoM-seq} If there is a proof $\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{m}}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\heartsuit\IK$.
+
+		\item\label{MtoS-seq} If there is a proof $\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right}}$ in $\lab\heartsuit\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{s}}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$.
+	\end{enumerate}
+\end{proposition}
+
+\vspace{2mm}
+
+On the other hand, as part of the proof of Theorem~\ref{thm:simpson-sound-compl}, we obtain the proof for different lemmas such as:
+
+\begin{lemma}\label{lem:weak}\hbox{}\quad
+	\begin{enumerate}
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\G, \Left \SEQ \Right}}$
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\G, \Left \SEQ \Right}}$
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\rn w}}{\G, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
+	\end{enumerate}
+\end{lemma}
+
+\begin{lemma}\label{lem:inv}\hbox{}\quad
+	\begin{enumerate}
+	\item
+	If there exists a proof 
+	$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
+	then there exists a proof 
+	$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\G, \Left, \labels{y}{B} \SEQ \Right}}$
+	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+	\item
+	If there exists a proof 
+	$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
+	then there exists a proof 
+	$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\G, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
+	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+	\item 
+	If there exists a proof 
+	$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
+	then there exists a proof 
+	$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\G, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
+	of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
+
+	\item 
+	If there exists a proof 
+	$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
+	then there exists a proof 
+	$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\G, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
+	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+	\end{enumerate}
+\end{lemma}
 
@@
 
+	\bibitem{Ewald}
+	W. B. Ewald. \emph{Intuitionistic tense and modal logic}. The Journal of Symbolic Logic, 51(1):166–179, 1986.
+
+	\bibitem{Gabbay}
+	Dov M. Gabbay. \emph{Labelled Deductive Systems}. Clarendon Press, 1996.
+
 	%	\bibitem{kuz:str}

### 2018-05-01 WiL.tex
minor things

@@
 %% Title information
-\title{Decomposing labelled proof theory\\for intuitionistic modal logic}         %% [Short Title] is optional;
+\title[Decomposing labelled proof theory for intuitionistic modal logic]{Decomposing labelled proof theory\\ for intuitionistic modal logic}         $$[Short Title] is optional;
                                         %% when present, will be used in
@@
 
-\sonia{Removed paragraph. Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
+\sonia{Removed paragraph.
+Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}\lutz{maybe, but getting all the theorems right is not so easy, we had a hard time in the nested variant}
 
-\section{Preliminaries\todo{give a more informative title}}
+For sequent systems for intuitionistic logics there is always a choice
+to be made: make the system \emph{single conclusion} following
+Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
+Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
+variant because of the closer correspondence to the semantics. In that
+respect, our system is closer to~\cite{kuz:str} than
+to~\cite{Simpson} and~\cite{mar:str}.
+
+\section{Preliminaries on intuitionistic modal logics}
 

### 2018-05-01 WiL.tex
minor things

@@
 %% Title information
-\title[Decomposing labelled proof theory for intuitionistic modal logic]{Decomposing labelled proof theory\\ for intuitionistic modal logic}         $$[Short Title] is optional;
+\title[Decomposing labelled proof theory for intuitionistic modal logic]{Decomposing labelled proof theory\\ for intuitionistic modal logic}        %%[Short Title] is optional;
                                         %% when present, will be used in
@@
 \begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$: $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
+	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
 	\begin{itemize}
@@
 \begin{definition}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V: W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-	\begin{center}
-		$w \le w'$ $\Rightarrow$ $V(w)$ $\subseteq$ $V(w')$
-	\end{center}
-
+	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
+$$w \le w' \Rightarrow V(w)\subseteq V(w')$$
 \end{definition}
-
-\vspace{4mm}
 
@@
 
-\begin{figure}%[h]
+\begin{figure*}%[h]
 	\begin{center}
@@
 
-	\caption{System $\lab\heartsuit\IK$}
+	\caption{System $\lab\heartsuit\IK$}% \lutz{that figure should be two-column...}}
 	\label{fig:labHIK}
-\end{figure}
+\end{figure*}
 

### 2018-05-01 WiL.tex
some small modif

--- 2018-05-01 WiL.tex
@@
 %%% Systems
+\newcommand*{\ax}[1]{\mathsf{#1}}
 \newcommand*{\lab}{\mathsf{lab}}
@@
 
+%%% Labelled sequents
 \newcommand*{\labels}[2]{{\color{blue}{#1}\:\colon}{#2}}
@@
 \newcommand*{\rel}{R}
+
+%%% Labelled rules
+\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
 \newcommand*{\rlabrn}[2][]  {\rn{#2}_{R#1}}%^\lab}}
 \newcommand*{\llabrn}[2][]  {\rn{#2}_{L#1}}%^\lab}}
+%
+%\DeclareFontShape{U}{MnSymbolC}{m}{n}{
+%	<-6>  MnSymbolC5
+%	<6-7>  MnSymbolC6
+%	<7-8>  MnSymbolC7
+%	<8-9>  MnSymbolC8
+%	<9-10> MnSymbolC9
+%	<10-12> MnSymbolC10
+%	<12->   MnSymbolC12}{}
+%\DeclareFontShape{U}{MnSymbolC}{b}{n}{
+%	<-6>  MnSymbolC-Bold5
+%	<6-7>  MnSymbolC-Bold6
+%	<7-8>  MnSymbolC-Bold7
+%	<8-9>  MnSymbolC-Bold8
+%	<9-10> MnSymbolC-Bold9
+%	<10-12> MnSymbolC-Bold10
+%	<12->   MnSymbolC-Bold12}{}
+%
+%\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
+%%
+%\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
+%\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
+%
+\newcommand*{\brsym}{\mathord{\scalebox{.8}{$\blacksquare$}}}
+\newcommand*{\boxbrn}[1]{\rn{\brsym_\rn{#1}}}%^{\lab}}}
+\newcommand*{\diasym}{\mathord{\blacklozenge}}
+\newcommand*{\diabrn}[1][]{\rn{\diasym_\rn{#1}}}
 
@@
 %% Title information
-\title[Decomposing labelled proof theory for intuitionistic modal logic]{Decomposing labelled proof theory\\ for intuitionistic modal logic}         $$[Short Title] is optional;
+\title{Decomposing labelled proof theory for~intuitionistic~modal~logic}         
+										%%[Short Title] is optional;
                                         %% when present, will be used in
@@
 \author{Sonia Marin}
-%\authornote{with author1 note}          %% \authornote is optional;
+\authornote{Funded by the Qatar National Research Council project MetaCLF nb. xxx. }          %% \authornote is optional;
                                         %% can be repeated if necessary
@@
 \author{Marianela Morales}
-%\authornote{with author2 note}          %% \authornote is optional;
+\authornote{with author2 note}          %% \authornote is optional;
 %% can be repeated if necessary
@@
 
-\sonia{Removed paragraph.
-Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}\lutz{maybe, but getting all the theorems right is not so easy, we had a hard time in the nested variant}
+\sonia{Removed paragraph. Simpson's system can easily be made multi-conclusion in the style of Maehara without the $\le$-atoms.}
+\lutz{maybe, but getting all the theorems right is not so easy, we had a hard time in the nested variant}
+\sonia{I did not mean it like that.
+I mean that the point of our system is not that it is multi-conclusion (it is that it allows us to give systems for some more logics!).
+This paragraph is confusing as such because it shifts the attention of the reader.
+I think that we can actually restrict to single conclusion with no difference.}
 
@@
 
-\section{Preliminaries on intuitionistic modal logics}
+\section{Intuitionistic modal logics}
 
@@
 \marianela{is this enough as an introduction of the axiomatisations to present the theorem 2.5?}
+\sonia{no, we would need the formal definition. But the text is good.}
 
 The axiomatisation that is now generally accepted as intuitionistic modal logic denoted by IK was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi ~\cite{Fischer}, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic.
-It then was investigated in detail in ~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
+%
+It then was investigated in detail in ~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
+%
+it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
 
 The Kripke semantics for IK was first defined by Fischer-Servi in ~\cite{Fischer}.
+%
 This semantics for intuitionistic modal logic combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
@@
 
-$w \not\Vdash \bot$
+$w \not\Vdash \bot$ (i.e.~it is never the case that $w \Vdash \bot$)
 
@@
 
-We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \vljm \bot$).
+%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$.%, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \vljm \bot$).
 
-From the monotonicity of the valuation function $V$ , we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
-For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
+%From the monotonicity of the valuation function $V$ , we get a monotonicity property for the relation:
+%\begin{proposition}(Monotonicity) 
+%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
 
-\end{proposition}
+%\end{proposition}
 
@@
 
-To show completeness wrt.~Simpson's $\lab\IK$ we obtain the proof for the next proposition:\marianela{I do not know if it is a good idea to add this but...}
+%To show completeness wrt.~Simpson's $\lab\IK$ we obtain the proof for the next proposition:\marianela{I do not know if it is a good idea to add this but...}
+%
+%\begin{proposition}
+%	\begin{enumerate}
+%		\item\label{StoM-seq} If there is a proof $\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{m}}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\heartsuit\IK$.
+%		
+%		\item\label{MtoS-seq} If there is a proof $\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right}}$ in $\lab\heartsuit\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{s}}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$.
+%	\end{enumerate}
+%\end{proposition}
+%
+%\vspace{2mm}
+%
+%On the other hand, as part of the proof of Theorem~\ref{thm:simpson-sound-compl}, we obtain the proof for different lemmas such as:
+%
+%\begin{lemma}\label{lem:weak}\hbox{}\quad
+%	\begin{enumerate}
+%		\item 
+%		If there exists a proof 
+%		$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
+%		then there exists a proof 
+%		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\G, \Left \SEQ \Right}}$
+%		
+%		\item 
+%		If there exists a proof 
+%		$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
+%		then there exists a proof 
+%		$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\G, \Left \SEQ \Right}}$
+%		
+%		\item 
+%		If there exists a proof 
+%		$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right}}$ 
+%		then there exists a proof 
+%		$\vlderivation{\vlhtr{\DD^{\rn w}}{\G, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
+%	\end{enumerate}
+%\end{lemma}
+%
+%\begin{lemma}\label{lem:inv}\hbox{}\quad
+%	\begin{enumerate}
+%	\item
+%	If there exists a proof 
+%	$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
+%	then there exists a proof 
+%	$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\G, \Left, \labels{y}{B} \SEQ \Right}}$
+%	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+%	
+%	\item
+%	If there exists a proof 
+%	$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
+%	then there exists a proof 
+%	$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\G, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
+%	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+%	
+%	\item 
+%	If there exists a proof 
+%	$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
+%	then there exists a proof 
+%	$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\G, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
+%	of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
+%	
+%	\item 
+%	If there exists a proof 
+%	$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
+%	then there exists a proof 
+%	$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\G, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
+%	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+%	
+%	\end{enumerate}
+%\end{lemma}
+%
 
-\begin{proposition}
-	\begin{enumerate}
-		\item\label{StoM-seq} If there is a proof $\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{m}}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\heartsuit\IK$.
+Proof of $\ax{4_{\BOX}} \colon \BOX A \IMP \BOX\BOX A$
 
-		\item\label{MtoS-seq} If there is a proof $\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right}}$ in $\lab\heartsuit\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{s}}{\G, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$.
-	\end{enumerate}
-\end{proposition}
+$\vlderivation{
+	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
+		\vliq{\rlabrn\BOX}{}{x \le w, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
+			\vlin{\rn{F_1}}{}{x \le w, w \le w', \bm{w' \rel v}, \bm{v \le v'}, v' \rel u, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+				\vlin{\rn{trans}}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, \bm{w' \le t}, \bm{t \rel v'}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+					\vlin{\boxbrn{4}}{}{x \le w, w \le w', w' \rel v, v \le v', \bm{v' \rel u}, w' \le t, \bm{t \rel v'}, w \le t \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+						\vlin{\labrn\BOX}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, w' \le t, t \rel v', w \le t, \bm{t \rel u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+							\vlin{\labrn{id}}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, w' \le t, t \rel v', w \le t, t \rel u, \labels{w}{\BOX A}, \labels{u}{A} \SEQ \labels{u}{A}}{
+								\vlhy{}
+							}
+						}
+					}
+				}
+			}
+		}
+	}
+}
+$
 
-\vspace{2mm}
+Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
 
-On the other hand, as part of the proof of Theorem~\ref{thm:simpson-sound-compl}, we obtain the proof for different lemmas such as:
-
-\begin{lemma}\label{lem:weak}\hbox{}\quad
-	\begin{enumerate}
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\G, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\G, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\rn w}}{\G, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
-	\end{enumerate}
-\end{lemma}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-	\item
-	If there exists a proof 
-	$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-	then there exists a proof 
-	$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\G, \Left, \labels{y}{B} \SEQ \Right}}$
-	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\item
-	If there exists a proof 
-	$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-	then there exists a proof 
-	$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\G, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\item 
-	If there exists a proof 
-	$\vlderivation{\vlhtr{\DD}{\G, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-	then there exists a proof 
-	$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\G, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-	of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-	\item 
-	If there exists a proof 
-	$\vlderivation{\vlhtr{\DD}{\G, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-	then there exists a proof 
-	$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\G, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-	of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
+$\vlderivation{
+	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
+		\vliq{\llabrn\DIA}{}{x \le w, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
+			\vlin{\diasym_\rn{4}}{}{x \le w, w \rel v, v \rel u, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
+				\vlin{\rlabrn\DIA}{}{x \le w, w \rel v, v \rel u, u \le u', w \rel u'  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
+					\vlin{\labrn{id}}{}{x \le w, w \rel v, v \rel u, u \le u', w \rel u'  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
+						\vlhy{}
+					}
+				}
+			}
+		}
+	}
+}
+$
 

### 2019-05-27 thesis-Marianela/thesis/chapters/conclusion.tex
thesis

\chapter{Conclusiones}
\label{cap:conclusion}

Este último capítulo abarca, por un lado, un pequeño resumen de lo realizado a lo largo de esta tesis, como así también algunos detalles sobre las líneas de trabajo futuro. Por otro lado, se incluye una breve sección sobre la experiencia que tuve a la hora de realizar este trabajo para finalizar mi carrera como Licenciada en Ciencias de la Computación.

\section{Sobre la tesis}

En este trabajo estudiamos un sistema de prueba etiquetado para la lógica modal intuicionista. Para lograr este resultado se requirió el estudio de conceptos fundamentales para el desarrollo de esta contribución. Los mismos fueron introducidos a lo largo de los primeros capítulos de la tesis. Comenzamos repasando la sintaxis y la semántica de la lógica modal básica, para luego introducir una axiomatización a la Hilbert y otra a la Gentzen, en particular, nos enfocamos en el sistema de secuentes etiquetados propuesto en~\cite{negri2005}. Luego nos centramos en la lógica modal intuicionista, donde nuevamente estudiamos su sintaxis y semántica, para comprender las herramientas necesarias para introducir un nuevo sistema de secuentes etiquetados que nos permitiera capturar este tipo de lógica.

El enfoque adoptado en este trabajo final consiste  en extender el sistema para la lógica modal básica propuesto por Negri para capturar la lógica modal intuicionista, que denominamos $\labIKh$. Para ello agregamos un nuevo símbolo de relación: la relación futura o mejor conocida como relación de pre-orden $\le$. A diferencia de la lógica modal básica, los operadores modales $\Diamond$ y $\square$ no son duales, debido a que la sintaxis de la lógica modal intuicionista no presenta el operador de negación $\neg$. Por tal motivo, resulta necesario contar con dos reglas de secuentes para cada operador para obtener un sistema completo. Otro aspecto a tener en cuenta fue la necesidad de reglas que caractericen las condiciones de la relación de pre-orden (es decir, reflexividad y transitividad). Este enfoque resulta novedoso ya que nos permite poner el sistema de prueba en estrecha relación con la semántica birelacional de Kripke.

En este trabajo final demostramos que el cálculo de secuentes para la lógica modal intuicionista que definimos es correcto y completo. Esto quiere decir, por un lado, que cada una de las reglas introducidas son semánticamente correctas, y por el otro, que son suficientes para caracterizar todos los teoremas de la lógica. En particular, demostramos completitud sintácticamente por medio del sistema a la Hilbert, lo cual nos permite concluir que el sistema $\labIKh$ es correcto y completo con la regla de $\mathsf{cut}$. Sin embargo, continuamos trabajando para obtener un sistema que sea completo libre de $\mathsf{cut}$. Una alternativa para lograr este tipo de sistemas, consiste en demostrar la propiedad de \emph{cut elimination}, aunque decidimos continuar nuestro trabajo con el estudio de sistemas completos libres de $\mathsf{cut}$, por el enorme desafío que representa dicha prueba. El sistema propuesto por Simpson~\cite{simpson1994} se presenta como una buena alternativa, debido a que resulta simple establecer una correspondencia entre las reglas de tal sistema y las reglas de nuestro sistema $\labIKh$. Para completar esta demostración, es necesario demostrar que el resto de las reglas de Simpson pueden ser deducidas en nuestro sistema. Esta conjetura terminará de ser formalizada y estudiada en nuestro trabajo futuro. Vale la pena destacar que, a pesar de poseer reglas similares a nuestro sistema, el sistema de Simpson no es suficiente para capturar la semántica de la lógica modal intuicionista. Como se puede observar en la Figura \ref{fig:simpson}, las reglas presentadas para el operador $\square$ no capturan la relación de pre-orden así como tampoco el sistema nos permite hablar de la implicación intuicionista. Dado que el cálculo de secuentes etiquetados propuesto en este trabajo nos permite hablar tanto de la relación de pre-orden como de la implicación intuicionista, es posible continuar con el estudio de esta demostración para lograr que el sistema $\labIKh$ sea un sistema completo sin la regla de $\mathsf{cut}$.

Por otra parte, nuestro trabajo futuro también contempla el estudio de extensiones del sistema para caracterizar lógicas más fuertes, en particular, para restringir la clase de frames que queremos considerar. En el último capítulo discutimos extensiones con el axioma $\agklmn$, presentando una nueva regla de secuente para el sistema $\labIKh$, y demostrando completitud para este nuevo sistema. Por el momento, sólo se discutió completitud para el caso $k = l = m = n = \mathsf{1}$ pero se continuará con el desarrollo del caso general. Esta demostración y el estudio de otras extensiones es parte de lo que seguiremos trabajando en un futuro próximo.

Vale la pena agregar que una de las principales ventajas del sistema de secuentes etiquetado $\labIKh$, es que nos permite extender de una manera sencilla a otros sistemas. Por otro lado, gracias al uso de etiquetas, es posible obtener una demostración simple de completitud.

Finalmente, consideramos que el sistema propuesto en este trabajo final, constituye una herramienta importante para el estudio de la complejidad computacional de las tareas de inferencia de la lógica modal intuicionista. En particular, del problema de decidir si una fórmula de esta lógica es válida. Esto también forma parte de las posibles líneas de investigación futuras.

 \section{Sobre mi experiencia de trabajo final de Licenciatura}

 Los comienzos de mi tesis surgieron a partir de una pasantía realizada en Francia desde diciembre de 2017 a marzo de 2018. El objetivo propuesto fue obtener mi primer experiencia en el mundo de la investigación y fue allí donde descubrí con certeza que esto era lo quería para mi futuro. Mi pasantía se realizó en INRIA bajo la supervisión del Dr. Lutz Strassburger en el equipo PARSIFAL, dirigido por el Dr. Dale Miller.

 Mis estudios que constituyen la base de mi trabajo final de Licenciatura comenzaron allí en Palaiseau - Saclay. Luego de tener la oportunidad de indagar en otros temas como \emph{nested sequents} y \emph{combinatorial proofs}, decidí inclinarme por el estudio de la lógica modal intuicionista y su teoría de prueba. A pesar de que antes de esta pasantía realicé un curso de lógicas modales en FaMAF con el Dr. Carlos Areces y el Dr. Raul Fervari, este fue mi primer acercamiento a la teoría de prueba. Comenzar con el estudio de dicha área, constituyó uno de mis mayores desafíos en conjunto con un nuevo idioma, una nueva cultura, un nuevo grupo humano y mi primera vez en investigación. Durante mi pasantía tuve la oportunidad de visitar y colaborar con Sonia Marin (post-doc en IT-University de Copenhague y PhD obtenido con Dr. Lutz Strassburger) quien fue uno de mis mayores soportes a lo largo de mi trabajo en INRIA.

Una vez concluida mi pasantía continué con mi trabajo de Licenciatura acompañada del Dr. Raul Fervari de la FaMAF quien actualmente es uno de mis directores de tesis junto con el Dr. Lutz Strassburger. En cada uno de mis avances fui también recibiendo sugerencias, consejos y correcciones del Dr. Carlos Areces.

Considero que dicha pasantía fue una buena oportunidad para afianzar los conocimientos obtenidos en diferentes etapas de la carrera. Para concluir, es importante destacar que los aprendizajes adquiridos resultan una base fundamental para continuar con mis estudios de doctorado.

### 2019-05-27 thesis-Marianela/thesis/chapters/futuro.tex
thesis

\chapter{Trabajo futuro}
\label{cap:future}
%En este capítulo se describirá un resultado que constituye la continuación de este trabajo final. Presentamos algunas extensiones de nuestro sistema para lógicas más fuertes, en particular, extendemos el sistema $\labIKh$ añadiendo el axioma de Scott-Lemmon o también conocido como $\agklmn$
 En este capítulo se describirán brevemente dos resultados que constituyen la continuación de este trabajo final. 
 En primer lugar discutiremos la demostración de completitud por medio del sistema de Simpson~\cite{simpson1994} mencionada anteriormente, y luego presentaremos algunas extensiones de nuestro sistema para lógicas más fuertes. En particular, para esto último, extendemos el sistema $\labIKh$ añadiendo el axioma de Scott-Lemmon o también conocido como $\agklmn$.

\input{chapters/simpson.tex}
\input{chapters/gklmn.tex}

### 2019-05-27 thesis-Marianela/thesis/chapters/introd.tex
thesis

\renewcommand{\chaptername}{}
\chapter{Introducción}
%Las lógicas modales clásicas son extensiones de la lógica clásica con nuevos operadores llamados $modalidades$.
Existen al menos dos formas de caracterizar todas las verdades o teoremas de una lógica: por un lado, el formato conocido como \emph{axiomatización a la Hilbert} y por otra parte, el formato que sigue el \emph{estilo de Gentzen}, el cual utiliza reglas de secuentes. 
En este trabajo final, nuestra contribución se basa en un cálculo de secuentes para lógicas modales intuicionistas. El resultado se obtiene a partir de extender un cálculo para lógicas modales clásicas con una relación de pre-orden ($\le$) (además de la relación de accesibilidad que nos provee la lógica modal básica) con el objetivo de poder capturar el comportamiento intuicionista. Desde un punto de vista de la lógica modal, esencialmente la lógica modal intuicionista es simplemente una lógica con dos modalidades, donde una de ellas es interpretada en una relación de pre-orden. En esta introducción, haremos un breve recorrido por la historia de la \emph{teoría de prueba} y su relación con las lógicas modales, así como también veremos qué aporta nuestro nuevo cálculo sobre otros.

\section{Teoría de prueba}
En el razonamiento matemático, existen los teoremas y sus demostraciones. Frecuentemente, existen distintas demostraciones para un mismo teorema y nos interesa estudiar y entender sus similitudes y sus diferencias. Por otro lado, es posible que las demostraciones de distintos teoremas compartan ciertos patrones, como por ejemplo, inducción o reducción por el absurdo. Parte de nuestro trabajo es entender cuáles son los contextos de aplicación de estas formas particulares de razonamiento y cómo hacerlo. Sin embargo, con el objetivo de comunicar demostraciones (es decir, presentar demostraciones a otras personas y que ellas las comprendan) los matemáticos usualmente utilizan lenguaje natural con algunos símbolos especiales. Con el objeto de describir de manera precisa las demostraciones, es necesario contar con un lenguaje puramente matemático. De esta manera nace una disciplina dedicada a estudiar las demostraciones como un objeto formal: la \textit{teoría de prueba} (en inglés \textit{proof theory}). Frege lideró esta disciplina sugiriendo que las pruebas deben ser consideradas como objetos de estudio matemático en 1879 en su libro \textit{Begriffschrift} \cite{frege1879}. Luego, Hilbert siguió las ideas de Frege proponiendo una definición de un sistema deductivo para formalizar el razonamiento \cite{hilbert1967}.

\textit{La Teoría de Prueba} puede ser considerada como uno de los cuatro pilares de la lógica matemática junto con la teoría de modelos, la teoría de conjuntos y la teoría de la recursión. Al diseñar diversos formalismos para ver las pruebas como objetos matemáticos, debemos entender sus propiedades a través de métodos matemáticos formales. Desde el punto de vista de las ciencias de la computación, una aplicación directa podría ser el desarrollo de algoritmos para demostrar teoremas automáticamente (demostradores automáticos), o verificar pruebas matemáticas (verificación/comprobación automática de teoremas). Otra aplicación podría ser extraer de una prueba un algoritmo; por ejemplo, si el teorema establece la existencia de un objeto, este objeto también podría construirse efectivamente; otro ejemplo podría ser el uso de las demostraciones fallidas para la construcción de contraejemplos. Por otro lado, desde un punto de vista más abstracto, podríamos tratar de entender qué axiomas se requieren para demostrar ciertos teoremas (matemática inversa), como así también comparar diferentes métodos de prueba y, en particular, los tamaños de las pruebas que producen (complejidad de la prueba).

Así, como mencionamos al comienzo, podríamos decir que las matemáticas están hechas de muchos lemas, algunos teoremas y de sus pruebas. Se podría decir que los matemáticos no demuestran un teorema desde cero, si no que construyen la prueba a partir de demostrar otras afirmaciones intermedias que son llamadas \emph{lemas}.
En un sistema deductivo \emph{a la Hilbert y Frege}, para probar un teorema T, es posible utilizar un lema dado L si, por un lado, podemos probar L y si, por otra parte, podemos inferir T de L. Este paso de razonamiento es llamado \emph{Modus Ponens}. El desafío radica en encontrar el lema apropiado.

Sin embargo, para las aplicaciones que mencionamos, cambiar a una teoría diferente del teorema que queremos demostrar puede no resultar tan sencillo, por lo que muchas veces preferimos una demostración sin lemas. Es importante aclarar que no todas las pruebas matemáticas pueden realizarse libres de lemas.

Fue así que Gentzen en su \emph{Untersuchungen {\"u}ber das logische Schlie{\ss}en. I} en 1934 \cite{gentzen1934} introdujo métodos teóricos de prueba para demostrar resultados en la lógica matemática. En particular, Gentzen fue quién desarrolló el \emph{cálculo de secuentes}, una representación alternativa de las pruebas que promueven las reglas de inferencia sobre los axiomas. El teorema de \emph{cut-elimination} o también conocido como \emph{Hauptsatz} declara que cualquier prueba en el cálculo de secuentes puramente lógica puede transformarse en una forma analítica normal. Esto quiere decir que en cálculo de secuentes, cualquier prueba puede ser realizada sin lemas. Para poder probar el \emph{Hauptsatz}, uno necesita mostrar que una regla llamada \emph{cut}, la cual reformula Modus Ponens en el cálculo de secuentes, es redundante en el sistema. Es decir, establece que cualquier prueba que tenga una demostración en el cálculo de secuentes utilizando \emph{cut}, también tiene una demostración sin esta regla.

Otra de las grandes contribuciones de Gentzen fue el estudio paralelo de las lógicas clásicas e intuicionistas. Las lógicas intuicionisticas surgen con Brouwer \cite{brouwer1920} como una formalización del razonamiento constructivista (la existencia de un objeto es equivalente a la posibilidad de su construcción), rechazando el \emph{Principio del Tercero Excluído} el cual establece que una proposición tiene que ser verdadera o falsa. Mientras que en la lógica intuicionista puede haber incertidumbre sobre si una proposición se mantiene o no, en la lógica clásica, el principio es aceptado.

En este trabajo, vale la pena destacar que por \emph{lógica intuicionista} nos referimos a la lógica intuicionista proposicional básica. A la hora de definir cálculos de prueba para esta lógica, una caracterísitica importante es que es posible obtener tales cálculos, simplemente restringiendo sintácticamente el cálculo de prueba para la lógica clásica correspondiente \cite{vandalen2004} (en nuestro caso, lógica proposicional).

El enfoque intuicionista fue utilizado sobre diferentes lógicas. En este trabajo, nos centraremos en el desarrollo de un cálculo de secuentes para una lógica modal intuicionista. Como se discutirá en las siguientes secciones, el enfoque modal se acopla adecuadamente, ya que una de las características principales es la definición y combinación de nuevos operadores, dando origen a nuevas familias de lógicas modales. Desde esta perspectiva, la componente intuicionista es simplemente una modalidad en el lenguaje.

\section{Lógicas modales y su teoría de prueba}

En sus comienzos, las lógicas modales surgen del deseo de analizar ciertos conceptos filosóficos como \emph{necesidad, creencia, conocimiento, obligación}, entre otros. Lo que llamamos \emph{lógicas modales} se obtienen como extensiones de lógicas clásicas (por ejemplo: lógica proposicional o lógica de predicados) describiendo el comportamiento de modalidades como $\square$ y $\Diamond$ que representan los conceptos a investigar. Más precisamente estos operadores permiten describir propiedades de los estados accesibles desde el punto de evaluación. Las lógicas modales más estudiadas son aquellas basadas en el razonamiento clásico. El interés en las versiones intuicionistas de las lógicas modales se produjo mucho más tarde y de dos fuentes diferentes: por un lado, los lógicos se interesaron por obtener versiones intuicionistas (es decir, utilizando razonamiento constructivista), y por otra parte, aplicaciones de las mismas.

Desde Aristóteles y con un gran desarrollo en la Edad Media se fundan las bases de la lógica modal. Su consolidación se produjo a fines de la década de 1950 y principios de la década de 1960 con el desarrollo de una semántica basada en los \emph{``mundos posibles"} introducida por Kripke \cite{kripke1959} (de allí el nombre de la semántica). Nos permite ver a la lógica modal como un lenguaje para grafos o bien como un lenguaje para describir procesos, es decir, ver a los elementos del grafo como un conjunto de estados computacionales y ver a las relaciones como acciones que transforman un estado a otro.

Como consecuencia de lo propuesto por Kripke, en términos de \emph{teoría de prueba}, algunas extensiones para secuentes fueron incorporadas beneficiando el manejo de las modalidades. Dos enfoques se destacaron dentro de estas extensiones: por un lado, sistemas que incorporan semántica relacional explícita en su formalismo, llamados \emph{sistemas etiquetados deductivos} como los \emph{cálculos etiquetados} \cite{negri2005} y el \emph{método de tablas semánticas} (mejor conocido en inglés como \emph{semantic tableaux} \cite{fitting1983}), y por otra parte, sistemas que utilizan dispositivos sintácticos para recuperar el lenguaje modal, llamados \emph{sistemas deductivos sin etiquetas} (por ejemplo: \emph{hypersequents} \cite{avron1996}, \emph{nested sequents} \cite{brunnler2009}). Así, los teóricos de prueba interesados en la lógica modal tienen a su disposición una amplia gama de diferentes formalismos de prueba para elegir, que nos permiten tener herramientas complementarias para poder explorar la teoría de prueba de la lógica modal. El trabajo de esta tesis nos muestra uno de estos formalismos nombrados, el de \emph{sistemas de pruebas etiquetados}, para analizar pruebas modales.

\section{Motivación}

%Como se nombró anteriormente, los teoremas de una lógica pueden caracterizarse a través de dos formatos: por un lado, \emph{axiomatización a la Hilbert} y por otro lado, a través de reglas de secuentes conocido como \emph{estilo Gentzen}. 
Nuestro trabajo se centra en sistemas de prueba etiquetados para lógicas modales intuicionistas usando dos tipos de relaciones de accesibilidad. Esto significa que hay un símbolo relacional para la relación de accesibilidad modal y una para la relación futura (o conocida como relación de pre-orden). Esta es una novedad ya que nos permite poner el sistema de prueba en estrecha relación con la semántica birelacional de Kripke.

Extendemos el sistema etiquetado propuesto por Negri para la lógica modal básica \cite{negri2005} con la relación de pre-orden que se nombró anteriormente (la relación de accesibilidad ya esta presente en el cálculo para la lógica clásica) para capturar lógicas modales intuicionistas. Para nuestro nuevo sistema, probamos tanto correctitud como completitud, así como también utilizamos el sistema etiquetado propuesto por Simpson \cite{simpson1994} para demostrar que nuestro sistema es un sistema libre de $\mathsf{cut}$. Por último y como trabajo a futuro, extendemos nuestro sistema agregando el axioma de Scott-Lemmon volviendo a demostrar correctitud y completitud para nuestro nuevo sistema (con el axioma agregado).

\section{Organización del trabajo}

Esta tesis se estructura de la siguiente manera:

En el \textbf{Capítulo \ref{cap:logclasica}} presentamos a la lógica modal básica con su sintaxis, semántica y sus distintos formatos de caracterización: presentamos una axiomatización a la Hilbert y una axiomatización a la Gentzen, en donde vemos en detalle el cálculo de secuentes etiquetado propuesto por Negri \cite{negri2005}.

En el \textbf{Capítulo \ref{cap:logintuicionista}} se presentan los conceptos de sintaxis y semántica para la lógica modal intuicionista como así también una axiomatización a la Hilbert.

En el \textbf{Capítulo \ref{cap:labIKh}} se plantea en detalle el problema principal que abordamos y se presenta en detalle el sistema de secuentes etiquetado propuesto para la lógica modal intuicionista (llamado $\labIKh$). Se ven en detalle cada una de las reglas de secuentes que conforman al sistema. En este capítulo también se desarrolla la demostración de que nuestro sistema es correcto.

En el \textbf{Capítulo \ref{cap:completeness}} se desarrolla una prueba de completitud sintáctica por medio del sistema a la Hilbert para el sistema $\labIKh$. Se realiza una demostración en la que se demuestran todos los axiomas de la lógica modal proposicional, se simula modus ponens y necesitación, y se prueban las variantes $\kaxiom_{1}$, ... $\kaxiom_{5}$ del axioma de distributividad $\kaxiom$ (presentados en detalle en el Capítulo 3). De esta prueba se obtiene un sistema completo con la regla de $\mathsf{cut}$ (utilizada para simular modus ponens).

En el \textbf{Capítulo \ref{cap:future}} se presentan algunas líneas de trabajo futuro. Entre ellas, se continuará trabajando en una prueba de completitud utilizando el sistema de secuentes propuesto por Simpson \cite{simpson1994}. Y por otra parte, se presentan algunas extensiones del sistema $\labIKh$ para generar lógicas más fuertes. En particular, en el Capítulo 6 extendemos nuestro sistema con el axioma de Scott-Lemmon o también conocido como $\agklmn$.

Por último, en el \textbf{Capítulo \ref{cap:conclusion}} presenta un breve resumen de lo realizado a lo largo de este trabajo final de Licenciatura como así también se incluye una pequeña sección de la experiencia que tuve a lo largo de este trabajo.

### 2019-05-27 thesis-Marianela/thesis/chapters/logintuic.tex
thesis

\chapter{Lógica modal intuicionista}
\label{cap:logintuicionista}

El intuicionismo surgió como una escuela de matemáticas fundada por el matemático holandés Brouwer \cite{brouwer1920}. Él rechazaba los métodos matemáticos cuya justificación requería apelar a un concepto abstracto de ``verdad". Más precisamente, Brouwer creía que el significado matemático se originaba en el acto humano de ``hacer" \vspace{0.02mm} las matemáticas. Por lo tanto, para Brouwer, un objeto matemático debía ser dado por una construcción, y no hay un sentido abstracto en el que una declaración pueda ser verdadera a menos que tengamos una prueba de ella (o los medios para encontrar una). Además, los pasos dados en cualquier prueba deben ser legítimos de acuerdo con esta rígida interpretación de las matemáticas. Como se ha mencionado anteriormente, tales consideraciones llevaron a Brouwer a rechazar varios principios clásicos como, por ejemplo, el conocido \emph{Tercero excluído}: $\vls[A.\neg A]$ es válida para cualquier proposición $A$.

En la década de 1930, Heyting desarrolló la lógica intuicionista, una lógica que incorpora los principios subyacentes del razonamiento intuicionista. La lógica intuicionista ha sido enormemente exitosa. En primer lugar, se acepta ampliamente que ha logrado su objetivo original de aislar los métodos de prueba intuicionistas aceptables. En segundo lugar, ha logrado proporcionar una base para la investigación meta-matemática de las matemáticas revelando que las matemáticas intuicionistas son un campo de notable coherencia y de belleza matemática, ya sea que uno acepte o no sus principios filosóficos subyacentes. En tercer lugar, hay conexiones profundas con algunos conceptos de reciente crecimiento dentro de las ciencias de la computación (como ejemplo de dos aplicaciones diferentes ver Martin-L\"of \cite{martin1982} y Scott \cite{scott1980}).  La teoría de prueba de la lógica intuicionista también ha encontrado aplicación filosófica reciente. Dummett ha argumentado que la teoría de prueba justifica la lógica intuicionista como la lógica subyacente de una filosofía anti-realista \cite{dummett1991}. Su argumento da lugar a un intuicionismo que es sustancialmente diferente al de Brouwer y que se aplica tanto al razonamiento no matemático como al razonamiento matemático. Para una introducción general a la filosofía y las matemáticas del intuicionismo y la lógica intuicionista, ver Dummett \cite{dummett1977}.

Dada esta breve introducción a la lógica intuicionista, en este trabajo final, como se dijo en la intruducción, nos centraremos en las lógicas modales intuicionistas. Es decir, nos aprovecharemos de la semántica de Kripke subyacente, para combinar operadores modales con el razonamiento intuicionista. Como veremos más adelante, esta combinación resultará natural a la hora de estudiar su teoría de prueba. En esta sección presentaremos los conceptos y las notaciones de la lógica modal intuicionista que serán necesarios para el desarrollo de nuestro trabajo (para mayor detalle, ver \cite{simpson1994}).

\section{Sintaxis y semántica}

En el caso intuicionista, trabajamos con un conjunto  diferente de conectivos. Empezando con un conjunto de proposiciones atómicas que seguimos denotando con $a$, las fórmulas se construyen a partir de la siguiente gramática:

\begin{center}
	$A ::=  a$ $| $$\top$ $|$ $\bot $ $|$ $\vls(A.A)$ $|$ $\vls[A.A]$ $|$ $A \vljm A$ $|$ $\square A$ $|$ $\Diamond A$ 
\end{center}

Cuando escribimos $\neg A$, queremos representar $A \vljm \bot$.

La semántica de Kripke para la lógica modal intuicionista combina la semántica de Kripke para la lógica proposicional intuicionista con la de la lógica modal clásica, utilizando dos relaciones distintas en el conjunto de mundos. Para introducir la semántica que es de nuestro interés introducimos las siguientes definiciones:

\dfn(Frame bi-relacional) Un \emph{frame bi-relacional} $\F$ es una tupla $\langle W, R, \le \rangle$ donde $W$ es un conjunto no vacío y $R$, $\le$ son dos relaciones binarias $R$ $\subseteq$ $W \times W$ y $\le$ $\subseteq$ $W \times W$. Insistimos además que $\le$ sea un pre-orden (es decir, reflexividad y transitividad) que satisface las siguientes condiciones:\\

(F1) Para todo $u, v, v'$ $\in W$, si $uRv$ y $v \le v'$ entonces existe $u'$ tal que $u \le u'$ y $u'Rv'$.\\

\begin{figure}[h]
	\begin{center}
		\begin{tikzpicture}[>=latex]
		\node (a0) at (-1,0)   [shape=circle,draw,fill, inner sep=1pt,label=left:$u$] {} ;
		\node (a1) at (-1,2)  [shape=circle,draw,fill, inner sep=1pt, label=left:$u'$] {} ;
		\node (a2) at (1,0)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v$] {} ;
		\node (a3) at (1,2)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v'$] {} ;
		\draw [dotted,->] node[left] at (-1,1){$\le$}(a0) edge [ left] (a1);
		\draw [ar,->] node[above] at (0,2){$R$}(a0) edge [ right] (a2);
		\draw [dotted, ->] node[right] at (1,1){$\le$}(a1) edge [ left] (a3);
		\draw [ar,->] node[above] {$R$} (a2) edge [ left] (a3);
 ;
		\end{tikzpicture}
	\end{center}
\end{figure}

(F2) Para todo $u', u, v$ $\in W$, si $u \le u'$ y $u R v$ entonces existe $v'$ tal que $u'Rv'$ y $v\le v'$.\\

\begin{figure}[h]
	\begin{center}
		\begin{tikzpicture}[>=latex]
		\node (a0) at (-1,0)   [shape=circle,draw,fill, inner sep=1pt,label=left:$u$] {} ;
		\node (a1) at (-1,2)  [shape=circle,draw,fill, inner sep=1pt, label=left:$u'$] {} ;
		\node (a2) at (1,0)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v$] {} ;
		\node (a3) at (1,2)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v'$] {} ;
		\draw [ar,->] node[left] at (-1,1){$\le$}(a0) edge [ left] (a1);
		\draw [ar,->] node[above] at (0,2){$R$}(a0) edge [ right] (a2);
		\draw [dotted, ->] node[right] at (1,1){$\le$}(a1) edge [ left] (a3);
		\draw [dotted,->] node[above] {$R$} (a2) edge [ left] (a3);
		;
		\end{tikzpicture}
	\end{center}
\end{figure}

De acuerdo al paradigma de Kripke para la lógica intuicionista, los hechos atómicos se acumulan a medida que ascendemos el orden parcial. Es decir, podría razonablemente sostenerse que el hecho de que un mundo $w$ accedía a otro mundo $v$, es un tipo razonable de hecho atómico que debería persistir. Así, cualquier mundo $ w \le w'$ debería también, en efecto, ver $v$; pero es razonable esperar que también hayamos acumulado más datos sobre $v$ que, por lo tanto, pueden haber 'evolucionado' en algún mundo $v \le v'$. Formalizando estas consideraciones, llegamos a obtener la condición (F1). Un argumento dual partiendo de que el mundo $v$ está viendo al mundo $w$ justifica la condición (F2).

\dfn(Modelo bi-relacional) Un \emph{modelo bi-relacional} $\M$ es una cuatro-upla $\langle W, R, \break\le, V \rangle$ donde $\langle W, R, \le \rangle$ es un frame bi-relacional y $V$ una función de valuación monótona $V: W$$\rightarrow$ $2^{\mathsf{PROP}}$ tal que es una función que asigna a cada mundo $w$ el subconjunto de átomos proposicionales que son verdaderos en $w$, sujeto a:

\begin{center}
	$w \le w'$ $\Rightarrow$ $V(w)$ $\subseteq$ $V(w')$
\end{center}

De esta manera, obtenemos el \emph{lema de monotonía}:

\begin{lemma} (Lema de monotonía) 
	Si $w \le w'$ y $\M, w \Vdash A$ entonces $\M, w' \Vdash A$.
\end{lemma}

Como vimos en el caso de la lógica clásica, escribimos $\M, w \Vdash a$ si y sólo si $a \in V(w)$ y lo extendemos con inducción a todas las fórmulas siguiendo las reglas para los modelos de Kripke tanto intuicionistas como clásicos:

\dfn Sea $\M = \langle W, R, \le, V \rangle $ un modelo bi-relacional, $w \in W$ y $A$ una fórmula, decimos que $\M,w $ satisface $A$ (denotado $\M, w \Vdash A$) si:$$
\begin{array}{rcl}

%\M, w \Vdash a & \mbox{si y sólo si} & a \in V(w)\\

%\M, w \Vdash \vls-a& \mbox{si y sólo si} & a \not \in V(w)\\

\M, w \Vdash A \vlan B & \mbox{sii} & \M, w \Vdash A\mbox{ y }\M, w \Vdash B \\

\M, w \Vdash A \vlor B & \mbox{sii} & \M, w \Vdash A\mbox{ o }\M, w \Vdash B \\

\M, w \Vdash A \vljm B & \mbox{sii} & \mbox{para todo } w' \mbox{ con } w \le w', \mbox{ si } \M, w' \Vdash A \mbox{ entonces } \M, w' \Vdash B \\

\M, w \Vdash \square A & \mbox{sii} & \mbox{para todo } w' \mbox{ y } u \mbox{ con } w \le w' \mbox{ y } w'Ru \mbox{ entonces } \M, u \Vdash A \\

\M, w \Vdash \Diamond A & \mbox{sii} & \mbox{existe } u \in W \mbox{ tal que } wRu \mbox{ y } \M, u \Vdash A \\

\end{array}$$

 %\male{de nuevo, queda feo, no te parece?}
 %\hspace{9mm} $\M, w \Vdash \vls(A.B)$ si y sólo si $\M, w \Vdash A$ y $\M, w \Vdash B$

%\hspace{9mm} $\M, w \Vdash \vls[A.B]$ si y sólo si $\M, w \Vdash A$ o $\M, w \Vdash B$

%\hspace{9mm} $\M, w \Vdash A \vljm B$  si y sólo si para todo $w'$ con $w \le w'$, si $\M, w' \Vdash A$ entonces $\M, w' \Vdash B$.

%\hspace{9mm} $\M, w \Vdash \square A$ si y sólo si para todo $w'$ y $u$ con $w \le w'$ y $w'Ru$ entonces 
%se tiene que $\M, u \Vdash A$

%\hspace{9mm} $\M, w \Vdash \Diamond A$ si y sólo si existe un mundo $u \in W$ tal que $wRu$ y $\M, u \Vdash A$.

Escribimos $\M, w \not \Vdash A$ si no se da el caso de $\M, w\Vdash A$, en particular $\M, w ,\not \Vdash \bot $.\\

\dfn (Satisfabilidad y Validez de una fórmula) Una fórmula $A$ es \textit{satisfacible} en un modelo $\M = \langle W, R, \le, V \rangle$, si existe $w \in W$ tal que $\M, w \Vdash A$. Diremos que una fórmula $A$ es \emph{válida} en un modelo $\M$ si para todo $w \in W$, $\M, w \Vdash A$. Lo denotamos con $\M \vDash A$.

%%%%%%%

\section{Axiomatizaciones para la lógica modal intuicionista}
La lógica modal intuicionista $\IK$ (una variante intuicionista de la lógica modal $\K$) es una extensión de la lógica proposicional intuicionista \textbf{IPL} \cite{vandalen2004} compuesta por los siguientes axiomas:

\begin{itemize}

	\item{THEN-1}: $A  \vljm (B \vljm A)$

	\item{THEN-2}: $(A \vljm (B \vljm C)) \vljm ((A \vljm B) \vljm (A \vljm C))$

	\item{AND-1}: $\vls(A.B)\vljm A$

	\item{AND-2}: $\vls(A.B) \vljm B$

	\item{AND-3}: $A \vljm (B \vljm (\vls(A.B)))$

	\item{OR-1}: $A \vljm \vls[A.B]$

	\item{OR-2}: $B \vljm \vls[A.B]$

	\item{OR-3}: $(A \vljm C) \vljm ((B \vljm C) \vljm (\vls[A.B] \vljm C))$

	\item{FALSE}: $\bot \vljm A$

\end{itemize}

Una vez introducida la lógica \textbf{IPL}, obtenemos $\IK$ añadiendo los siguientes axiomas y reglas:

\begin{itemize}
	\item{la \emph{regla de necesitación} ($\mathsf{nec}$)}: si $A$ es un teorema, entonces también $\square A$ es un teorema.
	\item{las siguientes \emph{cinco variantes del axioma de distributividad $\kaxiom$}}:

	$\kaxiom_{1}$: $\square(A \vljm B) \vljm (\square A \vljm \square B)$

	$\kaxiom_{2}$: $\square (A \vljm B) \vljm (\Diamond A \vljm \Diamond B)$

	$\kaxiom_{3}$: $\Diamond (\vls[A.B]) \vljm (( \vls [\Diamond A. \Diamond B]))$

	$\kaxiom_{4}$: $(\Diamond A \vljm \square B) \vljm \square(A \vljm B)$

	$\kaxiom_{5}$: $\Diamond \bot \vljm \bot$

\end{itemize}

%El sistema modal intuicionista más básico que uno puede pensar sería considerar únicamente la modalidad $\square$ según lo establecido por el axioma $k$, mejor conocido en esta sección como $k_{1}$, obteniendo así el sistema \textbf{IPL+nec+$k_{1}$}. Aunque de aquí no podríamos tener ningún tipo de información acerca de la modalidad $\Diamond$.
 El sistema modal intuicionista más básico que podría ser considerado, consiste únicamente de la modalidad $\square$, axiomatizada por el axioma $\kaxiom_{1}$. Sin embargo, dicho sistema no contempla la modalidad $\Diamond$.
Fitch \cite{fitch1948} fue el primero en proponer un sistema intuicionista para trabajar con $\Diamond$ obteniéndolo a partir de \textbf{IPL+nec+$\kaxiom_{1}$+$\kaxiom_{2}$}, el cual muchas veces es conocido como \textbf{CK} por \emph{lógicas modales constructivas} (en inglés \emph{constructive modal logics}). En \cite{wijesekera1990} se introdujo un sistema intuicionista que no contempla la distribuividad de $\Diamond$ sobre $\vlor$; el mismo está compuesto por \textbf{IPL+nec+$\kaxiom_{1}$+$\kaxiom_{2}$+$\kaxiom_{5}$}.
%: luego obtenemos \textbf{CK} de constructive y de la anteriormente mencioada lógica modal K). Wijekesera \cite{wijesekera1990} propuso un sistema intuicionista que agregaba al sistema de Fitch el axioma $k_{5}$, que establece que $\Diamond$ distribuye sobre disyunciones 0-aria, pero no asumió que siempre distribuiría sobre disyunciones binarias; el sistema que él propuso entonces fue \textbf{IPL+nec+$k_{1}$+$k_{2}$+$k_{5}$}. 
Estos sistemas fueron diseñados para algunas aplicaciones concretas, tal como analizar algunos sistemas de tipos \cite{benton1998} o para razonar sobre los estados de una máquina bajo información parcial  \cite{wijesekera2005}. Sin embargo, desde un punto de vista estrictamente lógico, no resulta satisfactorio, ya que la adición del principio del Tercero Excluído al sistema no produce la lógica modal clásica $\K$, es decir, en este caso no es posible recuperar la dualidad de De Morgan entre $\square$ y $\Diamond$.

La axiomatización que es ahora generalmente aceptada como \emph{lógica modal intuicionista} denotada como $\IK$ fue introducida por Plotkin y Stirling \cite{plotkin1986} y es equivalente a la propuesta por Fischer-Servi \cite{servi1984} y por Ewald \cite{ewald1986}. Como se mencionó anteriormente, consiste de \textbf{IPL}, la regla de necesitación, y los axiomas $\kaxiom_{1}$, $\kaxiom_{2}$, $\kaxiom_{3}$, $\kaxiom_{4}$, $\kaxiom_{5}$.

Es posible demostrar que el sistema $\IK$ es correcto y completo con respecto a la clase de modelos indicada.

%\dfn (Validez de una fórmula) Una fórmula $A$ es \textit{válida} en un frame $\F = \langle W, R, \le \rangle$, si para toda valuación $V$ se tiene que $A$ es satisfacible en $\langle W, R, \le, V \rangle$.

\begin{teo}
	 (\cite{servi1984,plotkin1986}) Una fórmula $A$ es un teorema de $\IK$ si y sólo si $A$ es válida en cada frame bi-relacional.
\end{teo}

Para culminar, notar el paralelismo establecido entre las diferentes axiomatizaciones para la lógica $\K$ (Capítulo 2). En este capítulo, presentamos un sistema \emph{á la Hilbert} para la lógica modal intuicionista. Nuestra contribución consiste en la definición de un sistema \emph{a la Gentzen} para lógica modal intuicionista, y al estudio de las relaciones con otros sistemas existentes. Los siguientes capítulos estarán dedicados a la presentación de dichas contribuciones.
%Siguiendo Getnzen, un primer intento de cálculo de secuentes para la lógica modal intuicionista \textbf{IK} sería considerar una versión bilateral del cálculo de secuentes clásico para la lógica modal \textbf{K} con la restricción de que sólo una fórmula puede aparecer en el lado derecho. Un cálculo de secuentes intuicionista es un conjunto múltiple de fórmulas

### 2019-05-27 thesis-Marianela/thesis/chapters/newsyst.tex
thesis

\section{El sistema $\labIKh$}
En esta sección buscamos resolver el problema recientemente propuesto a partir del sistema de prueba etiquetado que se observa en la Figura \ref{fig:labIKheart}. Como se dijo anteriormente, para obtener este nuevo sistema, se extendió el cálculo de secuentes etiquetado propuesto por Negri para la lógica modal básica agregando un símbolo de relación de pre-orden. En las siguientes secciones desarrollamos en detalle las reglas que forman parte de este sistema de secuentes etiquetado para la lógica modal intuicionista llamado $\labIKh$.

\subsection{Condiciones para frames}

Para poder capturar la lógica modal intuicionista, en primer lugar, buscamos responder a los requisitos de las definiciones presentadas en el Capítulo 3. La semántica de la lógica modal intuicionista habla de un modelo bi-relacional el cual esta compuesto por dos relaciones binarias $R$ y $\le$, donde exigimos que $\le$ sea una relación de pre-orden, es decir, que sea reflexiva y transitiva. Por lo tanto, el sistema $\labIKh$ debe tener reglas que caractericen tales condiciones (estas reglas se representan con \emph{refl} y \emph{trans}). También debe poseer reglas que caractericen las condiciones F1 y F2 (en el sistema $\labIKh$ estas reglas son $\fone$ y $\ftwo$). Por otra parte, recordemos que la definición de la función de valuación monótona $V$ nos introduce el \emph{lema de monotonía} que será capturado por la regla $\ids$ del sistema. Estas reglas son las siguientes:

\begin{center}
	$\vlinf{\refl}{}{\G, \Left \Rightarrow \Right}{\G, x\le x, \Left \Rightarrow \Right}$\hspace{8mm}
	$\vlinf{\trans}{}{\G, x \le y, y \le z, \Left \Rightarrow \Right}{\G, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$

	\vspace{6mm}

	$\vlinf{\ids}{}{\G, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$

	\vspace{6mm}

	$\vlinf{\fone}{$ $u$ fresh$}{\G, \Left, xRy, y \le z \Rightarrow \Right}{\G, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$\hspace{4mm}$\vlinf{\ftwo}{u$ fresh$}{\G, \Left, xRy,x \le z \Rightarrow \Right}{\G, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$

\end{center}

\bigskip

A modo de ejemplo, explicaremos en detalle las reglas $\fone$ y $\ftwo$:

\begin{itemize}
		\item Regla $\fone$.

		La regla presentada para el cumplimiento de una de las condiciones ($\fone$) de la relación de preorden $\le$ es la siguiente:

		\begin{center}
			$\vlinf{\fone}{$ $u$ fresh$}{\G, \Left, xRy, y \le z \Rightarrow \Right}{\G, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
		\end{center}

		Dado $\G$ un conjunto de átomos relacionales y de pre-orden, y dados $\Left$ y $\Right$ conjuntos de fórmulas etiquetadas, la regla en cuestión expresa la semántica de la condición $\fone$. Leyendo desde la conclusión hacia la premisa tenemos etiquetas $x, y$ tal que $xRy$ y $y \le z$, entonces existe un mundo $u$ tal que $x \le u$ y $uRz$.

		\item Regla $\ftwo$:

		Como vimos anteriormente, la regla para el cumplimiento de F2 se presenta de la siguiente manera en $\labIKh$:

		\begin{center}
			$\vlinf{\ftwo}{u$ fresh$}{\G, \Left, xRy,x \le z \Rightarrow \Right}{\G, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
		\end{center}

		Al igual que con F1, sea $\G$ un conjunto de átomos relacionales y de pre-orden, y dados $\Left$ y $\Right$ conjuntos de fórmulas etiquetadas, esta regla expresa semánticamente desde su conclusión hace su premisa, que dadas las etiquetas $x, y$ y $z$, si $xRy$ y $x \le z$, entonces hay una etiqueta (o mundo) $u$ (fresh) tal que $y \le u$ y $zRu$.

\end{itemize}

\subsection{Conectivos lógicos de la lógica proposicional intuicionista}

Para seguir construyendo un sistema completo y correcto etiquetado para la lógica modal intuicionista, en esta sección presentamos las reglas que expresan la semántica de los conectivos lógicos usuales. Es decir, presentamos reglas para la conjunción y la disjunción que forman parte del sistema $\labIKh$. Las mismas se presentan a continuación:

\begin{center}
		\hspace{4mm}$\vlinf{\svlef}{}{\G,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$\hspace{10mm}
		$\vliinf{\svrig}{}{\G,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$

		\vspace{5mm}

		$\vliinf{\solef}{}{\G, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\G, \Left, x   \colon   A \Rightarrow \Right}{\G, \Left, x   \colon   B \Rightarrow \Right}$\hspace{10mm}
		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
\end{center}

También el sistema $\labIKh$ debe capturar las constantes proposicionales $\top$ y $\bot$. Para ello, incorpora las siguientes dos reglas al sistema:

\begin{center}
	$\vlinf{\sbot}{}{\G,\Left, x \colon \bot \Rightarrow \Right}{}$\hspace{18mm}
	$\vlinf{\Stop}{}{\G, \Left \Rightarrow \Right, x \colon \top}{}$
\end{center}

A continuación explicaremos en detalle la regla de conjunción izquierda $\svlef$ y la regla de disjunción derecha $\sorig$:

\begin{itemize}
	\item Regla $\svlef$:

	El sistema $\labIKh$ presenta la siguiente regla para la conjunción en el lado izquierdo:

	\begin{center}
		$\vlinf{\svlef}{}{\G,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
	\end{center}

	Al igual que las reglas presentadas en la sección anterior $\G$ es un conjunto de átomos relacionales y de pre-orden, y $\Left$ y $\Right$ son conjuntos de fórmulas etiquetadas. Desde la conclusión hacia la premisa de esta regla, semánticamente nos dice que si en $x$ se satisface la fórmula $A \vlan B$, entonces en $x$ se satisface la fórmula $A$ y también se satisface la fórmula $B$.

	\item Regla $\sorig$:

	Sea la regla presentada en $\labIKh$ para la disjunción en el lado derecho:

	\begin{center}
		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
	\end{center}

	Tenemos que, leyendo desde la conclusión hacia la premisa, si en $x$ se satisface $A \vlor B$ (del lado derecho), entonces en $x$ es verdadera la fórmula $A$ y también la fórmula $B$.

\end{itemize}

\subsection{Capturando los operadores modales}

En esta sección, introduciremos las reglas que expresan la semántica de los operadores modales $\square$ y $\Diamond$. El sistema $\labIKh$ presenta las siguientes cuatro reglas (dos para el $\square$ y dos para el $\Diamond$):

\begin{center}
	\hspace{5mm}$\vlinf{\sbl}{}{\G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\G,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$\hspace{10mm}$\vlinf{\sbr}{$ $y, z$ fresh$}{\G, \Left \Rightarrow \Right, x \colon \square A}{\G, \Left, x \le y, yRz \Rightarrow \Right, z \colon A}$

	\vspace{5mm}

	$\vlinf{\sdl}{$ $y$ fresh $}{\G, \Left, x \colon \Diamond A \Rightarrow \Right}{\G, \Left, xRy, y \colon A \Rightarrow \Right}$\hspace{10mm}
	$\vlinf{\sdr}{}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$

\end{center}

Expliquemos más en detalle algunas de ellas:

\begin{itemize}
	\item Regla $\sbl$.

	Para capturar el $\square$ del lado izquierdo, en nuestro sistema introducimos la siguiente regla:
	\begin{center}
		$\vlinf{\sbl}{}{\G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\G,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
	\end{center}
	Nuevamente dado $\G$ un conjunto de átomos relacionales y de pre-orden, y sean $\Left$ y $\Right$ conjuntos de fórmulas etiquetadas. Esta regla semánticamente expresa, desde su conclusión hacia su premisa, que dado $x, y$ y $z$ tal que $x \le y$ y $yRz$ donde en $x$ se hace verdadera la fórmula $\square A$, entonces en $z$ se hace válida la fórmula $A$.

	\item Regla $\sdr$.

	Sea la regla presentada en $\labIKh$ para $\Diamond$ en el lado derecho:	
	\begin{center}
		$\vlinf{\sdr}{}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
	\end{center}

	Semánticamente, el diamante establece que en un modelo $\M$ y en un mundo $v$ vale $\Diamond A$ si y sólo si existe un mundo $u$ tal que $vRu$ y en $u$ la fórmula $A$ se satisface. Para capturar esta definición semántica, la regla introducida (leyendo desde la conclusión hacia la premisa) nos dice que, si $xRy$ y en $x$ se satisface $\Diamond A$, luego en $y$ la fórmula $A$ tiene que ser verdadera.

\end{itemize}

\subsection{Implicación intuicionista}

Por último, nos resta ver que el sistema $\labIKh$ captura la semántica del operador de implicación. Es por ello que este sistema de secuentes etiquetado para que sea completo necesita de las siguientes dos reglas:

\begin{center}
		$\vlinf{\sir}{$ $y$ fresh$}{\G, \Left \Rightarrow \Right, x \colon A \vljm B}{\G, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$

		\vspace{5mm}

		$\vliinf{\sil}{}{\G, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right}{\G, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right, y \colon A}{\G, \Left, x \le y, x \colon A \vljm B, y \colon B \Rightarrow \Right}$
\end{center}

Veamos en detalle el significado de la regla de implicación del lado derecho:

\begin{itemize}
	\item Regla $\sir$.

	El sistema $\labIKh$ presenta la siguiente regla para la implicación en el lado derecho:

	\begin{center}
		$\vlinf{\sir}{$ $y$ fresh$}{\G, \Left \Rightarrow \Right, x \colon A \vljm B}{\G, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
	\end{center}

	Dado $\G$ un conjunto de átomos relacionales y de preorden, y dados $\Left$ y $\Right$ conjuntos de fórmulas etiquetadas, esta regla (leyendo desde la conclusión hacia la premisa) semánticamente nos dice que si $A \vljm B$ se satisface en $x$, entonces existe un nuevo (mundo) $y$ tal que $x \le y$ y en $y$ vale $A$, luego en $y$ también $B$ es válida.

\end{itemize}

%\subsection{\textbf{¿Por qué necesitamos dos reglas para cada operador?}}

\subsection{Uniendo todas las reglas: sistema $\labIKh$}
Como pudimos ver a lo largo de las subsecciones anteriores, el sistema $\labIKh$ tiene dos reglas para cada operador. Esto se debe a que la sintaxis para la lógica modal intuicionista no presenta la negación $\neg$, por lo que los operadores $\Diamond$ y $\square$ dejan de ser operadores duales como lo eran en el caso clásico.

En la Figura \ref{fig:labIKheart} se puede ver el sistema de secuentes etiquetado $\labIKh$ completo con cada una de las reglas mencionadas anteriormente.

\begin{figure}[!h]
	\small
	\begin{center}

			$\vlinf{\sbot}{}{\G,\Left, x \colon \bot \Rightarrow \Right}{}$\hspace{6mm}
			$\vlinf{\ids}{}{\G, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$\hspace{6mm}
			$\vlinf{\Stop}{}{\G, \Left \Rightarrow \Right, x \colon \top}{}$

		\vspace{5mm}

			$\vlinf{\svlef}{}{\G,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$\hspace{10mm}
			$\vliinf{\svrig}{}{\G,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$

		\vspace{5mm}

			$\vliinf{\solef}{}{\G, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\G, \Left, x   \colon   A \Rightarrow \Right}{\G, \Left, x   \colon   B \Rightarrow \Right}$\hspace{10mm}
			$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$

		\vspace{5mm}

			$\vlinf{\sir}{$ $y$ fresh$}{\G, \Left \Rightarrow \Right, x \colon A \vljm B}{\G, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$

		\vspace{5mm}

		$\vliinf{\sil}{}{\G, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right}{\G, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right, y \colon A}{\G, \Left, x \le y, x \colon A \vljm B, y \colon B \Rightarrow \Right}$

		\vspace{5mm}

			$\vlinf{\sbl}{}{\G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\G,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$\hspace{10mm}$\vlinf{\sbr}{$ $y, z$ fresh$}{\G, \Left \Rightarrow \Right, x \colon \square A}{\G, \Left, x \le y, yRz \Rightarrow \Right, z \colon A}$

		\vspace{5mm}

			$\vlinf{\sdl}{$ $y$ fresh $}{\G, \Left, x \colon \Diamond A \Rightarrow \Right}{\G, \Left, xRy, y \colon A \Rightarrow \Right}$\hspace{10mm}
			$\vlinf{\sdr}{}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$

		\vspace{5mm}

		\vspace{2mm}
			$\vlinf{\refl}{}{\G, \Left \Rightarrow \Right}{\G, x\le x, \Left \Rightarrow \Right}$\hspace{10mm}
			$\vlinf{\trans}{}{\G, x \le y, y \le z, \Left \Rightarrow \Right}{\G, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$

		\vspace{5mm}

			$\vlinf{\fone}{$ $u$ fresh$}{\G, \Left, xRy, y \le z \Rightarrow \Right}{\G, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$\hspace{4mm}
			$\vlinf{\ftwo}{u$ fresh$}{\G, \Left, xRy,x \le z \Rightarrow \Right}{\G, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$

	\end{center}
	\caption{Sistema $\labIKh$}
	\label{fig:labIKheart}
\end{figure}

%Veamos un ejemplo en el cual la ausencia de una regla no nos permitiría

%\raul{Completar esta idea, o sacar la subseccion y dejar solo el comentario sin ejemplo.}

### 2019-05-27 thesis-Marianela/thesis/chapters/simpson.tex
thesis

%\chapter{Completitud utilizando el sistema de Simpson}
\section{Completitud utilizando el sistema de Simpson}
El objetivo de esta sección, es discutir una demostración alternativa del resultado de completitud. Para ello utilizaremos el sistema de Simpson \cite{simpson1994} que se puede observar en la Figura \ref{fig:simpson}. En la sección anterior se realizó una prueba de completitud sintáctica para el nuevo sistema utilizando la regla de $\mathsf{cut}$ para simular modus ponens. Esto quiere decir que pudimos demostrar \emph{completitud con $\mathsf{cut}$} para nuestro sistema. Lo que deseamos lograr ahora, es tener un sistema completo sin $\mathsf{cut}$. Si bien se puede realizar una prueba conocida como \emph{cut elimination}, decidimos resolver este problema a partir de saber que el sistema propuesto por Simpson ya es un sistema libre de $\mathsf{cut}$. Como podemos observar en la Figura \ref{fig:simpson}, la mayoría de las reglas de secuentes que se encuentran en el sistema de Simpson (lo llamamos $\labIKs$) también están presentes en el sistema $\labIKh$, por lo que nos resta ver que las reglas que son distintas o bien no se encuentran en nuestro sistema, pueden ser deducidas a partir de la aplicación de reglas de secuentes del sistema $\labIKh$. Realizando este análisis a cada una de las reglas con éxito, podemos concluir que nuestro sistema $\labIKh$ es completo sin $\mathsf{cut}$.

\begin{teo}
	El sistema $\labIKs$ es completo sin la regla de $\mathsf{cut}$.
\end{teo}

\begin{figure}[h]
	\begin{center}
		$\vlderivation { \vlin {\idsim}{}{\G, \Left, x \colon a \Rightarrow x\colon a}{\vlhy {}}}$ \hspace{9mm} $\vlderivation { \vlin {\sbot}{}{\G, \Left, x \colon \bot \Rightarrow z\colon A}{\vlhy {}}}$

		\vspace{4mm}
		$\vlderivation {\vlin {\svlefs}{}{\G, \Left, x \colon \vls(A.B) \Rightarrow z \colon C}{\vlhy {\G, \Left, x \colon A, x \colon B \Rightarrow z \colon C}}}$
		\hspace{9mm}$\vlderivation { \vliin {\svrigs}{}{\G, \Left, \Rightarrow x \colon \vls(A.B)}{\vlhy {\G, \Left \Rightarrow x \colon A }}{\vlhy {\G, \Left \Rightarrow x \colon B}}}$

		\vspace{4mm}
		$\vlderivation {\vliin {\solefs}{}{\G, \Left, x \colon \vls[A.B] \Rightarrow z \colon C}{\vlhy {\G, \Left, x \colon A \Rightarrow z \colon C}}{\vlhy {\G, \Left, x \colon B \Rightarrow z \colon C}}}$
		\hspace{5mm}$\vlderivation { \vlin{\sorones}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlhy {\G, \Left \Rightarrow x \colon A}}}$
		\hspace{5mm}$\vlderivation { \vlin {\sotwos}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlhy {\G, \Left \Rightarrow x \colon B}}}$

		\vspace{4mm}
		$\vlderivation {\vliin{\sils}{}{\G, \Left, x \colon A \vljm B \Rightarrow z \colon C}{\vlhy {\G, \Left \Rightarrow x \colon A}}{\vlhy {\G, \Left, x \colon B \Rightarrow z \colon C}}}$
		\hspace{7mm}$\vlderivation {\vlin{\sirs}{}{\G,  \Left, x \colon A \Rightarrow x \colon B}{\vlhy {\G, \Left, x \colon A \Rightarrow x \colon B}}}$

		\vspace{4mm}
		$\vlderivation { \vlin {\sbls}{}{\G, xRy, \Left, x \colon \square A \Rightarrow z\colon B}{\vlhy {\G, xRy, \Left, x \colon \square A, y \colon A \Rightarrow z\colon B}}}$
		\hspace{23mm}$\vlderivation { \vlin {\sbrs}{y$ fresh$}{\G, \Left \Rightarrow x \colon \square A}{\vlhy {\G, xRy, \Left \Rightarrow y \colon A}}}$

		\vspace{4mm}
		$\vlderivation { \vlin{\sdls}{y$ fresh$}{\G, \Left, x \colon \Diamond A \Rightarrow z \colon B}{\vlhy {\G, xRy, \Left, y \colon A \Rightarrow z \colon B}}}$
		\hspace{7mm}$\vlderivation {\vlin {\sdrs}{}{\G,xRy, \Left \Rightarrow x \colon \Diamond A}{\vlhy {\G, xRy, \Left \Rightarrow y \colon A }}}$
	\end{center}
	\caption{System $\labIKs$}
	\label{fig:simpson}
\end{figure}

%\raul{Aca mencionar que es solo un sketch, y decir en una frase qué falta}
Lo siguiente representa un boceto de la prueba que se continuará como trabajo a futuro. Faltan incluir las demostraciones para la regla de $\sirs$ y para $\sbrs$.

\newpage
\begin{proof}
	La demostración de completitud utilizando el sistema propuesto por Simpson, como se detalló rápidamente al comienzo de esta sección, será a través de
	 análisis de casos. La mayoría de las reglas en $\labIKs$ son las mismas reglas que en el sistema $\labIKh$ excepto por las siguientes:
	\begin{center}
		\begin{itemize}

		\item Regla $\idsim$:

		\begin{center}
		$\vlderivation { \vlin {\idsim}{}{\G, \Left, x \colon A \Rightarrow x \colon a}{\vlhy {}}}$ \hspace{4mm}  \begin{huge}$  \rightarrow$ \end{huge} \hspace{4mm} $\vlderivation{\vlin {\refl}{}{\G, \Left, x \colon a \Rightarrow x \colon a}{\vlin {\ids}{}{\G,x \le x, \Left, x\colon a \Rightarrow x \colon a}{\vlhy {}}}}$
	\end{center}

		\vspace{5mm}
		\item Regla $\sorones$ y $\sotwos$:

		\begin{center}
		$\vlderivation {\vlin {\sorones}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlpd {\Done}{}{\G, \Left \Rightarrow x \colon A}}}$\hspace{2mm} or \hspace{2mm}$\vlderivation {\vlin {\sotwos}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlpd {\Done}{}{\G, \Left \Rightarrow x \colon B}}}$ \hspace{4mm} \begin{huge}$\rightarrow$\end{huge} \hspace{4mm} $\vlderivation {\vlin {\sorig}{}{\G, \Left \Rightarrow x \colon \vls[A.B]}{\vlpd{\Dwone}{}{\G, \Left \Rightarrow x \colon A, x \colon B}}}$
	\end{center}

		\newpage

		\item Regla $\sils$:

		\begin{center}
		$\vlderivation { \vliin {\sils}{}{\G, \Left, x \colon A \vljm B \Rightarrow z \colon C}{\vlpd {\Done}{}{\G, \Left \Rightarrow x \colon A}}{\vlpd {\Dtwo}{}{\G, \Left, x \colon B \Rightarrow z \colon C}}}$ \bigskip

			\begin{huge}$\downarrow$\end{huge}\\

		 \bigskip

		  $\vlderivation {\vlin {\refl}{}{\G, \Left, x \colon A \vljm B \Rightarrow z \colon C}{\vliin {\sil}{}{\G, \Left, x\le x, x \colon A \vljm B \Rightarrow z \colon C}{\vlpd {\Dwone}{}{\G, \Left, x \le x, x \colon A \vljm B \Rightarrow x\colon A}}{\vlpd {\Dwtwo}{}{\G, \Left, x \le x, x \colon B \Rightarrow z \colon C}}}}$
	\end{center}
		%\vspace{5mm}
		%\item Regla $\sirs$:

		%\begin{center}
		%$\vlderivation {\vlin {\sirs}{}{\G, \Left \Rightarrow x \colon A \vljm B}{\vlpd {\Done}{}{\G, \Left, x \colon A \Rightarrow x \colon B}}}$ \hspace{4mm} \begin{huge}$\rightarrow$\end{huge} \hspace{4mm} $\vlderivation {\vlin {\sir}{}{\G, \Left \Rightarrow x \colon A \vljm B}{\vlpd {\Dwone}{}{\G, \Left, x \le x, x \colon A \Rightarrow x \colon B}}}$
		%\end{center}

		\vspace{5mm}
		\item Regla $\sbls$:

		\begin{center}
		$\vlderivation {\vlin {\sbls}{}{\G, \Left, xRy, x \colon \square A \Rightarrow z \colon B}{\vlpd {\Done}{}{\G, \Left, xRy, x \colon \square A, y \colon A \Rightarrow z \colon B}}}$ \bigskip

			\begin{huge}$\downarrow$\end{huge}\\

		\bigskip

		 $\vlderivation {\vlin {\refl}{}{\G, \Left, xRy, x \colon \square A \Rightarrow z \colon B}{\vlin {\sbl}{}{\G, \Left, x \le x, xRy, x \colon \square A \Rightarrow z \colon B}{\vlpd {\Dwone}{}{\G, \Left, x \le x, xRy, x \colon \square A, y \colon A \Rightarrow z \colon B}}}}$
	\end{center}

		%\vspace{5mm}
		%\item Regla $\sbrs$:

		%\begin{center}
		%$\vlderivation {\vlin {\sbrs}{}{\G, \Left \Rightarrow x \colon \square A}{\vlpd {\Done}{}{\G, \Left, xRy \Rightarrow y \colon A}}}$ \hspace{4mm} \begin{huge}$\rightarrow$ \end{huge} \hspace{4mm} $\vlderivation {\vlin {\sbr}{}{\G, \Left \Rightarrow x \colon \square A}{\vlpd {\Dwone}{}{\G, \Left, x \le x, xRy \Rightarrow y \colon A}}}$
	%\end{center}

		\vspace{5mm}
		\item Regla $\sdrs$:

		\begin{center}
		$\vlderivation {\vlin {\sdrs}{}{\G, xRy, \Left \Rightarrow x \colon \Diamond A}{\vlpd {\Done}{}{\G, xRy, \Left \Rightarrow y \colon A}}}$ \hspace{4mm} \begin{huge}$\rightarrow$ \end{huge} \hspace{4mm} $\vlderivation {\vlin {\sdr}{}{\G, xRy, \Left \Rightarrow x \colon \Diamond A}{\vlpd {\Dwone}{}{\G, xRy, \Left \Rightarrow x \colon \Diamond A, y \colon A}}}$
	\end{center}

		\end{itemize}
	\end{center}
\end{proof}

Nuestra conjetura es que es posible demostrar completitud del sistema $\labIKh$ haciendo un análisis de cada una de las reglas de secuentes presentes en el sistema de Simpson (a partir del uso de las reglas de nuestro sistema).

### 2019-08-05 caleidoscope/caleidoscope.tex
first version caleidoscope

\documentclass[twoside]{aiml18}

\usepackage{aiml18macro}

\usepackage[noxy]{virginialake}                        
\usepackage{lmodern}
\usepackage{amssymb,amsmath} 
\usepackage{mathtools}
\usepackage[spanish]{babel}
\usepackage[utf8]{inputenc} 
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{color}
\usepackage{pgf}
\usepackage[all]{xy}
\usepackage{tikz}
%\usepackage{hyperref}
\usepackage{pgffor}

\tikzset{
	annotated cuboid/.pic={
		\tikzset{%
			every edge quotes/.append style={midway, auto},
			/cuboid/.cd,
			#1
		}
		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;

		;
	},
	/cuboid/.search also={/tikz},
	/cuboid/.cd,
	width/.store in=\cubex,
	height/.store in=\cubey,
	depth/.store in=\cubez,
	units/.store in=\cubeunits,
	scale/.store in=\cubescale,
	width=10,
	height=10,
	depth=10,
	units=cm,
	scale=.1,
}
%tikz parameters

\tikzstyle{point}=[circle,draw]
\usetikzlibrary{arrows,automata,shapes,decorations.markings,
	decorations.pathmorphing,backgrounds,fit,snakes,calc}

%\usepackage{float}
%\floatstyle{boxed} 
%\restylefloat{figure}

\usepackage{colonequals}
\usepackage{bm}

%%% Extracting symbols from MnSymbol 
\DeclareFontFamily{U} {MnSymbolC}{}
%
\DeclareFontShape{U}{MnSymbolC}{m}{n}{
	<-6>  MnSymbolC5
	<6-7>  MnSymbolC6
	<7-8>  MnSymbolC7
	<8-9>  MnSymbolC8
	<9-10> MnSymbolC9
	<10-12> MnSymbolC10
	<12->   MnSymbolC12}{}
\DeclareFontShape{U}{MnSymbolC}{b}{n}{
	<-6>  MnSymbolC-Bold5
	<6-7>  MnSymbolC-Bold6
	<7-8>  MnSymbolC-Bold7
	<8-9>  MnSymbolC-Bold8
	<9-10> MnSymbolC-Bold9
	<10-12> MnSymbolC-Bold10
	<12->   MnSymbolC-Bold12}{}
%
\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
%
\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}

%%% Comments  
\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
\newcommand{\lutz}[1]{{\color{green}[Lutz: #1]}}
\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}

%%% General
\input{aiml_macros}
%\newcommand{\F}{\mathcal{F}}
%\newcommand{\M}{\mathcal{M}}
%\newcommand{\G}{\mathcal{G}}
\newcommand{\B}{\mathcal{B}}
%\newcommand{\Left}{\mathcal{L}}
%\newcommand{\Right}{\mathcal{R}}

%%% Systems
\newcommand*{\ax}[1]{\mathsf{#1}}
\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
\newcommand*{\lab}{\mathsf{lab}}
\newcommand*{\IK}{\mathsf{IK}}
\newcommand*{\labIKp}{\lab\IK_{\le}}

%%% Connectives
\newcommand*{\NOT}{\neg}
\newcommand*{\AND}{\mathbin{\wedge}}
\newcommand*{\TOP}{\mathord{\top}}
\newcommand*{\OR}{\mathbin{\vee}}
\newcommand*{\BOT}{\mathord{\bot}}
\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}

\newcommand*{\BOX}{\mathord{\Box}}
\newcommand*{\DIA}{\mathord{\Diamond}}

%%% Labelled sequents
\newcommand*{\labels}[2]{{\color{blue}{#1}\:\colon}{#2}}
\newcommand{\SEQ}{\Rightarrow}
\newcommand*{\DD}{\mathcal{D}}
\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
\newcommand*{\invr}[1]{#1^\bullet}
\newcommand*{\rel}{R}

%%% Labelled rules
\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
%
\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
%
\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%The following line defines the page header consisting of the surnames of the authors.
% Please include only the last names! 
% Separate by commas except the last two surnames which are separated by an "and".
\def\lastname{Marin, Morales and Stra{\ss}burger}

\begin{document}

\begin{frontmatter}
  \title{Decomposing labelled proof theory for intuitionistic modal logic}
  \author{Sonia Marin}
  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
 \author{Marianela Morales}
 \address{Universidad Nacional de C\'ordoba \\ Argentina}
   \author{Lutz Stra{\ss}burger}
 \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}

 \begin{abstract}
   We present a labelled sequent system for intuitionistic modal logic equipped 
   with two relation symbols, one for the accessibility
   relation associated with the Kripke semantics for modal logics and
   one for the preorder relation associated with the Kripke semantics
   for intuitionistic logic. 
   %
   Thus, it is in close correspondence with birelational Kripke semantics for intuitionistic modal logic and can encompass a wider range of intuitionistic logics than state-of-the-art labelled systems.

   %% . We show the possibility of extend labelled sequents
   %% with a preorder relation symbol in order to capture intuitionistic
   %% modal logic. For this, we obtain a proof system which is complete
   %% with respect to Hilbert system.  Also, we present the proof for
   %% completeness using Simpson system.
  \end{abstract}

  \begin{keyword}
  Intuitionistic modal logic, Labelled sequents, Proof theory.
  \end{keyword}
 \end{frontmatter}

\section{Introduction}
One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged. Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.

\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
systems for a wide range of logics. 
%
For modal logics it can take
the form of labelled natural deduction and labelled sequent systems as
used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
Negri~\cite{Negri}. 
%
These formalisms make explicit use not only of
labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
%
In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
logics) and the \emph{preorder relation} (for intuitionistic
logic), using the full power of the bi-relational semantics for
intuitionistic modal logics,
and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.

%
%For sequent systems for intuitionistic logics there is always a choice
%to be made: make the system \emph{single conclusion} following
%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
%variant because of the closer correspondence to the semantics. In that
%respect, our system is closer to~\cite{kuz:str} than
%to~\cite{Simpson} and~\cite{mar:str}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminaries}
\marianela{Depends on how long the paper has to be, we can add a section with preliminaries: labelled sequents for classical modal logic and syntax and semantics of classical modal logic}

Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $xRy$, where $x$, $y$ range over a set of variables and $A$ is a modal formula. A one-sided labelled sequent is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational atoms and $\Right$ a multiset of labelled formulas. A simple proof system for classical modal logic K can be obtained in this formalism (\ref{fig:systemlabK}). 
\begin{figure}[h]
\begin{center}

$\vlderivation {\vlinf{\id}{}{\B \SEQ \Right, x: a, x: \vls-a}{}}$
\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$

$\vliinf{\vlab}{}{\B \SEQ \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
\hspace{7mm}$\vlinf{\olab}{}{\B \SEQ \Right, x \colon \vls[A.B]}{\olabr}$

$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$

\end{center}
\caption{System $\mathsf{labK}$}
\label{fig:systemlabK}
\end{figure}

These rule schemes can occur in different contexts and different calculi. The context that interests us is when it is applied to modal logic.
The idea to extend this system to another to capture intuitionistic modal logics allows us to study the Kripke semantics for this type of logics:

\section{Intuitionistic modal logics}

	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
	%
	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
	%
	$$
	A \coloncolonequals
	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
	$$
	%
	%We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.

%Obtaining the intuitionistic variant of K is more involved than the classical variant. 
%%
%Lacking De Morgan duality, there are several variants of k that are classically but not intuitionistically
%equivalent. 
%%
%Five axioms have been considered as primitives in the literature. 
%

The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
%
It is obtained from intuitionistic propositional logic by adding:
\begin{itemize}
\item the \emph{necessitation rule}: $\BOX A$ is a theorem if $A$ is a theorem; and
\item the following five variants of the \emph{distributivity axiom}:
\begin{equation*}
\label{eq:ik}%\hskip-2em
\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
&
\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
&
\kax[5]\colon&\DIA\BOT\IMP\BOT
\\
\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
&
\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
\end{array}
\end{equation*}
\end{itemize}

The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
%
It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.

\begin{definition}
	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
	\begin{enumerate}
		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
		\marianela{we can add the figures for each condition}
%	\begin{figure}[h]
%		\begin{center}
%			\begin{tikzpicture}[>=latex]
%			\node (a0) at (-1,0)   [shape=circle,draw,fill, inner sep=1pt,label=left:$u$] {} ;
%			\node (a1) at (-1,2)  [shape=circle,draw,fill, inner sep=1pt, label=left:$u'$] {} ;
%			\node (a2) at (1,0)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v$] {} ;
%			\node (a3) at (1,2)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v'$] {} ;
%			\draw [dotted,->] node[left] at (-1,1){$\le$}(a0) edge [ left] (a1);
%			\draw [ar,->] node[above] at (0,2){$R$}(a0) edge [ right] (a2);
%			\draw [dotted, ->] node[right] at (1,1){$\le$}(a1) edge [ left] (a3);
%			\draw [ar,->] node[above] {$R$} (a2) edge [ left] (a3);
%			;
%			\end{tikzpicture}
%			\end{center}
%		\end{figure}

		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
	\end{enumerate}
%	
\end{definition}

\begin{definition}
	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
	if $w \le w'$ then $V(w)\subseteq V(w')$.
\end{definition}

We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
%
Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:

$w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$

$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$

$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$

$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill $(\ast)$

$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.

%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\

We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \SEQ \bot$).

From the monotonicity of the valuation function $V$ , we get a monotonicity property for the relation:
\begin{proposition}(Monotonicity) 
For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
\end{proposition}

\begin{definition}
	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
%
	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
\end{definition}

%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
%
%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.

Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.

\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
\end{theorem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Labelled sequent calculi with $\rel$ and $\le$}

\begin{figure}%[h]
	\centering
	\small
	\fbox{
	\begin{minipage}{.95\textwidth}
	\begin{tabular}{@{\!}c@{\quad}c}
		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
		&
		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
		\quad
		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
		\\\\
		$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
		&
		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
		\\\\
		$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
		&
		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
		\\\\
		\multicolumn{2}{c}{
		$\vlinf{\llabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, x \le y, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
		}
		\\\\
		\multicolumn{2}{c}{
 		$\vliinf{\rlabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
 		}
		\\\\
		$\vlinf{\llabrn\BOX}{}{\B, \Left, x \le y, yRz, \labels{x}{\BOX A} \SEQ \Right}{\B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
		&
		$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \Left, x \le y, y \rel z \SEQ \Right, \labels{z}{A}}$
		\\\\
		$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \Left, x \rel y, \labels{y}{A} \SEQ \Right}$
		&
		$\vlinf{\rlabrn\DIA}{}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
		\\
		\multicolumn{2}{c}{
		$\mbox{\hbox to .9\linewidth{\dotfill}}$
		}
		\\
		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
		&
		$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
		\\\\
		\multicolumn{2}{c}{
		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
		}
		\\\\
		\multicolumn{2}{c}{
		$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
		}
	\end{tabular}		
\end{minipage}
}		
	\caption{System $\labIKp$}
	\label{fig:labIKp}
\end{figure}

%%
%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.

Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{Simpson}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{Strassburger} (for a survey see~\cite[Chap.~3]{Marin}).

Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent. Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
%
Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
%
The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}. 
%

\begin{definition}
A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
\end{definition}

%
We obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic in this formalism. 
%
Most rules are similar to the ones of Simpson~\cite{Simpson}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
%
In particular, the rules introducing the $\BOX$-operator correspond to the definition $(\ast)$.
%
Furthermore, our system has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.

As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:

%\begin{theorem}
%	\label{thm:sound-compl}
%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
%\end{theorem}
%
%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
%
%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.

%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.

\begin{theorem}\label{thm:cutfree-compl}
	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
	%
	For any formula $A$, the following are equivalent.
	%
	\begin{enumerate}
		\item\label{i} $A$ is a theorem of $\IK$ 
		%
		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
%		
%		\todo{}
		\smash{%\fbox{
			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
		}%}
		%
		\item\label{iii} $A$ is provable in $\labIKp$
		%
		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
	\end{enumerate}
\end{theorem}

%We show that each rule from our system is sound.
%
%
%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
%
%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
%
%We show the proof by case analysis. 
%
%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.

The proof is a careful adaptation of standard techniques.
%
In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens. As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms. 
%
As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.

\vspace*{-.9cm}
$$
\hspace*{-.5cm}
\scalebox{.9}{
$
\vlderivation{
	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
										\vlhy {}
										}
									}
								}
							}{
%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
										\vlhy {\qquad\vdots\qquad}
%										}
%									}
%								}
%							}
						}
					}
				}
			}
		}
	}
}$
}$$
%\end{example}

%\vspace*{-.5cm}

Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
%
We therefore have to show that such a rule is admissible in our system.
%
As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).

\vspace*{-.5cm}
%\begin{example}
$$
\scalebox{.9}{
$
\vlderivation{
	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
					\vlhy{}
				}
			}
		}
	}
}
$
}
$$
%\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marianela{If it is a long paper, we can give us the space to explain the system with details. So we can add something like the next section (presenting the system by parts and then put the whole system).}

\section{Building $\labIKp$}

As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{Negri}. In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics. This new system has labelled formulas of the form $x \colon A$, the expressions $xRy$ (the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and expressions $x \le y$ were introduced to represent the pre-order relation. In the next sub-sections, we study each rule of the system $\labIKp$ in detail.

\subsection{Frame conditions}
%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a pre-order relation, i.e, a reflexivity and transitivity relation. For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$. Furthermore, the rules that characterized the frame conditions $\rn{F1}$ and $\rn{F2}$. On the other hand, the valuation function $V$ that introduces the $Monoto$ is captured with the rule $\rn{id}$ in our system. All these rules are the next ones:

\todo{fix this figure!}

\begin{center}
	$\vlinf{\refl}{}{\B, \Left \Rightarrow \Right}{\B, x\le x, \Left \Rightarrow \Right}$\hspace{8mm}
	$\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \Rightarrow \Right}{\B, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$

	$\vlinf{\ids}{}{\B, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$

	\vspace{2mm}

	$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$

	\vspace{2mm}
	$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$

\end{center}

As an example, here there is a small explanation about the rules $\fone$ and $\ftwo$:

\begin{itemize}
	\item Rule $\fone$.

	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:

	\begin{center}
		$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
	\end{center}

	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, then reading the rule $\fone$ from the conclusion to the premises, we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.

	\item Rule $\ftwo$:

	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:

	\begin{center}
		$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
	\end{center}

	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses semantically from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.

\end{itemize}

\subsection{Logical connectives for intuitionistic propositional logic}

To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives. That means, we present the rules for the conjunction and dijunction of the system $\labIKp$:

\begin{center}
	\hspace{4mm}$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$\hspace{10mm}
	$\vliinf{\svrig}{}{B,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$

	\vspace{5mm}

	$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\B, \Left, x   \colon   A \Rightarrow \Right}{\B, \Left, x   \colon   B \Rightarrow \Right}$\hspace{10mm}
	$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
\end{center}

To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:

\begin{center}
	$\vlinf{\sbot}{}{\B,\Left, x \colon \bot \Rightarrow \Right}{}$\hspace{18mm}
	$\vlinf{\Stop}{}{B, \Left \Rightarrow \Right, x \colon \top}{}$
\end{center}

You can find a small explanation about the rules $\svlef$ and  $\sorig$:

\begin{itemize}
	\item Rule $\svlef$:

	The system $\labIKp$ presents the next rule for the conjunction left:

	\begin{center}
		$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
	\end{center}

	Following the explanation of the rules presented before, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of labelled formulas. From the conclusion to the premise, this rule shows semantically that if in the $x$ the formula $A \vlan B$ is satisfied, then in $x$ the formula $A$ is satisfied and the formula $B$ too.

	\item Rule $\sorig$:

	Let the rule presented in $\labIKp$ for disjunction right:

	\begin{center}
		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
	\end{center}

	From the conclusion to the premise we have: if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.

\end{itemize}

\subsection{Modal operators}

We introduce the rules that represent the semantics of modal operators $\square$ and $\Diamond$. The system $\labIKp$ presents the next four rules (two for $\square$ and two for $\Diamond$):

\begin{center}
	$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$

	$\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \Rightarrow \Right, x \colon \square A}{\B, \Left, x \le y, yRz \Rightarrow \Right, z \colon A}$

	\vspace{5mm}

	$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \Diamond A \Rightarrow \Right}{\B, \Left, xRy, y \colon A \Rightarrow \Right}$\hspace{10mm}
	$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$

\end{center}

A more detailed explanation is below:

\begin{itemize}
	\item Rule $\sbl$.

	In order to capture $\square$ left, in our system the next rule is introduced:

	\begin{center}
		$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
	\end{center}

	Continue with the same reasoning, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of laballed formulas. Semantically, the rule express, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.

	\item Rule $\sdr$.

	The rule presented in the system $\labIKp$ for the $\Diamond$ left is the following:

	\begin{center}
		$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
	\end{center}

	Semantically, the diamond establish that in a model $\M$ and a world $v$ the formula $\Diamond A$ is valid, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$. In order to capture this definition, the rule shows that if $xRy$ and the fomula $\Diamond A$ is satisfied in $x$, then the formula $A$ is true in $y$.

\end{itemize}

\subsection{Intuitionistic implication}

\todo{complete}

\section{Extensions}

In~\cite{Simpson}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
%
For example, you can add the following rule:
$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, w \rel u, \Left \SEQ \Right}$}$$
to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
$\ax{4}\colon (\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)$, that is, wrt.~to all frames in which $\rel$ is transitive.

In~\cite{Plotkin}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
%
For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \DIA\DIA A \IMP \DIA A$ are exactly the ones satisfying the condition:
%\begin{center}
	($\diabrn{4}$) if $w \rel v$ and $v \rel u$, there exists a $u'\in W$ s.t.~$u \le u'$ and $wRu'$.
%\end{center}

Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, u \le u', w \rel u' , \Left \SEQ \Right}$}$$

Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
%
These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.

\bibliographystyle{alpha}
\bibliography{references}

\end{document}

%\begin{figure}[h]
%\begin{center}
%$\vlderivation{\vlinf{\id}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}}$
%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\B, \Left, x\colon \bot \SEQ z\colon A}{}}$
%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\B, \Left \SEQ x \colon \top}{}}$
%
%\vspace{2mm}
%
%$\vlinf{\andleflab}{}{\B,\Left, x \colon \vls(A.B) \SEQ z \colon C}{\B, \Left, x\colon \vls(A.B,\labels{x}{A}, \labels{x}{B} \SEQ z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\B,\Left \SEQ x \colon \vls(A.B)}{\B, \Left \SEQ \labels{x}{A}}{\B, \Left \SEQ \labels{x}{B}}$
%
%\vspace{2mm}
%$\vliinf{\orleflab}{}{\B, \Left, x \colon \vls[A.B] \SEQ  \colon C}{\B, \Left, x \colon \vls[A.B], \labels{x}{A} \SEQ z \colon C}{\B, \Left, x \colon \vls[A.B], x   \colon   B \SEQ z \colon C}$
%
%\vspace{2mm}
%
%$\vlinf{\orriglabo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x   \colon   A}$
%\hspace{7mm}$\vlinf{\orriglabt}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x \colon  B}$
%
%\vspace{2mm}
%
%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \vljm B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \vljm B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \vljm B, \labels{x}{B} \SEQ z \colon C}$
%
%\vspace{2mm}
%
%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \vljm B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
%
%\vspace{2mm}
%
% $\vlderivation {\vlinf{\bllab}{}{\B, x \rel y, \Left x \colon \BOX A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z \colon B}}$
%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\B, \Left \SEQ x \colon \BOX A}{\B, x \rel y, \Left \SEQ y \colon A}$
%
%\vspace{2mm}
%
%$\vlinf{\dllab}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \DIA A, y \colon A \SEQ z \colon B}$
%\hspace{5mm}$\vlinf{\drlab}{}{\B, x \rel y, \Left,  \SEQ x \colon \DIA A}{\B, x \rel y, \Left \SEQ y \colon A}$
%
%\end{center}
%\caption{System labIK}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{figure}%[h]
%	
%	\begin{center}
%		
%		$\vlderivation { \vlin {\ids}{}{\B, \Left, \labels{x}{A} \SEQ x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\B, \Left, x \colon \bot \SEQ z\colon A}{\vlhy {}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation {\vlin {\svlef}{}{\B, \Left, x \colon \vls(A.B) \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ z \colon C}}}$
%		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\B, \Left, \SEQ x \colon \vls(A.B)}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
%		
%		\vspace{3mm}
%		
%		
%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \vljm B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
%		
%	\end{center}
%	
%	\caption{System $\lab\IK$}
%	\label{fig:labIK}
%\end{figure}
%
%\begin{theorem}[Simpson~\cite{Simpson}]
%	\label{thm:simpson-sound-compl}
%	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
%\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{figure}%[h]
%	\small
%	\centering
%
%		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
%		\hspace{5mm}
%		$\vlinf{\llabrn\bot}{}{\B, \Left, x\colon \bot \SEQ \Right}{}$
%		\hspace{5mm}
%		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, x \colon \top}{}$
%%		
%%		\vspace{4mm}
%		\\[1.5ex]
%%		
%		$\vlinf{\llabrn\AND}{}{\B,\Left, x \colon \vls(A.B) \SEQ \Right}{\conjlef}$
%		\hspace{7mm}
%		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
%		
%		\vspace{4mm}
%		
%		$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ \Right}{\B, \Left, x   \colon   A \SEQ \Right}{\B, \Left, x   \colon   B \SEQ \Right}$
%		\hspace{7mm}
%		$\vlinf{\sorig}{}{\B, \Left \SEQ \Right, x \colon \vls[A.B]}{\B, \Left \SEQ \Right, x   \colon   A, x   \colon   B}$
%		
%		\vspace{4mm}
%		
%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \vljm B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
%		
%		\vspace{4mm}
%		
%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \vljm B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \vljm B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
%		
%		\vspace{4mm}
%		
%		$\vlderivation {\vlinf{\sbl}{}{\B, \Left, x \le y, y \rel z, x \colon \BOX A \SEQ \Right}{\B,\Left, x \le y, y \rel z, x \colon \BOX A, z \colon A \SEQ \Right}}$
%		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \SEQ \Right, x \colon \BOX A}{\B, \Left, x \le y, y \rel z \SEQ \Right, z \colon A}$
%		
%		
%		\vspace{4mm}
%		
%		$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ \Right}{\B, \Left, x \rel y, y \colon A \SEQ \Right}$
%		\hspace{5mm}$\vlinf{\sdr}{}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A, y \colon A}$
%		
%		
%		\vspace{2mm}
%		
%		
%		\vspace{2mm}
%		
%		$\vlinf{\refl}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
%		\hspace{7mm} $\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
%		
%		
%		\vspace{2mm}
%		
%		$\vlinf{\rn{F_1}}{\text{\footnotesize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
%		%
%		$\vlinf{\rn{F_2}}{\text{\footnotesize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
%	
%	\caption{System $\labIKp$}
%	\label{fig:labHIK}
%\end{figure}

### 2019-08-06 caleidoscope/caleidoscope.tex
adding more information

@@
 \input{aiml_macros}
-%\newcommand{\F}{\mathcal{F}}
-%\newcommand{\M}{\mathcal{M}}
-%\newcommand{\G}{\mathcal{G}}
 \newcommand{\B}{\mathcal{B}}
-%\newcommand{\Left}{\mathcal{L}}
-%\newcommand{\Right}{\mathcal{R}}
 
@@
 \newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Equation environments
+\newdimen\mydisplayskip
+\mydisplayskip=.4\abovedisplayskip
+\newenvironment{smallequation}
+{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
+\newenvironment{smallequation*}
+{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
+\newenvironment{smallalign}
+{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
+\newenvironment{smallalign*}
+{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
+%
+\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
+\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
+%
+%
+\makeatletter
+\newbox\@conclbox
+\newdimen\@conclheight
+%
+%%%%%%
+\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
+\newcommand\vlderiibase[5]{{%
+		\setbox\@conclbox=\hbox{$#3$}\relax%
+		\@conclheight=\ht\@conclbox%
+		\setbox\@conclbox=\hbox{$%
+			\vlderivationnc{%
+				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
+			}$}%
+		\lower\@conclheight\box\@conclbox%
+	}}
+%%
+\newcommand\vlderibase[4]{{%
+		\setbox\@conclbox=\hbox{$#3$}\relax%
+		\@conclheight=\ht\@conclbox%
+		\setbox\@conclbox=\hbox{$%
+			\vlderivationnc{%
+				\vlin{#1}{#2}{\box\@conclbox}{#4}%
+			}$}%
+		\lower\@conclheight\box\@conclbox%
+	}}
+%
+\newcommand\vlderidbase[4]{{%
+		\setbox\@conclbox=\hbox{$#3$}\relax%
+		\@conclheight=\ht\@conclbox%
+		\setbox\@conclbox=\hbox{$%
+			\vlderivationnc{%
+				\vlid{#1}{#2}{\box\@conclbox}{#4}%
+			}$}%
+		\lower\@conclheight\box\@conclbox%
+	}}
+	%
+	\makeatother
+	%
+%%%General maths
+\newcommand*{\reducesto}{\quad{\leadsto}\quad}
 
@@
 
+\marianela{If it is a long paper, we can give us the space to explain the system with details.
+So we can add something like the next section (presenting the system by parts and then put the whole system).}
+
+\section{Building $\labIKp$}
+
+As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{Negri}.
+In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
+This new system has labelled formulas of the form $x \colon A$, the expressions $xRy$ (the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and expressions $x \le y$ were introduced to represent the pre-order relation.
+In the next sub-sections, we study each rule of the new system $\labIKp$ in details (Figure \ref{fig:labIKp}).
+
+\subsection{Frame conditions}
+%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
+The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a pre-order relation, i.e, a reflexivity and transitivity relation.
+For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
+Furthermore, the rules that characterized the frame conditions $\rn{F1}$ and $\rn{F2}$.
+On the other hand, the valuation function $V$ that introduces the $Monoto$ is captured with the rule $\rn{id}$ in our system.
+All these rules are the next ones:
+
+\todo{fix this figure!}
+
+\begin{center}
+	$\vlinf{\refl}{}{\B, \Left \Rightarrow \Right}{\B, x\le x, \Left \Rightarrow \Right}$\hspace{8mm}
+	$\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \Rightarrow \Right}{\B, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$
+
+	$\vlinf{\ids}{}{\B, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$
+
+	\vspace{2mm}
+
+	$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
+
+	\vspace{2mm}
+	$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
+
+\end{center}
+
+As an example, here there is a small explanation about the rules $\fone$ and $\ftwo$:
+
+\begin{itemize}
+	\item Rule $\fone$.
+
+	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
+
+	\begin{center}
+		$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
+	\end{center}
+
+	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, then reading the rule $\fone$ from the conclusion to the premises, we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
+
+	\item Rule $\ftwo$:
+
+	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
+
+	\begin{center}
+		$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
+	\end{center}
+
+	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses semantically from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
+
+\end{itemize}
+
+\subsection{Logical connectives for intuitionistic propositional logic}
+
+To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
+That means, we present the rules for the conjunction and dijunction of the system $\labIKp$:
+
+\begin{center}
+	\hspace{4mm}$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$\hspace{10mm}
+	$\vliinf{\svrig}{}{B,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
+
+	\vspace{5mm}
+
+	$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\B, \Left, x   \colon   A \Rightarrow \Right}{\B, \Left, x   \colon   B \Rightarrow \Right}$\hspace{10mm}
+	$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
+\end{center}
+
+To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
+
+\begin{center}
+	$\vlinf{\sbot}{}{\B,\Left, x \colon \bot \Rightarrow \Right}{}$\hspace{18mm}
+	$\vlinf{\Stop}{}{B, \Left \Rightarrow \Right, x \colon \top}{}$
+\end{center}
+
+You can find a small explanation about the rules $\svlef$ and  $\sorig$:
+
+\begin{itemize}
+	\item Rule $\svlef$:
+
+	The system $\labIKp$ presents the next rule for the conjunction left:
+
+	\begin{center}
+		$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
+	\end{center}
+
+	Following the explanation of the rules presented before, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
+From the conclusion to the premise, this rule shows semantically that if in the $x$ the formula $A \vlan B$ is satisfied, then in $x$ the formula $A$ is satisfied and the formula $B$ too.
+
+	\item Rule $\sorig$:
+
+	Let the rule presented in $\labIKp$ for disjunction right:
+
+	\begin{center}
+		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
+	\end{center}
+
+	From the conclusion to the premise we have: if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
+
+\end{itemize}
+
+\subsection{Modal operators}
+
+We introduce the rules that represent the semantics of modal operators $\square$ and $\Diamond$. The system $\labIKp$ presents the next four rules (two for $\square$ and two for $\Diamond$):
+
+\begin{center}
+	$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
+
+	$\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \Rightarrow \Right, x \colon \square A}{\B, \Left, x \le y, yRz \Rightarrow \Right, z \colon A}$
+
+	\vspace{5mm}
+
+	$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \Diamond A \Rightarrow \Right}{\B, \Left, xRy, y \colon A \Rightarrow \Right}$\hspace{10mm}
+	$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
+
+\end{center}
+
+A more detailed explanation is below:
+
+\begin{itemize}
+	\item Rule $\sbl$.
+
+	In order to capture $\square$ left, in our system the next rule is introduced:
+
+	\begin{center}
+		$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
+	\end{center}
+
+	Continue with the same reasoning, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
+Semantically, the rule express, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
+
+	\item Rule $\sdr$.
+
+	The rule presented in the system $\labIKp$ for the $\Diamond$ left is the following:
+
+	\begin{center}
+		$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
+	\end{center}
+
+	Semantically, the diamond establish that in a model $\M$ and a world $v$ the formula $\Diamond A$ is valid, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
+In order to capture this definition, the rule shows that if $xRy$ and the fomula $\Diamond A$ is satisfied in $x$, then the formula $A$ is true in $y$.
+
+\end{itemize}
+
+\subsection{Intuitionistic implication}
+
+\todo{complete}
+
+\section{A complete and sound system for intuitionistic modal logics}
+
 %
@@
 
+\begin{proof}[Proof of \ref{ii} $\rightarrow$ \ref{iii}]
+
+	By induction on number of cuts + (rank,height) of the left-most top-most cut.
+
+	\textbf{Commutative cases:}\label{commutative-cases}
+
+	\begin{smallequation*}
+		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
+				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
+			}{
+			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
+		}
+	}{
+	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
+}
+\reducesto
+\end{smallequation*}
+
+\begin{smallequation*}\hspace*{-10em}
+	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
+			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
+		}{
+		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
+	}
+}{
+\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
+	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
+}{
+\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
+}
+}
+\end{smallequation*}
+
+We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
+%
+If it does we rewrite it with a fresh variable $v$ first.
+
+%\begin{smallequation*}
+%	\reducesto
+%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
+%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
+%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
+%%				}{
+%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
+%%				}
+%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
+%			}{
+%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
+%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
+%%				}{
+%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
+%%				}
+%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
+%			}
+%		}
+%\end{smallequation*}
+%
+%\begin{smallalign*}&
+%	\text{with } \DD_4 = \quad
+%	\vlderivation{
+%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
+%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
+%		}{
+%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
+%		}
+%	}
+%	\\&
+%	\text{and } \DD_5 = \quad
+%	\vlderivation{
+%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
+%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
+%		}{
+%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
+%		}
+%	}
+%\end{smallalign*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
+		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
+			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\reducesto
+	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
+		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
+			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
+		}{
+		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
+	}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
+		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
+			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\reducesto
+	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
+		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
+			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
+		}{
+		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
+	}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
+		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
+			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\reducesto
+	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
+		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
+			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
+		}{
+		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
+	}
+}
+\end{smallequation*}
+
+\begin{smallequation*}\hspace*{-7em}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
+			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
+}
+\reducesto
+\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
+		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
+	}{
+	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
+}
+}
+\end{smallequation*}
+
+\begin{smallequation*}\hspace*{-10em}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
+		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
+			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
+}
+\reducesto
+%	\end{smallequation*}
+%	
+%	\begin{smallequation*}
+\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
+	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
+		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
+	}{
+	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
+}
+}
+\end{smallequation*}
+
+\textbf{Key cases:}\label{key-cases}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
+		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
+			\vlhy{}	
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
+}
+\reducesto
+\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
+	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
+		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
+	}{
+	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
+		\vlhy{}	
+	}
+}
+\reducesto
+\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
+	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
+		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
+			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
+		}
+	}{
+	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
+	}{
+	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
+}
+}
+\reducesto
+\end{smallequation*}
+
+\begin{smallequation*}
+	\hspace*{-7em}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
+		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
+			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
+				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
+			}
+			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
+		}{
+		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
+	}
+}{
+\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
+	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
+}{
+\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
+}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
+		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
+			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
+		}
+	}{
+	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
+		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
+	}
+}
+\reducesto
+\end{smallequation*}
+
+\begin{smallequation*}\hspace*{-7em}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
+		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
+		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
+		%			}{
+		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
+		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
+		%					\vlhy{}
+		%					}
+		%				}
+		%			}
+	}{
+	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
+		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
+			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
+		}
+	}{
+	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
+}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
+		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
+			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
+		}
+	}{
+	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
+	}	
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
+		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
+			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
+		}{
+		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
+			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
+		}
+	}
+}{
+\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
+}
+\end{smallequation*}
+\end{proof}
+
+\begin{lemma}\label{lem:weak}\hbox{}\quad
+	\begin{enumerate}
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	Standard
+\end{proof}
+
+\begin{lemma}\label{lem:inv}\hbox{}\quad
+	\begin{enumerate}
+		\item
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
+		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+		\item
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
+		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
+		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
+		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+	\end{enumerate}
+\end{lemma}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\marianela{If it is a long paper, we can give us the space to explain the system with details.
-So we can add something like the next section (presenting the system by parts and then put the whole system).}
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{Negri}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system has labelled formulas of the form $x \colon A$, the expressions $xRy$ (the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and expressions $x \le y$ were introduced to represent the pre-order relation.
-In the next sub-sections, we study each rule of the system $\labIKp$ in detail.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a pre-order relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, the rules that characterized the frame conditions $\rn{F1}$ and $\rn{F2}$.
-On the other hand, the valuation function $V$ that introduces the $Monoto$ is captured with the rule $\rn{id}$ in our system.
-All these rules are the next ones:
-
-\todo{fix this figure!}
-
-\begin{center}
-	$\vlinf{\refl}{}{\B, \Left \Rightarrow \Right}{\B, x\le x, \Left \Rightarrow \Right}$\hspace{8mm}
-	$\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \Rightarrow \Right}{\B, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$
-
-	$\vlinf{\ids}{}{\B, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$
-
-	\vspace{2mm}
-
-	$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
-
-	\vspace{2mm}
-	$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
-
-\end{center}
-
-As an example, here there is a small explanation about the rules $\fone$ and $\ftwo$:
-
-\begin{itemize}
-	\item Rule $\fone$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, then reading the rule $\fone$ from the conclusion to the premises, we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-		$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses semantically from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and dijunction of the system $\labIKp$:
-
-\begin{center}
-	\hspace{4mm}$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$\hspace{10mm}
-	$\vliinf{\svrig}{}{B,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-
-	\vspace{5mm}
-
-	$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\B, \Left, x   \colon   A \Rightarrow \Right}{\B, \Left, x   \colon   B \Rightarrow \Right}$\hspace{10mm}
-	$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-	$\vlinf{\sbot}{}{\B,\Left, x \colon \bot \Rightarrow \Right}{}$\hspace{18mm}
-	$\vlinf{\Stop}{}{B, \Left \Rightarrow \Right, x \colon \top}{}$
-\end{center}
-
-You can find a small explanation about the rules $\svlef$ and  $\sorig$:
-
-\begin{itemize}
-	\item Rule $\svlef$:
-
-	The system $\labIKp$ presents the next rule for the conjunction left:
-
-	\begin{center}
-		$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
-	\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if in the $x$ the formula $A \vlan B$ is satisfied, then in $x$ the formula $A$ is satisfied and the formula $B$ too.
-
-	\item Rule $\sorig$:
-
-	Let the rule presented in $\labIKp$ for disjunction right:
-
-	\begin{center}
-		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
-	\end{center}
-
-	From the conclusion to the premise we have: if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\square$ and $\Diamond$. The system $\labIKp$ presents the next four rules (two for $\square$ and two for $\Diamond$):
-
-\begin{center}
-	$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
-
-	$\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \Rightarrow \Right, x \colon \square A}{\B, \Left, x \le y, yRz \Rightarrow \Right, z \colon A}$
-
-	\vspace{5mm}
-
-	$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \Diamond A \Rightarrow \Right}{\B, \Left, xRy, y \colon A \Rightarrow \Right}$\hspace{10mm}
-	$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
-
-\end{center}
-
-A more detailed explanation is below:
-
-\begin{itemize}
-	\item Rule $\sbl$.
-
-	In order to capture $\square$ left, in our system the next rule is introduced:
-
-	\begin{center}
-		$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
-	\end{center}
-
-	Continue with the same reasoning, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule express, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\sdr$.
-
-	The rule presented in the system $\labIKp$ for the $\Diamond$ left is the following:
-
-	\begin{center}
-		$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
-	\end{center}
-
-	Semantically, the diamond establish that in a model $\M$ and a world $v$ the formula $\Diamond A$ is valid, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the fomula $\Diamond A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-
-\todo{complete}
 

### 2019-08-06 caleidoscope/caleidoscope.tex
adding extensions with Scott-Lemmon
small modif

@@
 \usepackage{mathtools}
-\usepackage[spanish]{babel}
-\usepackage[utf8]{inputenc} 
 \usepackage{enumerate}
@@
 \newcommand{\B}{\mathcal{B}}
+\newcommand*{\A}{\mathcal{A}}
 
@@
 
+\todo{Simpson does not have internal cut-elimination}
 %
@@
 		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
-		\marianela{we can add the figures for each condition}
-%	\begin{figure}[h]
-%		\begin{center}
-%			\begin{tikzpicture}[>=latex]
-%			\node (a0) at (-1,0)   [shape=circle,draw,fill, inner sep=1pt,label=left:$u$] {} ;
-%			\node (a1) at (-1,2)  [shape=circle,draw,fill, inner sep=1pt, label=left:$u'$] {} ;
-%			\node (a2) at (1,0)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v$] {} ;
-%			\node (a3) at (1,2)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v'$] {} ;
-%			\draw [dotted,->] node[left] at (-1,1){$\le$}(a0) edge [ left] (a1);
-%			\draw [ar,->] node[above] at (0,2){$R$}(a0) edge [ right] (a2);
-%			\draw [dotted, ->] node[right] at (1,1){$\le$}(a1) edge [ left] (a3);
-%			\draw [ar,->] node[above] {$R$} (a2) edge [ left] (a3);
-%			;
-%			\end{tikzpicture}
-%			\end{center}
-%		\end{figure}
+
+			\begin{equation*}
+			\xymatrix{
+				u' \ar@{.>}[r]_R  & v' \\
+				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
+			}
+			\end{equation*}
 
 		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
+
+			\begin{equation*}
+			\xymatrix{
+				u' \ar@{.>}[r]^R & v' \\
+				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
+			}
+			\end{equation*}
 	\end{enumerate}
@@
 
+In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
+
 \marianela{If it is a long paper, we can give us the space to explain the system with details.
@@
 
+\marianela{add the next proofs as extensions with Scott-Lemmon?}
+
+Proof of $\ax{4_{\BOX}} \colon \BOX A \IMP \BOX\BOX A$
+
+$\vlderivation{
+	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
+		\vliq{\rlabrn\BOX}{}{x \le w, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
+			\vlin{\rn{F_1}}{}{x \le w, w \le w', \bm{w' \rel v}, \bm{v \le v'}, v' \rel u, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+				\vlin{\rn{trans}}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, \bm{w' \le t}, \bm{t \rel v'}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+					\vlin{\boxbrn{4}}{}{x \le w, w \le w', w' \rel v, v \le v', \bm{v' \rel u}, w' \le t, \bm{t \rel v'}, w \le t \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+						\vlin{\labrn\BOX}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, w' \le t, t \rel v', w \le t, \bm{t \rel u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+							\vlin{\labrn{id}}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, w' \le t, t \rel v', w \le t, t \rel u, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
+								\vlhy{}
+							}
+						}
+					}
+				}
+			}
+		}
+	}
+}
+$
+
+Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
+
+$\vlderivation{
+	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
+		\vliq{\llabrn\DIA}{}{x \le w, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
+			\vlin{\diasym_\rn{4}}{}{x \le w, w \rel v, v \rel u, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
+				\vlin{\rlabrn\DIA}{}{x \le w, w \rel v, v \rel u, u \le u', w \rel u'  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
+					\vlin{\labrn{id}}{}{x \le w, w \rel v, v \rel u, u \le u', w \rel u'  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
+						\vlhy{}
+					}
+				}
+			}
+		}
+	}
+}
+$
+
 \bibliographystyle{alpha}

### 2019-08-06 caleidoscope/caleidoscope.tex
adding intuitionistic implication rule

@@
 For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, the rules that characterized the frame conditions $\rn{F1}$ and $\rn{F2}$.
-On the other hand, the valuation function $V$ that introduces the $Monoto$ is captured with the rule $\rn{id}$ in our system.
+Furthermore, the system includes the rules that characterized the frame conditions $\rn{F1}$ and $\rn{F2}$.
+On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
 All these rules are the next ones:
@@
 
-As an example, here there is a small explanation about the rules $\fone$ and $\ftwo$:
+As an example, a small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
 
@@
 
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, then reading the rule $\fone$ from the conclusion to the premises, we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
+	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
 
@@
 
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses semantically from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
+	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
 
@@
 To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and dijunction of the system $\labIKp$:
+That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
 
@@
 
-You can find a small explanation about the rules $\svlef$ and  $\sorig$:
+You can find a small explanation about the rules $\svlef$ and  $\sorig$ below:
 
@@
 	Following the explanation of the rules presented before, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if in the $x$ the formula $A \vlan B$ is satisfied, then in $x$ the formula $A$ is satisfied and the formula $B$ too.
+From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$ , then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
 
@@
 	Continue with the same reasoning, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule express, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
+Semantically, the rule express \marianela{spelling}, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
 
@@
 \subsection{Intuitionistic implication}
-
-\todo{complete}
+To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
+
+\begin{center}
+	$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \vljm B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
+
+	\vspace{5mm}
+
+	$\vliinf{\sil}{}{\B, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right}{\B, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right, y \colon A}{\B, \Left, x \le y, x \colon A \vljm B, y \colon B \Rightarrow \Right}$
+\end{center}
+
+The meaning of the rule for implication right is below:
+
+\begin{itemize}
+	\item Rule $\sir$.
+
+	The system $\labIKp$ presents the following rule for implication right:
+
+	\begin{center}
+		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \vljm B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
+	\end{center}
+
+	Let $\B$ be a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \vljm B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
+\end{itemize}
 

### 2019-08-19 caleidoscope/caleidoscope.tex
some comments
adding todos and small modig

@@
   \author{Sonia Marin}
+
+  \todo{New university?}
   \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
  \author{Marianela Morales}
- \address{Universidad Nacional de C\'ordoba \\ Argentina}
+
+ \marianela{I think that now I have the same as Lutz, right?}
+ \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
    \author{Lutz Stra{\ss}burger}
@@
  \begin{abstract}
+
    We present a labelled sequent system for intuitionistic modal logic equipped 
@@
 \section{Introduction}
+\todo{We should work on the introduction}
+
 One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
@@
 
+\todo{re-build this section since the section \emph{intuitionistic modal logics} is part of the preliminaries}
+
 Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $xRy$, where $x$, $y$ range over a set of variables and $A$ is a modal formula.
@@
 A simple proof system for classical modal logic K can be obtained in this formalism (\ref{fig:systemlabK}).
+
+\todo{fix the next figure}
+
 \begin{figure}[h]
@@
 \begin{definition}
+	\label{model}
 	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
@@
 
-$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill $(\ast)$
+$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
 
@@
 \end{theorem}
+
+\todo{Add something else about Fischer-Servi theorem?}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\todo{re-write a small introduction for this section}
+
 %
@@
 %
-In particular, the rules introducing the $\BOX$-operator correspond to the definition $(\ast)$.
+In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
 %
@@
 %\end{example}
+
+\todo{Fix the size of the next proof}
 
@@
 
+\todo{Missing: Proof of iii $\rightarrow$ iv and Proof of iv $\rightarrow$ i}
+
+\todo{soundness sketch: general lemma? explain one or two rules?}
+
+\todo{how to introduce the next lemmas? add small explanation. both are necessary?}
+
 \begin{lemma}\label{lem:weak}\hbox{}\quad
@@
 
+\todo{Is necessary to write the entire proof?}
 \begin{proof}
@@
 \section{Extensions}
+
+\todo{Better explanation about the extensions. Maybe two sections: Simpson and Scott-Lemmon?}
+
+\marianela{Should we add Simpson proof?}
+
+\marianela{Scott-Lemmon with the new rules for the system and the lemma that shows that each rule is admissible?}
 

### 2019-08-22 caleidoscope/caleidoscope.tex
small modif

@@
 	%
-	%We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.
-
-%Obtaining the intuitionistic variant of K is more involved than the classical variant. 
+	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.
+
+Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
 %%
-%Lacking De Morgan duality, there are several variants of k that are classically but not intuitionistically
-%equivalent. 
-%%
-%Five axioms have been considered as primitives in the literature. 
+Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
 %

### 2019-08-28 caleidoscope/caleidoscope.tex
working on presentation of the system

@@
 
-\section{Preliminaries}
-\marianela{Depends on how long the paper has to be, we can add a section with preliminaries: labelled sequents for classical modal logic and syntax and semantics of classical modal logic}
-
-\todo{re-build this section since the section \emph{intuitionistic modal logics} is part of the preliminaries}
-
-Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $xRy$, where $x$, $y$ range over a set of variables and $A$ is a modal formula.
+%\section{Preliminaries}
+%\marianela{Depends on how long the paper has to be, we can add a section with preliminaries: labelled sequents for classical modal logic and syntax and semantics of classical modal logic}
+
+%\todo{re-build this section since the section \emph{intuitionistic modal logics} is part of the preliminaries}
+
+%\sonia{We should not have the definitions of classical modal logic.
+Just the intuitionistic part.
+If we want to say something else about labelled sequents, we should add it before the definition of \emph{a two-sided labelled sequent}}
+
+%Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $xRy$, where $x$, $y$ range over a set of variables and $A$ is a modal formula.
 A one-sided labelled sequent is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational atoms and $\Right$ a multiset of labelled formulas.
@@
 
-\todo{fix the next figure}
-
-\begin{figure}[h]
-\begin{center}
-
-$\vlderivation {\vlinf{\id}{}{\B \SEQ \Right, x: a, x: \vls-a}{}}$
-\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$
-
-$\vliinf{\vlab}{}{\B \SEQ \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
-\hspace{7mm}$\vlinf{\olab}{}{\B \SEQ \Right, x \colon \vls[A.B]}{\olabr}$
-
-$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
-\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
-
-\end{center}
-\caption{System $\mathsf{labK}$}
-\label{fig:systemlabK}
-\end{figure}
-
-These rule schemes can occur in different contexts and different calculi. The context that interests us is when it is applied to modal logic.
+%%\begin{figure}[h]
+%\begin{center}
+
+%$\vlderivation {\vlinf{\id}{}{\B \SEQ \Right, x: a, x: \vls-a}{}}$
+%\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$
+
+%$\vliinf{\vlab}{}{\B \SEQ \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
+%\hspace{7mm}$\vlinf{\olab}{}{\B \SEQ \Right, x \colon \vls[A.B]}{\olabr}$
+
+%$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
+%\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
+
+%\end{center}
+%\caption{System $\mathsf{labK}$}
+%\label{fig:systemlabK}
+%\end{figure}
+
+%These rule schemes can occur in different contexts and different calculi.
+The context that interests us is when it is applied to modal logic.
 The idea to extend this system to another to capture intuitionistic modal logics allows us to study the Kripke semantics for this type of logics:
@@
 	Continue with the same reasoning, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule express \marianela{spelling}, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
+Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
 
@@
 
-\todo{how to introduce the next lemmas? add small explanation. both are necessary?}
+\marianela{Yes! Soundness section: explain a box rule and an implication rule. Say that the scheme of the rest of the rules are similar}
+
+\todo{How to introduce the next lemmas? Add small explanation}
 
@@
 \end{lemma}
-
-\todo{Is necessary to write the entire proof?}
-\begin{proof}
-	Standard
-\end{proof}
 
@@
 
-\todo{Better explanation about the extensions. Maybe two sections: Simpson and Scott-Lemmon?}
-
-\marianela{Should we add Simpson proof?}
-
-\marianela{Scott-Lemmon with the new rules for the system and the lemma that shows that each rule is admissible?}
+\marianela{After Skype with Sonia: important section; add the generality of the rules for Scott-Lemmon; Simpson will be introduce in the introduction or/and in the conclusion. }
+
+\sonia{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
+
+\sonia{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}
 

### 2019-08-29 caleidoscope/caleidoscope.tex
working on extensions and soundness

@@
 	\begin{center}
-		$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
+		$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
 	\end{center}
@@
 
+\begin{proof} [Proof for soundness]
+	We need to prove that each sequent rule of our system $\labIKp$ is sound. As the proof is similar for each of the rules, we prove the soundness of some particular rules:
+
+	\begin{itemize}
+		\item Rule $\sbl$:
+
+		We want to prove that the rule for $\sbl$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
+
+		\begin{center}
+			\emph{For all model $\M$, if $\M \Vdash \B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$, then $\M \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$.}
+		\end{center}
+
+		By way of contradiction we want to see that if $\exists$ $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$,then $\M_{0} \not \Vdash premise$.
+More precisely for the $\sbl$ rule we want to show that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$ then $\M_{0} \not \Vdash \B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.
+
+		Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash x\colon \square A$ and  $\M_{0} \not \Vdash \Right$.
+Therefore, in particular, from $\M_{0} \Vdash \square A$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0},z \Vdash A$.
+Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.
+
+		\item Rule
+	\end{itemize}
+\end{proof}
+
 \todo{Missing: Proof of iii $\rightarrow$ iv and Proof of iv $\rightarrow$ i}
-
-\todo{soundness sketch: general lemma? explain one or two rules?}
 
@@
 
-\sonia{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
-
-\sonia{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}
+\todo{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
+
+\todo{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}
+
+The main goal of this section is to generate stronger logics adding new axioms to our system.
+We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
 
@@
 %
-These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
-
-\marianela{add the next proofs as extensions with Scott-Lemmon?}
+These systems enjoy cut-elimination via usual arguments. Proofs of the the axioms we mentioned are below:
 
@@
 $
+
+The generality of the result adds a new rule to the system $\labIKp$ in order to capture the \emph{Scott-Lemmon axiom} or \emph{$\agklmn$ axiom}: 
+\begin{center}
+	$\lozenge^{k} \square^{l} A \vljm \square^{m}\lozenge^{n} A$
+\end{center}
+Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
+
+$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
+
+$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \vljm \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
+
+See this axiom in the Figure~\ref{fig:gklmn} \todo{Wrong label}
+
+\begin{figure}[h]
+	\begin{center}
+		$
+		\xymatrix{
+			& u' \ar@{.>}[ddr]^{R^l} \\
+			& u \ar@{.>}[u]^{\le} \\
+			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
+			& v \ar@{.>}[ur]_{R^n}
+		}
+		$
+	\end{center}
+	\label{fig:gklmn}
+	\caption{$\agklmn$ axiom for intuitionistic case}
+\end{figure}
 

### 2019-08-30 caleidoscope/caleidoscope.tex
modif in the system

@@
 		\multicolumn{2}{c}{
-		$\vlinf{\llabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, x \le y, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+		$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
 		}
@@
 		\multicolumn{2}{c}{
- 		$\vliinf{\rlabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+ 		$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
 % 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
@@
 \begin{center}
-	$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \vljm B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
+	$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \IMP B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
 
@@
 
-	$\vliinf{\sil}{}{\B, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right}{\B, \Left, x \le y, x \colon A \vljm B \Rightarrow \Right, y \colon A}{\B, \Left, x \le y, x \colon A \vljm B, y \colon B \Rightarrow \Right}$
+	$\vliinf{\sil}{}{\B, \Left, x \le y, x \colon A \IMP B \Rightarrow \Right}{\B, \Left, x \le y, x \colon A \IMP B \Rightarrow \Right, y \colon A}{\B, \Left, x \le y, x \colon A \IMP B, y \colon B \Rightarrow \Right}$
 \end{center}
@@
 	\begin{center}
-		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \vljm B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
+		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \IMP B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
 	\end{center}
 
-	Let $\B$ be a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \vljm B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
+	Let $\B$ be a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
 \end{itemize}
@@
 \begin{center}
-	$\lozenge^{k} \square^{l} A \vljm \square^{m}\lozenge^{n} A$
+	$\lozenge^{k} \square^{l} A \IMP \square^{m}\lozenge^{n} A$
 \end{center}
@@
 
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \vljm \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
+$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
 
@@
 %
-%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \vljm B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \vljm B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \vljm B, \labels{x}{B} \SEQ z \colon C}$
+%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \IMP B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \IMP B, \labels{x}{B} \SEQ z \colon C}$
 %
@@
 %
-%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \vljm B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
+%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \IMP B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
 %
@@
 %		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \vljm B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
+%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
 %		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
@@
 %		
-%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \vljm B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
+%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \IMP B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
 %		
@@
 %		
-%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \vljm B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \vljm B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
+%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
 %		

### 2019-08-31 caleidoscope/caleidoscope.tex
modif on the system
soundness + lemmas

@@
 \usepackage{graphicx}
+\usepackage{bm}
 \usepackage{color}
@@
 %%% General
-\input{aiml_macros}
+\input{macros}
 \newcommand{\B}{\mathcal{B}}
@@
 	\begin{tabular}{@{\!}c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
+		$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
 		&
@@
 		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+ 		$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
 % 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
@@
 		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \Left, x \le y, yRz, \labels{x}{\BOX A} \SEQ \Right}{\B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+		$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
 		&
-		$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \Left, x \le y, y \rel z \SEQ \Right, \labels{z}{A}}$
+		$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
 		\\\\
-		$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \Left, x \rel y, \labels{y}{A} \SEQ \Right}$
+		$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
 		&
-		$\vlinf{\rlabrn\DIA}{}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
+		$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
 		\\
@@
 %This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
+Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
+Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{Gabbay}.
+For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{Simpson}, Vigano \cite{Vigano}, and Negri\cite{Negri}.
+These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{Nerode}).
 
@@
 %
+
 Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
@@
 \end{definition}
-
 In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\marianela{If it is a long paper, we can give us the space to explain the system with details.
-So we can add something like the next section (presenting the system by parts and then put the whole system).}
 
@@
 In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system has labelled formulas of the form $x \colon A$, the expressions $xRy$ (the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and expressions $x \le y$ were introduced to represent the pre-order relation.
-In the next sub-sections, we study each rule of the new system $\labIKp$ in details (Figure \ref{fig:labIKp}).
+This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
+In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
 
@@
 %In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a pre-order relation, i.e, a reflexivity and transitivity relation.
+The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
 For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, the system includes the rules that characterized the frame conditions $\rn{F1}$ and $\rn{F2}$.
+Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
 On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these rules are the next ones:
-
-\todo{fix this figure!}
+All these are presented in the system $\labIKp$ as follows:
 
 \begin{center}
-	$\vlinf{\refl}{}{\B, \Left \Rightarrow \Right}{\B, x\le x, \Left \Rightarrow \Right}$\hspace{8mm}
-	$\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \Rightarrow \Right}{\B, x \le y, y \le z, x \le z, \Left \Rightarrow \Right}$
-
-	$\vlinf{\ids}{}{\B, \Left,x \le y, x \colon a \Rightarrow \Right, y \colon a}{}$
-
-	\vspace{2mm}
-
-	$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
-
-	\vspace{2mm}
-	$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
+		\begin{minipage}{.95\textwidth}
+			\begin{tabular}{@{\!}c@{\quad}c}
+				\multicolumn{2}{c}{
+					\hspace{18mm}
+					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
+				}
+				\\\\
+				\hspace{15mm}
+				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
+				&
+				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
+
+				\\\\
+				\multicolumn{2}{c}{
+					\hspace{18mm}
+					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
+				}
+				\\\\
+				\multicolumn{2}{c}{
+					\hspace{18mm}
+					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
+				}
+			\end{tabular}		
+		\end{minipage}
 
@@
 
-As an example, a small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
+\bigskip
+
+A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
 
 \begin{itemize}
-	\item Rule $\fone$.
+	\item Rule $\rn{F1}$.
 
@@
 	\begin{center}
-		$\vlinf{\fone}{$ $u$ fresh$}{\B, \Left, xRy, y \le z \Rightarrow \Right}{\B, \Left, xRy, y \le z, x \le u, uRz \Rightarrow \Right}$
+		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
 	\end{center}
@@
 	\begin{center}
-		$\vlinf{\ftwo}{u$ fresh$}{\B, \Left, xRy,x \le z \Rightarrow \Right}{\B, \Left, xRy, x \le z, y \le u, zRu \Rightarrow \Right }$
+	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
 	\end{center}
@@
 \begin{center}
-	\hspace{4mm}$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$\hspace{10mm}
-	$\vliinf{\svrig}{}{B,\Left \Rightarrow \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-
-	\vspace{5mm}
-
-	$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \Rightarrow \Right}{\B, \Left, x   \colon   A \Rightarrow \Right}{\B, \Left, x   \colon   B \Rightarrow \Right}$\hspace{10mm}
-	$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
+	\begin{minipage}{.95\textwidth}
+		\begin{tabular}{@{\!}c@{\quad}c}
+			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
+			&
+			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
+			\\\\
+			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
+			&
+			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
+			\\\\
+		\end{tabular}
+	\end{minipage}
 \end{center}
@@
 \begin{center}
-	$\vlinf{\sbot}{}{\B,\Left, x \colon \bot \Rightarrow \Right}{}$\hspace{18mm}
-	$\vlinf{\Stop}{}{B, \Left \Rightarrow \Right, x \colon \top}{}$
+		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
+		\hspace{8mm}
+		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
 \end{center}
 
-You can find a small explanation about the rules $\svlef$ and  $\sorig$ below:
+You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
 
 \begin{itemize}
-	\item Rule $\svlef$:
-
-	The system $\labIKp$ presents the next rule for the conjunction left:
+	\item Rule $\llabrn\AND$:
+
+	%The system $\labIKp$ presents the next rule for the conjunction left:
+
+	%\begin{center}
+	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
+	%\end{center}
+
+	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
+From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
+
+	\item Rule $\rlabrn\OR$:
+
+	Let the rule presented in $\labIKp$ for disjunction right be as follows:
 
 	\begin{center}
-		$\vlinf{\svlef}{}{\B,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
+		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
 	\end{center}
 
-	Following the explanation of the rules presented before, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$ , then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\sorig$:
-
-	Let the rule presented in $\labIKp$ for disjunction right:
-
+	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
+
+\end{itemize}
+
+\subsection{Modal operators}
+
+We introduce the rules that represent the semantics of modal operators $\square$ and $\Diamond$. The system $\labIKp$ presents the next four rules (two for $\square$ and two for $\Diamond$): 
 \begin{center}
-		$\vlinf{\sorig}{}{\B, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\B, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
+	\begin{minipage}{.95\textwidth}
+		\begin{tabular}{@{\!}c@{\quad}c}
+			\\\\
+			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+			&
+			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
+			\\\\
+			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
+			&
+			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
+			\\
+		\end{tabular}
+	\end{minipage}
 \end{center}
 
-	From the conclusion to the premise we have: if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\square$ and $\Diamond$. The system $\labIKp$ presents the next four rules (two for $\square$ and two for $\Diamond$):
-
-\begin{center}
-	$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
-
-	$\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \Rightarrow \Right, x \colon \square A}{\B, \Left, x \le y, yRz \Rightarrow \Right, z \colon A}$
-
-	\vspace{5mm}
-
-	$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \Diamond A \Rightarrow \Right}{\B, \Left, xRy, y \colon A \Rightarrow \Right}$\hspace{10mm}
-	$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
-
-\end{center}
-
-A more detailed explanation is below:
+\bigskip
+
+A more detailed explanation for some rules is below:
 
 \begin{itemize}
-	\item Rule $\sbl$.
-
-	In order to capture $\square$ left, in our system the next rule is introduced:
-
-	\begin{center}
-		$\vlinf{\sbl}{}{\B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
-	\end{center}
-
-	Continue with the same reasoning, $\B$ is a set of relational and pre-order atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
+	\item Rule $\llabrn\BOX$.
+	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
 Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
 
-	\item Rule $\sdr$.
-
-	The rule presented in the system $\labIKp$ for the $\Diamond$ left is the following:
-
-	\begin{center}
-		$\vlinf{\sdr}{}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\B, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
-	\end{center}
-
-	Semantically, the diamond establish that in a model $\M$ and a world $v$ the formula $\Diamond A$ is valid, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the fomula $\Diamond A$ is satisfied in $x$, then the formula $A$ is true in $y$.
+	\item Rule $\rlabrn\DIA$.
+	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\Diamond A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
+In order to capture this definition, the rule shows that if $xRy$ and the formula $\Diamond A$ is satisfied in $x$, then the formula $A$ is true in $y$.
 
@@
 
+\bigskip
+
 \begin{center}
-	$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \IMP B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
-
-	\vspace{5mm}
-
-	$\vliinf{\sil}{}{\B, \Left, x \le y, x \colon A \IMP B \Rightarrow \Right}{\B, \Left, x \le y, x \colon A \IMP B \Rightarrow \Right, y \colon A}{\B, \Left, x \le y, x \colon A \IMP B, y \colon B \Rightarrow \Right}$
+	\begin{minipage}{.95\textwidth}
+		\begin{tabular}{@{\!}c@{\quad}c}
+			\multicolumn{2}{c}{
+				\hspace{9mm}
+				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+			}
+			\\
+			\multicolumn{2}{c}{
+				\hspace{10mm}
+				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+			}
+		\end{tabular}
+	\end{minipage}
 \end{center}
 
-The meaning of the rule for implication right is below:
+\bigskip
+
+The rule for implication right is explained below:
 
 \begin{itemize}
-	\item Rule $\sir$.
-
-	The system $\labIKp$ presents the following rule for implication right:
-
-	\begin{center}
-		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \Rightarrow \Right, x \colon A \IMP B}{\B, \Left, x \le y, y \colon A \Rightarrow \Right, y \colon B}$
-	\end{center}
-
-	Let $\B$ be a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
+	\item Rule $\rlabrn\IMP$.
+	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
 \end{itemize}
@@
 \section{A complete and sound system for intuitionistic modal logics}
-
-\todo{re-write a small introduction for this section}
-
-%
-We obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic in this formalism. 
+%
+Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
 %
@@
 %
-Furthermore, our system has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
+Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
 
@@
 %
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).
+As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$. The other cases are standard.
 
@@
 \todo{Fix the size of the next proof}
-
+\marianela{I will do it at the end when we have the format that we want to submit}
 \begin{proof}[Proof of \ref{ii} $\rightarrow$ \ref{iii}]
@@
 
-\begin{proof} [Proof for soundness]
-	We need to prove that each sequent rule of our system $\labIKp$ is sound. As the proof is similar for each of the rules, we prove the soundness of some particular rules:
+\begin{proof} [Proof of soundness]
+	We need to prove that each sequent rule of our system $\labIKp$ is sound.
+We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+As the proof is similar for each of the rules, we prove the soundness of some particular rules:
 
 	\begin{itemize}
-		\item Rule $\sbl$:
-
-		We want to prove that the rule for $\sbl$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
+		\item Rule $\llabrn\BOX$:
+
+		We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
 
 		\begin{center}
-			\emph{For all model $\M$, if $\M \Vdash \B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$, then $\M \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$.}
+			\emph{For all model $\M$, if $\M \Vdash \B,\Left, x \le y, yRz, \labels{x}{\BOX A}, z \colon A \Rightarrow \Right$, then $\M \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A} \Rightarrow \Right$.}
 		\end{center}
@@
 		By way of contradiction we want to see that if $\exists$ $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$,then $\M_{0} \not \Vdash premise$.
-More precisely for the $\sbl$ rule we want to show that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$ then $\M_{0} \not \Vdash \B,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.
-
-		Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash x\colon \square A$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular, from $\M_{0} \Vdash \square A$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0},z \Vdash A$.
-Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.
-
-		\item Rule
+More precisely for the $\llabrn\BOX$ rule we want to show that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, \break yRz, \labels{x}{\BOX A} \Rightarrow \Right$ then $\M_{0} \not \Vdash \B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
+
+		Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y,\break yRz, \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
+Therefore, in particular, from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0} \Vdash \labels{z}{A}$.
+Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
+Then, the rule $\llabrn\BOX$ is sound.
+
+		\item Rule $\rlabrn\BOX$: By way of contradiction.
+Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$, i.e.
+$\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{\BOX A}$, which is the same as $\M_{0} \Vdash \vlan (\B,\Left)$ and  $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$.
+From $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$, we have that $\M_{0} \not \Vdash \Right$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}$.
+Following the semantic definition of $\BOX$, there exists worlds $y, z$ in $\M_{0}$, such that $x \le y, yRz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
+Therefore, $\M_{0} \not \Vdash premise$, i.e.
+$\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
+Then, the rule $\rlabrn\BOX is sound$.
+
+		\item Rule $\rlabrn\IMP$: By way of contradiction.
+Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{A \IMP B}$, i.e., in particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
+Therefore, there exists $y$ such that $x \le y$ and $\M_{0} \Vdash \labels{y}{A}$ but $\M_{0} \not \Vdash \labels{y}{B}$.
+Then, we have $\M_{0} \not \Vdash \B, x \le y, \Left, \labels{y}{A} \Rightarrow \labels{y}{B}$.
+Finally, the rule $\rlabrn\IMP$ is sound.
 	\end{itemize}
+	The other cases are similar.
 \end{proof}
-
-\todo{Missing: Proof of iii $\rightarrow$ iv and Proof of iv $\rightarrow$ i}
-
-\marianela{Yes! Soundness section: explain a box rule and an implication rule. Say that the scheme of the rest of the rules are similar}
-
-\todo{How to introduce the next lemmas? Add small explanation}
 
@@
 \end{lemma}
+
+\begin{proof}
+	Standard.
+\end{proof}
 
@@
 \end{lemma}
+
+\begin{proof}
+In each case, we reason by induction on the height of $\DD$.
+
+\begin{itemize}
+\item $\llabrn\IMP$:
+For a proof of height $1$, it is straightforward.
+%
+For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
+%
+then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
+
+For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
+
+First let us fix a given index $y$ that does not appear in $\DD$.
+
+If we start with a proof
+\begin{smallequation*}
+	\DD = 
+	\vlderivation{
+		\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+			\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
+		}	
+	}
+\end{smallequation*}
+
+Then by induction hypothesis there exists a proof 
+\begin{smallequation*}
+	\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
+\end{smallequation*}
+of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
+
+Therefore, we have the proof
+\begin{smallequation*}
+	\DD^{\invr{\llabrn\IMP}} = 
+	\vlderivation{
+		\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
+			\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
+		}
+	}
+\end{smallequation*}
+of the same (or smaller) height as $\DD$.
+
+If we start with a proof 
+\begin{smallequation*}
+	\vlderivation{
+		\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+			\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
+		}{
+		\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
+	}
+	}
+\end{smallequation*}
+then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
+
+%
+\item $\llabrn\DIA$:
+
+If we start with a proof
+\begin{smallequation*}
+	\DD = 
+	\vlderivation{
+		\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+			\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
+		}	
+	}
+\end{smallequation*}
+
+Then by induction hypothesis there exists a proof 
+\begin{smallequation*}
+	\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
+\end{smallequation*}
+of the same (or smaller) height as $\DD'$.
+
+Therefore, we have the proof
+\begin{smallequation*}
+	\DD^{\invr{\llabrn\DIA}} = 
+	\vlderivation{
+		\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
+			\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
+		}
+	}
+\end{smallequation*}
+of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
+
+If we start with a proof 
+\begin{smallequation*}
+	\vlderivation{
+		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+			\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
+		}	
+	}
+\end{smallequation*}
+then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
+
+\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
+\end{itemize}
+\end{proof}
 
@@
 
-See this axiom in the Figure~\ref{fig:gklmn} \todo{Wrong label}
+See this axiom in the Figure~\ref{fig:gklmn} \todo{Wrong label. why??}
 

### 2019-08-31 caleidoscope/caleidoscope.tex
working on extensions section

@@
 %
-These systems enjoy cut-elimination via usual arguments. Proofs of the the axioms we mentioned are below:
+These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
 
@@
 
-The generality of the result adds a new rule to the system $\labIKp$ in order to capture the \emph{Scott-Lemmon axiom} or \emph{$\agklmn$ axiom}: 
-\begin{center}
-	$\lozenge^{k} \square^{l} A \IMP \square^{m}\lozenge^{n} A$
-\end{center}
+\bigskip
+
+Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
+why??}
+
 Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
@@
 $\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-See this axiom in the Figure~\ref{fig:gklmn} \todo{Wrong label. why??}
 
@@
 \end{figure}
+
+Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
+
+\bigskip
+
+\begin{center}
+	$\vlderivation { \vlin {\gklmn}{y', u$ fresh$}{\B, xR^{k}y, xR^{m}z, \Left \Rightarrow \Right}{\vlhy {\B, y \le y', xR^{k}y, xR^{m}z, y'R^{l}u, zR^{n}u, \Left\Rightarrow \Right}}}$
+\end{center}
+
+\bigskip
+
+We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
+
+\begin{theorem}
+	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
+\end{theorem}
+
+\begin{proof}
+	\begin{center}
+		\scalebox{0.93}{
+			$\vlderivation {\vlin {\sir}
+				{y$ fresh$}
+				{\Rightarrow x \colon \lozenge \square A \vljm \square \lozenge A}
+				{\vlin {\sbr}
+					{z, w $ fresh $}
+					{x \le y, y \colon \lozenge \square A \Rightarrow y \colon \square \lozenge A}
+					{\vlin {\sdl}
+						{u$ fresh$}
+						{x \le y, y \le z, zRw, y \colon \lozenge \square A \Rightarrow w \colon \lozenge A}
+						{\vlin {\ftwo}
+							{t$ fresh$}
+							{x \le y, y \le z, zRw, yRu, u \colon \square A \Rightarrow w \colon \lozenge A}
+							{\vlin {\gklmn}
+								{t', j$ fresh$}
+								{x \le y, y \le z, u \le t, zRw, yRu, zRt, u \colon \square A \Rightarrow w \colon \lozenge A}
+								{\vlin {\sdr}
+									{}
+									{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A}
+									{\vlin {\trans}
+										{}
+										{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
+										{\vlin {\sbl}
+											{}
+											{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
+											{\vlin {\refl}
+												{}
+												{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
+												{\vlin {\ids}
+													{}
+													{x \le y, y \le z, u \le t, t \le t', u \le t',j \le j, zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
+													{\vlhy {}}}}}}}}}}}}$}
+	\end{center}
+\end{proof}
+
+In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
+
+\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
+	\begin{enumerate}
+		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A, z \colon A \Rightarrow \Right}}}$}
+		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, x \colon \square^{k} A}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, y \colon A}}}$}
+		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, x \colon \lozenge^{k} A \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, y \colon A \Rightarrow \Right}}}$ }
+		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A, y \colon A}}}$}
+	\end{enumerate}
+	%\textbf{Probably F2g???}
+\end{lemma}
+
+Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
 

### 2019-08-31 caleidoscope/caleidoscope.tex
extensions section

@@
 
-\todo{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
-
-\todo{Scott-Lemmon with the new rules (general rules for F2, F1, etc) for the system and the lemma that shows that each rule is admissible}
+\marianela{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
 

### 2019-09-01 caleidoscope/caleidoscope.tex
modif on extensions section

@@
 \section{Extensions}
-
-\marianela{After Skype with Sonia: important section; add the generality of the rules for Scott-Lemmon; Simpson will be introduce in the introduction or/and in the conclusion. }
-
-\marianela{The idea of this section is to show the things that our system could do (extensions of the logic) and Simpson could not.}
 

### 2019-09-03 caleidoscope/caleidoscope.tex
added some material

@@
 \usepackage{bm}
-\usepackage{color}
+\usepackage{xcolor}
 \usepackage{pgf}
@@
 %%% Comments  
+\definecolor{notgreen}{rgb}{.1,.6,.1}
 \newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
 \newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{green}[Lutz: #1]}}
+\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
 \newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
@@
 
- \marianela{I think that now I have the same as Lutz, right?}
- \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
+% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
+ \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
    \author{Lutz Stra{\ss}burger}
@@
 \todo{Simpson does not have internal cut-elimination}
+
+\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
+  \begin{itemize}
+  \item what we do:
+    \begin{itemize}
+    \item first systems (nested and labelled) for intuitionistic modal
+      logic where ``single conclusion'', i.e., only one formula on the
+      right.
+    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
+    \item Still rules that forced single formula on the right (white implication and white box)
+    \item by allowing both relations of the model in the proof system
+      we go to genuinely multiple conclusion: never ever a formula on
+      the right has to be deleted during proof search.
+    \end{itemize}
+  \item why we do it: 
+    \begin{itemize}
+    \item getting things right: labelled systems for classical modal
+      logics, or plain propositional intuiionistic logic have one
+      binary relation, which is exactly the relation of the standard
+      Kripke semantics. The standard Kripke semantics for
+      intuitionistic modal logic is birelational, with a strong
+      connectiion between the two binary relations. A clean labelled
+      system for these logics should incorporate both relations.
+    \item We get new logics.  In the standard nested sequent
+      or labelled sequent system for intuitionistic modal logic we
+      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
+      but here we can have them separtely.
+    \end{itemize}
+  \item how we do it:
+    \begin{itemize}
+    \item We start from the Maehara nested sequent system (which can
+      be translated straightforwardly into a labelled system with one
+      relation $R$.
+    \item the rules for $\AND$ and $\OR$ are trivial and as expected
+      they can be presented such that they are invertible on the left
+      and the right, they do not concern the relations $R$ and $\le$. 
+    \item So should be the rules for $\IMP$-left and $\BOX$-left and
+      identity, but there is a subtlety; see below...
+    \item the rules for $\DIA$ are also straightforward, as they
+      concern only $R$ but not $\le$.
+    \item The rules $\BOX$-right and $\IMP$-right are the ones that
+      force single conclusion in the Maehara system. This means that
+      here they create a future, using the relation $\le$.
+    \item In order to make everything work together, this forces us to
+      have reflexivity and transitivity of $\le$, explicely as rules
+      in the system, and have rules for the F1 and F2 conditions
+      making the relations $R$ and $\le$ go together.
+    \item As a consequence we also need a rule realizing monotonicity
+      for the formulas on the right.
+    \item However, we designed the system such that monotonicity is
+      admisible by encorporating it into the rules for identity,
+      $\IMP$-left and $\BOX$-left.
+    \end{itemize}
+  \end{itemize}
+}
 %

### 2019-09-06 caleidoscope/caleidoscope.tex
small modif

@@
 
-We introduce the rules that represent the semantics of modal operators $\square$ and $\Diamond$. The system $\labIKp$ presents the next four rules (two for $\square$ and two for $\Diamond$): 
+We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
 \begin{center}
@@
 	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\square A$ is true in $x$, then the formula $A$ is true in $z$.
+Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
 
 	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\Diamond A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\Diamond A$ is satisfied in $x$, then the formula $A$ is true in $y$.
+	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
+In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
 
@@
 				{y$ fresh$}
-				{\Rightarrow x \colon \lozenge \square A \vljm \square \lozenge A}
+				{\Rightarrow \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
 				{\vlin {\sbr}
 					{z, w $ fresh $}
-					{x \le y, y \colon \lozenge \square A \Rightarrow y \colon \square \lozenge A}
+					{x \le y, \labels{y}{\DIA \BOX A} \Rightarrow \labels{y}{\BOX \DIA A}}
 					{\vlin {\sdl}
 						{u$ fresh$}
-						{x \le y, y \le z, zRw, y \colon \lozenge \square A \Rightarrow w \colon \lozenge A}
+						{x \le y, y \le z, zRw, \labels{y}{\DIA \BOX A} \Rightarrow \labels{w}{\DIA A}}
 						{\vlin {\ftwo}
 							{t$ fresh$}
-							{x \le y, y \le z, zRw, yRu, u \colon \square A \Rightarrow w \colon \lozenge A}
+							{x \le y, y \le z, zRw, yRu, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}}
 							{\vlin {\gklmn}
 								{t', j$ fresh$}
-								{x \le y, y \le z, u \le t, zRw, yRu, zRt, u \colon \square A \Rightarrow w \colon \lozenge A}
+								{x \le y, y \le z, u \le t, zRw, yRu, zRt, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}}
 								{\vlin {\sdr}
 									{}
-									{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A}
+									{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}}
 									{\vlin {\trans}
 										{}
-										{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
+										{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
 										{\vlin {\sbl}
 											{}
-											{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
+											{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
 											{\vlin {\refl}
 												{}
-												{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
+												{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A}, \labels{j}{A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
 												{\vlin {\ids}
 													{}
-													{x \le y, y \le z, u \le t, t \le t', u \le t',j \le j, zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
+													{x \le y, y \le z, u \le t, t \le t', u \le t',j \le j, zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A}, \labels{j}{A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
 													{\vlhy {}}}}}}}}}}}}$}
@@
 	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A, z \colon A \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, x \colon \square^{k} A}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, y \colon A}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, x \colon \lozenge^{k} A \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, y \colon A \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A, y \colon A}}}$}
+		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
+		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
+		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
+		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
 	\end{enumerate}

### 2019-09-07 caleidoscope/caleidoscope.tex
starting the intro

--- 2019-09-03 caleidoscope/caleidoscope.tex
@@
-\documentclass[twoside]{aiml18}
-
-\usepackage{aiml18macro}
-
+\documentclass[a4paper]{article}
+
+%\usepackage{aiml18macro}
+
+\usepackage[margin=3cm]{geometry}
 \usepackage[noxy]{virginialake}                        
@@
 \input{macros}
-\newcommand{\B}{\mathcal{B}}
+%\newcommand{\B}{\Digamma}
+\newcommand{\B}{\mathcal{R}}
+%\newcommand{\B}{\Xi}
+%\newcommand{\B}{\mathcal{B}}
 \newcommand*{\A}{\mathcal{A}}
@@
 \newcommand*{\IK}{\mathsf{IK}}
+\newcommand*{\K}{\mathsf{K}}
 \newcommand*{\labIKp}{\lab\IK_{\le}}
-
+\newcommand*{\ISfour}{\mathsf{IS4}}
+\newcommand*{\Sfour}{\mathsf{S4}}
+
+\newcommand{\fourax}{\mathsf{4}}
 %%% Connectives
@@
 %%% Labelled sequents
-\newcommand*{\labels}[2]{{\color{blue}{#1}\:\colon}{#2}}
-\newcommand{\SEQ}{\Rightarrow}
+\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
+\newcommand*{\lb}[1]{{\color{blue}{#1}}}
+\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
+\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
+\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
+\newcommand{\SEQ}{\Longrightarrow}
 \newcommand*{\DD}{\mathcal{D}}
@@
 
+\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
 %%% Labelled rules
@@
 
+%%%%%%%%%%%%%%%%%
+
+\newcommand{\qquand}{\qquad\mbox{and}\qquad}
+\newcommand{\quadcm}{\rlap{\quad,}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{frontmatter}
-  \title{Decomposing labelled proof theory for intuitionistic modal logic}
-  \author{Sonia Marin}
-
-  \todo{New university?}
-  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
- \author{Marianela Morales}
-
+%\begin{frontmatter}
+  \title{A properly labelled proof system for intuitionistic modal logics}
+  \author{Sonia Marin \and %}
+%  \todo{New university?}
+%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
+%    \author{
+      Marianela Morales %}
+ \and
 % \marianela{I think that now I have the same as Lutz, right?} No, the other order...
- \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
-   \author{Lutz Stra{\ss}burger}
- \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
+% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
+%      \author{
+        Lutz Stra{\ss}burger }
+% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
+
+  \maketitle
 
@@
 
-   We present a labelled sequent system for intuitionistic modal logic equipped 
-   with two relation symbols, one for the accessibility
+   In this paper we present a labelled sequent system for
+   intuitionistic modal logics such that there is not only one, but
+   two relation symbols for the labels: one for the accessibility
    relation associated with the Kripke semantics for modal logics and
@@
    for intuitionistic logic.
-   %
-   Thus, it is in close correspondence with birelational Kripke semantics for intuitionistic modal logic and can encompass a wider range of intuitionistic logics than state-of-the-art labelled systems.
+   %%
+   This puts our system in close correspondence with the standard
+   birelational Kripke semantics for intuitionistic modal logic. As a
+   consequence it can encompass a wider range of intuitionistic modal
+   logics than standard labelled systems.
+   %%
+   We also show an internal cut elimination proof for our system.
 
@@
   \begin{keyword}
-  Intuitionistic modal logic, Labelled sequents, Proof theory.
+  Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
   \end{keyword}
- \end{frontmatter}
-
-\section{Introduction}
+% \end{frontmatter}
+
+  %\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\todo{get bib-file right}
+
+\section{Introduction}\label{sec:intro}
+
+Since their introduction in the 1980s by Gabbay~\cite{Gabbay},
+\emph{labelled proof calculi} have been widely used by proof theorist
+to give sound, complete and cut-free deductive system to a broad range
+of logics. Unlike so-called \emph{internal calculi}, like
+hyper-sequents~\cite{avron} or nested
+sequents~\cite{kashima,brunnler,pog} or 2-sequents~\cite{masini},
+labelled calculi have the advantage of beeing more uniform and
+accommodating more logics.
+
+Standard labelled sequent calculi attach to every formula $A$ a label
+$x$, witten as $\labels xA$, and additionally admit so called
+\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
+binary relation symbol. These calculi work best for logics with
+standard Kripke semantics, as in this case the relation $\rel$ is used
+to encode the accessibility relation in the Kripke models, and the
+frame condition corresponding to the desired logic can be directly
+encoded as inference rules. Prominent examples are classical modal
+logics and intuitionistic propositional logic, where, e.g., the frame
+condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
+inference rule
+\begin{equation}
+  \label{eq:Rtrans}
+  \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+    \B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
+\end{equation}
+where $\B$ stands for a set of relation atoms, and $\Gamma$ and
+$\Delta$ for sets \lutz{or multisets?} of labelled formulas.
+
+However,
+in this paper we are concerned with \emph{intuitionistic modal
+  logics}, whose Kripke semantics is based on \emph{birelational}
+frames, i.e., they have two binary relations instead of one: one
+relation $R$ that corresponds to the accessibility relation in
+ordinary Kripke frames for modal logics, and a relation $\le$ that
+corresponds to the future relation in ordinary Kripke frames for
+intuitionistic logic. Consequently, standard labelled systems for
+these logics have certain shortcomings:
+\begin{enumerate}
+\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
+  versions of the $\fourax$-axiom
+  \begin{equation}
+    \label{eq:4ax}
+    \fm{\BOX A\IMP \BOX\BOX A}
+    \qquand
+    \fm{\DIA\DIA A\IMP\DIA A}
+    \quadcm
+  \end{equation}
+  as they are equivalent in classical
+  modal logic. However, in intuiotionistic modal logic they are not
+  equivalent, and even though the logic $\ISfour$, i.e., the
+  intuitionistic version of the modal logic $\Sfour$, contains both
+  axioms, they can be added independently to the logic $\IK$ (the
+  intuitionistic version of $\K$). However, the proof theory of these
+  new logics has not been studied before, as no existing labelled (or
+  label-free) proof system can handle them, even though the
+  corresponding frame conditions
+  \begin{equation}
+    \label{eq:4frame}
+    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
+    \qquand
+    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
+  \end{equation}
+  have already been studied
+  in~\cite{Plotkin}.\lutz{check: did they get that wrong in  \cite{Plotkin}?}
+\item The correspondence between the syntax and the semantics is not
+  as clean as one would expect. As only the $R$-relation (and not the
+  $\le$-relation) of the frame is visible in an ordinary labelled
+  sequent, we only have that a sequent $\Gamma$ is provable if and
+  only if is is valid in all \emph{graph-consistent}\footnote{This
+    means that every layer in the model can be lifted to any future of
+    any world in that layer.}\lutz{check terminology} models, as
+  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
+  and considered as a very unsatisfactory situation\lutz{check what he
+    said exactly} (see also \cite{mar:str:indexed}).
+\end{enumerate}
+In order to address these two issues we propose here to extend the
+notion of labelled sequent by also allowing relational atoms of the
+form $\futs xy$. Consequently, we can easily translate the frame
+conditions in~\eqref{eq:4frame} into inference rules:
+\begin{equation}
+  \label{eq:4rules}
+  \vlinf{\rn{4^\BOX}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+    \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
+  \qquand
+  \vlinf{\rn{4^\DIA}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+    \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
+\end{equation}
+
+\section{Introduction(old version, to be deleted)}
 \todo{We should work on the introduction}
@@
 \todo{Simpson does not have internal cut-elimination}
+
+\sonia{
+  \begin{itemize}
+  \item internal vs externl calculi
+  \item extesion to axioms are truly intuitionistic (not just the
+    classical versions as in Simpson style)
+  \item connection with semantics compared to graph homomorphism
+    restiction in Simpson and ``indexed nested systems''
+  \end{itemize}
+}
 

### 2019-09-07 caleidoscope/caleidoscope.tex
it compiles

@@
 
-\usepackage[margin=3cm]{geometry}
+\usepackage[margin=2cm]{geometry}
 \usepackage[noxy]{virginialake}                        
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath} 
+\usepackage{amssymb,amsmath,amsthm} 
 \usepackage{mathtools}
@@
 \usepackage{pgffor}
+
+	%%
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{conjecture}[theorem]{Conjecture}
+\newtheorem{fact}[theorem]{Fact}
+\newtheorem{claim}[theorem]{Claim}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lem}[theorem]{Lemma}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+	%%
+\theoremstyle{definition}
+\newtheorem{observation}[theorem]{Observation}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{problem}[theorem]{Problem}
+\newtheorem{construction}[theorem]{Construction}
+\newtheorem{remark}[theorem]{Remark}
+	%%
 
@@
 
-  \begin{keyword}
-  Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  \end{keyword}
+  %% \begin{keyword}
+  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
+  %% \end{keyword}
 % \end{frontmatter}
@@
   \label{eq:4rules}
-  \vlinf{\rn{4^\BOX}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+  \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
      \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
   \qquand
-  \vlinf{\rn{4^\DIA}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+  \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
     \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  

### 2019-09-07 caleidoscope/caleidoscope.tex
done with first draft of intro

@@
 \end{equation}
-
-\section{Introduction(old version, to be deleted)}
+This allows us to define cut-free deductive systems for a wide range
+of logics that could not be treated before.  Furthermore, the relation
+between syntax and semantics is as one would expect: A sequent is
+provable in our system if and only if it is valid in all models.
+
+Besides that, there is another pleasant observation to make about our
+system. Ordinary labelled sequent systems for intuitionistic modal
+logic are single-conclusion~\cite{simpson:phd}. The same is true for
+the corresponding nested sequent
+systems~\cite{str:fossacs13,mar:str:aiml}. It is possible to express
+Maehara style multiple-conclusion systems in nested
+sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
+labelled sequents. However, also in these systems there are rules
+($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
+premise, even though this is not the case in labelled
+systems~\cite{negri:xx} or nested sequents~\cite{fitting:xx} for
+intuitionistic logic. Our system eliminates this
+discrepancy. Consequently, every rule in our system is invertible, as
+we never delete information.\lutz{check, is this really the case?}
+
+\medskip
+
+This paper is organized as follows, In the next section we recall the standard syntax and semantics of intuitionistic modal logics.
+Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
+In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
+The cut elimination theorem, proved in Section~\ref{sec:cutelim}, then entails soundness and completeness for the cut-free system.
+Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
+\lutz{what about doing that directly in the system presentation, like Negri does it?}
+
+\section*{Introduction(old version, to be deleted)}
 \todo{We should work on the introduction}

### 2019-09-09 caleidoscope/caleidoscope.tex
started section 3

@@
 \newcommand*{\A}{\mathcal{A}}
+
+\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
 
@@
   have already been studied
-  in~\cite{Plotkin}.\lutz{check: did they get that wrong in  \cite{Plotkin}?}
+  in~\cite{Plotkin}.\todo{check: did they get that wrong in  \cite{Plotkin}?}
 \item The correspondence between the syntax and the semantics is not
@@
     means that every layer in the model can be lifted to any future of
-    any world in that layer.}\lutz{check terminology} models, as
+    any world in that layer.}\todo{check terminology in Simpson} models, as
   already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as a very unsatisfactory situation\lutz{check what he
+  and considered as a very unsatisfactory situation\todo{check what he
     said exactly} (see also \cite{mar:str:indexed}).
@@
 
-This paper is organized as follows, In the next section we recall the standard syntax and semantics of intuitionistic modal logics.
+This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
 Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
@@
 \lutz{what about doing that directly in the system presentation, like Negri does it?}
+
+\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{Maffezioli}.}
 
@@
 
-\section{Intuitionistic modal logics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Intuitionistic modal logics}\label{sec:intmod}
 
@@
 	%
-	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.
+        \lutz{why do we have $\TOP$?}
+	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
 
@@
 \begin{itemize}
-\item the \emph{necessitation rule}: $\BOX A$ is a theorem if $A$ is a theorem; and
+\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
 \item the following five variants of the \emph{distributivity axiom}:
@@
 Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-
+\begin{equation}
+  \label{eq:kripke}
+  \parbox{30em}{%
   $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
@@
 %We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-
-We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \SEQ \bot$).
-
-From the monotonicity of the valuation function $V$ , we get a monotonicity property for the relation:
+}
+\end{equation}
+\todo{fix typography}
+
+We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
+
+From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
 \begin{proposition}(Monotonicity) 
@@
 
-\todo{Add something else about Fischer-Servi theorem?}
+\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{The system}\label{sec:system}
+
+In this section we present our properly labelled sequent proof system
+for intuitionistic modal logics. The starting point is the notion of a
+\emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
+x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
+at world $\lb x$. A \emph{relation atom} is either an expression
+$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
+intended meaning is that the corresponing relation holds between the
+worlds $\lb x$ and $\lb y$. This is enough to define the notion of
+\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
+where $\B$ is a set of relation atoms, and $\Left$ and $\Right$ are
+sets of labelled formulas, all written as list, separated by commas.
+
+Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
+We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
+Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{kuz:str:maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$ \todo{$\TOP$ yes/no}, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
+However, this translation also yields the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
+\begin{equation}
+  \label{eq:nomon}
+  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
+  \quad
+  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A} \IMP B \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
+  \quad
+  \vlinf{\llabrn\BOX}{}{\B, xRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, xRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
+\end{equation}
+that are not sufficient for a complete system, and we will see below why.
+Before, let us first look at the rules $\rlabrn\IMP$ and $\rlabrn\BOX$.
+In the  multiple-conlusion nested sequent system of~\cite{kuz:str:maehara}, these are the two rules that force single-conclusion.
+This is the reason why in our system we need the $\le$ in the relational atoms; we need to go to the future of the current world.
+In the Kripke-semantics in~\eqref{eq:kripke} the two connectives $\IMP$ and $\BOX$ are the ones that need the future-relation $\le$.
+This relation is reflexive and transitive.
+In order to capture that in the proof system, we need to add the rules $\rn{refl}$ and $\rn{trans}$.
+Finally, in the semantics, the two relations $\rel$ and $\le$ are strongly connected through the two conditions $F_1$ and $F_2$ \todo{proper typography}.
+These need to be reflected in the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
+
+\todo{monotonicity}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{figure}%[h]
-	\centering
-	\small
+\begin{figure}[!t]
+  \begin{center}
 	\fbox{
-	\begin{minipage}{.95\textwidth}
-	\begin{tabular}{@{\!}c@{\quad}c}
+%	\begin{minipage}{.95\textwidth}
+	\begin{tabular}{c@{\quad}c}
 		$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
@@
 	\end{tabular}		
-\end{minipage}
-}		
+%\end{minipage}
+}		
+  \end{center}
   \caption{System $\labIKp$}
@@
 		%
+
+                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
 		\item\label{iii} $A$ is provable in $\labIKp$
@@
 
-\begin{smallequation*}\hspace*{-10em}
+\begin{smallequation*}\hspace*{-2em}
 	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
@@
 
-\begin{smallequation*}\hspace*{-7em}
+\begin{smallequation*}\hspace*{-2em}
 	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
@@
 
-\begin{smallequation*}\hspace*{-10em}
+\begin{smallequation*}\hspace*{-2em}
 	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
@@
 \begin{smallequation*}
-	\hspace*{-7em}
+	\hspace*{-2em}
 	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
@@
 		\end{center}
+		\lutz{we need to define what that means $\M\Vdash$sequent}
 
@@
 Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
-Then, the rule $\llabrn\BOX$ is sound.
+Then, the rule $\llabrn\BOX$ is sound.\lutz{that is unclear}
 
@@
 $\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
-Then, the rule $\rlabrn\BOX is sound$.
+Then, the rule $\rlabrn\BOX$ is sound.
 
@@
 	\end{itemize}
+        \lutz{the arguments are not clear}
+
 	The other cases are similar.

### 2019-09-10 caleidoscope/caleidoscope.tex
done section 3

@@
 
-Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
-We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{kuz:str:maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$ \todo{$\TOP$ yes/no}, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this translation also yields the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
-\begin{equation}
-  \label{eq:nomon}
-  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
-  \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A} \IMP B \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
-  \quad
-  \vlinf{\llabrn\BOX}{}{\B, xRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, xRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
-\end{equation}
-that are not sufficient for a complete system, and we will see below why.
-Before, let us first look at the rules $\rlabrn\IMP$ and $\rlabrn\BOX$.
-In the  multiple-conlusion nested sequent system of~\cite{kuz:str:maehara}, these are the two rules that force single-conclusion.
-This is the reason why in our system we need the $\le$ in the relational atoms; we need to go to the future of the current world.
-In the Kripke-semantics in~\eqref{eq:kripke} the two connectives $\IMP$ and $\BOX$ are the ones that need the future-relation $\le$.
-This relation is reflexive and transitive.
-In order to capture that in the proof system, we need to add the rules $\rn{refl}$ and $\rn{trans}$.
-Finally, in the semantics, the two relations $\rel$ and $\le$ are strongly connected through the two conditions $F_1$ and $F_2$ \todo{proper typography}.
-These need to be reflected in the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
-
-\todo{monotonicity}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
 \begin{figure}[!t]
@@
 \end{figure}
+
+Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
+We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
+Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{kuz:str:maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$ \todo{$\TOP$ yes/no}, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
+However, this translation also yields the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
+\begin{equation}
+  \label{eq:nomon}
+  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
+  \quad
+  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A} \IMP B \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
+  \quad
+  \vlinf{\llabrn\BOX}{}{\B, xRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, xRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
+\end{equation}
+that are not sufficient for a complete system, and we will see below
+why. Before, let us first look at the rules $\rlabrn\IMP$ and
+$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
+of~\cite{kuz:str:maehara}, these are the two rules that force
+single-conclusion. This is the reason why in our system we need the
+$\le$ in the relational atoms; we need to go to the future of the
+current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
+connectives $\IMP$ and $\BOX$ are the ones that need the
+future-relation $\le$. This relation is reflexive and transitive. In
+order to capture that in the proof system, we need to add the rules
+$\rn{refl}$ and $\rn{trans}$.
+
+Finally, in the semantics, the two relations $\rel$ and $\le$ are
+strongly connected through the two conditions $F_1$ and $F_2$
+\todo{proper typography}. These need to be reflected in the proof
+system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
+%
+However, these two rule create new labels, and in order to be
+complete, the system needs the \emph{monotonicity} rule:
+\begin{equation}
+  \label{eq:mono}
+  \vlinf{\rn{mon}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}\Right}{
+    \lseq{\B, x \le x'}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
+\end{equation}
+Since this rule is a form of contraction, it would cause the same
+problems as contraction in a cut elimination proof. Hence, it is
+preferable to have a system in which this rule is admissible. This is
+the reason why we have monotonicity incorporated in the rules
+$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
+instead of using the rules in~\eqref{eq:nomon}.
+
+\begin{theorem}
+  \label{thm:mon-adm}
+  The rule $\rn{mon}$ is admissible for system $\labIKp$.
+\end{theorem}
+
+For proving this theorem, we need a series of auxiliary lemmas.
+
+\todo{}
+
+\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
+  \todo{}
+\end{proof}
+
+In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
+\begin{equation}
+  \label{eq:cut}
+  \vliiinf{\labrn{cut}}{}{
+    \lseq\B\Left\Right}{
+    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
+    \lseq\B{\Left,\labels{z}{C}}{\Right}}
+\end{equation}
+Then we can summarize soundness and completeness, and cut
+admissibility of $\labIKp$ in the following Theorem:
+
+\begin{theorem}\label{thm:cutfree-compl}
+	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
+	%
+	For any formula $A$, the following are equivalent.
+	%
+	\begin{enumerate}
+		\item\label{i} $A$ is a theorem of $\IK$. 
+		%
+		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
+		\item\label{iii} $A$ is provable in $\labIKp$.
+		%
+		\item\label{iv} $A$ is valid in every birelational frame. %satisfying the properties in $\CC$.
+	\end{enumerate}
+\end{theorem}
+
+The proof of this theorem is the topic of the following sections. The
+equivalence of \ref{i} and \ref{iv} has already been stated in
+Theorem~\ref{thm:plotkin}~\cite{Fischer,Plotkin}. The implication
+\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
+the implication~\ref{ii}$\implies$\ref{iii} is shown in
+Section~\ref{sec:cut-elim}, and finally, the implication
+\ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Soundness}\label{sec:soundness}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Completness}\label{sec:completeness}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Cut Admissibility}\label{sec:cut-elim}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Labelled sequent calculi with $\rel$ and $\le$}
 

### 2019-09-10 caleidoscope/caleidoscope.tex
adding some material to section 2

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\section{Preliminaries}
-%\marianela{Depends on how long the paper has to be, we can add a section with preliminaries: labelled sequents for classical modal logic and syntax and semantics of classical modal logic}
-
-%\todo{re-build this section since the section \emph{intuitionistic modal logics} is part of the preliminaries}
-
-%\sonia{We should not have the definitions of classical modal logic.
-Just the intuitionistic part.
-If we want to say something else about labelled sequents, we should add it before the definition of \emph{a two-sided labelled sequent}}
-
-%Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $xRy$, where $x$, $y$ range over a set of variables and $A$ is a modal formula.
-A one-sided labelled sequent is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational atoms and $\Right$ a multiset of labelled formulas.
-A simple proof system for classical modal logic K can be obtained in this formalism (\ref{fig:systemlabK}).
-
-%%\begin{figure}[h]
-%\begin{center}
-
-%$\vlderivation {\vlinf{\id}{}{\B \SEQ \Right, x: a, x: \vls-a}{}}$
-%\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$
-
-%$\vliinf{\vlab}{}{\B \SEQ \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
-%\hspace{7mm}$\vlinf{\olab}{}{\B \SEQ \Right, x \colon \vls[A.B]}{\olabr}$
-
-%$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
-%\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
-
-%\end{center}
-%\caption{System $\mathsf{labK}$}
-%\label{fig:systemlabK}
-%\end{figure}
-
-%These rule schemes can occur in different contexts and different calculi.
-The context that interests us is when it is applied to modal logic.
-The idea to extend this system to another to capture intuitionistic modal logics allows us to study the Kripke semantics for this type of logics:
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%
+%
 \section{Intuitionistic modal logics}\label{sec:intmod}
-
 The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
@@
 \lutz{why do we have $\TOP$?}
-	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
 
@@
 %%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
-%
-
-The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
-%
-It is obtained from intuitionistic propositional logic by adding:
+Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
+Five axioms have been considered as primitives in the literature.
+An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
+%
+
+%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
+It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
 \begin{itemize}
@@
 
-The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
+The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
+The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system $\break \rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$.
+However this would give strictly no information on the behaviour of the $\DIA$ modality.
+It seems that Fitch \cite{Fitch} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
+Wijekesera \cite{Wijekesera:1990} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
+The systems are well-designed for some applications for example to analyse some type systems \cite{Benton:1998} or to reason about states of a machine under partial information \cite{WijesekeraNerode:2005}.
+However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
+
+The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi \cite{Fischer} and by Ewald \cite{Ewald} in the case of intuitionistic tense logic.
+It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
+
+The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
 %
@@
 \begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
+	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
 	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
@@
 	\begin{enumerate}
-		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
+		\item[($\rn{F_1}$)] For $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
 
@@
 		\xymatrix{
-				u' \ar@{.>}[r]_R  & v' \\
-				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
+			u' \ar@{.>}[r]^R  & v' \\
+			u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & v \ar@{->}[u]_{\le}
 		}
@@
 
-		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
+		\item[($\rn{F_2}$)] For $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
 
@@
 	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-	if $w \le w'$ then $V(w)\subseteq V(w')$.
+	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
+	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
 \end{definition}
@@
 
-$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
-
-$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
-
-$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
+	$w \Vdash A \IMP B$ iff for all $\lb{w'}$ with $\futs w{w'}$, if $w' \Vdash A$ then $w' \Vdash B$
+
+	$w \Vdash \BOX A$ iff for all $\lb{w'}$ and $\lb u$ with $\futs w{w'}$ and $\accs {w'}u$, $u \Vdash A$ \hfill %$(\ast)$
+
+	$w \Vdash \DIA A$ iff there exists a $u$ such that $\accs wu$ and $u \Vdash A$.
 
@@
 \begin{proposition}(Monotonicity) 
-For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
+	For any formula $A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $w \Vdash A$, then $w' \Vdash A$.
 \end{proposition}
@@
 \begin{definition}
-	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-%
-	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
+	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
+	%
+	A formula $A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}
@@
 \todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\marianela{maybe adding the following: ?}
+%Now, we would like to consider special restrictions on these bi-relational frames.
+For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
+%\section{Intuitionistic modal logics}\label{sec:intmod}
+%
+%	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
+%	%
+%	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
+%	%
+%	$$
+%	A \coloncolonequals
+%	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
+%	$$
+%	%
+%        \lutz{why do we have $\TOP$?}
+%	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
+%
+%Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
+%%%
+%Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
+%%
+%
+%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
+%%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
+%%
+%It is obtained from intuitionistic propositional logic by adding:
+%\begin{itemize}
+%\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
+%\item the following five variants of the \emph{distributivity axiom}:
+%\begin{equation*}
+%\label{eq:ik}%\hskip-2em
+%\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
+%\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
+%&
+%\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
+%&
+%\kax[5]\colon&\DIA\BOT\IMP\BOT
+%\\
+%\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
+%&
+%\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
+%\end{array}
+%\end{equation*}
+%\end{itemize}
+%
+%The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
+%%
+%It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
+%
+%\begin{definition}
+%	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
+%%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
+%	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
+%	\begin{enumerate}
+%		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
+%		
+%			\begin{equation*}
+%			\xymatrix{
+%				u' \ar@{.>}[r]_R  & v' \\
+%				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
+%			}
+%			\end{equation*}
+%		
+%		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
+%		
+%			\begin{equation*}
+%			\xymatrix{
+%				u' \ar@{.>}[r]^R & v' \\
+%				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
+%			}
+%			\end{equation*}
+%	\end{enumerate}
+%%	
+%\end{definition}
+%
+%\begin{definition}
+%	\label{model}
+%	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
+%	if $w \le w'$ then $V(w)\subseteq V(w')$.
+%\end{definition}
+%
+%We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
+%%
+%Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
+%\begin{equation}
+%  \label{eq:kripke}
+%  \parbox{30em}{%
+%  $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
+%
+%$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
+%
+%$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
+%
+%$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
+%
+%$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
+%
+%%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
+%}
+%\end{equation}
+%\todo{fix typography}
+%
+%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
+%
+%From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
+%\begin{proposition}(Monotonicity) 
+%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
+%\end{proposition}
+%
+%
+%
+%\begin{definition}
+%	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
+%%
+%	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
+%\end{definition}
+%
+%
+%
+%%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
+%%
+%%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
+%
+%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
+%
+%\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
+%	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
+%\end{theorem}
+%
+%\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $F_1$ and $F_2$
-\todo{proper typography}. These need to be reflected in the proof
+strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
 system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.

### 2019-09-16 caleidoscope/caleidoscope.tex
adding proof for admissibility of identity

@@
 \input{macros}
+\input{kax_macros}
 %\newcommand{\B}{\Digamma}
@@
 A \coloncolonequals
-a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
+a \mid A \AND A \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
 $$
 %
-\lutz{why do we have $\TOP$?}
 
@@
 		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\quad
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
+		%\quad
+		%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
 		\\\\
@@
 		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+ 		$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
 % 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
@@
 We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{kuz:str:maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$ \todo{$\TOP$ yes/no}, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
+Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{kuz:str:maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
 However, this translation also yields the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
@@
 
+\begin{lemma}
+	The following rule is admissible in $\labIKp$: 
+	$\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$
+\end{lemma}
+
+\begin{proof}
+	By induction of the size of the formula $A$.
+	\begin{smallequation*}
+		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
+		\reducesto
+		\vlinf{\labrn{id}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
+	\end{smallequation*}
+	\begin{smallequation*}
+		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
+		\reducesto
+	\end{smallequation*}
+	\begin{smallequation*}
+		\vlderivation{
+			\vlin{\llabrn\AND}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
+				\vliin{\rlabrn\AND}{}{\B, x \le y; \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
+					\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
+						\vlhy{}
+					}
+				}{
+				\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
+					\vlhy{}
+				}
+			}
+		}
+	}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
+	\reducesto
+\end{smallequation*}
+\begin{smallequation*}
+	\vlderivation{
+		\vliin{\llabrn\OR}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
+			\vlin{\rlabrn\OR}{}{\B, x \le y; \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
+				\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
+					\vlhy{}
+				}
+			}
+		}{
+		\vlin{\rlabrn\OR}{}{\B, x \le y; \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
+			\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
+				\vlhy{}
+			}
+		}
+	}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
+	\reducesto
+\end{smallequation*}
+\begin{smallequation*}\hspace*{-10em}
+	\vlderivation{
+		\vlin{\rlabrn\IMP}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
+			\vlin{trans}{}{\B, x \le y, y \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+				\vliin{\llabrn\IMP}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+					\vlin{refl}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
+						\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
+							\vlhy{}
+						}
+					}
+				}{
+				\vlin{refl}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+					\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+						\vlhy{}
+					}
+				}
+			}
+		}
+	}
+}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
+	\reducesto
+\end{smallequation*}
+\begin{smallequation*}
+	\vlderivation{
+		\vlin{\rlabrn\BOX}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
+			\vlin{trans}{}{\B, x \le y, y \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
+				\vlin{\llabrn\BOX}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
+					\vlin{refl}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
+						\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \rel w, w \le w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
+							\vlhy{}
+						}
+					}
+				}
+			}
+		}
+	}
+\end{smallequation*}
+
+\begin{smallequation*}
+	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
+	\reducesto
+\end{smallequation*}
+\begin{smallequation*}
+	\vlderivation{
+		\vlin{\llabrn\DIA}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+			\vlin{\color{red}{F_2}}{}{\B, x \le y, x \rel z; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+					\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
+						\vlhy{}
+					}
+				}
+			}
+		}
+	}
+\end{smallequation*}
+
+\end{proof}
+
 In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
@@
 Then we can summarize soundness and completeness, and cut
-admissibility of $\labIKp$ in the following Theorem:
+admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
 
@@
 \ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implication~\ref{ii}$\implies$\ref{iii} is shown in
+the implica tion~\ref{ii}$\implies$\ref{iii} is shown in
 Section~\ref{sec:cut-elim}, and finally, the implication
@@
 
-\section{Completness}\label{sec:completeness}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Completeness}\label{sec:completeness}
 
@@
 %
-In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
+%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
 As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
 %
-As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.
+%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
+\bigskip
 
@@
 %
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$. The other cases are standard.
+As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
 
@@
 
-\todo{Fix the size of the next proof}
-\marianela{I will do it at the end when we have the format that we want to submit}
 \begin{proof}[Proof of \ref{ii} $\rightarrow$ \ref{iii}]
@@
 		\lutz{we need to define what that means $\M\Vdash$sequent}
+        \marianela{working on that}
 

### 2019-09-16 caleidoscope/caleidoscope.tex
done section 5: completeness

@@
 
+\begin{theorem}
+	For any formula $A$. If $A$ is a theorem of $\IK$ then $A$ is provable in $\labIKp +\labrn{cut}$.
+\end{theorem}
+
+\begin{proof}
+	In order to prove completeness, we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necessitation rule and modus ponens.
+
+	As we mentioned, in the course of the proof, we have to derive the five $\kax$ axioms.
+In the derivation of $\kax[1]$ is illustrated the need of having the rules corresponding to $\rn{refl}$ and $\rn{trans}$ in the system:
+
+	\kone
+
+	%%%
+	We can also show that the rule $\rn{refl}$ is needed in the derivation of $\kax[2]$:
+
+	\ktwo
+
+	%%%%
+	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$ which also illustrates the need of having the rule corresponding to $\rn{refl}$:
+
+	\begin{center}
+
+		$\vlderivation {
+			\vlin{\rlabrn{\IMP}}
+			{}
+			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
+			{\vlin {\llabrn{\DIA}}
+				{}
+				{x \le y, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+				{\vliin{\llabrn{\OR}}{}{x \le y, yRz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlhy{\circledast \hspace{40mm}}}{\vlhy{\star}}}}
+		}$
+
+		\bigskip
+
+	\end{center}
+
+	After applying the rule $\llabrn{\OR}$, our proof continues with two premises. On one side, the premise that follows from $\circledast$:
+
+	\bigskip
+	\begin{center}
+		$\vlderivation{\vlin{\llabrn{\OR}}{}{\circledast}{\vlin {\rlabrn{\OR}}
+				{}
+				{x \le y, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+				{\vlin {\rlabrn{\DIA}}
+					{}
+					{x \le y, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+					{\vlin {\rn{refl}}
+						{}
+						{x \le y, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+						{\vlin {\rn{id}}
+							{}
+							{x \le y, z \le z, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+							{\vlhy {}}}}}}}$
+	\end{center}	
+	And on the other hand, we have that the derivation continues from $\star$ like this:
+
+	\begin{center}
+		$\vlderivation{\vlin {\llabrn{\OR}}
+			{}
+			{\star}
+			{\vlin {\rlabrn{\OR}}
+				{}
+				{x \le y, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+				{\vlin {\rlabrn{\DIA}}
+					{}
+					{x \le y, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+					{\vlin {\rn{refl}}
+						{}
+						{x \le y, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+						{\vlin {\rn{id}}
+							{}
+							{x \le y, z \le z, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+							{\vlhy {}}}}}}}$
+	\end{center}
+\end{proof}
+
+The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame conditions $\rn{F_1}$:
+
+\kfour
+
+To complete the proof of the five variants of $\kax$ we still have to see that we can prove $\kax[5]$:
+
+\begin{center}
+
+	$\vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{}
+		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
+		{\vlin {\llabrn{\DIA}}
+			{}
+			{x \le y, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
+			{\vlin {\llabrn{\BOT}}
+				{}
+				{x \le y, yRz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
+				{\vlhy {}}}}
+	}$
+
+\end{center}
+
+As we mentioned, in the course of the proof of the theorem, we have to give a proof for all the axioms of propositional intuitionistic logic.
+As an example, we display the proof of the axiom $\rn{AND}$-$\rn{2}$: $ \fm{A \AND B \IMP B}$:
+
+\begin{center}
+	$\vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{}
+		{\Rightarrow \labels{x}{A \AND B \IMP B}}
+		{\vlin {\llabrn{\AND}}
+			{}
+			{x \le y, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
+			{\vlin {\rn{refl}}
+				{}
+				{x \le y, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+				{\vlin {\rn{id}}
+					{}
+					{x \le y, y \le y, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+					{\vlhy {}}}}}
+	}$
+\end{center}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Cut Admissibility}\label{sec:cut-elim}

### 2019-09-16 caleidoscope/caleidoscope.tex
getting bib-file right

@@
 
-Since their introduction in the 1980s by Gabbay~\cite{Gabbay},
+Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
 \emph{labelled proof calculi} have been widely used by proof theorist
@@
 of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron} or nested
-sequents~\cite{kashima,brunnler,pog} or 2-sequents~\cite{masini},
+hyper-sequents~\cite{avron:elc96} or nested
+sequents~\cite{kashima,brunnler,pog} or 2-sequents~\cite{masini:apal92},
 labelled calculi have the advantage of beeing more uniform and
@@
 where $\B$ stands for a set of relation atoms, and $\Gamma$ and
-$\Delta$ for sets \lutz{or multisets?} of labelled formulas.
+$\Delta$ for sets of labelled formulas.
 
@@
 premise, even though this is not the case in labelled
-systems~\cite{negri:xx} or nested sequents~\cite{fitting:xx} for
+systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
 intuitionistic logic. Our system eliminates this
@@
 However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{Fitch} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
-Wijekesera \cite{Wijekesera:1990} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{Benton:1998} or to reason about states of a machine under partial information \cite{WijesekeraNerode:2005}.
+It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
+Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
+The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
 However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
 
-The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi \cite{Fischer} and by Ewald \cite{Ewald} in the case of intuitionistic tense logic.
+The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic.
 It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
 
-The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
+The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
 %
@@
 equivalence of \ref{i} and \ref{iv} has already been stated in
-Theorem~\ref{thm:plotkin}~\cite{Fischer,Plotkin}. The implication
+Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
 \ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
@@
 Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{Gabbay}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{Simpson}, Vigano \cite{Vigano}, and Negri\cite{Negri}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{Nerode}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{Simpson}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{Strassburger} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
+Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
+For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
+These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
+
+Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
+
+Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
 Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
@@
 %
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}.
+The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
 %
@@
 
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{Negri}.
+As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
 In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
@@
 %
-Most rules are similar to the ones of Simpson~\cite{Simpson}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
+Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
 %
@@
 
-In~\cite{Simpson}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
+In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
 %
@@
 
-In~\cite{Plotkin}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
+In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
 %
@@
 
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
+Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
 %

### 2019-09-16 caleidoscope/caleidoscope.tex
bib-file + new section for admissibility of mon + completeness

@@
 \usepackage{pgf}
+\usepackage{array}
 \usepackage[all]{xy}
@@
 hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima,brunnler,pog} or 2-sequents~\cite{masini:apal92},
+sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09} or 2-sequents~\cite{masini:apal92},
 labelled calculi have the advantage of beeing more uniform and
@@
 where $\B$ stands for a set of relation atoms, and $\Gamma$ and
-$\Delta$ for sets of labelled formulas.
+$\Delta$ for multi-sets of labelled formulas.
 
@@
   have already been studied
-  in~\cite{Plotkin}.\todo{check: did they get that wrong in  \cite{Plotkin}?}
+  in~\cite{plotkin:stirling:86}.\todo{check: did they get that wrong in  \cite{plotkin:stirling:86}?}
 \item The correspondence between the syntax and the semantics is not
@@
   and considered as a very unsatisfactory situation\todo{check what he
-    said exactly} (see also \cite{mar:str:indexed}).
+    said exactly} (see also \cite{mar:str:tableaux17}).
 \end{enumerate}
@@
 the corresponding nested sequent
-systems~\cite{str:fossacs13,mar:str:aiml}. It is possible to express
+systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
 Maehara style multiple-conclusion systems in nested
@@
 In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
-The cut elimination theorem, proved in Section~\ref{sec:cutelim}, then entails soundness and completeness for the cut-free system.
+The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
 Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
@@
 
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{Maffezioli}.}
+\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
 
@@
 
-We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
+We write $\M, w \Vdash a$ if $a \in V(w)$, and by definition, we always have $\M, w \Vdash \top$ and never that $\M, w \Vdash \bot$. 
 %
 Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-\begin{equation}
+$$
+\begin{array}{rcl}
 \label{eq:kripke}
-\parbox{30em}{%
-	$w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
-
-	$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
-
-	$w \Vdash A \IMP B$ iff for all $\lb{w'}$ with $\futs w{w'}$, if $w' \Vdash A$ then $w' \Vdash B$
-
-	$w \Vdash \BOX A$ iff for all $\lb{w'}$ and $\lb u$ with $\futs w{w'}$ and $\accs {w'}u$, $u \Vdash A$ \hfill %$(\ast)$
-
-	$w \Vdash \DIA A$ iff there exists a $u$ such that $\accs wu$ and $u \Vdash A$.
+%\parbox{30em}{%
+
+	\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
+
+	\M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\
+
+	\M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\
+
+	\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
+
+	\M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.
 
 	%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-}
-\end{equation}
-\todo{fix typography}
-
-We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
+%}
+\end{array}
+$$
+
+We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
 
@@
 \begin{proposition}(Monotonicity) 
-	For any formula $A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $w \Vdash A$, then $w' \Vdash A$.
+	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
 \end{proposition}
@@
 \begin{definition}
-	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-	%
-	A formula $A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
+	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
+	%
+	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}
@@
 
-\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
+\begin{theorem}[Fischer-Servi~\cite{fischer-servi:84}, Plotkin and Stirling~\cite{plotkin:stirling:86}]\label{thm:plotkin}
+	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
 \end{theorem}
@@
 where $\B$ is a set of relation atoms, and $\Left$ and $\Right$ are
-sets of labelled formulas, all written as list, separated by commas.
+multi-sets of labelled formulas, all written as list, separated by commas.
 
@@
 We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{kuz:str:maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
+Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
 However, this translation also yields the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
@@
 $\rlabrn\BOX$. In the multiple-conlusion nested sequent system
-of~\cite{kuz:str:maehara}, these are the two rules that force
+of~\cite{str:2017maehara}, these are the two rules that force
 single-conclusion. This is the reason why in our system we need the
@@
 $\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}.
-
-\begin{theorem}
-  \label{thm:mon-adm}
-  The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-For proving this theorem, we need a series of auxiliary lemmas.
-
-\todo{}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-  \todo{}
-\end{proof}
+instead of using the rules in~\eqref{eq:nomon}. We prove the admissibility of monotonicity in the Section~\ref{sec:mon}.
+
+\todo{I am not sure how to introduce the next lemma}
 
@@
 \begin{proof}
-	By induction of the size of the formula $A$.
-	\begin{smallequation*}
-		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		\reducesto
+	By induction of the size of the formula $\fm A$.
+	\begin{itemize}
+		\item Atomic case
+		\begin{smallequation*}
+			%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
+			%\reducesto
 			\vlinf{\labrn{id}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
 		\end{smallequation*}
-	\begin{smallequation*}
-		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
-		\reducesto
-	\end{smallequation*}
+
+		\item $\fm{A \AND B}$
+		%\begin{smallequation*}
+		%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
+		%	\reducesto
+		%\end{smallequation*}
 		\begin{smallequation*}
@@
 
-\begin{smallequation*}
-	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
-	\reducesto
-\end{smallequation*}
+	\item $\fm{A \OR B}$
+	%\begin{smallequation*}
+	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
+	%	\reducesto
+	%\end{smallequation*}
 	\begin{smallequation*}
@@
 
-\begin{smallequation*}
-	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
-	\reducesto
-\end{smallequation*}
-\begin{smallequation*}\hspace*{-10em}
+	\item $\fm{A \IMP B}$
+%	\begin{smallequation*}
+%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
+%		\reducesto
+%	\end{smallequation*}
+	\begin{smallequation*}
 		\vlderivation{
 			\vlin{\rlabrn\IMP}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-			\vlin{trans}{}{\B, x \le y, y \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+				\vlin{\rn{trans}}{}{\B, x \le y, y \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 					\vliin{\llabrn\IMP}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vlin{refl}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
+						\vlin{\rn{refl}}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
 							\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
@@
 					}{
-				\vlin{refl}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+					\vlin{\rn{refl}}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 						\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
@@
 
-\begin{smallequation*}
-	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
-	\reducesto
-\end{smallequation*}
+	\item $\fm{\BOX A}$
+%	\begin{smallequation*}
+%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
+%		\reducesto
+%	\end{smallequation*}
 	\begin{smallequation*}
@@
 			\vlin{\rlabrn\BOX}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-			\vlin{trans}{}{\B, x \le y, y \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
+				\vlin{\rn{trans}}{}{\B, x \le y, y \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
 					\vlin{\llabrn\BOX}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{refl}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
+						\vlin{\rn{refl}}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
 							\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \rel w, w \le w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
@@
 
-\begin{smallequation*}
-	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-	\reducesto
-\end{smallequation*}
+	\item $\fm{\DIA A}$
+%	\begin{smallequation*}
+%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
+%		\reducesto
+%	\end{smallequation*}
 	\begin{smallequation*}
@@
 			\vlin{\llabrn\DIA}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\color{red}{F_2}}{}{\B, x \le y, x \rel z; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
 					\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
@@
 	\end{smallequation*}
+	\end{itemize}
 
@@
 \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Admissibility of monotonicity}\label{sec:mon}
+
+\begin{theorem}
+	\label{thm:mon-adm}
+	The rule $\rn{mon}$ is admissible for system $\labIKp$.
+\end{theorem}
+
+For proving this theorem, we need a series of auxiliary lemmas.
+
+\todo{}
+
+\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
+	\todo{}
+\end{proof}
 
@@
 \begin{proof} [Proof of soundness]
-	We need to prove that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+	We need to prove that each sequent rule of our system $\labIKp$ is sound. We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+
+	In order to obtain the proof, let us introduce a definition:
+
+	\begin{definition}
+
+	\end{definition}
+
 	As the proof is similar for each of the rules, we prove the soundness of some particular rules:
@@
 
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
+	%	\item 
+	%	If there exists a proof 
+	%	$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
+	%	then there exists a proof 
+	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
 
@@
 		\item
+		If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
+
+		\item
 		If there exists a proof 
@@
 
-\section{Extensions}
+\section{Extensions}\label{sec:ext}
 

### 2019-09-16 caleidoscope/caleidoscope.tex
working on soundness section

@@
 
-We write $\M, w \Vdash a$ if $a \in V(w)$, and by definition, we always have $\M, w \Vdash \top$ and never that $\M, w \Vdash \bot$. 
+We write $\M, \lb w \Vdash a$ if $a \in V(w)$, and by definition, we always have $\M, w \Vdash \top$ and never that $\M, w \Vdash \bot$. 
 %
@@
 \emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relation atoms, and $\Left$ and $\Right$ are
+where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
 multi-sets of labelled formulas, all written as list, separated by commas.
@@
 	\begin{tabular}{c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
+		$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
 		&
@@
 		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+		$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
 		}
@@
 		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+ 		$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
 % 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
@@
 		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
 		&
-		$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
+		$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
 		\\\\
-		$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
+		$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
 		&
-		$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
+		$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
 		\\
@@
 		\\
-		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
+		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
 		&
-		$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
+		$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
 		\\\\
 		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
+		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
 		}
@@
 		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
+		$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
 		}
@@
 the implica tion~\ref{ii}$\implies$\ref{iii} is shown in
-Section~\ref{sec:cut-elim}, and finally, the implication
-\ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
+Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
 
@@
 
-\todo{}
+\todo{move lemma \ref{lem:inv}}
 
@@
 
+In order to prove the implication \ref{iii}$\implies$\ref{iv} from Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
+We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+
+In order to obtain the proof, let us introduce the next definitions:
+
+\begin{definition}
+	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
+\end{definition}
+
+\begin{definition}
+	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \Rightarrow \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \Rightarrow \Delta$ if there exists $\f$ such that:
+	\begin{enumerate}
+		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$.
+		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
+		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
+	\end{enumerate}
+	then for all $\labels{z}{B} \in \Delta$, we have that $\M, f(\lb z) \Vdash \fm B$.
+We say that $\M \not \Vdash \B, \Gamma \Rightarrow \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \Rightarrow \Delta$.
+\end{definition}
+
+Following the definitions, we display the proof for some rules since it is similar for each rule. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\todo{an introduction? do not repeat the theorem?}
 \begin{theorem}
@@
 	\end{center}
-\end{proof}
 
@@
 \end{center}
+
+\end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	\begin{enumerate}
-		\item
-		If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
+		%\item
+		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
 
@@
 \end{lemma}
+
+\todo{add missing cases}
 

### 2019-09-18 caleidoscope/caleidoscope.tex
fixing some details + finishing completeness

@@
 
-Standard labelled sequent calculi attach to every formula $A$ a label
-$x$, witten as $\labels xA$, and additionally admit so called
+Standard labelled sequent calculi attach to every formula $\fm A$ a label
+$\lb x$, witten as $\labels xA$, and additionally admit so called
 \emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
@@
 \end{equation}
-where $\B$ stands for a set of relation atoms, and $\Gamma$ and
+where $\B$ stands for a set of relational atoms, and $\Gamma$ and
 $\Delta$ for multi-sets of labelled formulas.
@@
   as they are equivalent in classical
-  modal logic. However, in intuiotionistic modal logic they are not
+  modal logic. However, in intuitionistic modal logic they are not
   equivalent, and even though the logic $\ISfour$, i.e., the
@@
 %
+\todo{change color?}
 
@@
 \begin{itemize}
-	\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom}:
+	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
+	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
 	\begin{equation*}
@@
 	\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
-	\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
+	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
 	&
-	\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
+	\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
 	&
-	\kax[5]\colon&\DIA\BOT\IMP\BOT
+	\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
 	\\
-	\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
+	\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
 	&
-	\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
+	\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
 	\end{array}
@@
 		\xymatrix{
-			u' \ar@{.>}[r]^R  & v' \\
-			u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & v \ar@{->}[u]_{\le}
+			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
+			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
 		}
@@
 		\xymatrix{
-			u' \ar@{.>}[r]^R & v' \\
-			u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
+			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
+			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
 		}
@@
 
-We write $\M, \lb w \Vdash a$ if $a \in V(w)$, and by definition, we always have $\M, w \Vdash \top$ and never that $\M, w \Vdash \bot$. 
+We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and by definition, we always have $\M, \lb w \Vdash \top$ and never that $\M, \lb w \Vdash \bot$. 
 %
 Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-$$
+
+\begin{equation*}\label{eq:kripke}
 	\begin{array}{rcl}
-\label{eq:kripke}
 	%\parbox{30em}{%
@@
 
-	%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-%}
 	\end{array}
-$$
+\end{equation*}
+\todo{label is not appearing}
 
@@
 
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-%\marianela{maybe adding the following: ?}
-%Now, we would like to consider special restrictions on these bi-relational frames.
+\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
+
+%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
+
+\begin{theorem}[\cite{plotkin:stirling:86}]
+	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
+
+	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
+
+\end{theorem}
+
+% we would like to consider special restrictions on these bi-relational frames.
 For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
@@
 $\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. We prove the admissibility of monotonicity in the Section~\ref{sec:mon}.
+instead of using the rules in~\eqref{eq:nomon}. We prove the admissibility of monotonicity in the Section~\ref{sec:cut-elim}.
 
@@
 	The following rule is admissible in $\labIKp$: 
-	$\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$
+	$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$
 \end{lemma}
@@
 			%\reducesto
-			\vlinf{\labrn{id}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
+			\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
 		\end{smallequation*}
@@
 			\vlderivation{
-				\vlin{\llabrn\AND}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
-					\vliin{\rlabrn\AND}{}{\B, x \le y; \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
-						\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
+				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
+					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
+						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
 							\vlhy{}
@@
 					}{
-					\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
+					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
 						\vlhy{}
@@
 		\vlderivation{
-			\vliin{\llabrn\OR}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\rlabrn\OR}{}{\B, x \le y; \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
-					\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
+			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
+				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
+					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
 						\vlhy{}
@@
 			}{
-			\vlin{\rlabrn\OR}{}{\B, x \le y; \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
+			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
+				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
 					\vlhy{}
@@
 		\vlderivation{
-			\vlin{\rlabrn\IMP}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-				\vlin{\rn{trans}}{}{\B, x \le y, y \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vliin{\llabrn\IMP}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\rn{refl}}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \le z; \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
+			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
+				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+					\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
+							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
 								\vlhy{}
@@
 					}{
-					\vlin{\rn{refl}}{}{\B, x \le y, y \le z, x \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \le z; \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 							\vlhy{}
@@
 		\vlderivation{
-			\vlin{\rlabrn\BOX}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-				\vlin{\rn{trans}}{}{\B, x \le y, y \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{\llabrn\BOX}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-						\vlin{\rn{refl}}{}{\B, x \le y, y \le z, x \le z, z \rel w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, x \le y, y \le z, x \le z, z \rel w, w \le w; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
+			\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
+				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
+					\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
+						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
+							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
 								\vlhy{}
@@
 		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-						\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u; \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
+			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+						\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
 							\vlhy{}
@@
 Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Admissibility of monotonicity}\label{sec:mon}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-For proving this theorem, we need a series of auxiliary lemmas.
-
-\todo{move lemma \ref{lem:inv}}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-	\todo{}
-\end{proof}
 
@@
 \section{Cut Admissibility}\label{sec:cut-elim}
+
+\begin{theorem}
+	\label{thm:mon-adm}
+	The rule $\rn{mon}$ is admissible for system $\labIKp$.
+\end{theorem}
+
+For proving this theorem, we need a series of auxiliary lemmas.
+
+\todo{move lemma \ref{lem:inv}}
+
+\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
+	\todo{}
+\end{proof}
 

### 2019-09-18 caleidoscope/caleidoscope.tex
making the completeness proof more beautiful

@@
 \begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \Rightarrow \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \Rightarrow \Delta$ if there exists $\f$ such that:
+	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \Rightarrow \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \Rightarrow \Delta$ if for all $\f$ such that:
 	\begin{enumerate}
@@
 	\end{enumerate}
-	then for all $\labels{z}{B} \in \Delta$, we have that $\M, f(\lb z) \Vdash \fm B$.
+	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$.
 We say that $\M \not \Vdash \B, \Gamma \Rightarrow \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \Rightarrow \Delta$.
@@
 \begin{theorem}
-	For any formula $A$. If $A$ is a theorem of $\IK$ then $A$ is provable in $\labIKp +\labrn{cut}$.
+	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
 \end{theorem}
@@
 
-	\kone
+		\begin{center}
+			$\vlderivation{
+				\vlin{\rlabrn{\IMP}}
+				{\lb y \mbox{ fresh}}
+				{\Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
+				{\vlin {\rlabrn{\IMP}}
+					{\lb z \mbox{ fresh}}
+					{\futs xy, \labels{y}{\BOX(A \IMP B)} \Rightarrow \labels{y}{\BOX A \IMP \BOX B}}
+					{\vlin {\rlabrn{\BOX}}
+						{\lb w, \lb u \mbox{ fresh}}
+						{\futs xy, \futs yz, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{z}{\BOX B}}
+						{\vlin {\llabrn{\BOX}}
+							{}
+							{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{u}{B}}
+							{\vlin {\color{red}\rn{trans}}
+								{}
+								{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+								{\vlin {\llabrn{\BOX}}
+									{}
+									{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+									{\vlin {\color{red}\rn{refl}}
+										{}
+										{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
+										{\vliin{\llabrn{\IMP}}
+											{}
+											{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
+											{\vlin {\rn{id}}
+												{}
+												{G, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}, \labels{u}{A}}
+												{\vlhy {}}}
+											{\vlin {\rn{id}}
+												{}
+												{G, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+												{\vlhy {}}}}}}}}}}
+			}$
+		\end{center}
+
+		where $G$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
 
@@
 
-	\ktwo
+\begin{center}
+	$\vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{\lb y \mbox{ fresh}}
+		{ \Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
+		{\vlin {\rlabrn{\IMP}}
+			{\lb z \mbox{ fresh}}
+			{ \futs xy, \labels{y}{\BOX (A \IMP B)} \Rightarrow \labels{y}{(\DIA A \IMP \DIA B)}}
+			{\vlin {\llabrn{\DIA}}
+				{\lb u \mbox{ fresh}}
+				{\futs xy, \futs yz, \labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A} \Rightarrow \labels{z}{\DIA B}}
+				{\vlin{\rlabrn{\DIA}}
+					{}
+					{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}}
+					{\vlin {\llabrn{\BOX}}
+						{}
+						{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+						{\vlin {\color{red}\rn{refl}}
+							{}
+							{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+							{\vliin{\llabrn{\IMP}}
+								{}
+								{\futs xy, \futs yz, \accs zu, \futs uu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+								{\vlin {\rn{id}}
+									{}
+									{T, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}
+									{\vlhy {}}}
+								{\vlin {\rn{id}}
+									{}
+									{T, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+									{\vlhy {}}}								}}}}}}
+	}$
+\end{center}
+
+where $T$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
 
@@
 				{}
-				{x \le y, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-				{\vliin{\llabrn{\OR}}{}{x \le y, yRz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlhy{\circledast \hspace{40mm}}}{\vlhy{\star}}}}
+				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
+						{}
+						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+						{\vlin {\rlabrn{\DIA}}
+							{}
+							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+							{\vlin {\color{red}{\rn{refl}}}
+								{}
+								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+								{\vlin {\rn{id}}
+									{}
+									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
+						{}
+						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+						{\vlin {\rlabrn{\DIA}}
+							{}
+							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+							{\vlin {\color{red}{\rn{refl}}}
+								{}
+								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+								{\vlin {\rn{id}}
+									{}
+									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+									{\vlhy {}}}}}}}}
 		}$
@@
 
-	\end{center}
-
-	After applying the rule $\llabrn{\OR}$, our proof continues with two premises. On one side, the premise that follows from $\circledast$:
-
-	\bigskip
-	\begin{center}
-		$\vlderivation{\vlin{\llabrn{\OR}}{}{\circledast}{\vlin {\rlabrn{\OR}}
-				{}
-				{x \le y, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-				{\vlin {\rlabrn{\DIA}}
-					{}
-					{x \le y, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-					{\vlin {\rn{refl}}
-						{}
-						{x \le y, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
-						{\vlin {\rn{id}}
-							{}
-							{x \le y, z \le z, yRz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
-							{\vlhy {}}}}}}}$
-	\end{center}	
-	And on the other hand, we have that the derivation continues from $\star$ like this:
-
-	\begin{center}
-		$\vlderivation{\vlin {\llabrn{\OR}}
-			{}
-			{\star}
-			{\vlin {\rlabrn{\OR}}
-				{}
-				{x \le y, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-				{\vlin {\rlabrn{\DIA}}
-					{}
-					{x \le y, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-					{\vlin {\rn{refl}}
-						{}
-						{x \le y, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
-						{\vlin {\rn{id}}
-							{}
-							{x \le y, z \le z, yRz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
-							{\vlhy {}}}}}}}$
 	\end{center}

### 2019-09-18 caleidoscope/caleidoscope.tex
done completeness section

@@
 	%%%%
-	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$ which also illustrates the need of having the rule corresponding to $\rn{refl}$:
+	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$: %which also illustrates the need of having the rule corresponding to $\rn{refl}$:
 
@@
 							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-							{\vlin {\color{red}{\rn{refl}}}
+							{\vlin {\rn{refl}}
 								{}
@@
 							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-							{\vlin {\color{red}{\rn{refl}}}
+							{\vlin {\rn{refl}}
 								{}
@@
 
-The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame conditions $\rn{F_1}$:
-
-\kfour
-
-To complete the proof of the five variants of $\kax$ we still have to see that we can prove $\kax[5]$:
-
-\begin{center}
-
-	$\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{x \le y, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{x \le y, yRz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
-				{\vlhy {}}}}
-	}$
-
-\end{center}
-
-As we mentioned, in the course of the proof of the theorem, we have to give a proof for all the axioms of propositional intuitionistic logic.
-As an example, we display the proof of the axiom $\rn{AND}$-$\rn{2}$: $ \fm{A \AND B \IMP B}$:
+The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame condition $\rn{F_1}$:
 
@@
 		\vlin{\rlabrn{\IMP}}
-		{}
-		{\Rightarrow \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{x \le y, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
+		{\lb y \mbox{ fresh}}
+		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
+		{\vlin {\rlabrn{\BOX}}
+			{\lb z, \lb w \mbox{ fresh}}
+			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
+			{\vlin {\rlabrn{\IMP}}
+				{\lb u \mbox{ fresh}}
+				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
+				{\vlin {\color{red}{\rn{F_1}}}
+					{}
+					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+					{\vlin {\rn{trans}}
+						{}
+						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+						{\vliin {\llabrn{\IMP}}
+							{}
+							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+							{\vlhy{\circledast  \hspace{75mm}}}
+							{\vlhy{\star}}}}}}}
+	}$
+
+\end{center}
+
+The derivation continues as the result of applying the rule $\llabrn{\IMP}$. From this rule we obtain two trees:
+
+On one side, the derivation that follows from $\circledast$:
+
+\begin{center}
+
+	$
+	\vlderivation{
+		\vlin{\llabrn{\IMP}}{}{\circledast}{\vlin {\rlabrn{\DIA}}
+			{}
+			{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
 			{\vlin {\rn{refl}}
 				{}
-				{x \le y, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+				{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
 				{\vlin {\rn{id}}
 					{}
-					{x \le y, y \le y, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+					{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \futs uu, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
 					{\vlhy {}}}}}
@@
 \end{center}
+
+To complete the proof of the five variants of $\kax$ we still have to see that we can prove $\kax[5]$:
+
+\begin{center}
+
+	$\vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{}
+		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
+		{\vlin {\llabrn{\DIA}}
+			{}
+			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
+			{\vlin {\llabrn{\BOT}}
+				{}
+				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
+				{\vlhy {}}}}
+	}$
+
+\end{center}
+
+As we mentioned, in the course of the proof of the theorem, we have to give a proof for all the axioms of propositional intuitionistic logic.
+As an example, we display the proof of the axiom $\rn{AND}$-$\rn{2}$: $ \fm{A \AND B \IMP B}$:
+
+\begin{center}
+	$\vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{}
+		{\Rightarrow \labels{x}{A \AND B \IMP B}}
+		{\vlin {\llabrn{\AND}}
+			{}
+			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
+			{\vlin {\rn{refl}}
+				{}
+				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+				{\vlin {\rn{id}}
+					{}
+					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+					{\vlhy {}}}}}
+	}$
+\end{center}
+
+\todo{I do not know how to close the theorem}
+
+As we mentioned, in order to conclude the proof of the Theorem~\ref{thm:cutfree-compl} we simulate the necessitation rule and modus ponens.
 

### 2019-09-24 caleidoscope/caleidoscope.tex
working on cut section

@@
 \input{macros}
-\input{kax_macros}
-%\newcommand{\B}{\Digamma}
 \newcommand{\B}{\mathcal{R}}
-%\newcommand{\B}{\Xi}
-%\newcommand{\B}{\mathcal{B}}
 \newcommand*{\A}{\mathcal{A}}
@@
 sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09} or 2-sequents~\cite{masini:apal92},
-labelled calculi have the advantage of beeing more uniform and
+labelled calculi have the advantage of being more uniform and
 accommodating more logics.
@@
 
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-For proving this theorem, we need a series of auxiliary lemmas.
-
-\todo{move lemma \ref{lem:inv}}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-	\todo{}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
-
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
-%
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
-%
-
-\begin{definition}
-A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
-In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
-On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these are presented in the system $\labIKp$ as follows:
-
-\begin{center}
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				}
-				\\\\
-				\hspace{15mm}
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
-
-\end{center}
-
-\bigskip
-
-A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
-
-\begin{itemize}
-	\item Rule $\rn{F1}$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-			\\\\
-			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-			\\\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\hspace{8mm}
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-\end{center}
-
-You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
-
-\begin{itemize}
-	\item Rule $\llabrn\AND$:
-
-	%The system $\labIKp$ presents the next rule for the conjunction left:
-
-	%\begin{center}
-	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-	%\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\rlabrn\OR$:
-
-	Let the rule presented in $\labIKp$ for disjunction right be as follows:
-
-	\begin{center}
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-	\end{center}
-
-	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\\\\
-			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
-			\\\\
-			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-			\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-A more detailed explanation for some rules is below:
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$.
-	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
-
-\bigskip
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\multicolumn{2}{c}{
-				\hspace{9mm}
-				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-			}
-			\\
-			\multicolumn{2}{c}{
-				\hspace{10mm}
-				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-			}
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-The rule for implication right is explained below:
-
-\begin{itemize}
-	\item Rule $\rlabrn\IMP$.
-	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
-\end{itemize}
-
-\section{A complete and sound system for intuitionistic modal logics}
-%
-Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
-%
-Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
-%
-Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$ 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
-%		
-%		\todo{}
-		\smash{%\fbox{
-			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
-		}%}
-		%
-
-                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
-		\item\label{iii} $A$ is provable in $\labIKp$
-		%
-		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-%We show that each rule from our system is sound.
-%
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-The proof is a careful adaptation of standard techniques.
-%
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
-As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
-%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
-\bigskip
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlhy {}
-										}
-									}
-								}
-							}{
-%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-										\vlhy {\qquad\vdots\qquad}
-%										}
-%									}
-%								}
-%							}
-						}
-					}
-				}
-			}
-		}
-	}
-}$
-}$$
-%\end{example}
-
-%\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-}
-$
-}
-$$
-%\end{example}
-
-\begin{proof}[Proof of \ref{ii} $\rightarrow$ \ref{iii}]
+\todo{I do not know how to organize this section. First cut elimination proof? (lemma before or after?) Then mon is admissible using cut proof?}
+
+Following the proof for the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
+
+For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
+
+\begin{proof}
 
@@
 
+\begin{theorem}
+	\label{thm:mon-adm}
+	The rule $\rn{mon}$ is admissible for system $\labIKp$.
+\end{theorem}
+
+\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
+
+	\todo{say that we can obtain the proof for monotonicity using the proof of cut.}
+
+\end{proof}
+
+\begin{lemma}\label{lem:inv}\hbox{}\quad
+	\begin{enumerate}
+		%\item
+		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
+
+		\item
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
+		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+		\item
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
+		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
+		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
+
+		\item 
+		If there exists a proof 
+		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
+		then there exists a proof 
+		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
+		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
+
+	\end{enumerate}
+\end{lemma}
+
+\todo{add missing cases}
+
+\begin{proof}
+	In each case, we reason by induction on the height of $\DD$.
+
+	\begin{itemize}
+		\item $\llabrn\IMP$:
+		For a proof of height $1$, it is straightforward.
+		%
+		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
+		%
+		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
+
+		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
+
+		First let us fix a given index $y$ that does not appear in $\DD$.
+
+		If we start with a proof
+		\begin{smallequation*}
+			\DD = 
+			\vlderivation{
+				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
+				}	
+			}
+		\end{smallequation*}
+
+		Then by induction hypothesis there exists a proof 
+		\begin{smallequation*}
+			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
+		\end{smallequation*}
+		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
+
+		Therefore, we have the proof
+		\begin{smallequation*}
+			\DD^{\invr{\llabrn\IMP}} = 
+			\vlderivation{
+				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
+					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
+				}
+			}
+		\end{smallequation*}
+		of the same (or smaller) height as $\DD$.
+
+		If we start with a proof 
+		\begin{smallequation*}
+			\vlderivation{
+				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
+				}{
+				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
+			}
+		}
+	\end{smallequation*}
+	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
+
+	%
+	\item $\llabrn\DIA$:
+
+	If we start with a proof
+	\begin{smallequation*}
+		\DD = 
+		\vlderivation{
+			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
+			}	
+		}
+	\end{smallequation*}
+
+	Then by induction hypothesis there exists a proof 
+	\begin{smallequation*}
+		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
+	\end{smallequation*}
+	of the same (or smaller) height as $\DD'$.
+
+	Therefore, we have the proof
+	\begin{smallequation*}
+		\DD^{\invr{\llabrn\DIA}} = 
+		\vlderivation{
+			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
+				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
+			}
+		}
+	\end{smallequation*}
+	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
+
+	If we start with a proof 
+	\begin{smallequation*}
+		\vlderivation{
+			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
+				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
+			}	
+		}
+	\end{smallequation*}
+	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
+
+	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
+\end{itemize}
+\end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Labelled sequent calculi with $\rel$ and $\le$}
+
+%%
+%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
+Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
+Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
+For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
+These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
+
+Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
+
+Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
+Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
+%
+
+Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
+%
+The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
+%
+
+\begin{definition}
+A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
+\end{definition}
+In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
+
+\section{Building $\labIKp$}
+
+As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
+In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
+This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
+In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
+
+\subsection{Frame conditions}
+%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
+The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
+For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
+Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
+On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
+All these are presented in the system $\labIKp$ as follows:
+
+\begin{center}
+		\begin{minipage}{.95\textwidth}
+			\begin{tabular}{@{\!}c@{\quad}c}
+				\multicolumn{2}{c}{
+					\hspace{18mm}
+					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
+				}
+				\\\\
+				\hspace{15mm}
+				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
+				&
+				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
+
+				\\\\
+				\multicolumn{2}{c}{
+					\hspace{18mm}
+					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
+				}
+				\\\\
+				\multicolumn{2}{c}{
+					\hspace{18mm}
+					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
+				}
+			\end{tabular}		
+		\end{minipage}
+
+\end{center}
+
+\bigskip
+
+A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
+
+\begin{itemize}
+	\item Rule $\rn{F1}$.
+
+	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
+
+	\begin{center}
+		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
+	\end{center}
+
+	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
+
+	\item Rule $\ftwo$:
+
+	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
+
+	\begin{center}
+	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
+	\end{center}
+
+	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
+
+\end{itemize}
+
+\subsection{Logical connectives for intuitionistic propositional logic}
+
+To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
+That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
+
+\begin{center}
+	\begin{minipage}{.95\textwidth}
+		\begin{tabular}{@{\!}c@{\quad}c}
+			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
+			&
+			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
+			\\\\
+			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
+			&
+			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
+			\\\\
+		\end{tabular}
+	\end{minipage}
+\end{center}
+
+To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
+
+\begin{center}
+		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
+		\hspace{8mm}
+		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
+\end{center}
+
+You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
+
+\begin{itemize}
+	\item Rule $\llabrn\AND$:
+
+	%The system $\labIKp$ presents the next rule for the conjunction left:
+
+	%\begin{center}
+	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
+	%\end{center}
+
+	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
+From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
+
+	\item Rule $\rlabrn\OR$:
+
+	Let the rule presented in $\labIKp$ for disjunction right be as follows:
+
+	\begin{center}
+		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
+	\end{center}
+
+	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
+
+\end{itemize}
+
+\subsection{Modal operators}
+
+We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
+\begin{center}
+	\begin{minipage}{.95\textwidth}
+		\begin{tabular}{@{\!}c@{\quad}c}
+			\\\\
+			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+			&
+			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
+			\\\\
+			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
+			&
+			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
+			\\
+		\end{tabular}
+	\end{minipage}
+\end{center}
+
+\bigskip
+
+A more detailed explanation for some rules is below:
+
+\begin{itemize}
+	\item Rule $\llabrn\BOX$.
+	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
+Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
+
+	\item Rule $\rlabrn\DIA$.
+	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
+In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
+
+\end{itemize}
+
+\subsection{Intuitionistic implication}
+To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
+
+\bigskip
+
+\begin{center}
+	\begin{minipage}{.95\textwidth}
+		\begin{tabular}{@{\!}c@{\quad}c}
+			\multicolumn{2}{c}{
+				\hspace{9mm}
+				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+			}
+			\\
+			\multicolumn{2}{c}{
+				\hspace{10mm}
+				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+			}
+		\end{tabular}
+	\end{minipage}
+\end{center}
+
+\bigskip
+
+The rule for implication right is explained below:
+
+\begin{itemize}
+	\item Rule $\rlabrn\IMP$.
+	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
+\end{itemize}
+
+\section{A complete and sound system for intuitionistic modal logics}
+%
+Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
+%
+Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
+%
+In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
+%
+Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
+
+As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
+
+%\begin{theorem}
+%	\label{thm:sound-compl}
+%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
+%\end{theorem}
+%
+%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
+%
+%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
+
+%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
+
+\begin{theorem}\label{thm:cutfree-compl}
+	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
+	%
+	For any formula $A$, the following are equivalent.
+	%
+	\begin{enumerate}
+		\item\label{i} $A$ is a theorem of $\IK$ 
+		%
+		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
+%		
+%		\todo{}
+		\smash{%\fbox{
+			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
+		}%}
+		%
+
+                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
+		\item\label{iii} $A$ is provable in $\labIKp$
+		%
+		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
+	\end{enumerate}
+\end{theorem}
+
+%We show that each rule from our system is sound.
+%
+%
+%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
+%
+%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
+%
+%We show the proof by case analysis. 
+%
+%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
+
+The proof is a careful adaptation of standard techniques.
+%
+%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
+As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
+%
+%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
+\bigskip
+
+\vspace*{-.9cm}
+$$
+\hspace*{-.5cm}
+\scalebox{.9}{
+$
+\vlderivation{
+	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
+		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
+			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
+				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
+								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
+									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
+										\vlhy {}
+										}
+									}
+								}
+							}{
+%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
+%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
+%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
+%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
+										\vlhy {\qquad\vdots\qquad}
+%										}
+%									}
+%								}
+%							}
+						}
+					}
+				}
+			}
+		}
+	}
+}$
+}$$
+%\end{example}
+
+%\vspace*{-.5cm}
+
+Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
+%
+We therefore have to show that such a rule is admissible in our system.
+%
+As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
+
+\vspace*{-.5cm}
+%\begin{example}
+$$
+\scalebox{.9}{
+$
+\vlderivation{
+	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
+					\vlhy{}
+				}
+			}
+		}
+	}
+}
+$
+}
+$$
+%\end{example}
+
 \begin{proof} [Proof of soundness]
@@
 	Standard.
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-In each case, we reason by induction on the height of $\DD$.
-
-\begin{itemize}
-\item $\llabrn\IMP$:
-For a proof of height $1$, it is straightforward.
-%
-For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-%
-then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-First let us fix a given index $y$ that does not appear in $\DD$.
-
-If we start with a proof
-\begin{smallequation*}
-	\DD = 
-	\vlderivation{
-		\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-		}	
-	}
-\end{smallequation*}
-
-Then by induction hypothesis there exists a proof 
-\begin{smallequation*}
-	\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-\end{smallequation*}
-of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-Therefore, we have the proof
-\begin{smallequation*}
-	\DD^{\invr{\llabrn\IMP}} = 
-	\vlderivation{
-		\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-			\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-		}
-	}
-\end{smallequation*}
-of the same (or smaller) height as $\DD$.
-
-If we start with a proof 
-\begin{smallequation*}
-	\vlderivation{
-		\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-		}{
-		\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-	}
-	}
-\end{smallequation*}
-then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-%
-\item $\llabrn\DIA$:
-
-If we start with a proof
-\begin{smallequation*}
-	\DD = 
-	\vlderivation{
-		\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-			\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-		}	
-	}
-\end{smallequation*}
-
-Then by induction hypothesis there exists a proof 
-\begin{smallequation*}
-	\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-\end{smallequation*}
-of the same (or smaller) height as $\DD'$.
-
-Therefore, we have the proof
-\begin{smallequation*}
-	\DD^{\invr{\llabrn\DIA}} = 
-	\vlderivation{
-		\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-			\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-		}
-	}
-\end{smallequation*}
-of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-If we start with a proof 
-\begin{smallequation*}
-	\vlderivation{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-			\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-		}	
-	}
-\end{smallequation*}
-then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
 \end{proof}

### 2019-09-24 caleidoscope/caleidoscope.tex
missing proof of completeness added and small modif

@@
 							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-							{\vlhy{\circledast  \hspace{75mm}}}
-							{\vlhy{\star}}}}}}}
+							{\vlin {\rlabrn{\DIA}}
+									{}
+									{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
+									{\vlin {\rn{refl}}
+										{}
+										{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
+										{\vlin {\rn{id}}
+											{}
+											{R, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
+											{\vlhy {}}}}}
+							{\vlin {\rn{refl}}
+								{}
+								{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
+								{\vlin {\llabrn{\BOX}}
+									{}
+									{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
+									{\vlin {\rn{refl}}
+										{}
+										{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+										{\vlin {\rn{id}}
+											{}
+											{R, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+											{\vlhy {}}}}}}}}}}}
 	}$
@@
 
-The derivation continues as the result of applying the rule $\llabrn{\IMP}$. From this rule we obtain two trees:
-
-On one side, the derivation that follows from $\circledast$:
-
-\begin{center}
-
-	$
-	\vlderivation{
-		\vlin{\llabrn{\IMP}}{}{\circledast}{\vlin {\rlabrn{\DIA}}
-			{}
-			{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
-			{\vlin {\rn{refl}}
-				{}
-				{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
-				{\vlin {\rn{id}}
-					{}
-					{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \futs uu, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
-					{\vlhy {}}}}}
-	}$
-\end{center}
+where $R$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
 
@@
 
-Following the proof for the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
+Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
 
@@
 
-	\todo{say that we can obtain the proof for monotonicity using the proof of cut.}
+	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
 

### 2019-09-26 caleidoscope/caleidoscope.tex
pass through sections 1 and 2

@@
 
+\newcommand{\quand}{\quad\mbox{and}\quad}
 \newcommand{\qquand}{\qquad\mbox{and}\qquad}
@@
 %\begin{frontmatter}
-  \title{A properly labelled proof system for intuitionistic modal logics}
+  \title{A fully labelled proof system for intuitionistic modal logics}
   \author{Sonia Marin \and %}
@@
    two relation symbols for the labels: one for the accessibility
-   relation associated with the Kripke semantics for modal logics and
+   relation associated with the Kripke semantics for normal modal logics and
    one for the preorder relation associated with the Kripke semantics
@@
    This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logic. As a
+   birelational Kripke semantics for intuitionistic modal logics. As a
    consequence it can encompass a wider range of intuitionistic modal
@@
 \emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive system to a broad range
+to give sound, complete and cut-free deductive systems to a broad range
 of logics. Unlike so-called \emph{internal calculi}, like
 hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09} or 2-sequents~\cite{masini:apal92},
-labelled calculi have the advantage of being more uniform and
-accommodating more logics.
-
-Standard labelled sequent calculi attach to every formula $\fm A$ a label
+sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
+labelled calculi have the advantage of being more uniform and being able to 
+accommode more logics.
+
+Standard labelled sequent calculi attach to every formla $\fm A$ a label
 $\lb x$, witten as $\labels xA$, and additionally admit so called
@@
 to encode the accessibility relation in the Kripke models, and the
-frame condition corresponding to the desired logic can be directly
+frame conditions corresponding to the desired logic can be directly
 encoded as inference rules. Prominent examples are classical modal
@@
     \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-    \qquand
+    \quand
     \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
+    \;,
   \end{equation}
-  have already been studied
-  in~\cite{plotkin:stirling:86}.\todo{check: did they get that wrong in  \cite{plotkin:stirling:86}?}
+  respectively, have already been studied
+  in~\cite{plotkin:stirling:86}.
   \item The correspondence between the syntax and the semantics is not
@@
     means that every layer in the model can be lifted to any future of
-    any world in that layer.}\todo{check terminology in Simpson} models, as
+    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
   already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as a very unsatisfactory situation\todo{check what he
-    said exactly} (see also \cite{mar:str:tableaux17}).
+  and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
 \end{enumerate}
@@
 discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.\lutz{check, is this really the case?}
+we never delete information.
 
@@
 Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
-\lutz{what about doing that directly in the system presentation, like Negri does it?}
 
@@
 %
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
+Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $a$, $b$, $c$,\ldots, modal formulas, denoted by capital letters $A$, $B$, $C$, \ldots, are constructed from the grammar:
 %
@@
 	\label{eq:ik}%\hskip-2em
-	\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
+	\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
 	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
@@
 The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
-The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system $\break \rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$.
+The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}.
 However this would give strictly no information on the behaviour of the $\DIA$ modality.
@@
 	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
+	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
 	\begin{enumerate}
-		\item[($\rn{F_1}$)] For $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
+		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
 
@@
 
-		\item[($\rn{F_2}$)] For $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
+		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
 
@@
 
-We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and by definition, we always have $\M, \lb w \Vdash \top$ and never that $\M, \lb w \Vdash \bot$. 
-%
-Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-
-\begin{equation*}\label{eq:kripke}
+We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:
+
+\begin{equation}\label{eq:kripke}
 	\begin{array}{rcl}
@@
 	\end{array}
-\end{equation*}
-\todo{label is not appearing}
-
-We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
+\end{equation}
+Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
+%
+We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
 
@@
 	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
+	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}
@@
 
-Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
-
-\begin{theorem}[Fischer-Servi~\cite{fischer-servi:84}, Plotkin and Stirling~\cite{plotkin:stirling:86}]\label{thm:plotkin}
-	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
+Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.
+
+\begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
+	A formula is a theorem of $\IK$ if and only if it is valid in every bi-relational frame.
 \end{theorem}
@@
 
+\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
 \begin{theorem}[\cite{plotkin:stirling:86}]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+%
 \section{The system}\label{sec:system}
 
-In this section we present our properly labelled sequent proof system
+In this section we present our fully labelled sequent proof system
 for intuitionistic modal logics. The starting point is the notion of a

### 2019-09-26 caleidoscope/caleidoscope.tex
pass through section 3

@@
 Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this translation also yields the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
+However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
 \begin{equation}
@@
 However, these two rule create new labels, and in order to be
-complete, the system needs the \emph{monotonicity} rule:
+complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
 \begin{equation}
   \label{eq:mono}
-  \vlinf{\rn{mon}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}\Right}{
+  \vlinf{\llabrn{mon}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}\Right}{
     \lseq{\B, x \le x'}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
+  \hskip6em
+  \vlinf{\rlabrn{mon}}{}{\lseq{\B, x\le x'}{\Left}{\Right, \labels{x'}{A}}}{
+    \lseq{\B, x \le x'}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
 \end{equation}
@@
 $\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. We prove the admissibility of monotonicity in the Section~\ref{sec:cut-elim}.
-
-\todo{I am not sure how to introduce the next lemma}
-
-\begin{lemma}
-	The following rule is admissible in $\labIKp$: 
-	$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$
-\end{lemma}
+instead of using the rules in~\eqref{eq:nomon}. Then, not only
+$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
+shown on the right in~\eqref{eq:mono} above is admissible.
+
+\begin{proposition}
+  \label{prop:mon-adm}
+  The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$.
+\end{proposition}
+
+One can prove this proposition in the same way as one usually proves
+admissibity of contraction in a sequent calculus, by inductiop on the
+height of the derivation, which in fact would yield a stronger result,
+namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
+  preserving} admissible for $\labIKp$. However, we do not need this
+result in this paper, and therefore we leave it as an exercise to the
+reader. Nonetheless, we will give a short proof of
+Proposition~\ref{prop:mon-adm} at the end of this section.
+
+Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.
+
+\begin{proposition}
+  \label{prop:id}
+	The following general idenity axiom~
+	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
+        ~is admissible for $\labIKp$. 
+\end{proposition}
 
 \begin{proof}
-	By induction of the size of the formula $\fm A$.
+	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
 	\begin{itemize}
-		\item Atomic case
-		\begin{smallequation*}
-			%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-			%\reducesto
-			\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		\end{smallequation*}
-
+		%% \item Atomic case
+		%% \begin{smallequation*}
+		%% 	%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
+		%% 	%\reducesto
+		%% 	\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
+		%% \end{smallequation*}
 		\item $\fm{A \AND B}$
@@
 	\end{smallequation*}
-
 	\item $\fm{A \OR B}$
@@
 	\end{smallequation*}
+        \quedhere
 	\end{itemize}
-
 \end{proof}
@@
 \ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implica tion~\ref{ii}$\implies$\ref{iii} is shown in
+the implication~\ref{ii}$\implies$\ref{iii} is shown in
 Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
+
+Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
+
+\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
+  The rule $\llabrn{mon}$ can be derived using the general identity and cut:
+  \begin{smallequation*}
+    \vlderivation{
+      \vliiin{\labrn{cut}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}\Right}{
+        \vlin{\labrn{id_g}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
+          \vlhy{}}}{
+        \vlhy{\quad}}{
+        \vlhy{\lseq{\B, x \le x'}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
+    }
+  \end{smallequation*}
+  And both these rules are admissible by Proposition~\ref{prop:id} and
+  Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
+  similar.
+\end{proof}
 

### 2019-09-26 caleidoscope/caleidoscope.tex
switched soundness and completeness
done with completeness

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Completeness}\label{sec:completeness}
+
+In this section we show our system at work, as most of the section
+consists of derivations of axioms of $\IK$ in $\labIKp$.
+More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
+
+\begin{theorem}\label{thm:completeness}
+	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
+\end{theorem}
+
+\begin{remark}
+  We have seem already in the proof of Proposition~\ref{prop:id} the
+  need of the rule $\rn{F_2}$. In the following proof of
+  Theorem~\ref{thm:completeness} we also see the need of the rules
+  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
+\end{remark}
+
+\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
+  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
+  \begin{itemize}
+  \item $\kax[1]$:
+    $$
+    \vlderivation{
+				\vlin{\rlabrn{\IMP}}
+				{\lb y \mbox{ fresh}}
+				{\Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
+				{\vlin {\rlabrn{\IMP}}
+					{\lb z \mbox{ fresh}}
+					{\futs xy, \labels{y}{\BOX(A \IMP B)} \Rightarrow \labels{y}{\BOX A \IMP \BOX B}}
+					{\vlin {\rlabrn{\BOX}}
+						{\lb w, \lb u \mbox{ fresh}}
+						{\futs xy, \futs yz, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{z}{\BOX B}}
+						{\vlin {\llabrn{\BOX}}
+							{}
+							{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{u}{B}}
+							{\vlin {\color{red}\rn{trans}}
+								{}
+								{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+								{\vlin {\llabrn{\BOX}}
+									{}
+									{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+									{\vlin {\color{red}\rn{refl}}
+										{}
+										{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
+										{\vliin{\llabrn{\IMP}}
+											{}
+											{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
+											{\vlin {\rn{id}}
+												{}
+												{\B, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}, \labels{u}{A}}
+												{\vlhy {}}}
+											{\vlin {\rn{id}}
+												{}
+												{\B, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+												{\vlhy {}}}}}}}}}}
+    }
+    $$
+    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
+  \item $\kax[2]$:
+    $$
+    \vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{\lb y \mbox{ fresh}}
+		{ \Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
+		{\vlin {\rlabrn{\IMP}}
+			{\lb z \mbox{ fresh}}
+			{ \futs xy, \labels{y}{\BOX (A \IMP B)} \Rightarrow \labels{y}{(\DIA A \IMP \DIA B)}}
+			{\vlin {\llabrn{\DIA}}
+				{\lb u \mbox{ fresh}}
+				{\futs xy, \futs yz, \labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A} \Rightarrow \labels{z}{\DIA B}}
+				{\vlin{\rlabrn{\DIA}}
+					{}
+					{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}}
+					{\vlin {\llabrn{\BOX}}
+						{}
+						{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+						{\vlin {\color{red}\rn{refl}}
+							{}
+							{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+							{\vliin{\llabrn{\IMP}}
+								{}
+								{\futs xy, \futs yz, \accs zu, \futs uu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+								{\vlin {\rn{id}}
+									{}
+									{\B, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}
+									{\vlhy {}}}
+								{\vlin {\rn{id}}
+									{}
+									{\B, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+									{\vlhy {}}}								}}}}}}
+    }
+    $$
+    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
+  \item $\kax[3]$:
+    $$
+    \vlderivation {
+			\vlin{\rlabrn{\IMP}}
+			{}
+			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
+			{\vlin {\llabrn{\DIA}}
+				{}
+				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
+						{}
+						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+						{\vlin {\rlabrn{\DIA}}
+							{}
+							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+							{\vlin {\rn{refl}}
+								{}
+								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+								{\vlin {\rn{id}}
+									{}
+									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
+						{}
+						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+						{\vlin {\rlabrn{\DIA}}
+							{}
+							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+							{\vlin {\rn{refl}}
+								{}
+								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+								{\vlin {\rn{id}}
+									{}
+									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+									{\vlhy {}}}}}}}}
+		}
+    $$
+  \item $\kax[4]$:
+    $$
+\vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{\lb y \mbox{ fresh}}
+		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
+		{\vlin {\rlabrn{\BOX}}
+			{\lb z, \lb w \mbox{ fresh}}
+			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
+			{\vlin {\rlabrn{\IMP}}
+				{\lb u \mbox{ fresh}}
+				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
+				{\vlin {\color{red}{\rn{F_1}}}
+					{}
+					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+					{\vlin {\rn{trans}}
+						{}
+						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+						{\vliin {\llabrn{\IMP}}
+							{}
+							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+							{\vlin {\rlabrn{\DIA}}
+									{}
+									{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
+									{\vlin {\rn{refl}}
+										{}
+										{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
+										{\vlin {\rn{id}}
+											{}
+											{\B, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
+											{\vlhy {}}}}}
+							{\vlin {\rn{refl}}
+								{}
+								{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
+								{\vlin {\llabrn{\BOX}}
+									{}
+									{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
+									{\vlin {\rn{refl}}
+										{}
+										{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+										{\vlin {\rn{id}}
+											{}
+											{\B, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+											{\vlhy {}}}}}}}}}}}
+}
+$$
+where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
+\item $\kax[5]$:
+  $$
+  \vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{}
+		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
+		{\vlin {\llabrn{\DIA}}
+			{}
+			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
+			{\vlin {\llabrn{\BOT}}
+				{}
+				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
+				{\vlhy {}}}}
+  }
+  $$
+  \end{itemize}
+  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
+  $$
+  \vlderivation {
+		\vlin{\rlabrn{\IMP}}
+		{}
+		{\Rightarrow \labels{x}{A \AND B \IMP B}}
+		{\vlin {\llabrn{\AND}}
+			{}
+			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
+			{\vlin {\rn{refl}}
+				{}
+				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+				{\vlin {\rn{id}}
+					{}
+					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+					{\vlhy {}}}}}
+  }
+  $$
+  Finally, we have to show how the rules of modus ponens and
+  necessitation can be simulated in our system. For modus ponens, this
+  is standard using the cut rule and for necesitation, we can
+  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
+  follows:
+
+  \todo{}
+
+  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
+\end{proof}
+
+\todo{all refl,trans, \rn{F_2} and $F_1$ in red}
+
+\todo{use the macro for sequents (the macro uses a longer arrow)}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-In order to prove the implication \ref{iii}$\implies$\ref{iv} from Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+In order to prove the implication \ref{iii}$\implies$\ref{iv} from
+Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
+of our system $\labIKp$ is sound. We want to prove that for all model
+$\M$ that satisfies the premise, then $\M$ satifies the conclusion.
 
@@
 Following the definitions, we display the proof for some rules since it is similar for each rule. 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-\todo{an introduction? do not repeat the theorem?}
-\begin{theorem}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{proof}
-	In order to prove completeness, we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necessitation rule and modus ponens.
-
-	As we mentioned, in the course of the proof, we have to derive the five $\kax$ axioms.
-In the derivation of $\kax[1]$ is illustrated the need of having the rules corresponding to $\rn{refl}$ and $\rn{trans}$ in the system:
-
-		\begin{center}
-			$\vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\futs xy, \labels{y}{\BOX(A \IMP B)} \Rightarrow \labels{y}{\BOX A \IMP \BOX B}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\futs xy, \futs yz, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{z}{\BOX B}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{u}{B}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
-											{\vlin {\rn{id}}
-												{}
-												{G, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}, \labels{u}{A}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{G, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
-												{\vlhy {}}}}}}}}}}
-			}$
-		\end{center}
-
-		where $G$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-
-	%%%
-	We can also show that the rule $\rn{refl}$ is needed in the derivation of $\kax[2]$:
-
-\begin{center}
-	$\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{ \futs xy, \labels{y}{\BOX (A \IMP B)} \Rightarrow \labels{y}{(\DIA A \IMP \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\futs xy, \futs yz, \labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A} \Rightarrow \labels{z}{\DIA B}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\futs xy, \futs yz, \accs zu, \futs uu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
-								{\vlin {\rn{id}}
-									{}
-									{T, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{T, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
-									{\vlhy {}}}								}}}}}}
-	}$
-\end{center}
-
-where $T$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-
-	%%%%
-	In order to continue our proof for the five variants of $\kax$, we display the proof for the axiom $\kax[3]$: %which also illustrates the need of having the rule corresponding to $\rn{refl}$:
-
-	\begin{center}
-
-		$\vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-							{\vlin {\rn{refl}}
-								{}
-								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
-								{\vlin {\rn{id}}
-									{}
-									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-							{\vlin {\rn{refl}}
-								{}
-								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
-								{\vlin {\rn{id}}
-									{}
-									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
-									{\vlhy {}}}}}}}}
-		}$
-
-		\bigskip
-
-	\end{center}
-
-The proof of $\kax[4]$ shows the need of having the rule corresponding to the frame condition $\rn{F_1}$:
-
-\begin{center}
-	$\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-					{\vlin {\rn{trans}}
-						{}
-						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
-									{\vlin {\rn{refl}}
-										{}
-										{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
-										{\vlin {\rn{id}}
-											{}
-											{R, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
-											{\vlhy {}}}}}
-							{\vlin {\rn{refl}}
-								{}
-								{R, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
-									{\vlin {\rn{refl}}
-										{}
-										{R, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
-										{\vlin {\rn{id}}
-											{}
-											{R, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
-											{\vlhy {}}}}}}}}}}}
-	}$
-
-\end{center}
-
-where $R$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-
-To complete the proof of the five variants of $\kax$ we still have to see that we can prove $\kax[5]$:
-
-\begin{center}
-
-	$\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
-				{\vlhy {}}}}
-	}$
-
-\end{center}
-
-As we mentioned, in the course of the proof of the theorem, we have to give a proof for all the axioms of propositional intuitionistic logic.
-As an example, we display the proof of the axiom $\rn{AND}$-$\rn{2}$: $ \fm{A \AND B \IMP B}$:
-
-\begin{center}
-	$\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\Rightarrow \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
-			{\vlin {\rn{refl}}
-				{}
-				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
-				{\vlin {\rn{id}}
-					{}
-					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
-					{\vlhy {}}}}}
-	}$
-\end{center}
-
-\todo{I do not know how to close the theorem}
-
-As we mentioned, in order to conclude the proof of the Theorem~\ref{thm:cutfree-compl} we simulate the necessitation rule and modus ponens.
-
-\end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-09-26 caleidoscope/caleidoscope.tex
cut elim

@@
 %%%%%%%%%%%%%%%%%
+
+%\newcommand{\height}[1]{\mathrm{ht}(#1)}
+\newcommand{\height}[1]{|#1|}
 
@@
 
+\lutz{some start below}
+
+In this section we are going to prove the admissibility of cut for $\labIKp$.
+
+\begin{theorem}
+  \label{thm:cut-adm}
+  The rule $\labrn{cut}$ is admissible for $\labIKp$.
+\end{theorem}
+
+This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
+
+The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is \todo{finish}
+
+We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
+A rule is \emph{height-preserving invertible} if \todo{...}
+
+The following two lemmas are standard.
+
+\begin{lemma}
+  \label{lem:weak-adm}
+  The weakening rule
+  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
+  is height-preserving admissible for $\labIKp$.
+\end{lemma}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+\begin{lemma}
+  \label{lem:inv}
+  The rules ..... are height-preserving invertible in
+  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
+  height-preserving invertible for the right premise.
+\end{lemma}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+The next lemma looks like a special case of
+Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
+preserve the height, and second, we cannot prove it using cut as we
+need it to eliminate the cut.
+
+\begin{lemma}
+  The atomic version of $\llabrn{mon}$
+  $$
+  \vlinf{\labrn{mon_a}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{a}}\Right}{
+    \lseq{\B, x \le x'}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
+  $$
+  is height-preserving admissible for $\labIKp$.
+\end{lemma}
+
+\begin{proof}
+  \todo{}
+\end{proof}
+
+The next lemma is the core of our cut elimination proof.
+
+\begin{lemma}
+  \label{lem:reduction}
+  Given a derivation of shape
+  $$
+  \vlderivation{
+    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
+      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
+      \vlhy{}}{
+      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
+  $$
+  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
+  derivation of ${\lseq\B\Left\Right}$
+\end{lemma}
+
+$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
+
 Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.

### 2019-09-27 caleidoscope/caleidoscope.tex
small modif

@@
 	\end{smallequation*}
-        \quedhere
+        \qedhere
 	\end{itemize}
@@
 							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-							{\vlin {\rn{refl}}
+							{\vlin {\color{red}\rn{refl}}
 								{}
@@
 							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
-							{\vlin {\rn{refl}}
+							{\vlin {\color{red}\rn{refl}}
 								{}
@@
 					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
-					{\vlin {\rn{trans}}
+					{\vlin {\color{red}\rn{trans}}
 						{}
@@
 									{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
-									{\vlin {\rn{refl}}
+									{\vlin {\color{red}\rn{refl}}
 										{}
@@
 											{\vlhy {}}}}}
-							{\vlin {\rn{refl}}
+							{\vlin {\color{red}\rn{refl}}
 								{}
@@
 									{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
-									{\vlin {\rn{refl}}
+									{\vlin {\color{red}\rn{refl}}
 										{}
@@
 			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
-			{\vlin {\rn{refl}}
+			{\vlin {\color{red}\rn{refl}}
 				{}
@@
   $$
+
   Finally, we have to show how the rules of modus ponens and
@@
 \end{proof}
-
-\todo{all refl,trans, \rn{F_2} and $F_1$ in red}
 
@@
 
-Following the definitions, we display the proof for some rules since it is similar for each rule. 
+Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
+
+\begin{itemize}
+	\item Rule $\llabrn\BOX$:
+
+	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
+
+	\begin{center}
+		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \Rightarrow \Right$.}
+	\end{center}
+
+	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, x \le y, yRz,\Left,\break \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
+Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $y, z \in W$ such that $\futs xy$ and $\accs yz$, then $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
+
+\marianela{working on this}
+	\marianela{
+	Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y,\break yRz, \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
+Therefore, in particular, from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0} \Vdash \labels{z}{A}$.
+Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
+Then, the rule $\llabrn\BOX$ is sound.
+
+	\item Rule $\rlabrn\BOX$: By way of contradiction.
+Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$, i.e.
+$\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{\BOX A}$, which is the same as $\M_{0} \Vdash \vlan (\B,\Left)$ and  $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$.
+From $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$, we have that $\M_{0} \not \Vdash \Right$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}$.
+Following the semantic definition of $\BOX$, there exists worlds $y, z$ in $\M_{0}$, such that $x \le y, yRz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
+Therefore, $\M_{0} \not \Vdash premise$, i.e.
+$\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
+Then, the rule $\rlabrn\BOX$ is sound.
+
+	\item Rule $\rlabrn\IMP$: By way of contradiction.
+Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{A \IMP B}$, i.e., in particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
+Therefore, there exists $y$ such that $x \le y$ and $\M_{0} \Vdash \labels{y}{A}$ but $\M_{0} \not \Vdash \labels{y}{B}$.
+Then, we have $\M_{0} \not \Vdash \B, x \le y, \Left, \labels{y}{A} \Rightarrow \labels{y}{B}$.
+Finally, the rule $\rlabrn\IMP$ is sound.}
+\end{itemize}
+
+The other cases are similar.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{proof} [Proof of soundness]
-	We need to prove that each sequent rule of our system $\labIKp$ is sound. We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-	In order to obtain the proof, let us introduce a definition:
-
-	\begin{definition}
-
-	\end{definition}
-
-	As the proof is similar for each of the rules, we prove the soundness of some particular rules:
-
-	\begin{itemize}
-		\item Rule $\llabrn\BOX$:
-
-		We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-		\begin{center}
-			\emph{For all model $\M$, if $\M \Vdash \B,\Left, x \le y, yRz, \labels{x}{\BOX A}, z \colon A \Rightarrow \Right$, then $\M \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A} \Rightarrow \Right$.}
-		\end{center}
-		\lutz{we need to define what that means $\M\Vdash$sequent}
-        \marianela{working on that}
-
-		By way of contradiction we want to see that if $\exists$ $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$,then $\M_{0} \not \Vdash premise$.
-More precisely for the $\llabrn\BOX$ rule we want to show that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y, \break yRz, \labels{x}{\BOX A} \Rightarrow \Right$ then $\M_{0} \not \Vdash \B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
-
-		Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y,\break yRz, \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular, from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0} \Vdash \labels{z}{A}$.
-Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
-Then, the rule $\llabrn\BOX$ is sound.\lutz{that is unclear}
-
-		\item Rule $\rlabrn\BOX$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$, i.e.
-$\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{\BOX A}$, which is the same as $\M_{0} \Vdash \vlan (\B,\Left)$ and  $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$.
-From $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$, we have that $\M_{0} \not \Vdash \Right$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}$.
-Following the semantic definition of $\BOX$, there exists worlds $y, z$ in $\M_{0}$, such that $x \le y, yRz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Therefore, $\M_{0} \not \Vdash premise$, i.e.
-$\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
-Then, the rule $\rlabrn\BOX$ is sound.
-
-		\item Rule $\rlabrn\IMP$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{A \IMP B}$, i.e., in particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $y$ such that $x \le y$ and $\M_{0} \Vdash \labels{y}{A}$ but $\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, x \le y, \Left, \labels{y}{A} \Rightarrow \labels{y}{B}$.
-Finally, the rule $\rlabrn\IMP$ is sound.
-	\end{itemize}
-        \lutz{the arguments are not clear}
-
-	The other cases are similar.
-\end{proof}
-
 \begin{lemma}\label{lem:weak}\hbox{}\quad

### 2019-09-27 caleidoscope/caleidoscope.tex
necessitation in completeness and details in other sections

@@
 %
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $a$, $b$, $c$,\ldots, modal formulas, denoted by capital letters $A$, $B$, $C$, \ldots, are constructed from the grammar:
+Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
 %
 $$
-A \coloncolonequals
-a \mid A \AND A \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
+\fm A \coloncolonequals
+\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
 $$
 %
-\todo{change color?}
 
@@
 \begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
-	A formula is a theorem of $\IK$ if and only if it is valid in every bi-relational frame.
+	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
 \end{theorem}
@@
 		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+		$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
 		}
@@
 		&
-		$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
+		$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
 		\\\\
-		$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
+		$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
 		&
@@
 		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
+		$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
 		}
@@
 		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
+		$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
 		}
@@
   \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A} \IMP B \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
+  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
   \quad
-  \vlinf{\llabrn\BOX}{}{\B, xRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, xRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
+  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
 \end{equation}
@@
   \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, x \le x'}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
+  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
+    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
   \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, x\le x'}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, x \le x'}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
+  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
+    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
 \end{equation}
@@
 One can prove this proposition in the same way as one usually proves
-admissibity of contraction in a sequent calculus, by inductiop on the
+admissibity of contraction in a sequent calculus, by induction on the
 height of the derivation, which in fact would yield a stronger result,
@@
 			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
 					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
@@
     \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
+      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
+        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
           \vlhy{}}}{
         \vlhy{\quad}}{
-        \vlhy{\lseq{\B, x \le x'}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
+        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
     }
@@
 				{\lb y \mbox{ fresh}}
-				{\Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
+				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
 				{\vlin {\rlabrn{\IMP}}
 					{\lb z \mbox{ fresh}}
-					{\futs xy, \labels{y}{\BOX(A \IMP B)} \Rightarrow \labels{y}{\BOX A \IMP \BOX B}}
+					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
 					{\vlin {\rlabrn{\BOX}}
 						{\lb w, \lb u \mbox{ fresh}}
-						{\futs xy, \futs yz, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{z}{\BOX B}}
+						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
 						{\vlin {\llabrn{\BOX}}
 							{}
-							{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A} \Rightarrow \labels{u}{B}}
+							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
 							{\vlin {\color{red}\rn{trans}}
 								{}
-								{\futs xy, \futs yz, \futs zw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
 								{\vlin {\llabrn{\BOX}}
 									{}
-									{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
 									{\vlin {\color{red}\rn{refl}}
 										{}
-										{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
+										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
 										{\vliin{\llabrn{\IMP}}
 											{}
-											{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}}
+											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
 											{\vlin {\rn{id}}
 												{}
-												{\B, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{u}{B}, \labels{u}{A}}
+												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
 												{\vlhy {}}}
@@
 												{}
-												{\B, \labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
 												{\vlhy {}}}}}}}}}}
@@
 		{\lb y \mbox{ fresh}}
-		{ \Rightarrow \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
+		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
 		{\vlin {\rlabrn{\IMP}}
 			{\lb z \mbox{ fresh}}
-			{ \futs xy, \labels{y}{\BOX (A \IMP B)} \Rightarrow \labels{y}{(\DIA A \IMP \DIA B)}}
+			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
 			{\vlin {\llabrn{\DIA}}
 				{\lb u \mbox{ fresh}}
-				{\futs xy, \futs yz, \labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A} \Rightarrow \labels{z}{\DIA B}}
+				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
 				{\vlin{\rlabrn{\DIA}}
 					{}
-					{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}}
+					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
 					{\vlin {\llabrn{\BOX}}
 						{}
-						{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
 						{\vlin {\color{red}\rn{refl}}
 							{}
-							{\futs xy, \futs yz, \accs zu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
 							{\vliin{\llabrn{\IMP}}
 								{}
-								{\futs xy, \futs yz, \accs zu, \futs uu, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
 								{\vlin {\rn{id}}
 									{}
-									{\B, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}
+									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
 									{\vlhy {}}}
@@
 									{}
-									{\B, \labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B} \Rightarrow \labels{z}{\DIA B}, \labels{u}{B}}
+									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
 									{\vlhy {}}}								}}}}}}
@@
 			{}
-			{\Rightarrow \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
+			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
 			{\vlin {\llabrn{\DIA}}
 				{}
-				{\futs xy, \labels{y}{\DIA (A \OR B)} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
-				{\vliin{\llabrn{\OR}}{}{\futs xy, \accs yz, \labels{z}{A \OR B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
+				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
+						{}
+						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
 						{\vlin {\rlabrn{\DIA}}
 							{}
-							{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
 							{\vlin {\color{red}\rn{refl}}
 								{}
-								{\futs xy, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
 								{\vlin {\rn{id}}
 									{}
-									{\futs xy, \futs zz, \accs yz, \labels{z}{A} \Rightarrow \labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}
+									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
 									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
 						{}
-						{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A \OR \DIA B}}
+						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
 						{\vlin {\rlabrn{\DIA}}
 							{}
-							{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}}
+							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
 							{\vlin {\color{red}\rn{refl}}
 								{}
-								{\futs xy, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
 								{\vlin {\rn{id}}
 									{}
-									{\futs xy, \futs zz, \accs yz, \labels{z}{B} \Rightarrow \labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}
+									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
 									{\vlhy {}}}}}}}}
@@
 		{\lb y \mbox{ fresh}}
-		{\Rightarrow \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
+		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
 		{\vlin {\rlabrn{\BOX}}
 			{\lb z, \lb w \mbox{ fresh}}
-			{\futs xy, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{y}{\BOX (A \IMP B)}}
+			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
 			{\vlin {\rlabrn{\IMP}}
 				{\lb u \mbox{ fresh}}
-				{\futs xy, \futs yz, \accs zw, \labels{y}{\DIA A \IMP \BOX B} \Rightarrow \labels{w}{A \IMP B}}
+				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
 				{\vlin {\color{red}{\rn{F_1}}}
 					{}
-					{\futs xy, \futs yz, \futs wu, \accs zw, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
 					{\vlin {\color{red}\rn{trans}}
 						{}
-						{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
 						{\vliin {\llabrn{\IMP}}
 							{}
-							{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}}
+							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
 							{\vlin {\rlabrn{\DIA}}
 									{}
-									{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}}
+									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
 									{\vlin {\color{red}\rn{refl}}
 										{}
-										{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
+										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
 										{\vlin {\rn{id}}
 											{}
-											{\B, \futs uu,  \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \Rightarrow \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}
+											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
 											{\vlhy {}}}}}
@@
 								{}
-								{\B, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
+								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
 								{\vlin {\llabrn{\BOX}}
 									{}
-									{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \Rightarrow \labels{u}{B}}
+									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
 									{\vlin {\color{red}\rn{refl}}
 										{}
-										{\B, \futs tt, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
 										{\vlin {\rn{id}}
 											{}
-											{\B, \futs tt, \futs uu, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \Rightarrow \labels{u}{B}}
+											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
 											{\vlhy {}}}}}}}}}}}
@@
 		{}
-		{\Rightarrow \labels{x}{\DIA \BOT \IMP \BOT}}
+		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
 		{\vlin {\llabrn{\DIA}}
 			{}
-			{\futs xy, \labels{y}{\DIA \BOT} \Rightarrow \labels{y}{\BOT}}
+			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
 			{\vlin {\llabrn{\BOT}}
 				{}
-				{\futs xy, \accs yz, \labels{z}{\BOT} \Rightarrow \labels{y}{\BOT}}
+				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
 				{\vlhy {}}}}
@@
 		{}
-		{\Rightarrow \labels{x}{A \AND B \IMP B}}
+		{\SEQ \labels{x}{A \AND B \IMP B}}
 		{\vlin {\llabrn{\AND}}
 			{}
-			{\futs xy, \labels{y}{A \AND B} \Rightarrow \labels{y}{B}}
+			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
 			{\vlin {\color{red}\rn{refl}}
 				{}
-				{\futs xy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
 				{\vlin {\rn{id}}
 					{}
-					{\futs xy, \futs yy, \labels{y}{A}, \labels{y}{B} \Rightarrow \labels{y}{B}}
+					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
 					{\vlhy {}}}}}
@@
   necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necesitation, we can
+  is standard using the cut rule and for necessitation, we can
   transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
@@
 
-  \todo{}
+\begin{lemma}
+	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
+\end{lemma}
+
+\begin{proof}
+
+	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
+
+	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
+	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
+
+	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
+
+%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
+%	
+%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
+%	Then using the \emph{weakening} rule, we have the following proof:
+%	
+%	\bigskip
+%	\begin{center}
+%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
+%	\end{center}
+%
+
+\end{proof}
 
@@
 \end{proof}
-
-\todo{use the macro for sequents (the macro uses a longer arrow)}
 
@@
 For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, w \rel u, \Left \SEQ \Right}$}$$
+$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
 to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon (\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)$, that is, wrt.~to all frames in which $\rel$ is transitive.
+$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
 
@@
 %
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \DIA\DIA A \IMP \DIA A$ are exactly the ones satisfying the condition:
+For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
 %\begin{center}
-	($\diabrn{4}$) if $w \rel v$ and $v \rel u$, there exists a $u'\in W$ s.t.~$u \le u'$ and $wRu'$.
+	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
 %\end{center}
@@
 Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, u \le u', w \rel u' , \Left \SEQ \Right}$}$$
+$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
 
@@
 
-Proof of $\ax{4_{\BOX}} \colon \BOX A \IMP \BOX\BOX A$
+Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
 
@@
 	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{x \le w, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{x \le w, w \le w', \bm{w' \rel v}, \bm{v \le v'}, v' \rel u, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, \bm{w' \le t}, \bm{t \rel v'}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{x \le w, w \le w', w' \rel v, v \le v', \bm{v' \rel u}, w' \le t, \bm{t \rel v'}, w \le t \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, w' \le t, t \rel v', w \le t, \bm{t \rel u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{x \le w, w \le w', w' \rel v, v \le v', v' \rel u, w' \le t, t \rel v', w \le t, t \rel u, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
+		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
+			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
+							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
 								\vlhy{}
@@
 	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{x \le w, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{x \le w, w \rel v, v \rel u, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{x \le w, w \rel v, v \rel u, u \le u', w \rel u'  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{x \le w, w \rel v, v \rel u, u \le u', w \rel u'  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
+		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
+			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
+				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
+					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
 						\vlhy{}
@@
 
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
+Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
 why??}
@@
 \begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u$ fresh$}{\B, xR^{k}y, xR^{m}z, \Left \Rightarrow \Right}{\vlhy {\B, y \le y', xR^{k}y, xR^{m}z, y'R^{l}u, zR^{n}u, \Left\Rightarrow \Right}}}$
+	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
 \end{center}
@@
 		\scalebox{0.93}{
-			$\vlderivation {\vlin {\sir}
-				{y$ fresh$}
-				{\Rightarrow \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\sbr}
-					{z, w $ fresh $}
-					{x \le y, \labels{y}{\DIA \BOX A} \Rightarrow \labels{y}{\BOX \DIA A}}
-					{\vlin {\sdl}
-						{u$ fresh$}
-						{x \le y, y \le z, zRw, \labels{y}{\DIA \BOX A} \Rightarrow \labels{w}{\DIA A}}
-						{\vlin {\ftwo}
-							{t$ fresh$}
-							{x \le y, y \le z, zRw, yRu, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}}
+			$\vlderivation {\vlin {\rlabrn{\IMP}}
+				{y \mbox{ fresh}}
+				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
+				{\vlin {\rlabrn{\BOX}}
+					{z, w \mbox{ fresh} }
+					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
+					{\vlin {\llabrn{\DIA}}
+						{u \mbox{ fresh}}
+						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
+						{\vlin {\rn{F_2}}
+							{t \mbox{ fresh}}
+							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
 							{\vlin {\gklmn}
-								{t', j$ fresh$}
-								{x \le y, y \le z, u \le t, zRw, yRu, zRt, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}}
-								{\vlin {\sdr}
-									{}
-									{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}}
-									{\vlin {\trans}
-										{}
-										{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
-										{\vlin {\sbl}
-											{}
-											{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
-											{\vlin {\refl}
-												{}
-												{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A}, \labels{j}{A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
-												{\vlin {\ids}
-													{}
-													{x \le y, y \le z, u \le t, t \le t', u \le t',j \le j, zRw, yRu, zRt, t'Rj, wRj, \labels{u}{\BOX A}, \labels{j}{A} \Rightarrow \labels{w}{\DIA A}, \labels{j}{A}}
+								{t', j \mbox{ fresh}}
+								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
+								{\vlin {\rlabrn{\DIA}}
+									{}
+									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
+									{\vlin {\rn{trans}}
+										{}
+										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
+										{\vlin {\llabrn{\BOX}}
+											{}
+											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
+											{\vlin {\rn{refl}}
+												{}
+												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
+												{\vlin {\rn{id}}
+													{}
+													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
 													{\vlhy {}}}}}}}}}}}}$}

### 2019-09-30 caleidoscope/caleidoscope.tex
soundness section

@@
 In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
-of our system $\labIKp$ is sound. We want to prove that for all model
-$\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
+We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
 
@@
 \begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \Rightarrow \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \Rightarrow \Delta$ if for all $\f$ such that:
+	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
 	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$.
+		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
 		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
@@
 	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$.
-We say that $\M \not \Vdash \B, \Gamma \Rightarrow \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \Rightarrow \Delta$.
+	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$. We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
 \end{definition}
@@
 	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \Rightarrow \Right$.}
+		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
 	\end{center}
 
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, x \le y, yRz,\Left,\break \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $y, z \in W$ such that $\futs xy$ and $\accs yz$, then $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
-
-\marianela{working on this}
-	\marianela{
-	Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y,\break yRz, \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular, from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0} \Vdash \labels{z}{A}$.
-Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
-Then, the rule $\llabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\BOX$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$, i.e.
-$\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{\BOX A}$, which is the same as $\M_{0} \Vdash \vlan (\B,\Left)$ and  $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$.
-From $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$, we have that $\M_{0} \not \Vdash \Right$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}$.
-Following the semantic definition of $\BOX$, there exists worlds $y, z$ in $\M_{0}$, such that $x \le y, yRz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Therefore, $\M_{0} \not \Vdash premise$, i.e.
-$\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
-Then, the rule $\rlabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\IMP$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{A \IMP B}$, i.e., in particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $y$ such that $x \le y$ and $\M_{0} \Vdash \labels{y}{A}$ but $\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, x \le y, \Left, \labels{y}{A} \Rightarrow \labels{y}{B}$.
-Finally, the rule $\rlabrn\IMP$ is sound.}
+	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
+Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $\lb y, \lb z \in W$ such that $\futs xy$ and $\accs yz$, $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
+From this result, we can say that $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
+Thus, we have already proved that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, then $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
+According to the definition, we proved that the rule $\llabrn\BOX$ is sound.
+
+	\item Rule $\rlabrn\BOX$:
+
+	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
+
+	\begin{center}
+		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
+	\end{center}
+
+	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
+Let us assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.
+In particular, $\M_{0} \not \Vdash \labels{x}{\BOX A}$, which means that there exist worlds $\lb y, \lb z$, such that $\futs xy$ and $\accs yz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
+Finally, we have that $\M_{0} \Vdash \B, \futs xy, \accs yz, \Left$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}, \labels{z}{A}$,  which is the same as $\M_{0} \not \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$.
+Then, by way of contradiction, we proved that the rule $\rlabrn\BOX$ is sound.
+
+	\item Rule $\rlabrn\IMP$:
+
+	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
+	\begin{center}
+		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
+	\end{center}
+
+	We prove this statement by way of contradiction.
+Assume there exists a model $\M_{0}$ such that $\M_{0}$ does not satisfy the conclusion, i.e.
+$\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.
+In particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
+Therefore, there exists $\lb y$ such that $\futs xy$ and $\M_{0}, f(\lb y) \Vdash A$ (i.e.
+$\M_{0} \Vdash \labels{y}{A}$) but $\M_{0}, f(\lb y) \Vdash B$, i.e.
+$\M_{0} \not \Vdash \labels{y}{B}$.
+Then, we have $\M_{0} \not \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \labels{y}{B}$.
+This means that the model $\M_{0}$ does not satisfy the premise and that is what we wanted to prove.
+Finally, we showed that the rule $\rlabrn\IMP$ is sound.
+
+	\item Rule $\llabrn\DIA$:
+
+	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
+
+	\begin{center}
+		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
+	\end{center}
+
+	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
+	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
+From $\M_{0} \Vdash \labels{x}{\DIA A}$, according to the definition of the $\DIA$ operator, we have that there exists a world $\lb y$ in $\M_{0}$ such that $\accs xy$ and $\M_{0} \Vdash \labels{y}{A}$.
+Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ and we prove that the rule $\llabrn\DIA$ is sound.
+
+	\item Rule $\rlabrn\DIA$:
+
+	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
+
+	\begin{center}
+		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
+	\end{center}
+
+	We prove this statement by way of contradiction.
+Let us assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$, we want to show that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
+	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
+for all world $\lb y \in \M_{0}$ where $\accs xy$ we have $\M_{0} \not \Vdash \labels{y}{A}$.
+Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
+Finally, assuming that $\M_{0}$ does not satisfy the conclusion, we proved that $\M_{0}$ does not satisfy the premise.
+Then we conclude that the rule $\rlabrn\DIA$ of the system $\labIKp$ is sound.
 \end{itemize}
 
-The other cases are similar.
+The other cases are similar and we leave them to the reader.
 
@@
 \section{Cut Admissibility}\label{sec:cut-elim}
-
-\todo{I do not know how to organize this section. First cut elimination proof? (lemma before or after?) Then mon is admissible using cut proof?}
-
-\lutz{some start below}
-
 In this section we are going to prove the admissibility of cut for $\labIKp$.
@@
 
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is \todo{finish}
+The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is the height of D when seen as a tree, i.e., the length of
+the longest path in the tree from its root to one of its leaves.
 
 We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if \todo{...}
+A rule is \emph{height-preserving invertible} if for every
+derivation of the conclusion of the rule there are derivations for each of its premisses with at most the same height.
 
@@
 \begin{proof}
-  \todo{}
+  \todo{\begin{lemma}
+  	If there exists a proof  $\vlderivation {\vlpd{\D}{}{\B, \Left \Rightarrow \Right}}$ then there exists a proof $\vlderivation {\vlpd {\Dw}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}}$
+
+  \end{lemma}
+
+  \vspace{3mm}
+
+  \begin{proof}
+  	By induction on the height of $\D$.
+
+  	For a proof of height 1:
+
+  	if $\D$ = $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, x \colon a \Rightarrow \Right, y \colon a}{\vlhy {}}}$ then we take $\Dw$ to be $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, xRy, u \le v, x \colon a, z \colon A \Rightarrow \Right, w \colon B, y \colon a}{\vlhy {}}}$.
+  	\vspace{2mm}
+
+  	For a proof $\D$ of height greater than 1:
+
+  	\begin{center}
+
+  		$\vlderivation{\vlin {$r$}{}{\B, \Left \Rightarrow \Right}{\vlpd {\Done}{}{\B', \Left' \Rightarrow \Right'}}}$
+
+  	\end{center}
+
+  	Then by induction hypothesis there exists a proof
+
+  	\begin{center}
+
+  		$\vlderivation {\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}$
+
+  	\end{center}
+
+  	Therefore, we have the proof
+
+  	\begin{center}
+
+  		$\Dw = \vlderivation {\vlin{}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}{\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}}$
+
+  	\end{center}
+
+  \end{proof}}
 \end{proof}
@@
   $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, x \le x'}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
+  \vlinf{\labrn{mon_a}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}}\Right}{
+    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
   $$
@@
 \begin{proof}
-  \todo{}
+  	\begin{smallequation*}
+  		\vlderivation{
+  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
+  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x''}{a}}{
+  					\vlhy{}
+  				}
+  			}
+  		}
+  		\reducesto
+  		\vlderivation{
+  		\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \futs{x}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
+  				\vlhy{}
+  			}}
+  	}
+  	\end{smallequation*}
+  	\todo{missing case}
+%  	\begin{smallequation*}
+%  		\vlderivation{
+%  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{
+%  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x'}{a}}{
+%  					\vlhy{}
+%  				}
+%  			}
+%  		}
+%  		\reducesto
+%  		\vlinf{\labrn{id}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{}
+%  		\qedhere
+%  	\end{smallequation*}
 \end{proof}
@@
 
-$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
+%$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
 
@@
 
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$ 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
-%		
-%		\todo{}
-		\smash{%\fbox{
-			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
-		}%}
-		%
-
-                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
-		\item\label{iii} $A$ is provable in $\labIKp$
-		%
-		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
 %We show that each rule from our system is sound.

### 2019-10-02 caleidoscope/caleidoscope.tex
fixed completeness

@@
   transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
+  follows. A proof of $\fm A$ is in fact a proof $\DD$ of the sequent
+  $\SEQ{\labels{z}{A}}$ for some label $\lb z$. If $\lb x$ and $\lb y$
+  are fresh labels, we can transform $\DD$ into a proof $\DD'$ of the
+  sequent $\futs xy, \accs yz \SEQ \labels{z}{A}$ by adding $\futs xy,
+  \accs yz$ to every line. We can now apply the $\rlabrn\BOX$-rule to
+  obtain a proof of $\SEQ \labels{x}{\BOX A}$.
+
+%% \begin{lemma}
+%% 	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
+%% \end{lemma}
+
+%% \begin{proof}
+
+%% 	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
+
+%% 	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
+%% 	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
+
+%% 	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
+
+%% %	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
+%% %	
+%% %	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
+%% %	Then using the \emph{weakening} rule, we have the following proof:
+%% %	
+%% %	\bigskip
+%% %	\begin{center}
+%% %		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
+%% %	\end{center}
+%% %
+
+%% \end{proof}
 

### 2019-10-02 caleidoscope/introduction.tex
reorganising folder

--- 2019-09-27 caleidoscope/caleidoscope.tex
@@
-\documentclass[a4paper]{article}
-
-%\usepackage{aiml18macro}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage[noxy]{virginialake}                        
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath,amsthm} 
-\usepackage{mathtools}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage{pgf}
-\usepackage{array}
-\usepackage[all]{xy}
-\usepackage{tikz}
-%\usepackage{hyperref}
-\usepackage{pgffor}
-
-	%%
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{fact}[theorem]{Fact}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-	%%
-\theoremstyle{definition}
-\newtheorem{observation}[theorem]{Observation}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-\newtheorem{remark}[theorem]{Remark}
-	%%
-
-\tikzset{
-	annotated cuboid/.pic={
-		\tikzset{%
-			every edge quotes/.append style={midway, auto},
-			/cuboid/.cd,
-			#1
-		}
-		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
-		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
-		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
-		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
-
-		;
-	},
-	/cuboid/.search also={/tikz},
-	/cuboid/.cd,
-	width/.store in=\cubex,
-	height/.store in=\cubey,
-	depth/.store in=\cubez,
-	units/.store in=\cubeunits,
-	scale/.store in=\cubescale,
-	width=10,
-	height=10,
-	depth=10,
-	units=cm,
-	scale=.1,
-}
-%tikz parameters
-
-\tikzstyle{point}=[circle,draw]
-\usetikzlibrary{arrows,automata,shapes,decorations.markings,
-	decorations.pathmorphing,backgrounds,fit,snakes,calc}
-
-%\usepackage{float}
-%\floatstyle{boxed} 
-%\restylefloat{figure}
-
-\usepackage{colonequals}
-\usepackage{bm}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Comments  
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
-\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
-
-%%% General
-\input{macros}
-\newcommand{\B}{\mathcal{R}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
-
-%%% Systems
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\ISfour}{\mathsf{IS4}}
-\newcommand*{\Sfour}{\mathsf{S4}}
-
-\newcommand{\fourax}{\mathsf{4}}
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-
-%%% Labelled sequents
-\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
-\newcommand{\SEQ}{\Longrightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\bullet}
-\newcommand*{\rel}{R}
-
-\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Equation environments
-\newdimen\mydisplayskip
-\mydisplayskip=.4\abovedisplayskip
-\newenvironment{smallequation}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
-\newenvironment{smallequation*}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
-\newenvironment{smallalign}
-{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
-\newenvironment{smallalign*}
-{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
-%
-\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
-\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
-%
-%
-\makeatletter
-\newbox\@conclbox
-\newdimen\@conclheight
-%
-%%%%%%
-\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
-\newcommand\vlderiibase[5]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%%
-\newcommand\vlderibase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlin{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%
-\newcommand\vlderidbase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlid{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-	%
-	\makeatother
-	%
-%%%General maths
-\newcommand*{\reducesto}{\quad{\leadsto}\quad}
-
-%%%%%%%%%%%%%%%%%
-
-%\newcommand{\height}[1]{\mathrm{ht}(#1)}
-\newcommand{\height}[1]{|#1|}
-
-\newcommand{\quand}{\quad\mbox{and}\quad}
-\newcommand{\qquand}{\qquad\mbox{and}\qquad}
-\newcommand{\quadcm}{\rlap{\quad,}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%The following line defines the page header consisting of the surnames of the authors.
-% Please include only the last names! 
-% Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
-
-\begin{document}
-
-%\begin{frontmatter}
-  \title{A fully labelled proof system for intuitionistic modal logics}
-  \author{Sonia Marin \and %}
-%  \todo{New university?}
-%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
-%    \author{
-      Marianela Morales %}
- \and
-% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
-% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
-%      \author{
-        Lutz Stra{\ss}burger }
-% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-
-  \maketitle
-
- \begin{abstract}
-
-   In this paper we present a labelled sequent system for
-   intuitionistic modal logics such that there is not only one, but
-   two relation symbols for the labels: one for the accessibility
-   relation associated with the Kripke semantics for normal modal logics and
-   one for the preorder relation associated with the Kripke semantics
-   for intuitionistic logic.
-   %%
-   This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logics. As a
-   consequence it can encompass a wider range of intuitionistic modal
-   logics than standard labelled systems.
-   %%
-   We also show an internal cut elimination proof for our system.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
-  \end{abstract}
-
-  %% \begin{keyword}
-  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  %% \end{keyword}
-% \end{frontmatter}
-
-  %\maketitle
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %to~\cite{Simpson} and~\cite{mar:str}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{Intuitionistic modal logics}\label{sec:intmod}
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
-%
-$$
-\fm A \coloncolonequals
-\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
-$$
-%
-
-Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
-Five axioms have been considered as primitives in the literature.
-An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
-%
-
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
-\begin{itemize}
-	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
-	\begin{equation*}
-	\label{eq:ik}%\hskip-2em
-	\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
-	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
-	&
-	\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
-	&
-	\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
-	\\
-	\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
-	&
-	\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
-	\end{array}
-	\end{equation*}
-\end{itemize}
-
-The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
-The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}.
-However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
-Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
-However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
-
-The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic.
-It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
-
-The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
-%
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-
-\begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
-	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
-	\begin{enumerate}
-		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
-			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
-		}
-		\end{equation*}
-
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
-			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
-		}
-		\end{equation*}
-	\end{enumerate}
-	%	
-\end{definition}
-
-\begin{definition}
-	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
-	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
-\end{definition}
-
-We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:
-
-\begin{equation}\label{eq:kripke}
-	\begin{array}{rcl}
-	%\parbox{30em}{%
-
-		\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
-
-		\M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.
-
-	\end{array}
-\end{equation}
-Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
-%
-We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
-
-From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
-	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
-\end{proposition}
-
-\begin{definition}
-	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
-	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
-\end{definition}
-
-%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%
-%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-
-Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.
-
-\begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
-	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
-
-%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
-
-\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
-\begin{theorem}[\cite{plotkin:stirling:86}]
-	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
-
-	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
-
-\end{theorem}
-
-% we would like to consider special restrictions on these bi-relational frames.
-For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%\section{Intuitionistic modal logics}\label{sec:intmod}
-%
-%	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%	%
-%	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
-%	%
-%	$$
-%	A \coloncolonequals
-%	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
-%	$$
-%	%
-%        \lutz{why do we have $\TOP$?}
-%	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
-%
-%Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%%
-%Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
-%%
-%
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-%%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
-%%
-%It is obtained from intuitionistic propositional logic by adding:
-%\begin{itemize}
-%\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
-%\item the following five variants of the \emph{distributivity axiom}:
-%\begin{equation*}
-%\label{eq:ik}%\hskip-2em
-%\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
-%\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
-%&
-%\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
-%&
-%\kax[5]\colon&\DIA\BOT\IMP\BOT
-%\\
-%\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
-%&
-%\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
-%\end{array}
-%\end{equation*}
-%\end{itemize}
-%
-%The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
-%%
-%It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-%
-%\begin{definition}
-%	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
-%%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-%	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
-%	\begin{enumerate}
-%		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]_R  & v' \\
-%				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
-%			}
-%			\end{equation*}
-%		
-%		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]^R & v' \\
-%				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
-%			}
-%			\end{equation*}
-%	\end{enumerate}
-%%	
-%\end{definition}
-%
-%\begin{definition}
-%	\label{model}
-%	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-%	if $w \le w'$ then $V(w)\subseteq V(w')$.
-%\end{definition}
-%
-%We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
-%%
-%Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-%\begin{equation}
-%  \label{eq:kripke}
-%  \parbox{30em}{%
-%  $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
-%
-%$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
-%
-%$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
-%
-%$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
-%
-%$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
-%
-%%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-%}
-%\end{equation}
-%\todo{fix typography}
-%
-%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
-%
-%From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-%\begin{proposition}(Monotonicity) 
-%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
-%\end{proposition}
-%
-%
-%
-%\begin{definition}
-%	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-%%
-%	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
-%\end{definition}
-%
-%
-%
-%%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%%
-%%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-%
-%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
-%
-%\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-%	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{The system}\label{sec:system}
-
-In this section we present our fully labelled sequent proof system
-for intuitionistic modal logics. The starting point is the notion of a
-\emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
-x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
-at world $\lb x$. A \emph{relation atom} is either an expression
-$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
-intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. This is enough to define the notion of
-\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
-multi-sets of labelled formulas, all written as list, separated by commas.
-
-\begin{figure}[!t]
-  \begin{center}
-	\fbox{
-%	\begin{minipage}{.95\textwidth}
-	\begin{tabular}{c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-		&
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		%\quad
-		%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-		\\\\
-		$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-		\\\\
-		$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
-% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
- 		}
-		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-		\\\\
-		$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-		\\
-		\multicolumn{2}{c}{
-		$\mbox{\hbox to .9\linewidth{\dotfill}}$
-		}
-		\\
-		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-		&
-		$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-		}
-	\end{tabular}		
-%\end{minipage}
-}		
-  \end{center}
-  \caption{System $\labIKp$}
-	\label{fig:labIKp}
-\end{figure}
-
-Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
-We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
-\begin{equation}
-  \label{eq:nomon}
-  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
-  \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
-  \quad
-  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
-\end{equation}
-that are not sufficient for a complete system, and we will see below
-why. Before, let us first look at the rules $\rlabrn\IMP$ and
-$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
-of~\cite{str:2017maehara}, these are the two rules that force
-single-conclusion. This is the reason why in our system we need the
-$\le$ in the relational atoms; we need to go to the future of the
-current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
-connectives $\IMP$ and $\BOX$ are the ones that need the
-future-relation $\le$. This relation is reflexive and transitive. In
-order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.
-
-Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
-system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
-%
-However, these two rule create new labels, and in order to be
-complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
-\begin{equation}
-  \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
-  \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
-\end{equation}
-Since this rule is a form of contraction, it would cause the same
-problems as contraction in a cut elimination proof. Hence, it is
-preferable to have a system in which this rule is admissible. This is
-the reason why we have monotonicity incorporated in the rules
-$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. Then, not only
-$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
-shown on the right in~\eqref{eq:mono} above is admissible.
-
-\begin{proposition}
-  \label{prop:mon-adm}
-  The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$.
-\end{proposition}
-
-One can prove this proposition in the same way as one usually proves
-admissibity of contraction in a sequent calculus, by induction on the
-height of the derivation, which in fact would yield a stronger result,
-namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
-  preserving} admissible for $\labIKp$. However, we do not need this
-result in this paper, and therefore we leave it as an exercise to the
-reader. Nonetheless, we will give a short proof of
-Proposition~\ref{prop:mon-adm} at the end of this section.
-
-Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.
-
-\begin{proposition}
-  \label{prop:id}
-	The following general idenity axiom~
-	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
-        ~is admissible for $\labIKp$. 
-\end{proposition}
-
-\begin{proof}
-	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
-	\begin{itemize}
-		%% \item Atomic case
-		%% \begin{smallequation*}
-		%% 	%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% 	%\reducesto
-		%% 	\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% \end{smallequation*}
-		\item $\fm{A \AND B}$
-		%\begin{smallequation*}
-		%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
-		%	\reducesto
-		%\end{smallequation*}
-		\begin{smallequation*}
-			\vlderivation{
-				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
-					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
-							\vlhy{}
-						}
-					}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-	\item $\fm{A \OR B}$
-	%\begin{smallequation*}
-	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
-	%	\reducesto
-	%\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
-						\vlhy{}
-					}
-				}
-			}{
-			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{A \IMP B}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-								\vlhy{}
-							}
-						}
-					}{
-					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{\BOX A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-
-	\item $\fm{\DIA A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-        \qedhere
-	\end{itemize}
-\end{proof}
-
-In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
-\begin{equation}
-  \label{eq:cut}
-  \vliiinf{\labrn{cut}}{}{
-    \lseq\B\Left\Right}{
-    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
-    \lseq\B{\Left,\labels{z}{C}}{\Right}}
-\end{equation}
-Then we can summarize soundness and completeness, and cut
-admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$. 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
-		\item\label{iii} $A$ is provable in $\labIKp$.
-		%
-		\item\label{iv} $A$ is valid in every birelational frame. %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-The proof of this theorem is the topic of the following sections. The
-equivalence of \ref{i} and \ref{iv} has already been stated in
-Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
-\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implication~\ref{ii}$\implies$\ref{iii} is shown in
-Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
-
-Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
-
-\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
-  The rule $\llabrn{mon}$ can be derived using the general identity and cut:
-  \begin{smallequation*}
-    \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
-          \vlhy{}}}{
-        \vlhy{\quad}}{
-        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
-    }
-  \end{smallequation*}
-  And both these rules are admissible by Proposition~\ref{prop:id} and
-  Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
-  similar.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-In this section we show our system at work, as most of the section
-consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
-
-\begin{theorem}\label{thm:completeness}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{remark}
-  We have seem already in the proof of Proposition~\ref{prop:id} the
-  need of the rule $\rn{F_2}$. In the following proof of
-  Theorem~\ref{thm:completeness} we also see the need of the rules
-  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
-  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
-  \begin{itemize}
-  \item $\kax[1]$:
-    $$
-    \vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
-												{\vlhy {}}}}}}}}}}
-    }
-    $$
-    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-  \item $\kax[2]$:
-    $$
-    \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-									{\vlhy {}}}								}}}}}}
-    }
-    $$
-    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-  \item $\kax[3]$:
-    $$
-    \vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
-				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-									{\vlhy {}}}}}}}}
-		}
-    $$
-  \item $\kax[4]$:
-    $$
-\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-					{\vlin {\color{red}\rn{trans}}
-						{}
-						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-											{\vlhy {}}}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-											{\vlhy {}}}}}}}}}}}
-}
-$$
-where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-\item $\kax[5]$:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
-				{\vlhy {}}}}
-  }
-  $$
-  \end{itemize}
-  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
-			{\vlin {\color{red}\rn{refl}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-				{\vlin {\rn{id}}
-					{}
-					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-					{\vlhy {}}}}}
-  }
-  $$
-
-  Finally, we have to show how the rules of modus ponens and
-  necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necessitation, we can
-  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
-
-  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Soundness}\label{sec:soundness}
-
-In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
-of our system $\labIKp$ is sound. We want to prove that for all model
-$\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
-\end{definition}
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \Rightarrow \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \Rightarrow \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$.
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$.
-We say that $\M \not \Vdash \B, \Gamma \Rightarrow \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \Rightarrow \Delta$.
-\end{definition}
-
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$:
-
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \Rightarrow \Right$.}
-	\end{center}
-
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, x \le y, yRz,\Left,\break \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $y, z \in W$ such that $\futs xy$ and $\accs yz$, then $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
-
-\marianela{working on this}
-	\marianela{
-	Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y,\break yRz, \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular, from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0} \Vdash \labels{z}{A}$.
-Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
-Then, the rule $\llabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\BOX$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$, i.e.
-$\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{\BOX A}$, which is the same as $\M_{0} \Vdash \vlan (\B,\Left)$ and  $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$.
-From $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$, we have that $\M_{0} \not \Vdash \Right$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}$.
-Following the semantic definition of $\BOX$, there exists worlds $y, z$ in $\M_{0}$, such that $x \le y, yRz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Therefore, $\M_{0} \not \Vdash premise$, i.e.
-$\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
-Then, the rule $\rlabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\IMP$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{A \IMP B}$, i.e., in particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $y$ such that $x \le y$ and $\M_{0} \Vdash \labels{y}{A}$ but $\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, x \le y, \Left, \labels{y}{A} \Rightarrow \labels{y}{B}$.
-Finally, the rule $\rlabrn\IMP$ is sound.}
-\end{itemize}
-
-The other cases are similar.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cut Admissibility}\label{sec:cut-elim}
-
-\todo{I do not know how to organize this section. First cut elimination proof? (lemma before or after?) Then mon is admissible using cut proof?}
-
-\lutz{some start below}
-
-In this section we are going to prove the admissibility of cut for $\labIKp$.
-
-\begin{theorem}
-  \label{thm:cut-adm}
-  The rule $\labrn{cut}$ is admissible for $\labIKp$.
-\end{theorem}
-
-This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
-
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is \todo{finish}
-
-We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if \todo{...}
-
-The following two lemmas are standard.
-
-\begin{lemma}
-  \label{lem:weak-adm}
-  The weakening rule
-  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:inv}
-  The rules ..... are height-preserving invertible in
-  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
-  height-preserving invertible for the right premise.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma looks like a special case of
-Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using cut as we
-need it to eliminate the cut.
-
-\begin{lemma}
-  The atomic version of $\llabrn{mon}$
-  $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, x \le x'}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
-  $$
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma is the core of our cut elimination proof.
-
-\begin{lemma}
-  \label{lem:reduction}
-  Given a derivation of shape
-  $$
-  \vlderivation{
-    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
-      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
-      \vlhy{}}{
-      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
-  $$
-  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
-  derivation of ${\lseq\B\Left\Right}$
-\end{lemma}
-
-$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
-
-Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
-
-For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
-
-\begin{proof}
-
-	By induction on number of cuts + (rank,height) of the left-most top-most cut.
-
-	\textbf{Commutative cases:}\label{commutative-cases}
-
-	\begin{smallequation*}
-		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
-				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-			}{
-			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
-%
-If it does we rewrite it with a fresh variable $v$ first.
-
-%\begin{smallequation*}
-%	\reducesto
-%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-%			}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%			}
-%		}
-%\end{smallequation*}
-%
-%\begin{smallalign*}&
-%	\text{with } \DD_4 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-%		}
-%	}
-%	\\&
-%	\text{and } \DD_5 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}
-%	}
-%\end{smallalign*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
-			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
-		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
-}
-\reducesto
-%	\end{smallequation*}
-%	
-%	\begin{smallequation*}
-\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
-		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-}
-}
-\end{smallequation*}
-
-\textbf{Key cases:}\label{key-cases}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-			\vlhy{}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
-}
-\reducesto
-\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
-	}{
-	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-		\vlhy{}	
-	}
-}
-\reducesto
-\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
-		}
-	}{
-	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}{
-	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
-				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
-			}
-			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
-	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
-}{
-\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
-		}
-	}{
-	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-	}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
-		%			}{
-		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
-		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
-		%					\vlhy{}
-		%					}
-		%				}
-		%			}
-	}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-		}
-	}{
-	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
-	}	
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
-		}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
-		}
-	}
-}{
-\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
-}
-\end{smallequation*}
-\end{proof}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-
-	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
-
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-	In each case, we reason by induction on the height of $\DD$.
-
-	\begin{itemize}
-		\item $\llabrn\IMP$:
-		For a proof of height $1$, it is straightforward.
-		%
-		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-		%
-		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-		First let us fix a given index $y$ that does not appear in $\DD$.
-
-		If we start with a proof
-		\begin{smallequation*}
-			\DD = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-				}	
-			}
-		\end{smallequation*}
-
-		Then by induction hypothesis there exists a proof 
-		\begin{smallequation*}
-			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-		Therefore, we have the proof
-		\begin{smallequation*}
-			\DD^{\invr{\llabrn\IMP}} = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-				}
-			}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD$.
-
-		If we start with a proof 
-		\begin{smallequation*}
-			\vlderivation{
-				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-				}{
-				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-			}
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-	%
-	\item $\llabrn\DIA$:
-
-	If we start with a proof
-	\begin{smallequation*}
-		\DD = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-			}	
-		}
-	\end{smallequation*}
-
-	Then by induction hypothesis there exists a proof 
-	\begin{smallequation*}
-		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD'$.
-
-	Therefore, we have the proof
-	\begin{smallequation*}
-		\DD^{\invr{\llabrn\DIA}} = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-			}
-		}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-	If we start with a proof 
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-			}	
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
-
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
-%
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
-%
-
-\begin{definition}
-A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
-In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
-On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these are presented in the system $\labIKp$ as follows:
-
-\begin{center}
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				}
-				\\\\
-				\hspace{15mm}
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
-
-\end{center}
-
-\bigskip
-
-A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
-
-\begin{itemize}
-	\item Rule $\rn{F1}$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-			\\\\
-			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-			\\\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\hspace{8mm}
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-\end{center}
-
-You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
-
-\begin{itemize}
-	\item Rule $\llabrn\AND$:
-
-	%The system $\labIKp$ presents the next rule for the conjunction left:
-
-	%\begin{center}
-	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-	%\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\rlabrn\OR$:
-
-	Let the rule presented in $\labIKp$ for disjunction right be as follows:
-
-	\begin{center}
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-	\end{center}
-
-	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\\\\
-			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
-			\\\\
-			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-			\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-A more detailed explanation for some rules is below:
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$.
-	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
-
-\bigskip
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\multicolumn{2}{c}{
-				\hspace{9mm}
-				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-			}
-			\\
-			\multicolumn{2}{c}{
-				\hspace{10mm}
-				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-			}
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-The rule for implication right is explained below:
-
-\begin{itemize}
-	\item Rule $\rlabrn\IMP$.
-	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
-\end{itemize}
-
-\section{A complete and sound system for intuitionistic modal logics}
-%
-Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
-%
-Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
-%
-Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$ 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
-%		
-%		\todo{}
-		\smash{%\fbox{
-			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
-		}%}
-		%
-
-                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
-		\item\label{iii} $A$ is provable in $\labIKp$
-		%
-		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-%We show that each rule from our system is sound.
-%
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-The proof is a careful adaptation of standard techniques.
-%
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
-As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
-%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
-\bigskip
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlhy {}
-										}
-									}
-								}
-							}{
-%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-										\vlhy {\qquad\vdots\qquad}
-%										}
-%									}
-%								}
-%							}
-						}
-					}
-				}
-			}
-		}
-	}
-}$
-}$$
-%\end{example}
-
-%\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-}
-$
-}
-$$
-%\end{example}
-
-\begin{lemma}\label{lem:weak}\hbox{}\quad
-	\begin{enumerate}
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
-
-	%	\item 
-	%	If there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-	%	then there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Standard.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}\label{sec:ext}
-
-The main goal of this section is to generate stronger logics adding new axioms to our system.
-We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
-
-In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
-%
-These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
-
-Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-\bigskip
-
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
-why??}
-
-Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
-
-$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
-
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-\begin{figure}[h]
-	\begin{center}
-		$
-		\xymatrix{
-			& u' \ar@{.>}[ddr]^{R^l} \\
-			& u \ar@{.>}[u]^{\le} \\
-			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
-			& v \ar@{.>}[ur]_{R^n}
-		}
-		$
-	\end{center}
-	\label{fig:gklmn}
-	\caption{$\agklmn$ axiom for intuitionistic case}
-\end{figure}
-
-Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
-
-\bigskip
-
-\begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
-\end{center}
-
-\bigskip
-
-We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
-
-\begin{theorem}
-	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
-\end{theorem}
-
-\begin{proof}
-	\begin{center}
-		\scalebox{0.93}{
-			$\vlderivation {\vlin {\rlabrn{\IMP}}
-				{y \mbox{ fresh}}
-				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\rlabrn{\BOX}}
-					{z, w \mbox{ fresh} }
-					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
-					{\vlin {\llabrn{\DIA}}
-						{u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
-						{\vlin {\rn{F_2}}
-							{t \mbox{ fresh}}
-							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-							{\vlin {\gklmn}
-								{t', j \mbox{ fresh}}
-								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-								{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-									{\vlin {\rn{trans}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-										{\vlin {\llabrn{\BOX}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-											{\vlin {\rn{refl}}
-												{}
-												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-												{\vlin {\rn{id}}
-													{}
-													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-													{\vlhy {}}}}}}}}}}}}$}
-	\end{center}
-\end{proof}
-
-In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
-
-\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
-	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
-	\end{enumerate}
-	%\textbf{Probably F2g???}
-\end{lemma}
-
-Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
-
-\bibliographystyle{alpha}
-\bibliography{references}
-
-\end{document}
-
-%\begin{figure}[h]
-%\begin{center}
-%$\vlderivation{\vlinf{\id}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\B, \Left, x\colon \bot \SEQ z\colon A}{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\B, \Left \SEQ x \colon \top}{}}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\andleflab}{}{\B,\Left, x \colon \vls(A.B) \SEQ z \colon C}{\B, \Left, x\colon \vls(A.B,\labels{x}{A}, \labels{x}{B} \SEQ z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\B,\Left \SEQ x \colon \vls(A.B)}{\B, \Left \SEQ \labels{x}{A}}{\B, \Left \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%$\vliinf{\orleflab}{}{\B, \Left, x \colon \vls[A.B] \SEQ  \colon C}{\B, \Left, x \colon \vls[A.B], \labels{x}{A} \SEQ z \colon C}{\B, \Left, x \colon \vls[A.B], x   \colon   B \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\orriglabo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x   \colon   A}$
-%\hspace{7mm}$\vlinf{\orriglabt}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x \colon  B}$
-%
-%\vspace{2mm}
-%
-%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \IMP B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \IMP B, \labels{x}{B} \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \IMP B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%
-% $\vlderivation {\vlinf{\bllab}{}{\B, x \rel y, \Left x \colon \BOX A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z \colon B}}$
-%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\B, \Left \SEQ x \colon \BOX A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\dllab}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \DIA A, y \colon A \SEQ z \colon B}$
-%\hspace{5mm}$\vlinf{\drlab}{}{\B, x \rel y, \Left,  \SEQ x \colon \DIA A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\end{center}
-%\caption{System labIK}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	
-%	\begin{center}
-%		
-%		$\vlderivation { \vlin {\ids}{}{\B, \Left, \labels{x}{A} \SEQ x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\B, \Left, x \colon \bot \SEQ z\colon A}{\vlhy {}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vlin {\svlef}{}{\B, \Left, x \colon \vls(A.B) \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\B, \Left, \SEQ x \colon \vls(A.B)}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		
-%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
-%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
-%		
-%	\end{center}
-%	
-%	\caption{System $\lab\IK$}
-%	\label{fig:labIK}
-%\end{figure}
-%
-%\begin{theorem}[Simpson~\cite{Simpson}]
-%	\label{thm:simpson-sound-compl}
-%	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	\small
-%	\centering
-%
-%		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
-%		\hspace{5mm}
-%		$\vlinf{\llabrn\bot}{}{\B, \Left, x\colon \bot \SEQ \Right}{}$
-%		\hspace{5mm}
-%		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, x \colon \top}{}$
-%%		
-%%		\vspace{4mm}
-%		\\[1.5ex]
-%%		
-%		$\vlinf{\llabrn\AND}{}{\B,\Left, x \colon \vls(A.B) \SEQ \Right}{\conjlef}$
-%		\hspace{7mm}
-%		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ \Right}{\B, \Left, x   \colon   A \SEQ \Right}{\B, \Left, x   \colon   B \SEQ \Right}$
-%		\hspace{7mm}
-%		$\vlinf{\sorig}{}{\B, \Left \SEQ \Right, x \colon \vls[A.B]}{\B, \Left \SEQ \Right, x   \colon   A, x   \colon   B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \IMP B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlderivation {\vlinf{\sbl}{}{\B, \Left, x \le y, y \rel z, x \colon \BOX A \SEQ \Right}{\B,\Left, x \le y, y \rel z, x \colon \BOX A, z \colon A \SEQ \Right}}$
-%		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \SEQ \Right, x \colon \BOX A}{\B, \Left, x \le y, y \rel z \SEQ \Right, z \colon A}$
-%		
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ \Right}{\B, \Left, x \rel y, y \colon A \SEQ \Right}$
-%		\hspace{5mm}$\vlinf{\sdr}{}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A, y \colon A}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\refl}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-%		\hspace{7mm} $\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\rn{F_1}}{\text{\footnotesize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-%		%
-%		$\vlinf{\rn{F_2}}{\text{\footnotesize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-%	
-%	\caption{System $\labIKp$}
-%	\label{fig:labHIK}
-%\end{figure}

### 2019-10-02 caleidoscope/preliminaries.tex
reorganising folder

--- 2019-09-27 caleidoscope/caleidoscope.tex
@@
-\documentclass[a4paper]{article}
-
-%\usepackage{aiml18macro}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage[noxy]{virginialake}                        
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath,amsthm} 
-\usepackage{mathtools}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage{pgf}
-\usepackage{array}
-\usepackage[all]{xy}
-\usepackage{tikz}
-%\usepackage{hyperref}
-\usepackage{pgffor}
-
-	%%
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{fact}[theorem]{Fact}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-	%%
-\theoremstyle{definition}
-\newtheorem{observation}[theorem]{Observation}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-\newtheorem{remark}[theorem]{Remark}
-	%%
-
-\tikzset{
-	annotated cuboid/.pic={
-		\tikzset{%
-			every edge quotes/.append style={midway, auto},
-			/cuboid/.cd,
-			#1
-		}
-		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
-		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
-		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
-		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
-
-		;
-	},
-	/cuboid/.search also={/tikz},
-	/cuboid/.cd,
-	width/.store in=\cubex,
-	height/.store in=\cubey,
-	depth/.store in=\cubez,
-	units/.store in=\cubeunits,
-	scale/.store in=\cubescale,
-	width=10,
-	height=10,
-	depth=10,
-	units=cm,
-	scale=.1,
-}
-%tikz parameters
-
-\tikzstyle{point}=[circle,draw]
-\usetikzlibrary{arrows,automata,shapes,decorations.markings,
-	decorations.pathmorphing,backgrounds,fit,snakes,calc}
-
-%\usepackage{float}
-%\floatstyle{boxed} 
-%\restylefloat{figure}
-
-\usepackage{colonequals}
-\usepackage{bm}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Comments  
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
-\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
-
-%%% General
-\input{macros}
-\newcommand{\B}{\mathcal{R}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
-
-%%% Systems
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\ISfour}{\mathsf{IS4}}
-\newcommand*{\Sfour}{\mathsf{S4}}
-
-\newcommand{\fourax}{\mathsf{4}}
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-
-%%% Labelled sequents
-\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
-\newcommand{\SEQ}{\Longrightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\bullet}
-\newcommand*{\rel}{R}
-
-\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Equation environments
-\newdimen\mydisplayskip
-\mydisplayskip=.4\abovedisplayskip
-\newenvironment{smallequation}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
-\newenvironment{smallequation*}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
-\newenvironment{smallalign}
-{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
-\newenvironment{smallalign*}
-{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
-%
-\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
-\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
-%
-%
-\makeatletter
-\newbox\@conclbox
-\newdimen\@conclheight
-%
-%%%%%%
-\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
-\newcommand\vlderiibase[5]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%%
-\newcommand\vlderibase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlin{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%
-\newcommand\vlderidbase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlid{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-	%
-	\makeatother
-	%
-%%%General maths
-\newcommand*{\reducesto}{\quad{\leadsto}\quad}
-
-%%%%%%%%%%%%%%%%%
-
-%\newcommand{\height}[1]{\mathrm{ht}(#1)}
-\newcommand{\height}[1]{|#1|}
-
-\newcommand{\quand}{\quad\mbox{and}\quad}
-\newcommand{\qquand}{\qquad\mbox{and}\qquad}
-\newcommand{\quadcm}{\rlap{\quad,}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%The following line defines the page header consisting of the surnames of the authors.
-% Please include only the last names! 
-% Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
-
-\begin{document}
-
-%\begin{frontmatter}
-  \title{A fully labelled proof system for intuitionistic modal logics}
-  \author{Sonia Marin \and %}
-%  \todo{New university?}
-%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
-%    \author{
-      Marianela Morales %}
- \and
-% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
-% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
-%      \author{
-        Lutz Stra{\ss}burger }
-% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-
-  \maketitle
-
- \begin{abstract}
-
-   In this paper we present a labelled sequent system for
-   intuitionistic modal logics such that there is not only one, but
-   two relation symbols for the labels: one for the accessibility
-   relation associated with the Kripke semantics for normal modal logics and
-   one for the preorder relation associated with the Kripke semantics
-   for intuitionistic logic.
-   %%
-   This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logics. As a
-   consequence it can encompass a wider range of intuitionistic modal
-   logics than standard labelled systems.
-   %%
-   We also show an internal cut elimination proof for our system.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
-  \end{abstract}
-
-  %% \begin{keyword}
-  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  %% \end{keyword}
-% \end{frontmatter}
-
-  %\maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{get bib-file right}
-
-\section{Introduction}\label{sec:intro}
-
-Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
-\emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive systems to a broad range
-of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
-labelled calculi have the advantage of being more uniform and being able to 
-accommode more logics.
-
-Standard labelled sequent calculi attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally admit so called
-\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
-binary relation symbol. These calculi work best for logics with
-standard Kripke semantics, as in this case the relation $\rel$ is used
-to encode the accessibility relation in the Kripke models, and the
-frame conditions corresponding to the desired logic can be directly
-encoded as inference rules. Prominent examples are classical modal
-logics and intuitionistic propositional logic, where, e.g., the frame
-condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
-inference rule
-\begin{equation}
-  \label{eq:Rtrans}
-  \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
-\end{equation}
-where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas.
-
-However,
-in this paper we are concerned with \emph{intuitionistic modal
-  logics}, whose Kripke semantics is based on \emph{birelational}
-frames, i.e., they have two binary relations instead of one: one
-relation $R$ that corresponds to the accessibility relation in
-ordinary Kripke frames for modal logics, and a relation $\le$ that
-corresponds to the future relation in ordinary Kripke frames for
-intuitionistic logic. Consequently, standard labelled systems for
-these logics have certain shortcomings:
-\begin{enumerate}
-\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
-  versions of the $\fourax$-axiom
-  \begin{equation}
-    \label{eq:4ax}
-    \fm{\BOX A\IMP \BOX\BOX A}
-    \qquand
-    \fm{\DIA\DIA A\IMP\DIA A}
-    \quadcm
-  \end{equation}
-  as they are equivalent in classical
-  modal logic. However, in intuitionistic modal logic they are not
-  equivalent, and even though the logic $\ISfour$, i.e., the
-  intuitionistic version of the modal logic $\Sfour$, contains both
-  axioms, they can be added independently to the logic $\IK$ (the
-  intuitionistic version of $\K$). However, the proof theory of these
-  new logics has not been studied before, as no existing labelled (or
-  label-free) proof system can handle them, even though the
-  corresponding frame conditions
-  \begin{equation}
-    \label{eq:4frame}
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-    \quand
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-    \;,
-  \end{equation}
-  respectively, have already been studied
-  in~\cite{plotkin:stirling:86}.
-  \item The correspondence between the syntax and the semantics is not
-  as clean as one would expect. As only the $R$-relation (and not the
-  $\le$-relation) of the frame is visible in an ordinary labelled
-  sequent, we only have that a sequent $\Gamma$ is provable if and
-  only if is is valid in all \emph{graph-consistent}\footnote{This
-    means that every layer in the model can be lifted to any future of
-    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
-  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
-\end{enumerate}
-In order to address these two issues we propose here to extend the
-notion of labelled sequent by also allowing relational atoms of the
-form $\futs xy$. Consequently, we can easily translate the frame
-conditions in~\eqref{eq:4frame} into inference rules:
-\begin{equation}
-  \label{eq:4rules}
-  \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-     \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
-  \qquand
-  \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
-\end{equation}
-This allows us to define cut-free deductive systems for a wide range
-of logics that could not be treated before.  Furthermore, the relation
-between syntax and semantics is as one would expect: A sequent is
-provable in our system if and only if it is valid in all models.
-
-Besides that, there is another pleasant observation to make about our
-system. Ordinary labelled sequent systems for intuitionistic modal
-logic are single-conclusion~\cite{simpson:phd}. The same is true for
-the corresponding nested sequent
-systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
-Maehara style multiple-conclusion systems in nested
-sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
-labelled sequents. However, also in these systems there are rules
-($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
-premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
-intuitionistic logic. Our system eliminates this
-discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.
-
-\medskip
-
-This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
-Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
-The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
-
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
-
-\section*{Introduction(old version, to be deleted)}
-\todo{We should work on the introduction}
-
-One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.
-
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
-%
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as
-used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
-Negri~\cite{Negri}. 
-%
-These formalisms make explicit use not only of
-labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
-%
-In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
-logics) and the \emph{preorder relation} (for intuitionistic
-logic), using the full power of the bi-relational semantics for
-intuitionistic modal logics,
-and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.
-
-\todo{Simpson does not have internal cut-elimination}
-
-\sonia{
-  \begin{itemize}
-  \item internal vs externl calculi
-  \item extesion to axioms are truly intuitionistic (not just the
-    classical versions as in Simpson style)
-  \item connection with semantics compared to graph homomorphism
-    restiction in Simpson and ``indexed nested systems''
-  \end{itemize}
-}
-
-\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
-  \begin{itemize}
-  \item what we do:
-    \begin{itemize}
-    \item first systems (nested and labelled) for intuitionistic modal
-      logic where ``single conclusion'', i.e., only one formula on the
-      right.
-    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
-    \item Still rules that forced single formula on the right (white implication and white box)
-    \item by allowing both relations of the model in the proof system
-      we go to genuinely multiple conclusion: never ever a formula on
-      the right has to be deleted during proof search.
-    \end{itemize}
-  \item why we do it: 
-    \begin{itemize}
-    \item getting things right: labelled systems for classical modal
-      logics, or plain propositional intuiionistic logic have one
-      binary relation, which is exactly the relation of the standard
-      Kripke semantics. The standard Kripke semantics for
-      intuitionistic modal logic is birelational, with a strong
-      connectiion between the two binary relations. A clean labelled
-      system for these logics should incorporate both relations.
-    \item We get new logics.  In the standard nested sequent
-      or labelled sequent system for intuitionistic modal logic we
-      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
-      but here we can have them separtely.
-    \end{itemize}
-  \item how we do it:
-    \begin{itemize}
-    \item We start from the Maehara nested sequent system (which can
-      be translated straightforwardly into a labelled system with one
-      relation $R$.
-    \item the rules for $\AND$ and $\OR$ are trivial and as expected
-      they can be presented such that they are invertible on the left
-      and the right, they do not concern the relations $R$ and $\le$. 
-    \item So should be the rules for $\IMP$-left and $\BOX$-left and
-      identity, but there is a subtlety; see below...
-    \item the rules for $\DIA$ are also straightforward, as they
-      concern only $R$ but not $\le$.
-    \item The rules $\BOX$-right and $\IMP$-right are the ones that
-      force single conclusion in the Maehara system. This means that
-      here they create a future, using the relation $\le$.
-    \item In order to make everything work together, this forces us to
-      have reflexivity and transitivity of $\le$, explicely as rules
-      in the system, and have rules for the F1 and F2 conditions
-      making the relations $R$ and $\le$ go together.
-    \item As a consequence we also need a rule realizing monotonicity
-      for the formulas on the right.
-    \item However, we designed the system such that monotonicity is
-      admisible by encorporating it into the rules for identity,
-      $\IMP$-left and $\BOX$-left.
-    \end{itemize}
-  \end{itemize}
-}
-%
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{The system}\label{sec:system}
-
-In this section we present our fully labelled sequent proof system
-for intuitionistic modal logics. The starting point is the notion of a
-\emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
-x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
-at world $\lb x$. A \emph{relation atom} is either an expression
-$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
-intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. This is enough to define the notion of
-\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
-multi-sets of labelled formulas, all written as list, separated by commas.
-
-\begin{figure}[!t]
-  \begin{center}
-	\fbox{
-%	\begin{minipage}{.95\textwidth}
-	\begin{tabular}{c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-		&
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		%\quad
-		%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-		\\\\
-		$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-		\\\\
-		$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
-% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
- 		}
-		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-		\\\\
-		$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-		\\
-		\multicolumn{2}{c}{
-		$\mbox{\hbox to .9\linewidth{\dotfill}}$
-		}
-		\\
-		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-		&
-		$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-		}
-	\end{tabular}		
-%\end{minipage}
-}		
-  \end{center}
-  \caption{System $\labIKp$}
-	\label{fig:labIKp}
-\end{figure}
-
-Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
-We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
-\begin{equation}
-  \label{eq:nomon}
-  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
-  \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
-  \quad
-  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
-\end{equation}
-that are not sufficient for a complete system, and we will see below
-why. Before, let us first look at the rules $\rlabrn\IMP$ and
-$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
-of~\cite{str:2017maehara}, these are the two rules that force
-single-conclusion. This is the reason why in our system we need the
-$\le$ in the relational atoms; we need to go to the future of the
-current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
-connectives $\IMP$ and $\BOX$ are the ones that need the
-future-relation $\le$. This relation is reflexive and transitive. In
-order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.
-
-Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
-system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
-%
-However, these two rule create new labels, and in order to be
-complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
-\begin{equation}
-  \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
-  \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
-\end{equation}
-Since this rule is a form of contraction, it would cause the same
-problems as contraction in a cut elimination proof. Hence, it is
-preferable to have a system in which this rule is admissible. This is
-the reason why we have monotonicity incorporated in the rules
-$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. Then, not only
-$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
-shown on the right in~\eqref{eq:mono} above is admissible.
-
-\begin{proposition}
-  \label{prop:mon-adm}
-  The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$.
-\end{proposition}
-
-One can prove this proposition in the same way as one usually proves
-admissibity of contraction in a sequent calculus, by induction on the
-height of the derivation, which in fact would yield a stronger result,
-namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
-  preserving} admissible for $\labIKp$. However, we do not need this
-result in this paper, and therefore we leave it as an exercise to the
-reader. Nonetheless, we will give a short proof of
-Proposition~\ref{prop:mon-adm} at the end of this section.
-
-Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.
-
-\begin{proposition}
-  \label{prop:id}
-	The following general idenity axiom~
-	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
-        ~is admissible for $\labIKp$. 
-\end{proposition}
-
-\begin{proof}
-	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
-	\begin{itemize}
-		%% \item Atomic case
-		%% \begin{smallequation*}
-		%% 	%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% 	%\reducesto
-		%% 	\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% \end{smallequation*}
-		\item $\fm{A \AND B}$
-		%\begin{smallequation*}
-		%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
-		%	\reducesto
-		%\end{smallequation*}
-		\begin{smallequation*}
-			\vlderivation{
-				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
-					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
-							\vlhy{}
-						}
-					}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-	\item $\fm{A \OR B}$
-	%\begin{smallequation*}
-	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
-	%	\reducesto
-	%\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
-						\vlhy{}
-					}
-				}
-			}{
-			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{A \IMP B}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-								\vlhy{}
-							}
-						}
-					}{
-					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{\BOX A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-
-	\item $\fm{\DIA A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-        \qedhere
-	\end{itemize}
-\end{proof}
-
-In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
-\begin{equation}
-  \label{eq:cut}
-  \vliiinf{\labrn{cut}}{}{
-    \lseq\B\Left\Right}{
-    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
-    \lseq\B{\Left,\labels{z}{C}}{\Right}}
-\end{equation}
-Then we can summarize soundness and completeness, and cut
-admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$. 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
-		\item\label{iii} $A$ is provable in $\labIKp$.
-		%
-		\item\label{iv} $A$ is valid in every birelational frame. %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-The proof of this theorem is the topic of the following sections. The
-equivalence of \ref{i} and \ref{iv} has already been stated in
-Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
-\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implication~\ref{ii}$\implies$\ref{iii} is shown in
-Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
-
-Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
-
-\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
-  The rule $\llabrn{mon}$ can be derived using the general identity and cut:
-  \begin{smallequation*}
-    \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
-          \vlhy{}}}{
-        \vlhy{\quad}}{
-        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
-    }
-  \end{smallequation*}
-  And both these rules are admissible by Proposition~\ref{prop:id} and
-  Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
-  similar.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-In this section we show our system at work, as most of the section
-consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
-
-\begin{theorem}\label{thm:completeness}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{remark}
-  We have seem already in the proof of Proposition~\ref{prop:id} the
-  need of the rule $\rn{F_2}$. In the following proof of
-  Theorem~\ref{thm:completeness} we also see the need of the rules
-  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
-  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
-  \begin{itemize}
-  \item $\kax[1]$:
-    $$
-    \vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
-												{\vlhy {}}}}}}}}}}
-    }
-    $$
-    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-  \item $\kax[2]$:
-    $$
-    \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-									{\vlhy {}}}								}}}}}}
-    }
-    $$
-    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-  \item $\kax[3]$:
-    $$
-    \vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
-				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-									{\vlhy {}}}}}}}}
-		}
-    $$
-  \item $\kax[4]$:
-    $$
-\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-					{\vlin {\color{red}\rn{trans}}
-						{}
-						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-											{\vlhy {}}}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-											{\vlhy {}}}}}}}}}}}
-}
-$$
-where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-\item $\kax[5]$:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
-				{\vlhy {}}}}
-  }
-  $$
-  \end{itemize}
-  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
-			{\vlin {\color{red}\rn{refl}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-				{\vlin {\rn{id}}
-					{}
-					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-					{\vlhy {}}}}}
-  }
-  $$
-
-  Finally, we have to show how the rules of modus ponens and
-  necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necessitation, we can
-  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
-
-  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Soundness}\label{sec:soundness}
-
-In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
-of our system $\labIKp$ is sound. We want to prove that for all model
-$\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
-\end{definition}
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \Rightarrow \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \Rightarrow \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$.
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$.
-We say that $\M \not \Vdash \B, \Gamma \Rightarrow \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \Rightarrow \Delta$.
-\end{definition}
-
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$:
-
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \Rightarrow \Right$.}
-	\end{center}
-
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, x \le y, yRz,\Left,\break \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $y, z \in W$ such that $\futs xy$ and $\accs yz$, then $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
-
-\marianela{working on this}
-	\marianela{
-	Then assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, x \le y,\break yRz, \labels{x}{\BOX A} \Rightarrow \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular, from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all world $y, z$ such that $x \le y$ and $yRz$, then $\M_{0} \Vdash \labels{z}{A}$.
-Finally, we obtain that $\M_{0} \not \Vdash \B, \Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \Rightarrow \Right$.
-Then, the rule $\llabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\BOX$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash$ $conclusion$, i.e.
-$\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{\BOX A}$, which is the same as $\M_{0} \Vdash \vlan (\B,\Left)$ and  $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$.
-From $\M_{0} \not \Vdash \vlor (\Right, \labels{x}{\BOX A})$, we have that $\M_{0} \not \Vdash \Right$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}$.
-Following the semantic definition of $\BOX$, there exists worlds $y, z$ in $\M_{0}$, such that $x \le y, yRz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Therefore, $\M_{0} \not \Vdash premise$, i.e.
-$\M_{0} \not \Vdash \B, x \le y, yRz, \Left \Rightarrow \Right, \labels{z}{A}$.
-Then, the rule $\rlabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\IMP$: By way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \Rightarrow \Right, \labels{x}{A \IMP B}$, i.e., in particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $y$ such that $x \le y$ and $\M_{0} \Vdash \labels{y}{A}$ but $\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, x \le y, \Left, \labels{y}{A} \Rightarrow \labels{y}{B}$.
-Finally, the rule $\rlabrn\IMP$ is sound.}
-\end{itemize}
-
-The other cases are similar.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cut Admissibility}\label{sec:cut-elim}
-
-\todo{I do not know how to organize this section. First cut elimination proof? (lemma before or after?) Then mon is admissible using cut proof?}
-
-\lutz{some start below}
-
-In this section we are going to prove the admissibility of cut for $\labIKp$.
-
-\begin{theorem}
-  \label{thm:cut-adm}
-  The rule $\labrn{cut}$ is admissible for $\labIKp$.
-\end{theorem}
-
-This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
-
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is \todo{finish}
-
-We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if \todo{...}
-
-The following two lemmas are standard.
-
-\begin{lemma}
-  \label{lem:weak-adm}
-  The weakening rule
-  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:inv}
-  The rules ..... are height-preserving invertible in
-  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
-  height-preserving invertible for the right premise.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma looks like a special case of
-Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using cut as we
-need it to eliminate the cut.
-
-\begin{lemma}
-  The atomic version of $\llabrn{mon}$
-  $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, x \le x'}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, x \le x'}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
-  $$
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma is the core of our cut elimination proof.
-
-\begin{lemma}
-  \label{lem:reduction}
-  Given a derivation of shape
-  $$
-  \vlderivation{
-    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
-      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
-      \vlhy{}}{
-      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
-  $$
-  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
-  derivation of ${\lseq\B\Left\Right}$
-\end{lemma}
-
-$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
-
-Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
-
-For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
-
-\begin{proof}
-
-	By induction on number of cuts + (rank,height) of the left-most top-most cut.
-
-	\textbf{Commutative cases:}\label{commutative-cases}
-
-	\begin{smallequation*}
-		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
-				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-			}{
-			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
-%
-If it does we rewrite it with a fresh variable $v$ first.
-
-%\begin{smallequation*}
-%	\reducesto
-%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-%			}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%			}
-%		}
-%\end{smallequation*}
-%
-%\begin{smallalign*}&
-%	\text{with } \DD_4 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-%		}
-%	}
-%	\\&
-%	\text{and } \DD_5 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}
-%	}
-%\end{smallalign*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
-			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
-		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
-}
-\reducesto
-%	\end{smallequation*}
-%	
-%	\begin{smallequation*}
-\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
-		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-}
-}
-\end{smallequation*}
-
-\textbf{Key cases:}\label{key-cases}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-			\vlhy{}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
-}
-\reducesto
-\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
-	}{
-	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-		\vlhy{}	
-	}
-}
-\reducesto
-\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
-		}
-	}{
-	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}{
-	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
-				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
-			}
-			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
-	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
-}{
-\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
-		}
-	}{
-	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-	}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
-		%			}{
-		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
-		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
-		%					\vlhy{}
-		%					}
-		%				}
-		%			}
-	}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-		}
-	}{
-	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
-	}	
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
-		}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
-		}
-	}
-}{
-\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
-}
-\end{smallequation*}
-\end{proof}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-
-	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
-
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-	In each case, we reason by induction on the height of $\DD$.
-
-	\begin{itemize}
-		\item $\llabrn\IMP$:
-		For a proof of height $1$, it is straightforward.
-		%
-		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-		%
-		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-		First let us fix a given index $y$ that does not appear in $\DD$.
-
-		If we start with a proof
-		\begin{smallequation*}
-			\DD = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-				}	
-			}
-		\end{smallequation*}
-
-		Then by induction hypothesis there exists a proof 
-		\begin{smallequation*}
-			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-		Therefore, we have the proof
-		\begin{smallequation*}
-			\DD^{\invr{\llabrn\IMP}} = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-				}
-			}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD$.
-
-		If we start with a proof 
-		\begin{smallequation*}
-			\vlderivation{
-				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-				}{
-				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-			}
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-	%
-	\item $\llabrn\DIA$:
-
-	If we start with a proof
-	\begin{smallequation*}
-		\DD = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-			}	
-		}
-	\end{smallequation*}
-
-	Then by induction hypothesis there exists a proof 
-	\begin{smallequation*}
-		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD'$.
-
-	Therefore, we have the proof
-	\begin{smallequation*}
-		\DD^{\invr{\llabrn\DIA}} = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-			}
-		}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-	If we start with a proof 
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-			}	
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
-
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
-%
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
-%
-
-\begin{definition}
-A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
-In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
-On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these are presented in the system $\labIKp$ as follows:
-
-\begin{center}
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				}
-				\\\\
-				\hspace{15mm}
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
-
-\end{center}
-
-\bigskip
-
-A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
-
-\begin{itemize}
-	\item Rule $\rn{F1}$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-			\\\\
-			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-			\\\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\hspace{8mm}
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-\end{center}
-
-You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
-
-\begin{itemize}
-	\item Rule $\llabrn\AND$:
-
-	%The system $\labIKp$ presents the next rule for the conjunction left:
-
-	%\begin{center}
-	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-	%\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\rlabrn\OR$:
-
-	Let the rule presented in $\labIKp$ for disjunction right be as follows:
-
-	\begin{center}
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-	\end{center}
-
-	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\\\\
-			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
-			\\\\
-			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-			\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-A more detailed explanation for some rules is below:
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$.
-	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
-
-\bigskip
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\multicolumn{2}{c}{
-				\hspace{9mm}
-				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-			}
-			\\
-			\multicolumn{2}{c}{
-				\hspace{10mm}
-				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-			}
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-The rule for implication right is explained below:
-
-\begin{itemize}
-	\item Rule $\rlabrn\IMP$.
-	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
-\end{itemize}
-
-\section{A complete and sound system for intuitionistic modal logics}
-%
-Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
-%
-Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
-%
-Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$ 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
-%		
-%		\todo{}
-		\smash{%\fbox{
-			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
-		}%}
-		%
-
-                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
-		\item\label{iii} $A$ is provable in $\labIKp$
-		%
-		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-%We show that each rule from our system is sound.
-%
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-The proof is a careful adaptation of standard techniques.
-%
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
-As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
-%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
-\bigskip
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlhy {}
-										}
-									}
-								}
-							}{
-%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-										\vlhy {\qquad\vdots\qquad}
-%										}
-%									}
-%								}
-%							}
-						}
-					}
-				}
-			}
-		}
-	}
-}$
-}$$
-%\end{example}
-
-%\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-}
-$
-}
-$$
-%\end{example}
-
-\begin{lemma}\label{lem:weak}\hbox{}\quad
-	\begin{enumerate}
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
-
-	%	\item 
-	%	If there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-	%	then there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Standard.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}\label{sec:ext}
-
-The main goal of this section is to generate stronger logics adding new axioms to our system.
-We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
-
-In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
-%
-These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
-
-Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-\bigskip
-
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
-why??}
-
-Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
-
-$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
-
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-\begin{figure}[h]
-	\begin{center}
-		$
-		\xymatrix{
-			& u' \ar@{.>}[ddr]^{R^l} \\
-			& u \ar@{.>}[u]^{\le} \\
-			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
-			& v \ar@{.>}[ur]_{R^n}
-		}
-		$
-	\end{center}
-	\label{fig:gklmn}
-	\caption{$\agklmn$ axiom for intuitionistic case}
-\end{figure}
-
-Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
-
-\bigskip
-
-\begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
-\end{center}
-
-\bigskip
-
-We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
-
-\begin{theorem}
-	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
-\end{theorem}
-
-\begin{proof}
-	\begin{center}
-		\scalebox{0.93}{
-			$\vlderivation {\vlin {\rlabrn{\IMP}}
-				{y \mbox{ fresh}}
-				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\rlabrn{\BOX}}
-					{z, w \mbox{ fresh} }
-					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
-					{\vlin {\llabrn{\DIA}}
-						{u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
-						{\vlin {\rn{F_2}}
-							{t \mbox{ fresh}}
-							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-							{\vlin {\gklmn}
-								{t', j \mbox{ fresh}}
-								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-								{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-									{\vlin {\rn{trans}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-										{\vlin {\llabrn{\BOX}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-											{\vlin {\rn{refl}}
-												{}
-												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-												{\vlin {\rn{id}}
-													{}
-													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-													{\vlhy {}}}}}}}}}}}}$}
-	\end{center}
-\end{proof}
-
-In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
-
-\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
-	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
-	\end{enumerate}
-	%\textbf{Probably F2g???}
-\end{lemma}
-
-Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
-
-\bibliographystyle{alpha}
-\bibliography{references}
-
-\end{document}
-
-%\begin{figure}[h]
-%\begin{center}
-%$\vlderivation{\vlinf{\id}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\B, \Left, x\colon \bot \SEQ z\colon A}{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\B, \Left \SEQ x \colon \top}{}}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\andleflab}{}{\B,\Left, x \colon \vls(A.B) \SEQ z \colon C}{\B, \Left, x\colon \vls(A.B,\labels{x}{A}, \labels{x}{B} \SEQ z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\B,\Left \SEQ x \colon \vls(A.B)}{\B, \Left \SEQ \labels{x}{A}}{\B, \Left \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%$\vliinf{\orleflab}{}{\B, \Left, x \colon \vls[A.B] \SEQ  \colon C}{\B, \Left, x \colon \vls[A.B], \labels{x}{A} \SEQ z \colon C}{\B, \Left, x \colon \vls[A.B], x   \colon   B \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\orriglabo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x   \colon   A}$
-%\hspace{7mm}$\vlinf{\orriglabt}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x \colon  B}$
-%
-%\vspace{2mm}
-%
-%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \IMP B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \IMP B, \labels{x}{B} \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \IMP B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%
-% $\vlderivation {\vlinf{\bllab}{}{\B, x \rel y, \Left x \colon \BOX A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z \colon B}}$
-%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\B, \Left \SEQ x \colon \BOX A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\dllab}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \DIA A, y \colon A \SEQ z \colon B}$
-%\hspace{5mm}$\vlinf{\drlab}{}{\B, x \rel y, \Left,  \SEQ x \colon \DIA A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\end{center}
-%\caption{System labIK}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	
-%	\begin{center}
-%		
-%		$\vlderivation { \vlin {\ids}{}{\B, \Left, \labels{x}{A} \SEQ x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\B, \Left, x \colon \bot \SEQ z\colon A}{\vlhy {}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vlin {\svlef}{}{\B, \Left, x \colon \vls(A.B) \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\B, \Left, \SEQ x \colon \vls(A.B)}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		
-%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
-%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
-%		
-%	\end{center}
-%	
-%	\caption{System $\lab\IK$}
-%	\label{fig:labIK}
-%\end{figure}
-%
-%\begin{theorem}[Simpson~\cite{Simpson}]
-%	\label{thm:simpson-sound-compl}
-%	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	\small
-%	\centering
-%
-%		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
-%		\hspace{5mm}
-%		$\vlinf{\llabrn\bot}{}{\B, \Left, x\colon \bot \SEQ \Right}{}$
-%		\hspace{5mm}
-%		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, x \colon \top}{}$
-%%		
-%%		\vspace{4mm}
-%		\\[1.5ex]
-%%		
-%		$\vlinf{\llabrn\AND}{}{\B,\Left, x \colon \vls(A.B) \SEQ \Right}{\conjlef}$
-%		\hspace{7mm}
-%		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ \Right}{\B, \Left, x   \colon   A \SEQ \Right}{\B, \Left, x   \colon   B \SEQ \Right}$
-%		\hspace{7mm}
-%		$\vlinf{\sorig}{}{\B, \Left \SEQ \Right, x \colon \vls[A.B]}{\B, \Left \SEQ \Right, x   \colon   A, x   \colon   B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \IMP B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlderivation {\vlinf{\sbl}{}{\B, \Left, x \le y, y \rel z, x \colon \BOX A \SEQ \Right}{\B,\Left, x \le y, y \rel z, x \colon \BOX A, z \colon A \SEQ \Right}}$
-%		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \SEQ \Right, x \colon \BOX A}{\B, \Left, x \le y, y \rel z \SEQ \Right, z \colon A}$
-%		
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ \Right}{\B, \Left, x \rel y, y \colon A \SEQ \Right}$
-%		\hspace{5mm}$\vlinf{\sdr}{}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A, y \colon A}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\refl}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-%		\hspace{7mm} $\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\rn{F_1}}{\text{\footnotesize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-%		%
-%		$\vlinf{\rn{F_2}}{\text{\footnotesize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-%	
-%	\caption{System $\labIKp$}
-%	\label{fig:labHIK}
-%\end{figure}

### 2019-10-02 caleidoscope/soundness.tex
reorganising folder

--- 2019-09-30 caleidoscope/caleidoscope.tex
@@
-\documentclass[a4paper]{article}
-
-%\usepackage{aiml18macro}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage[noxy]{virginialake}                        
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath,amsthm} 
-\usepackage{mathtools}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage{pgf}
-\usepackage{array}
-\usepackage[all]{xy}
-\usepackage{tikz}
-%\usepackage{hyperref}
-\usepackage{pgffor}
-
-	%%
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{fact}[theorem]{Fact}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-	%%
-\theoremstyle{definition}
-\newtheorem{observation}[theorem]{Observation}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-\newtheorem{remark}[theorem]{Remark}
-	%%
-
-\tikzset{
-	annotated cuboid/.pic={
-		\tikzset{%
-			every edge quotes/.append style={midway, auto},
-			/cuboid/.cd,
-			#1
-		}
-		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
-		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
-		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
-		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
-
-		;
-	},
-	/cuboid/.search also={/tikz},
-	/cuboid/.cd,
-	width/.store in=\cubex,
-	height/.store in=\cubey,
-	depth/.store in=\cubez,
-	units/.store in=\cubeunits,
-	scale/.store in=\cubescale,
-	width=10,
-	height=10,
-	depth=10,
-	units=cm,
-	scale=.1,
-}
-%tikz parameters
-
-\tikzstyle{point}=[circle,draw]
-\usetikzlibrary{arrows,automata,shapes,decorations.markings,
-	decorations.pathmorphing,backgrounds,fit,snakes,calc}
-
-%\usepackage{float}
-%\floatstyle{boxed} 
-%\restylefloat{figure}
-
-\usepackage{colonequals}
-\usepackage{bm}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Comments  
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
-\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
-
-%%% General
-\input{macros}
-\newcommand{\B}{\mathcal{R}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
-
-%%% Systems
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\ISfour}{\mathsf{IS4}}
-\newcommand*{\Sfour}{\mathsf{S4}}
-
-\newcommand{\fourax}{\mathsf{4}}
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-
-%%% Labelled sequents
-\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
-\newcommand{\SEQ}{\Longrightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\bullet}
-\newcommand*{\rel}{R}
-
-\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Equation environments
-\newdimen\mydisplayskip
-\mydisplayskip=.4\abovedisplayskip
-\newenvironment{smallequation}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
-\newenvironment{smallequation*}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
-\newenvironment{smallalign}
-{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
-\newenvironment{smallalign*}
-{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
-%
-\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
-\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
-%
-%
-\makeatletter
-\newbox\@conclbox
-\newdimen\@conclheight
-%
-%%%%%%
-\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
-\newcommand\vlderiibase[5]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%%
-\newcommand\vlderibase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlin{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%
-\newcommand\vlderidbase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlid{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-	%
-	\makeatother
-	%
-%%%General maths
-\newcommand*{\reducesto}{\quad{\leadsto}\quad}
-
-%%%%%%%%%%%%%%%%%
-
-%\newcommand{\height}[1]{\mathrm{ht}(#1)}
-\newcommand{\height}[1]{|#1|}
-
-\newcommand{\quand}{\quad\mbox{and}\quad}
-\newcommand{\qquand}{\qquad\mbox{and}\qquad}
-\newcommand{\quadcm}{\rlap{\quad,}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%The following line defines the page header consisting of the surnames of the authors.
-% Please include only the last names! 
-% Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
-
-\begin{document}
-
-%\begin{frontmatter}
-  \title{A fully labelled proof system for intuitionistic modal logics}
-  \author{Sonia Marin \and %}
-%  \todo{New university?}
-%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
-%    \author{
-      Marianela Morales %}
- \and
-% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
-% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
-%      \author{
-        Lutz Stra{\ss}burger }
-% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-
-  \maketitle
-
- \begin{abstract}
-
-   In this paper we present a labelled sequent system for
-   intuitionistic modal logics such that there is not only one, but
-   two relation symbols for the labels: one for the accessibility
-   relation associated with the Kripke semantics for normal modal logics and
-   one for the preorder relation associated with the Kripke semantics
-   for intuitionistic logic.
-   %%
-   This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logics. As a
-   consequence it can encompass a wider range of intuitionistic modal
-   logics than standard labelled systems.
-   %%
-   We also show an internal cut elimination proof for our system.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
-  \end{abstract}
-
-  %% \begin{keyword}
-  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  %% \end{keyword}
-% \end{frontmatter}
-
-  %\maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{get bib-file right}
-
-\section{Introduction}\label{sec:intro}
-
-Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
-\emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive systems to a broad range
-of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
-labelled calculi have the advantage of being more uniform and being able to 
-accommode more logics.
-
-Standard labelled sequent calculi attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally admit so called
-\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
-binary relation symbol. These calculi work best for logics with
-standard Kripke semantics, as in this case the relation $\rel$ is used
-to encode the accessibility relation in the Kripke models, and the
-frame conditions corresponding to the desired logic can be directly
-encoded as inference rules. Prominent examples are classical modal
-logics and intuitionistic propositional logic, where, e.g., the frame
-condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
-inference rule
-\begin{equation}
-  \label{eq:Rtrans}
-  \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
-\end{equation}
-where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas.
-
-However,
-in this paper we are concerned with \emph{intuitionistic modal
-  logics}, whose Kripke semantics is based on \emph{birelational}
-frames, i.e., they have two binary relations instead of one: one
-relation $R$ that corresponds to the accessibility relation in
-ordinary Kripke frames for modal logics, and a relation $\le$ that
-corresponds to the future relation in ordinary Kripke frames for
-intuitionistic logic. Consequently, standard labelled systems for
-these logics have certain shortcomings:
-\begin{enumerate}
-\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
-  versions of the $\fourax$-axiom
-  \begin{equation}
-    \label{eq:4ax}
-    \fm{\BOX A\IMP \BOX\BOX A}
-    \qquand
-    \fm{\DIA\DIA A\IMP\DIA A}
-    \quadcm
-  \end{equation}
-  as they are equivalent in classical
-  modal logic. However, in intuitionistic modal logic they are not
-  equivalent, and even though the logic $\ISfour$, i.e., the
-  intuitionistic version of the modal logic $\Sfour$, contains both
-  axioms, they can be added independently to the logic $\IK$ (the
-  intuitionistic version of $\K$). However, the proof theory of these
-  new logics has not been studied before, as no existing labelled (or
-  label-free) proof system can handle them, even though the
-  corresponding frame conditions
-  \begin{equation}
-    \label{eq:4frame}
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-    \quand
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-    \;,
-  \end{equation}
-  respectively, have already been studied
-  in~\cite{plotkin:stirling:86}.
-  \item The correspondence between the syntax and the semantics is not
-  as clean as one would expect. As only the $R$-relation (and not the
-  $\le$-relation) of the frame is visible in an ordinary labelled
-  sequent, we only have that a sequent $\Gamma$ is provable if and
-  only if is is valid in all \emph{graph-consistent}\footnote{This
-    means that every layer in the model can be lifted to any future of
-    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
-  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
-\end{enumerate}
-In order to address these two issues we propose here to extend the
-notion of labelled sequent by also allowing relational atoms of the
-form $\futs xy$. Consequently, we can easily translate the frame
-conditions in~\eqref{eq:4frame} into inference rules:
-\begin{equation}
-  \label{eq:4rules}
-  \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-     \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
-  \qquand
-  \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
-\end{equation}
-This allows us to define cut-free deductive systems for a wide range
-of logics that could not be treated before.  Furthermore, the relation
-between syntax and semantics is as one would expect: A sequent is
-provable in our system if and only if it is valid in all models.
-
-Besides that, there is another pleasant observation to make about our
-system. Ordinary labelled sequent systems for intuitionistic modal
-logic are single-conclusion~\cite{simpson:phd}. The same is true for
-the corresponding nested sequent
-systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
-Maehara style multiple-conclusion systems in nested
-sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
-labelled sequents. However, also in these systems there are rules
-($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
-premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
-intuitionistic logic. Our system eliminates this
-discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.
-
-\medskip
-
-This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
-Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
-The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
-
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
-
-\section*{Introduction(old version, to be deleted)}
-\todo{We should work on the introduction}
-
-One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.
-
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
-%
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as
-used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
-Negri~\cite{Negri}. 
-%
-These formalisms make explicit use not only of
-labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
-%
-In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
-logics) and the \emph{preorder relation} (for intuitionistic
-logic), using the full power of the bi-relational semantics for
-intuitionistic modal logics,
-and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.
-
-\todo{Simpson does not have internal cut-elimination}
-
-\sonia{
-  \begin{itemize}
-  \item internal vs externl calculi
-  \item extesion to axioms are truly intuitionistic (not just the
-    classical versions as in Simpson style)
-  \item connection with semantics compared to graph homomorphism
-    restiction in Simpson and ``indexed nested systems''
-  \end{itemize}
-}
-
-\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
-  \begin{itemize}
-  \item what we do:
-    \begin{itemize}
-    \item first systems (nested and labelled) for intuitionistic modal
-      logic where ``single conclusion'', i.e., only one formula on the
-      right.
-    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
-    \item Still rules that forced single formula on the right (white implication and white box)
-    \item by allowing both relations of the model in the proof system
-      we go to genuinely multiple conclusion: never ever a formula on
-      the right has to be deleted during proof search.
-    \end{itemize}
-  \item why we do it: 
-    \begin{itemize}
-    \item getting things right: labelled systems for classical modal
-      logics, or plain propositional intuiionistic logic have one
-      binary relation, which is exactly the relation of the standard
-      Kripke semantics. The standard Kripke semantics for
-      intuitionistic modal logic is birelational, with a strong
-      connectiion between the two binary relations. A clean labelled
-      system for these logics should incorporate both relations.
-    \item We get new logics.  In the standard nested sequent
-      or labelled sequent system for intuitionistic modal logic we
-      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
-      but here we can have them separtely.
-    \end{itemize}
-  \item how we do it:
-    \begin{itemize}
-    \item We start from the Maehara nested sequent system (which can
-      be translated straightforwardly into a labelled system with one
-      relation $R$.
-    \item the rules for $\AND$ and $\OR$ are trivial and as expected
-      they can be presented such that they are invertible on the left
-      and the right, they do not concern the relations $R$ and $\le$. 
-    \item So should be the rules for $\IMP$-left and $\BOX$-left and
-      identity, but there is a subtlety; see below...
-    \item the rules for $\DIA$ are also straightforward, as they
-      concern only $R$ but not $\le$.
-    \item The rules $\BOX$-right and $\IMP$-right are the ones that
-      force single conclusion in the Maehara system. This means that
-      here they create a future, using the relation $\le$.
-    \item In order to make everything work together, this forces us to
-      have reflexivity and transitivity of $\le$, explicely as rules
-      in the system, and have rules for the F1 and F2 conditions
-      making the relations $R$ and $\le$ go together.
-    \item As a consequence we also need a rule realizing monotonicity
-      for the formulas on the right.
-    \item However, we designed the system such that monotonicity is
-      admisible by encorporating it into the rules for identity,
-      $\IMP$-left and $\BOX$-left.
-    \end{itemize}
-  \end{itemize}
-}
-%
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{Intuitionistic modal logics}\label{sec:intmod}
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
-%
-$$
-\fm A \coloncolonequals
-\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
-$$
-%
-
-Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
-Five axioms have been considered as primitives in the literature.
-An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
-%
-
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
-\begin{itemize}
-	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
-	\begin{equation*}
-	\label{eq:ik}%\hskip-2em
-	\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
-	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
-	&
-	\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
-	&
-	\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
-	\\
-	\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
-	&
-	\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
-	\end{array}
-	\end{equation*}
-\end{itemize}
-
-The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
-The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}.
-However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
-Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
-However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
-
-The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic.
-It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
-
-The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
-%
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-
-\begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
-	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
-	\begin{enumerate}
-		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
-			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
-		}
-		\end{equation*}
-
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
-			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
-		}
-		\end{equation*}
-	\end{enumerate}
-	%	
-\end{definition}
-
-\begin{definition}
-	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
-	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
-\end{definition}
-
-We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:
-
-\begin{equation}\label{eq:kripke}
-	\begin{array}{rcl}
-	%\parbox{30em}{%
-
-		\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
-
-		\M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.
-
-	\end{array}
-\end{equation}
-Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
-%
-We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
-
-From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
-	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
-\end{proposition}
-
-\begin{definition}
-	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
-	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
-\end{definition}
-
-%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%
-%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-
-Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.
-
-\begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
-	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
-
-%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
-
-\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
-\begin{theorem}[\cite{plotkin:stirling:86}]
-	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
-
-	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
-
-\end{theorem}
-
-% we would like to consider special restrictions on these bi-relational frames.
-For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%\section{Intuitionistic modal logics}\label{sec:intmod}
-%
-%	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%	%
-%	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
-%	%
-%	$$
-%	A \coloncolonequals
-%	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
-%	$$
-%	%
-%        \lutz{why do we have $\TOP$?}
-%	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
-%
-%Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%%
-%Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
-%%
-%
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-%%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
-%%
-%It is obtained from intuitionistic propositional logic by adding:
-%\begin{itemize}
-%\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
-%\item the following five variants of the \emph{distributivity axiom}:
-%\begin{equation*}
-%\label{eq:ik}%\hskip-2em
-%\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
-%\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
-%&
-%\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
-%&
-%\kax[5]\colon&\DIA\BOT\IMP\BOT
-%\\
-%\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
-%&
-%\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
-%\end{array}
-%\end{equation*}
-%\end{itemize}
-%
-%The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
-%%
-%It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-%
-%\begin{definition}
-%	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
-%%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-%	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
-%	\begin{enumerate}
-%		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]_R  & v' \\
-%				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
-%			}
-%			\end{equation*}
-%		
-%		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]^R & v' \\
-%				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
-%			}
-%			\end{equation*}
-%	\end{enumerate}
-%%	
-%\end{definition}
-%
-%\begin{definition}
-%	\label{model}
-%	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-%	if $w \le w'$ then $V(w)\subseteq V(w')$.
-%\end{definition}
-%
-%We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
-%%
-%Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-%\begin{equation}
-%  \label{eq:kripke}
-%  \parbox{30em}{%
-%  $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
-%
-%$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
-%
-%$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
-%
-%$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
-%
-%$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
-%
-%%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-%}
-%\end{equation}
-%\todo{fix typography}
-%
-%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
-%
-%From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-%\begin{proposition}(Monotonicity) 
-%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
-%\end{proposition}
-%
-%
-%
-%\begin{definition}
-%	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-%%
-%	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
-%\end{definition}
-%
-%
-%
-%%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%%
-%%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-%
-%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
-%
-%\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-%	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{The system}\label{sec:system}
-
-In this section we present our fully labelled sequent proof system
-for intuitionistic modal logics. The starting point is the notion of a
-\emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
-x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
-at world $\lb x$. A \emph{relation atom} is either an expression
-$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
-intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. This is enough to define the notion of
-\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
-multi-sets of labelled formulas, all written as list, separated by commas.
-
-\begin{figure}[!t]
-  \begin{center}
-	\fbox{
-%	\begin{minipage}{.95\textwidth}
-	\begin{tabular}{c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-		&
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		%\quad
-		%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-		\\\\
-		$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-		\\\\
-		$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
-% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
- 		}
-		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-		\\\\
-		$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-		\\
-		\multicolumn{2}{c}{
-		$\mbox{\hbox to .9\linewidth{\dotfill}}$
-		}
-		\\
-		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-		&
-		$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-		}
-	\end{tabular}		
-%\end{minipage}
-}		
-  \end{center}
-  \caption{System $\labIKp$}
-	\label{fig:labIKp}
-\end{figure}
-
-Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
-We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
-\begin{equation}
-  \label{eq:nomon}
-  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
-  \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
-  \quad
-  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
-\end{equation}
-that are not sufficient for a complete system, and we will see below
-why. Before, let us first look at the rules $\rlabrn\IMP$ and
-$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
-of~\cite{str:2017maehara}, these are the two rules that force
-single-conclusion. This is the reason why in our system we need the
-$\le$ in the relational atoms; we need to go to the future of the
-current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
-connectives $\IMP$ and $\BOX$ are the ones that need the
-future-relation $\le$. This relation is reflexive and transitive. In
-order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.
-
-Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
-system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
-%
-However, these two rule create new labels, and in order to be
-complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
-\begin{equation}
-  \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
-  \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
-\end{equation}
-Since this rule is a form of contraction, it would cause the same
-problems as contraction in a cut elimination proof. Hence, it is
-preferable to have a system in which this rule is admissible. This is
-the reason why we have monotonicity incorporated in the rules
-$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. Then, not only
-$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
-shown on the right in~\eqref{eq:mono} above is admissible.
-
-\begin{proposition}
-  \label{prop:mon-adm}
-  The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$.
-\end{proposition}
-
-One can prove this proposition in the same way as one usually proves
-admissibity of contraction in a sequent calculus, by induction on the
-height of the derivation, which in fact would yield a stronger result,
-namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
-  preserving} admissible for $\labIKp$. However, we do not need this
-result in this paper, and therefore we leave it as an exercise to the
-reader. Nonetheless, we will give a short proof of
-Proposition~\ref{prop:mon-adm} at the end of this section.
-
-Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.
-
-\begin{proposition}
-  \label{prop:id}
-	The following general idenity axiom~
-	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
-        ~is admissible for $\labIKp$. 
-\end{proposition}
-
-\begin{proof}
-	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
-	\begin{itemize}
-		%% \item Atomic case
-		%% \begin{smallequation*}
-		%% 	%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% 	%\reducesto
-		%% 	\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% \end{smallequation*}
-		\item $\fm{A \AND B}$
-		%\begin{smallequation*}
-		%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
-		%	\reducesto
-		%\end{smallequation*}
-		\begin{smallequation*}
-			\vlderivation{
-				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
-					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
-							\vlhy{}
-						}
-					}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-	\item $\fm{A \OR B}$
-	%\begin{smallequation*}
-	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
-	%	\reducesto
-	%\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
-						\vlhy{}
-					}
-				}
-			}{
-			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{A \IMP B}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-								\vlhy{}
-							}
-						}
-					}{
-					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{\BOX A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-
-	\item $\fm{\DIA A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-        \qedhere
-	\end{itemize}
-\end{proof}
-
-In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
-\begin{equation}
-  \label{eq:cut}
-  \vliiinf{\labrn{cut}}{}{
-    \lseq\B\Left\Right}{
-    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
-    \lseq\B{\Left,\labels{z}{C}}{\Right}}
-\end{equation}
-Then we can summarize soundness and completeness, and cut
-admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$. 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
-		\item\label{iii} $A$ is provable in $\labIKp$.
-		%
-		\item\label{iv} $A$ is valid in every birelational frame. %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-The proof of this theorem is the topic of the following sections. The
-equivalence of \ref{i} and \ref{iv} has already been stated in
-Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
-\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implication~\ref{ii}$\implies$\ref{iii} is shown in
-Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
-
-Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
-
-\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
-  The rule $\llabrn{mon}$ can be derived using the general identity and cut:
-  \begin{smallequation*}
-    \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
-          \vlhy{}}}{
-        \vlhy{\quad}}{
-        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
-    }
-  \end{smallequation*}
-  And both these rules are admissible by Proposition~\ref{prop:id} and
-  Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
-  similar.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-In this section we show our system at work, as most of the section
-consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
-
-\begin{theorem}\label{thm:completeness}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{remark}
-  We have seem already in the proof of Proposition~\ref{prop:id} the
-  need of the rule $\rn{F_2}$. In the following proof of
-  Theorem~\ref{thm:completeness} we also see the need of the rules
-  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
-  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
-  \begin{itemize}
-  \item $\kax[1]$:
-    $$
-    \vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
-												{\vlhy {}}}}}}}}}}
-    }
-    $$
-    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-  \item $\kax[2]$:
-    $$
-    \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-									{\vlhy {}}}								}}}}}}
-    }
-    $$
-    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-  \item $\kax[3]$:
-    $$
-    \vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
-				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-									{\vlhy {}}}}}}}}
-		}
-    $$
-  \item $\kax[4]$:
-    $$
-\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-					{\vlin {\color{red}\rn{trans}}
-						{}
-						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-											{\vlhy {}}}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-											{\vlhy {}}}}}}}}}}}
-}
-$$
-where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-\item $\kax[5]$:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
-				{\vlhy {}}}}
-  }
-  $$
-  \end{itemize}
-  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
-			{\vlin {\color{red}\rn{refl}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-				{\vlin {\rn{id}}
-					{}
-					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-					{\vlhy {}}}}}
-  }
-  $$
-
-  Finally, we have to show how the rules of modus ponens and
-  necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necessitation, we can
-  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
-
-  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The other cases are similar and we leave them to the reader.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cut Admissibility}\label{sec:cut-elim}
-In this section we are going to prove the admissibility of cut for $\labIKp$.
-
-\begin{theorem}
-  \label{thm:cut-adm}
-  The rule $\labrn{cut}$ is admissible for $\labIKp$.
-\end{theorem}
-
-This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
-
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is the height of D when seen as a tree, i.e., the length of
-the longest path in the tree from its root to one of its leaves.
-
-We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if for every
-derivation of the conclusion of the rule there are derivations for each of its premisses with at most the same height.
-
-The following two lemmas are standard.
-
-\begin{lemma}
-  \label{lem:weak-adm}
-  The weakening rule
-  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{\begin{lemma}
-  	If there exists a proof  $\vlderivation {\vlpd{\D}{}{\B, \Left \Rightarrow \Right}}$ then there exists a proof $\vlderivation {\vlpd {\Dw}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}}$
-
-  \end{lemma}
-
-  \vspace{3mm}
-
-  \begin{proof}
-  	By induction on the height of $\D$.
-
-  	For a proof of height 1:
-
-  	if $\D$ = $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, x \colon a \Rightarrow \Right, y \colon a}{\vlhy {}}}$ then we take $\Dw$ to be $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, xRy, u \le v, x \colon a, z \colon A \Rightarrow \Right, w \colon B, y \colon a}{\vlhy {}}}$.
-  	\vspace{2mm}
-
-  	For a proof $\D$ of height greater than 1:
-
-  	\begin{center}
-
-  		$\vlderivation{\vlin {$r$}{}{\B, \Left \Rightarrow \Right}{\vlpd {\Done}{}{\B', \Left' \Rightarrow \Right'}}}$
-
-  	\end{center}
-
-  	Then by induction hypothesis there exists a proof
-
-  	\begin{center}
-
-  		$\vlderivation {\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}$
-
-  	\end{center}
-
-  	Therefore, we have the proof
-
-  	\begin{center}
-
-  		$\Dw = \vlderivation {\vlin{}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}{\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}}$
-
-  	\end{center}
-
-  \end{proof}}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:inv}
-  The rules ..... are height-preserving invertible in
-  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
-  height-preserving invertible for the right premise.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma looks like a special case of
-Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using cut as we
-need it to eliminate the cut.
-
-\begin{lemma}
-  The atomic version of $\llabrn{mon}$
-  $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
-  $$
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  	\begin{smallequation*}
-  		\vlderivation{
-  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x''}{a}}{
-  					\vlhy{}
-  				}
-  			}
-  		}
-  		\reducesto
-  		\vlderivation{
-  		\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \futs{x}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlhy{}
-  			}}
-  	}
-  	\end{smallequation*}
-  	\todo{missing case}
-%  	\begin{smallequation*}
-%  		\vlderivation{
-%  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{
-%  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x'}{a}}{
-%  					\vlhy{}
-%  				}
-%  			}
-%  		}
-%  		\reducesto
-%  		\vlinf{\labrn{id}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{}
-%  		\qedhere
-%  	\end{smallequation*}
-\end{proof}
-
-The next lemma is the core of our cut elimination proof.
-
-\begin{lemma}
-  \label{lem:reduction}
-  Given a derivation of shape
-  $$
-  \vlderivation{
-    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
-      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
-      \vlhy{}}{
-      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
-  $$
-  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
-  derivation of ${\lseq\B\Left\Right}$
-\end{lemma}
-
-%$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
-
-Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
-
-For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
-
-\begin{proof}
-
-	By induction on number of cuts + (rank,height) of the left-most top-most cut.
-
-	\textbf{Commutative cases:}\label{commutative-cases}
-
-	\begin{smallequation*}
-		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
-				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-			}{
-			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
-%
-If it does we rewrite it with a fresh variable $v$ first.
-
-%\begin{smallequation*}
-%	\reducesto
-%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-%			}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%			}
-%		}
-%\end{smallequation*}
-%
-%\begin{smallalign*}&
-%	\text{with } \DD_4 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-%		}
-%	}
-%	\\&
-%	\text{and } \DD_5 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}
-%	}
-%\end{smallalign*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
-			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
-		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
-}
-\reducesto
-%	\end{smallequation*}
-%	
-%	\begin{smallequation*}
-\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
-		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-}
-}
-\end{smallequation*}
-
-\textbf{Key cases:}\label{key-cases}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-			\vlhy{}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
-}
-\reducesto
-\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
-	}{
-	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-		\vlhy{}	
-	}
-}
-\reducesto
-\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
-		}
-	}{
-	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}{
-	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
-				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
-			}
-			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
-	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
-}{
-\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
-		}
-	}{
-	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-	}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
-		%			}{
-		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
-		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
-		%					\vlhy{}
-		%					}
-		%				}
-		%			}
-	}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-		}
-	}{
-	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
-	}	
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
-		}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
-		}
-	}
-}{
-\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
-}
-\end{smallequation*}
-\end{proof}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-
-	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
-
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-	In each case, we reason by induction on the height of $\DD$.
-
-	\begin{itemize}
-		\item $\llabrn\IMP$:
-		For a proof of height $1$, it is straightforward.
-		%
-		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-		%
-		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-		First let us fix a given index $y$ that does not appear in $\DD$.
-
-		If we start with a proof
-		\begin{smallequation*}
-			\DD = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-				}	
-			}
-		\end{smallequation*}
-
-		Then by induction hypothesis there exists a proof 
-		\begin{smallequation*}
-			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-		Therefore, we have the proof
-		\begin{smallequation*}
-			\DD^{\invr{\llabrn\IMP}} = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-				}
-			}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD$.
-
-		If we start with a proof 
-		\begin{smallequation*}
-			\vlderivation{
-				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-				}{
-				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-			}
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-	%
-	\item $\llabrn\DIA$:
-
-	If we start with a proof
-	\begin{smallequation*}
-		\DD = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-			}	
-		}
-	\end{smallequation*}
-
-	Then by induction hypothesis there exists a proof 
-	\begin{smallequation*}
-		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD'$.
-
-	Therefore, we have the proof
-	\begin{smallequation*}
-		\DD^{\invr{\llabrn\DIA}} = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-			}
-		}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-	If we start with a proof 
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-			}	
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
-
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
-%
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
-%
-
-\begin{definition}
-A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
-In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
-On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these are presented in the system $\labIKp$ as follows:
-
-\begin{center}
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				}
-				\\\\
-				\hspace{15mm}
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
-
-\end{center}
-
-\bigskip
-
-A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
-
-\begin{itemize}
-	\item Rule $\rn{F1}$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-			\\\\
-			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-			\\\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\hspace{8mm}
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-\end{center}
-
-You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
-
-\begin{itemize}
-	\item Rule $\llabrn\AND$:
-
-	%The system $\labIKp$ presents the next rule for the conjunction left:
-
-	%\begin{center}
-	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-	%\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\rlabrn\OR$:
-
-	Let the rule presented in $\labIKp$ for disjunction right be as follows:
-
-	\begin{center}
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-	\end{center}
-
-	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\\\\
-			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
-			\\\\
-			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-			\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-A more detailed explanation for some rules is below:
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$.
-	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
-
-\bigskip
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\multicolumn{2}{c}{
-				\hspace{9mm}
-				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-			}
-			\\
-			\multicolumn{2}{c}{
-				\hspace{10mm}
-				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-			}
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-The rule for implication right is explained below:
-
-\begin{itemize}
-	\item Rule $\rlabrn\IMP$.
-	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
-\end{itemize}
-
-\section{A complete and sound system for intuitionistic modal logics}
-%
-Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
-%
-Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
-%
-Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
-%We show that each rule from our system is sound.
-%
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-The proof is a careful adaptation of standard techniques.
-%
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
-As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
-%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
-\bigskip
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlhy {}
-										}
-									}
-								}
-							}{
-%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-										\vlhy {\qquad\vdots\qquad}
-%										}
-%									}
-%								}
-%							}
-						}
-					}
-				}
-			}
-		}
-	}
-}$
-}$$
-%\end{example}
-
-%\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-}
-$
-}
-$$
-%\end{example}
-
-\begin{lemma}\label{lem:weak}\hbox{}\quad
-	\begin{enumerate}
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
-
-	%	\item 
-	%	If there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-	%	then there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Standard.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}\label{sec:ext}
-
-The main goal of this section is to generate stronger logics adding new axioms to our system.
-We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
-
-In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
-%
-These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
-
-Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-\bigskip
-
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
-why??}
-
-Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
-
-$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
-
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-\begin{figure}[h]
-	\begin{center}
-		$
-		\xymatrix{
-			& u' \ar@{.>}[ddr]^{R^l} \\
-			& u \ar@{.>}[u]^{\le} \\
-			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
-			& v \ar@{.>}[ur]_{R^n}
-		}
-		$
-	\end{center}
-	\label{fig:gklmn}
-	\caption{$\agklmn$ axiom for intuitionistic case}
-\end{figure}
-
-Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
-
-\bigskip
-
-\begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
-\end{center}
-
-\bigskip
-
-We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
-
-\begin{theorem}
-	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
-\end{theorem}
-
-\begin{proof}
-	\begin{center}
-		\scalebox{0.93}{
-			$\vlderivation {\vlin {\rlabrn{\IMP}}
-				{y \mbox{ fresh}}
-				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\rlabrn{\BOX}}
-					{z, w \mbox{ fresh} }
-					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
-					{\vlin {\llabrn{\DIA}}
-						{u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
-						{\vlin {\rn{F_2}}
-							{t \mbox{ fresh}}
-							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-							{\vlin {\gklmn}
-								{t', j \mbox{ fresh}}
-								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-								{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-									{\vlin {\rn{trans}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-										{\vlin {\llabrn{\BOX}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-											{\vlin {\rn{refl}}
-												{}
-												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-												{\vlin {\rn{id}}
-													{}
-													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-													{\vlhy {}}}}}}}}}}}}$}
-	\end{center}
-\end{proof}
-
-In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
-
-\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
-	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
-	\end{enumerate}
-	%\textbf{Probably F2g???}
-\end{lemma}
-
-Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
-
-\bibliographystyle{alpha}
-\bibliography{references}
-
-\end{document}
-
-%\begin{figure}[h]
-%\begin{center}
-%$\vlderivation{\vlinf{\id}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\B, \Left, x\colon \bot \SEQ z\colon A}{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\B, \Left \SEQ x \colon \top}{}}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\andleflab}{}{\B,\Left, x \colon \vls(A.B) \SEQ z \colon C}{\B, \Left, x\colon \vls(A.B,\labels{x}{A}, \labels{x}{B} \SEQ z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\B,\Left \SEQ x \colon \vls(A.B)}{\B, \Left \SEQ \labels{x}{A}}{\B, \Left \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%$\vliinf{\orleflab}{}{\B, \Left, x \colon \vls[A.B] \SEQ  \colon C}{\B, \Left, x \colon \vls[A.B], \labels{x}{A} \SEQ z \colon C}{\B, \Left, x \colon \vls[A.B], x   \colon   B \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\orriglabo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x   \colon   A}$
-%\hspace{7mm}$\vlinf{\orriglabt}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x \colon  B}$
-%
-%\vspace{2mm}
-%
-%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \IMP B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \IMP B, \labels{x}{B} \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \IMP B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%
-% $\vlderivation {\vlinf{\bllab}{}{\B, x \rel y, \Left x \colon \BOX A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z \colon B}}$
-%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\B, \Left \SEQ x \colon \BOX A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\dllab}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \DIA A, y \colon A \SEQ z \colon B}$
-%\hspace{5mm}$\vlinf{\drlab}{}{\B, x \rel y, \Left,  \SEQ x \colon \DIA A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\end{center}
-%\caption{System labIK}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	
-%	\begin{center}
-%		
-%		$\vlderivation { \vlin {\ids}{}{\B, \Left, \labels{x}{A} \SEQ x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\B, \Left, x \colon \bot \SEQ z\colon A}{\vlhy {}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vlin {\svlef}{}{\B, \Left, x \colon \vls(A.B) \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\B, \Left, \SEQ x \colon \vls(A.B)}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		
-%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
-%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
-%		
-%	\end{center}
-%	
-%	\caption{System $\lab\IK$}
-%	\label{fig:labIK}
-%\end{figure}
-%
-%\begin{theorem}[Simpson~\cite{Simpson}]
-%	\label{thm:simpson-sound-compl}
-%	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	\small
-%	\centering
-%
-%		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
-%		\hspace{5mm}
-%		$\vlinf{\llabrn\bot}{}{\B, \Left, x\colon \bot \SEQ \Right}{}$
-%		\hspace{5mm}
-%		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, x \colon \top}{}$
-%%		
-%%		\vspace{4mm}
-%		\\[1.5ex]
-%%		
-%		$\vlinf{\llabrn\AND}{}{\B,\Left, x \colon \vls(A.B) \SEQ \Right}{\conjlef}$
-%		\hspace{7mm}
-%		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ \Right}{\B, \Left, x   \colon   A \SEQ \Right}{\B, \Left, x   \colon   B \SEQ \Right}$
-%		\hspace{7mm}
-%		$\vlinf{\sorig}{}{\B, \Left \SEQ \Right, x \colon \vls[A.B]}{\B, \Left \SEQ \Right, x   \colon   A, x   \colon   B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \IMP B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlderivation {\vlinf{\sbl}{}{\B, \Left, x \le y, y \rel z, x \colon \BOX A \SEQ \Right}{\B,\Left, x \le y, y \rel z, x \colon \BOX A, z \colon A \SEQ \Right}}$
-%		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \SEQ \Right, x \colon \BOX A}{\B, \Left, x \le y, y \rel z \SEQ \Right, z \colon A}$
-%		
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ \Right}{\B, \Left, x \rel y, y \colon A \SEQ \Right}$
-%		\hspace{5mm}$\vlinf{\sdr}{}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A, y \colon A}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\refl}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-%		\hspace{7mm} $\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\rn{F_1}}{\text{\footnotesize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-%		%
-%		$\vlinf{\rn{F_2}}{\text{\footnotesize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-%	
-%	\caption{System $\labIKp$}
-%	\label{fig:labHIK}
-%\end{figure}

### 2019-10-03 caleidoscope/caleidoscope.tex
fixed soundness

@@
 
+\newcommand*{\SG}{\fm{\mathcal{G}}}
+\newcommand{\SGi}[1]{\fm{\mathcal{G}_{#1}}}
 \newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
@@
 \newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
+
+\newcommand{\inter}[1]{\lb{\llbracket #1\rrbracket}}
+\newcommand{\force}[3]{#1,#2\Vdash#3}
+\newcommand{\nforce}[3]{#1,#2\not\Vdash#3}
+\newcommand{\cforce}[3]{#1,\lb{#2}\Vdash\fm{#3}}
+\newcommand{\cnforce}[3]{#1,\lb{#2}\not\Vdash\fm{#3}}
 
@@
 From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
+\begin{proposition}(Monotonicity)\label{prop:mon}
 	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
@@
 In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
+Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
+of our system $\labIKp$ is sound. To make precise what that actually
+means, we have to extend the relation $\Vdash$, defined in
+Section~\ref{sec:intmod} from formulas to sequents. This is the
+purpose of the following definitions.
+
+\begin{definition}\label{def:force-seq}
+Let $\M = \langle W, \rel_\M, \le_\M, V \rangle$ be a model, and let
+$\SG$ be the sequent $\lseq\B\Left\Right$. A \emph{$\SG$-interpretation
+  in $\M$} is a mapping $\inter{\cdot}$ from the labels in $\SG$ to the set $W$ of worlds in $\M$, such that whenever $\accs xy$ in $\B$, then $\inter x\rel_\M\inter y$, and whenever $\futs xy$ in $\B$, then $\inter x\le_\M\inter y$.
+Now we can define
+\begin{equation}
+  \M,\inter\cdot\Vdash\SG\qquad\mbox{iff}\qquad
+  \parbox{20em}{if for all $\labels{x}{A} \in \Gamma$, we have $\M, \inter x \Vdash \fm A$, then there exists $\labels{z}{B} \in \Delta$ such that $\M, \inter z \Vdash \fm B$.}
+\end{equation}
 \end{definition}
 
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$. We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
+\begin{definition}\label{def:valid-seq}
+  A sequent $\SG$ is \emph{satisfied} in $\M = \langle W, \rel, \le, V
+  \rangle$ iff for all $\SG$-interpretations $\inter\cdot$ we have
+  $\M,\inter\cdot\Vdash\SG$.
+  %%
+  A sequent $\SG$ is \emph{valid} in a frame $\F = \langle W, \rel,
+  \le \rangle$, if for all valuations $V$, the sequent $\SG$ is
+  satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}
 
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
-
+We are now ready to state the main theorem of this section, of which
+the implication \ref{iii}$\implies$\ref{iv} in
+Theorem~\ref{thm:cutfree-compl} is an immediate consequence.
+
+\begin{theorem}\label{thm:soundness}
+  If a sequent $\SG$ is provable in $\labIKp$, then it is valid in every birelational frame.
+\end{theorem}
+
+\begin{proof}
+  We proceed by induction on the height of the derivation of $\SG$, and we show for all rules in $\labIKp$
+  $$
+  \vliiinf{\labrn{r}}{}{\SG}{\SGi1}{\cdots}{\SGi n}
+  $$ for $n\in\{0,1,2\}$, that whenever $\SGi1,\ldots,\SGi n$ are
+  valid in all birelational frame, then so is $\SG$. It follows a case analysis on $\rn r$:
   \begin{itemize}
-	\item Rule $\llabrn\BOX$:
-
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
-	\end{center}
-
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
+  \item $\rlabrn\bot$: This is trivial because $\bot$ is never forced.
+  \item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon}.
+  \item $\llabrn\BOX$: By way of contradiction, assume $\B, \Left,
+    \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
+    is valid in all birelational frames, but $\B,\Left, \futs xy,
+    \accs yz, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
+    we have a model $\M$ and an interpretation $\inter\cdot$, such
+    that $\M,\inter\cdot\not\Vdash\B,\Left, \futs xy, \accs yz,
+    \labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
+    and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ and
+    $\cnforce \M wB$ for all $\labels wB\in\Right$. However, by the
+    definition of forcing in~\eqref{eq:kripke} we also have $\cforce
+    \M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \Left, \futs
+      xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
+      \Right}$. Contradiction.
+  \item $\rlabrn\BOX$: By way of contradiction, assume that $\futs xy,
+    \accs yz, \Left \SEQ \Right, \labels{z}{A}$ is valid in all
+    birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{\BOX
+      A}$ is not, where $\lb y$ and $\lb z$ do not occur in $\B$ or
+    $\Left$ or $\Right$.This means that we have a model $\M$ and an
+    interpretation $\inter\cdot$, such that
+    $\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX
+        A}}$. This means that there are worlds $\lb{y'}$ and $\lb{z'}$
+    in $\M$ such that $\inter x\le_\M \lb{y'}$ and
+    $\lb{y'}\rel_\M\lb{z'}$ and $\cforce\M{z'}{A}$. Now we let
+    $\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
+    y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
+    on all other labels. Then $\nforce\M{\inter\cdot'}{\futs xy,
+    \accs yz, \Left \SEQ \Right, \labels{z}{A}}$. Contradiction.
+  \item \lutz{if you want, you can add some more cases here, following the pattern above.}
+  \end{itemize}
+  The other cases are similar (and simpler), and we leave them to the
+  reader. In particular, note that the cases for the rules $\rn{refl}$,
+  $\rn{trans}$, $\rn{F_1}$ and $\rn{F_2}$ are trivial, as all
+  birelations frames have to obey the corresponding conditions.
+\end{proof}
+
+%% We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+
+%% In order to obtain the proof, let us introduce the next definitions:
+
+%% \begin{definition}
+%% 	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
+%% \end{definition}
+
+%% \begin{definition}
+%% 	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
+%% 	\begin{enumerate}
+%% 		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
+%% 		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
+%% 		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
+%% 	\end{enumerate}
+%% 	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$.
+We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
+%% \end{definition}
+
+%% Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
+
+%% \begin{itemize}
+%% 	\item Rule $\llabrn\BOX$:
+
+%% 	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
+
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
+%% 	\end{center}
+
+%% 	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
 Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $\lb y, \lb z \in W$ such that $\futs xy$ and $\accs yz$, $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
@@
 
-	\item Rule $\rlabrn\BOX$:
-
-	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
-	\end{center}
-
-	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
+%% 	\item Rule $\rlabrn\BOX$:
+
+%% 	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
+
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
+%% 	\end{center}
+
+%% 	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
 Let us assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.
@@
 
-	\item Rule $\rlabrn\IMP$:
-
-	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
-	\end{center}
-
-	We prove this statement by way of contradiction.
+%% 	\item Rule $\rlabrn\IMP$:
+
+%% 	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
+%% 	\end{center}
+
+%% 	We prove this statement by way of contradiction.
 Assume there exists a model $\M_{0}$ such that $\M_{0}$ does not satisfy the conclusion, i.e.
@@
 
-	\item Rule $\llabrn\DIA$:
-
-	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
-	\end{center}
-
-	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
-	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
+%% 	\item Rule $\llabrn\DIA$:
+
+%% 	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
+
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
+%% 	\end{center}
+
+%% 	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
+%% 	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
 From $\M_{0} \Vdash \labels{x}{\DIA A}$, according to the definition of the $\DIA$ operator, we have that there exists a world $\lb y$ in $\M_{0}$ such that $\accs xy$ and $\M_{0} \Vdash \labels{y}{A}$.
@@
 
-	\item Rule $\rlabrn\DIA$:
-
-	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
-
-	\begin{center}
-		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
-	\end{center}
-
-	We prove this statement by way of contradiction.
+%% 	\item Rule $\rlabrn\DIA$:
+
+%% 	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
+
+%% 	\begin{center}
+%% 		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
+%% 	\end{center}
+
+%% 	We prove this statement by way of contradiction.
 Let us assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$, we want to show that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
+%% 	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
 for all world $\lb y \in \M_{0}$ where $\accs xy$ we have $\M_{0} \not \Vdash \labels{y}{A}$.
@@
 Then we conclude that the rule $\rlabrn\DIA$ of the system $\labIKp$ is sound.
-\end{itemize}
-
-The other cases are similar and we leave them to the reader.
+%% \end{itemize}
+
+%% The other cases are similar and we leave them to the reader.
 

### 2019-10-03 caleidoscope/main.tex

--- 2019-09-30 caleidoscope/caleidoscope.tex
@@
 
-%\usepackage{aiml18macro}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage[noxy]{virginialake}                        
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath,amsthm} 
-\usepackage{mathtools}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage{pgf}
-\usepackage{array}
-\usepackage[all]{xy}
-\usepackage{tikz}
-%\usepackage{hyperref}
-\usepackage{pgffor}
-
-	%%
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{fact}[theorem]{Fact}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-	%%
-\theoremstyle{definition}
-\newtheorem{observation}[theorem]{Observation}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-\newtheorem{remark}[theorem]{Remark}
-	%%
-
-\tikzset{
-	annotated cuboid/.pic={
-		\tikzset{%
-			every edge quotes/.append style={midway, auto},
-			/cuboid/.cd,
-			#1
-		}
-		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
-		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
-		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
-		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
-
-		;
-	},
-	/cuboid/.search also={/tikz},
-	/cuboid/.cd,
-	width/.store in=\cubex,
-	height/.store in=\cubey,
-	depth/.store in=\cubez,
-	units/.store in=\cubeunits,
-	scale/.store in=\cubescale,
-	width=10,
-	height=10,
-	depth=10,
-	units=cm,
-	scale=.1,
-}
-%tikz parameters
-
-\tikzstyle{point}=[circle,draw]
-\usetikzlibrary{arrows,automata,shapes,decorations.markings,
-	decorations.pathmorphing,backgrounds,fit,snakes,calc}
-
-%\usepackage{float}
-%\floatstyle{boxed} 
-%\restylefloat{figure}
-
-\usepackage{colonequals}
-\usepackage{bm}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Comments  
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
-\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
-
-%%% General
-\input{macros}
-\newcommand{\B}{\mathcal{R}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
-
-%%% Systems
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\ISfour}{\mathsf{IS4}}
-\newcommand*{\Sfour}{\mathsf{S4}}
-
-\newcommand{\fourax}{\mathsf{4}}
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-
-%%% Labelled sequents
-\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
-\newcommand{\SEQ}{\Longrightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\bullet}
-\newcommand*{\rel}{R}
-
-\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Equation environments
-\newdimen\mydisplayskip
-\mydisplayskip=.4\abovedisplayskip
-\newenvironment{smallequation}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
-\newenvironment{smallequation*}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
-\newenvironment{smallalign}
-{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
-\newenvironment{smallalign*}
-{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
-%
-\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
-\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
-%
-%
-\makeatletter
-\newbox\@conclbox
-\newdimen\@conclheight
-%
-%%%%%%
-\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
-\newcommand\vlderiibase[5]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%%
-\newcommand\vlderibase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlin{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%
-\newcommand\vlderidbase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlid{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-	%
-	\makeatother
-	%
-%%%General maths
-\newcommand*{\reducesto}{\quad{\leadsto}\quad}
-
-%%%%%%%%%%%%%%%%%
-
-%\newcommand{\height}[1]{\mathrm{ht}(#1)}
-\newcommand{\height}[1]{|#1|}
-
-\newcommand{\quand}{\quad\mbox{and}\quad}
-\newcommand{\qquand}{\qquad\mbox{and}\qquad}
-\newcommand{\quadcm}{\rlap{\quad,}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%The following line defines the page header consisting of the surnames of the authors.
-% Please include only the last names! 
-% Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
-
-\begin{document}
+\input{macros2}
 
@@
 \author{Sonia Marin \and %}
-%  \todo{New university?}
-%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
+	%  \address{University College London \\ United Kingdom }
 	%    \author{
@@
 	\and
-% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
-% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
+	% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
 	%      \author{
@@
 % \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
+%% \begin{keyword}
+%% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
+%% \end{keyword}
+% \end{frontmatter}
+
+\begin{document}
 
@@
  \begin{abstract}
-
    In this paper we present a labelled sequent system for
@@
    We also show an internal cut elimination proof for our system.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
  \end{abstract}
 
-  %% \begin{keyword}
-  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  %% \end{keyword}
-% \end{frontmatter}
+\input{introduction}
+\input{preliminaries}
+\input{system}
+\input{completeness}
+\input{soundness}
+\input{cut-elim}
+\input{extensions}
 
-  %\maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{get bib-file right}
-
-\section{Introduction}\label{sec:intro}
-
-Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
-\emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive systems to a broad range
-of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
-labelled calculi have the advantage of being more uniform and being able to 
-accommode more logics.
-
-Standard labelled sequent calculi attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally admit so called
-\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
-binary relation symbol. These calculi work best for logics with
-standard Kripke semantics, as in this case the relation $\rel$ is used
-to encode the accessibility relation in the Kripke models, and the
-frame conditions corresponding to the desired logic can be directly
-encoded as inference rules. Prominent examples are classical modal
-logics and intuitionistic propositional logic, where, e.g., the frame
-condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
-inference rule
-\begin{equation}
-  \label{eq:Rtrans}
-  \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
-\end{equation}
-where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas.
-
-However,
-in this paper we are concerned with \emph{intuitionistic modal
-  logics}, whose Kripke semantics is based on \emph{birelational}
-frames, i.e., they have two binary relations instead of one: one
-relation $R$ that corresponds to the accessibility relation in
-ordinary Kripke frames for modal logics, and a relation $\le$ that
-corresponds to the future relation in ordinary Kripke frames for
-intuitionistic logic. Consequently, standard labelled systems for
-these logics have certain shortcomings:
-\begin{enumerate}
-\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
-  versions of the $\fourax$-axiom
-  \begin{equation}
-    \label{eq:4ax}
-    \fm{\BOX A\IMP \BOX\BOX A}
-    \qquand
-    \fm{\DIA\DIA A\IMP\DIA A}
-    \quadcm
-  \end{equation}
-  as they are equivalent in classical
-  modal logic. However, in intuitionistic modal logic they are not
-  equivalent, and even though the logic $\ISfour$, i.e., the
-  intuitionistic version of the modal logic $\Sfour$, contains both
-  axioms, they can be added independently to the logic $\IK$ (the
-  intuitionistic version of $\K$). However, the proof theory of these
-  new logics has not been studied before, as no existing labelled (or
-  label-free) proof system can handle them, even though the
-  corresponding frame conditions
-  \begin{equation}
-    \label{eq:4frame}
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-    \quand
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-    \;,
-  \end{equation}
-  respectively, have already been studied
-  in~\cite{plotkin:stirling:86}.
-  \item The correspondence between the syntax and the semantics is not
-  as clean as one would expect. As only the $R$-relation (and not the
-  $\le$-relation) of the frame is visible in an ordinary labelled
-  sequent, we only have that a sequent $\Gamma$ is provable if and
-  only if is is valid in all \emph{graph-consistent}\footnote{This
-    means that every layer in the model can be lifted to any future of
-    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
-  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
-\end{enumerate}
-In order to address these two issues we propose here to extend the
-notion of labelled sequent by also allowing relational atoms of the
-form $\futs xy$. Consequently, we can easily translate the frame
-conditions in~\eqref{eq:4frame} into inference rules:
-\begin{equation}
-  \label{eq:4rules}
-  \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-     \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
-  \qquand
-  \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
-\end{equation}
-This allows us to define cut-free deductive systems for a wide range
-of logics that could not be treated before.  Furthermore, the relation
-between syntax and semantics is as one would expect: A sequent is
-provable in our system if and only if it is valid in all models.
-
-Besides that, there is another pleasant observation to make about our
-system. Ordinary labelled sequent systems for intuitionistic modal
-logic are single-conclusion~\cite{simpson:phd}. The same is true for
-the corresponding nested sequent
-systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
-Maehara style multiple-conclusion systems in nested
-sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
-labelled sequents. However, also in these systems there are rules
-($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
-premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
-intuitionistic logic. Our system eliminates this
-discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.
-
-\medskip
-
-This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
-Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
-The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
-
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
-
-\section*{Introduction(old version, to be deleted)}
-\todo{We should work on the introduction}
-
-One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.
-
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
-%
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as
-used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
-Negri~\cite{Negri}. 
-%
-These formalisms make explicit use not only of
-labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
-%
-In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
-logics) and the \emph{preorder relation} (for intuitionistic
-logic), using the full power of the bi-relational semantics for
-intuitionistic modal logics,
-and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.
-
-\todo{Simpson does not have internal cut-elimination}
-
-\sonia{
-  \begin{itemize}
-  \item internal vs externl calculi
-  \item extesion to axioms are truly intuitionistic (not just the
-    classical versions as in Simpson style)
-  \item connection with semantics compared to graph homomorphism
-    restiction in Simpson and ``indexed nested systems''
-  \end{itemize}
-}
-
-\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
-  \begin{itemize}
-  \item what we do:
-    \begin{itemize}
-    \item first systems (nested and labelled) for intuitionistic modal
-      logic where ``single conclusion'', i.e., only one formula on the
-      right.
-    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
-    \item Still rules that forced single formula on the right (white implication and white box)
-    \item by allowing both relations of the model in the proof system
-      we go to genuinely multiple conclusion: never ever a formula on
-      the right has to be deleted during proof search.
-    \end{itemize}
-  \item why we do it: 
-    \begin{itemize}
-    \item getting things right: labelled systems for classical modal
-      logics, or plain propositional intuiionistic logic have one
-      binary relation, which is exactly the relation of the standard
-      Kripke semantics. The standard Kripke semantics for
-      intuitionistic modal logic is birelational, with a strong
-      connectiion between the two binary relations. A clean labelled
-      system for these logics should incorporate both relations.
-    \item We get new logics.  In the standard nested sequent
-      or labelled sequent system for intuitionistic modal logic we
-      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
-      but here we can have them separtely.
-    \end{itemize}
-  \item how we do it:
-    \begin{itemize}
-    \item We start from the Maehara nested sequent system (which can
-      be translated straightforwardly into a labelled system with one
-      relation $R$.
-    \item the rules for $\AND$ and $\OR$ are trivial and as expected
-      they can be presented such that they are invertible on the left
-      and the right, they do not concern the relations $R$ and $\le$. 
-    \item So should be the rules for $\IMP$-left and $\BOX$-left and
-      identity, but there is a subtlety; see below...
-    \item the rules for $\DIA$ are also straightforward, as they
-      concern only $R$ but not $\le$.
-    \item The rules $\BOX$-right and $\IMP$-right are the ones that
-      force single conclusion in the Maehara system. This means that
-      here they create a future, using the relation $\le$.
-    \item In order to make everything work together, this forces us to
-      have reflexivity and transitivity of $\le$, explicely as rules
-      in the system, and have rules for the F1 and F2 conditions
-      making the relations $R$ and $\le$ go together.
-    \item As a consequence we also need a rule realizing monotonicity
-      for the formulas on the right.
-    \item However, we designed the system such that monotonicity is
-      admisible by encorporating it into the rules for identity,
-      $\IMP$-left and $\BOX$-left.
-    \end{itemize}
-  \end{itemize}
-}
-%
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{Intuitionistic modal logics}\label{sec:intmod}
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
-%
-$$
-\fm A \coloncolonequals
-\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
-$$
-%
-
-Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
-Five axioms have been considered as primitives in the literature.
-An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
-%
-
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
-\begin{itemize}
-	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
-	\begin{equation*}
-	\label{eq:ik}%\hskip-2em
-	\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
-	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
-	&
-	\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
-	&
-	\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
-	\\
-	\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
-	&
-	\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
-	\end{array}
-	\end{equation*}
-\end{itemize}
-
-The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
-The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}.
-However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
-Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
-However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
-
-The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic.
-It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
-
-The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
-%
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-
-\begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
-	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
-	\begin{enumerate}
-		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
-			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
-		}
-		\end{equation*}
-
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
-			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
-		}
-		\end{equation*}
-	\end{enumerate}
-	%	
-\end{definition}
-
-\begin{definition}
-	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
-	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
-\end{definition}
-
-We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:
-
-\begin{equation}\label{eq:kripke}
-	\begin{array}{rcl}
-	%\parbox{30em}{%
-
-		\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
-
-		\M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.
-
-	\end{array}
-\end{equation}
-Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
-%
-We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
-
-From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
-	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
-\end{proposition}
-
-\begin{definition}
-	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
-	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
-\end{definition}
-
-%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%
-%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-
-Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.
-
-\begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
-	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
-
-%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
-
-\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
-\begin{theorem}[\cite{plotkin:stirling:86}]
-	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
-
-	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
-
-\end{theorem}
-
-% we would like to consider special restrictions on these bi-relational frames.
-For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%\section{Intuitionistic modal logics}\label{sec:intmod}
-%
-%	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%	%
-%	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
-%	%
-%	$$
-%	A \coloncolonequals
-%	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
-%	$$
-%	%
-%        \lutz{why do we have $\TOP$?}
-%	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
-%
-%Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%%
-%Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
-%%
-%
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-%%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
-%%
-%It is obtained from intuitionistic propositional logic by adding:
-%\begin{itemize}
-%\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
-%\item the following five variants of the \emph{distributivity axiom}:
-%\begin{equation*}
-%\label{eq:ik}%\hskip-2em
-%\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
-%\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
-%&
-%\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
-%&
-%\kax[5]\colon&\DIA\BOT\IMP\BOT
-%\\
-%\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
-%&
-%\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
-%\end{array}
-%\end{equation*}
-%\end{itemize}
-%
-%The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
-%%
-%It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-%
-%\begin{definition}
-%	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
-%%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-%	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
-%	\begin{enumerate}
-%		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]_R  & v' \\
-%				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
-%			}
-%			\end{equation*}
-%		
-%		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]^R & v' \\
-%				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
-%			}
-%			\end{equation*}
-%	\end{enumerate}
-%%	
-%\end{definition}
-%
-%\begin{definition}
-%	\label{model}
-%	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-%	if $w \le w'$ then $V(w)\subseteq V(w')$.
-%\end{definition}
-%
-%We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
-%%
-%Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-%\begin{equation}
-%  \label{eq:kripke}
-%  \parbox{30em}{%
-%  $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
-%
-%$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
-%
-%$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
-%
-%$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
-%
-%$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
-%
-%%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-%}
-%\end{equation}
-%\todo{fix typography}
-%
-%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
-%
-%From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-%\begin{proposition}(Monotonicity) 
-%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
-%\end{proposition}
-%
-%
-%
-%\begin{definition}
-%	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-%%
-%	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
-%\end{definition}
-%
-%
-%
-%%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%%
-%%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-%
-%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
-%
-%\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-%	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{The system}\label{sec:system}
-
-In this section we present our fully labelled sequent proof system
-for intuitionistic modal logics. The starting point is the notion of a
-\emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
-x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
-at world $\lb x$. A \emph{relation atom} is either an expression
-$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
-intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. This is enough to define the notion of
-\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
-multi-sets of labelled formulas, all written as list, separated by commas.
-
-\begin{figure}[!t]
-  \begin{center}
-	\fbox{
-%	\begin{minipage}{.95\textwidth}
-	\begin{tabular}{c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-		&
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		%\quad
-		%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-		\\\\
-		$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-		\\\\
-		$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
-% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
- 		}
-		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-		\\\\
-		$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-		\\
-		\multicolumn{2}{c}{
-		$\mbox{\hbox to .9\linewidth{\dotfill}}$
-		}
-		\\
-		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-		&
-		$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-		}
-	\end{tabular}		
-%\end{minipage}
-}		
-  \end{center}
-  \caption{System $\labIKp$}
-	\label{fig:labIKp}
-\end{figure}
-
-Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
-We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
-\begin{equation}
-  \label{eq:nomon}
-  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
-  \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
-  \quad
-  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
-\end{equation}
-that are not sufficient for a complete system, and we will see below
-why. Before, let us first look at the rules $\rlabrn\IMP$ and
-$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
-of~\cite{str:2017maehara}, these are the two rules that force
-single-conclusion. This is the reason why in our system we need the
-$\le$ in the relational atoms; we need to go to the future of the
-current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
-connectives $\IMP$ and $\BOX$ are the ones that need the
-future-relation $\le$. This relation is reflexive and transitive. In
-order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.
-
-Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
-system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
-%
-However, these two rule create new labels, and in order to be
-complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
-\begin{equation}
-  \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
-  \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
-\end{equation}
-Since this rule is a form of contraction, it would cause the same
-problems as contraction in a cut elimination proof. Hence, it is
-preferable to have a system in which this rule is admissible. This is
-the reason why we have monotonicity incorporated in the rules
-$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. Then, not only
-$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
-shown on the right in~\eqref{eq:mono} above is admissible.
-
-\begin{proposition}
-  \label{prop:mon-adm}
-  The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$.
-\end{proposition}
-
-One can prove this proposition in the same way as one usually proves
-admissibity of contraction in a sequent calculus, by induction on the
-height of the derivation, which in fact would yield a stronger result,
-namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
-  preserving} admissible for $\labIKp$. However, we do not need this
-result in this paper, and therefore we leave it as an exercise to the
-reader. Nonetheless, we will give a short proof of
-Proposition~\ref{prop:mon-adm} at the end of this section.
-
-Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.
-
-\begin{proposition}
-  \label{prop:id}
-	The following general idenity axiom~
-	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
-        ~is admissible for $\labIKp$. 
-\end{proposition}
-
-\begin{proof}
-	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
-	\begin{itemize}
-		%% \item Atomic case
-		%% \begin{smallequation*}
-		%% 	%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% 	%\reducesto
-		%% 	\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% \end{smallequation*}
-		\item $\fm{A \AND B}$
-		%\begin{smallequation*}
-		%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
-		%	\reducesto
-		%\end{smallequation*}
-		\begin{smallequation*}
-			\vlderivation{
-				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
-					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
-							\vlhy{}
-						}
-					}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-	\item $\fm{A \OR B}$
-	%\begin{smallequation*}
-	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
-	%	\reducesto
-	%\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
-						\vlhy{}
-					}
-				}
-			}{
-			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{A \IMP B}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-								\vlhy{}
-							}
-						}
-					}{
-					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{\BOX A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-
-	\item $\fm{\DIA A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-        \qedhere
-	\end{itemize}
-\end{proof}
-
-In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
-\begin{equation}
-  \label{eq:cut}
-  \vliiinf{\labrn{cut}}{}{
-    \lseq\B\Left\Right}{
-    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
-    \lseq\B{\Left,\labels{z}{C}}{\Right}}
-\end{equation}
-Then we can summarize soundness and completeness, and cut
-admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$. 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
-		\item\label{iii} $A$ is provable in $\labIKp$.
-		%
-		\item\label{iv} $A$ is valid in every birelational frame. %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-The proof of this theorem is the topic of the following sections. The
-equivalence of \ref{i} and \ref{iv} has already been stated in
-Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
-\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implication~\ref{ii}$\implies$\ref{iii} is shown in
-Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
-
-Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
-
-\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
-  The rule $\llabrn{mon}$ can be derived using the general identity and cut:
-  \begin{smallequation*}
-    \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
-          \vlhy{}}}{
-        \vlhy{\quad}}{
-        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
-    }
-  \end{smallequation*}
-  And both these rules are admissible by Proposition~\ref{prop:id} and
-  Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
-  similar.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-In this section we show our system at work, as most of the section
-consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
-
-\begin{theorem}\label{thm:completeness}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{remark}
-  We have seem already in the proof of Proposition~\ref{prop:id} the
-  need of the rule $\rn{F_2}$. In the following proof of
-  Theorem~\ref{thm:completeness} we also see the need of the rules
-  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
-  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
-  \begin{itemize}
-  \item $\kax[1]$:
-    $$
-    \vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
-												{\vlhy {}}}}}}}}}}
-    }
-    $$
-    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-  \item $\kax[2]$:
-    $$
-    \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-									{\vlhy {}}}								}}}}}}
-    }
-    $$
-    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-  \item $\kax[3]$:
-    $$
-    \vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
-				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-									{\vlhy {}}}}}}}}
-		}
-    $$
-  \item $\kax[4]$:
-    $$
-\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-					{\vlin {\color{red}\rn{trans}}
-						{}
-						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-											{\vlhy {}}}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-											{\vlhy {}}}}}}}}}}}
-}
-$$
-where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-\item $\kax[5]$:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
-				{\vlhy {}}}}
-  }
-  $$
-  \end{itemize}
-  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
-			{\vlin {\color{red}\rn{refl}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-				{\vlin {\rn{id}}
-					{}
-					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-					{\vlhy {}}}}}
-  }
-  $$
-
-  Finally, we have to show how the rules of modus ponens and
-  necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necessitation, we can
-  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
-
-  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Soundness}\label{sec:soundness}
-
-In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
-\end{definition}
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$. We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
-\end{definition}
-
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$:
-
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
-	\end{center}
-
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $\lb y, \lb z \in W$ such that $\futs xy$ and $\accs yz$, $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
-From this result, we can say that $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
-Thus, we have already proved that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, then $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
-According to the definition, we proved that the rule $\llabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\BOX$:
-
-	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
-	\end{center}
-
-	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
-Let us assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.
-In particular, $\M_{0} \not \Vdash \labels{x}{\BOX A}$, which means that there exist worlds $\lb y, \lb z$, such that $\futs xy$ and $\accs yz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Finally, we have that $\M_{0} \Vdash \B, \futs xy, \accs yz, \Left$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}, \labels{z}{A}$,  which is the same as $\M_{0} \not \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$.
-Then, by way of contradiction, we proved that the rule $\rlabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\IMP$:
-
-	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
-	\end{center}
-
-	We prove this statement by way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0}$ does not satisfy the conclusion, i.e.
-$\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.
-In particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $\lb y$ such that $\futs xy$ and $\M_{0}, f(\lb y) \Vdash A$ (i.e.
-$\M_{0} \Vdash \labels{y}{A}$) but $\M_{0}, f(\lb y) \Vdash B$, i.e.
-$\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \labels{y}{B}$.
-This means that the model $\M_{0}$ does not satisfy the premise and that is what we wanted to prove.
-Finally, we showed that the rule $\rlabrn\IMP$ is sound.
-
-	\item Rule $\llabrn\DIA$:
-
-	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
-	\end{center}
-
-	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
-	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
-From $\M_{0} \Vdash \labels{x}{\DIA A}$, according to the definition of the $\DIA$ operator, we have that there exists a world $\lb y$ in $\M_{0}$ such that $\accs xy$ and $\M_{0} \Vdash \labels{y}{A}$.
-Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ and we prove that the rule $\llabrn\DIA$ is sound.
-
-	\item Rule $\rlabrn\DIA$:
-
-	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
-
-	\begin{center}
-		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
-	\end{center}
-
-	We prove this statement by way of contradiction.
-Let us assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$, we want to show that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
-for all world $\lb y \in \M_{0}$ where $\accs xy$ we have $\M_{0} \not \Vdash \labels{y}{A}$.
-Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-Finally, assuming that $\M_{0}$ does not satisfy the conclusion, we proved that $\M_{0}$ does not satisfy the premise.
-Then we conclude that the rule $\rlabrn\DIA$ of the system $\labIKp$ is sound.
-\end{itemize}
-
-The other cases are similar and we leave them to the reader.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cut Admissibility}\label{sec:cut-elim}
-In this section we are going to prove the admissibility of cut for $\labIKp$.
-
-\begin{theorem}
-  \label{thm:cut-adm}
-  The rule $\labrn{cut}$ is admissible for $\labIKp$.
-\end{theorem}
-
-This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
-
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is the height of D when seen as a tree, i.e., the length of
-the longest path in the tree from its root to one of its leaves.
-
-We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if for every
-derivation of the conclusion of the rule there are derivations for each of its premisses with at most the same height.
-
-The following two lemmas are standard.
-
-\begin{lemma}
-  \label{lem:weak-adm}
-  The weakening rule
-  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{\begin{lemma}
-  	If there exists a proof  $\vlderivation {\vlpd{\D}{}{\B, \Left \Rightarrow \Right}}$ then there exists a proof $\vlderivation {\vlpd {\Dw}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}}$
-
-  \end{lemma}
-
-  \vspace{3mm}
-
-  \begin{proof}
-  	By induction on the height of $\D$.
-
-  	For a proof of height 1:
-
-  	if $\D$ = $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, x \colon a \Rightarrow \Right, y \colon a}{\vlhy {}}}$ then we take $\Dw$ to be $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, xRy, u \le v, x \colon a, z \colon A \Rightarrow \Right, w \colon B, y \colon a}{\vlhy {}}}$.
-  	\vspace{2mm}
-
-  	For a proof $\D$ of height greater than 1:
-
-  	\begin{center}
-
-  		$\vlderivation{\vlin {$r$}{}{\B, \Left \Rightarrow \Right}{\vlpd {\Done}{}{\B', \Left' \Rightarrow \Right'}}}$
-
-  	\end{center}
-
-  	Then by induction hypothesis there exists a proof
-
-  	\begin{center}
-
-  		$\vlderivation {\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}$
-
-  	\end{center}
-
-  	Therefore, we have the proof
-
-  	\begin{center}
-
-  		$\Dw = \vlderivation {\vlin{}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}{\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}}$
-
-  	\end{center}
-
-  \end{proof}}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:inv}
-  The rules ..... are height-preserving invertible in
-  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
-  height-preserving invertible for the right premise.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma looks like a special case of
-Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using cut as we
-need it to eliminate the cut.
-
-\begin{lemma}
-  The atomic version of $\llabrn{mon}$
-  $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
-  $$
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  	\begin{smallequation*}
-  		\vlderivation{
-  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x''}{a}}{
-  					\vlhy{}
-  				}
-  			}
-  		}
-  		\reducesto
-  		\vlderivation{
-  		\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \futs{x}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlhy{}
-  			}}
-  	}
-  	\end{smallequation*}
-  	\todo{missing case}
-%  	\begin{smallequation*}
-%  		\vlderivation{
-%  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{
-%  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x'}{a}}{
-%  					\vlhy{}
-%  				}
-%  			}
-%  		}
-%  		\reducesto
-%  		\vlinf{\labrn{id}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{}
-%  		\qedhere
-%  	\end{smallequation*}
-\end{proof}
-
-The next lemma is the core of our cut elimination proof.
-
-\begin{lemma}
-  \label{lem:reduction}
-  Given a derivation of shape
-  $$
-  \vlderivation{
-    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
-      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
-      \vlhy{}}{
-      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
-  $$
-  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
-  derivation of ${\lseq\B\Left\Right}$
-\end{lemma}
-
-%$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
-
-Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
-
-For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
-
-\begin{proof}
-
-	By induction on number of cuts + (rank,height) of the left-most top-most cut.
-
-	\textbf{Commutative cases:}\label{commutative-cases}
-
-	\begin{smallequation*}
-		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
-				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-			}{
-			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
-%
-If it does we rewrite it with a fresh variable $v$ first.
-
-%\begin{smallequation*}
-%	\reducesto
-%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-%			}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%			}
-%		}
-%\end{smallequation*}
-%
-%\begin{smallalign*}&
-%	\text{with } \DD_4 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-%		}
-%	}
-%	\\&
-%	\text{and } \DD_5 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}
-%	}
-%\end{smallalign*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
-			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
-		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
-}
-\reducesto
-%	\end{smallequation*}
-%	
-%	\begin{smallequation*}
-\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
-		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-}
-}
-\end{smallequation*}
-
-\textbf{Key cases:}\label{key-cases}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-			\vlhy{}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
-}
-\reducesto
-\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
-	}{
-	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-		\vlhy{}	
-	}
-}
-\reducesto
-\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
-		}
-	}{
-	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}{
-	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
-				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
-			}
-			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
-	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
-}{
-\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
-		}
-	}{
-	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-	}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
-		%			}{
-		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
-		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
-		%					\vlhy{}
-		%					}
-		%				}
-		%			}
-	}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-		}
-	}{
-	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
-	}	
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
-		}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
-		}
-	}
-}{
-\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
-}
-\end{smallequation*}
-\end{proof}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-
-	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
-
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-	In each case, we reason by induction on the height of $\DD$.
-
-	\begin{itemize}
-		\item $\llabrn\IMP$:
-		For a proof of height $1$, it is straightforward.
-		%
-		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-		%
-		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-		First let us fix a given index $y$ that does not appear in $\DD$.
-
-		If we start with a proof
-		\begin{smallequation*}
-			\DD = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-				}	
-			}
-		\end{smallequation*}
-
-		Then by induction hypothesis there exists a proof 
-		\begin{smallequation*}
-			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-		Therefore, we have the proof
-		\begin{smallequation*}
-			\DD^{\invr{\llabrn\IMP}} = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-				}
-			}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD$.
-
-		If we start with a proof 
-		\begin{smallequation*}
-			\vlderivation{
-				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-				}{
-				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-			}
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-	%
-	\item $\llabrn\DIA$:
-
-	If we start with a proof
-	\begin{smallequation*}
-		\DD = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-			}	
-		}
-	\end{smallequation*}
-
-	Then by induction hypothesis there exists a proof 
-	\begin{smallequation*}
-		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD'$.
-
-	Therefore, we have the proof
-	\begin{smallequation*}
-		\DD^{\invr{\llabrn\DIA}} = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-			}
-		}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-	If we start with a proof 
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-			}	
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
-
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
-%
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
-%
-
-\begin{definition}
-A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
-In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
-On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these are presented in the system $\labIKp$ as follows:
-
-\begin{center}
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				}
-				\\\\
-				\hspace{15mm}
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
-
-\end{center}
-
-\bigskip
-
-A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
-
-\begin{itemize}
-	\item Rule $\rn{F1}$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-			\\\\
-			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-			\\\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\hspace{8mm}
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-\end{center}
-
-You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
-
-\begin{itemize}
-	\item Rule $\llabrn\AND$:
-
-	%The system $\labIKp$ presents the next rule for the conjunction left:
-
-	%\begin{center}
-	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-	%\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\rlabrn\OR$:
-
-	Let the rule presented in $\labIKp$ for disjunction right be as follows:
-
-	\begin{center}
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-	\end{center}
-
-	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\\\\
-			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
-			\\\\
-			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-			\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-A more detailed explanation for some rules is below:
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$.
-	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
-
-\bigskip
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\multicolumn{2}{c}{
-				\hspace{9mm}
-				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-			}
-			\\
-			\multicolumn{2}{c}{
-				\hspace{10mm}
-				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-			}
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-The rule for implication right is explained below:
-
-\begin{itemize}
-	\item Rule $\rlabrn\IMP$.
-	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
-\end{itemize}
-
-\section{A complete and sound system for intuitionistic modal logics}
-%
-Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
-%
-Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
-%
-Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
-%We show that each rule from our system is sound.
-%
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-The proof is a careful adaptation of standard techniques.
-%
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
-As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
-%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
-\bigskip
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlhy {}
-										}
-									}
-								}
-							}{
-%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-										\vlhy {\qquad\vdots\qquad}
-%										}
-%									}
-%								}
-%							}
-						}
-					}
-				}
-			}
-		}
-	}
-}$
-}$$
-%\end{example}
-
-%\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-}
-$
-}
-$$
-%\end{example}
-
-\begin{lemma}\label{lem:weak}\hbox{}\quad
-	\begin{enumerate}
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
-
-	%	\item 
-	%	If there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-	%	then there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Standard.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}\label{sec:ext}
-
-The main goal of this section is to generate stronger logics adding new axioms to our system.
-We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
-
-In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
-%
-These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
-
-Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-\bigskip
-
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
-why??}
-
-Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
-
-$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
-
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-\begin{figure}[h]
-	\begin{center}
-		$
-		\xymatrix{
-			& u' \ar@{.>}[ddr]^{R^l} \\
-			& u \ar@{.>}[u]^{\le} \\
-			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
-			& v \ar@{.>}[ur]_{R^n}
-		}
-		$
-	\end{center}
-	\label{fig:gklmn}
-	\caption{$\agklmn$ axiom for intuitionistic case}
-\end{figure}
-
-Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
-
-\bigskip
-
-\begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
-\end{center}
-
-\bigskip
-
-We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
-
-\begin{theorem}
-	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
-\end{theorem}
-
-\begin{proof}
-	\begin{center}
-		\scalebox{0.93}{
-			$\vlderivation {\vlin {\rlabrn{\IMP}}
-				{y \mbox{ fresh}}
-				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\rlabrn{\BOX}}
-					{z, w \mbox{ fresh} }
-					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
-					{\vlin {\llabrn{\DIA}}
-						{u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
-						{\vlin {\rn{F_2}}
-							{t \mbox{ fresh}}
-							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-							{\vlin {\gklmn}
-								{t', j \mbox{ fresh}}
-								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-								{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-									{\vlin {\rn{trans}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-										{\vlin {\llabrn{\BOX}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-											{\vlin {\rn{refl}}
-												{}
-												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-												{\vlin {\rn{id}}
-													{}
-													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-													{\vlhy {}}}}}}}}}}}}$}
-	\end{center}
-\end{proof}
-
-In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
-
-\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
-	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
-	\end{enumerate}
-	%\textbf{Probably F2g???}
-\end{lemma}
-
-Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Bibliography
+%\nocite{*}
 \bibliographystyle{alpha}
@@
 \end{document}
-
-%\begin{figure}[h]
-%\begin{center}
-%$\vlderivation{\vlinf{\id}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\B, \Left, x\colon \bot \SEQ z\colon A}{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\B, \Left \SEQ x \colon \top}{}}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\andleflab}{}{\B,\Left, x \colon \vls(A.B) \SEQ z \colon C}{\B, \Left, x\colon \vls(A.B,\labels{x}{A}, \labels{x}{B} \SEQ z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\B,\Left \SEQ x \colon \vls(A.B)}{\B, \Left \SEQ \labels{x}{A}}{\B, \Left \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%$\vliinf{\orleflab}{}{\B, \Left, x \colon \vls[A.B] \SEQ  \colon C}{\B, \Left, x \colon \vls[A.B], \labels{x}{A} \SEQ z \colon C}{\B, \Left, x \colon \vls[A.B], x   \colon   B \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\orriglabo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x   \colon   A}$
-%\hspace{7mm}$\vlinf{\orriglabt}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x \colon  B}$
-%
-%\vspace{2mm}
-%
-%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \IMP B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \IMP B, \labels{x}{B} \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \IMP B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%
-% $\vlderivation {\vlinf{\bllab}{}{\B, x \rel y, \Left x \colon \BOX A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z \colon B}}$
-%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\B, \Left \SEQ x \colon \BOX A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\dllab}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \DIA A, y \colon A \SEQ z \colon B}$
-%\hspace{5mm}$\vlinf{\drlab}{}{\B, x \rel y, \Left,  \SEQ x \colon \DIA A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\end{center}
-%\caption{System labIK}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	
-%	\begin{center}
-%		
-%		$\vlderivation { \vlin {\ids}{}{\B, \Left, \labels{x}{A} \SEQ x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\B, \Left, x \colon \bot \SEQ z\colon A}{\vlhy {}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vlin {\svlef}{}{\B, \Left, x \colon \vls(A.B) \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\B, \Left, \SEQ x \colon \vls(A.B)}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		
-%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
-%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
-%		
-%	\end{center}
-%	
-%	\caption{System $\lab\IK$}
-%	\label{fig:labIK}
-%\end{figure}
-%
-%\begin{theorem}[Simpson~\cite{Simpson}]
-%	\label{thm:simpson-sound-compl}
-%	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	\small
-%	\centering
-%
-%		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
-%		\hspace{5mm}
-%		$\vlinf{\llabrn\bot}{}{\B, \Left, x\colon \bot \SEQ \Right}{}$
-%		\hspace{5mm}
-%		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, x \colon \top}{}$
-%%		
-%%		\vspace{4mm}
-%		\\[1.5ex]
-%%		
-%		$\vlinf{\llabrn\AND}{}{\B,\Left, x \colon \vls(A.B) \SEQ \Right}{\conjlef}$
-%		\hspace{7mm}
-%		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ \Right}{\B, \Left, x   \colon   A \SEQ \Right}{\B, \Left, x   \colon   B \SEQ \Right}$
-%		\hspace{7mm}
-%		$\vlinf{\sorig}{}{\B, \Left \SEQ \Right, x \colon \vls[A.B]}{\B, \Left \SEQ \Right, x   \colon   A, x   \colon   B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \IMP B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlderivation {\vlinf{\sbl}{}{\B, \Left, x \le y, y \rel z, x \colon \BOX A \SEQ \Right}{\B,\Left, x \le y, y \rel z, x \colon \BOX A, z \colon A \SEQ \Right}}$
-%		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \SEQ \Right, x \colon \BOX A}{\B, \Left, x \le y, y \rel z \SEQ \Right, z \colon A}$
-%		
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ \Right}{\B, \Left, x \rel y, y \colon A \SEQ \Right}$
-%		\hspace{5mm}$\vlinf{\sdr}{}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A, y \colon A}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\refl}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-%		\hspace{7mm} $\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\rn{F_1}}{\text{\footnotesize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-%		%
-%		$\vlinf{\rn{F_2}}{\text{\footnotesize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-%	
-%	\caption{System $\labIKp$}
-%	\label{fig:labHIK}
-%\end{figure}

### 2019-10-03 caleidoscope/old-text.tex

--- 2019-09-30 caleidoscope/caleidoscope.tex
@@
-\documentclass[a4paper]{article}
-
-%\usepackage{aiml18macro}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage[noxy]{virginialake}                        
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath,amsthm} 
-\usepackage{mathtools}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage{pgf}
-\usepackage{array}
-\usepackage[all]{xy}
-\usepackage{tikz}
-%\usepackage{hyperref}
-\usepackage{pgffor}
-
-	%%
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{fact}[theorem]{Fact}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-	%%
-\theoremstyle{definition}
-\newtheorem{observation}[theorem]{Observation}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-\newtheorem{remark}[theorem]{Remark}
-	%%
-
-\tikzset{
-	annotated cuboid/.pic={
-		\tikzset{%
-			every edge quotes/.append style={midway, auto},
-			/cuboid/.cd,
-			#1
-		}
-		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
-		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
-		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
-		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
-
-		;
-	},
-	/cuboid/.search also={/tikz},
-	/cuboid/.cd,
-	width/.store in=\cubex,
-	height/.store in=\cubey,
-	depth/.store in=\cubez,
-	units/.store in=\cubeunits,
-	scale/.store in=\cubescale,
-	width=10,
-	height=10,
-	depth=10,
-	units=cm,
-	scale=.1,
-}
-%tikz parameters
-
-\tikzstyle{point}=[circle,draw]
-\usetikzlibrary{arrows,automata,shapes,decorations.markings,
-	decorations.pathmorphing,backgrounds,fit,snakes,calc}
-
-%\usepackage{float}
-%\floatstyle{boxed} 
-%\restylefloat{figure}
-
-\usepackage{colonequals}
-\usepackage{bm}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Comments  
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
-\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
-
-%%% General
-\input{macros}
-\newcommand{\B}{\mathcal{R}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
-
-%%% Systems
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\ISfour}{\mathsf{IS4}}
-\newcommand*{\Sfour}{\mathsf{S4}}
-
-\newcommand{\fourax}{\mathsf{4}}
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-
-%%% Labelled sequents
-\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
-\newcommand{\SEQ}{\Longrightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\bullet}
-\newcommand*{\rel}{R}
-
-\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Equation environments
-\newdimen\mydisplayskip
-\mydisplayskip=.4\abovedisplayskip
-\newenvironment{smallequation}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
-\newenvironment{smallequation*}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
-\newenvironment{smallalign}
-{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
-\newenvironment{smallalign*}
-{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
-%
-\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
-\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
-%
-%
-\makeatletter
-\newbox\@conclbox
-\newdimen\@conclheight
-%
-%%%%%%
-\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
-\newcommand\vlderiibase[5]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%%
-\newcommand\vlderibase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlin{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%
-\newcommand\vlderidbase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlid{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-	%
-	\makeatother
-	%
-%%%General maths
-\newcommand*{\reducesto}{\quad{\leadsto}\quad}
-
-%%%%%%%%%%%%%%%%%
-
-%\newcommand{\height}[1]{\mathrm{ht}(#1)}
-\newcommand{\height}[1]{|#1|}
-
-\newcommand{\quand}{\quad\mbox{and}\quad}
-\newcommand{\qquand}{\qquad\mbox{and}\qquad}
-\newcommand{\quadcm}{\rlap{\quad,}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%The following line defines the page header consisting of the surnames of the authors.
-% Please include only the last names! 
-% Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
-
-\begin{document}
-
-%\begin{frontmatter}
-  \title{A fully labelled proof system for intuitionistic modal logics}
-  \author{Sonia Marin \and %}
-%  \todo{New university?}
-%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
-%    \author{
-      Marianela Morales %}
- \and
-% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
-% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
-%      \author{
-        Lutz Stra{\ss}burger }
-% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-
-  \maketitle
-
- \begin{abstract}
-
-   In this paper we present a labelled sequent system for
-   intuitionistic modal logics such that there is not only one, but
-   two relation symbols for the labels: one for the accessibility
-   relation associated with the Kripke semantics for normal modal logics and
-   one for the preorder relation associated with the Kripke semantics
-   for intuitionistic logic.
-   %%
-   This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logics. As a
-   consequence it can encompass a wider range of intuitionistic modal
-   logics than standard labelled systems.
-   %%
-   We also show an internal cut elimination proof for our system.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
-  \end{abstract}
-
-  %% \begin{keyword}
-  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  %% \end{keyword}
-% \end{frontmatter}
-
-  %\maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{get bib-file right}
-
-\section{Introduction}\label{sec:intro}
-
-Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
-\emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive systems to a broad range
-of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
-labelled calculi have the advantage of being more uniform and being able to 
-accommode more logics.
-
-Standard labelled sequent calculi attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally admit so called
-\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
-binary relation symbol. These calculi work best for logics with
-standard Kripke semantics, as in this case the relation $\rel$ is used
-to encode the accessibility relation in the Kripke models, and the
-frame conditions corresponding to the desired logic can be directly
-encoded as inference rules. Prominent examples are classical modal
-logics and intuitionistic propositional logic, where, e.g., the frame
-condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
-inference rule
-\begin{equation}
-  \label{eq:Rtrans}
-  \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
-\end{equation}
-where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas.
-
-However,
-in this paper we are concerned with \emph{intuitionistic modal
-  logics}, whose Kripke semantics is based on \emph{birelational}
-frames, i.e., they have two binary relations instead of one: one
-relation $R$ that corresponds to the accessibility relation in
-ordinary Kripke frames for modal logics, and a relation $\le$ that
-corresponds to the future relation in ordinary Kripke frames for
-intuitionistic logic. Consequently, standard labelled systems for
-these logics have certain shortcomings:
-\begin{enumerate}
-\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
-  versions of the $\fourax$-axiom
-  \begin{equation}
-    \label{eq:4ax}
-    \fm{\BOX A\IMP \BOX\BOX A}
-    \qquand
-    \fm{\DIA\DIA A\IMP\DIA A}
-    \quadcm
-  \end{equation}
-  as they are equivalent in classical
-  modal logic. However, in intuitionistic modal logic they are not
-  equivalent, and even though the logic $\ISfour$, i.e., the
-  intuitionistic version of the modal logic $\Sfour$, contains both
-  axioms, they can be added independently to the logic $\IK$ (the
-  intuitionistic version of $\K$). However, the proof theory of these
-  new logics has not been studied before, as no existing labelled (or
-  label-free) proof system can handle them, even though the
-  corresponding frame conditions
-  \begin{equation}
-    \label{eq:4frame}
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-    \quand
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-    \;,
-  \end{equation}
-  respectively, have already been studied
-  in~\cite{plotkin:stirling:86}.
-  \item The correspondence between the syntax and the semantics is not
-  as clean as one would expect. As only the $R$-relation (and not the
-  $\le$-relation) of the frame is visible in an ordinary labelled
-  sequent, we only have that a sequent $\Gamma$ is provable if and
-  only if is is valid in all \emph{graph-consistent}\footnote{This
-    means that every layer in the model can be lifted to any future of
-    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
-  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
-\end{enumerate}
-In order to address these two issues we propose here to extend the
-notion of labelled sequent by also allowing relational atoms of the
-form $\futs xy$. Consequently, we can easily translate the frame
-conditions in~\eqref{eq:4frame} into inference rules:
-\begin{equation}
-  \label{eq:4rules}
-  \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-     \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
-  \qquand
-  \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
-\end{equation}
-This allows us to define cut-free deductive systems for a wide range
-of logics that could not be treated before.  Furthermore, the relation
-between syntax and semantics is as one would expect: A sequent is
-provable in our system if and only if it is valid in all models.
-
-Besides that, there is another pleasant observation to make about our
-system. Ordinary labelled sequent systems for intuitionistic modal
-logic are single-conclusion~\cite{simpson:phd}. The same is true for
-the corresponding nested sequent
-systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
-Maehara style multiple-conclusion systems in nested
-sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
-labelled sequents. However, also in these systems there are rules
-($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
-premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
-intuitionistic logic. Our system eliminates this
-discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.
-
-\medskip
-
-This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
-Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
-The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
-
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
-
-\section*{Introduction(old version, to be deleted)}
-\todo{We should work on the introduction}
-
-One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.
-
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
-%
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as
-used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
-Negri~\cite{Negri}. 
-%
-These formalisms make explicit use not only of
-labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
-%
-In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
-logics) and the \emph{preorder relation} (for intuitionistic
-logic), using the full power of the bi-relational semantics for
-intuitionistic modal logics,
-and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.
-
-\todo{Simpson does not have internal cut-elimination}
-
-\sonia{
-  \begin{itemize}
-  \item internal vs externl calculi
-  \item extesion to axioms are truly intuitionistic (not just the
-    classical versions as in Simpson style)
-  \item connection with semantics compared to graph homomorphism
-    restiction in Simpson and ``indexed nested systems''
-  \end{itemize}
-}
-
-\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
-  \begin{itemize}
-  \item what we do:
-    \begin{itemize}
-    \item first systems (nested and labelled) for intuitionistic modal
-      logic where ``single conclusion'', i.e., only one formula on the
-      right.
-    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
-    \item Still rules that forced single formula on the right (white implication and white box)
-    \item by allowing both relations of the model in the proof system
-      we go to genuinely multiple conclusion: never ever a formula on
-      the right has to be deleted during proof search.
-    \end{itemize}
-  \item why we do it: 
-    \begin{itemize}
-    \item getting things right: labelled systems for classical modal
-      logics, or plain propositional intuiionistic logic have one
-      binary relation, which is exactly the relation of the standard
-      Kripke semantics. The standard Kripke semantics for
-      intuitionistic modal logic is birelational, with a strong
-      connectiion between the two binary relations. A clean labelled
-      system for these logics should incorporate both relations.
-    \item We get new logics.  In the standard nested sequent
-      or labelled sequent system for intuitionistic modal logic we
-      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
-      but here we can have them separtely.
-    \end{itemize}
-  \item how we do it:
-    \begin{itemize}
-    \item We start from the Maehara nested sequent system (which can
-      be translated straightforwardly into a labelled system with one
-      relation $R$.
-    \item the rules for $\AND$ and $\OR$ are trivial and as expected
-      they can be presented such that they are invertible on the left
-      and the right, they do not concern the relations $R$ and $\le$. 
-    \item So should be the rules for $\IMP$-left and $\BOX$-left and
-      identity, but there is a subtlety; see below...
-    \item the rules for $\DIA$ are also straightforward, as they
-      concern only $R$ but not $\le$.
-    \item The rules $\BOX$-right and $\IMP$-right are the ones that
-      force single conclusion in the Maehara system. This means that
-      here they create a future, using the relation $\le$.
-    \item In order to make everything work together, this forces us to
-      have reflexivity and transitivity of $\le$, explicely as rules
-      in the system, and have rules for the F1 and F2 conditions
-      making the relations $R$ and $\le$ go together.
-    \item As a consequence we also need a rule realizing monotonicity
-      for the formulas on the right.
-    \item However, we designed the system such that monotonicity is
-      admisible by encorporating it into the rules for identity,
-      $\IMP$-left and $\BOX$-left.
-    \end{itemize}
-  \end{itemize}
-}
-%
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{Intuitionistic modal logics}\label{sec:intmod}
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
-%
-$$
-\fm A \coloncolonequals
-\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
-$$
-%
-
-Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
-Five axioms have been considered as primitives in the literature.
-An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
-%
-
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
-\begin{itemize}
-	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
-	\begin{equation*}
-	\label{eq:ik}%\hskip-2em
-	\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
-	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
-	&
-	\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
-	&
-	\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
-	\\
-	\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
-	&
-	\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
-	\end{array}
-	\end{equation*}
-\end{itemize}
-
-The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
-The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}.
-However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
-Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
-However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
-
-The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic.
-It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
-
-The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
-%
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-
-\begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
-	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
-	\begin{enumerate}
-		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
-			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
-		}
-		\end{equation*}
-
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
-			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
-		}
-		\end{equation*}
-	\end{enumerate}
-	%	
-\end{definition}
-
-\begin{definition}
-	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
-	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
-\end{definition}
-
-We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:
-
-\begin{equation}\label{eq:kripke}
-	\begin{array}{rcl}
-	%\parbox{30em}{%
-
-		\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
-
-		\M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.
-
-	\end{array}
-\end{equation}
-Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
-%
-We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
-
-From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
-	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
-\end{proposition}
-
-\begin{definition}
-	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
-	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
-\end{definition}
-
-%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%
-%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-
-Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.
-
-\begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
-	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
-
-%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
-
-\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
-\begin{theorem}[\cite{plotkin:stirling:86}]
-	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
-
-	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
-
-\end{theorem}
-
-% we would like to consider special restrictions on these bi-relational frames.
-For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%\section{Intuitionistic modal logics}\label{sec:intmod}
-%
-%	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%	%
-%	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
-%	%
-%	$$
-%	A \coloncolonequals
-%	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
-%	$$
-%	%
-%        \lutz{why do we have $\TOP$?}
-%	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
-%
-%Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%%
-%Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
-%%
-%
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-%%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
-%%
-%It is obtained from intuitionistic propositional logic by adding:
-%\begin{itemize}
-%\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
-%\item the following five variants of the \emph{distributivity axiom}:
-%\begin{equation*}
-%\label{eq:ik}%\hskip-2em
-%\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
-%\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
-%&
-%\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
-%&
-%\kax[5]\colon&\DIA\BOT\IMP\BOT
-%\\
-%\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
-%&
-%\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
-%\end{array}
-%\end{equation*}
-%\end{itemize}
-%
-%The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
-%%
-%It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-%
-%\begin{definition}
-%	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
-%%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-%	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
-%	\begin{enumerate}
-%		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]_R  & v' \\
-%				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
-%			}
-%			\end{equation*}
-%		
-%		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]^R & v' \\
-%				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
-%			}
-%			\end{equation*}
-%	\end{enumerate}
-%%	
-%\end{definition}
-%
-%\begin{definition}
-%	\label{model}
-%	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-%	if $w \le w'$ then $V(w)\subseteq V(w')$.
-%\end{definition}
-%
-%We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
-%%
-%Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-%\begin{equation}
-%  \label{eq:kripke}
-%  \parbox{30em}{%
-%  $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
-%
-%$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
-%
-%$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
-%
-%$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
-%
-%$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
-%
-%%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-%}
-%\end{equation}
-%\todo{fix typography}
-%
-%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
-%
-%From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-%\begin{proposition}(Monotonicity) 
-%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
-%\end{proposition}
-%
-%
-%
-%\begin{definition}
-%	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-%%
-%	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
-%\end{definition}
-%
-%
-%
-%%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%%
-%%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-%
-%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
-%
-%\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-%	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{The system}\label{sec:system}
-
-In this section we present our fully labelled sequent proof system
-for intuitionistic modal logics. The starting point is the notion of a
-\emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
-x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
-at world $\lb x$. A \emph{relation atom} is either an expression
-$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
-intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. This is enough to define the notion of
-\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
-multi-sets of labelled formulas, all written as list, separated by commas.
-
-\begin{figure}[!t]
-  \begin{center}
-	\fbox{
-%	\begin{minipage}{.95\textwidth}
-	\begin{tabular}{c@{\quad}c}
-		$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-		&
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		%\quad
-		%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-		\\\\
-		$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-		\\\\
-		$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
- 		$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
-% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
- 		}
-		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-		\\\\
-		$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-		&
-		$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-		\\
-		\multicolumn{2}{c}{
-		$\mbox{\hbox to .9\linewidth{\dotfill}}$
-		}
-		\\
-		$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-		&
-		$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-		}
-		\\\\
-		\multicolumn{2}{c}{
-		$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-		}
-	\end{tabular}		
-%\end{minipage}
-}		
-  \end{center}
-  \caption{System $\labIKp$}
-	\label{fig:labIKp}
-\end{figure}
-
-Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
-We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
-\begin{equation}
-  \label{eq:nomon}
-  \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
-  \quad
-  \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
-  \quad
-  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
-\end{equation}
-that are not sufficient for a complete system, and we will see below
-why. Before, let us first look at the rules $\rlabrn\IMP$ and
-$\rlabrn\BOX$. In the multiple-conlusion nested sequent system
-of~\cite{str:2017maehara}, these are the two rules that force
-single-conclusion. This is the reason why in our system we need the
-$\le$ in the relational atoms; we need to go to the future of the
-current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
-connectives $\IMP$ and $\BOX$ are the ones that need the
-future-relation $\le$. This relation is reflexive and transitive. In
-order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.
-
-Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
-system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
-%
-However, these two rule create new labels, and in order to be
-complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
-\begin{equation}
-  \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
-  \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
-\end{equation}
-Since this rule is a form of contraction, it would cause the same
-problems as contraction in a cut elimination proof. Hence, it is
-preferable to have a system in which this rule is admissible. This is
-the reason why we have monotonicity incorporated in the rules
-$\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
-instead of using the rules in~\eqref{eq:nomon}. Then, not only
-$\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
-shown on the right in~\eqref{eq:mono} above is admissible.
-
-\begin{proposition}
-  \label{prop:mon-adm}
-  The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$.
-\end{proposition}
-
-One can prove this proposition in the same way as one usually proves
-admissibity of contraction in a sequent calculus, by induction on the
-height of the derivation, which in fact would yield a stronger result,
-namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
-  preserving} admissible for $\labIKp$. However, we do not need this
-result in this paper, and therefore we leave it as an exercise to the
-reader. Nonetheless, we will give a short proof of
-Proposition~\ref{prop:mon-adm} at the end of this section.
-
-Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.
-
-\begin{proposition}
-  \label{prop:id}
-	The following general idenity axiom~
-	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
-        ~is admissible for $\labIKp$. 
-\end{proposition}
-
-\begin{proof}
-	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
-	\begin{itemize}
-		%% \item Atomic case
-		%% \begin{smallequation*}
-		%% 	%\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% 	%\reducesto
-		%% 	\vlinf{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
-		%% \end{smallequation*}
-		\item $\fm{A \AND B}$
-		%\begin{smallequation*}
-		%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{}
-		%	\reducesto
-		%\end{smallequation*}
-		\begin{smallequation*}
-			\vlderivation{
-				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
-					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
-							\vlhy{}
-						}
-					}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-	\item $\fm{A \OR B}$
-	%\begin{smallequation*}
-	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
-	%	\reducesto
-	%\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
-					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
-						\vlhy{}
-					}
-				}
-			}{
-			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
-				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{A \IMP B}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-					\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
-								\vlhy{}
-							}
-						}
-					}{
-					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	}
-	\end{smallequation*}
-
-	\item $\fm{\BOX A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
-				\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-					\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
-						\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-							\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-
-	\item $\fm{\DIA A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-%		\reducesto
-%	\end{smallequation*}
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-						\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-							\vlhy{}
-						}
-					}
-				}
-			}
-		}
-	\end{smallequation*}
-        \qedhere
-	\end{itemize}
-\end{proof}
-
-In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
-\begin{equation}
-  \label{eq:cut}
-  \vliiinf{\labrn{cut}}{}{
-    \lseq\B\Left\Right}{
-    \lseq\B\Left{\Right,\labels{z}{C}}}{}{
-    \lseq\B{\Left,\labels{z}{C}}{\Right}}
-\end{equation}
-Then we can summarize soundness and completeness, and cut
-admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
-
-\begin{theorem}\label{thm:cutfree-compl}
-	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
-	%
-	For any formula $A$, the following are equivalent.
-	%
-	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$. 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
-		\item\label{iii} $A$ is provable in $\labIKp$.
-		%
-		\item\label{iv} $A$ is valid in every birelational frame. %satisfying the properties in $\CC$.
-	\end{enumerate}
-\end{theorem}
-
-The proof of this theorem is the topic of the following sections. The
-equivalence of \ref{i} and \ref{iv} has already been stated in
-Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
-\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
-the implication~\ref{ii}$\implies$\ref{iii} is shown in
-Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.
-
-Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
-
-\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
-  The rule $\llabrn{mon}$ can be derived using the general identity and cut:
-  \begin{smallequation*}
-    \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
-          \vlhy{}}}{
-        \vlhy{\quad}}{
-        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
-    }
-  \end{smallequation*}
-  And both these rules are admissible by Proposition~\ref{prop:id} and
-  Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
-  similar.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-In this section we show our system at work, as most of the section
-consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
-
-\begin{theorem}\label{thm:completeness}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{remark}
-  We have seem already in the proof of Proposition~\ref{prop:id} the
-  need of the rule $\rn{F_2}$. In the following proof of
-  Theorem~\ref{thm:completeness} we also see the need of the rules
-  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
-  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
-  \begin{itemize}
-  \item $\kax[1]$:
-    $$
-    \vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
-												{\vlhy {}}}}}}}}}}
-    }
-    $$
-    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-  \item $\kax[2]$:
-    $$
-    \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-									{\vlhy {}}}								}}}}}}
-    }
-    $$
-    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-  \item $\kax[3]$:
-    $$
-    \vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
-				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-									{\vlhy {}}}}}}}}
-		}
-    $$
-  \item $\kax[4]$:
-    $$
-\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-					{\vlin {\color{red}\rn{trans}}
-						{}
-						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-											{\vlhy {}}}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-											{\vlhy {}}}}}}}}}}}
-}
-$$
-where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-\item $\kax[5]$:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
-				{\vlhy {}}}}
-  }
-  $$
-  \end{itemize}
-  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
-			{\vlin {\color{red}\rn{refl}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-				{\vlin {\rn{id}}
-					{}
-					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-					{\vlhy {}}}}}
-  }
-  $$
-
-  Finally, we have to show how the rules of modus ponens and
-  necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necessitation, we can
-  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
-
-  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Soundness}\label{sec:soundness}
-
-In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
-\end{definition}
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$. We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
-\end{definition}
-
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$:
-
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
-	\end{center}
-
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $\lb y, \lb z \in W$ such that $\futs xy$ and $\accs yz$, $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
-From this result, we can say that $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
-Thus, we have already proved that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, then $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
-According to the definition, we proved that the rule $\llabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\BOX$:
-
-	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
-	\end{center}
-
-	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
-Let us assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.
-In particular, $\M_{0} \not \Vdash \labels{x}{\BOX A}$, which means that there exist worlds $\lb y, \lb z$, such that $\futs xy$ and $\accs yz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Finally, we have that $\M_{0} \Vdash \B, \futs xy, \accs yz, \Left$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}, \labels{z}{A}$,  which is the same as $\M_{0} \not \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$.
-Then, by way of contradiction, we proved that the rule $\rlabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\IMP$:
-
-	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
-	\end{center}
-
-	We prove this statement by way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0}$ does not satisfy the conclusion, i.e.
-$\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.
-In particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $\lb y$ such that $\futs xy$ and $\M_{0}, f(\lb y) \Vdash A$ (i.e.
-$\M_{0} \Vdash \labels{y}{A}$) but $\M_{0}, f(\lb y) \Vdash B$, i.e.
-$\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \labels{y}{B}$.
-This means that the model $\M_{0}$ does not satisfy the premise and that is what we wanted to prove.
-Finally, we showed that the rule $\rlabrn\IMP$ is sound.
-
-	\item Rule $\llabrn\DIA$:
-
-	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
-	\end{center}
-
-	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
-	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
-From $\M_{0} \Vdash \labels{x}{\DIA A}$, according to the definition of the $\DIA$ operator, we have that there exists a world $\lb y$ in $\M_{0}$ such that $\accs xy$ and $\M_{0} \Vdash \labels{y}{A}$.
-Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ and we prove that the rule $\llabrn\DIA$ is sound.
-
-	\item Rule $\rlabrn\DIA$:
-
-	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
-
-	\begin{center}
-		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
-	\end{center}
-
-	We prove this statement by way of contradiction.
-Let us assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$, we want to show that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
-for all world $\lb y \in \M_{0}$ where $\accs xy$ we have $\M_{0} \not \Vdash \labels{y}{A}$.
-Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-Finally, assuming that $\M_{0}$ does not satisfy the conclusion, we proved that $\M_{0}$ does not satisfy the premise.
-Then we conclude that the rule $\rlabrn\DIA$ of the system $\labIKp$ is sound.
-\end{itemize}
-
-The other cases are similar and we leave them to the reader.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cut Admissibility}\label{sec:cut-elim}
-In this section we are going to prove the admissibility of cut for $\labIKp$.
-
-\begin{theorem}
-  \label{thm:cut-adm}
-  The rule $\labrn{cut}$ is admissible for $\labIKp$.
-\end{theorem}
-
-This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
-
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is the height of D when seen as a tree, i.e., the length of
-the longest path in the tree from its root to one of its leaves.
-
-We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if for every
-derivation of the conclusion of the rule there are derivations for each of its premisses with at most the same height.
-
-The following two lemmas are standard.
-
-\begin{lemma}
-  \label{lem:weak-adm}
-  The weakening rule
-  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{\begin{lemma}
-  	If there exists a proof  $\vlderivation {\vlpd{\D}{}{\B, \Left \Rightarrow \Right}}$ then there exists a proof $\vlderivation {\vlpd {\Dw}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}}$
-
-  \end{lemma}
-
-  \vspace{3mm}
-
-  \begin{proof}
-  	By induction on the height of $\D$.
-
-  	For a proof of height 1:
-
-  	if $\D$ = $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, x \colon a \Rightarrow \Right, y \colon a}{\vlhy {}}}$ then we take $\Dw$ to be $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, xRy, u \le v, x \colon a, z \colon A \Rightarrow \Right, w \colon B, y \colon a}{\vlhy {}}}$.
-  	\vspace{2mm}
-
-  	For a proof $\D$ of height greater than 1:
-
-  	\begin{center}
-
-  		$\vlderivation{\vlin {$r$}{}{\B, \Left \Rightarrow \Right}{\vlpd {\Done}{}{\B', \Left' \Rightarrow \Right'}}}$
-
-  	\end{center}
-
-  	Then by induction hypothesis there exists a proof
-
-  	\begin{center}
-
-  		$\vlderivation {\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}$
-
-  	\end{center}
-
-  	Therefore, we have the proof
-
-  	\begin{center}
-
-  		$\Dw = \vlderivation {\vlin{}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}{\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}}$
-
-  	\end{center}
-
-  \end{proof}}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:inv}
-  The rules ..... are height-preserving invertible in
-  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
-  height-preserving invertible for the right premise.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma looks like a special case of
-Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using cut as we
-need it to eliminate the cut.
-
-\begin{lemma}
-  The atomic version of $\llabrn{mon}$
-  $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
-  $$
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  	\begin{smallequation*}
-  		\vlderivation{
-  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x''}{a}}{
-  					\vlhy{}
-  				}
-  			}
-  		}
-  		\reducesto
-  		\vlderivation{
-  		\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \futs{x}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlhy{}
-  			}}
-  	}
-  	\end{smallequation*}
-  	\todo{missing case}
-%  	\begin{smallequation*}
-%  		\vlderivation{
-%  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{
-%  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x'}{a}}{
-%  					\vlhy{}
-%  				}
-%  			}
-%  		}
-%  		\reducesto
-%  		\vlinf{\labrn{id}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{}
-%  		\qedhere
-%  	\end{smallequation*}
-\end{proof}
-
-The next lemma is the core of our cut elimination proof.
-
-\begin{lemma}
-  \label{lem:reduction}
-  Given a derivation of shape
-  $$
-  \vlderivation{
-    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
-      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
-      \vlhy{}}{
-      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
-  $$
-  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
-  derivation of ${\lseq\B\Left\Right}$
-\end{lemma}
-
-%$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
-
-Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
-
-For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
-
-\begin{proof}
-
-	By induction on number of cuts + (rank,height) of the left-most top-most cut.
-
-	\textbf{Commutative cases:}\label{commutative-cases}
-
-	\begin{smallequation*}
-		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
-				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-			}{
-			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
-%
-If it does we rewrite it with a fresh variable $v$ first.
-
-%\begin{smallequation*}
-%	\reducesto
-%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-%			}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%			}
-%		}
-%\end{smallequation*}
-%
-%\begin{smallalign*}&
-%	\text{with } \DD_4 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-%		}
-%	}
-%	\\&
-%	\text{and } \DD_5 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}
-%	}
-%\end{smallalign*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
-			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
-		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
-}
-\reducesto
-%	\end{smallequation*}
-%	
-%	\begin{smallequation*}
-\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
-		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-}
-}
-\end{smallequation*}
-
-\textbf{Key cases:}\label{key-cases}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-			\vlhy{}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
-}
-\reducesto
-\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
-	}{
-	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-		\vlhy{}	
-	}
-}
-\reducesto
-\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
-		}
-	}{
-	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}{
-	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
-				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
-			}
-			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
-	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
-}{
-\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
-		}
-	}{
-	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-	}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
-		%			}{
-		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
-		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
-		%					\vlhy{}
-		%					}
-		%				}
-		%			}
-	}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-		}
-	}{
-	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
-	}	
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
-		}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
-		}
-	}
-}{
-\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
-}
-\end{smallequation*}
-\end{proof}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-
-	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
-
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-	In each case, we reason by induction on the height of $\DD$.
-
-	\begin{itemize}
-		\item $\llabrn\IMP$:
-		For a proof of height $1$, it is straightforward.
-		%
-		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-		%
-		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-		First let us fix a given index $y$ that does not appear in $\DD$.
-
-		If we start with a proof
-		\begin{smallequation*}
-			\DD = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-				}	
-			}
-		\end{smallequation*}
-
-		Then by induction hypothesis there exists a proof 
-		\begin{smallequation*}
-			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-		Therefore, we have the proof
-		\begin{smallequation*}
-			\DD^{\invr{\llabrn\IMP}} = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-				}
-			}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD$.
-
-		If we start with a proof 
-		\begin{smallequation*}
-			\vlderivation{
-				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-				}{
-				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-			}
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-	%
-	\item $\llabrn\DIA$:
-
-	If we start with a proof
-	\begin{smallequation*}
-		\DD = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-			}	
-		}
-	\end{smallequation*}
-
-	Then by induction hypothesis there exists a proof 
-	\begin{smallequation*}
-		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD'$.
-
-	Therefore, we have the proof
-	\begin{smallequation*}
-		\DD^{\invr{\llabrn\DIA}} = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-			}
-		}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-	If we start with a proof 
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-			}	
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
-\end{proof}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
+
+\begin{theorem}\label{thm:cutfree-compl}
+	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
+	%
+	For any formula $A$, the following are equivalent.
+	%
+	\begin{enumerate}
+		\item\label{i} $A$ is a theorem of $\IK$ 
+		%
+		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
+%		
+%		\todo{}
+		\smash{%\fbox{
+			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
+		}%}
+		%
+
+                \lutz{why is that multiplicative on $\B$ and additive on the rest???}
+		\item\label{iii} $A$ is provable in $\labIKp$
+		%
+		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
+	\end{enumerate}
+\end{theorem}
 
@@
 		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
+		$\vlderivation{\vlhtr{\DD^{\BOT}}{\B, \Left \SEQ \Right}}$
 
@@
 	%	then there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
+	%	$\vlderivation{\vlhtr{\DD^{\TOP}}{\B, \Left \SEQ \Right}}$
 
@@
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}\label{sec:ext}
-
-The main goal of this section is to generate stronger logics adding new axioms to our system.
-We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
-
-In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
-%
-These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
-
-Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-\bigskip
-
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
-why??}
-
-Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
-
-$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
-
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-\begin{figure}[h]
-	\begin{center}
-		$
-		\xymatrix{
-			& u' \ar@{.>}[ddr]^{R^l} \\
-			& u \ar@{.>}[u]^{\le} \\
-			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
-			& v \ar@{.>}[ur]_{R^n}
-		}
-		$
-	\end{center}
-	\label{fig:gklmn}
-	\caption{$\agklmn$ axiom for intuitionistic case}
-\end{figure}
-
-Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
-
-\bigskip
-
-\begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
-\end{center}
-
-\bigskip
-
-We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
-
-\begin{theorem}
-	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
-\end{theorem}
-
-\begin{proof}
-	\begin{center}
-		\scalebox{0.93}{
-			$\vlderivation {\vlin {\rlabrn{\IMP}}
-				{y \mbox{ fresh}}
-				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\rlabrn{\BOX}}
-					{z, w \mbox{ fresh} }
-					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
-					{\vlin {\llabrn{\DIA}}
-						{u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
-						{\vlin {\rn{F_2}}
-							{t \mbox{ fresh}}
-							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-							{\vlin {\gklmn}
-								{t', j \mbox{ fresh}}
-								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-								{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-									{\vlin {\rn{trans}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-										{\vlin {\llabrn{\BOX}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-											{\vlin {\rn{refl}}
-												{}
-												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-												{\vlin {\rn{id}}
-													{}
-													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-													{\vlhy {}}}}}}}}}}}}$}
-	\end{center}
-\end{proof}
-
-In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
-
-\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
-	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
-	\end{enumerate}
-	%\textbf{Probably F2g???}
-\end{lemma}
-
-Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
-
-\bibliographystyle{alpha}
-\bibliography{references}
-
-\end{document}
 

### 2019-10-03 caleidoscope/system.tex

--- 2019-09-30 caleidoscope/caleidoscope.tex
@@
-\documentclass[a4paper]{article}
-
-%\usepackage{aiml18macro}
-
-\usepackage[margin=2cm]{geometry}
-\usepackage[noxy]{virginialake}                        
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath,amsthm} 
-\usepackage{mathtools}
-\usepackage{enumerate}
-\usepackage{graphicx}
-\usepackage{bm}
-\usepackage{xcolor}
-\usepackage{pgf}
-\usepackage{array}
-\usepackage[all]{xy}
-\usepackage{tikz}
-%\usepackage{hyperref}
-\usepackage{pgffor}
-
-	%%
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{conjecture}[theorem]{Conjecture}
-\newtheorem{fact}[theorem]{Fact}
-\newtheorem{claim}[theorem]{Claim}
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lem}[theorem]{Lemma}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-	%%
-\theoremstyle{definition}
-\newtheorem{observation}[theorem]{Observation}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{problem}[theorem]{Problem}
-\newtheorem{construction}[theorem]{Construction}
-\newtheorem{remark}[theorem]{Remark}
-	%%
-
-\tikzset{
-	annotated cuboid/.pic={
-		\tikzset{%
-			every edge quotes/.append style={midway, auto},
-			/cuboid/.cd,
-			#1
-		}
-		\draw [every edge/.append style={pic actions, opacity=.5}, pic actions]
-		(0,0,0) coordinate (o) -- ++(-\cubescale*\cubex,0,0) coordinate (a) -- ++(0,-\cubescale*\cubey,0) coordinate (b) edge coordinate [pos=1] (g) ++(0,0,-\cubescale*\cubez)  -- ++(\cubescale*\cubex,0,0) coordinate (c) -- cycle
-		(o) -- ++(0,0,-\cubescale*\cubez) coordinate (d) -- ++(0,-\cubescale*\cubey,0) coordinate (e) edge (g) -- (c) -- cycle
-		(o) -- (a) -- ++(0,0,-\cubescale*\cubez) coordinate (f) edge (g) -- (d) -- cycle;
-
-		;
-	},
-	/cuboid/.search also={/tikz},
-	/cuboid/.cd,
-	width/.store in=\cubex,
-	height/.store in=\cubey,
-	depth/.store in=\cubez,
-	units/.store in=\cubeunits,
-	scale/.store in=\cubescale,
-	width=10,
-	height=10,
-	depth=10,
-	units=cm,
-	scale=.1,
-}
-%tikz parameters
-
-\tikzstyle{point}=[circle,draw]
-\usetikzlibrary{arrows,automata,shapes,decorations.markings,
-	decorations.pathmorphing,backgrounds,fit,snakes,calc}
-
-%\usepackage{float}
-%\floatstyle{boxed} 
-%\restylefloat{figure}
-
-\usepackage{colonequals}
-\usepackage{bm}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Comments  
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
-\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
-
-%%% General
-\input{macros}
-\newcommand{\B}{\mathcal{R}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
-
-%%% Systems
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\ISfour}{\mathsf{IS4}}
-\newcommand*{\Sfour}{\mathsf{S4}}
-
-\newcommand{\fourax}{\mathsf{4}}
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-
-%%% Labelled sequents
-\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\color{blue}{#2}}}
-\newcommand{\SEQ}{\Longrightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\bullet}
-\newcommand*{\rel}{R}
-
-\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Equation environments
-\newdimen\mydisplayskip
-\mydisplayskip=.4\abovedisplayskip
-\newenvironment{smallequation}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
-\newenvironment{smallequation*}
-{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
-\newenvironment{smallalign}
-{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
-\newenvironment{smallalign*}
-{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
-%
-\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
-\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
-%
-%
-\makeatletter
-\newbox\@conclbox
-\newdimen\@conclheight
-%
-%%%%%%
-\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
-\newcommand\vlderiibase[5]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%%
-\newcommand\vlderibase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlin{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-%
-\newcommand\vlderidbase[4]{{%
-		\setbox\@conclbox=\hbox{$#3$}\relax%
-		\@conclheight=\ht\@conclbox%
-		\setbox\@conclbox=\hbox{$%
-			\vlderivationnc{%
-				\vlid{#1}{#2}{\box\@conclbox}{#4}%
-			}$}%
-		\lower\@conclheight\box\@conclbox%
-	}}
-	%
-	\makeatother
-	%
-%%%General maths
-\newcommand*{\reducesto}{\quad{\leadsto}\quad}
-
-%%%%%%%%%%%%%%%%%
-
-%\newcommand{\height}[1]{\mathrm{ht}(#1)}
-\newcommand{\height}[1]{|#1|}
-
-\newcommand{\quand}{\quad\mbox{and}\quad}
-\newcommand{\qquand}{\qquad\mbox{and}\qquad}
-\newcommand{\quadcm}{\rlap{\quad,}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%The following line defines the page header consisting of the surnames of the authors.
-% Please include only the last names! 
-% Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
-
-\begin{document}
-
-%\begin{frontmatter}
-  \title{A fully labelled proof system for intuitionistic modal logics}
-  \author{Sonia Marin \and %}
-%  \todo{New university?}
-%  \address{IT-Universitetet i K{\o}benhavn \\ Denmark }
-%    \author{
-      Marianela Morales %}
- \and
-% \marianela{I think that now I have the same as Lutz, right?} No, the other order...
-% \address{ LIX, \'Ecole Polytechnique  \& Inria Saclay\\ France}
-%      \author{
-        Lutz Stra{\ss}burger }
-% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-
-  \maketitle
-
- \begin{abstract}
-
-   In this paper we present a labelled sequent system for
-   intuitionistic modal logics such that there is not only one, but
-   two relation symbols for the labels: one for the accessibility
-   relation associated with the Kripke semantics for normal modal logics and
-   one for the preorder relation associated with the Kripke semantics
-   for intuitionistic logic.
-   %%
-   This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logics. As a
-   consequence it can encompass a wider range of intuitionistic modal
-   logics than standard labelled systems.
-   %%
-   We also show an internal cut elimination proof for our system.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
-  \end{abstract}
-
-  %% \begin{keyword}
-  %% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-  %% \end{keyword}
-% \end{frontmatter}
-
-  %\maketitle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\todo{get bib-file right}
-
-\section{Introduction}\label{sec:intro}
-
-Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
-\emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive systems to a broad range
-of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron:elc96} or nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
-labelled calculi have the advantage of being more uniform and being able to 
-accommode more logics.
-
-Standard labelled sequent calculi attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally admit so called
-\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
-binary relation symbol. These calculi work best for logics with
-standard Kripke semantics, as in this case the relation $\rel$ is used
-to encode the accessibility relation in the Kripke models, and the
-frame conditions corresponding to the desired logic can be directly
-encoded as inference rules. Prominent examples are classical modal
-logics and intuitionistic propositional logic, where, e.g., the frame
-condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
-inference rule
-\begin{equation}
-  \label{eq:Rtrans}
-  \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
-\end{equation}
-where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas.
-
-However,
-in this paper we are concerned with \emph{intuitionistic modal
-  logics}, whose Kripke semantics is based on \emph{birelational}
-frames, i.e., they have two binary relations instead of one: one
-relation $R$ that corresponds to the accessibility relation in
-ordinary Kripke frames for modal logics, and a relation $\le$ that
-corresponds to the future relation in ordinary Kripke frames for
-intuitionistic logic. Consequently, standard labelled systems for
-these logics have certain shortcomings:
-\begin{enumerate}
-\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
-  versions of the $\fourax$-axiom
-  \begin{equation}
-    \label{eq:4ax}
-    \fm{\BOX A\IMP \BOX\BOX A}
-    \qquand
-    \fm{\DIA\DIA A\IMP\DIA A}
-    \quadcm
-  \end{equation}
-  as they are equivalent in classical
-  modal logic. However, in intuitionistic modal logic they are not
-  equivalent, and even though the logic $\ISfour$, i.e., the
-  intuitionistic version of the modal logic $\Sfour$, contains both
-  axioms, they can be added independently to the logic $\IK$ (the
-  intuitionistic version of $\K$). However, the proof theory of these
-  new logics has not been studied before, as no existing labelled (or
-  label-free) proof system can handle them, even though the
-  corresponding frame conditions
-  \begin{equation}
-    \label{eq:4frame}
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-    \quand
-    \forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-    \;,
-  \end{equation}
-  respectively, have already been studied
-  in~\cite{plotkin:stirling:86}.
-  \item The correspondence between the syntax and the semantics is not
-  as clean as one would expect. As only the $R$-relation (and not the
-  $\le$-relation) of the frame is visible in an ordinary labelled
-  sequent, we only have that a sequent $\Gamma$ is provable if and
-  only if is is valid in all \emph{graph-consistent}\footnote{This
-    means that every layer in the model can be lifted to any future of
-    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
-  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-  and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
-\end{enumerate}
-In order to address these two issues we propose here to extend the
-notion of labelled sequent by also allowing relational atoms of the
-form $\futs xy$. Consequently, we can easily translate the frame
-conditions in~\eqref{eq:4frame} into inference rules:
-\begin{equation}
-  \label{eq:4rules}
-  \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-     \B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
-  \qquand
-  \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-    \B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
-\end{equation}
-This allows us to define cut-free deductive systems for a wide range
-of logics that could not be treated before.  Furthermore, the relation
-between syntax and semantics is as one would expect: A sequent is
-provable in our system if and only if it is valid in all models.
-
-Besides that, there is another pleasant observation to make about our
-system. Ordinary labelled sequent systems for intuitionistic modal
-logic are single-conclusion~\cite{simpson:phd}. The same is true for
-the corresponding nested sequent
-systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
-Maehara style multiple-conclusion systems in nested
-sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
-labelled sequents. However, also in these systems there are rules
-($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
-premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
-intuitionistic logic. Our system eliminates this
-discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.
-
-\medskip
-
-This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
-Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
-The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
-
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
-
-\section*{Introduction(old version, to be deleted)}
-\todo{We should work on the introduction}
-
-One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.
-
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
-%
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as
-used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
-Negri~\cite{Negri}. 
-%
-These formalisms make explicit use not only of
-labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
-%
-In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
-logics) and the \emph{preorder relation} (for intuitionistic
-logic), using the full power of the bi-relational semantics for
-intuitionistic modal logics,
-and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.
-
-\todo{Simpson does not have internal cut-elimination}
-
-\sonia{
-  \begin{itemize}
-  \item internal vs externl calculi
-  \item extesion to axioms are truly intuitionistic (not just the
-    classical versions as in Simpson style)
-  \item connection with semantics compared to graph homomorphism
-    restiction in Simpson and ``indexed nested systems''
-  \end{itemize}
-}
-
-\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
-  \begin{itemize}
-  \item what we do:
-    \begin{itemize}
-    \item first systems (nested and labelled) for intuitionistic modal
-      logic where ``single conclusion'', i.e., only one formula on the
-      right.
-    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
-    \item Still rules that forced single formula on the right (white implication and white box)
-    \item by allowing both relations of the model in the proof system
-      we go to genuinely multiple conclusion: never ever a formula on
-      the right has to be deleted during proof search.
-    \end{itemize}
-  \item why we do it: 
-    \begin{itemize}
-    \item getting things right: labelled systems for classical modal
-      logics, or plain propositional intuiionistic logic have one
-      binary relation, which is exactly the relation of the standard
-      Kripke semantics. The standard Kripke semantics for
-      intuitionistic modal logic is birelational, with a strong
-      connectiion between the two binary relations. A clean labelled
-      system for these logics should incorporate both relations.
-    \item We get new logics.  In the standard nested sequent
-      or labelled sequent system for intuitionistic modal logic we
-      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
-      but here we can have them separtely.
-    \end{itemize}
-  \item how we do it:
-    \begin{itemize}
-    \item We start from the Maehara nested sequent system (which can
-      be translated straightforwardly into a labelled system with one
-      relation $R$.
-    \item the rules for $\AND$ and $\OR$ are trivial and as expected
-      they can be presented such that they are invertible on the left
-      and the right, they do not concern the relations $R$ and $\le$. 
-    \item So should be the rules for $\IMP$-left and $\BOX$-left and
-      identity, but there is a subtlety; see below...
-    \item the rules for $\DIA$ are also straightforward, as they
-      concern only $R$ but not $\le$.
-    \item The rules $\BOX$-right and $\IMP$-right are the ones that
-      force single conclusion in the Maehara system. This means that
-      here they create a future, using the relation $\le$.
-    \item In order to make everything work together, this forces us to
-      have reflexivity and transitivity of $\le$, explicely as rules
-      in the system, and have rules for the F1 and F2 conditions
-      making the relations $R$ and $\le$ go together.
-    \item As a consequence we also need a rule realizing monotonicity
-      for the formulas on the right.
-    \item However, we designed the system such that monotonicity is
-      admisible by encorporating it into the rules for identity,
-      $\IMP$-left and $\BOX$-left.
-    \end{itemize}
-  \end{itemize}
-}
-%
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-\section{Intuitionistic modal logics}\label{sec:intmod}
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
-%
-$$
-\fm A \coloncolonequals
-\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
-$$
-%
-
-Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
-Five axioms have been considered as primitives in the literature.
-An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
-%
-
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
-\begin{itemize}
-	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
-	\begin{equation*}
-	\label{eq:ik}%\hskip-2em
-	\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
-	\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
-	&
-	\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
-	&
-	\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
-	\\
-	\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
-	&
-	\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
-	\end{array}
-	\end{equation*}
-\end{itemize}
-
-The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways.
-The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}.
-However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
-Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
-However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
-
-The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic.
-It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.
-
-The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
-%
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-
-\begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
-	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
-	\begin{enumerate}
-		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
-			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
-		}
-		\end{equation*}
-
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
-
-		\begin{equation*}
-		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
-			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
-		}
-		\end{equation*}
-	\end{enumerate}
-	%	
-\end{definition}
-
-\begin{definition}
-	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
-	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
-\end{definition}
-
-We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:
-
-\begin{equation}\label{eq:kripke}
-	\begin{array}{rcl}
-	%\parbox{30em}{%
-
-		\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\
-
-		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
-
-		\M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.
-
-	\end{array}
-\end{equation}
-Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
-%
-We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).
-
-From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-\begin{proposition}(Monotonicity) 
-	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
-\end{proposition}
-
-\begin{definition}
-	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
-	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
-\end{definition}
-
-%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%
-%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-
-Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.
-
-\begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
-	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
-
-%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
-
-\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
-\begin{theorem}[\cite{plotkin:stirling:86}]
-	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
-
-	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
-
-\end{theorem}
-
-% we would like to consider special restrictions on these bi-relational frames.
-For example, we would be interested in having a correspondence between the logic $\IK$ extended with some variants of axioms and bi-relational frames satisfyins the corresponding d
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%
-%\section{Intuitionistic modal logics}\label{sec:intmod}
-%
-%	The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
-%	%
-%	Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
-%	%
-%	$$
-%	A \coloncolonequals
-%	a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
-%	$$
-%	%
-%        \lutz{why do we have $\TOP$?}
-%	We might sometimes write $\NOT A$ to mean $A \IMP \BOT$. \lutz{do we?}
-%
-%Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
-%%%
-%Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. 
-%%
-%
-%The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-%%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
-%%
-%It is obtained from intuitionistic propositional logic by adding:
-%\begin{itemize}
-%\item the \emph{necessitation rule}: if $A$ is a theorem then $\BOX A$ is also a theorem; and
-%\item the following five variants of the \emph{distributivity axiom}:
-%\begin{equation*}
-%\label{eq:ik}%\hskip-2em
-%\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
-%\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
-%&
-%\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
-%&
-%\kax[5]\colon&\DIA\BOT\IMP\BOT
-%\\
-%\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
-%&
-%\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
-%\end{array}
-%\end{equation*}
-%\end{itemize}
-%
-%The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
-%%
-%It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
-%
-%\begin{definition}
-%	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
-%%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
-%	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.} a reflexive and transitive relation) satisfying:
-%	\begin{enumerate}
-%		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]_R  & v' \\
-%				u \ar@{.>}[u]^{\le} \ar@{->}[r]_R  & v \ar@{->}[u]_{\le}
-%			}
-%			\end{equation*}
-%		
-%		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
-%		
-%			\begin{equation*}
-%			\xymatrix{
-%				u' \ar@{.>}[r]^R & v' \\
-%				u \ar@{->}[u]^{\le} \ar@{->}[r]^R & v \ar@{.>}[u]_{\le}
-%			}
-%			\end{equation*}
-%	\end{enumerate}
-%%	
-%\end{definition}
-%
-%\begin{definition}
-%	\label{model}
-%	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-%	if $w \le w'$ then $V(w)\subseteq V(w')$.
-%\end{definition}
-%
-%We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
-%%
-%Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-%\begin{equation}
-%  \label{eq:kripke}
-%  \parbox{30em}{%
-%  $w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
-%
-%$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
-%
-%$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
-%
-%$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill %$(\ast)$
-%
-%$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
-%
-%%We write $w \not\Vdash A$  if it is not the case that $w\Vdash A$.\\
-%}
-%\end{equation}
-%\todo{fix typography}
-%
-%We write $w \not\Vdash A$ if it is not the case that $w \Vdash A$, but contrarily to the classical case, we do not have $w \Vdash \neg A$ iff $w \Vdash A$ (since $\neg A$ is defined as $A \IMP \bot$).
-%
-%From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
-%\begin{proposition}(Monotonicity) 
-%For any formula $A$ and for $w, w' \in W$, if $w \le w'$ and $w \Vdash A$, then $w' \Vdash A$.
-%\end{proposition}
-%
-%
-%
-%\begin{definition}
-%	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
-%%
-%	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
-%\end{definition}
-%
-%
-%
-%%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%%
-%%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-%
-%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
-%
-%\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-%	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions}
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Completeness}\label{sec:completeness}
-
-In this section we show our system at work, as most of the section
-consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
-
-\begin{theorem}\label{thm:completeness}
-	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
-\end{theorem}
-
-\begin{remark}
-  We have seem already in the proof of Proposition~\ref{prop:id} the
-  need of the rule $\rn{F_2}$. In the following proof of
-  Theorem~\ref{thm:completeness} we also see the need of the rules
-  $\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
-  We begin by showning how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
-  \begin{itemize}
-  \item $\kax[1]$:
-    $$
-    \vlderivation{
-				\vlin{\rlabrn{\IMP}}
-				{\lb y \mbox{ fresh}}
-				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
-				{\vlin {\rlabrn{\IMP}}
-					{\lb z \mbox{ fresh}}
-					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
-					{\vlin {\rlabrn{\BOX}}
-						{\lb w, \lb u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
-						{\vlin {\llabrn{\BOX}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
-							{\vlin {\color{red}\rn{trans}}
-								{}
-								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-										{\vliin{\llabrn{\IMP}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
-												{\vlhy {}}}
-											{\vlin {\rn{id}}
-												{}
-												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
-												{\vlhy {}}}}}}}}}}
-    }
-    $$
-    where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
-  \item $\kax[2]$:
-    $$
-    \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
-		{\vlin {\rlabrn{\IMP}}
-			{\lb z \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
-			{\vlin {\llabrn{\DIA}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
-				{\vlin{\rlabrn{\DIA}}
-					{}
-					{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
-					{\vlin {\llabrn{\BOX}}
-						{}
-						{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-						{\vlin {\color{red}\rn{refl}}
-							{}
-							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-							{\vliin{\llabrn{\IMP}}
-								{}
-								{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
-									{\vlhy {}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
-									{\vlhy {}}}								}}}}}}
-    }
-    $$
-    where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
-  \item $\kax[3]$:
-    $$
-    \vlderivation {
-			\vlin{\rlabrn{\IMP}}
-			{}
-			{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
-			{\vlin {\llabrn{\DIA}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
-				{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
-									{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
-						{}
-						{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
-						{\vlin {\rlabrn{\DIA}}
-							{}
-							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-								{\vlin {\rn{id}}
-									{}
-									{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
-									{\vlhy {}}}}}}}}
-		}
-    $$
-  \item $\kax[4]$:
-    $$
-\vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{\lb y \mbox{ fresh}}
-		{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
-		{\vlin {\rlabrn{\BOX}}
-			{\lb z, \lb w \mbox{ fresh}}
-			{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
-			{\vlin {\rlabrn{\IMP}}
-				{\lb u \mbox{ fresh}}
-				{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
-				{\vlin {\color{red}{\rn{F_1}}}
-					{}
-					{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-					{\vlin {\color{red}\rn{trans}}
-						{}
-						{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-						{\vliin {\llabrn{\IMP}}
-							{}
-							{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
-							{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
-											{\vlhy {}}}}}
-							{\vlin {\color{red}\rn{refl}}
-								{}
-								{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-								{\vlin {\llabrn{\BOX}}
-									{}
-									{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
-									{\vlin {\color{red}\rn{refl}}
-										{}
-										{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-										{\vlin {\rn{id}}
-											{}
-											{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
-											{\vlhy {}}}}}}}}}}}
-}
-$$
-where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
-\item $\kax[5]$:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
-		{\vlin {\llabrn{\DIA}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
-			{\vlin {\llabrn{\BOT}}
-				{}
-				{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
-				{\vlhy {}}}}
-  }
-  $$
-  \end{itemize}
-  Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
-  $$
-  \vlderivation {
-		\vlin{\rlabrn{\IMP}}
-		{}
-		{\SEQ \labels{x}{A \AND B \IMP B}}
-		{\vlin {\llabrn{\AND}}
-			{}
-			{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
-			{\vlin {\color{red}\rn{refl}}
-				{}
-				{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-				{\vlin {\rn{id}}
-					{}
-					{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
-					{\vlhy {}}}}}
-  }
-  $$
-
-  Finally, we have to show how the rules of modus ponens and
-  necessitation can be simulated in our system. For modus ponens, this
-  is standard using the cut rule and for necessitation, we can
-  transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
-  follows:
-
-\begin{lemma}
-	If there exists a proof of $\vlderivation {\vlpd{\Done}{}{\SEQ \labels{z}{A}}}$ then there exists a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$
-\end{lemma}
-
-\begin{proof}
-
-	We assume that there exists a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ and we want to obtain a proof of $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-	Using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ from our hypothesis, we can build the following proof:
-	$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$ \hspace{3mm} or what it is the same $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$.
-
-	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$. Therefore, we have the proof $\vlderivation { \vlpd{\Dtwo}{}{\SEQ \labels{x}{\BOX A}}}$.
-
-%	If we have a proof of $\vlderivation {\vlpd {\Done}{}{\SEQ \labels{z}{A}}}$ then we can obtain a proof of $\labels{x}{\BOX A}$ using the rule $\rlabrn{\BOX}$ introduced in the system $\labIKp$ and the proof of $\labels{z}{A}$ that we assumed  $\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}}$
-%	
-%	Let $\Dtwo$ be equal to: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}}$.
-%	Then using the \emph{weakening} rule, we have the following proof:
-%	
-%	\bigskip
-%	\begin{center}
-%		$\vlderivation{\vlin{\rlabrn{\BOX}}{}{\SEQ \labels{x}{\BOX A}}{\vlin{\rn{w}}{}{\futs xy, \accs yz \SEQ \labels{z}{A}}{\vlhy{ \SEQ \labels{z}{A}}}}}$
-%	\end{center}
-%
-
-\end{proof}
-
-  This completes the proof of Proof of Theorem~\ref{thm:completeness}.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Soundness}\label{sec:soundness}
-
-In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
-
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
-\end{definition}
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$. We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
-\end{definition}
-
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$:
-
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
-	\end{center}
-
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
-Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $\lb y, \lb z \in W$ such that $\futs xy$ and $\accs yz$, $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
-From this result, we can say that $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
-Thus, we have already proved that if there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, then $\M_{0} \not \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$.
-According to the definition, we proved that the rule $\llabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\BOX$:
-
-	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
-	\end{center}
-
-	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
-Let us assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.
-In particular, $\M_{0} \not \Vdash \labels{x}{\BOX A}$, which means that there exist worlds $\lb y, \lb z$, such that $\futs xy$ and $\accs yz$ where $\M_{0} \not \Vdash \labels{z}{A}$.
-Finally, we have that $\M_{0} \Vdash \B, \futs xy, \accs yz, \Left$ and $\M_{0} \not \Vdash \labels{x}{\BOX A}, \labels{z}{A}$,  which is the same as $\M_{0} \not \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$.
-Then, by way of contradiction, we proved that the rule $\rlabrn\BOX$ is sound.
-
-	\item Rule $\rlabrn\IMP$:
-
-	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
-	\end{center}
-
-	We prove this statement by way of contradiction.
-Assume there exists a model $\M_{0}$ such that $\M_{0}$ does not satisfy the conclusion, i.e.
-$\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.
-In particular, $\M_{0} \not \Vdash \labels{x}{A \IMP B}$.
-Therefore, there exists $\lb y$ such that $\futs xy$ and $\M_{0}, f(\lb y) \Vdash A$ (i.e.
-$\M_{0} \Vdash \labels{y}{A}$) but $\M_{0}, f(\lb y) \Vdash B$, i.e.
-$\M_{0} \not \Vdash \labels{y}{B}$.
-Then, we have $\M_{0} \not \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \labels{y}{B}$.
-This means that the model $\M_{0}$ does not satisfy the premise and that is what we wanted to prove.
-Finally, we showed that the rule $\rlabrn\IMP$ is sound.
-
-	\item Rule $\llabrn\DIA$:
-
-	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
-
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
-	\end{center}
-
-	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
-	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
-From $\M_{0} \Vdash \labels{x}{\DIA A}$, according to the definition of the $\DIA$ operator, we have that there exists a world $\lb y$ in $\M_{0}$ such that $\accs xy$ and $\M_{0} \Vdash \labels{y}{A}$.
-Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ and we prove that the rule $\llabrn\DIA$ is sound.
-
-	\item Rule $\rlabrn\DIA$:
-
-	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
-
-	\begin{center}
-		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
-	\end{center}
-
-	We prove this statement by way of contradiction.
-Let us assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$, we want to show that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
-for all world $\lb y \in \M_{0}$ where $\accs xy$ we have $\M_{0} \not \Vdash \labels{y}{A}$.
-Therefore, we have that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-Finally, assuming that $\M_{0}$ does not satisfy the conclusion, we proved that $\M_{0}$ does not satisfy the premise.
-Then we conclude that the rule $\rlabrn\DIA$ of the system $\labIKp$ is sound.
-\end{itemize}
-
-The other cases are similar and we leave them to the reader.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Cut Admissibility}\label{sec:cut-elim}
-In this section we are going to prove the admissibility of cut for $\labIKp$.
-
-\begin{theorem}
-  \label{thm:cut-adm}
-  The rule $\labrn{cut}$ is admissible for $\labIKp$.
-\end{theorem}
-
-This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.
-
-The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is the height of D when seen as a tree, i.e., the length of
-the longest path in the tree from its root to one of its leaves.
-
-We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$.
-A rule is \emph{height-preserving invertible} if for every
-derivation of the conclusion of the rule there are derivations for each of its premisses with at most the same height.
-
-The following two lemmas are standard.
-
-\begin{lemma}
-  \label{lem:weak-adm}
-  The weakening rule
-  ~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  \todo{\begin{lemma}
-  	If there exists a proof  $\vlderivation {\vlpd{\D}{}{\B, \Left \Rightarrow \Right}}$ then there exists a proof $\vlderivation {\vlpd {\Dw}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}}$
-
-  \end{lemma}
-
-  \vspace{3mm}
-
-  \begin{proof}
-  	By induction on the height of $\D$.
-
-  	For a proof of height 1:
-
-  	if $\D$ = $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, x \colon a \Rightarrow \Right, y \colon a}{\vlhy {}}}$ then we take $\Dw$ to be $\vlderivation {\vlin{\rn{id}}{}{\B, \Left, x \le y, xRy, u \le v, x \colon a, z \colon A \Rightarrow \Right, w \colon B, y \colon a}{\vlhy {}}}$.
-  	\vspace{2mm}
-
-  	For a proof $\D$ of height greater than 1:
-
-  	\begin{center}
-
-  		$\vlderivation{\vlin {$r$}{}{\B, \Left \Rightarrow \Right}{\vlpd {\Done}{}{\B', \Left' \Rightarrow \Right'}}}$
-
-  	\end{center}
-
-  	Then by induction hypothesis there exists a proof
-
-  	\begin{center}
-
-  		$\vlderivation {\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}$
-
-  	\end{center}
-
-  	Therefore, we have the proof
-
-  	\begin{center}
-
-  		$\Dw = \vlderivation {\vlin{}{}{\B, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}{\vlpd {\Dwone}{}{\B', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}}$
-
-  	\end{center}
-
-  \end{proof}}
-\end{proof}
-
-\begin{lemma}
-  \label{lem:inv}
-  The rules ..... are height-preserving invertible in
-  $\labIKp$. Furthermore, the rule $\llabrn{\IMP}$ is
-  height-preserving invertible for the right premise.
-\end{lemma}
-
-\begin{proof}
-  \todo{}
-\end{proof}
-
-The next lemma looks like a special case of
-Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using cut as we
-need it to eliminate the cut.
-
-\begin{lemma}
-  The atomic version of $\llabrn{mon}$
-  $$
-  \vlinf{\labrn{mon_a}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{a}, \labels{x'}{a}}\Right}
-  $$
-  is height-preserving admissible for $\labIKp$.
-\end{lemma}
-
-\begin{proof}
-  	\begin{smallequation*}
-  		\vlderivation{
-  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x''}{a}}{
-  					\vlhy{}
-  				}
-  			}
-  		}
-  		\reducesto
-  		\vlderivation{
-  		\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \futs{x'}{x''}, \futs{x}{x''}, \Left, \labels{x}{a} \SEQ \Right, \labels{x''}{a}}{
-  				\vlhy{}
-  			}}
-  	}
-  	\end{smallequation*}
-  	\todo{missing case}
-%  	\begin{smallequation*}
-%  		\vlderivation{
-%  			\vlin{\labrn{mon_a}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{
-%  				\vlin{\labrn{id}}{}{\B, \futs{x}{x'}, \labels{x}{a}, \labels{x'}{a} \SEQ \Right, \labels{x'}{a}}{
-%  					\vlhy{}
-%  				}
-%  			}
-%  		}
-%  		\reducesto
-%  		\vlinf{\labrn{id}}{}{\B, \futs{x}{x'}, \Left, \labels{x}{a} \SEQ \Right, \labels{x'}{a}}{}
-%  		\qedhere
-%  	\end{smallequation*}
-\end{proof}
-
-The next lemma is the core of our cut elimination proof.
-
-\begin{lemma}
-  \label{lem:reduction}
-  Given a derivation of shape
-  $$
-  \vlderivation{
-    \vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
-      \vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
-      \vlhy{}}{
-      \vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
-  $$
-  where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
-  derivation of ${\lseq\B\Left\Right}$
-\end{lemma}
-
-%$\vlderivation{\vlhtr{\DD}{\lseq\B\Left\Right}}$
-
-Following the proof of the Theorem \ref{thm:cutfree-compl}, in this section, we prove the implication \ref{ii}$\implies$\ref{iii}, i.e, we want to prove that our system $\labIKp$ is complete without the \rn{cut} rule.
-
-For proving this theorem, we need a series of auxiliary lemmas (see Lemma \ref{lem:inv}).
-
-\begin{proof}
-
-	By induction on number of cuts + (rank,height) of the left-most top-most cut.
-
-	\textbf{Commutative cases:}\label{commutative-cases}
-
-	\begin{smallequation*}
-		\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-			\vliin{\llabrn\IMP}{}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
-				\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-			}{
-			\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_3}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B_1, x \le y, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3[v/y]^{\invr{\llabrn\IMP}}}{\B_2, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-We need to make sure that $y$ does not appear in $\DD_3$, before applying Lemma~\ref{lem:inv}.
-%
-If it does we rewrite it with a fresh variable $v$ first.
-
-%\begin{smallequation*}
-%	\reducesto
-%	\vlderibase{\llabrn{cont}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-%		\vliin{\llabrn\IMP}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%%				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_4}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-%			}{
-%%			\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%%				\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}{
-%%				\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%%				}
-%				\vlhtr{\DD_5}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%			}
-%		}
-%\end{smallequation*}
-%
-%\begin{smallalign*}&
-%	\text{with } \DD_4 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
-%			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-%		}
-%	}
-%	\\&
-%	\text{and } \DD_5 = \quad
-%	\vlderivation{
-%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}{
-%			\vlhtr{\DD_2^{\rn w}}{\B_1, x \le y, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}{
-%			\vlhtr{\DD_3^{\rn w}}{\B_2, \Left, \labels{x}{A \IMP B}, \labels{y}{B} \SEQ \Right}
-%		}
-%	}
-%\end{smallalign*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vlin{\rlabrn\IMP}{\text{\footnotesize $x'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $x''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le x'' \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
-			\vlhtr{\DD_1[x''/x']}{\B_1, x \le x'', \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B_2, x \le x'', \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlin{\llabrn\BOX}{}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\llabrn\BOX}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vlin{\rlabrn\BOX}{\text{\footnotesize $x',y'$ fresh}}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y' \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\reducesto
-	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $u,v$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
-		}{
-		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B_1, x \le u, u \rel v, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
-	}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B_1, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y', \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
-}
-\reducesto
-\vlderibase{\llabrn\DIA}{\text{\footnotesize $y''$ fresh (also in $\DD_2$)}}{\B_1, \B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right}{
-		\vlhtr{\DD_1[y''/y']}{\B_1, x \rel y'', \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B_2, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
-}
-\reducesto
-%	\end{smallequation*}
-%	
-%	\begin{smallequation*}
-\vlderibase{\rlabrn\DIA}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
-		\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
-	}{
-	\vlhtr{\DD_2^{\rn w}}{\B_2, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-}
-}
-\end{smallequation*}
-
-\textbf{Key cases:}\label{key-cases}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-		\vlin{\labrn{id}}{}{\B_1, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-			\vlhy{}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
-}
-\reducesto
-\vlderibase{\llabrn{mon}}{}{\B_1, \B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right}{
-	\vlhtr{\DD_2^{\rn w}}{\B_1, \B_2, x \le y, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-		\vlhtr{\DD_1}{\B_1, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}		
-	}{
-	\vlin{\labrn{id}}{}{\B_2, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
-		\vlhy{}	
-	}
-}
-\reducesto
-\vlderibase{\rlabrn{mon}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{a}}{
-	\vlhtr{\DD_1^{\rn w}}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
-		}
-	}{
-	\vliin{\llabrn\IMP}{}{\B_2, \B_3, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}{
-	\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-2em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, \B_3, x \le y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlin{\rlabrn\IMP}{}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
-				\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
-			}
-			%			\vlhtr{\DD_{1\rn w}'}{\B_1, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}
-		}{
-		\vlhtr{\DD_{2}}{\B_2, x \le y, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
-	}
-}{
-\vliin{\labrn{cut}}{}{\B_1, \B_3, x \le y, \Left, \labels{y}{A} \SEQ \Right}{
-	\vlhtr{\DD_1[y/x']}{\B_1, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
-}{
-\vlhtr{\DD_3}{\B_3, x \le y, \Left, \labels{y}{B} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B_1, x \le x', x' \rel y', \Left \SEQ \Right, \labels{y'}{A}}	
-		}
-	}{
-	\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-	}
-}
-\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right}{
-		%		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}{
-		\vlhtr{\DD_1[u/x',v/y']}{\B_1, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}	
-		%			}{
-		%			\vlin{\llabrn\BOX}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{v}{A}}{
-		%				\vlin{\labrn{id}}{}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{v}{A}}{
-		%					\vlhy{}
-		%					}
-		%				}
-		%			}
-	}{
-	\vliin{\labrn{cut}}{}{\B_1, \B_2, x \le u, u \rel v, \Left, \labels{v}{A} \SEQ \Right}{
-		\vlin{\rlabrn\BOX}{}{\B_1, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1^{\rn w}}{\B_1, x \le x', x' \rel y', \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
-		}
-	}{
-	\vlhtr{\DD_2}{\B_2, x \le u, u \rel v, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
-}
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vlin{\rlabrn\DIA}{}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
-		}
-	}{
-	\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-		\vlhtr{\DD_2}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right}
-	}	
-}
-\end{smallequation*}
-
-\begin{smallequation*}
-	\vlderiibase{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right}{
-		\vliin{\labrn{cut}}{}{\B_1, \B_2, x \rel y, \Left \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_1}{\B_1, x \rel y, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
-		}{
-		\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ is fresh}}{\B_2, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
-			\vlhtr{\DD_2^{\rn w}}{\B_2, x \rel y',\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
-		}
-	}
-}{
-\vlhtr{\DD_2[y/y']}{\B_2, x \rel y,\Left, \labels{y}{A} \SEQ \Right}
-}
-\end{smallequation*}
-\end{proof}
-
-\begin{theorem}
-	\label{thm:mon-adm}
-	The rule $\rn{mon}$ is admissible for system $\labIKp$.
-\end{theorem}
-
-\begin{proof}[Proof of Theorem~\ref{thm:mon-adm}]
-
-	\todo{say that we can obtain the proof of monotonicity using the proof of cut.}
-
-\end{proof}
-
-\begin{lemma}\label{lem:inv}\hbox{}\quad
-	\begin{enumerate}
-		%\item
-		%If there exists a proof $\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}}$ then there exists a proof $\vlderivation{\vlhtr{\DD^{\invr{\llabrn\AND}}}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}$ of the same (or smaller) height, for any label $x$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\IMP}}}{\B, \Left, \labels{y}{B} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\IMP}}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\rlabrn\BOX}}}{\B, x \le u, u \rel v, \Left \SEQ \Right, \labels{v}{A}}}$
-		of the same (or smaller) height, for any label $u$ and $v$ that do not appear in $\DD$.
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\invr{\llabrn\DIA}}}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$
-		of the same (or smaller) height, for any label $y$ that does not appear in $\DD$.
-
-	\end{enumerate}
-\end{lemma}
-
-\todo{add missing cases}
-
-\begin{proof}
-	In each case, we reason by induction on the height of $\DD$.
-
-	\begin{itemize}
-		\item $\llabrn\IMP$:
-		For a proof of height $1$, it is straightforward.
-		%
-		For example, if $\DD = \vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a}, \labels{x}{A \IMP B} \SEQ \Right, \labels{v}{a}}{}$, 
-		%
-		then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlinf{\labrn{id}}{}{\B, u \le v, \Left, \labels{u}{a},\labels{y}{B} \SEQ \Right, \labels{v}{a}}{}$.
-
-		For a proof $\DD$ of height greater than $1$ we have two cases, depending on whether the last rule of $\DD$ acts on $\labels{x}{A \IMP B}$ or only on some part of the context.
-
-		First let us fix a given index $y$ that does not appear in $\DD$.
-
-		If we start with a proof
-		\begin{smallequation*}
-			\DD = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD'}{\B', \Left', \labels{x}{A \IMP B} \SEQ \Right'}
-				}	
-			}
-		\end{smallequation*}
-
-		Then by induction hypothesis there exists a proof 
-		\begin{smallequation*}
-			\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD'$ (as $y$ also does not appear in $\DD'$).
-
-		Therefore, we have the proof
-		\begin{smallequation*}
-			\DD^{\invr{\llabrn\IMP}} = 
-			\vlderivation{
-				\vlin{\rn{r}}{}{\B, \Left, \labels{y}{B} \SEQ \Right}{
-					\vlhtr{{\DD'}^{\invr{\llabrn\IMP}}}{\B', \Left', \labels{y}{B} \SEQ \Right'}
-				}
-			}
-		\end{smallequation*}
-		of the same (or smaller) height as $\DD$.
-
-		If we start with a proof 
-		\begin{smallequation*}
-			\vlderivation{
-				\vliin{\llabrn\IMP}{\text{\footnotesize $x \le z$ appears in $\B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
-					\vlhtr{\DD_1}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{A}}
-				}{
-				\vlhtr{\DD_2}{\B, \Left, \labels{z}{B} \SEQ \Right}
-			}
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\IMP}}$ to be $\vlderivation{\vlhtr{\DD_2[y/z]}{\B, \Left, \labels{y}{B} \SEQ \Right}}$ (as $y$ also does not appear in $\DD_2$) and its height is smaller than the one of $\DD$.
-
-	%
-	\item $\llabrn\DIA$:
-
-	If we start with a proof
-	\begin{smallequation*}
-		\DD = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B', \Left', \labels{x}{\DIA A} \SEQ \Right'}
-			}	
-		}
-	\end{smallequation*}
-
-	Then by induction hypothesis there exists a proof 
-	\begin{smallequation*}
-		\vlderivation{\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD'$.
-
-	Therefore, we have the proof
-	\begin{smallequation*}
-		\DD^{\invr{\llabrn\DIA}} = 
-		\vlderivation{
-			\vlin{\rn{r}}{}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}{
-				\vlhtr{{\DD'}^{\invr{\llabrn\DIA}}}{\B', x \rel y, \Left', \labels{y}{A} \SEQ \Right'}
-			}
-		}
-	\end{smallequation*}
-	of the same (or smaller) height as $\DD$, for any label $y$ that does not appear in $\DD$.
-
-	If we start with a proof 
-	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn\DIA}{\text{\footnotesize $y'$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
-				\vlhtr{\DD'}{\B, x \rel y', \Left, \labels{y'}{A} \SEQ \Right}
-			}	
-		}
-	\end{smallequation*}
-	then we take $\DD^{\invr{\llabrn\DIA}}$ to be $\vlderivation{\vlhtr{\DD'[y/y']}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}}$ for any label $y$ that does not appear in $\DD$.
-
-	\item $\rlabrn\IMP$ and $\rlabrn\BOX$ : Similar.
-\end{itemize}
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Labelled sequent calculi with $\rel$ and $\le$}
-
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-Once possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
-Labelled deduction has been more generally proposed by Gabbay in the 80's as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics \cite{gabbay:96}.
-For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson:phd}, Vigano \cite{vigano:00}, and Negri\cite{negri:jpl2005}.
-These formalisms make explicit use not only of labels, but also of relational atoms (which, to our knowledge, are not commonly used in tableaux systems, except for the pioneering work of Nerode \cite{nerode:91}).
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson:phd}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{strassburger:fossacs13} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{simpson:phd} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
-
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
-%
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli:etal:synthese13}.
-%
-
-\begin{definition}
-A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-In the next section, we present the system (called $\labIKp$) that we obtained to capture intuitionistic modal logics (see Figure \ref{fig:labIKp}).
-
-\section{Building $\labIKp$}
-
-As we mentioned, a labelled sequent calculus for classical modal logic was introduced in \cite{negri:jpl2005}.
-In our work, we show an extension of Negri's system in order to capture intuitionistic modal logics.
-This new system is formed from formulas of the form $\labels{x}{A}$ where $A$ is an intuitionistic modal formula, relational atoms $xRy$ ($R$ is the modal accesibility relation) where $x$, $y$ range over a set of variables called \emph{labels} and preorder atoms of the form $x \le y$.
-In this section, we study each rule of the system $\labIKp$ (Figure \ref{fig:labIKp}) in details.
-
-\subsection{Frame conditions}
-%In order to capture intuitionistic modal logics, we need to answer the requirements of the de
-The semantics of intuitionistic modal logic introduces a bi-relational model with two binary relations: $R$ and $\le$, where $\le$ is a preorder relation, i.e, a reflexivity and transitivity relation.
-For that reason, the system $\labIKp$ contains the rules $\rn{refl}$ and $\rn{trans}$.
-Furthermore, our system has to incorporate the two semantic conditions into deductive rules as $\rn{F1}$ and $\rn{F2}$ .
-On the other hand, the valuation function $V$ that introduces the \emph{monotonicity property} is captured with the rule $\rn{id}$ in our system.
-All these are presented in the system $\labIKp$ as follows:
-
-\begin{center}
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{id}}{}{\B, x \le y, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				}
-				\\\\
-				\hspace{15mm}
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					\hspace{18mm}
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
-
-\end{center}
-
-\bigskip
-
-A small explanation about the rules $\rn{F1}$ and $\rn{F2}$ is below:
-
-\begin{itemize}
-	\item Rule $\rn{F1}$.
-
-	As we mentioned, the next rule is needed to cover one of the pre-order relation conditions:
-
-	\begin{center}
-		$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-	\end{center}
-
-	Given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\rn{F1}$ is read from the conclusion to the premises as following: we have labels $x$, $y$ and $z$ such that $xRy$ and $y \le z$, then there exists a world $u$ such that $x \le u$ and $uRz$.
-
-	\item Rule $\ftwo$:
-
-	The rule that is capturing the frame condition $\rn{F2}$ is represented in the system  $\labIKp$ as the following:
-
-	\begin{center}
-	$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$	
-	\end{center}
-
-	As the rule for $\rn{F1}$, given $\B$ a set of relational and pre-order atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, the rule $\ftwo$ expresses, semantically, from the conclusion to the premise that given the labels $x, y$ and $z$, if $xRy$ and $x \le z$, then there exists a variable $u$ such that $y \le u$ and $zRu$.
-
-\end{itemize}
-
-\subsection{Logical connectives for intuitionistic propositional logic}
-
-To continue building a complete and sound labelled system for intuitionistic modal logic, in this small section we present the rules that are needed to express the semantics of the usual logical connectives.
-That means, we present the rules for the conjunction and disjunction of the system $\labIKp$:
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-			\\\\
-			$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-			\\\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-To capture the propositional constants $\top$ and $\bot$, the system $\labIKp$ introduces the next two rules:
-
-\begin{center}
-		$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-		\hspace{8mm}
-		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-\end{center}
-
-You can find a small explanation about the rules $\llabrn\AND$ and  $\rlabrn\OR$ below:
-
-\begin{itemize}
-	\item Rule $\llabrn\AND$:
-
-	%The system $\labIKp$ presents the next rule for the conjunction left:
-
-	%\begin{center}
-	%	$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-	%\end{center}
-
-	Following the explanation of the rules presented before, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of labelled formulas.
-From the conclusion to the premise, this rule shows semantically that if the formula $A \vlan B$ is satisfied in the label $x$, then the formula $A$ is satisfied  in $x$ and the formula $B$ too.
-
-	\item Rule $\rlabrn\OR$:
-
-	Let the rule presented in $\labIKp$ for disjunction right be as follows:
-
-	\begin{center}
-		$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-	\end{center}
-
-	From the conclusion to the premise we have that if the formula $A \vlor B$ is satisfied in $x$, then the formula $A$ and the formula $B$ are true in $x$.
-
-\end{itemize}
-
-\subsection{Modal operators}
-
-We introduce the rules that represent the semantics of modal operators $\BOX$ and $\DIA$. The system $\labIKp$ presents the next four rules (two for $\BOX$ and two for $\DIA$): 
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\\\\
-			$\vlinf{\llabrn\BOX}{}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, yRz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, x \le y, y \rel z, \Left \SEQ \Right, \labels{z}{A}}$
-			\\\\
-			$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, x \rel y, \Left, \labels{y}{A} \SEQ \Right}$
-			&
-			$\vlinf{\rlabrn\DIA}{}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, x \rel y, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-			\\
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-A more detailed explanation for some rules is below:
-
-\begin{itemize}
-	\item Rule $\llabrn\BOX$.
-	Continue with the same reasoning, $\B$ is a set of relational and preorder atoms and $\Left$ and $\Right$ are multiset of laballed formulas.
-Semantically, the rule expresses, from the conclusion to the premise, that given $x, y$ and $z$ such that $x \le y$ and $yRz$ where the formula $\BOX A$ is true in $x$, then the formula $A$ is true in $z$.
-
-	\item Rule $\rlabrn\DIA$.
-	Semantically, the diamond establishes that in a model $\M$ and a world $v$ the formula $\DIA A$ is satisfied, if and only if, there exists a world $u$ such that $vRu$ and the formula $A$ is satisfied in $u$.
-In order to capture this definition, the rule shows that if $xRy$ and the formula $\DIA A$ is satisfied in $x$, then the formula $A$ is true in $y$.
-
-\end{itemize}
-
-\subsection{Intuitionistic implication}
-To finish our system $\labIKp$, we have to introduce the rules that capture the intuitionistic implication:
-
-\bigskip
-
-\begin{center}
-	\begin{minipage}{.95\textwidth}
-		\begin{tabular}{@{\!}c@{\quad}c}
-			\multicolumn{2}{c}{
-				\hspace{9mm}
-				$\vlinf{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, x \le y, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-			}
-			\\
-			\multicolumn{2}{c}{
-				\hspace{10mm}
-				$\vliinf{\llabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \IMP B \SEQ \Right}{\B, x \le y, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-			}
-		\end{tabular}
-	\end{minipage}
-\end{center}
-
-\bigskip
-
-The rule for implication right is explained below:
-
-\begin{itemize}
-	\item Rule $\rlabrn\IMP$.
-	Let $\B$ be a set of relational and preorder atoms, and given $\Left$ and $\Right$ multiset of labelled formulas, this rule shows, semantically, that if the formula $A \IMP B$ is satisfied in $x$, then there exists $y$ such that $x \le y$ and the formula $A$ is true in $y$, then the formula $B$ is also true in $y$.
-\end{itemize}
-
-\section{A complete and sound system for intuitionistic modal logics}
-%
-Using the rules that are presented in the previous section, we obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic following the formalism of labelled sequents.
-%
-Most rules are similar to the ones of Simpson~\cite{simpson:phd}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition \ref{model}.
-%
-Furthermore, our system, unlike Simpson's system, has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
-%We show that each rule from our system is sound.
-%
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-The proof is a careful adaptation of standard techniques.
-%
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
-As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
-%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
-\bigskip
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-		\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-			\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-				\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-					\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlhy {}
-										}
-									}
-								}
-							}{
-%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-										\vlhy {\qquad\vdots\qquad}
-%										}
-%									}
-%								}
-%							}
-						}
-					}
-				}
-			}
-		}
-	}
-}$
-}$$
-%\end{example}
-
-%\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $\rn{F_2}$. The other cases are standard.
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-$
-\vlderivation{
-	\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-		\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-					\vlhy{}
-				}
-			}
-		}
-	}
-}
-$
-}
-$$
-%\end{example}
-
-\begin{lemma}\label{lem:weak}\hbox{}\quad
-	\begin{enumerate}
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right, \labels{x}{\BOT}}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\bm\BOT}}{\B, \Left \SEQ \Right}}$
-
-	%	\item 
-	%	If there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD}{\B, \Left, \labels{x}{\TOP} \SEQ \Right}}$ 
-	%	then there exists a proof 
-	%	$\vlderivation{\vlhtr{\DD^{\bm\TOP}}{\B, \Left \SEQ \Right}}$
-
-		\item 
-		If there exists a proof 
-		$\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \Right}}$ 
-		then there exists a proof 
-		$\vlderivation{\vlhtr{\DD^{\rn w}}{\B, x \rel y, u \le v, \Left, \labels{z}{A} \SEQ \Right, \labels{w}{B}}}$
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	Standard.
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}\label{sec:ext}
-
-The main goal of this section is to generate stronger logics adding new axioms to our system.
-We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.
-
-In~\cite{simpson:phd}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin:stirling:86}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-	($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin:stirling:86}.
-%
-These systems enjoy cut-elimination via usual arguments. Proofs of the axiom mentioned for $\DIA$ and $\BOX$ are below:
-
-Proof of $\ax{4_{\BOX}} \colon \fm{\BOX A \IMP \BOX\BOX A}$
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
-		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
-			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, \bm{\accs{w'}{v}}, \bm{\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-				\vlin{\rn{trans}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \bm{\futs{w'}{t}}, \bm{\accs{t}{v'}}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-					\vlin{\boxbrn{4}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \bm{\accs{v'}{u}}, \futs{w'}{t}, \bm{\accs{t}{v'}}, \futs wt \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-						\vlin{\labrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \bm{\accs tu}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
-							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs wt, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
-								\vlhy{}
-							}
-						}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-Proof of $\ax{4_{\DIA}} \colon \DIA\DIA A \IMP \DIA A$:
-
-$\vlderivation{
-	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
-		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
-			\vlin{\diasym_\rn{4}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
-					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-}
-$
-
-\bigskip
-
-Now we want to obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\agklmn$ (also known as $\mathsf{Scott-Lemmon}$ $\mathsf{axiom}$): $\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}$ (Figure \ref*{fig:gklmn}).\todo{Wrong label.
-why??}
-
-Writing this axiom in both classical and intuitionistic logic in first-order language, we obtain:
-
-$\star$ \emph{Classical case} \hspace{2.2mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$
-
-$\star$ \emph{Intuitionistic case} $\rightsquigarrow$  $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \IMP \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\
-
-\begin{figure}[h]
-	\begin{center}
-		$
-		\xymatrix{
-			& u' \ar@{.>}[ddr]^{R^l} \\
-			& u \ar@{.>}[u]^{\le} \\
-			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
-			& v \ar@{.>}[ur]_{R^n}
-		}
-		$
-	\end{center}
-	\label{fig:gklmn}
-	\caption{$\agklmn$ axiom for intuitionistic case}
-\end{figure}
-
-Following the idea to have a sound and complete system adding the axiom $\agklmn$ to the system $\labIKp$, we introduce the next rule:
-
-\bigskip
-
-\begin{center}
-	$\vlderivation { \vlin {\gklmn}{y', u \mbox{ fresh}}{\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \Rightarrow \Right}{\vlhy {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\Rightarrow \Right}}}$
-\end{center}
-
-\bigskip
-
-We start proving that our new system is complete with the base case of $\mathsf{k = l = m = n = 1}$:
-
-\begin{theorem}
-	The system $\labIKp +\agklmn$ is complete for $\mathsf{k = l = m = n = 1}$.
-\end{theorem}
-
-\begin{proof}
-	\begin{center}
-		\scalebox{0.93}{
-			$\vlderivation {\vlin {\rlabrn{\IMP}}
-				{y \mbox{ fresh}}
-				{\SEQ \labels{x}{\DIA \BOX A \IMP \BOX \DIA A}}
-				{\vlin {\rlabrn{\BOX}}
-					{z, w \mbox{ fresh} }
-					{\lseq{\futs xy}{\labels{y}{\DIA \BOX A}}{\labels{y}{\BOX \DIA A}}}
-					{\vlin {\llabrn{\DIA}}
-						{u \mbox{ fresh}}
-						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA \BOX A}}{\labels{w}{\DIA A}}}
-						{\vlin {\rn{F_2}}
-							{t \mbox{ fresh}}
-							{\lseq{\futs xy, \futs yz, \accs zw, \accs yu}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-							{\vlin {\gklmn}
-								{t', j \mbox{ fresh}}
-								{\lseq{\futs xy, \futs yz, \futs ut, \accs zw, \accs yu, \accs zt}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-								{\vlin {\rlabrn{\DIA}}
-									{}
-									{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}}}
-									{\vlin {\rn{trans}}
-										{}
-										{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-										{\vlin {\llabrn{\BOX}}
-											{}
-											{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-											{\vlin {\rn{refl}}
-												{}
-												{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'}, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-												{\vlin {\rn{id}}
-													{}
-													{\lseq{\futs xy, \futs yz, \futs ut, \futs{t}{t'}, \futs{u}{t'},\futs jj, \accs zw, \accs yu, \accs zt, \accs{t'}{j}, \accs wj}{\labels{u}{\BOX A}, \labels{j}{A}}{\labels{w}{\DIA A}, \labels{j}{A}}}
-													{\vlhy {}}}}}}}}}}}}$}
-	\end{center}
-\end{proof}
-
-In order to have a completeness proof for the general case, we need to introduce the rules from the Lemma~\ref{lemma:admis}.
-
-\begin{lemma}\label{lemma:admis} The following rules are admissible in $\labIKp$:
-	\begin{enumerate}
-		\item{$\vlderivation {\vlin {\boxlk}{}{\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}\Rightarrow \Right}{\vlhy {\B, \Left, x(\le \circ $R$)^{k}y, \labels{x}{\BOX^{k} A}, \labels{z}{A} \Rightarrow \Right}}}$}
-		\item{$\vlderivation{\vlin {\boxk}{}{\B, \Left \Rightarrow \Right, \labels{x}{\BOX^{k} A}}{\vlhy {\B, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, \labels{y}{A}}}}$}
-		\item{$\vlderivation { \vlin {\diamk}{}{\B, \Left, \labels{x}{\DIA^{k} A} \Rightarrow \Right}{\vlhy {\B, xR^{k}y, \Left, \labels{y}{A} \Rightarrow \Right}}}$ }
-		\item{$\vlderivation { \vlin {\diamrk}{}{\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}}{\vlhy {\B, \Left, xR^{k}y \Rightarrow \Right, \labels{x}{\DIA^{k}A}, \labels{y}{A}}}}$}
-	\end{enumerate}
-	%\textbf{Probably F2g???}
-\end{lemma}
-
-Our conjecture is that it is possible to prove completeness of the system for the general case by induction in the $k$ parameter. This proof is ongoing study.
-
-\bibliographystyle{alpha}
-\bibliography{references}
-
-\end{document}
-
-%\begin{figure}[h]
-%\begin{center}
-%$\vlderivation{\vlinf{\id}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\botlab}{}{\B, \Left, x\colon \bot \SEQ z\colon A}{}}$
-%\hspace{5mm}$\vlderivation{\vlinf{\toplab}{}{\B, \Left \SEQ x \colon \top}{}}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\andleflab}{}{\B,\Left, x \colon \vls(A.B) \SEQ z \colon C}{\B, \Left, x\colon \vls(A.B,\labels{x}{A}, \labels{x}{B} \SEQ z \colon C)}$\hspace{5mm}$\vliinf{\andriglab}{}{\B,\Left \SEQ x \colon \vls(A.B)}{\B, \Left \SEQ \labels{x}{A}}{\B, \Left \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%$\vliinf{\orleflab}{}{\B, \Left, x \colon \vls[A.B] \SEQ  \colon C}{\B, \Left, x \colon \vls[A.B], \labels{x}{A} \SEQ z \colon C}{\B, \Left, x \colon \vls[A.B], x   \colon   B \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\orriglabo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x   \colon   A}$
-%\hspace{7mm}$\vlinf{\orriglabt}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\B, \Left \SEQ x \colon  B}$
-%
-%\vspace{2mm}
-%
-%$\vliinf{\illab}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\B, \Left, \labels{x}{A} \IMP B \SEQ \labels{x}{A}}{\B, \Left, \labels{x}{A} \IMP B, \labels{x}{B} \SEQ z \colon C}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\irlab}{}{\B, \Left \SEQ \labels{x}{A} \IMP B}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}$
-%
-%\vspace{2mm}
-%
-% $\vlderivation {\vlinf{\bllab}{}{\B, x \rel y, \Left x \colon \BOX A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z \colon B}}$
-%\hspace{5mm}  $\vlinf{\brlab}{$ $y$ fresh$}{\B, \Left \SEQ x \colon \BOX A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\vspace{2mm}
-%
-%$\vlinf{\dllab}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\B, x \rel y, \Left, x \colon \DIA A, y \colon A \SEQ z \colon B}$
-%\hspace{5mm}$\vlinf{\drlab}{}{\B, x \rel y, \Left,  \SEQ x \colon \DIA A}{\B, x \rel y, \Left \SEQ y \colon A}$
-%
-%\end{center}
-%\caption{System labIK}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	
-%	\begin{center}
-%		
-%		$\vlderivation { \vlin {\ids}{}{\B, \Left, \labels{x}{A} \SEQ x\colon a}{\vlhy {}}}$ \hspace{7mm} $\vlderivation { \vlin {\sbot}{}{\B, \Left, x \colon \bot \SEQ z\colon A}{\vlhy {}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vlin {\svlef}{}{\B, \Left, x \colon \vls(A.B) \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vliin {\svrig}{}{\B, \Left, \SEQ x \colon \vls(A.B)}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		
-%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \IMP B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
-%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
-%		
-%	\end{center}
-%	
-%	\caption{System $\lab\IK$}
-%	\label{fig:labIK}
-%\end{figure}
-%
-%\begin{theorem}[Simpson~\cite{Simpson}]
-%	\label{thm:simpson-sound-compl}
-%	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}%[h]
-%	\small
-%	\centering
-%
-%		$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
-%		\hspace{5mm}
-%		$\vlinf{\llabrn\bot}{}{\B, \Left, x\colon \bot \SEQ \Right}{}$
-%		\hspace{5mm}
-%		$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, x \colon \top}{}$
-%%		
-%%		\vspace{4mm}
-%		\\[1.5ex]
-%%		
-%		$\vlinf{\llabrn\AND}{}{\B,\Left, x \colon \vls(A.B) \SEQ \Right}{\conjlef}$
-%		\hspace{7mm}
-%		$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, x \colon \vls(A.B)}{\conjrig}{\conjrigh}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ \Right}{\B, \Left, x   \colon   A \SEQ \Right}{\B, \Left, x   \colon   B \SEQ \Right}$
-%		\hspace{7mm}
-%		$\vlinf{\sorig}{}{\B, \Left \SEQ \Right, x \colon \vls[A.B]}{\B, \Left \SEQ \Right, x   \colon   A, x   \colon   B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sir}{$ $y$ fresh$}{\B, \Left \SEQ \Right, \labels{x}{A} \IMP B}{\B, \Left, x \le y, y \colon A \SEQ \Right, y \colon B}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vliinf{\sil}{}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right}{\B, \Left, x \le y, \labels{x}{A} \IMP B \SEQ \Right, y \colon A}{\B, \Left, x \le y, y \colon B \SEQ \Right}$
-%		
-%		\vspace{4mm}
-%		
-%		$\vlderivation {\vlinf{\sbl}{}{\B, \Left, x \le y, y \rel z, x \colon \BOX A \SEQ \Right}{\B,\Left, x \le y, y \rel z, x \colon \BOX A, z \colon A \SEQ \Right}}$
-%		\hspace{5mm} $\vlinf{\sbr}{$ $y, z$ fresh$}{\B, \Left \SEQ \Right, x \colon \BOX A}{\B, \Left, x \le y, y \rel z \SEQ \Right, z \colon A}$
-%		
-%		
-%		\vspace{4mm}
-%		
-%		$\vlinf{\sdl}{$ $y$ fresh $}{\B, \Left, x \colon \DIA A \SEQ \Right}{\B, \Left, x \rel y, y \colon A \SEQ \Right}$
-%		\hspace{5mm}$\vlinf{\sdr}{}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A}{\B, \Left, x \rel y \SEQ \Right, x \colon \DIA A, y \colon A}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\refl}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-%		\hspace{7mm} $\vlinf{\trans}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-%		
-%		
-%		\vspace{2mm}
-%		
-%		$\vlinf{\rn{F_1}}{\text{\footnotesize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-%		%
-%		$\vlinf{\rn{F_2}}{\text{\footnotesize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-%	
-%	\caption{System $\labIKp$}
-%	\label{fig:labHIK}
-%\end{figure}

### 2019-10-03 caleidoscope/soundness.tex
correcting the soundness file

@@
 In order to prove the implication \ref{iii}$\implies$\ref{iv} from
-Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule of our system $\labIKp$ is sound.
-We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
+Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
+of our system $\labIKp$ is sound. To make precise what that actually
+means, we have to extend the relation $\Vdash$, defined in
+Section~\ref{sec:intmod} from formulas to sequents. This is the
+purpose of the following definitions.
 
-In order to obtain the proof, let us introduce the next definitions:
-
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
+\begin{definition}\label{def:force-seq}
+	Let $\M = \langle W, \rel_\M, \le_\M, V \rangle$ be a model, and let
+	$\SG$ be the sequent $\lseq\B\Left\Right$. A \emph{$\SG$-interpretation
+		in $\M$} is a mapping $\inter{\cdot}$ from the labels in $\SG$ to the set $W$ of worlds in $\M$, such that whenever $\accs xy$ in $\B$, then $\inter x\rel_\M\inter y$, and whenever $\futs xy$ in $\B$, then $\inter x\le_\M\inter y$.
+Now we can define
+	\begin{equation}
+	\M,\inter\cdot\Vdash\SG\qquad\mbox{iff}\qquad
+	\parbox{20em}{if for all $\labels{x}{A} \in \Gamma$, we have $\M, \inter x \Vdash \fm A$, then there exists $\labels{z}{B} \in \Delta$ such that $\M, \inter z \Vdash \fm B$.}
+	\end{equation}
 \end{definition}
 
-\begin{definition}
-	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
-	\begin{enumerate}
-		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
-		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
-		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
-	\end{enumerate}
-	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$. We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
+\begin{definition}\label{def:valid-seq}
+	A sequent $\SG$ is \emph{satisfied} in $\M = \langle W, \rel, \le, V
+	\rangle$ iff for all $\SG$-interpretations $\inter\cdot$ we have
+	$\M,\inter\cdot\Vdash\SG$.
+	%%
+	A sequent $\SG$ is \emph{valid} in a frame $\F = \langle W, \rel,
+	\le \rangle$, if for all valuations $V$, the sequent $\SG$ is
+	satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}
 
-Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
+We are now ready to state the main theorem of this section, of which
+the implication \ref{iii}$\implies$\ref{iv} in
+Theorem~\ref{thm:cutfree-compl} is an immediate consequence.
 
+\begin{theorem}\label{thm:soundness}
+	If a sequent $\SG$ is provable in $\labIKp$, then it is valid in every birelational frame.
+\end{theorem}
+
+\begin{proof}
+	We proceed by induction on the height of the derivation of $\SG$, and we show for all rules in $\labIKp$
+	$$
+	\vliiinf{\labrn{r}}{}{\SG}{\SGi1}{\cdots}{\SGi n}
+	$$ for $n\in\{0,1,2\}$, that whenever $\SGi1,\ldots,\SGi n$ are
+	valid in all birelational frame, then so is $\SG$. It follows a case analysis on $\rn r$:
 	\begin{itemize}
-	\item Rule $\llabrn\BOX$:
+		\item $\rlabrn\bot$: This is trivial because $\bot$ is never forced.
+		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon}.
+		\item $\llabrn\BOX$: By way of contradiction, assume $\B, \Left,
+		\futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
+		is valid in all birelational frames, but $\B,\Left, \futs xy,
+		\accs yz, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
+		we have a model $\M$ and an interpretation $\inter\cdot$, such
+		that $\M,\inter\cdot\not\Vdash\B,\Left, \futs xy, \accs yz,
+		\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
+		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ and
+		$\cnforce \M wB$ for all $\labels wB\in\Right$. However, by the
+		definition of forcing in~\eqref{eq:kripke} we also have $\cforce
+		\M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \Left, \futs
+			xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
+			\Right}$. Contradiction.
+		\item $\rlabrn\BOX$: By way of contradiction, assume that $\futs xy,
+		\accs yz, \Left \SEQ \Right, \labels{z}{A}$ is valid in all
+		birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{\BOX
+			A}$ is not, where $\lb y$ and $\lb z$ do not occur in $\B$ or
+		$\Left$ or $\Right$.This means that we have a model $\M$ and an
+		interpretation $\inter\cdot$, such that
+		$\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX
+				A}}$. This means that there are worlds $\lb{y'}$ and $\lb{z'}$
+		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
+		$\lb{y'}\rel_\M\lb{z'}$ and $\cforce\M{z'}{A}$. Now we let
+		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
+		y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
+		on all other labels. Then $\nforce\M{\inter\cdot'}{\futs xy,
+			\accs yz, \Left \SEQ \Right, \labels{z}{A}}$. Contradiction.
+		\item \lutz{if you want, you can add some more cases here, following the pattern above.}
+	\end{itemize}
+	The other cases are similar (and simpler), and we leave them to the
+	reader. In particular, note that the cases for the rules $\rn{refl}$,
+	$\rn{trans}$, $\rn{F_1}$ and $\rn{F_2}$ are trivial, as all
+	birelations frames have to obey the corresponding conditions.
+\end{proof}
 
-	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
+%% We want to prove that for all model $\M$ that satisfies the premise, then $\M$ satifies the conclusion.
 
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
-	\end{center}
+%% In order to obtain the proof, let us introduce the next definitions:
 
-	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
+%% \begin{definition}
+%% 	Let $\M = \langle W, \rel, \le, V \rangle$ be a model. We say that $\f$ is an \emph{assignment function} such that $\f : Labels \rightarrow W$.
+%% \end{definition}
+
+%% \begin{definition}
+%% 	Let $\M = \langle W, \rel, \le, V \rangle$ be a model and $\B, \Gamma \SEQ \Delta$ a sequent. We say that $\M \Vdash \B, \Gamma \SEQ \Delta$ if for all $\f$ such that:
+%% 	\begin{enumerate}
+%% 		\item For all $\labels{x}{A} \in \Gamma$, we have $\M, f(\lb x) \Vdash \fm A$. \marianela{should we say that this is equal to $\M \Vdash \labels{x}{A}$?}
+%% 		\item For all $\lb x, \lb y \in \B$, we have $f(\lb x) \rel f(\lb y)$.
+%% 		\item For all $\futs xy \in \B$, we have $f(\lb x) \le f(\lb y)$.
+%% 	\end{enumerate}
+%% 	then there exists $\labels{z}{B} \in \Delta$ such that $\M, f(\lb z) \Vdash \fm B$.
+We say that $\M \not \Vdash \B, \Gamma \SEQ \Delta$ if it is not the case that $\M \Vdash \B, \Gamma \SEQ \Delta$.
+%% \end{definition}
+
+%% Following the definitions, we display the proof of soundness for some rules since it is similar for each rule.
+
+%% \begin{itemize}
+%% 	\item Rule $\llabrn\BOX$:
+
+%% 	We want to prove that the rule for $\llabrn\BOX$ introduced in the Figure \ref{fig:labIKp} is sound. What we want to prove is:
+
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$.}
+%% 	\end{center}
+
+%% 	By way of contradiction, we assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \futs xy, \accs yz,\Left,\break \labels{x}{\BOX A} \SEQ \Right$, i.e $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \futs xy$, $ \M_{0} \Vdash \accs yz$, $\M_{0} \Vdash \labels{x}{\BOX A}$ and  $\M_{0} \not \Vdash \Right$.
 Therefore, in particular from $\M_{0} \Vdash \labels{x}{\BOX A}$ we have that for all $\lb y, \lb z \in W$ such that $\futs xy$ and $\accs yz$, $\M_{0}, f(\lb z) \Vdash \fm A$, i.e $\M_{0} \Vdash \labels{z}{\fm A}$.
@@
 
-	\item Rule $\rlabrn\BOX$:
+%% 	\item Rule $\rlabrn\BOX$:
 
-	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
+%% 	In order to prove that the rule $\rlabrn\BOX$ of the system $\labIKp$ is sound, we need to show that:
 
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
-	\end{center}
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.}
+%% 	\end{center}
 
-	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
+%% 	By way of contradiction, we want to prove that if there exists a model that does not satisfy the conclusion, then the same model does not satisfy the premise.
 Let us assume that there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left \SEQ \Right, \labels{x}{\BOX A}$.
@@
 
-	\item Rule $\rlabrn\IMP$:
+%% 	\item Rule $\rlabrn\IMP$:
 
-	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
-	\end{center}
+%% 	We display the proof of soundness for the rule $\rlabrn\IMP$ showing that:
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B, \futs xy, \Left, \labels{y}{A} \SEQ \Right \labels{y}{B}$, then $\M \Vdash \B, \Left \SEQ \Right, \labels{x}{A \IMP B}$.}
+%% 	\end{center}
 
-	We prove this statement by way of contradiction.
+%% 	We prove this statement by way of contradiction.
 Assume there exists a model $\M_{0}$ such that $\M_{0}$ does not satisfy the conclusion, i.e.
@@
 
-	\item Rule $\llabrn\DIA$:
+%% 	\item Rule $\llabrn\DIA$:
 
-	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
+%% 	Following the same reasoning that we have been tabling, we define what means soundness of the rule $\llabrn\DIA$:
 
-	\begin{center}
-		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
-	\end{center}
+%% 	\begin{center}
+%% 		\emph{For all model $\M$, if $\M \Vdash \B, \accs xy,  \Left, \labels{y}{A} \SEQ \Right$, then $\M \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$.}
+%% 	\end{center}
 
-	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
-	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
+%% 	In order to prove this statement, we assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ and we want to see that $\M_{0} \not \Vdash \B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$.
+%% 	From our assumption, we have that from $\M_{0} \not \Vdash \B, \Left, \labels{x}{\DIA A} \SEQ \Right$ we obtain $\M_{0} \Vdash \B$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash \labels{x}{\DIA A}$ and $\M_{0} \not \Vdash \Right$.
 From $\M_{0} \Vdash \labels{x}{\DIA A}$, according to the definition of the $\DIA$ operator, we have that there exists a world $\lb y$ in $\M_{0}$ such that $\accs xy$ and $\M_{0} \Vdash \labels{y}{A}$.
@@
 
-	\item Rule $\rlabrn\DIA$:
+%% 	\item Rule $\rlabrn\DIA$:
 
-	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
+%% 	We want to prove that the rule $\rlabrn\DIA$ is sound, which means that:
 
-	\begin{center}
-		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
-	\end{center}
+%% 	\begin{center}
+%% 		For all model $\M$, if $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$ then $\M \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$
+%% 	\end{center}
 
-	We prove this statement by way of contradiction.
+%% 	We prove this statement by way of contradiction.
 Let us assume there exists a model $\M_{0}$ such that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$, we want to show that $\M_{0} \not \Vdash \B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}$.
-	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
+%% 	From our hypothesis we have that $\M_{0} \not \Vdash \labels{x}{\DIA A}$, i.e.
 for all world $\lb y \in \M_{0}$ where $\accs xy$ we have $\M_{0} \not \Vdash \labels{y}{A}$.
@@
 Then we conclude that the rule $\rlabrn\DIA$ of the system $\labIKp$ is sound.
-\end{itemize}
+%% \end{itemize}
 
-The other cases are similar and we leave them to the reader.
+%% The other cases are similar and we leave them to the reader.

### 2019-10-03 caleidoscope/introduction.tex
small changes and comments everywhere

@@
 of logics. Unlike so-called \emph{internal calculi}, like
-hyper-sequents~\cite{avron:elc96} or nested
+hypersequents~\cite{avron:elc96}, nested
 sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
 labelled calculi have the advantage of being more uniform and being able to 
-accommode more logics.
+accommode a larger class of logics.
 
 Standard labelled sequent calculi attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally admit so called
+$\lb x$, witten as $\labels xA$, and additionally use
 \emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
@@
 relation $R$ that corresponds to the accessibility relation in 
-ordinary Kripke frames for modal logics, and a relation $\le$ that
-corresponds to the future relation in ordinary Kripke frames for
+Kripke frames for modal logics, and a relation $\le$ that
+corresponds to the preorder relation in Kripke frames for
 intuitionistic logic. Consequently, standard labelled systems for
@@
   modal logic. However, in intuitionistic modal logic they are not
-  equivalent, and even though the logic $\ISfour$, i.e., the
-  intuitionistic version of the modal logic $\Sfour$, contains both
-  axioms, they can be added independently to the logic $\IK$ (the
+  equivalent, and even though the logic $\IKfour$, i.e., the
+  intuitionistic version of the modal logic $\Kfour$, contains both
+  axioms, they can also be added independently to the logic $\IK$ (an
   intuitionistic version of $\K$). However, the proof theory of these
@@
   \end{equation}
+  \todo{add graphical representation of the conditions}
   respectively, have already been studied
   in~\cite{plotkin:stirling:86}.
+  \sonia{the general condition is correct but not the application to 4}
   \item The correspondence between the syntax and the semantics is not
@@
     means that every layer in the model can be lifted to any future of
-    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.} for  models, as
-  already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
+    any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.}   
+  models, 
+  \sonia{this is only true for logics outside of the path axioms.}
+  \todo{check that Simpson's system is sound and complete for all logics defined by path axioms.
+Is it that the axiomatisation is also sound and complete for every models and not only graph-consistent ones?}
+  as already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
   and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
 \end{enumerate}
-In order to address these two issues we propose here to extend the
-notion of labelled sequent by also allowing relational atoms of the
-form $\futs xy$. Consequently, we can easily translate the frame
+In order to address these two concerns we propose here to enrich usual 
+labelled sequent by allowing both, relational atoms of the
+form $\futs xy$ and of the form $\accs xy$. Consequently, we can easily translate the frame
 conditions in~\eqref{eq:4frame} into inference rules:
@@
 system. Ordinary labelled sequent systems for intuitionistic modal
-logic are single-conclusion~\cite{simpson:phd}. The same is true for
-the corresponding nested sequent
+logic are single-conclusion~\cite{simpson:phd}. 
+\sonia{No! the system for epistemic logic by Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13} is multi-conclusion}
+%
+The same is true for the corresponding nested sequent
 systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
@@
 
-\todo{maybe paragraph on related work? cite Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13}.}
+\todo{maybe paragraph on related work?}
 
-\section*{Introduction(old version, to be deleted)}
-\todo{We should work on the introduction}
-
-One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
+%\section*{Introduction(old version, to be deleted)}
+%\todo{We should work on the introduction}
+%
+%One possible-world semantics was established as a solid base to define modal logics, the idea of incorporating these notions into the proof theory of modal logics emerged.
 Fitch seems to have been the first one to formalise it, directly including symbols representing worlds into the language of his proofs in natural deduction \cite{Fitch}.
-
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
 %
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as
-used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
-Negri~\cite{Negri}. 
+%\emph{Labelled deduction} has been proposed by Gabbay~\cite{Gabbay} in the 80s as a unifying framework throughout proof theory in order to provide proof
+%systems for a wide range of logics. 
+%%
+%For modal logics it can take
+%the form of labelled natural deduction and labelled sequent systems as
+%used, for example, by Simpson~\cite{Simpson}, Vigan\`o~\cite{Vigano}, and
+%Negri~\cite{Negri}. 
+%%
+%These formalisms make explicit use not only of
+%labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
+%%
+%In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
+%logics) and the \emph{preorder relation} (for intuitionistic
+%logic), using the full power of the bi-relational semantics for
+%intuitionistic modal logics,
+%and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}. 
 %
-These formalisms make explicit use not only of
-labels, but also of relational atoms referring to the accessibility relation of a Kripke frame.
+%\todo{Simpson does not have internal cut-elimination}
 %
-In this short note we propose a system that represents both the \emph{accessibility relation} (for modal
-logics) and the \emph{preorder relation} (for intuitionistic
-logic), using the full power of the bi-relational semantics for
-intuitionistic modal logics,
-and developing fully the idea that Maffezioli, Naibo and Negri employed in~\cite{Maffezioli}.
-
-\todo{Simpson does not have internal cut-elimination}
-
-\sonia{
-  \begin{itemize}
-  \item internal vs externl calculi
-  \item extesion to axioms are truly intuitionistic (not just the
-    classical versions as in Simpson style)
-  \item connection with semantics compared to graph homomorphism
-    restiction in Simpson and ``indexed nested systems''
-  \end{itemize}
-}
-
-\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
-  \begin{itemize}
-  \item what we do:
-    \begin{itemize}
-    \item first systems (nested and labelled) for intuitionistic modal
-      logic where ``single conclusion'', i.e., only one formula on the
-      right.
-    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
-    \item Still rules that forced single formula on the right (white implication and white box)
-    \item by allowing both relations of the model in the proof system
-      we go to genuinely multiple conclusion: never ever a formula on
-      the right has to be deleted during proof search.
-    \end{itemize}
-  \item why we do it: 
-    \begin{itemize}
-    \item getting things right: labelled systems for classical modal
-      logics, or plain propositional intuiionistic logic have one
-      binary relation, which is exactly the relation of the standard
-      Kripke semantics. The standard Kripke semantics for
-      intuitionistic modal logic is birelational, with a strong
-      connectiion between the two binary relations. A clean labelled
-      system for these logics should incorporate both relations.
-    \item We get new logics.  In the standard nested sequent
-      or labelled sequent system for intuitionistic modal logic we
-      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
-      but here we can have them separtely.
-    \end{itemize}
-  \item how we do it:
-    \begin{itemize}
-    \item We start from the Maehara nested sequent system (which can
-      be translated straightforwardly into a labelled system with one
-      relation $R$.
-    \item the rules for $\AND$ and $\OR$ are trivial and as expected
-      they can be presented such that they are invertible on the left
-      and the right, they do not concern the relations $R$ and $\le$. 
-    \item So should be the rules for $\IMP$-left and $\BOX$-left and
-      identity, but there is a subtlety; see below...
-    \item the rules for $\DIA$ are also straightforward, as they
-      concern only $R$ but not $\le$.
-    \item The rules $\BOX$-right and $\IMP$-right are the ones that
-      force single conclusion in the Maehara system. This means that
-      here they create a future, using the relation $\le$.
-    \item In order to make everything work together, this forces us to
-      have reflexivity and transitivity of $\le$, explicely as rules
-      in the system, and have rules for the F1 and F2 conditions
-      making the relations $R$ and $\le$ go together.
-    \item As a consequence we also need a rule realizing monotonicity
-      for the formulas on the right.
-    \item However, we designed the system such that monotonicity is
-      admisible by encorporating it into the rules for identity,
-      $\IMP$-left and $\BOX$-left.
-    \end{itemize}
-  \end{itemize}
-}
+%\sonia{
+%  \begin{itemize}
+%  \item internal vs externl calculi
+%  \item extesion to axioms are truly intuitionistic (not just the
+%    classical versions as in Simpson style)
+%  \item connection with semantics compared to graph homomorphism
+%    restiction in Simpson and ``indexed nested systems''
+%  \end{itemize}
+%}
 %  
-%For sequent systems for intuitionistic logics there is always a choice
-%to be made: make the system \emph{single conclusion} following
-%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
-%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
-%variant because of the closer correspondence to the semantics. In that
-%respect, our system is closer to~\cite{kuz:str} than
-%to~\cite{Simpson} and~\cite{mar:str}.
+%\lutz{things that should be said explicitely somewhere (maybe intro, maybe somewhere else):
+%  \begin{itemize}
+%  \item what we do:
+%    \begin{itemize}
+%    \item first systems (nested and labelled) for intuitionistic modal
+%      logic where ``single conclusion'', i.e., only one formula on the
+%      right.
+%    \item Then ``multiple conclusion'' (Meahara-style) nested sequent.
+%    \item Still rules that forced single formula on the right (white implication and white box)
+%    \item by allowing both relations of the model in the proof system
+%      we go to genuinely multiple conclusion: never ever a formula on
+%      the right has to be deleted during proof search.
+%    \end{itemize}
+%  \item why we do it: 
+%    \begin{itemize}
+%    \item getting things right: labelled systems for classical modal
+%      logics, or plain propositional intuiionistic logic have one
+%      binary relation, which is exactly the relation of the standard
+%      Kripke semantics. The standard Kripke semantics for
+%      intuitionistic modal logic is birelational, with a strong
+%      connectiion between the two binary relations. A clean labelled
+%      system for these logics should incorporate both relations.
+%    \item We get new logics.  In the standard nested sequent
+%      or labelled sequent system for intuitionistic modal logic we
+%      always have both conjuncts we we add Scott-Lemmon/Geach axioms;
+%      but here we can have them separtely.
+%    \end{itemize}
+%  \item how we do it:
+%    \begin{itemize}
+%    \item We start from the Maehara nested sequent system (which can
+%      be translated straightforwardly into a labelled system with one
+%      relation $R$.
+%    \item the rules for $\AND$ and $\OR$ are trivial and as expected
+%      they can be presented such that they are invertible on the left
+%      and the right, they do not concern the relations $R$ and $\le$. 
+%    \item So should be the rules for $\IMP$-left and $\BOX$-left and
+%      identity, but there is a subtlety; see below...
+%    \item the rules for $\DIA$ are also straightforward, as they
+%      concern only $R$ but not $\le$.
+%    \item The rules $\BOX$-right and $\IMP$-right are the ones that
+%      force single conclusion in the Maehara system. This means that
+%      here they create a future, using the relation $\le$.
+%    \item In order to make everything work together, this forces us to
+%      have reflexivity and transitivity of $\le$, explicely as rules
+%      in the system, and have rules for the F1 and F2 conditions
+%      making the relations $R$ and $\le$ go together.
+%    \item As a consequence we also need a rule realizing monotonicity
+%      for the formulas on the right.
+%    \item However, we designed the system such that monotonicity is
+%      admisible by encorporating it into the rules for identity,
+%      $\IMP$-left and $\BOX$-left.
+%    \end{itemize}
+%  \end{itemize}
+%}
+%%
+%%For sequent systems for intuitionistic logics there is always a choice
+%%to be made: make the system \emph{single conclusion} following
+%%Gentzen~\cite{Gentzen} or \emph{multiple conclusion} following
+%%Maehara~\cite{Maehara}. In our work we choose the multiple conclusion
+%%variant because of the closer correspondence to the semantics. In that
+%%respect, our system is closer to~\cite{kuz:str} than
+%%to~\cite{Simpson} and~\cite{mar:str}.

### 2019-10-03 caleidoscope/main.tex
correcting the soundness file
small changes and comments everywhere

@@
 
-\input{macros2}
+\input{new-macros}
 
@@
    intuitionistic modal logics such that there is not only one, but
-   two relation symbols for the labels: one for the accessibility
+   two relation symbols appearing in sequents: one for the accessibility
    relation associated with the Kripke semantics for normal modal logics and
@@
    consequence it can encompass a wider range of intuitionistic modal
-   logics than standard labelled systems.
+   logics than existing labelled systems.
    %%

### 2019-10-03 caleidoscope/old-text.tex
small changes and comments everywhere

@@
 %
-%In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
+In particular, in order to prove (i) $\rightarrow$ (ii), we present a syntactic completeness proof with respect the Hilbert system which means that we prove all Hilbert axioms using the rules from our system $\labIKp$: we give a proof for all the axioms of propositional intuionistic logic, for the five variants of $\mathsf{k}$ axiom from the intuitionistic syntax and finally, we simulate the necesssitation rule and modus ponens.
 As we mentioned, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms.
 %
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
+As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $\rn{F_1}$ in the system.
 \bigskip

### 2019-10-03 caleidoscope/preliminaries.tex
small changes and comments everywhere

@@
 \end{itemize}
+\sonia{axioms vs. axiom schemes? do we need to write these on atomic formulas $a,b$ instead of generic formulas $A,B$?}
 
@@
 	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\todo{Add something else about Fischer-Servi theorem?}\lutz{no, but we should add the Plotkin-Stirling theorem about the relation between axioms and frame conditions} \todo{add an intro to the next theorem}
-
-%Plotkin and Stirling give proper correspondence results, but they must distinguish the two dual parts of each axiom and appeal to both relations of the frames,
-
-\lutz{maybe the foloowing goes to the ``extensions'' section. otherwise we have to define $\agklmn$ here}
-\begin{theorem}[\cite{plotkin:stirling:86}]
-	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\agklmn$ if and only if the frame satisfies:
-
-	if $\lb w R^{k} \lb u$ and $\lb w R^{m} \lb v$ then there exists $\lb{u'}$ such that $\futs{u}{u'}$ and there exists $\lb x$ such that $\lb{u'}R^{l}\lb x$ and $\lb v R^{n} \lb x$.
-
 \end{theorem}

### 2019-10-03 caleidoscope/system.tex
small changes and comments everywhere

@@
 intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. This is enough to define the notion of
+worlds $\lb x$ and $\lb y$. 
+\sonia{Not sure we want to make it sound so semantical here, with not much context.}
+%
+This is enough to define the notion of
 \emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, and $\Left$ and $\Right$ are
+where $\B$ is a set of relational and pre-order atoms, 
+\sonia{inconsistent naming with intro}
+and $\Left$ and $\Right$ are
 multi-sets of labelled formulas, all written as list, separated by commas.
@@
 We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
+\sonia{This is an interesting alternative view but for me the starting point really is the Maffezioli, Naibo and Negri paper. Maybe rephrase slightly to acknowledge their work too.}
 Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
@@
   preserving} admissible for $\labIKp$. However, we do not need this
-result in this paper, and therefore we leave it as an exercise to the
+result in this paper, and therefore we leave it to the interested
 reader. Nonetheless, we will give a short proof of

### 2019-10-03 caleidoscope/soundness.tex
adding some cases to soundness section

@@
 		\item $\rlabrn\bot$: This is trivial because $\bot$ is never forced.
-		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon}.
-		\item $\llabrn\BOX$: By way of contradiction, assume $\B, \Left,
+		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon-adm}.
+		\item $\llabrn\BOX$: By way of contradiction, assume that $\B, \Left,
 		\futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
@@
 			\Right}$. Contradiction.
-		\item $\rlabrn\BOX$: By way of contradiction, assume that $\futs xy,
+		\item $\rlabrn\BOX$: By way of contradiction, assume that $\B, \futs xy,
 		\accs yz, \Left \SEQ \Right, \labels{z}{A}$ is valid in all
@@
 		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
-		$\lb{y'}\rel_\M\lb{z'}$ and $\cforce\M{z'}{A}$. Now we let
+		$\lb{y'}\rel_\M\lb{z'}$ and $\nforce\M{\lb{z'}}{\fm A}$. Now we let
 		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
 		y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
-		on all other labels. Then $\nforce\M{\inter\cdot'}{\futs xy,
+		on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \futs xy,
 			\accs yz, \Left \SEQ \Right, \labels{z}{A}}$. Contradiction.
-		\item \lutz{if you want, you can add some more cases here, following the pattern above.}
+
+		\item $\rlabrn\IMP$: By way of contradiction, assume that $\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}$ is valid in all birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{A \IMP B}$ is not, where $\lb y$ does not occur in $\B$ or $\Left$ or $\Right$.
+This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}$.
+This means that there exists world $\lb{y'}$ in $\M$ such that $\inter x\le_\M \lb{y'}$ and $\cforce\M{y'}{A}$ but $\nforce\M{\lb{y'}}{\fm B}$.
+Now we let 	$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot'=\inter\cdot$ on all other labels.
+Then $\nforce\M{\inter\cdot'}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$.
+Contradiction.
+
+		\item $\llabrn\DIA$: By way of contradiction, assume that $\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ is valid in all birelational frames, but $\B, \Left, \labels{x}{\DIA A} \SEQ \Right$ is not, where $\lb y$ does not occur in $\B$ or $\Left$ or $\Right$.
+This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}$, i.e.
+$\cforce \M x{\DIA A}$.
+This means that there exists world $\lb{y'}$ in $\M$ such that $\inter x\rel_\M \lb{y'}$ and $\cforce \M {\lb{y'}}{A}$.
+Now we let $\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot' = \inter\cdot$ on all other labels.
+Then $\nforce\M{\inter\cdot'}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$.
+Contradiction.
+
+		%\item $\rlabrn\DIA$: By way of contradiction, assume that $\B, \accs xy, \Left \SEQ \Right,  \labels{x}{\DIA A}, \labels{y}{A}$ is valid in all birelational frames, but $\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}$ is not.
+This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}$, i.e., $\inter x\rel_\M\inter y$ and $\nforce\M {\lb x}{\fm{\DIA A}}$.
+This means that for all worlds $\lb{y}$ where $\inter x\rel_\M\inter y$,  \marianela{to be completed}
 	\end{itemize}

### 2019-10-07 caleidoscope/conclusion.tex
conclusion file

\section{Conclusion}

In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:naibo:negri} and generalise it to the class of logics defined by (one-sided intuitionistic) Scott-Lemmon axioms.
%
We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut-elimination argument.

We believe that it is furthermore the more appropriate way to treat logics outside of the path axioms definable fragment.
%
However, we have not showed that our system satisfies Simpson's 6th requirement, that is, "there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [our system] is sound and complete".
%
To make sure that his system satisfies this requirement, Simpson chose to depart from the direct correspondence with modal axioms and their corresponding class of Kripke frames.
%
We instead took the way of a direct correspondence of our system with the class of frames defined by Scott-Lemmon axioms as uncovered by~\cite{plotkin:sterling}, but as this class of logics seems to be rather well-behaved, we believe it shoud be possible to prove the satisfaction of Simpson's 6th requirement too.

As for more general future work, there is a real necessity of a global view on intutionistic modal logics.
%
The work of~\cite{dalmonte:grellois:olivetti:arxiv19} is a great first step in understanding them in the context of non-normal modalities and neighbourhood semantics.
%
It would be interesting to know how and where the class of logics we considered can be included in their framework.

### 2019-10-07 caleidoscope/introduction.tex
proof read section 1, 2 and 3

@@
 hypersequents~\cite{avron:elc96}, nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann?},
+sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann:tableaux15},
 labelled calculi have the advantage of being more uniform and being able to 
@@
 \begin{enumerate}
-\item The transitivity rule in~\eqref{eq:Rtrans} corresponds to both
+\item The transitivity rule in~\eqref{eq:Rtrans} can be axiomatised by the conjunction of the two
   versions of the $\fourax$-axiom
@@
   \end{equation}
-  as they are equivalent in classical
+  which are equivalent in classical
   modal logic. However, in intuitionistic modal logic they are not
@@
   axioms, they can also be added independently to the logic $\IK$ (an
-  intuitionistic version of $\K$). However, the proof theory of these
-  new logics has not been studied before, as no existing labelled (or
+  intuitionistic version of $\K$). The proof theory of these
+  new logics has not been studied before; no existing labelled (or
   label-free) proof system can handle them, even though the
@@
   \end{equation}
-  \todo{add graphical representation of the conditions}
+%  \todo{add graphical representation of the conditions}
+  $$
+  \xymatrix{
+  	x' \ar@{.>}[drr]^R \\
+  	x \ar@{.>}[u]^\le \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z
+  }
+  \qquad\qquad
+  \xymatrix{
+  	&& z''  \\
+  	x  \ar@{.>}[urr]^R \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z \ar@{.>}[u]^\le
+  }
+  $$
   respectively, have already been studied
   in~\cite{plotkin:stirling:86}.
-  \sonia{the general condition is correct but not the application to 4}
+%  \sonia{the general condition is correct but not the application to 4}
   \item The correspondence between the syntax and the semantics is not
@@
 Is it that the axiomatisation is also sound and complete for every models and not only graph-consistent ones?}
+  \sonia{yes, they are sound and complete for the general models, but they do not \emph{characterize} the frames, they are not \emph{frame conditions}, as opposed to the \emph{correspondence result} of Plotkin and Sterling.}
   as already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
@@
 \sonia{No! the system for epistemic logic by Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13} is multi-conclusion}
+\todo{need to say that it is the same principle as in their work, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics while keeping the nice invertibility property.}
 %

### 2019-10-07 caleidoscope/system.tex
some progress on extension section
proof read section 1, 2 and 3

@@
 \emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
-x$ and a formula $\fm A$. The intended meaning is that $\fm A$ holds
-at world $\lb x$. A \emph{relation atom} is either an expression
-$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels and the
-intended meaning is that the corresponing relation holds between the
-worlds $\lb x$ and $\lb y$. 
-\sonia{Not sure we want to make it sound so semantical here, with not much context.}
+x$ and a formula $\fm A$. 
+%The intended meaning is that $\fm A$ holds at world $\lb x$. 
+A \emph{relation atom} is either an expression
+$\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels. 
+%and the intended meaning is that the corresponing relation holds between the worlds $\lb x$ and $\lb y$. 
+%\sonia{Not sure we want to make it sound so semantical here, with not much context. Also, it is wron, because of sequent LHS!}
 %
-This is enough to define the notion of
-\emph{(labelled) sequent}, which is a triple $\lseq\B\Left\Right$,
-where $\B$ is a set of relational and pre-order atoms, 
-\sonia{inconsistent naming with intro}
+%This is enough to define the notion of
+A \emph{(labelled) sequent} is a triple $\lseq\B\Left\Right$,
+where $\B$ is a set of relational atoms
+%\sonia{inconsistent naming with intro}
 and $\Left$ and $\Right$ are
-multi-sets of labelled formulas, all written as list, separated by commas.
+multi-sets of labelled formulas, all written as lists, separated by commas.
 
@@
 		\\\\
-		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, x \le y, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+		$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
 		&
@@
 Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
-However, this naive translation wpould also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
+However, this naive translation would also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
 \begin{equation}
@@
 of~\cite{str:2017maehara}, these are the two rules that force
-single-conclusion. This is the reason why in our system we need the
-$\le$ in the relational atoms; we need to go to the future of the
-current world.  In the Kripke-semantics in~\eqref{eq:kripke} the two
-connectives $\IMP$ and $\BOX$ are the ones that need the
-future-relation $\le$. This relation is reflexive and transitive. In
+single-conclusion. 
+%This is the reason why in our system we need the
+%$\le$ in the relational atoms; we need to go to the future of the
+%current world.  
+%
+In our system, this phenomenon is replaced by a re-positioning of the considered formulas to a fresh label.
+%
+In the Kripke-semantics in~\eqref{eq:kripke} the two
+connectives $\IMP$ and $\BOX$ are the ones that make use of the
+pre-order relation $\le$. This relation is reflexive and transitive. In
 order to capture that in the proof system, we need to add the rules
 $\rn{refl}$ and $\rn{trans}$.
+%
+These can be obtained by applying the axioms-as-rules methodology as in~\cite{maffezioli:etal:synthese13}.
 
 Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected in the proof
-system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
+strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
 %
-However, these two rule create new labels, and in order to be
+However, these two rules create new labels, and in order to be
 complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
@@
   \label{eq:mono}
-  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-    \lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}
+  \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}\Right}{
+    \lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}, \labels{y}{A}}\Right}
   \hskip6em
-  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x'}{A}}}{
-    \lseq{\B, \futs{x}{x'}}{\Left}{\Right, \labels{x}{A}, \labels{x'}{A}}}
+  \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{y}{A}}}{
+    \lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{x}{A}, \labels{y}{A}}}
 \end{equation}
@@
 $\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
-shown on the right in~\eqref{eq:mono} above is admissible.
+shown on the right in~\eqref{eq:mono} above become admissible.
 
@@
   \label{prop:id}
-	The following general idenity axiom~
+	The following general identity axiom~
 	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
@@
 
+%\sonia{is a simpler derivation available along those lines, using Proposition~\ref{prop:mon-adm}?
+%	\begin{smallequation*}
+%		\vlderivation{
+%			\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
+%				\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+%					\vlin{\rn{mon_R}+\rn{mon_L}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{y}{A}}{
+%						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A}, \labels{y}{A} \SEQ \Right, \labels{z}{B}, \labels{y}{A}, \labels{z}{A}}{
+%							\vlhy{}
+%						}
+%					}
+%				}{
+%				\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \Left, \labels{y}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
+%					\vlhy{}
+%				}
+%			}
+%		}
+%	}
+%\end{smallequation*}
+%}
+
 	\item $\fm{\BOX A}$
@@
 		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+			\vlin{\llabrn\DIA}{}{\B, \futs xy, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
 				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
@@
 \end{equation}
-Then we can summarize soundness and completeness, and cut
-admissibil\texttt{}ity of $\labIKp$ in the following Theorem:
+Then we can summarize soundness, completeness, and cut
+admissibility of $\labIKp$ in the following Theorem:
 
@@
 
-Once we have shown cut elimination (the implcation \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
+Once we have shown cut elimination (the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.
 
@@
     \vlderivation{
-      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}\Right}{
-        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}}{\Right, \labels{x'}{A}}}{
+      \vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}\Right}{
+        \vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}{\Right, \labels{y}{A}}}{
           \vlhy{}}}{
         \vlhy{\quad}}{
-        \vlhy{\lseq{\B, \futs{x}{x'}}{\Left, \labels{x}{A}, \labels{x'}{A}}\Right}}
+        \vlhy{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}, \labels{y}{A}}\Right}}
     }
   \end{smallequation*}
-  And both these rules are admissible by Proposition~\ref{prop:id} and
+  and both these rules are admissible by Proposition~\ref{prop:id} and
   Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is

### 2019-10-07 caleidoscope/soundness.tex
proof read section 4 and 5

@@
 	Let $\M = \langle W, \rel_\M, \le_\M, V \rangle$ be a model, and let
-	$\SG$ be the sequent $\lseq\B\Left\Right$. A \emph{$\SG$-interpretation
+	$\SG$ be the sequent $\lseq\B\Left\Right$. 
+	\sonia{$\mathcal G$ usually denotes only the relational context.
+using it for the whole sequent is confusing.
+this concept is called $\mathcal G$-interpretation as it is a graph homomorphism from the graph described by $\mathcal G$ to the model.}
+	A \emph{$\SG$-interpretation
 		in $\M$} is a mapping $\inter{\cdot}$ from the labels in $\SG$ to the set $W$ of worlds in $\M$, such that whenever $\accs xy$ in $\B$, then $\inter x\rel_\M\inter y$, and whenever $\futs xy$ in $\B$, then $\inter x\le_\M\inter y$.
@@
 			\Right}$. Contradiction.
+		\todo{The reasoning by contradiction is not necessary. Could be rewritten more lightly as follows:}
+			%
+			Assume that $\B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
+			is valid in all birelational frames. 
+			Consider a model $\M$ and an interpretation $\inter\cdot$ of the conclusion sequent
+			$\B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$ into $\M$, such
+			that for all $\labels{z}{C} \in \Gamma$ we have $\M, \inter z \Vdash \fm C$
+			and $\cforce \M x{\BOX A}$. %and $\cnforce \M wB$ for all $\labels wB\in\Right$. However, 
+			Hence, as $\inter x\le_\M\inter y$ and $\inter y\rel_\M\inter z$, 
+			by the definition of forcing in~\eqref{eq:kripke} we also have $\cforce \M zA$, and 
+			consequently $\cforce \M wB$ for all $\labels wB\in\Right$. 
+			Thus, $\cforce \M{\inter\cdot}{\B, \Left, \futs
+				xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
+				\Right}$. \todo{should we rewrite the whole proof?}
+
 		\item $\rlabrn\BOX$: By way of contradiction, assume that $\B, \futs xy,
@@
 			A}$ is not, where $\lb y$ and $\lb z$ do not occur in $\B$ or
-		$\Left$ or $\Right$.This means that we have a model $\M$ and an
+		$\Left$ or $\Right$.
+		This means that we have a model $\M$ and an
 		interpretation $\inter\cdot$, such that
-		$\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX
-				A}}$. This means that there are worlds $\lb{y'}$ and $\lb{z'}$
+		$\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}$. 
+%		Namely, for all $\labels{w}{C}$ in $\Gamma$, $\M, \inter w \Vdash \fm C$, but
+%		for all $\labels{z}{B}$ in $\Delta$, $\nforce {\M }{\inter z}{ \fm B}$.
+		So in particular, there are worlds $\lb{y'}$ and $\lb{z'}$
 		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
-		$\lb{y'}\rel_\M\lb{z'}$ and $\nforce\M{\lb{z'}}{\fm A}$. Now we let
+		$\lb{y'}\rel_\M\lb{z'}$ and $\nforce\M{\lb{z'}}{\fm A}$. 
+		%
+		Now we let
 		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
@@
 This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}$.
-This means that there exists world $\lb{y'}$ in $\M$ such that $\inter x\le_\M \lb{y'}$ and $\cforce\M{y'}{A}$ but $\nforce\M{\lb{y'}}{\fm B}$.
+So there exists a world $\lb{y'}$ in $\M$ such that $\inter x\le_\M \lb{y'}$ and $\cforce\M{y'}{A}$ but $\nforce\M{\lb{y'}}{\fm B}$.
 Now we let 	$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot'=\inter\cdot$ on all other labels.

### 2019-10-08 caleidoscope/soundness.tex
1 answer
rewrote section 7

@@
 			\Right}$. Contradiction.
-		\todo{The reasoning by contradiction is not necessary. Could be rewritten more lightly as follows:}
-			%
-			Assume that $\B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
-			is valid in all birelational frames. 
-			Consider a model $\M$ and an interpretation $\inter\cdot$ of the conclusion sequent
-			$\B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$ into $\M$, such
-			that for all $\labels{z}{C} \in \Gamma$ we have $\M, \inter z \Vdash \fm C$
-			and $\cforce \M x{\BOX A}$. %and $\cnforce \M wB$ for all $\labels wB\in\Right$. However, 
-			Hence, as $\inter x\le_\M\inter y$ and $\inter y\rel_\M\inter z$, 
-			by the definition of forcing in~\eqref{eq:kripke} we also have $\cforce \M zA$, and 
-			consequently $\cforce \M wB$ for all $\labels wB\in\Right$. 
-			Thus, $\cforce \M{\inter\cdot}{\B, \Left, \futs
-				xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
-				\Right}$. \todo{should we rewrite the whole proof?}
+%		\todo{The reasoning by contradiction is not necessary. Could be rewritten more lightly as follows:}
+%			%
+%			Assume that $\B, \Left, \futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
+%			is valid in all birelational frames. 
+%			Consider a model $\M$ and an interpretation $\inter\cdot$ of the conclusion sequent
+%			$\B,\Left, \futs xy, \accs yz, \labels{x}{\BOX A} \SEQ \Right$ into $\M$, such
+%			that for all $\labels{z}{C} \in \Gamma$ we have $\M, \inter z \Vdash \fm C$
+%			and $\cforce \M x{\BOX A}$. %and $\cnforce \M wB$ for all $\labels wB\in\Right$. However, 
+%			Hence, as $\inter x\le_\M\inter y$ and $\inter y\rel_\M\inter z$, 
+%			by the definition of forcing in~\eqref{eq:kripke} we also have $\cforce \M zA$, and 
+%			consequently $\cforce \M wB$ for all $\labels wB\in\Right$. 
+%			Thus, $\cforce \M{\inter\cdot}{\B, \Left, \futs
+%				xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
+%				\Right}$. \todo{should we rewrite the whole proof?}\lutz{no. we do by contradiction. I'll explainon skype.}
 

### 2019-10-08 caleidoscope/introduction.tex
added missing fresh labels on proofs

@@
 Maehara style multiple-conclusion systems in nested
-sequents~\cite{kuz:str:maehara}, and therefore also in ordinary
+sequents~\cite{str:2017maehara}, and therefore also in ordinary
 labelled sequents. However, also in these systems there are rules

### 2019-10-08 caleidoscope/soundness.tex
general details

@@
 		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon-adm}.
-		\item $\llabrn\BOX$: By way of contradiction, assume that $\B, \Left,
-		\futs xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
-		is valid in all birelational frames, but $\B,\Left, \futs xy,
-		\accs yz, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
+		\item $\llabrn\BOX$: By way of contradiction, assume that $\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
+		is valid in all birelational frames, but $\B, \futs xy,	\accs yz,\Left, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
 		we have a model $\M$ and an interpretation $\inter\cdot$, such
-		that $\M,\inter\cdot\not\Vdash\B,\Left, \futs xy, \accs yz,
-		\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
+		that $\M,\inter\cdot\not\Vdash\B, \futs xy, \accs yz, \Left,	\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
 		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ and
@@
 		definition of forcing in~\eqref{eq:kripke} we also have $\cforce
-		\M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \Left, \futs
-			xy, \accs yz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
+		\M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
 			\Right}$. Contradiction.

### 2019-10-08 caleidoscope/conclusion.tex
final pass

@@
 
-In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:naibo:negri} and generalise it to the class of logics defined by (one-sided intuitionistic) Scott-Lemmon axioms.
+In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and generalise it to the class of logics defined by (one-sided intuitionistic) Scott-Lemmon axioms.
 %
@@
 
-We believe that it is furthermore the more appropriate way to treat logics outside of the path axioms definable fragment.
+For a restricted class of logics defined by so-called \emph{path axioms}: $(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\ref{simpson:phd}.
 %
+%\todo{For path axioms we must have that adding the rule for the two sides of the axiom is equivalent to adding the rule that doesn't make use of the pre-order.
+Is it possible to see that directly on the proof theoretical side?}
+%\sonia{probably not because the preorder is introduced/used in other rules for $\BOX$ and $\IMP$}
+%
+We believe that the framework presented here might be the more appropriate way to treat logics outside of the path axioms definable fragment.
+
 However, we have not showed that our system satisfies Simpson's 6th requirement, that is, "there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [our system] is sound and complete".
 %
-To make sure that his system satisfies this requirement, Simpson chose to depart from the direct correspondence with modal axioms and their corresponding class of Kripke frames.
+To make sure that his system satisfies this requirement, Simpson chose to depart from the direct correspondence with modal axioms and their corresponding class of Kripke frames, and to study intuitionistic purely as a fragment of intuitionistic first-order logic.
 %
-We instead took the way of a direct correspondence of our system with the class of frames defined by Scott-Lemmon axioms as uncovered by~\cite{plotkin:sterling}, but as this class of logics seems to be rather well-behaved, we believe it shoud be possible to prove the satisfaction of Simpson's 6th requirement too.
+We instead took the way of a direct correspondence of our system with the class of frames defined by Scott-Lemmon axioms as uncovered by~\cite{plotkin:stirling:86}, but as this class of logics seems to be rather well-behaved, we believe it shoud be possible to prove the satisfaction of Simpson's 6th requirement too.
 

### 2019-10-08 caleidoscope/system.tex
final pass

@@
 We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
-\sonia{This is an interesting alternative view but for me the starting point really is the Maffezioli, Naibo and Negri paper. Maybe rephrase slightly to acknowledge their work too.}
+%\sonia{This is an interesting alternative view but for me the starting point really is the Maffezioli, Naibo and Negri paper. Maybe rephrase slightly to acknowledge their work too.}
 Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
@@
 		\vlderivation{
-			\vlin{\llabrn\DIA}{}{\B, \futs xy, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\color{red}\rn{F_2}}{}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+			\vlin{\llabrn\DIA}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\color{red}\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
 					\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{

### 2019-10-08 caleidoscope/conclusion.tex
small modif

@@
 
-For a restricted class of logics defined by so-called \emph{path axioms}: $(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\ref{simpson:phd}.
+For a restricted class of logics defined by so-called \emph{path axioms}: $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\ref{simpson:phd}.
 %

### 2019-12-03 caleidoscope/conclusion.tex
fixed missing refs

--- 2019-10-08 caleidoscope/conclusion.tex
@@
 
-For a restricted class of logics defined by so-called \emph{path axioms}: $(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\ref{simpson:phd}.
+For a restricted class of logics defined by so-called \emph{path axioms}: $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
 %

### 2020-03-10 aiml20/simpson.tex
added idea for Simpson proof

\documentclass[twoside]{aiml18}
\usepackage{aiml18macro}
%%% Extracting symbols from MnSymbol 
\DeclareFontFamily{U} {MnSymbolC}{}
%
\DeclareFontShape{U}{MnSymbolC}{m}{n}{
	<-6>  MnSymbolC5
	<6-7>  MnSymbolC6
	<7-8>  MnSymbolC7
	<8-9>  MnSymbolC8
	<9-10> MnSymbolC9
	<10-12> MnSymbolC10
	<12->   MnSymbolC12}{}
\DeclareFontShape{U}{MnSymbolC}{b}{n}{
	<-6>  MnSymbolC-Bold5
	<6-7>  MnSymbolC-Bold6
	<7-8>  MnSymbolC-Bold7
	<8-9>  MnSymbolC-Bold8
	<9-10> MnSymbolC-Bold9
	<10-12> MnSymbolC-Bold10
	<12->   MnSymbolC-Bold12}{}
%
\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
%
\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}

\input{new-macros}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%The following line defines the page header consisting of the surnames of the authors.
% Please include only the last names! 
% Separate by commas except the last two surnames which are separated by an "and".
\def\lastname{Marin, Morales and Stra{\ss}burger}

\begin{document}

\begin{frontmatter}
  \title{Comparing system $\labIKp$ and Simpson system}
 % \author{Sonia Marin}
  %\address{IT-Universitetet i K{\o}benhavn \\ Denmark }
 %\author{Marianela Morales}
 %\address{Universidad Nacional de C\'ordoba \\ Argentina}
  % \author{Lutz Stra{\ss}burger}
 %\address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}

 \begin{abstract}
   %We present a labelled sequent system for intuitionistic modal logic equipped with two relation symbols, one for the accessibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics   for intuitionistic logic. 
   %
   %Thus, it is in close correspondence with birelational Kripke semantics for intuitionistic modal logic and can encompass a wider range of intuitionistic logics than state-of-the-art labelled systems.

   %% . We show the possibility of extend labelled sequents
   %% with a preorder relation symbol in order to capture intuitionistic
   %% modal logic. For this, we obtain a proof system which is complete
   %% with respect to Hilbert system.  Also, we present the proof for
   %% completeness using Simpson system.
  \end{abstract}

  \begin{keyword}
  Intuitionistic modal logic, Labelled sequents, Proof theory, Simpson system.
  \end{keyword}
 \end{frontmatter}

\section{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marianela{Introduce the idea of having cut-elimination for multi-conclusion systems}

\section{Intuitionistic modal logics}

%%Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $x$R$y$, where $x$, $y$ range over a set of variables and $A$ is a modal formula. A one-sided labelled sequent is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational atoms and $\Right$ a multiset of labelled formulas. A simple proof system for classical modal logic K can be obtained in this formalism (\textbf{Fig. 1}). 
%%
%%\begin{figure}[h]
%%\begin{center}
%%
%%$\vlderivation {\vlinf{\id}{}{\B \SEQ \Right, x: a, x: \vls-a}{}}$
%%\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$
%%
%%
%%$\vliinf{\vlab}{}{\B \SEQ \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
%%\hspace{7mm}$\vlinf{\olab}{}{\B \SEQ \Right, x \colon \vls[A.B]}{\olabr}$
%%
%%
%%$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
%%\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
%%
%%
%%\end{center}
%%\caption{System labK}
%%\end{figure}
%%These rule schemes can occur in different contexts and different calculi. The context that interests us is when it is applied to modal logic.
%%\\
%%
%%The idea to extend this system to another to capture intuitionistic modal logics allows us to study the Kripke semantics for this type of logics:

The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$. %, standing most generally for \emph{necessity} and \emph{possibility}.
%
Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
%
$$
A \coloncolonequals
a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
$$
%
%We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.

%Obtaining the intuitionistic variant of K is more involved than the classical variant. 
%%
%Lacking De Morgan duality, there are several variants of k that are classically but not intuitionistically
%equivalent. 
%%
%Five axioms have been considered as primitives in the literature. 
%

The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
%, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
%
It is obtained from intuitionistic propositional logic by adding:
\begin{itemize}
	\item the \emph{necessitation rule}: $\BOX A$ is a theorem if $A$ is a theorem; and
	\item the following five variants of the \emph{distributivity axiom}:
	\begin{equation*}
	\label{eq:ik}%\hskip-2em
	\begin{array}[t]{r@{\;}l@{\quad}r@{\;}l@{\quad}r@{\;}l}
	\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
	&
	\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
	&
	\kax[5]\colon&\DIA\BOT\IMP\BOT
	\\
	\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
	&
	\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
	\end{array}
	\end{equation*}
\end{itemize}

The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
%
It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.

\begin{definition}
	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ satisfying:
	\begin{enumerate}
		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.

		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
	\end{enumerate}
	%	
\end{definition}

\begin{definition}
	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
	if $w \le w'$ then $V(w)\subseteq V(w')$.
\end{definition}

We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
%
Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:

$w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$

$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$

$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$

$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill $(\ast)$

$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.

\begin{definition}
	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
	%
	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
\end{definition}

%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
%
%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.

Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.

\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
\end{theorem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Intuitionistic labelled sequent}

\todo{finish writing Simpson system}
\begin{figure}%[h]
	\centering
	\small
	\fbox{
		\begin{tabular}{@{\!}c@{\quad}c}
			$\vlinf{\rn{id_{s}}}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}$
			&
			$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \labels{z}{A}}{}$

			\\\\

			$\vlderivation {\vlin {\llabrn\AND}{}{\B, \Left, \labels{x}{A \AND B} \SEQ \labels{z}{C}}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \labels{z}{C}}}}$
			&
			$\vlderivation { \vliin {\rlabrn\AND}{}{\B, \Left, \SEQ \labels{x}{A \AND B}}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
%		
			\\\\

%		\vspace{3mm}
%		
%		
%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \vljm B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
%		
%		\vspace{3mm}
%		
%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
%

		\end{tabular}		
	}		
	\caption{System $\lab\IK$}
	\label{fig:labIK}
\end{figure}

\begin{figure}[!t]
	\begin{center}
		\fbox{
			%	\begin{minipage}{.95\textwidth}
			\begin{tabular}{c@{\quad}c}
				$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
				&
				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
				%\quad
				%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
				\\\\
				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
				&
				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
				\\\\
				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
				&
				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
				\\\\
				\multicolumn{2}{c}{
					$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
				}
				\\\\
				\multicolumn{2}{c}{
					$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$ 
					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
				}
				\\\\
				$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
				&
				$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
				\\\\
				$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
				&
				$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
				\\
				\multicolumn{2}{c}{
					$\mbox{\hbox to .9\linewidth{\dotfill}}$
				}
				\\
				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
				&
				$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
				\\\\
				\multicolumn{2}{c}{
					$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
				}
				\\\\
				\multicolumn{2}{c}{
					$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
				}
			\end{tabular}		
			%\end{minipage}
		}		
	\end{center}
	\caption{System $\labIKp$}
	\label{fig:labIKp}
\end{figure}

%\begin{figure}%[h]
%	\centering
%	\small
%	\fbox{
%		\begin{minipage}{.95\textwidth}
%			\begin{tabular}{@{\!}c@{\quad}c}
%				$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
%				&
%				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
%				\quad
%				$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
%				\\\\
%				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
%				&
%				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
%				\\\\
%				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
%				&
%				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
%				\\\\
%				\multicolumn{2}{c}{
%					$\vlinf{\llabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, x \le y, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
%				}
%				\\\\
%				\multicolumn{2}{c}{
%					$\vliinf{\rlabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
%					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
%				}
%				\\\\
%				$\vlinf{\llabrn\BOX}{}{\B, \Left, x \le y, yRz, \labels{x}{\BOX A} \SEQ \Right}{\B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
%				&
%				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \Left, x \le y, y \rel z \SEQ \Right, \labels{z}{A}}$
%				\\\\
%				$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \Left, x \rel y, \labels{y}{A} \SEQ \Right}$
%				&
%				$\vlinf{\rlabrn\DIA}{}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
%				\\
%				\multicolumn{2}{c}{
%					$\mbox{\hbox to .9\linewidth{\dotfill}}$
%				}
%				\\
%				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
%				&
%				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
%				\\\\
%				\multicolumn{2}{c}{
%					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
%				}
%				\\\\
%				\multicolumn{2}{c}{
%					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
%				}
%			\end{tabular}		
%		\end{minipage}
%	}		
%	\caption{System $\labIKp$}
%	\label{fig:labIKp}
%\end{figure}

Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{Simpson}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{Strassburger} (for a survey see~\cite[Chap.~3]{Marin}).

Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent. Simpson's system is displayed on Figure~\ref{fig:}

Echoing the definition of bi-relational structures, in  ~\cite{MarinMoralesStrassburger} another extension of labelled deduction to the intuitionistic setting is presented. This extension allows us to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}. 
%

\begin{definition}
	A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $\accs{x}{y}$ and preorder atoms $\futs{x}{y}$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
\end{definition}

The proof system for intuitionistic modal logic in this formalism obtained is $\labIKp$, displayed on Figure~\ref{fig:labIKp}.

\section{Multi-conclusion vs Single-conclusion??}

\section{Differences between Simpson system and system $\labIKp$}

Most rules in the system $\labIKp$ are similar to the ones of Simpson~\cite{Simpson}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
%
In particular, the rules introducing the $\BOX$-operator correspond to the definition $(\ast)$.
%
Furthermore, the system $\labIKp$ has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.

\section{title}
%We present a completeness proof for the system $\labIKp$ using Simpson system. Knowing that Simpson system is a \emph{cut-free} system, the proof lets us know that the system $\labIKp$ is complete without the cut rule. 
%
%We show the proof by case analysis. 
%
%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
We show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.

\begin{theorem}[Simpson~\cite{Simpson}]
	\label{thm:simpson-sound-compl}
	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
\end{theorem}

\begin{definition}

\end{definition}

\begin{theorem}
	If there is a proof $\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{m}}{\B, \Left \SEQ \labels{z}{C}}}$ in $\labIKp$.
\end{theorem}

\begin{proof}

	In order to develop this proof, we transform the relation $\rel$ presented in Simpson system to $S$ in order to incorporate the following definition:

	$\rels xy \equiv \futs xz, \accs zy$ where $\lb z$ can be $\lb z = \lb x$ or a new fresh variable.

	We are proving the theorem by case analysis on the last rule in $\DD$. 
%
	Most of the rules in $\lab\IK$ are the same as rules in $\labIKp$ except for the following:

	\begin{itemize}
		\item Rule $\rn{id}$:

		$$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}
		\reducesto
		\vlderibase{\rn{refl}}{}{\B, \Left, \labels{x}{a} \SEQ \labels{x}{a}}{
			\vlin{\labrn{id}}{}{\B, \futs xx, \Left, \labels{x}{a} \SEQ \labels{x}{a}}{
				\vlhy{}
			}
		}$$

		\item Rules $\rlabrn[1]\OR$ and $\rlabrn[2]\OR$ :
		$$	\vlderibase{\rlabrn[1]\OR}{}{\B, \Left \SEQ \labels{x}{A \OR B}}{
			\vlhtr{\DD_1}{\B, \Left \SEQ \labels{x}{A}}
		}
		\quad\text{or}\quad
		\vlderibase{\rlabrn[2]\OR}{}{\B, \Left \SEQ \labels{x}{A \OR B}}{
			\vlhtr{\DD_1}{\B, \Left \SEQ \labels{x}{B}}
		}
		\reducesto
		\vlderibase{\rlabrn\OR}{}{\B, \Left \SEQ \labels{x}{A \OR B}}{
			\vlhtr{\DD_1^\rn{mw}}{\B, \Left \SEQ \labels{x}{A}, \labels{x}{B}}
		}$$

		\item Rule $\llabrn\BOX$:

		$$\vlderibase{\llabrn\BOX}{}{\B, \rels xy, \Left, \labels{x}{\BOX A} \SEQ \labels{z}{B}}{
		\vlhtr{\DD_1}{\B, \rels xy, \Left, \labels{x}{\BOX A}, \labels{y}{A} \SEQ \labels{z}{B}}
		}\reducesto
		\vlderibase{\equiv}{}{\B, \rels xy, \Left, \labels{x}{\BOX A} \SEQ \labels{z}{B}}{
		\vlin{\llabrn\BOX}{}{\B, \futs xz, \accs zy, \Left, \labels{x}{\BOX A} \SEQ \labels{z}{B}}{ \vlin{\equiv}{}{\B, \futs xz, \accs zy, \Left, \labels{x}{\BOX A}, \labels{y}{A} \SEQ \labels{z}{B}}{\vlhtr{\DD_1^\rn{mw}}{\B, \rels xy, \Left, \labels{x}{\BOX A}, \labels{y}{A} \SEQ \labels{z}{B}}}
		}
		}$$

		\item Rule $\rlabrn\BOX$:

		$$\vlderibase{\rlabrn\BOX}{}{\B, \Left \SEQ \labels{x}{\BOX A}}{
			\vlhtr{\DD_1}{\B, \rels xy, \Left \SEQ \labels{y}{A}}
		}
		\reducesto
		\vlderibase{\rlabrn\BOX}{\lb z, \lb y \mbox{ fresh}}{\B, \Left \SEQ \labels{x}{\BOX A}}{ \vlin{\equiv}{}{\B, \futs xz, \accs zy, \Left \SEQ \labels{y}{A}}{	\vlhtr{\DD_1^\rn{m}}{\B, \rels xy, \Left \SEQ \labels{y}{A}}}
		}$$

		\item Rule $\llabrn\DIA$:

		$$\vlderibase{\llabrn\DIA}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \labels{z}{B}}{\vlhtr{\DD_1}{\B, \rels xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}}
		\reducesto
		\vlderibase{\llabrn\DIA}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \labels{z}{B}}{\vlin{\rn{refl}}{}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}{\vlin{\equiv}{}{\B, \futs xx, \accs xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}{\vlhtr{\DD_1^\rn{m}}{\B, \rels xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}}}}$$

		\item Rule $\rlabrn\DIA$:

		$$\vlderibase{\rlabrn\DIA}{}{\B, \rels xy, \Left \SEQ \labels{x}{\DIA A}}{\vlhtr{\DD_1}{\B, \rels xy, \Left \SEQ \labels{y}{A}}}
		\reducesto
		\vlderibase{\equiv}{}{\B, \rels xy, \Left \SEQ \labels{x}{\DIA A}}{\vlin{\rlabrn\DIA}{}{\B, \futs xx, \accs xy, \Left \SEQ \labels{x}{\DIA A}}{\vlin{\equiv}{}{\B, \futs xx, \accs xy, \Left \SEQ \labels{x}{\DIA A}, \labels{y}{A}}{\vlhtr{\DD_1^\rn{mw}}{\B, \rels xy, \Left\SEQ \labels{x}{\DIA A}, \labels{y}{A}}}}}
		$$

		\item Rule $\llabrn\IMP$:

		$$\vlderiibase{\llabrn\IMP}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}}{
			\vlhtr{\DD_1}{\B, \Left \SEQ \labels{x}{A}}
		}{
		\vlhtr{\DD_2}{\B, \Left, \labels{x}{B} \SEQ \labels{z}{C}}
		}$$
		\begin{center} $\downarrow$\end{center}
		$$
		\vlderibase{\rn{refl}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}}{
		\vliin{\llabrn\IMP}{}{\B, x \le x, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}}{
			\vlhtr{\DD_1^\rn{mw}}{\B, x \le x, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}, \labels{x}{A}}
		}{
		\vlhtr{\DD_2^\rn{mw}}{\B, x \le x, \Left, \labels{x}{B} \SEQ \labels{z}{C}}
		}
		}$$

		%\item Rule $\rlabrn\IMP$:

	\end{itemize}
\end{proof}				
%	
%		\\

%		%	\end{smallequation*}
%		\\
%		%	\begin{smallequation*}
%		$$\vlderibase{\rlabrn\IMP}{}{\B, \Left \SEQ \labels{x}{A \IMP B}}{
%			\vlhtr{\DD_1}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}
%		}$$
%		\reducesto&$$
%		\vlderibase{\rlabrn\IMP}{}{\B, \Left \SEQ \labels{x}{A \IMP B}}{
%			\vlhtr{\DD_1^\rn{mw}}{\B, x \le x, \Left, \labels{x}{A} \SEQ \labels{x}{B}}
%		}$$
%		%	\end{smallequation*}
%		\\
%

\end{document}

### 2020-05-10 bicolor NS/abstract/wil20.tex
starting with draft for wil submission

% easychair.tex,v 3.5 2017/03/15

\documentclass{easychair}
%\documentclass[EPiC]{easychair}
%\documentclass[EPiCempty]{easychair}
%\documentclass[debug]{easychair}
%\documentclass[verbose]{easychair}
%\documentclass[notimes]{easychair}
%\documentclass[withtimes]{easychair}
%\documentclass[a4paper]{easychair}
%\documentclass[letterpaper]{easychair}

\usepackage{doc}

% use this if you have a long article and want to create an index
% \usepackage{makeidx}

% In order to save space or manage large tables or figures in a
% landcape-like text, you can use the rotating and pdflscape
% packages. Uncomment the desired from the below.
%
% \usepackage{rotating}
% \usepackage{pdflscape}

% Some of our commands for this guide.
%
\newcommand{\easychair}{\textsf{easychair}}
\newcommand{\miktex}{MiK{\TeX}}
\newcommand{\texniccenter}{{\TeX}nicCenter}
\newcommand{\makefile}{\texttt{Makefile}}
\newcommand{\latexeditor}{LEd}

%\makeindex

%% Front Matter
%%
% Regular title as in the article class.
%
\title{A bicolor nested sequents for intuitionistic modal logics}

% Authors are joined by \and. Their affiliations are given by \inst, which indexes
% into the list defined using \institute
%
\author{
	Sonia Marin\inst{1}%\thanks{Designed and implemented the class style}
\and
    Marianela Morales\inst{2}%\thanks{Did numerous tests and provided a lot of suggestions}
}

% Institutes for affiliations are also joined by \and,
\institute{
	University College London  \\
  \email{s.marin@ucl.ac.uk}
  \and
  LIX, \'Ecole Polytechnique  \&  Inria Saclay\\
	\email{marianela.morales@polytechnique.edu}
 }

%  \authorrunning{} has to be set for the shorter version of the authors' names;
% otherwise a warning will be rendered in the running heads. When processed by
% EasyChair, this command is mandatory: a document without \authorrunning
% will be rejected by EasyChair

\authorrunning{Marin ad Morales}

% \titlerunning{} has to be set to either the main title or its shorter
% version for the running heads. When processed by
% EasyChair, this command is mandatory: a document without \titlerunning
% will be rejected by EasyChair
\titlerunning{bicolor NS}

\begin{document}

\maketitle

\begin{abstract}
	We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
\end{abstract}

\section{Introduction}

\bibliographystyle{plain}
%\bibliographystyle{alpha}
%\bibliographystyle{unsrt}
%\bibliographystyle{abbrv}
\bibliography{references}

\end{document}

### 2020-05-11 bicolor NS/abstract/wil20.tex
new version of the draft

@@
 \usepackage{doc}
-
+\input{macros}
 % use this if you have a long article and want to create an index
@@
 
-\authorrunning{Marin ad Morales}
+\authorrunning{Marin and Morales}
 
@@
 We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
+%
+
+\emph{Keywords:} Nested sequents, Intuitionistic modal logic, Proof theory. 
 \end{abstract}
@@
 \section{Introduction}
+\todo{Say: working on multi-conclusion nested sequents for intuitionistic modal logic. A bit of story? Why is useful?}
+
+Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and sequent systems \cite{simpson1994proof},
+or the one of \emph{unlabelled deduction} in the form of sequent~\cite{bierman2000} or nested sequent systems \cite{strassburger2013cut}.
+Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
+
+\section{Preliminaries}
+
+Nested sequents are a generalisation of sequents from a multiset
+of formulas to a tree of multisets of formulas.
+In nested sequent notation, brackets are used to indicate the parent-child relation in the tree, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$).
+for intuitionistic logic we need two-sided sequents, which are formally generated by:
+\begin{center}
+	$\Cx \coloncolonequals \lf{A_{1}}, ..., \lf{A_{n}}, \rt{B_{1}},..., \rt{B_{k}}, \BR{\Cx[1]},..., \BR{\Cx[m]}$
+\end{center}
+
+where $A_{1}, .
+.
+.
+, A_{n}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $B_{1}, .
+.
+.
+, B_{k}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], .
+.
+.
+, \Cx[m]$ are nested sequents.
+We use the $\bullet$ and $\circ$ as polarities indication for formulas.
+
+In this short article, we present a nested sequent system for intuiniotistic modal logic.
+Intuitionistic modal logics are intuitionistic propositional logic extended with the modalities $\BOX$ and $\DIA$, and the necessitation rule, obeying some variants of the $\kax$-axiom since De Morgan duality between the modalities is not present in the intuitionistic case:
+
+\begin{equation*}
+\label{eq:ik}%\hskip-2em
+\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
+\kax[1]\colon&\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)
+&
+\kax[3]\colon&\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)
+&
+\kax[5]\colon&\DIA\BOT\IMP\BOT
+\\
+\kax[2]\colon&\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)
+&
+\kax[4]\colon&(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)\\%x[1ex]
+\end{array}
+\end{equation*}
+%%
+\section{Bicolor nested sequent system}
+
+In order to capture intuitionistic modal logics, we build a nested sequent system with the two relations explicitly: one of for the accessibility relation $\rel$ associated with the Kripke semantics for normal modal logics (represented with one bracket in the sequent) and one for the preorder relation $\le$ associated with the Kripje semantics for intuitionistic logic (represented with two brackets in the system).
+
+In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
+$\force{x}{\BOX A}$ iff for all $y$ and $z$ s.t. $\futs xy$ and $\accs yz$, $\force{z}{A}$. Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
+
+\begin{center}
+	$\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
+	\quad
+	\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}$
+\end{center}
 

### 2020-05-11 bicolor NS/abstract/wil20.tex
adding definition

@@
 %%
+We recall the birelational models [21, 7] for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
+A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:
+
+\begin{enumerate}
+	\item[($\rn{F_1}$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
+
+	\item[($\rn{F_2}$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
+\end{enumerate}
+
 \section{Bicolor nested sequent system}
@@
 
+\marianela{add F1 rule?}
+
 \bibliographystyle{plain}

### 2020-05-28 bicolor NS/aiml20/aiml20.tex
aiml20: structure + sec 2

--- 2020-03-10 aiml20/simpson.tex
@@
-\documentclass[twoside]{aiml18}
-\usepackage{aiml18macro}
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
-%
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-	<-6>  MnSymbolC5
-	<6-7>  MnSymbolC6
-	<7-8>  MnSymbolC7
-	<8-9>  MnSymbolC8
-	<9-10> MnSymbolC9
-	<10-12> MnSymbolC10
-	<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-	<-6>  MnSymbolC-Bold5
-	<6-7>  MnSymbolC-Bold6
-	<7-8>  MnSymbolC-Bold7
-	<8-9>  MnSymbolC-Bold8
-	<9-10> MnSymbolC-Bold9
-	<10-12> MnSymbolC-Bold10
-	<12->   MnSymbolC-Bold12}{}
-%
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
+\documentclass[twoside]{aiml20}
 
-\input{new-macros}
+% Please include these macros
+\usepackage{aiml20macro}
+\usepackage{virginialake}
+\input{macros}
+
+% Here you can include the standard packages you use.
+% Try to avoid using non-standard packages.
+% If you use a non-standard package you will have
+% to submit it when you submit the final version of
+% your paper.
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Setting the correct page numbers                      
+% Ignore the next two commented lines                   
+% but please don't delete                               
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\input{../procnum.tex}
+%\numbering{../aiml20db}{paper}
+
+% definitions specific to your article
+\newcommand{\ob}{[}
+\newcommand{\cb}{]}
 
@@
 % Separate by commas except the last two surnames which are separated by an "and".
-\def\lastname{Marin, Morales and Stra{\ss}burger}
+\def\lastname{Marin and Morales}
 
@@
 \begin{frontmatter}
-  \title{Comparing system $\labIKp$ and Simpson system}
- % \author{Sonia Marin}
-  %\address{IT-Universitetet i K{\o}benhavn \\ Denmark }
- %\author{Marianela Morales}
- %\address{Universidad Nacional de C\'ordoba \\ Argentina}
-  % \author{Lutz Stra{\ss}burger}
- %\address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
+  \title{This is the title of the paper}
+  \author{Sonia Marin}
+  %\footnote{You can put your email address or grant acknowledgement as a footnote, if you wish.}
+  \address{University College London}
+  \author{Marianela Morales}
+  \address{LIX, \'Ecole Polytechnique  \&  Inria Saclay}
 
   \begin{abstract}
-   %We present a labelled sequent system for intuitionistic modal logic equipped with two relation symbols, one for the accessibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics   for intuitionistic logic.
+  We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
   %
-   %Thus, it is in close correspondence with birelational Kripke semantics for intuitionistic modal logic and can encompass a wider range of intuitionistic logics than state-of-the-art labelled systems.
-
-   %% . We show the possibility of extend labelled sequents
-   %% with a preorder relation symbol in order to capture intuitionistic
-   %% modal logic. For this, we obtain a proof system which is complete
-   %% with respect to Hilbert system.  Also, we present the proof for
-   %% completeness using Simpson system.
   \end{abstract}
@@
   \begin{keyword}
-  Intuitionistic modal logic, Labelled sequents, Proof theory, Simpson system.
+  Nested sequents, Intuitionistic modal logic, Proof theory.
   \end{keyword}
@@
 
+%
+%\section{Instructions for authors}
+%Important information pertaining to the preparation of your paper:
+%\begin{itemize}
+%  \item Please prepare your paper by editing this file (\verb|aiml20.tex|) as well as the bibliography file, \verb|aiml20.bib|.
+%  \item Please do not use includegraphics on any PDF files not having all fonts embedded. If in doubt, please convert to JPG before including.
+%  \item It is strictly prohibited to tamper with the text dimensions, including adding to the text height or width.
+The dimensions of the style files are already taken to the limit of what the printer of the final proceedings is able to handle.
+Also, please refrain from using any kind of negative white space.
+%  \item Please make sure too split lines that are too wide in the final output (avoid overfull \verb|\hbox|es).
+%\end{itemize}
+
 \section{Introduction}
+\todo{Say: working on multi-conclusion nested sequents for intuitionistic modal logic. A bit of story? Why is useful?}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\marianela{Introduce the idea of having cut-elimination for multi-conclusion systems}
+Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and sequent systems \cite{simpson1994proof},
+or the one of \emph{unlabelled deduction} in the form of sequent~\cite{bierman2000} or nested sequent systems \cite{strassburger2013cut}.
+Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
 
 \section{Intuitionistic modal logics}
-
-%%Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$  and relational atoms of the form $x$R$y$, where $x$, $y$ range over a set of variables and $A$ is a modal formula.
-A one-sided labelled sequent is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational atoms and $\Right$ a multiset of labelled formulas.
-A simple proof system for classical modal logic K can be obtained in this formalism (\textbf{Fig.
-1}).
-%%
-%%\begin{figure}[h]
-%%\begin{center}
-%%
-%%$\vlderivation {\vlinf{\id}{}{\B \SEQ \Right, x: a, x: \vls-a}{}}$
-%%\hspace{7mm}$\vlderivation {\vlinf{\tolab}{}{\toprule}{}}$
-%%
-%%
-%%$\vliinf{\vlab}{}{\B \SEQ \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
-%%\hspace{7mm}$\vlinf{\olab}{}{\B \SEQ \Right, x \colon \vls[A.B]}{\olabr}$
-%%
-%%
-%%$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
-%%\hspace{7mm}$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
-%%
-%%
-%%\end{center}
-%%\caption{System labK}
-%%\end{figure}
-%%These rule schemes can occur in different contexts and different calculi. The context that interests us is when it is applied to modal logic.
-%%\\
-%%
-%%The idea to extend this system to another to capture intuitionistic modal logics allows us to study the Kripke semantics for this type of logics:
-
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$.
-%, standing most generally for \emph{necessity} and \emph{possibility}.
+The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
 %
@@
 %
-%We might sometimes write $\NOT A$ to mean $A \IMP \BOT$.
-
-%Obtaining the intuitionistic variant of K is more involved than the classical variant. 
-%%
-%Lacking De Morgan duality, there are several variants of k that are classically but not intuitionistically
-%equivalent. 
-%%
-%Five axioms have been considered as primitives in the literature. 
-%
-
-The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
+The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{plotkin1986} and is equivalent to the one proposed by Fischer-Servi~\cite{fischer1984}.
 %, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
@@
 
-The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{Fischer}.
+The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer1984}.
 %
@@
 
-$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ \hfill $(\ast)$
+$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ %\hfill $(\ast)$
 
@@
 
-%It then was investigated in detail in~\cite{Simpson}, in which strong arguments are given in favour of this axiomatic definition: 
-%
-%it allows for adapting to intuitionistic logic the standard embedding of modal logic into first-order logic, and also provides an extension of the standard Kripke semantics for classical modal logic to the intuitionistic case.
-
 Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
@@
 \end{theorem}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Intuitionistic labelled sequent}
+\section{Bicolor NS: nested sequents capturing $\rel$ and $\le$}
+\marianela{small introduction of nested sequents}
 
-\todo{finish writing Simpson system}
-\begin{figure}%[h]
-	\centering
-	\small
-	\fbox{
-		\begin{tabular}{@{\!}c@{\quad}c}
-			$\vlinf{\rn{id_{s}}}{}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{A} }{}$
-			&
-			$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \labels{z}{A}}{}$
+\marianela{put the whole system}
 
-			\\\\
+\marianela{explain some specific rules: $\rrn\BOX$, $\rrn\IMP$. maybe $\rn F_1$?}
 
-			$\vlderivation {\vlin {\llabrn\AND}{}{\B, \Left, \labels{x}{A \AND B} \SEQ \labels{z}{C}}{\vlhy {\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \labels{z}{C}}}}$
-			&
-			$\vlderivation { \vliin {\rlabrn\AND}{}{\B, \Left, \SEQ \labels{x}{A \AND B}}{\vlhy {\B, \Left \SEQ \labels{x}{A} }}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-			\\\\
+\section{Conclusion}
+\marianela{say something like the idea comes from proving termination for is4...}
 
-%		\vspace{3mm}
-%		
-%		
-%		$\vlderivation {\vliin {\solef}{}{\B, \Left, x \colon \vls[A.B] \SEQ z \colon C}{\vlhy {\B, \Left, \labels{x}{A} \SEQ z \colon C}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation { \vlin{\sorone}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sotwo}{}{\B, \Left \SEQ x \colon \vls[A.B]}{\vlhy {\B, \Left \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation {\vliin{\sil}{}{\B, \Left, \labels{x}{A} \vljm B \SEQ z \colon C}{\vlhy {\B, \Left \SEQ \labels{x}{A}}}{\vlhy {\B, \Left, \labels{x}{B} \SEQ z \colon C}}}$
-%		\hspace{7mm}$\vlderivation {\vlin{\sir}{}{\B,  \Left, \labels{x}{A} \SEQ \labels{x}{B}}{\vlhy {\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin {\sbl}{}{\B, x \rel y, \Left, x \colon \BOX A \SEQ z\colon B}{\vlhy {\B, x \rel y, \Left, x \colon \BOX A, y \colon A \SEQ z\colon B}}}$
-%		\hspace{7mm}$\vlderivation { \vlin {\sbr}{y$ is fresh$}{\B, \Left \SEQ x \colon \BOX A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A}}}$
-%		
-%		\vspace{3mm}
-%		
-%		$\vlderivation { \vlin{\sdl}{y$ is fresh$}{\B, \Left, x \colon \DIA A \SEQ z \colon B}{\vlhy {\B, x \rel y, \Left, y \colon A \SEQ z \colon B}}}$
-%		\hspace{7mm}$\vlderivation {\vlin {\sdr}{}{\B,x \rel y, \Left \SEQ x \colon \DIA A}{\vlhy {\B, x \rel y, \Left \SEQ y \colon A }}}$
-%
+%% Appendix.
+%% Remove the \Appendix command if an 
+%% appendix is not required.
+\Appendix
+Here starts the appendix. If you don't wish an appendix, please remove the \verb|\Appendix| command from the \LaTeX\ file.
 
-		\end{tabular}		
-	}		
-	\caption{System $\lab\IK$}
-	\label{fig:labIK}
-\end{figure}
-
-\begin{figure}[!t]
-	\begin{center}
-		\fbox{
-			%	\begin{minipage}{.95\textwidth}
-			\begin{tabular}{c@{\quad}c}
-				$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
-				&
-				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-				%\quad
-				%$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-				\\\\
-				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-				&
-				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-				\\\\
-				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-				&
-				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-				\\\\
-				\multicolumn{2}{c}{
-					$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$
-					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
-				}
-				\\\\
-				$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-				&
-				$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-				\\\\
-				$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-				&
-				$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-				\\
-				\multicolumn{2}{c}{
-					$\mbox{\hbox to .9\linewidth{\dotfill}}$
-				}
-				\\
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-				\\\\
-				\multicolumn{2}{c}{
-					$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-			%\end{minipage}
-		}		
-	\end{center}
-	\caption{System $\labIKp$}
-	\label{fig:labIKp}
-\end{figure}
-
-%\begin{figure}%[h]
-%	\centering
-%	\small
-%	\fbox{
-%		\begin{minipage}{.95\textwidth}
-%			\begin{tabular}{@{\!}c@{\quad}c}
-%				$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
-%				&
-%				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-%				\quad
-%				$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-%				\\\\
-%				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-%				&
-%				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-%				\\\\
-%				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-%				&
-%				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-%				\\\\
-%				\multicolumn{2}{c}{
-%					$\vlinf{\llabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, x \le y, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-%				}
-%				\\\\
-%				\multicolumn{2}{c}{
-%					$\vliinf{\rlabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
-%					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
-%				}
-%				\\\\
-%				$\vlinf{\llabrn\BOX}{}{\B, \Left, x \le y, yRz, \labels{x}{\BOX A} \SEQ \Right}{\B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-%				&
-%				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \Left, x \le y, y \rel z \SEQ \Right, \labels{z}{A}}$
-%				\\\\
-%				$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \Left, x \rel y, \labels{y}{A} \SEQ \Right}$
-%				&
-%				$\vlinf{\rlabrn\DIA}{}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-%				\\
-%				\multicolumn{2}{c}{
-%					$\mbox{\hbox to .9\linewidth{\dotfill}}$
-%				}
-%				\\
-%				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
-%				&
-%				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
-%				\\\\
-%				\multicolumn{2}{c}{
-%					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
-%				}
-%				\\\\
-%				\multicolumn{2}{c}{
-%					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
-%				}
-%			\end{tabular}		
-%		\end{minipage}
-%	}		
-%	\caption{System $\labIKp$}
-%	\label{fig:labIKp}
-%\end{figure}
-
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{Simpson}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{Strassburger} (for a survey see~\cite[Chap.~3]{Marin}).
-
-Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-Simpson's system is displayed on Figure~\ref{fig:}
-
-Echoing the definition of bi-relational structures, in  ~\cite{MarinMoralesStrassburger} another extension of labelled deduction to the intuitionistic setting is presented.
-This extension allows us to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}.
-%
-
-\begin{definition}
-	A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $\accs{x}{y}$ and preorder atoms $\futs{x}{y}$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
-\end{definition}
-
-The proof system for intuitionistic modal logic in this formalism obtained is $\labIKp$, displayed on Figure~\ref{fig:labIKp}.
-
-\section{Multi-conclusion vs Single-conclusion??}
-
-\section{Differences between Simpson system and system $\labIKp$}
-
-Most rules in the system $\labIKp$ are similar to the ones of Simpson~\cite{Simpson}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
-%
-In particular, the rules introducing the $\BOX$-operator correspond to the definition $(\ast)$.
-%
-Furthermore, the system $\labIKp$ has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
-
-\section{title}
-%We present a completeness proof for the system $\labIKp$ using Simpson system.
-Knowing that Simpson system is a \emph{cut-free} system, the proof lets us know that the system $\labIKp$ is complete without the cut rule.
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-We show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-\begin{theorem}[Simpson~\cite{Simpson}]
-	\label{thm:simpson-sound-compl}
-	A formula $A$ is provable in the calculus $\lab\IK$ if and only if $A$ is valid in every bi-relational frame.
-\end{theorem}
-
-\begin{definition}
-
-\end{definition}
-
-\begin{theorem}
-	If there is a proof $\vlderivation{\vlhtr{\DD}{\B, \Left \SEQ \labels{z}{C}}}$ in $\lab\IK$ then there is a proof $\vlderivation{\vlhtr{\DD^\rn{m}}{\B, \Left \SEQ \labels{z}{C}}}$ in $\labIKp$.
-\end{theorem}
-
-\begin{proof}
-
-	In order to develop this proof, we transform the relation $\rel$ presented in Simpson system to $S$ in order to incorporate the following definition:
-
-	$\rels xy \equiv \futs xz, \accs zy$ where $\lb z$ can be $\lb z = \lb x$ or a new fresh variable.
-
-	We are proving the theorem by case analysis on the last rule in $\DD$. 
-%
-	Most of the rules in $\lab\IK$ are the same as rules in $\labIKp$ except for the following:
-
-	\begin{itemize}
-		\item Rule $\rn{id}$:
-
-		$$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}
-		\reducesto
-		\vlderibase{\rn{refl}}{}{\B, \Left, \labels{x}{a} \SEQ \labels{x}{a}}{
-			\vlin{\labrn{id}}{}{\B, \futs xx, \Left, \labels{x}{a} \SEQ \labels{x}{a}}{
-				\vlhy{}
-			}
-		}$$
-
-		\item Rules $\rlabrn[1]\OR$ and $\rlabrn[2]\OR$ :
-		$$	\vlderibase{\rlabrn[1]\OR}{}{\B, \Left \SEQ \labels{x}{A \OR B}}{
-			\vlhtr{\DD_1}{\B, \Left \SEQ \labels{x}{A}}
-		}
-		\quad\text{or}\quad
-		\vlderibase{\rlabrn[2]\OR}{}{\B, \Left \SEQ \labels{x}{A \OR B}}{
-			\vlhtr{\DD_1}{\B, \Left \SEQ \labels{x}{B}}
-		}
-		\reducesto
-		\vlderibase{\rlabrn\OR}{}{\B, \Left \SEQ \labels{x}{A \OR B}}{
-			\vlhtr{\DD_1^\rn{mw}}{\B, \Left \SEQ \labels{x}{A}, \labels{x}{B}}
-		}$$
-
-		\item Rule $\llabrn\BOX$:
-
-		$$\vlderibase{\llabrn\BOX}{}{\B, \rels xy, \Left, \labels{x}{\BOX A} \SEQ \labels{z}{B}}{
-		\vlhtr{\DD_1}{\B, \rels xy, \Left, \labels{x}{\BOX A}, \labels{y}{A} \SEQ \labels{z}{B}}
-		}\reducesto
-		\vlderibase{\equiv}{}{\B, \rels xy, \Left, \labels{x}{\BOX A} \SEQ \labels{z}{B}}{
-		\vlin{\llabrn\BOX}{}{\B, \futs xz, \accs zy, \Left, \labels{x}{\BOX A} \SEQ \labels{z}{B}}{ \vlin{\equiv}{}{\B, \futs xz, \accs zy, \Left, \labels{x}{\BOX A}, \labels{y}{A} \SEQ \labels{z}{B}}{\vlhtr{\DD_1^\rn{mw}}{\B, \rels xy, \Left, \labels{x}{\BOX A}, \labels{y}{A} \SEQ \labels{z}{B}}}
-		}
-		}$$
-
-		\item Rule $\rlabrn\BOX$:
-
-		$$\vlderibase{\rlabrn\BOX}{}{\B, \Left \SEQ \labels{x}{\BOX A}}{
-			\vlhtr{\DD_1}{\B, \rels xy, \Left \SEQ \labels{y}{A}}
-		}
-		\reducesto
-		\vlderibase{\rlabrn\BOX}{\lb z, \lb y \mbox{ fresh}}{\B, \Left \SEQ \labels{x}{\BOX A}}{ \vlin{\equiv}{}{\B, \futs xz, \accs zy, \Left \SEQ \labels{y}{A}}{	\vlhtr{\DD_1^\rn{m}}{\B, \rels xy, \Left \SEQ \labels{y}{A}}}
-		}$$
-
-		\item Rule $\llabrn\DIA$:
-
-		$$\vlderibase{\llabrn\DIA}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \labels{z}{B}}{\vlhtr{\DD_1}{\B, \rels xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}}
-		\reducesto
-		\vlderibase{\llabrn\DIA}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \labels{z}{B}}{\vlin{\rn{refl}}{}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}{\vlin{\equiv}{}{\B, \futs xx, \accs xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}{\vlhtr{\DD_1^\rn{m}}{\B, \rels xy, \Left, \labels{y}{A} \SEQ \labels{z}{B}}}}}$$
-
-		\item Rule $\rlabrn\DIA$:
-
-		$$\vlderibase{\rlabrn\DIA}{}{\B, \rels xy, \Left \SEQ \labels{x}{\DIA A}}{\vlhtr{\DD_1}{\B, \rels xy, \Left \SEQ \labels{y}{A}}}
-		\reducesto
-		\vlderibase{\equiv}{}{\B, \rels xy, \Left \SEQ \labels{x}{\DIA A}}{\vlin{\rlabrn\DIA}{}{\B, \futs xx, \accs xy, \Left \SEQ \labels{x}{\DIA A}}{\vlin{\equiv}{}{\B, \futs xx, \accs xy, \Left \SEQ \labels{x}{\DIA A}, \labels{y}{A}}{\vlhtr{\DD_1^\rn{mw}}{\B, \rels xy, \Left\SEQ \labels{x}{\DIA A}, \labels{y}{A}}}}}
-		$$
-
-		\item Rule $\llabrn\IMP$:
-
-		$$\vlderiibase{\llabrn\IMP}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}}{
-			\vlhtr{\DD_1}{\B, \Left \SEQ \labels{x}{A}}
-		}{
-		\vlhtr{\DD_2}{\B, \Left, \labels{x}{B} \SEQ \labels{z}{C}}
-		}$$
-		\begin{center} $\downarrow$\end{center}
-		$$
-		\vlderibase{\rn{refl}}{}{\B, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}}{
-		\vliin{\llabrn\IMP}{}{\B, x \le x, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}}{
-			\vlhtr{\DD_1^\rn{mw}}{\B, x \le x, \Left, \labels{x}{A \IMP B} \SEQ \labels{z}{C}, \labels{x}{A}}
-		}{
-		\vlhtr{\DD_2^\rn{mw}}{\B, x \le x, \Left, \labels{x}{B} \SEQ \labels{z}{C}}
-		}
-		}$$
-
-		%\item Rule $\rlabrn\IMP$:
-
-	\end{itemize}
-\end{proof}				
-%	
-%		\\
-
-%		%	\end{smallequation*}
-%		\\
-%		%	\begin{smallequation*}
-%		$$\vlderibase{\rlabrn\IMP}{}{\B, \Left \SEQ \labels{x}{A \IMP B}}{
-%			\vlhtr{\DD_1}{\B, \Left, \labels{x}{A} \SEQ \labels{x}{B}}
-%		}$$
-%		\reducesto&$$
-%		\vlderibase{\rlabrn\IMP}{}{\B, \Left \SEQ \labels{x}{A \IMP B}}{
-%			\vlhtr{\DD_1^\rn{mw}}{\B, x \le x, \Left, \labels{x}{A} \SEQ \labels{x}{B}}
-%		}$$
-%		%	\end{smallequation*}
-%		\\
-%
+%% Bibliography
+%% Make sure to use the bibliographystyle aiml20.
+\bibliographystyle{aiml20}
+\bibliography{aiml20}
 

### 2020-06-01 bicolor NS/aiml20/aiml20.tex
adding system -- does not compile
adding system -- compile ok now
beginning of the aiml abstract

@@
 \usepackage{aiml20macro}
-\usepackage{virginialake}
-\input{macros}
 
@@
 \usepackage{amssymb}
+
+\usepackage{colonequals}
+
+%\usepackage[matrix,arrow]{xy}
+\usepackage[noxy]{virginialake}
+%\vlnosmallleftlabels
+\vlnostructuressyntax
 
@@
 
+\input{macros}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{frontmatter}
-  \title{This is the title of the paper}
+  \title{Fully structured proof theory \\for intuitionistic modal logics \\(working title)}
   \author{Sonia Marin}
   %\footnote{You can put your email address or grant acknowledgement as a footnote, if you wish.}
-  \address{University College London}
+  \address{University College London, UK}
   \author{Marianela Morales}
-  \address{LIX, \'Ecole Polytechnique  \&  Inria Saclay}
+  \address{LIX, \'Ecole Polytechnique  \&  Inria Saclay, France}
 
@@
 Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and sequent systems \cite{simpson1994proof},
-or the one of \emph{unlabelled deduction} in the form of sequent~\cite{bierman2000} or nested sequent systems \cite{strassburger2013cut}.
-Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
+or the one of \emph{unlabelled deduction} in the form of nested sequent systems \cite{strassburger2013cut,}.
 
@@
 
+\marianela{We recall the birelational models \cite{plotkin1986, ewald1986} for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
+A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:
+}
+
 \begin{definition}
@@
 
+\section{Labelled sequent calculi with $\rel$ and $\le$}
+
+\begin{figure}%[h]
+	\centering
+	\small
+	\fbox{
+		\begin{minipage}{.95\textwidth}
+			\begin{tabular}{@{\!}c@{\quad}c}
+				$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
+				&
+				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
+%				\quad
+%				$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
+				\\\\
+				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
+				&
+				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
+				\\\\
+				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
+				&
+				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
+				\\\\
+				\multicolumn{2}{c}{
+					$\vlinf{\llabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, x \le y, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+				}
+				\\\\
+				\multicolumn{2}{c}{
+					$\vliinf{\rlabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
+				}
+				\\\\
+				$\vlinf{\llabrn\BOX}{}{\B, \Left, x \le y, yRz, \labels{x}{\BOX A} \SEQ \Right}{\B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+				&
+				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \Left, x \le y, y \rel z \SEQ \Right, \labels{z}{A}}$
+				\\\\
+				$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \Left, x \rel y, \labels{y}{A} \SEQ \Right}$
+				&
+				$\vlinf{\rlabrn\DIA}{}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
+				\\
+				\multicolumn{2}{c}{
+					$\mbox{\hbox to .9\linewidth{\dotfill}}$
+				}
+				\\
+				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
+				&
+				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
+				\\\\
+				\multicolumn{2}{c}{
+					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
+				}
+				\\\\
+				\multicolumn{2}{c}{
+					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
+				}
+			\end{tabular}		
+		\end{minipage}
+	}		
+	\caption{System $\labIKp$}
+	\label{fig:labIKp}
+\end{figure}
+
+%Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
+%%
+%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
+
+Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{Simpson}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{Strassburger} (for a survey see~\cite[Chap.~3]{Marin}).
+
+Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
+%
+Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
+%
+The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}.
+%
+
+\begin{definition}
+	A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
+\end{definition}
+
+%Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$ and relational or equality atoms of the form $x \rel y$ or $x = y $ respectively, where $x$,$y$ range over  a set of variables (called labels) and $A$ is a modal formula.
+A (onde-sided) \emph{labelled sequent} is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational or equality atoms, and $\Right$ a multiset of labelled formulas.
+
+%
+We obtain a proof system $\labIKp$, displayed on Figure~\ref{fig:labIKp}, for intuitionistic modal logic in this formalism. 
+%
+Most rules are similar to the ones of Simpson~\cite{Simpson}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
+%
+In particular, the rules introducing the $\BOX$-operator correspond to the definition $(\ast)$.
+%
+Furthermore, our system has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
+%
+%As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
+
+%\begin{theorem}
+%	\label{thm:sound-compl}
+%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
+%\end{theorem}
+%
+%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
+%
+%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
+
+%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
+
+\begin{theorem}\label{thm:cutfree-compl}
+	%	Let $\CC$ be a set of geometric frame properties as in~\eqref{eq:cla-geometric} and $\labbrn{\CC}$ be the corresponding set of rules following schema~\eqref{eq:modal-grs}.
+	%
+	For any formula $A$, the following are equivalent.
+	%
+	\begin{enumerate}
+		\item\label{i} $A$ is a theorem of $\IK$ 
+		%
+		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
+		%		
+		%		\todo{}
+		\smash{%\fbox{
+			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
+		}%}
+		%
+		\item\label{iii} $A$ is provable in $\labIKp$
+		%
+		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
+	\end{enumerate}
+\end{theorem}
+
+%We show that each rule from our system is sound.
+%
+%We also present a syntactic completeness proof with respect the Hilbert system: we prove all Hilbert axioms using the rules from our system (i.e.
+proof of all propositional intuitionistic axioms, the five variants of k axiom from the intuitionistic syntax, simulate the necessitation rule and simulate modus ponens).
+%
+%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
+%
+%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
+%
+%We show the proof by case analysis. 
+%
+%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
+
+The proof is a careful adaptation of standard techniques.
+%
+In particular, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms. 
+%
+As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.
+
+\vspace*{-.9cm}
+$$
+\hspace*{-.5cm}
+\scalebox{.9}{
+	$
+	\vlderivation{
+		\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
+			\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
+				\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
+					\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+						\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+							\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+								\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
+									\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
+										\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
+											\vlhy {}
+										}
+									}
+								}
+							}{
+								%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
+								%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
+								%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
+								%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
+								\vlhy {\qquad\vdots\qquad}
+								%										}
+								%									}
+								%								}
+								%							}
+							}
+						}
+					}
+				}
+			}
+		}
+	}$
+}$$
+%\end{example}
+
+%\vspace*{-.5cm}
+
+Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
+%
+We therefore have to show that such a rule is admissible in our system.
+%
+As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).
+
+\vspace*{-.5cm}
+%\begin{example}
+$$
+\scalebox{.9}{
+	$
+	\vlderivation{
+		\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+			\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+				\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+					\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
+						\vlhy{}
+					}
+				}
+			}
+		}
+	}
+	$
+}
+$$
+%\end{example}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Extensions}
+
+In~\cite{Simpson}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
+%
+For example, you can add the following rule:
+$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, w \rel u, \Left \SEQ \Right}$}$$
+to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
+$\ax{4}\colon (\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)$, that is, wrt.~to all frames in which $\rel$ is transitive.
+
+In~\cite{Plotkin}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
+%
+For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \DIA\DIA A \IMP \DIA A$ are exactly the ones satisfying the condition:
+%\begin{center}
+($\diabrn{4}$) if $w \rel v$ and $v \rel u$, there exists a $u'\in W$ s.t.~$u \le u'$ and $wRu'$.
+%\end{center}
+
+Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
+$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, u \le u', w \rel u' , \Left \SEQ \Right}$}$$
+
+Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
+%
+These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
+
 \section{Bicolor NS: nested sequents capturing $\rel$ and $\le$}
 \marianela{small introduction of nested sequents}
+Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
+%
+Nested sequents are a generalisation of sequents from a multiset
+of formulas to a tree of multisets of formulas.
+In nested sequent notation, brackets are used to indicate the parent-child relation in the tree, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$).
+for intuitionistic logic we need two-sided sequents, which are formally generated by:
+\begin{center}
+	$\Cx \coloncolonequals \lf{A_{1}}, ..., \lf{A_{n}}, \rt{B_{1}},..., \rt{B_{k}}, \BR{\Cx[1]},..., \BR{\Cx[m]}$
+\end{center}
 
-\marianela{put the whole system}
+where $A_{1}, .
+.
+.
+, A_{n}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $B_{1}, .
+.
+.
+, B_{k}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], .
+.
+.
+, \Cx[m]$ are nested sequents.
+We use the $\bullet$ and $\circ$ as polarities indication for formulas.
+
+In order to capture intuitionistic modal logics, we build a nested sequent system with the two relations explicitly: one of for the accessibility relation $\rel$ associated with the Kripke semantics for normal modal logics (represented with one bracket in the sequent) and one for the preorder relation $\le$ associated with the Kripje semantics for intuitionistic logic (represented with two brackets in the system).
+
+In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
+$\force{x}{\BOX A}$ iff for all $y$ and $z$ s.t. $\futs xy$ and $\accs yz$, $\force{z}{A}$. Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
+
+\begin{center}
+	$\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
+	\quad
+	\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}$
+\end{center}
+
+\marianela{add F1 rule?}
+
+\begin{figure}%[h]
+	\centering
+	\small
+	\fbox{
+\begin{minipage}{.95\textwidth}
+\[
+%\vlinf{\rn{id}}{}{\Cx[1]{\lf A, \bBR{\rt A, \Cx[2]}}}{}
+\vlinf{\rn{id}}{}{\Cx{\lf A, \rt A}}{}
+\quad
+\vlinf{\lrn{\BOT}}{}{\Cx{\lf \BOT}}{}
+\]
+\[
+\vlinf{\lrn\AND}{}{\Cx{\lf{A \AND B}}}{\Cx{\lf A, \lf B}}
+\quad
+\vliinf{\rrn\AND}{}{\Cx{\rt{A \AND B}}}{\Cx{\rt A}}{\Cx{\rt B}}
+\quad
+\vliinf{\lrn\OR}{}{\Cx{\lf{A \OR B}}}{\Cx{\lf A}}{\Cx{\lf B}}
+\quad
+\vlinf{\rrn\OR}{}{\Cx{\rt{A \OR B}}}{\Cx{\rt A, \rt B}}
+\]
+\[
+%\vliinf{\lrn\IMP}{}{\Cx[1]{\lf{A \IMP B}, \bBR{\Cx[2]}}}{\Cx[1]{\lf{A \IMP B}, \bBR{\rt A, \Cx[2]}}}{\Cx[1]{\bBR{\lf B, \Cx[2]}}}
+%
+\vliinf{\lrn\IMP}{}{\Cx[1]{\lf{A \IMP B}}}{\Cx[1]{\lf{A \IMP B}, \rt A}}{\Cx[1]{\lf B}}
+\quad
+%\vlinf{\lrn[2]\IMP}{}{\Cx[1]{\lf{A \IMP B}, \bBR{\Cx[2]}}}{\Cx[1]{\bBR{\lf{A \IMP B}, \Cx[2]}}}
+\quad
+\vlinf{\rrn\IMP}{}{\Cx{\rt{A \IMP B}}}{\Cx{\bBR{\lf A, \rt B}}}
+\]
+\[
+%\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf A, \Cx[2]}}}}
+\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
+\quad
+\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}
+\quad
+\vlinf{\lrn\DIA}{}{\Cx{\lf{\DIA A}}}{\Cx{\BR{\lf A}}}
+\quad
+\vlinf{\rrn\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt A, \Cx[2]}}}
+\]
+\[
+\vlinf{\rrn{mon}}{}{\Cx[1]{\bBR{\rt A, \Cx[2]}}}{\Cx[1]{\rt A, \bBR{\Cx[2]}}}
+\quad
+%\vlinf{\lrn{mon}}{}{\Cx[1]{\lf A, \bBR{\Cx[2]}}}{\Cx[1]{\bBR{\lf A, \Cx[2]}}}
+\vlinf{\lrn{mon}}{}{\Cx[1]{\lf A, \bBR{\Cx[2]}}}{\Cx[1]{\lf A, \bBR{\lf A, \Cx[2]}}}
+\quad
+%\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\bBR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\Cx[2]}}}}
+%\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\bBR{\Cx[2]}}}}{\Cx[1]{\BR{\bBR{\Cx[2]}}, \bBR{\BR{\Cx[2]}}}}
+\vlinf{\rn{F_1}}{\mbox{\footnotesize$\Dx$ is shallow}}{\Cx[1]{\BR{\Cx[2], \bBR{\Dx}}}}{\Cx[1]{\BR{\Cx[2]}, \bBR{{\BR{\Dx}}}}}
+\]
+%\[\mbox{\hbox to .9\linewidth{\dotfill}}\]
+%\[
+%\vlinf{\rrn{mon}}{}{\Cx[1]{\bBR{\rt A, \Cx[2]}}}{\Cx[1]{\rt A, \bBR{\Cx[2]}}}
+%\quad
+%\vlinf{\rn{refl}_\le}{}{\Cx[1]{\Cx[2]}}{\Cx[1]{\bBR{\Cx[2]}}}
+%\quad
+%\vlinf{\rn{trans}_\le}{}{\Cx[1]{\bBR{\Cx[2], \bBR{\Cx[3]}}}}{\Cx[1]{\bBR{\Cx[2]}, \bBR{\Cx[3]}}}
+%\]
+\end{minipage}
+}		
+\caption{System $\nIKp$}
+\label{fig:nIK}
+\end{figure}
 
@@
 %% appendix is not required.
-\Appendix
-Here starts the appendix. If you don't wish an appendix, please remove the \verb|\Appendix| command from the \LaTeX\ file.
+%\Appendix
 

### 2020-06-01 bicolor NS/aiml20/aiml20.tex
aiml abstract continued

@@
 
-The proof is a careful adaptation of standard techniques.
+%The proof is a careful adaptation of standard techniques.
+%%
+%In particular, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms. 
+%%
+%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.
 %
-In particular, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms. 
-%
-As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.
-
-\vspace*{-.9cm}
-$$
-\hspace*{-.5cm}
-\scalebox{.9}{
-	$
-	\vlderivation{
-		\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-			\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-				\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-					\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-						\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-							\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-								\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-									\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-										\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-											\vlhy {}
-										}
-									}
-								}
-							}{
-								%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-								%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-								%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-								%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-								\vlhy {\qquad\vdots\qquad}
+%\vspace*{-.9cm}
+%$$
+%\hspace*{-.5cm}
+%\scalebox{.9}{
+%	$
+%	\vlderivation{
+%		\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
+%			\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
+%				\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
+%					\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+%						\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+%							\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
+%								\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
+%									\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
+%										\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
+%											\vlhy {}
+%										}
+%									}
+%								}
+%							}{
+%								%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
+%								%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
+%								%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
+%								%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
+%								\vlhy {\qquad\vdots\qquad}
+%								%										}
+%								%									}
+%								%								}
+%								%							}
 %							}
@@
 %				}
-							}
-						}
-					}
-				}
-			}
-		}
-	}$
-}$$
-%\end{example}
-
+%			}
+%		}
+%	}$
+%}$$
+%%\end{example}
+%
+%%\vspace*{-.5cm}
+%
+%Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
+%%
+%We therefore have to show that such a rule is admissible in our system.
+%%
+%As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).
+%
 %\vspace*{-.5cm}
-
-Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%
-We therefore have to show that such a rule is admissible in our system.
-%
-As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).
-
-\vspace*{-.5cm}
-%\begin{example}
-$$
-\scalebox{.9}{
-	$
-	\vlderivation{
-		\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-			\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-				\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-					\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-						\vlhy{}
-					}
-				}
-			}
-		}
-	}
-	$
-}
-$$
-%\end{example}
+%%\begin{example}
+%$$
+%\scalebox{.9}{
+%	$
+%	\vlderivation{
+%		\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
+%			\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+%				\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
+%					\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
+%						\vlhy{}
+%					}
+%				}
+%			}
+%		}
+%	}
+%	$
+%}
+%$$
+%%\end{example}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Extensions}
-
-In~\cite{Simpson}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, w \rel u, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon (\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{Plotkin}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \DIA\DIA A \IMP \DIA A$ are exactly the ones satisfying the condition:
-%\begin{center}
-($\diabrn{4}$) if $w \rel v$ and $v \rel u$, there exists a $u'\in W$ s.t.~$u \le u'$ and $wRu'$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, u \le u', w \rel u' , \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
-%
-These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
 
@@
 %\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\bBR{\Cx[2]}}}}{\Cx[1]{\BR{\bBR{\Cx[2]}}, \bBR{\BR{\Cx[2]}}}}
-\vlinf{\rn{F_1}}{\mbox{\footnotesize$\Dx$ is shallow}}{\Cx[1]{\BR{\Cx[2], \bBR{\Dx}}}}{\Cx[1]{\BR{\Cx[2]}, \bBR{{\BR{\Dx}}}}}
+\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\Cx[2], \bBR{\Cx[3]}}}}{\Cx[1]{\BR{\Cx[2]}, \bBR{{\BR{\Cx[3]}}}}}
 \]
@@
 
-\section{Conclusion}
+\sonia{Say that teh meta theoretic result ie cut-elimination is much harder}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Extensions}
+
 \marianela{say something like the idea comes from proving termination for is4...}
+
+\paragraph{Labelled}
+
+In~\cite{Simpson}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
+%
+For example, you can add the following rule:
+$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, w \rel u, \Left \SEQ \Right}$}$$
+to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
+$\ax{4}\colon (\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)$, that is, wrt.~to all frames in which $\rel$ is transitive.
+
+In~\cite{Plotkin}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
+%
+For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \DIA\DIA A \IMP \DIA A$ are exactly the ones satisfying the condition:
+%\begin{center}
+($\diabrn{4}$) if $w \rel v$ and $v \rel u$, there exists a $u'\in W$ s.t.~$u \le u'$ and $wRu'$.
+%\end{center}
+
+Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
+$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, u \le u', w \rel u' , \Left \SEQ \Right}$}$$
+
+Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
+%
+These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
+
+\paragraph{Nested}
+Replace $\lrn\BOX$ and $\rrn\DIA$ above by the following:
+\[
+\vlinf{\lrn[t]\BOX}{}{\Cx{\lf{\BOX A}}}{\Cx{\lf{\BOX A}, \lf A}}
+\quad
+%\vlinf{\lrn[2]\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf{\BOX A}, \Cx[2]}}}}
+\vlinf{\lrn[4]\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf{\BOX A}, \Cx[2]}}}
+\quad
+\vlinf{\rrn[t]\DIA}{}{\Cx{\rt{\DIA A}}}{\Cx{\rt{\DIA A}, \rt A}}
+\quad
+\vlinf{\rrn[4]\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt{\DIA A}, \Cx[2]}}}
+\]
+%\[\mbox{\hbox to .9\linewidth{\dotfill}}\]
+%\[
+%\vlinf{\rn{refl_{\BR{\cdot}}}}{}{\Cx[1]{\Cx[2]}}{\Cx[1]{\BR{\Cx[2]}}}
+%\qquad
+%\vlinf{\rn{trans_{\BR{\cdot}}}}{}{\Cx[1]{\BR{\Cx[2], \BR{\Cx[3]}}}}{\Cx[1]{\BR{\Cx[2]}, \BR{\Cx[3]}}}
+%\]
 

### 2020-06-01 bicolor NS/aiml20/aiml20.tex
working on aiml abstract

@@
   \begin{abstract}
-  We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
+  %We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
   %
+  We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accesibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic.
+Both systems are in close correspondence with birelational Kripke semantics for intuitionistic modal logic.
   \end{abstract}
@@
   \begin{keyword}
-  Nested sequents, Intuitionistic modal logic, Proof theory.
+  Nested sequents, Labelled sequents, Intuitionistic modal logic, Proof theory.
   \end{keyword}
@@
 \section{Introduction}
-\todo{Say: working on multi-conclusion nested sequents for intuitionistic modal logic. A bit of story? Why is useful?}
 
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and sequent systems \cite{simpson1994proof},
-or the one of \emph{unlabelled deduction} in the form of nested sequent systems \cite{strassburger2013cut,}.
+\todo{sell the systems! more emphasis in the nested sequent system?}
+
+Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson1994}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{bierman2000} or nested sequent systems~\cite{strassburger2013} (for a survey see~\cite[Chap.~3]{marin2018}).
+In this article, we present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing the accesibility relation for modal logics and the intuitionistic relation $\le$.
+In the labelled calculus we made explicity both relations with $\rel$ and $\le$ into the system.
+In the nested sequent system, we represent this relations with one bracket in a sequent (for the accesibility relation) and a with two brackets in a sequent (preorder relation).
 
@@
 %
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted $a$, modal formulas are constructed from the grammar:
+Starting with a set $\mathcal{A}$ of atomic propositions, denoted $\fm a$, modal formulas are constructed from the grammar:
 %
 $$
-A \coloncolonequals
-a \mid A \AND A \mid \TOP \mid A \OR A \mid \BOT \mid A \IMP A \mid \BOX A \mid \DIA A
+\fm A \coloncolonequals
+\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm{\TOP} \mid \fm{\BOT} \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
 $$
@@
 \begin{itemize}
-	\item the \emph{necessitation rule}: $\BOX A$ is a theorem if $A$ is a theorem; and
+	\item the \emph{necessitation rule}: $\fm{\BOX A}$ is a theorem if $\fm{A}$ is a theorem; and
 	\item the following five variants of the \emph{distributivity axiom}:
@@
 	\begin{enumerate}
-		\item[($F_1$)] For $u, v, v' \in W$, if $u \rel v$ and $v \le v'$, there exists $u'$ s.t.~$u \le u'$ and $u' \rel v'$.
+		\item[($F_1$)] For $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs{v}{v'}$, there exists $\lb{u'}$ s.t.~$\futs{u}{u'}$ and $\accs{u'}{v'}$.
 
-		\item[($F_2$)] For $u', u, v \in W$, if $u \le v$, there exists $v'$ s.t.~$u' \rel v'$ and $v\le v'$.
+		\item[($F_2$)] For $\lb{u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb{v'}$ s.t.~$\accs{u'}{v'}$ and $\futs{v}{v'}$.
 	\end{enumerate}
@@
 
-\marianela{We recall the birelational models \cite{plotkin1986, ewald1986} for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
-A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:
-}
+%\marianela{We recall the birelational models \cite{plotkin1986, ewald1986} for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
+A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:}
 
 \begin{definition}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $w$ to the subset of propositional atoms true at $w$, additionally subject to:
-	if $w \le w'$ then $V(w)\subseteq V(w')$.
+	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
+	if $\futs{w}{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
 \end{definition}
 
-We write $w \Vdash a$ if $a \in V(w)$, and by definition, we always have $w \Vdash \top$ and never that $w \Vdash \bot$. 
+We write $\lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and by definition, we always have $\lb w \Vdash \fm{\TOP}$ and never that $\lb w \Vdash \fm{\BOT}$. 
 %
@@
 
-$w \Vdash A \AND B$ iff $w \Vdash A$ and $w \Vdash B$
+$\lb w \Vdash \fm{A \AND B}$ iff $\lb w \Vdash \fm A$ and $\lb w \Vdash \fm B$
 
-$w \Vdash A \OR B$ iff $w \Vdash A$ or $w \Vdash B$
+$\lb w \Vdash \fm{A \OR B}$ iff $\lb w \Vdash \fm A$ or $\lb w \Vdash \fm B$
 
-$w \Vdash A \IMP B$ iff for all $w'$ with $w \le w'$, if $w' \Vdash A$ then $w' \Vdash B$
+$\lb w \Vdash \fm{A \IMP B}$ iff for all $\lb{w'}$ with $\futs{w}{w'}$, if $\lb{w'} \Vdash \fm A$ then $\lb{w'} \Vdash \fm B$
 
-$w \Vdash \BOX A$ iff for all $w'$ and $u$ with $w \le w'$ and $w'Ru$, $u \Vdash A$ %\hfill $(\ast)$
+$\lb w \Vdash \fm{\BOX A}$ iff for all $\lb{w'}$ and $\lb u$ with $\futs{w}{w'}$ and $\accs{w'}{u}$, $\lb u \Vdash \fm A$ %\hfill $(\ast)$
 
-$w \Vdash \DIA A$ iff there exists a $u$ such that $wRu$ and $u \Vdash A$.
+$\lb w \Vdash \fm{\DIA A}$ iff there exists a $\lb u$ such that $\accs wu$ and $\lb u \Vdash \fm A$.
 
 \begin{definition}
-	A formula $A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $w \in W$ we have $w \Vdash A$.
+	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $\lb w \in W$ we have $\lb w \Vdash \fm A$.
 	%
-	A formula $A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $A$ is satisfied in $\langle W, R, \le, V \rangle$.
+	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}
@@
 
-\begin{theorem}[Fischer-Servi~\cite{Fischer}, Plotkin and Stirling~\cite{Plotkin}]\label{thm:plotkin}
-	A formula $A$ is a theorem of $\IK$ if and only if $A$ is valid in every bi-relational frame.
+\begin{theorem}[Fischer-Servi~\cite{fischer1984}, Plotkin and Stirling~\cite{plotkin1986}]\label{thm:plotkin}
+	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
 \end{theorem}
@@
 				\multicolumn{2}{c}{
-					$\vlinf{\llabrn\IMP}{\text{\scriptsize $y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, x \le y, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
+					$\vlinf{\llabrn\IMP}{\text{\scriptsize $\lb y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, \futs xy, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
 				}
@@
 				\multicolumn{2}{c}{
-					$\vliinf{\rlabrn\IMP}{}{\B, x \le y, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, x \le y, \Left \SEQ \Right, \labels{y}{A}}{\B, x \le y, \Left, \labels{y}{B} \SEQ \Right}$ 
+					$\vliinf{\rlabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$ 
 					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
@@
 				\\\\
-				$\vlinf{\llabrn\BOX}{}{\B, \Left, x \le y, yRz, \labels{x}{\BOX A} \SEQ \Right}{\B,\Left, x \le y, yRz, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
+				$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
 				&
-				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $y, z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \Left, x \le y, y \rel z \SEQ \Right, \labels{z}{A}}$
+				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $\lb y, \lb z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
 				\\\\
-				$\vlinf{\llabrn\DIA}{\text{\scriptsize $y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \Left, x \rel y, \labels{y}{A} \SEQ \Right}$
+				$\vlinf{\llabrn\DIA}{\text{\scriptsize $\lb y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
 				&
-				$\vlinf{\rlabrn\DIA}{}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}}{\B, \Left, x \rel y \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
+				$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
 				\\
@@
 				\\
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, x\le x, \Left \SEQ \Right}$
+				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
 				&
-				$\vlinf{\rn{trans}}{}{\B, x \le y, y \le z, \Left \SEQ \Right}{\B, x \le y, y \le z, x \le z, \Left \SEQ \Right}$
+				$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
 				\\\\
 				\multicolumn{2}{c}{
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $u$ fresh}}{\B, xRy, y \le z, \Left \SEQ \Right}{\B, xRy, y \le z, x \le u, uRz, \Left \SEQ \Right}$
+					$\vlinf{\rn{F_1}}{\text{\scriptsize $\lb u$ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
 				}
@@
 				\multicolumn{2}{c}{
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $u$ fresh}}{\B, xRy,x \le z, \Left \SEQ \Right}{\B, xRy, x \le z, y \le u, zRu, \Left \SEQ \Right }$		
+					$\vlinf{\rn{F_2}}{\text{\scriptsize $\lb u$ fresh}}{\B, \accs xy,\futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
 				}
@@
 
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{Simpson}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{Bierman} or nested sequent systems~\cite{Strassburger} (for a survey see~\cite[Chap.~3]{Marin}).
-
+\emph{Labelled deduction} has been proposed by Gabbay~\cite{gabbay1996} in the 80s as a unifying framework throughout proof theory in order to provide proof
+systems for a wide range of logics. 
+%
+For modal logics it can take
+the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson~\cite{simpson1994}, Vigan\`o~\cite{vigano2000}, and Negri~\cite{negri2005}. 
+%
 Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
@@
 %
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{Maffezioli}.
+The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli2013}.
 %
@@
 \begin{definition}
-	A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $x \rel y$ and preorder atoms $x \le y$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $x$ and $y$ taken from the set of labels and $A$ an intuitionistic modal formula).
+	A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $\accs xy$ and preorder atoms $\futs xy$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $\lb x$ and $\lb y$ taken from the set of labels and $A$ an intuitionistic modal formula).
 \end{definition}
@@
 %
-Most rules are similar to the ones of Simpson~\cite{Simpson}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
+Most rules are similar to the ones of Simpson~\cite{simpson1994}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
 %
@@
 
-where $A_{1}, .
+where $\fm{A_{1}}, .
 .
 .
-, A_{n}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $B_{1}, .
+, \fm{A_{n}}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $\fm{B_{1}}, .
 .
 .
-, B_{k}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], .
+, \fm{B_{k}}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], .
 .
@@
 In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
-$\force{x}{\BOX A}$ iff for all $y$ and $z$ s.t. $\futs xy$ and $\accs yz$, $\force{z}{A}$. Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
+$\force{\lb x}{\fm{\BOX A}}$ iff for all $\lb y$ and $\lb z$ s.t.
+$\futs xy$ and $\accs yz$, $\force{\lb z}{\fm{A}}$.
+Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
 
@@
 For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, w \rel u, \Left \SEQ \Right}$}$$
+$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
 to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon (\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)$, that is, wrt.~to all frames in which $\rel$ is transitive.
+$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
 
-In~\cite{Plotkin}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
+In~\cite{plotkin1986}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
 %
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \DIA\DIA A \IMP \DIA A$ are exactly the ones satisfying the condition:
+For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
 %\begin{center}
-($\diabrn{4}$) if $w \rel v$ and $v \rel u$, there exists a $u'\in W$ s.t.~$u \le u'$ and $wRu'$.
+($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
 %\end{center}
@@
 Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $u'$ fresh}}{\B, w \rel v, v \rel u, \Left \SEQ \Right}{\B, w \rel v, v \rel u, u \le u', w \rel u' , \Left \SEQ \Right}$}$$
+$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
 
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{Plotkin}.
+Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
 %

### 2020-06-01 BicolorNS/wil20/wil20.tex
changing the repo structure

--- 2020-05-11 bicolor NS/abstract/wil20.tex
@@
 %%
-We recall the birelational models [21, 7] for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
+We recall the birelational models \cite{plotkin1986, ewald1986} for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
 A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:

### 2020-06-01 FullyLabelled/JLC/introduction.tex
changing the repo structure

--- 2019-10-08 caleidoscope/introduction.tex
@@
 
-\todo{get bib-file right}
+%\todo{get bib-file right}
 
@@
   sequent, we only have that a sequent $\Gamma$ is provable if and
-  only if is is valid in all \emph{graph-consistent}\footnote{This
+  only if is satisfied in all \emph{graph-consistent}\footnote{This
     means that every layer in the model can be lifted to any future of
@@
   models, 
-  \sonia{this is only true for logics outside of the path axioms.}
-  \todo{check that Simpson's system is sound and complete for all logics defined by path axioms.
+%  \sonia{this is only true for logics outside of the path axioms.}
+%  \todo{check that Simpson's system is sound and complete for all logics defined by path axioms.
 Is it that the axiomatisation is also sound and complete for every models and not only graph-consistent ones?}
-  \sonia{yes, they are sound and complete for the general models, but they do not \emph{characterize} the frames, they are not \emph{frame conditions}, as opposed to the \emph{correspondence result} of Plotkin and Sterling.}
+%  \sonia{yes, they are sound and complete for the general models, but they do not \emph{characterize} the frames, they are not \emph{frame conditions}, as opposed to the \emph{correspondence result} of Plotkin and Sterling.}
   as already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
@@
 logic are single-conclusion~\cite{simpson:phd}. 
-\sonia{No! the system for epistemic logic by Maffezioli, Naibo and Negri~\cite{maffezioli:etal:synthese13} is multi-conclusion}
-\todo{need to say that it is the same principle as in their work, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics while keeping the nice invertibility property.}
 %
@@
 systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
-intuitionistic logic. Our system eliminates this
-discrepancy. Consequently, every rule in our system is invertible, as
-we never delete information.
-
-\medskip
+intuitionistic logic. 
+%
+Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.
+%
+Our system uses the same principle, both labelled and multi-conclusion sequents, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics.
+%
+This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.
 
@@
 
-\todo{maybe paragraph on related work?}
+%\todo{maybe paragraph on related work?}
 

### 2020-06-01 FullyLabelled/JLC/preliminaries.tex
changing the repo structure

--- 2019-10-03 caleidoscope/preliminaries.tex
@@
 %%
-Lacking De Morgan duality, there are several variants of $\mathsf{k}$ that are classically but not intuitionistically equivalent.
+Lacking De Morgan duality, there are many variants of the \emph{distributivity axiom} $\mathsf{k}$ that are classically but not intuitionistically equivalent.
 Five axioms have been considered as primitives in the literature.
@@
 	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
-	\item the following five variants of the \emph{distributivity axiom} $\rn{k}$:
+	\item the following five variants of $\rn{k}$:
 	\begin{equation*}
@@
 \end{itemize}
-\sonia{axioms vs. axiom schemes? do we need to write these on atomic formulas $a,b$ instead of generic formulas $A,B$?}
 
@@
 Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-The systems are well-designed for some applications for example to analyse some type systems \cite{benton:etal:jfp98} or to reason about states of a machine under partial information \cite{wijesekera:nerode:apal05}.
-However, they cannot satisfy the logicians as the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
+In these systems, however, the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
 
@@
 	%\parbox{30em}{%
-
 		\M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\
@@
 \end{equation}
-Observe that we never that $\M, \lb w \Vdash \fm\bot$. 
+Observe that we never have that $\M, \lb w \Vdash \fm\bot$. 
 %

### 2020-06-01 FullyLabelled/JLC/soundness.tex
changing the repo structure

--- 2019-10-08 caleidoscope/soundness.tex
@@
 	$\SG$ be the sequent $\lseq\B\Left\Right$. 
-	\sonia{$\mathcal G$ usually denotes only the relational context.
+%	\sonia{$\mathcal G$ usually denotes only the relational context.
 using it for the whole sequent is confusing.

### 2020-06-01 Marianela/thesis/chapters/abstract_en.tex
changing the repo structure

\paragraph{Abstract}

The study of modal logic \cite{blackburn01}, going back to Aristotle, comes from the desire to analyse certain philosophical arguments, and thus qualify finely the truth of a proposition: for example a proposition may be false now but true later, or on the contrary true and necessarily so, and so on. What is now called modal logic describes the behaviour of the abstract modalities $\square$ and $\Diamond$, but covers a wide range of ‘real’ modalities in linguistic expressions: time, necessity, possibility, obligation, knowledge, belief, etc. Semantically, the modal operators and more precisely the $\Diamond$, allows to describe properties of the different states that you can reach from the evaluation point.

Since the modal model theory began to develop, there is a tendency to use methods based on model theory instead of proof theory, because the classical proof systems were generally insufficient. However, in the last years, new techniques were developed, and proof systems began to be more familiar, that’s why they have certain advantages when it comes to analysis or standardization of proofs. Look at \cite{negri2005} to have more details of this dichotomy. Labelled deduction has been more generally proposed by Gabbay \cite{gabbay1996} in the 80’s as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics. For modal logics it can also take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson \cite{simpson1994}, Vigano \cite{vigano2013}, and Negri \cite{negri2005}. These formalisms make explicit use not only of labels, but also of relational atoms that reference the accessibility relation with a Kripke model \cite{kripke1959}.

We will continue with a choice of a sequent presentation. More precisely, in this work, the main goal consists of developing a labelled sequent system for intuitionistic modal logic, that comes with two relation symbols: one for the accessible world relation associated with the Kripke semantics for classical modal logics, and one for the preorder relation associated with the Kripke semantics for intuitionistic logic. To obtain this result, we used a labelled sequent calculus proposed by Negri \cite{negri2005} for classical modal logics and we extended it with a preorder relation. That allows to have a labelled system in close correspondence to the birelational Kripke models.

\bigskip
\bigskip
\bigskip

\textbf{Palabras clave:} lógica modal, lógica intuicionista, cálculo de secuentes etiquetados, teoría de prueba, Gentzen, modelos bi-relacionales.

\textbf{Key words:} modal logic, intuitionistic logic, labelled sequent calculus, proof theory, Gentzen, bi-relational models.

### 2020-06-01 Marianela/thesis/chapters/abstract_es.tex
changing the repo structure

\paragraph{Resumen}

El estudio de la lógica modal \cite{blackburn01}, desde Aristóteles, proviene del deseo de analizar ciertos argumentos filosóficos y así poder establecer la verdad de una proposición: por ejemplo, una proposición puede ser falsa ahora pero verdadera más tarde, o por el contrario necesariamente verdadera, y así sucesivamente. Lo que llamamos lógica modal describe el comportamiento abstracto de las modalidades $\square$ y $\Diamond$, pero abarca una amplia cantidad de modalidades 'reales' en las expresiones ling\"{u}ísticas: tiempo, necesidad, posibilidad, obligación, conocimiento, creencia, etc. Semánticamente, los operadores modales y más precisamente el $\Diamond$, nos permite describir propiedades de los diferentes estados que podemos alcanzar a partir de un punto de evalación.

Desde que la teoría de modelos modal comenzó a desarrollarse, existe una tendencia a utilizar métodos basados en la teoría de modelos en lugar de aquellos basados en la teoría de prueba ya que los sistemas de prueba clásicos eran generalmente insuficientes. Sin embargo, en los últimos años, nuevas técnicas fueron desarrolladas y los sistemas de prueba comenzaron a ser mayormente utilizados ya que proveen ciertas ventajas cuando se trabaja con el análisis y estandarización de pruebas. Para tener más detalles sobre esta dicotomía vease \cite{negri2005}. La deducción etiquetada propuesta por Gabbay \cite{gabbay1996} en los 80's se presentó como un marco unificador de la teoría de prueba para proporcionar sistemas de prueba para una amplia gama de lógicas. Para las lógicas modales, también puede tomar la forma de deducción natural etiquetada y sistemas de secuentes etiquetados como los de Simpson \cite{simpson1994}, Vigano \cite{vigano2013} y Negri \cite{negri2005}. Estos formalismos hacen un uso explícito no sólo de las etiquetas sino también de los átomos relacionales que hacen referencia a la relación de accesibilidad con un modelo de Kripke \cite{kripke1959}.

Continuaremos con la elección de una presentación de secuentes. Más precisamente, en este trabajo, el objetivo principal consiste en desarrollar un sistema de secuentes etiquetados para la lógica modal intuicionista, que involucra dos símbolos de relación: uno para la relación de accesibilidad asociada con la semántica de Kripke para lógicas modales clásicas, y otra relación de pre-orden asociada a la semántica de Kripke para la lógica intuicionista. Para obtener este resultado, utilizamos un cálculo de secuentes etiquetado propuesto por Negri \cite{negri2005} para lógicas modales clásicas y lo extendimos con una relación de pre-orden. Esto permite tener un sistema etiquetado en estrecha correspondencia con los modelos bi-relacionales de Kripke.

### 2020-06-01 Marianela/thesis/chapters/acknow.tex
changing the repo structure

\newpage
\bigskip

\paragraph{Menciones especiales}

\begin{quote}
	Antes de comenzar, quiero destacar en este pequeño párrafo que gran parte de este trabajo fue resultado de un trabajo en conjunto con Sonia Marin. Ella realizó sus estudios de doctorado con uno de mis directores, el Dr. Lutz Stra$\ss$burger, y el desarrollo de su tesis doctoral (Ver \cite{marin2018}) fue el punto de partida de esta tesis de Licenciatura que se fue conformando con ideas provenientes de Sonia. El labor y el acompañamiento por parte de ella fue fundamental a lo largo de este trabajo final de Licenciatura.s
\end{quote}

### 2020-06-01 Marianela/thesis/chapters/completeness.tex
changing the repo structure

\chapter{Completitud}
\label{cap:completeness}
%En esta sección demostramos completitud con respecto al sistema de Hilbert utilizando nuestro sistema de prueba etiquetado \textbf{labIK$\heartsuit$}.
Como se mencionó en el capítulo previo, necesitamos demostrar una propiedad importante de nuestro sistema que llamamos completitud. Intuitivamente, esta propiedad indica que nuestro sistema posee todo aquello que es necesario para demostrar las verdades de la lógica que caracteriza.

En esta tesis, para la demostración de completitud de $\labIKh$ seguiremos dos estrategias. La primera consiste en demostrar que con las reglas de $\labIKh$ podemos obtener todos los axiomas y reglas del sistema $\IK$. Dado que $\IK$ ya es completo, obtenemos la completitud de nuestro sistema. Por otro lado, demostraremos que nuestro sistema permite simular todas las reglas del sistema propuesto por Simpson \cite{simpson1994} que también es completo. Esta última estrategia además nos permite eliminar la regla de $\mathsf{cut}$. Veremos esto en mayor detalle en el Capítulo \ref{cap:future}.

En este capítulo seguiremos la primer estrategia, es decir, realizamos una demostración sintáctica en la cual las reglas de nuestro sistema son suficientes para la prueba de cada uno de los axiomas que necesitamos probar.

\begin{teo} Cada teorema de la lógica $\IK$ es demostrable en $\labIKh$.
\end{teo}
\emph{Demostración}. Como se dijo anteriormente, nuestra demostración demuestra completitud con respecto del sistema a la Hilbert. Para esta prueba necesitamos:
\begin{enumerate}
	\item Probar las variantes $\kaxiom_{1}$, ..., $\kaxiom_{5}$ del axioma de distributividad $\kaxiom$ presentados en el Capítulo \ref{cap:logintuicionista}.
	\item Demostrar todos los axiomas de la lógica modal proposicional.
	\item Simular modus ponens.
	\item Simular necesitación.
\end{enumerate}

Para llevar a cabo todo lo anterior, realizaremos nuestras demostraciones a partir del uso de las reglas de nuestro sistema $\labIKh$. De esta manera, como el sistema \emph{a la Hilbert} es completo, obtenemos completitud de nuestro sistema.

En primer lugar, veremos que los axiomas $\kaxiom_{1}$, ..., $\kaxiom_{5}$ se pueden demostrar en el sistema $\labIKh$ como se muestra a continuación:

\section{Axiomas modales}

\begin{lemma}
	Los axiomas $\kaxiom_{1}$, ..., $\kaxiom_{5}$ son demostrables en $\labIKh$
\end{lemma}

\paragraph{Axioma $\kaxiom_{1}$}
\kone

\paragraph{Axioma $\kaxiom_{2}$}
	\ktwo

\paragraph{Axioma $\kaxiom_{3}$}

\begin{center}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon \Diamond (\vls[A.B]) \vljm (\vls[\Diamond A. \Diamond B ])}
		{\vlin {\sdl}
			{}
			{x \le y, y \colon \Diamond (\vls[A.B]) \Rightarrow y \colon \vls[\Diamond A. \Diamond B] }
			{\vliin{\solef}{}{x \le y, yRz, z \colon \vls[A.B] \Rightarrow y \colon \vls[\Diamond A. \Diamond B]}{\vlhy{\circledast \hspace{40mm}}}{\vlhy{\star}}}}
	}$

	\bigskip

\end{center}

	Luego de aplicar la regla de disjunción para el lado izquierdo, nuestra derivación continúa con dos premisas. Por un lado tenemos la premisa que se sigue de $\circledast$:

	\bigskip
	\begin{center}
	$\vlderivation{\vlin{\solef}{}{\circledast}{\vlin {\sorig}
			{}
			{x \le y, yRz, z \colon A \Rightarrow y \colon \vls[\Diamond A. \Diamond B]}
			{\vlin {\sdr}
				{}
				{x \le y, yRz, z \colon A \Rightarrow y \colon \Diamond A, y \colon \Diamond B}
				{\vlin {\refl}
					{}
					{x \le y, yRz, z \colon A \Rightarrow y \colon \Diamond A, z \colon A, y \colon \Diamond B}
					{\vlin {\ids}
						{}
						{x \le y, z \le z, yRz, z \colon A \Rightarrow y \colon \Diamond A, z \colon A, y \colon \Diamond B}
						{\vlhy {}}}}}}}$
	\end{center}	
		Y por otra parte, tenemos la derivación que continua a partir de $\star$:

		\begin{center}
	$\vlderivation{\vlin {\solef}
	{}
	{\star}
	{\vlin {\sorig}
		{}
		{x \le y, yRz, z \colon B \Rightarrow y \colon \vls[\Diamond A. \Diamond B]}
		{\vlin {\sdr}
			{}
			{x \le y, yRz, z \colon B \Rightarrow y \colon \Diamond A, y \colon \Diamond B}
			{\vlin {\refl}
				{}
				{x \le y, yRz, z \colon B \Rightarrow y \colon \Diamond A, y \colon \Diamond B, z \colon B}
				{\vlin {\ids}
					{}
					{x \le y, z \le z, yRz, z \colon B \Rightarrow y \colon \Diamond A, y \colon \Diamond B, z \colon B}
					{\vlhy {}}}}}}}$
\end{center}

\paragraph{Axioma $\kaxiom_{4}$}
	\kfour

\paragraph{Axioma $\kaxiom_{5}$}

\begin{center}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon \Diamond \bot \vljm \bot}
		{\vlin {\sdl}
			{}
			{x \le y, y \colon \Diamond \bot \Rightarrow y \colon \bot}
			{\vlin {\sbot}
				{}
				{x \le y, yRz, z \colon \bot \Rightarrow y \colon \bot}
				{\vlhy {}}}}
	}$

\end{center}

\vspace{4mm}

\section{Axiomas proposicionales intuicionistas}
Para continuar con esta demostración, también debemos ver que todos los axiomas de la lógica proposicional intuicionista son demostrables en $\labIKh$. A continuación se puede observar una demostración para cada uno de los axiomas que fueron introducidos en el Capítulo 3. Continuamos con un método sintáctico de prueba en el que utilizamos las reglas de nuestro sistema.

\begin{lemma}
	Los axiomas la lógica proposicional intuicionista son demostrables en $\labIKh$.
\end{lemma}

\begin{center}
	\textbf{THEN-1}

	$\vlderivation{
		\vlin{\sir}
		{}
		{\Rightarrow x \colon A \vljm (B \vljm A)}
		{\vlin {\sir}
			{}
			{x \le y, y \colon A \Rightarrow y\colon B \vljm A}
			{\vlin {\ids}
				{}
				{x \le y, y \le z, y \colon A, z \colon B \Rightarrow z \colon A}
				{\vlhy {}}}}
	}$

\end{center}

\bigskip

\begin{center}
	\textbf{AND-1}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon \vls(A.B) \vljm A}
		{\vlin {\svlef}
			{}
			{x \le y, y \colon \vls(A.B) \Rightarrow y \colon A}
			{\vlin {\refl}
				{}
				{x \le y, y \colon A, y \colon B \Rightarrow y \colon A}
				{\vlin {\ids}
					{}
					{x \le y, y \le y, y \colon A, y \colon B \Rightarrow y \colon A}
					{\vlhy {}}}}}
	}$
\end{center}

\bigskip

\begin{center}
	\textbf{AND-2}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon \vls(A.B) \vljm B}
		{\vlin {\svlef}
			{}
			{x \le y, y \colon \vls(A.B) \Rightarrow y \colon B}
			{\vlin {\refl}
				{}
				{x \le y, y \colon A, y \colon B \Rightarrow y \colon B}
				{\vlin {\ids}
					{}
					{x \le y, y \le y, y \colon A, y \colon B \Rightarrow y \colon B}
					{\vlhy {}}}}}
	}$
\end{center}

\bigskip

\begin{center}
	\textbf{AND-3}

	$\vlderivation{
		\vlin{\sir}
		{}
		{\Rightarrow x \colon A \vljm (B \vljm (\vls(A.B)))}
		{\vlin {\sir}
			{}
			{x \le y, y \colon A \Rightarrow y \colon B \vljm (\vls(A.B))}
			{\vliin {\svrig}
				{}
				{x \le y, y \le z, y \colon A, z \colon B \Rightarrow z \colon \vls(A.B)}
				{\vlin {\ids}
					{}
					{x \le y, y \le z, y \colon A, z \colon B \Rightarrow z \colon A}
					{\vlhy {}}}
				{\vlin {\refl}
					{}
					{x \le y, y \le z, y \colon A, z \colon B \Rightarrow z \colon B}
					{\vlin {\ids}
						{}
						{x \le y, y \le z, z \le z, y \colon A, z \colon B \Rightarrow z \colon B}
						{\vlhy {}}}}}}
	}$

\end{center}

\bigskip

\begin{center}
	\textbf{OR-1}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon A \vljm \vls[A.B]}
		{\vlin {\sorig}
			{}
			{x \le y, y \colon A \Rightarrow y \colon \vls[A.B]}
			{\vlin {\refl}
				{}
				{x \le y, y \colon A \Rightarrow y \colon A, y \colon B}
				{\vlin {\ids}
					{}
					{x \le y, y \le y, y \colon A \Rightarrow y \colon A, y \colon B}
					{\vlhy {}}}}}
	}$

\end{center}

\bigskip

\begin{center}
	\textbf{OR-2}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon B \vljm \vls[A.B]}
		{\vlin {\sorig}
			{}
			{x \le y, y \colon B \Rightarrow y \colon \vls[A.B]}
			{\vlin {\refl}
				{}
				{x \le y, y \colon B \Rightarrow y \colon A, y \colon B}
				{\vlin {\ids}
					{}
					{x \le y, y \le y, y \colon B \Rightarrow y \colon A, y \colon B}
					{\vlhy {}}}}}
	}$

\end{center}

\bigskip

\begin{center}
	\textbf{OR-3}
\end{center}
\orthree

\bigskip

\begin{center}
	\textbf{FALSE}

	$\vlderivation {
		\vlin{\sir}
		{}
		{\Rightarrow x \colon \bot \vljm A}
		{\vlin {\sbot}
			{}
			{x \le y, y \colon \bot \Rightarrow y \colon A}
			{\vlhy {}}}
	}$

\end{center}

\vspace{3mm}

\begin{center}
	\textbf{THEN-2}
\end{center}
\thentwo

\vspace{3mm}

\section{Simulando Modus Ponens}
Una vez concluida esta demostración para cada uno de los axiomas de la lógica proposicional intuicionista, seguimos adelante con el resto de nuestra demostración para poder probar la completitud de nuestro sistema $\labIKh$. Para ello, continuamos mostrando que podemos simular de modus ponens utilizando \emph{la regla de cut} donde $\mathsf{cut}$ es:

\begin{center}

	$\vliinf{\mathsf{cut}}{}{\Gone, \Gtwo, \Left \Rightarrow \Right}{\Gone, \Left \Rightarrow \Right, z \colon C}{\Gtwo, \Left, z \colon C \Rightarrow \Right}$

\end{center}

Es así que utilizando $\mathsf{cut}$ vemos que la regla de modus ponens $\vliinf{}{}{B}{A}{A \vljm B}$ es simulada de la siguiente manera:

\vspace{3mm}

\begin{center}

		$\vlderivation {
			\vliin{\cut}
			{}
			{\Rightarrow x \colon B}
			{\vlin {w}
				{}
				{\Rightarrow x \colon A, x \colon B}
				{\vlhy {\Rightarrow x \colon A}}}
			{\vliin {\mathsf{cut}}
				{}
				{x \colon A \Rightarrow x \colon B}
				{\vlhy{\circledast}}
				{\vlhy{\star}}}
		}$
\end{center}

\bigskip

	Hemos representado con $\circledast$ y $\star$ la continuación de esta derivación en donde de $\circledast$ se sigue:

	\bigskip

	\begin{center}
	$\vlderivation{\vlin{\mathsf{cut}}{}{\circledast}{\vlin {\mathsf{w}}
			{}
			{x \colon A \Rightarrow x \colon B, x \colon A \vljm B}
			{\vlhy {\Rightarrow x \colon A \vljm B}}}}$

\end{center}

Mientras que de $\star$ se obtiene:

\begin{center}
	$\vlderivation{\vlin{\mathsf{cut}}{}{\star}{\vlin {\refl}
			{}
			{x \colon A, x \colon A \vljm B \Rightarrow x \colon B}
			{\vliin {\sil}
				{}
				{x \le x, x \colon A, x \colon A \vljm B \Rightarrow x \colon B}
				{\vlin {\ids}
					{}
					{x \le x, x \colon A, x \colon A \vljm B \Rightarrow x \colon B, x \colon A}
					{\vlhy {}}}
				{\vlin {\ids}
					{}
					{x \le x, x \colon A, x \colon A \vljm B, x \colon B \Rightarrow x \colon B}
					{\vlhy {}}}}}}$
\end{center}

Finalmente, queda demostrado que pudimos simular la regla de modus ponens a partir del uso de las reglas de secuentes que conforman el sistema $\labIKh$ y de la regla de $\mathsf{cut}$.

\section{Simulando Necesitación}

Una vez demostrado que podemos simular modus ponens utilizando la regla cut y las reglas de nuestro sistema, nos resta ver que podemos simular la regla de necesitación donde \emph{necesitación} es: Si existe una prueba de $A$, entonces existe una prueba de $\square A$.

En otras palabras, queremos probar que:

\begin{lemma}
	Si existe una prueba de $\vlderivation {\vlpd{\Done}{}{\Rightarrow z \colon A}}$ entonces existe una prueba de $\vlderivation { \vlpd{\Dtwo}{}{\Rightarrow x \colon \square A}}$.
\end{lemma}

\begin{proof}

	Podemos mostrar que:

		Si $\vlderivation {\vlpd {\mathcal{D}_{1}}{}{\Rightarrow z \colon A}}$ \hspace{4mm} entonces tenemos que \hspace{4mm} $\vlderivation{\vlin{\sbr}{}{\Rightarrow x \colon \square A}{\vlpd {\Dwone}{}{x \le y, yRz \Rightarrow z \colon A}}}$

	\bigskip

		     donde llamaremos $\Dtwo$ a lo siguiente: $\Dtwo = \vlderivation {\vlpd {\Dwone}{}{x \le y, yRz \Rightarrow z \colon A}}$ 
	\bigskip

Luego, utilizando la regla de debilitamiento (o en inglés \emph{weakening}) tenemos que:

\bigskip
\begin{center}
	$\vlderivation{\vlin{\sbr}{}{\Rightarrow x \colon \square A}{\vlin{\mathsf{w}}{}{x \le y, yRz \Rightarrow z \colon A}{\vlhy{ \Rightarrow z \colon A}}}}$
\end{center}

\end{proof}

A continuación veremos la demostración de otros lemas que nos permitieron realizar las distintas demostraciones de las reglas para probar completitud.

En el Lema \ref{lemaw} demostramos la admisibilidad de la regla de debilitamiento o \emph{weakening} que fue ya utilizada para simular la regla de necesitación.

\begin{lemma}
	\label{lemaw}
	Si existe una prueba $\vlderivation {\vlpd{\D}{}{\G, \Left \Rightarrow \Right}}$ entonces existe una prueba \break $\vlderivation {\vlpd {\Dw}{}{\G, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}}$

\end{lemma}

\vspace{3mm}

\begin{proof}
	Por induccion en la altura de $\D$.

	Para una prueba de altura 1:

	Si $\D$ = $\vlderivation {\vlin{\ids}{}{\G, \Left, x \le y, x \colon a \Rightarrow \Right, y \colon a}{\vlhy {}}}$ entonces tenemos que:

		\hspace{40mm}$\Dw$ = $\vlderivation {\vlin{\ids}{}{\G, \Left, x \le y, x$R$y, u \le v, x \colon a, z \colon A \Rightarrow \Right, w \colon B, y \colon a}{\vlhy {}}}$.

	\vspace{3mm}

	Para una prueba en la altura de $\D$ mayor a 1:

	\begin{center}

		$\vlderivation{\vlin {$r$}{}{\G, \Left \Rightarrow \Right}{\vlpd {\Done}{}{\G', \Left' \Rightarrow \Right'}}}$

	\end{center}

	Luego, por hipótesis inductiva existe una prueba
	\begin{center}

		$\vlderivation {\vlpd {\Dwone}{}{\G', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}$

	\end{center}

	Por lo tanto, tenemos la prueba

	\begin{center}

		$\Dw = \vlderivation {\vlin{}{}{\G, xRy, u \le v, \Left, z \colon A \Rightarrow \Right, w \colon B}{\vlpd {\Dwone}{}{\G', xRy, u \le v, \Left', z \colon A \Rightarrow \Right', w \colon B}}}$

	\end{center}

\end{proof}

A lo largo de nuestras pruebas sintácticas, hemos utilizado la regla de identidad para las fórmulas. Ya que $\labIKh$ presenta únicamente la regla de identidad para átomos, en el siguiente lema vemos la admisibilidad de la regla para el caso general en nuestro sistema.

\begin{lemma}
	La siguiente regla es admisible en $\labIKh$:

	\begin{center}

		$\vlderivation {\vlin{\idg}{}{\G, x \le y,  \Left, x \colon A \Rightarrow \Right, y \colon A }{\vlhy {}}}$

	\end{center}

\end{lemma}

\vspace{3mm}

\begin{proof}  Por inducción en el tamaño de $A$.

	\begin{itemize}
		\item{$A=a$}:

		Tenemos que la regla $\vlderivation {\vlin{\idg}{}{\G, x \le y,  \Left, x \colon a \Rightarrow \Right, y \colon a }{\vlhy {}}}$ es la misma regla que forma parte del sistema $\labIKh$:  $\vlderivation {\vlin{\ids}{}{\G, x \le y,  \Left, x \colon a \Rightarrow \Right, y \colon a }{\vlhy {}}}$

		\item{$A= \vls(A.B)$:}

		\begin{center}
			$\vlderivation{\vliin{\svrig}{}{\G, x \le y, x\colon \vls(A.B), \Left \Rightarrow \Right, y \colon \vls(A.B)}{\vlin{\svlef}{}{\G, x \le y, x\colon \vls(A.B), \Left \Rightarrow \Right, y \colon A}{\vlin {}{}{\G, x \le y, x\colon A,x \colon B, \Left \Rightarrow \Right, y \colon A}{\vlhy {$Por hipótesis inductiva, tamaño($A$)$\le n$$}}}}{\vlin{\svlef}{}{\G, x \le y, x\colon \vls(A.B), \Left \Rightarrow \Right, y \colon B}{\vlin {}{}{\G, x \le y, x\colon A,x \colon B, \Left \Rightarrow \Right, y \colon B}{\vlhy {$Por hipótesis inductiva, tamaño($B$)$\le n}}}}}$
		\end{center}
		\item{$A = \vls[A.B]$:}
		\begin{center}
			$\vlderivation { \vlin{\sorig}{}{\G, x\le y, x \colon \vls[A.B], \Left \Rightarrow \Right, y \colon \vls[A.B]}{\vliin {\solef}{}{\G, x\le y, x \colon \vls[A.B], \Left \Rightarrow \Right, y \colon A, y \colon B}{\vlin {}{}{\G, x\le y, x \colon A, \Left \Rightarrow \Right, y \colon A, y \colon B}{\vlhy {$Por hipótesis inductiva, tamaño($A$)$ \le n}}}{\vlin {}{}{\G, x\le y, x \colon B, \Left \Rightarrow \Right, y \colon A, y \colon B}{\vlhy {$Por hipótesis inductiva, tamaño($B$)$\le n}}}}}$
		\end{center}
		\item{$A = \square A$}
		\begin{center}
			$\vlderivation {\vlin {\sbr}
				{}
				{\G, x \le y, \Left, x \colon \square A \Rightarrow \Right, y \colon \square A}{\vlin {\sbl}
					{}
					{\G,\Left, x \le y, x \le z, zRw, x \colon \square A \Rightarrow \Right, w \colon A }
					{\vlin {\refl}
						{}
						{\G,\Left, x \le y, x \le z, zRw, x \colon \square A, w \colon A \Rightarrow \Right, w \colon A }
						{\vlin {}
							{}
							{\G,\Left, x \le y, x \le z, w \le w, zRw, x \colon \square A, w \colon A \Rightarrow \Right, w \colon A }
							{\vlhy {$Por hipótesis inductiva, tamaño($A$)$\le n}}}}}}$
		\end{center}
		\item{$A= \Diamond A$}
		\begin{center}
			$\vlderivation{\vlin {\sdl}
				{}
				{\G, \Left, x \le y, x \colon \Diamond A \Rightarrow \Right, y \colon \Diamond A}
				{\vlin {\ftwo}
					{}
					{\G, \Left, x \le y, xRz, z \colon A \Rightarrow \Right, y \colon \Diamond A}
					{\vlin {\sdr}
						{}
						{\G, \Left, x \le y, z \le u, xRz, yRu, z \colon A \Rightarrow \Right, y \colon \Diamond A}
						{\vlin {}
							{}
							{\G, \Left, x \le y, z \le u, xRz, yRu, z \colon A \Rightarrow \Right, y \colon \Diamond A, u \colon A}
							{\vlhy {$Por hipótesis inductiva, tamaño($B$)$\le n}}}}}}$
		\end{center}
	\end{itemize}
\end{proof}

%\input{chapters/simpson}

### 2020-06-01 Marianela/thesis/chapters/gklmn.tex
changing the repo structure

%\chapter{Sistema $\labIKh$ + $\agklmn$}
\section{Extensiones del sistema $\labIKh$}

%Esta sección hace referencia a trabajo futuro por terminar. 
La idea parte de generar lógicas más fuertes extendiendo nuestro sistema con otros axiomas. Decimos \emph{una lógica más fuerte} para hacer referencia a que estamos restringiendo la clase de frames que queremos considerar, imponiendo algunas restricciones en la relación de accesibilidad. En particular, nuestro objetivo es realizar esto utilizando el \emph{axioma de Scott-Lemmon} o \emph{axioma $\agklmn$}:
\begin{center}
	 $\lozenge^{k} \square^{l} A \vljm \square^{m}\lozenge^{n} A$
\end{center}

Escribiendo nuestro axioma tanto en la lógica clásica como en la intuicionista en lenguaje de primer orden obtenemos lo siguiente:

$\star$ \emph{Caso clásico} \hspace{14mm} $\rightsquigarrow$ \hspace{3.7mm}$\forall x,y,z ( xR^{k}y \vlan xR^{m}z \rightarrow \exists u yR^{l}u \vlan zR^{n}u)$

$\star$ \emph{Caso intuicionista} \hspace{3mm} $\rightsquigarrow$ \hspace{3mm} $\forall x,y,z((xR^{k}y \vlan xR^{m}z) \vljm \exists y' (y \le y' \vlan \exists u (y'R^{l}u \vlan zR^{n} u)))$\\

Para entenderlo en mayor detalle podemos observar la Figura \ref{fig:gklmn} que representa al axioma de Scott-Lemmon para el caso intuicionista la cual nos dice que:

\begin{quote}
	Sean $w$, $u$ y $v$ mundos (o etiquetas). Si $wR^k u$ y $wR^m v$ entonces existe un mundo (o etiqueta) $u'$ tal que $u \le u'$ y existe un mundo (o etiqueta) $x$ tal que $u'R^l x$ y $vR^n x$.
\end{quote}

\begin{figure}[h]
	\begin{center}
		$
		\xymatrix{
			& u' \ar@{.>}[ddr]^{R^l} \\
			& u \ar@{.>}[u]^{\le} \\
			w \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && x \\
			& v \ar@{.>}[ur]_{R^n}
		}
		$
	\end{center}
	\label{fig:gklmn}
	\caption{Axioma $\agklmn$ para el caso intuicionista}
\end{figure}

Ahora añadimos el axioma $\agklmn$ ($\agklmn$ para el caso intuicionista) y creamos una nueva regla de sequente para nuestro sistema $\labIKh$ con el objetivo de capturar el axioma en cuestión:

\begin{center}
	$\vlderivation { \vlin {\gklmn}{y', u$ fresh$}{\G, xR^{k}y, xR^{m}z, \Left \Rightarrow \Right}{\vlhy {\G, y \le y', xR^{k}y, xR^{m}z, y'R^{l}u, zR^{n}u, \Left\Rightarrow \Right}}}$
\end{center}
%\section{Completitud}

\begin{teo}
El sistema $\labIKh$ $\mathsf{+}$ $\mathsf{ axioma}$ $\agklmn$	es completo para k = l = m = n = $\mathsf{1}$.
\end{teo}

\begin{proof}
	Como resultado de la sección \emph{Completitud Sintáctica} sabemos que $\labIKh$+$\mathsf{cut}$ es completo. Por lo tanto, sólo necesitamos mostrar que el axioma $\agklmn$ se puede probar a partir de las reglas que componen a nuestro sistema.
	Primero demostraremos completitud para \emph{k = l = m = n = $\mathsf{1}$} como se ve a continuación:
	\begin{center}
		\scalebox{0.93}{
		$\vlderivation {\vlin {\sir}
			{y$ fresh$}
			{\Rightarrow x \colon \lozenge \square A \vljm \square \lozenge A}
			{\vlin {\sbr}
				{z, w $ fresh $}
				{x \le y, y \colon \lozenge \square A \Rightarrow y \colon \square \lozenge A}
				{\vlin {\sdl}
					{u$ fresh$}
					{x \le y, y \le z, zRw, y \colon \lozenge \square A \Rightarrow w \colon \lozenge A}
					{\vlin {\ftwo}
						{t$ fresh$}
						{x \le y, y \le z, zRw, yRu, u \colon \square A \Rightarrow w \colon \lozenge A}
						{\vlin {\gklmn}
							{t', j$ fresh$}
							{x \le y, y \le z, u \le t, zRw, yRu, zRt, u \colon \square A \Rightarrow w \colon \lozenge A}
							{\vlin {\sdr}
								{}
								{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A}
								{\vlin {\trans}
									{}
									{x \le y, y \le z, u \le t, t \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
									{\vlin {\sbl}
										{}
										{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A \Rightarrow w \colon \lozenge A, j \colon A}
										{\vlin {\refl}
											{}
											{x \le y, y \le z, u \le t, t \le t', u \le t', zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
											{\vlin {\ids}
												{}
												{x \le y, y \le z, u \le t, t \le t', u \le t',j \le j, zRw, yRu, zRt, t'Rj, wRj, u \colon \square A, j \colon A \Rightarrow w \colon \lozenge A, j \colon A}
												{\vlhy {}}}}}}}}}}}}$}
	\end{center}
\end{proof}

Para la demostración de completitud del caso general, necesitamos introducir las reglas que se presentan en el Lema~\ref{lemma:admis}.

\begin{lemma}\label{lemma:admis} Las siguientes reglas son admisibles en $\labIKh$:
	\begin{enumerate}
		\item{$\vlderivation {\vlin {\boxlk}{}{\G, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A\Rightarrow \Right}{\vlhy {\G, \Left, x(\le \circ $R$)^{k}y, x \colon \square^{k} A, z \colon A \Rightarrow \Right}}}$}
		\item{$\vlderivation{\vlin {\boxk}{}{\G, \Left \Rightarrow \Right, x \colon \square^{k} A}{\vlhy {\G, x(\le \circ $R$)^{k}y,\Left \Rightarrow \Right, y \colon A}}}$}
		\item{$\vlderivation { \vlin {\diamk}{}{\G, \Left, x \colon \lozenge^{k} A \Rightarrow \Right}{\vlhy {\G, xR^{k}y, \Left, y \colon A \Rightarrow \Right}}}$ }
		\item{$\vlderivation { \vlin {\diamrk}{}{\G, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A}{\vlhy {\G, \Left, xR^{k}y \Rightarrow \Right, x \colon \lozenge^{k}A, y \colon A}}}$}
	\end{enumerate}
	%\textbf{Probably F2g???}
\end{lemma}

Nuestra conjetura es que es posible demostrar completitud del sistema para el caso general, haciendo una demostración por inducción en el parámetro $k$. Esta demostración se deja como trabajo futuro.

% \begin{proof}
% 	Por inducción en k.
% 	\emph{\textbf{To be continued}}
% \end{proof}

### 2020-06-01 Marianela/thesis/chapters/labelledsyst.tex
changing the repo structure

\chapter{Sistemas de pruebas etiquetados}

Una vez que la semántica de los \emph{posibles mundos} se estableció como una base sólida para definir lógicas modales, surgió la idea de incorporar estas nociones en la teoría de la prueba de las lógicas modales. Fitch parece haber sido el primero en formalizarlo, directamente, incluyendo símbolos que representan mundos en el lenguaje de sus pruebas en deducción natural.

Los sistemas de prueba etiquetados han sido propuestos por Gabbay \cite{gabbay1996} en los años 80 como un marco unificador a través de la teoría de prueba con el fin de proporcionar sistemas de prueba para una amplia gama de lógicas. Para las lógicas modales, un ejemplo de ello  son, los sistemas de deducción natural etiquetados y sistemas de secuentes etiquetados, tales como los introducidos por Simpson \cite{simpson1994}, Vigano \cite{vigano2013} y Negri \cite{negri2005}. Estos formalismos hacen uso explícito no sólo de las etiquetas, sino también de los átomos relacionales que se refieren a la relación de accesibilidad de un modelo de Kripke. En esta sección presentaremos el cálculo de secuentes de Negri para la lógica modal clásica.

Los \emph{secuentes etiquetados} están formados por fórmulas etiquetadas de la forma $x \colon A$ y por átomos relacionales de la forma $x$R$y$, donde $x, y$ pertenecen a un conjunto de variables (llamados etiquetas) y $A$ es una fórmula modal. Un \emph{secuente etiquetado unilateral} es de la forma $\G \Rightarrow \Right$ donde $\G$ denota un conjunto de átomos relacionales y $\Right$ un conjunto de fórmulas etiquetadas.

Un sistema de pruebas simple para la lógica modal clásica K puede ser obtenido a partir del siguiente formalismo como se ve en la siguiente figura:

\vspace{3mm}

\begin{figure}[h]
	\begin{center}
			$\vlinf{\id}{}{\G \Rightarrow \Right, x \colon a, x \colon \vls-a}{}$ \hspace{25mm}	
			$\vlinf{\tolab}{}{\toprule}{}$

			$\vliinf{\vlab}{}{\G \Rightarrow \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$\hspace{9mm}
			$\vlinf{\olab}{}{\G \Rightarrow \Right, x \colon \vls[A.B]}{\olabr}$

		\hspace{8mm}$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$ \hspace{9mm} $\vlinf{\dlab}{}{\dlabr}{\dlabu}$

	\end{center}
	\caption{Sistema labK}
\end{figure}

\vspace{5mm}

\begin{teo}(\cite{negri2005}) 
	Una fórmula $A$ es demostrable en el cálculo labK si y sólo si $A$ es válida en cada frame.
\end{teo}

\newpage

### 2020-06-01 Marianela/thesis/chapters/labik.tex
changing the repo structure

\chapter{Un c\'alculo de secuentes para la l\'ogica modal intuicionista}
\label{cap:labIKh}

En los capítulos anteriores se introdujeron todos los conceptos fundamentales que resultan necesarios para comprender nuestra contribución, que presentaremos en detalle en el resto de la tesis. A lo largo de este capítulo, en diferentes secciones, presentamos un nuevo sistema de prueba etiquetado para la lógica modal intuicionista, como así también la prueba de correctitud para cada uno de las reglas que conforman el sistema en cuestión.

\input{chapters/mainproblem}
\input{chapters/newsyst}
\input{chapters/soundness}

### 2020-06-01 Marianela/thesis/chapters/logclas.tex
changing the repo structure

\chapter{Lógica modal clásica}
\label{cap:logclasica}

Usualmente, existen situaciones donde necesitamos como herramienta de modelado una lógica que tenga buenas propiedades computacionales. En estos casos, la lógica de primer orden ($\mathsf{LPO}$)~\cite{enderton72} no es la mejor alternativa. En particular, las tareas de inferencia para $\mathsf{LPO}$ no son tratables computacionalmente. Por ejemplo, el problema de determinar si una fórmula $\varphi$ de $\mathsf{LPO}$ es satisfacible, es indecidible \cite{chur:note36,turi:comp37,berg:unde66}, mientras que \emph{model checking} (es decir, dado un modelo $\M$ y una fórmula $\varphi$, determinar si $\M$ satisface $\varphi$) es $\sf{PSPACE}$-completo \cite{Stockmeyer74,chan:opti77,Vardi82}. Por este motivo, es natural buscar nuevos lenguajes con mejores propiedades computacionales. Las lógicas modales~\cite{blackburn01,blackmodal06} se encuentran dentro de esta familia de lógicas: son lógicas diseñadas para hablar de estructuras relacionales lo cual permite su utilización en diversos campos: ling\"uística, verificación de software, teoría de juegos, etc. Es por este motivo que las lógicas modales resultan una elección tan recurrente en ciencias de la computación: en general, poseen un buen balance entre expresividad y comportamiento computacional.

En este trabajo nos dedicaremos al estudio de lógicas modales intuicionistas. En este capítulo, comenzaremos por introducir las nociones básicas de la lógica modal clásica: su sintaxis, su semántica, y una discusión sobre su teoría de prueba, para luego trabajar sobre el caso intuicionista en los capítulos siguientes.

\section{Sintaxis y semántica}
El lenguaje de la lógica modal básica se obtiene extendiendo lógica proposicional clásica con los conectivos modales $\square$ y $\Diamond$, los cuales históricamente representan \textit{necesidad} y \textit{posibilidad} respectivamente.

\dfn Sea $\mathsf{PROP}$ un conjunto infinito contable de proposiciones atómicas, las fórmulas modales se construyen a partir de la siguiente gramática:
\begin{center}
	 $A ::=  a$ $| $ $\vls-a$ $ | $  $\top$ $|$ $\bot $ $|$ $\vls(A.A)$ $|$ $\vls[A.A]$ $|$  $\square A$ $|$ $\Diamond A$,
\end{center} 
\noindent donde $a \in A$ y $\vls-a$ es su negación.

Siempre asumimos que las fórmulas están en \textit{negation normal form}, esto es, la negación está restringida a los átomos. Cuando escribimos $\neg A$, nos referimos al resultado de computar la \emph{negation normal form}, utilizando las siguientes equivalencias: $\neg a \equiv \vls-a$, $\neg \vls-a \equiv a$, $\neg \neg A $ $\equiv$ $A$, $\neg (\vls(A.B))\equiv \vls[\neg A. \neg B]$ y $\neg \square A \equiv \Diamond \neg A$, donde $\equiv$ denota equivalencia. La implicación material puede ser definida a partir de este conjunto de conectivos como: $A \vljm B \coloneqq \vls[\neg A. B]$. $\top$ and $\bot$ son las constantes usuales denotando verdadero y falso respectivamente.

Como dijimos anteriormente, las fórmulas de lógica modal se interpretan sobre estructuras relacionales. Por razones históricas, dichas estructuras se conocen como modelos de Kripke \cite{kripke1959}. La semántica en términos de estos modelos se conoce como \emph{semántica de Kripke} o por la interpretación original de los operadores modales, como \emph{semántica de mundos posibles}. Intuitivamente, un modelo es un grafo dirigido con etiquetas en los nodos, y las fórmulas modales permiten expresar propiedades de estos grafos. A la estructura relacional, sin considerar las etiquetas en los nodos, se la conoce como \emph{frame}. A continuación introducimos formalmente la definición de frame y de modelo de Kripke.

\dfn(Frame) Un \textit{frame} es un par $\langle W, R\rangle$ donde $W$ es un conjunto no vacío de mundos posibles y $R$ es una relación binaria (mejor conocida como \textit{relación de accesibilidad}) tal que $R \subseteq W\times W$.

Las lógicas modales permiten describir axiomáticamente propiedades estructurales de un modelo, es decir propiedades del frame. Ejemplos de esto pueden ser reflexividad, transitividad, o simetría de la relación de accesibilidad.

Agregando valuaciones a los mundos, obtenemos los modelos de Kripke:

\dfn(Modelos de Kripke) Un \textit{modelo} $\M$ es una tupla $\langle W, R, V \rangle$, donde $\langle W, R \rangle$ es un frame, y $V : W \rightarrow 2^{\mathsf{PROP}}$ es una función de valuación, que asigna a cada mundo $w$ un conjunto de variables proposicionales que se hacen verdaderas en $w$. Sea $w \in W$, llamamos a $\M, w$ un \emph{pointed model}.

La Figura~\ref{fig:kmodel}  muestra un ejemplo de un modelo de Kripke. Podemos observar que el modelo $\M$ es un grafo con 3 elementos, $\cset{w,v,u}$. 
$w$ está etiquetado con $p$, $u$ con $p$ y $q$, y $v$ no posee etiqueta.
Formalmente, $\M{=}\tup{W,R,V}$, donde $W=\cset{w,v,u}$, $R=\cset{(w,v),(w,u),(v,v),\linebreak (v,u),(u,v)}$, y $V(w){=}\cset{p},V(u)=\cset{p, q}$.

\begin{figure}[h]
	\begin{center}
		\begin{tikzpicture}[>=latex]
		\node (a0) at (-1,0)   [shape=circle,draw,fill, inner sep=1pt,label=above left:$w$,label=below left:$\cset{p}$] {} ;
		\node (a1) at (1,1)  [shape=circle,draw,fill, inner sep=1pt, label=right:$v$] {} ;
		\node (a2) at (1,-1)  [shape=circle,draw,fill, inner sep=1pt, label=right:$u$,label=below:$\cset{p,q}$] {} ;
		\draw [ar,->] (a0) edge [bend left] (a1);
		\draw [ar,->] (a0) edge [bend right] (a2);
		\path [ar,->] (a1) edge [loop] (b0);
		\draw [ar,->] (a1) edge [bend left] (a2);
		\draw [ar,->] (a2) edge [bend left] (a1);
		\node (a3) at (-1.5,-.9)  [] {$\M$} ;
		\end{tikzpicture}
	\end{center}
	\caption{Ejemplo de un modelo de Kripke.}
	\label{fig:kmodel}
\end{figure}

Una proposición expresada por una fórmula que involucra solo los conectivos lógicos de la lógica proposicional se determina localmente sobre un mundo en particular y es independiente del estado de otros \emph{mundos}. Por otra parte, una proposición expresada por una fórmula que involucra las modalidades depende fundamentalmente del estado de otros \emph{mundos}. En un mundo \emph{w}, la fórmula $\Diamond A$ expresa la proposición de que $A$ es cierta en algún mundo $v$ considerado posible desde el punto de vista de $w$ (técnicamente, la definición de que $v$ es posible de acuerdo con $w$ será modelada por la relación de accesibilidad del modelo). Dualmente, la fórmula $\square A$ expresa la proposición (en $w$) de que $A$ es verdadera en todos los mundos $v$ considerados posibles por $w$. De este modo, el significado de las modalidades $\square$ y $\Diamond$ recibe una lectura basada en la noción primitiva de verdad relativa, es decir, verdad en un mundo.

Los operadores de la lógica modal básica describen propiedades \emph{locales} de los modelos, lo que significa que las fórmulas son evaluadas en algún punto específico. Para eso usamos \emph{pointed models}.

\dfn Sea $\M = \langle W, R, V \rangle $ un modelo, $w \in W$ y $A$ una fórmula, decimos que $\M, w $ satisface $A$ (denotado $\M, w \Vdash A$) si: %\male{se ve feo así! no te parece?}
	$$
	\begin{array}{rcl}

 \M, w \Vdash a & \mbox{sii} & a \in V(w)\\

	\M, w \Vdash \vls-a& \mbox{sii} & a \not \in V(w)\\

	\M, w \Vdash A \vlan B & \mbox{sii} & \M, w \Vdash A\mbox{ y }\M, w \Vdash B \\

	\M, w \Vdash A \vlor B & \mbox{sii} & \M, w \Vdash A\mbox{ o }\M, w \Vdash B \\

	\M, w \Vdash \square A & \mbox{sii} & \mbox{para todo } v \in W \mbox{ tal que } wRv \mbox{ y } \M, v \Vdash A \\

	\M, w \Vdash \Diamond A & \mbox{sii} & \mbox{existe } v \in W \mbox{ tal que } wRv \mbox{ y } \M, v \Vdash A \\
\end{array}$$
%\hspace{9mm}	$\M, w \Vdash a$ si y sólo si $a \in V(w)$

%\hspace{9mm}	$\M, w \Vdash \vls-a$ si y sólo si $a \not \in V(w)$

%\hspace{9mm}	$\M, w \Vdash \vls(A.B)$ si y sólo si $\M, w \Vdash A$ y $\M, w \Vdash B$

%\hspace{9mm} $\M, w \Vdash \vls[A.B]$ si y sólo si $\M, w \Vdash A$ o $\M, w \Vdash B$

%\hspace{9mm} $\M, w \Vdash \square A$ si y sólo si para todo $v \in W$ tal que $(w, v) \in $ R y $\M, v \Vdash A$

%\hspace{9mm} $\M, w \Vdash \Diamond A$ si y sólo si existe un $v \in W$ tal que $(w, v) \in R$ y $\M, v \Vdash A$

\vspace{1mm}

Una fórmula $A$ es satisfacible si existe un pointed model $\M, w$ tal que $\M,w \Vdash A$. Diremos que una fórmula $A$ es válida en un modelo (notación $\M \vDash A$) $\M$ si y sólo si en todos los estados $w \in W$ vale $\M, w \Vdash A$.

Notemos la correspondencia entre $\square$ y el cuantificador $\forall$, así como también la correspondencia entre el operador $\Diamond$ y el cuantificador $\exists$. En particular, podemos identificar a la lógica modal clásica como un fragmento de la lógica de primer orden clásica simplemente internalizando su semántica en $\mathsf{LPO}$.

Como se mencionó anteriormente, en este trabajo nos interesa estudiar los teoremas y sus demostraciones, en particular, de la lógica modal intuicionista. Para ello veremos las demostraciones como objetos formales. Existen diferentes tipos de sistemas de pruebas para un lenguaje lógico, cada uno con ciertas características particulares. Por ejemplo, los sistemas \emph{á la Hilbert} en general consisten de un conjunto de axiomas, y unas pocas reglas que permiten inferir teoremas a partir de axiomas. En contrapartida, en los sistemas \emph{á la Gentzen} predominan las reglas de inferencia por sobre los axiomas. A continuación presentaremos ambos tipos de sistemas para la lógica modal clásica.
% Podemos definir la satisfabilidad de una fórmula de la siguiente manera:

% \dfn(Satisfabilidad y Validez de una fórmula) Una formula $A$ se \emph{satisface} en un modelo $M$=$\langle W, R, V \rangle$ si existe  $w \in W$ tal que $\M, w \Vdash A$. Lo denotaremos con $\M, w\vDash A$. Diremos que una fórmula $A$ es \emph{válida} en un modelo $\M$ si para todo $w \in W$, $\M, w \vDash A$. Lo denotamos con $\M \vDash A$

%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Axiomatizaciones \emph{á la Hilbert}}

Presentaremos a la lógica modal básica y su teoría como la llamada lógica modal $\K$. La misma se obtiene a partir de una axiomatización arbitraria de la lógica proposicional clásica, agregando los siguientes componentes:

\begin{itemize}
	\item la regla de \textit{necesitación:} si $A$ es un teorema de $\K$, entonces $\square A$ también lo es.
	\item el axioma de \textit{distributividad}, normalmente escrito de la siguiente forma:
		\begin{center}
		$\kaxiom$ $\colon$ $\square(A \vljm B) \vljm (\square A \vljm \square B)$.
		\end{center}
\end{itemize}

Es importante mencionar que lo que llamamos un axioma aquí es de hecho, como es estándar en las axiomatizaciones al estilo de Hilbert, un esquema de axiomas, para evitar una mención explícita de la regla de sustitución. Más concretamente, una derivación es una lista de fórmulas que son instancias de algunos esquemas de axiomas dados o deducciones de fórmulas anteriores combinadas usando una regla de inferencia. Además, como estamos aceptando el esquema del axioma $k$ en nuestro sistema base, todas las lógicas que consideramos pertenecen a la familia de las \emph{lógicas modales normales}. Se pueden obtener lógicas modales más fuertes agregando a $\K$ otros axiomas que contienen los conectivos modales. Una clase de axiomas modales que serán de nuestro interés han sido propuestos por Lemmon y Scott en \cite{lemmon1977}. Estos axiomas denominados \emph{de Scott-Lemmon} están definidos esquemáticamente por una 4-upla de números naturales $\langle h, i, j, k \rangle$ como:
\begin{center}
	$\mathsf{\mbox{g}_{hijk}} := \Diamond^{h} \square^{i} A \vljm \square^{j}  \Diamond^{k} A$,
\end{center}
donde $\square^{n}$ denota $n$ ocurrencias de $\square$ ($ \Diamond^{n}$ denota $n$ ocurrencias de $\Diamond$). Notemos que en el caso clásico $\mathsf{\mbox{g}_{hijk}}$ y $\mathsf{\mbox{g}_{jkhi}}$ son equivalentes por De Morgan.

Consideraremos también una subclase particular de estos axiomas llamados \emph{path Scott-Lemmon axioms} que corresponden al caso donde $i + k$ es exactamente igual a 1. Por ejemplo, obtenemos el siguiente axioma:

\begin{center}
		$\mathsf{\mbox{g}_{h1j0}} := \Diamond^{h} \square A \vljm \square^{j} A$
\end{center}

Algunas ocurrencias específicas del axioma de Scott-Lemmon se han estudiando con distintos nombres, como por ejemplo:

  $$
\begin{array}{rcl}
	\mathsf{\mbox{g}_{0001}} & \mbox{corresponde al axioma} & \taxiom := A \vljm \Diamond A \\

	\mathsf{\mbox{g}_{0011}} & \mbox{corresponde al axioma} & \baxiom := A \vljm \square \Diamond A \\

	\mathsf{\mbox{g}_{0101}} & \mbox{corresponde al axioma} & \daxiom := \square A \vljm \Diamond A \\

	\mathsf{\mbox{g}_{1002}} & \mbox{corresponde al axioma} & \fouraxiom := \Diamond A \vljm \Diamond \Diamond A \\

	\mathsf{\mbox{g}_{1011}} & \mbox{corresponde al axioma} & \fiveaxiom := \Diamond A \vljm \square \Diamond A \\

	\mathsf{\mbox{g}_{1111}} & \mbox{corresponde al axioma} & \twoaxiom := \Diamond \square A \vljm \square \Diamond A
\end{array}
$$

Podemos notar que $\taxiom$, $\baxiom$, $\fouraxiom$ y $\fiveaxiom$ son \emph{path Scott-Lemmon axioms}, pero $\daxiom$ y $\twoaxiom$ no lo son.

Seleccionando subconjuntos de estos axiomas nos permite \emph{a priori} definir treinta y dos lógicas modales. Sin embargo, algunas de ellas coinciden. Por ejemplo, los conjuntos $\{ \baxiom, \fouraxiom \}$ y $\{ \taxiom, \fiveaxiom\}$ ambos dan como resultado la lógica modal conocida como $\sfive$. Se obtienen quince lógicas modales distintas que se extienden entre $\K$ y $\sfive$ y se pueden representar en un cubo, como se muestra en la Figura \ref{fig:cubesfive}. Este cubo es conocido como el \emph{cubo $\sfive$}.

\begin{figure}[h]
	\begin{center}
	\begin{tikzpicture}
	[every node/.style={inner sep=1pt,outer sep=0},
	logic/.style={shape=circle,draw}]
	\def\xx{4.5}\def\hxx{2}\def\hhxx{2}
	\def\yy{4}\def\hyy{2}\def\hhyy{1}
	\def\zz{-4}\def\hzz{-2}\def\hhzz{-1}
	\node[logic,label=225:K]   (ik)   at (0, 0, 0)            {} ;
	\node[logic,label=-45:KB]  (ikb)  at (\xx, 0, 0)          {} ;
	\node[logic,label=-45:KB5] (ikb5) at (\xx, 0, \zz)        {} ;
	\node[logic,label=170:K4]  (ik4)  at (0, 0, \zz)          {} ;
	\node[logic,label=180:D]   (id)   at (0, \hyy, 0)         {} ;
	\node[logic,label=135:T]   (it)   at (0, \yy, 0)          {} ;
	\node[logic,label=135:S4]  (is4)  at (0, \yy, \zz)        {} ;
	\node[logic,label=45:S5]   (is5)  at (\xx, \yy, \zz)      {} ;
	\node[logic,label=-45:TB]  (itb)  at (\xx, \yy, 0)        {} ;
	\node[logic,label=0:DB]    (idb)  at (\xx, \hyy, 0)       {} ;
	\node[logic,label=135:D4]  (id4)  at (0, \hyy, \zz)       {} ;
	\node[logic,label=-45:D45] (id45) at (\hxx, \hyy, \zz)    {} ;
	\node[logic,label=-45:K45] (ik45) at (\hxx, 0, \zz)       {} ;
	\node[logic,label=-10:D5]  (id5)  at (\hhxx, \hyy, \hhzz) {} ;
	\node[logic,label=-10:K5]  (ik5)  at (\hhxx, 0, \hhzz)    {} ;
	\draw[line width=.6pt,color=black!40]
	(ik) -- (ik4) -- (id4) (ik4) -- (ik45) ;
	\draw[line width=.7pt,color=black!60]
	(ik45) -- (ikb5)
	(id) -- (id4) -- (is4) (id4) -- (id45) -- (id5) -- (id)
	(ik) -- (ik5) -- (ik45) -- (id45) (ik5) -- (id5)
	(id45) to[bend left] (is5) ;
	\draw[line width=.8pt]
	(ik) -- (ikb) -- (ikb5) -- (is5) -- (is4) -- (it) -- (id) -- (ik)
	(it) -- (itb) -- (is5)
	(itb) -- (idb) -- (ikb)
	(id) -- (idb) ;
	\end{tikzpicture}
	\end{center}
	\caption{Cubo $\sfive$}
	\label{fig:cubesfive}
\end{figure}

%\male{Definir el problema de SAT y VAL?}
%Como se mencionó al comienzo de la sección, la lógica modal tiene mejores propiedades computacionales que la lógica de primer orden. En efecto, una vez introducida la definición de satisfabilidad, queremos destacar que este problema de determinar si una fórmula es satisfacible o no en la lógica modal, es decidible y su complejidad es {\sc PSPACE}-complete.

%\dfn (Validez de una fórmula) Una fórmula $A$ es \emph{válida} en un frame $\F = \langle W, R \rangle$ si para cada función de valuación $V$ se tiene que $\langle W, R, V \rangle \vDash A$. Lo denotamos con $\F \vDash A$.

%Con esta definición presentada anteriormente para \emph{validez}, surgen varias preguntas naturales con respecto a las relaciones entre las lógicas modales y las clases de frames.

 La sintáxis y la semántica descripta en la Sección 2.1 se vinculan mediante el hecho de que la lógica $\K$ es correcta y completa con respecto a la clase de todos los \emph{frames}.

\begin{teo}(\cite{kripke1963}). 
	Una fórmula $A$ es un teorema de $\K$ si y sólo si $A$ es válida en cada frame. 
\end{teo}

Además, el poder de esta construcción es que este enlace no está restringido a $\K$: algunas clases de fórmulas modales corresponden a propiedades específicas de frames. Una forma alternativa, entonces, para obtener lógicas modales más fuertes que $\K$ es restringiendo la clase de frames que queremos considerar, imponiendo algunas restricciones en la relación de accesibilidad.

\section{Axiomatizaciones \emph{á la Gentzen}}
A pesar de que la noción de pruebas dada para un sistema axiomático \emph{á la Hilbert} es claro y amigable, encontrar una prueba para un teorema específico puede resultar muy complicado. Uno de los objetivos del formalismo de cálculo de secuentes propuesto por Gentzen es brindar una forma más intuitiva de estudiar las pruebas.

En el caso clásico, definimos un \emph{secuente} $\Right = A_{1}, ..., A_{n}$ como un conjunto de fórmulas donde la coma representa la unión. Una \emph{regla de secuentes} es una expresión de la forma:

\begin{center}
$\vlderivation{\vlinf{}{}{S}{S_{1}$ ... $S_{n}}}$,
\end{center}

\noindent tal que $n \geq 0$, y el secuente $S$, la \emph{conclusión}, puede deducirse de los secuentes $S_{1}$ ... $S_{n}$ llamados \emph{premisas}.

Una \emph{derivación}, denotada con $\D$, es construida de acuerdo a estas reglas; tendrá una estructura de un árbol, donde cada arista es un secuente y cada nodo interno es una regla. Una derivación es una \emph{prueba} de un secuente en la raíz, si cada hoja es una regla sin premisas. La altura de una derivación $\D$, denotada por $ht(\D)$, es la altura de $\D$ vista como un árbol, es decir, la longitud del camino más largo en el árbol desde su raíz hasta una de sus hojas.

Diseñar un sistema de secuentes \emph{completo} y \emph{correcto} para una lógica dada significa definir el conjunto correcto de reglas de secuentes, de manera que cada fórmula válida de la lógica en cuestión tenga una prueba en el sistema de secuentes (\emph{completitud}), y que cualquier prueba que pueda construirse en el sistema de secuentes deriva una fórmula válida de la lógica (\emph{correctitud}).

Decimos que una regla es \emph{admisible} por un sistema $\system$ si, siempre que sus premisas son demostrables en $\system$, existe una prueba de su conclusión en $\system$. Decimos que es \emph{derivable} si existe una derivación en $\system$ de sus premisas a su conclusión, posiblemente utilizando premisas varias veces.

\subsection{Sistemas de secuentes etiquetados}

Una vez que la semántica de los \emph{mundos posibles} se estableció como una base sólida para definir lógicas modales, surgió la idea de incorporar estas nociones en la teoría de la prueba de las mismas. Una de las primeras formalizaciones de este tipo fue introducida por Fitch \cite{fitch1948} incluyendo símbolos que representan mundos posibles, dentro del lenguaje de sus pruebas en deducción natural.

Los sistemas de prueba etiquetados han sido propuestos por Gabbay \cite{gabbay1996} en los años 80, como un marco unificador para proporcionar sistemas de prueba para una amplia gama de lógicas. Para las lógicas modales, un ejemplo de ello  son los sistemas de deducción natural etiquetados y sistemas de secuentes etiquetados, tales como los introducidos por Simpson \cite{simpson1994}, Vigano \cite{vigano2013} y Negri \cite{negri2005}. Estos formalismos hacen uso explícito no sólo de etiquetas, sino también de átomos relacionales que se refieren a la relación de accesibilidad de un modelo de Kripke. En esta sección presentaremos el cálculo de secuentes de Negri para la lógica modal clásica.

Los \emph{secuentes etiquetados} están formados por fórmulas etiquetadas de la forma $x \colon A$ y por átomos relacionales de la forma $xRy$, donde $x, y$ pertenecen a un conjunto de variables (llamados etiquetas) y $A$ es una fórmula modal. Un \emph{secuente etiquetado unilateral} es de la forma $\G \Rightarrow \Right$ donde $\G$ denota un conjunto de átomos relacionales y $\Right$ un conjunto de fórmulas etiquetadas. \emph{Labels} será el conjunto de variables llamadas etiquetas.

Un sistema de pruebas simple para la lógica modal clásica $\K$ puede ser obtenido a partir del formalismo presentado en la Figura \ref{fig:labK}.

\begin{figure}[!h]
	\begin{center}
		$\vlinf{\id}{}{\G \Rightarrow \Right, x \colon a, x \colon \vls-a}{}$ \hspace{25mm}	
		$\vlinf{\tolab}{}{\toprule}{}$

		\vspace{8mm}
		$\vliinf{\vlab}{}{\G \Rightarrow \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$\hspace{9mm}
		$\vlinf{\olab}{}{\G \Rightarrow \Right, x \colon \vls[A.B]}{\olabr}$

		\vspace{8mm}
		\hspace{8mm}$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$ \hspace{9mm} $\vlinf{\dlab}{}{\dlabr}{\dlabu}$

	\end{center}
	\caption{Sistema $\labK$}
	\label{fig:labK}
\end{figure}

Las reglas de la Figura \ref{fig:labK} hacen uso de etiquetas para expresar explícitamente la semántica de una fórmula en un estado en particular. Expliquemos más en detalle la regla para la conjunción, la regla para el box y la regla para el diamante:

\begin{itemize}
	\item Regla $\vlab$.

	La regla propuesta en el sistema $\labK$ para la conjunción es la que se observa a continuación:
	\begin{center}
		$\vliinf{\vlab}{}{\G \Rightarrow \Right, x :\vls(A.B)}{\vlabr}{\vlabu}$
	\end{center}
	Dado $\G$ un conjunto de átomos relacionales y dado $\Right$ un conjunto de fórmulas etiquetadas, esta regla (leyendo desde la conclusión hacia las premisas) semánticamente nos dice que si $A \vlan B$ se satisface en $x$, entonces en $x$ debe valer $A$ y en $x$ también debe ser verdadera $B$.

	\item Regla $\blab$.

	El caso del $\square$ queda representado en el sistema $\labK$ con la regla que vemos a continuación:
	\begin{center}
		$\vlinf{\blab}{y$ fresh$}{\blabr}{\blabu}$
	\end{center}
	Nuevamente dado $\G$ un conjunto de átomos relacionales y dado $\Right$ un conjunto de fórmulas etiquetadas, la regla para el $\square$ expresa semánticamente que si en $x$ es verdadera la fórmula $\square A$ (conclusión de la regla) entonces si existe una etiqueta (o mundo) $y$ tal que $xRy$, la fórmula $A$ es verdadera en $y$. Cabe destacar que cuando decimos \emph{existe una etiqueta (o mundo) $y$}, no utilizamos el existe como cuantificador, si no que hacemos referencia a $y fresh$. Es decir, $y$ es una nueva etiqueta que no estaba presente en la conclusión de la regla.

	\item Regla $\dlab$:

	Para representar el operador $\Diamond$, el sistema $\labK$ presenta la siguiente regla:

	\begin{center}
		$\vlinf{\dlab}{}{\dlabr}{\dlabu}$
	\end{center}

	Al igual que en las reglas anteriores, dado $\G$ un conjunto de átomos relacionales y dado $\Right$ un conjunto de fórmulas etiquetadas, la regla para el $\Diamond$ expresa semánticamente (leyendo desde la conclusión hacia las premisas) que dado mundos $x, y$ tal que $xRy$ entonces en $x$ se satisface $\Diamond A$, tenemos que la fórmula $A$ se hace verdadera en $y$.
\end{itemize}

De esta manera queda reflejado cómo el uso de etiquetas nos provee una correspondencia casi directa entre expresiones sintácticas y su semántica, haciendo la teoría de prueba mucho más intuitiva. Por ejemplo, en \cite{Brauner07} se discuten los beneficios de las etiquetas en la teoría de prueba modal.

Concluímos este capítulo enunciando el siguiente resultado:

\begin{teo}(\cite{negri2005}) 
	Una fórmula $A$ es demostrable en el cálculo $\labK$ si y sólo si $A$ es válida en cada frame.
\end{teo}

### 2020-06-01 Marianela/thesis/chapters/mainproblem.tex
changing the repo structure

\section{El problema principal}

Como se dijo anteriormente, nuestro trabajo consiste en la definición de un sistema de prueba etiquetado para lógicas modales intuicionistas. La extensión directa de la deducción etiquetada al entorno intuicionista consiste en la utilización de dos tipos de átomos relaciones: uno para la relación de accesibilidad modal representada con $R$, y otro para la relación intuicionista o mejor conocida como relación de preorden $\le$. Esto resulta interesante ya que nos permite poner el sistema de prueba en estrecha relación con la semántica birelacional de Kripke que se detalló en el Capítulo~\ref{cap:logintuicionista}.

En \cite{negri2005} se introdujo un cálculo de secuentes etiquetado para la lógica modal básica. En este trabajo extenderemos dicho sistema con el objetivo de capturar lógicas modales intuicionistas. Además de las fórmulas etiquetadas de la forma $x \colon A$, y de las expresiones $xRy$, capturando la relación de accesibilidad (donde $x, y$ pertenecen a un conjunto de etiquetas, y $A$ es un fórmula), utilizaremos expresiones del tipo $x \le y$ para capturar la relación de preorden intuicionista. De una manera más formal introducimos la siguiente definición:

%La idea es extender un cálculo de secuentes etiquetado con un símbolo de relación de preorden con el objetivo de capturar lógicas modales intuicionistas; esto quiere decir, buscamos definir secuentes etiquetados intuicionistas a partir de fórmulas etiquetadas $x \colon A$, de la relación de accesibilidad modal $x$R$y$, y la nueva relación de preorden de la forma $x \le y$, donde $x, y$ pertenecen a un conjunto de etiquetas y $A$ es una fórmula modal intuicionista. El cálculo de secuentes etiquetado en el cual nos basamos fue el propuesto por Negri para la lógica modal básica \cite{negri2005}.

\dfn{Un \emph{secuente etiquetado intuicionista} es de la forma $\G$, $\Left \Rightarrow \Right$ donde $\G$ denota un conjunto de átomos relacionales y de preorden, y  $\Left$ y $\Right$ son conjuntos de fórmulas etiquetadas. }

\vspace{2mm}

De esta manera obtenemos el sistema de prueba $\labIKh$ para lógicas modales intuicionistas en este formalismo, y podemos demostrar el siguiente teorema:

\begin{quote}
 \emph{Una fórmula $A$ es demostrable en el cálculo $\labIKh$ si y sólo si $A$ es válida en cada frame bi-relacional.}
\end{quote}

La dirección de izquierda a derecha de la sentencia anterior indica que el cálculo es \emph{correcto}: las reglas me permiten inferir solo fórmulas válidas. Por otro lado, la implicación de derecha a izquierda se conoce como \emph{completitud}: todos los teoremas son demostrables en el cálculo.

En la siguiente sección, se presenta el nuevo sistema de cálculo de secuentes etiquetados para las lógicas modales intuicionistas.

### 2020-06-01 Marianela/thesis/chapters/soundness.tex
changing the repo structure

\section{Corrección de $\labIKh$}

Como se mencionó anteriormente, debemos mostrar que el sistema introducido tiene dos propiedades. Por un lado, es necesario demostrar que es un sistema completo (como se verá en el Capítulo~\ref{cap:completeness}, y por otro lado, debemos asegurar que es correcto. Esto último quiere decir que cada una de las reglas de secuentes que posee nuestro sistema $\labIKh$ es correcta. Formalmente:

\begin{center}
	\emph{Para todo modelo $\M$, si $\M$ satisface la premisa entonces $\M$ satisface la conclusión.}
\end{center}

Para poder demostrar la sentencia anterior, primero necesitamos introducir algunas definiciones y notación:

\dfn{Sea $\M = \langle W, R, \le, V \rangle$ un modelo, una \emph{función de asignación} es una $\f : Labels \rightarrow W$, que a cada etiqueta ( en inglés label) le asigna un mundo en el modelo $\M$.
%\raul{nunca definiste Labels. Introducir ese nombre cuando se introducen sistemas etiquetados por primera vez.}
\dfn Sea $\M = \langle W, R, \le, V \rangle$ un modelo y sea $\G, \Left \Rightarrow \Right$ un secuente. Decimos que $\M \Vdash \G, \Left \Rightarrow \Right$ si existe una función de asignación $\f$ tal que:
\medskip
 Si se cumplen:
\begin{enumerate}
	\item Para todo $x \colon A \in \Left$ tenemos que $\M, f(x) \Vdash A$ (Notación: $\M \Vdash \Left$)
	\item Para todo $xRy \in \G$ tenemos que $f(x)Rf(y)$ (Notación: $\M \Vdash \G$)
	\item Para todo $x \le y \in \G$ tenemos que $f(x) \le f(y)$ (Notación: $\M \Vdash \G$)
\end{enumerate}
Entonces para todo $z \colon B \in \Right$ tenemos que $\M, f(z) \Vdash B$ (Notación: $\M \Vdash \Right$).
Diremos que $\M \not \Vdash \G, \Left \Rightarrow \Right$ si no es cierto que $\M \Vdash \G, \Left \Rightarrow \Right$.}

\medskip
Siguiendo estas definiciones, en esta sección demostramos que todas las reglas presentadas en la Figura \ref{fig:labIKheart} son correctas. Como la prueba es similar para cada una de las reglas, demostramos la correctitud de algunas reglas particulares:

\begin{itemize}
\item {Regla $\svlef$}:

Sea $\svlef$ la regla izquierda para la conjunción definida en la Figura~\ref{fig:labIKheart}:

\begin{center}
		$\vlinf{\svlef}{}{\G,\Left, x \colon \vls(A.B) \Rightarrow \Right}{\conjlef}$
\end{center}

Queremos ver que es correcta. Aplicando la definición, queremos ver que:

\begin{center}
\emph{Para todo modelo $\M$, si $\M \Vdash \conjlef$, entonces $\M \Vdash \G, \Left, x \colon A \vlan B \Rightarrow \Right$.}

\end{center}

Para demostrar este enunciado lo hacemos a partir del uso de la contrarrecíproca, es decir queremos ver que si un existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left, x \colon \vls(A.B) \Rightarrow \Right$, entonces $\M_{0} \not \Vdash \conjlef$. Asumimos la primera parte de la implicación y tenemos que $\M_{0} \not \Vdash \G, \Left, x \colon \vls(A.B) \Rightarrow \Right$, es decir, por un lado tenemos que $\M_{0} \Vdash \G$, $\M_{0} \Vdash \Left$ y $\M_{0} \Vdash x \colon \vls(A.B)$, y por otro lado, $\M_{0} \not \Vdash \Right$. Como dijimos, en particular tenemos que $\M_{0} \Vdash x \colon \vls (A.B)$.  Por definición, obtenemos que $\M_{0} \Vdash x \colon A$ y $\M_{0} \Vdash x \colon B$. Finalmente, concluimos que, por un lado: $\M_{0} \Vdash \G$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \colon A$ y $\M_{0} \Vdash x \colon B$ y por otro lado, $\M_{0} \not \Vdash \Right$, que es lo mismo que $\M_{0} \not \Vdash \conjlef $. Por lo tanto, la regla $\svlef$ del sistema $\labIKh$ es correcta.

\item {Regla $\sorig$}:

Sea la regla $\sorig$ propuesta para el sistema $\labIKh$ la siguiente:

\begin{center}
	$\vlinf{\sorig}{}{\G, \Left \Rightarrow \Right, x \colon \vls[A.B]}{\G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B}$
\end{center}

Queremos ver la correctitud de esta regla. Más precisamente, queremos ver que:

\begin{center}
	\emph{Para todo modelo $\M$, si $\M \Vdash \G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B$, entonces $\M \Vdash \G, \Left \Rightarrow \Right, x \colon A \vlor B$.}
\end{center}

Para esta prueba utilizamos la contrarrecíproca, es decir, deseamos ver que, si existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left \Rightarrow \Right, x \colon \vls[A.B]$, entonces $\M_{0} \not \Vdash \G, \Left \Rightarrow \Right, x   \colon   A, x   \colon   B$. Asumimos entonces que $\M_{0} \not \Vdash \G, \Left \Rightarrow \Right, x \colon \vls[A.B]$, es decir, tenemos que por un lado $\M_{0} \Vdash \G$ y $\M_{0} \Vdash \Left$, y por otro, $\M_{0} \not \Vdash \Right$ y $\M_{0} \not \Vdash x \colon \vls[A.B]$. Por definición de $\Vdash$ para $\M_{0} \not \Vdash x \colon \vls[A.B]$ tenemos que $\M_{0} \not \Vdash A$ y $\M_{0} \not \Vdash B$. Por lo tanto, vimos por un lado que $\M_{0} \Vdash \G$ y $\M_{0} \Vdash \Left$, y por otro lado, vimos que $\M_{0} \not \Vdash \Right$, $\M_{0} \not \Vdash x \colon A$ y $\M_{0} \not \Vdash x \colon B$. Estas observaciones pueden reescribirse de la siguiente forma: $\M_{0} \not \Vdash \G, \Left \Rightarrow \Right, x \colon A, x \colon B$. Luego, queda demostrado que la regla $\sorig$ es correcta.

\item{Regla $\sbr$}:

La regla presentada en la Figura \ref{fig:labIKheart} para $\sbr$ es la siguiente:

\begin{center}
$\vlinf{\sbr}{}{\G, \Left \Rightarrow \Right, x \colon \square A}{\G, \Left, x \le y, yRz \Rightarrow \Right, x \colon \square A, z \colon A}$
\end{center}

Queremos saber si esta regla es correcta. Utilizando la definición de corrección que vimos anteriormente queremos ver que:
\begin{center}
	\emph{Para todo modelo $\M$, si $\M \Vdash \G, \Left, x \le y, yRz \Rightarrow \Right, x \colon \square A, z \colon A$, entonces $\M \Vdash \G, \Left \Rightarrow \Right, x \colon \square A.$}
\end{center}

Asumimos que existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left \Rightarrow \Right, x \colon \square A$ y queremos ver que $\M_{0} \not \Vdash \G, \Left, x \le y, y$R$z \Rightarrow \Right, x \colon \square A, z \colon A$. De nuestra hipótesis obtenemos que $\M_{0} \Vdash \G$ y $\M_{0} \Vdash \Left$, y también que $\M_{0} \not \Vdash \Right$ y $\M_{0} \not \Vdash x: \square A$. Por definición de $\M_{0},x \not \Vdash \square A $ tenemos que existen mundos $y, z$ pertenecientes a $\M_{0}$, tal que $x \le y$, $yRz$ donde $\M_{0}\not \Vdash z \colon A$. Por lo tanto, $\M_{0} \not \Vdash \G, \Left, x \le y, yRz \Rightarrow \Right, x \colon \square A, z \colon A$. Finalmente, utilizando la contrarrecíproca queda demostrado que la regla $\sbr$ es correcta.

\item {Regla $\sdr$}:

La regla presentada en la Figura \ref{fig:labIKheart} para $\sdr$ es la siguiente:

\begin{center}
	$\vlinf{\sdr}{}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A}{\G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A}$
\end{center}

Al igual que como se demostró para $\sbr$, queremos saber si la regla $\sdr$ es correcta. Para ello, volvemos a utilizar la definición de corrección para esta regla en cuestión. Es decir, correctitud para la regla derecha del diamante $\sdr$ es:

\begin{center}
	\emph{Para todo modelo $\M$, si $\M \Vdash \G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A$, entonces $\M \Vdash \G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A$.}
\end{center}

Utilizando la contrarrecíproca a la definición planteada, asumimos que existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A$ y queremos ver que $\M_{0} \not \Vdash \G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A$. Desglosando nuestra hipótesis tenemos que $\M_{0} \Vdash \G$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash xRy$, $\M_{0} \not \Vdash \Right$ y $ \M_{0} \not \Vdash x: \Diamond A$. Por definición de $\M_{0} \not \Vdash x: \Diamond A$ tenemos que para todo mundo $y$ en $\M_{0}$ donde $xRy$, $\M_{0} \not \Vdash y \colon A$. Por lo tanto, podemos concluir que $\M_{0} \not \Vdash \G, \Left, xRy \Rightarrow \Right, x \colon \Diamond A, y \colon A$.

\item {Regla $\sdl$}:

La regla presentada en la Figura \ref{fig:labIKheart} para la regla del diamante izquierda (denotada con $\sdl$) es la siguiente:

 \begin{center}  
$\vlinf{\sdl}{}{\G, \Left, x: \Diamond A \Rightarrow \Right}{\G, \Left, x$R$y,  y \colon A \Rightarrow \Right}$
\end{center}

Siguiendo el mismo criterio que venimos utilizando para las reglas anteriores para la prueba de corrección, definimos corrección para $\sdl$:

\begin{center}
	\emph{Para todo modelo $\M$, si $\M \Vdash \G, \Left, xRy,  y \colon A \Rightarrow \Right$, entonces $\M \Vdash \G, \Left, x: \Diamond A \Rightarrow \Right$.}
\end{center}

Para probar este enunciado, utilizamos la contrarrecíproca: asumimos que existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left, x: \Diamond A \Rightarrow \Right$, y queremos ver que $\M_{0} \not \Vdash \G, \Left, xRy,  y \colon A$. De $\M_{0} \not \Vdash \G, \Left, x: \Diamond A \Rightarrow \Right$ tenemos que $\M_{0} \Vdash \G$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \colon \Diamond A$ y $\M_{0} \not \Vdash \Right$. Por $\M_{0}, x \Vdash \Diamond A$ sabemos que existe un mundo $y$ en $\M_{0}$ tal que $xRy$ y $\M_{0}, y \Vdash A$. Por lo tanto, $\M_{0} \not \Vdash \G, \Left, xRy,  y \colon A \Rightarrow \Right$.

\item {Regla $\sbl$}:

La regla para $\sbl$ presentada en nuestro sistema $\labIKh$ es la siguiente:

\begin{center}
	$\vlinf{\sbl}{}{\G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right}{\G,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right}$
\end{center}

Queremos ver que esta regla es correcta. Para ello, así como hicimos con las reglas anteriores, lo que queremos demostrar es:

\begin{center}
	\emph{Para todo modelo $\M$, si $\M \Vdash \G,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$, entonces $\M \Vdash \G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$.}
\end{center}

La prueba de este enunciado la hacemos a partir del uso de la contrarrecíproca, es decir, lo que queremos ver es que si existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash conclusion$, entonces $\M_{0} \not \Vdash premisa$. Más particularmente para nuestra regla: si existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$, entonces $\M_{0} \not \Vdash \G,\Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.

Asumimos entonces que existe un modelo $\M_{0}$ tal que $\M_{0} \not \Vdash \G, \Left, x \le y, yRz, x \colon \square A \Rightarrow \Right$, es decir $\M_{0} \Vdash \G$, $\M_{0} \Vdash \Left$, $\M_{0} \Vdash x \le y$, $ \M_{0} \Vdash yRz$, $\M_{0} \Vdash x\colon \square A$ y  $\M_{0} \not \Vdash \Right$. Por lo tanto, en particular de $\M_{0} \Vdash \square A$ tenemos que para todo mundo $y, z$ tal que $x \le y$ y $yRz$, $\M_{0}, f(z) \Vdash A$, o lo que es lo mismo $\M_{0} \Vdash z \colon A$. Finalmente obtenemos que $\M_{0} \not \Vdash \G, \Left, x \le y, yRz, x \colon \square A, z \colon A \Rightarrow \Right$.

\end{itemize}

La corrección del resto de las reglas puede demostrarse de manera similar. De esta forma podemos concluir:

\begin{teo} El sistema $\labIKh$ es correcto.\end{teo}

Las siguientes secciones serán dedicadas a demostrar la otra propiedad que buscamos, es decir, que el sistema $\labIKh$ es completo.

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
changing the repo structure
intro done

--- 2020-06-01 bicolor NS/aiml20/aiml20.tex
@@
 %\usepackage[matrix,arrow]{xy}
-\usepackage[noxy]{virginialake}
+\usepackage[noxy]{../../virginialake}
 %\vlnosmallleftlabels
@@
 \begin{frontmatter}
-  \title{Fully structured proof theory \\for intuitionistic modal logics \\(working title)}
+  \title{Fully structured proof theory for intuitionistic modal logics}
   \author{Sonia Marin}
@@
 
-\todo{sell the systems! more emphasis in the nested sequent system?}
+Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.
 
-Structural proof theoretic accounts of intuitionistic modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction and labelled sequent systems~\cite{simpson1994}, or the one of \emph{unlabelled deduction} in the form of sequent~\cite{bierman2000} or nested sequent systems~\cite{strassburger2013} (for a survey see~\cite[Chap.~3]{marin2018}).
-In this article, we present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing the accesibility relation for modal logics and the intuitionistic relation $\le$.
-In the labelled calculus we made explicity both relations with $\rel$ and $\le$ into the system.
-In the nested sequent system, we represent this relations with one bracket in a sequent (for the accesibility relation) and a with two brackets in a sequent (preorder relation).
+These generalisations of the sequent framework, inspired by relational semantics, are needed to treat modalities uniformly. 
+%
+By extending the ordinary sequent structure with \emph{one} extra element, either relational atoms between labels or nested bracketing, they encode respectively graphs or trees in the sequents, giving them enough power to represent modalities.
 
-\section{Intuitionistic modal logics}
-The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
+Similarly, proof systems have been designed for intuitionistic modal logic both as labelled sequent systems~\cite{simpson1994} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara}.
+%
+Surprisingly, in both settings, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.
+
+This no longer matches the relational semantics of these logics, which requires to combine the relation for intuitionistic propositional logic and the one for modal logic. 
+%
+More importantly, it leads to deductive systems that are not entirely satisfactory; they cannot as modularly capture axiomatic extensions (or equivalently restricted semantical conditions) and, in particular, can only provide decision procedures for a handful of them~\cite{simpson1994}.
+
+This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing both the modal accesibility relation and the intuitionistic pre-order relation. 
+%
+A fully labelled framework, described succintly in Section~\ref{sec:labelled}, has already allowed us to obtain modular systems for all intuitionistic Scott-Lemmon logics~\cite{marin:morales:strassburger:hal}.
+%
+In an attempt to make this system amenable for proof-search and decision procedures, we have started investigated a fully nested framework, presented in Section~\ref{sec:nested}.
+
+%We present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing both the modal accesibility relation and the intuitionistic pre-order relation. 
+%
+%In the labelled calculus we made explicity both relations with $\rel$ and $\le$ into the system. 
+%
+%In the nested sequent system, we represent this relations with one bracket in a sequent (for the accesibility relation) and a with two brackets in a sequent (preorder relation).  
+%
+
+\section{Intuitionistic modal logic}
+The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$.
+%standing most generally for \emph{necessity} and \emph{possibility}.
 %
@@
 \fm A \coloncolonequals
-\fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm{\TOP} \mid \fm{\BOT} \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
+\fm a \mid \fm{\BOT} \mid \fm{(A \AND A)} \mid \fm{(A \OR A)} \mid \fm{(A \IMP A)} \mid \fm{\BOX A} \mid \fm{\DIA A}
 $$
 %
-The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{plotkin1986} and is equivalent to the one proposed by Fischer-Servi~\cite{fischer1984}.
+The axiomatisation of intuitionistic modal logic $\IK$ \cite{plotkin1986,fischer1984}
 %, and by Ewald~\cite{Ewald} in the case of intuitionistic tense logic. 
 %
-It is obtained from intuitionistic propositional logic by adding:
+is obtained from intuitionistic propositional logic by adding:
 \begin{itemize}
@@
 
-The relational semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer1984}.
-%
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
+The relational semantics for $\IK$~\cite{fischer1984} combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic.
+% using two distinct relations on the set of worlds.
 
 \begin{definition}
-	A \emph{bi-relational frame} $\F$ is a triple $\langle W, R, \le \rangle$ 
+	A \emph{bi-relational frame} $\F$ consists %is a triple $\langle W, R, \le \rangle$ 
 	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
@@
 	\begin{enumerate}
-		\item[($F_1$)] For $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs{v}{v'}$, there exists $\lb{u'}$ s.t.~$\futs{u}{u'}$ and $\accs{u'}{v'}$.
+		\item[($F_1$)] For $\lb x, \lb y, \lb z \in W$, if $\accs xy$ and $\futs yz$, there exists $\lb u$ s.t.~$\futs xu$ and $\accs uz$.
 
-		\item[($F_2$)] For $\lb{u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb{v'}$ s.t.~$\accs{u'}{v'}$ and $\futs{v}{v'}$.
+		\item[($F_2$)] For $\lb x, \lb y, \lb z \in W$, if $\futs xy$ and $\accs xz$, there exists $\lb u$ s.t.~$\accs yu$ and $\futs zu$.
 	\end{enumerate}
@@
 
-%\marianela{We recall the birelational models \cite{plotkin1986, ewald1986} for intuitionistic modal logics, which are a combination of the Kripke semantics for propositional intuitionistic logic and the one for classical modal logic.
-A \emph{birelational frame} $\F = \langle W, R, \le \rangle$ is a non-empty set $W$ of worlds together with two binary relations $\le, \rel \subseteq W \times W$, where $\le$ is a preorder(i.e., reflexive and transitive), such that the following two conditions hold:}
+\begin{definition}
+	A \emph{bi-relational model} $\M$ is %a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ 
+	a bi-relational frame and a monotone valuation function $V\colon W \to 2^\mathcal{A}$.%, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to: if $\futs{w}{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
+\end{definition}
+
+We write $\lb x \Vdash \fm a$ if $\fm a \in V(\lb x)$ and, by definition, it is never the case that $\lb x \Vdash \fm{\BOT}$. %and always have $\lb w \Vdash \fm{\TOP}$
+%
+The relation $\Vdash$ is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
+\begin{align}
+	&\lb x \Vdash \fm{A \AND B} && \text{iff}\qquad 
+	\lb x \Vdash \fm A \text{ and } \lb x \Vdash \fm B
+	\nonumber\\
+	&\lb x \Vdash \fm{A \OR B} && \text{iff}\qquad 
+	\lb x \Vdash \fm A \text{ or } \lb x \Vdash \fm B
+	\nonumber\\
+	&\lb x \Vdash \fm{A \IMP B} && \text{iff}\qquad 
+	\text{for all } \lb y \text{ with } \futs xy\text{, if }\lb y \Vdash \fm A\text{ then }\lb y \Vdash \fm B
+	\nonumber\\
+	&\lb x \Vdash \fm{\BOX A} && \text{iff}\qquad
+	\text{for all }\lb y\text{ and }\lb z\text{ with }\futs xy\text{ and }\accs yz, \lb z \Vdash \fm A %\hfill $(\ast)$
+	\tag{$\star$}\label{eq:box}\\
+	&\lb x \Vdash \fm{\DIA A} && \text{iff}\qquad
+	\text{there exists a }\lb y\text{ such that }\accs xy\text{ and }\lb y \Vdash \fm A
+	\nonumber
+\end{align}
 
 \begin{definition}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
-	if $\futs{w}{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
-\end{definition}
-
-We write $\lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and by definition, we always have $\lb w \Vdash \fm{\TOP}$ and never that $\lb w \Vdash \fm{\BOT}$. 
+%	A formula $\fm A$ is \emph{satisfied} in a model $\langle W, R, \le, V \rangle$, if for all $\lb w \in W$ we have $\lb w \Vdash \fm A$.
 	%
-Then the relation is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
-
-$\lb w \Vdash \fm{A \AND B}$ iff $\lb w \Vdash \fm A$ and $\lb w \Vdash \fm B$
-
-$\lb w \Vdash \fm{A \OR B}$ iff $\lb w \Vdash \fm A$ or $\lb w \Vdash \fm B$
-
-$\lb w \Vdash \fm{A \IMP B}$ iff for all $\lb{w'}$ with $\futs{w}{w'}$, if $\lb{w'} \Vdash \fm A$ then $\lb{w'} \Vdash \fm B$
-
-$\lb w \Vdash \fm{\BOX A}$ iff for all $\lb{w'}$ and $\lb u$ with $\futs{w}{w'}$ and $\accs{w'}{u}$, $\lb u \Vdash \fm A$ %\hfill $(\ast)$
-
-$\lb w \Vdash \fm{\DIA A}$ iff there exists a $\lb u$ such that $\accs wu$ and $\lb u \Vdash \fm A$.
-
-\begin{definition}
-	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, R, \le, V \rangle$, if for all $\lb w \in W$ we have $\lb w \Vdash \fm A$.
-	%
-	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, R, \le \rangle$, if for all valuations $V$, $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
+	A formula $\fm A$ is \emph{valid} in a frame $\langle W, R, \le \rangle$, if for all monotone valuations $V$ and for all $\lb w \in W$, we have $\lb w \Vdash \fm A$
 \end{definition}
@@
 
-\begin{theorem}[Fischer-Servi~\cite{fischer1984}, Plotkin and Stirling~\cite{plotkin1986}]\label{thm:plotkin}
+\begin{theorem}[\cite{fischer1984,plotkin1986}]\label{thm:plotkin}
 	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
@@
 
-\section{Labelled sequent calculi with $\rel$ and $\le$}
+\section{Fully labelled sequent calculus}\label{sec:labelled}
 
@@
 			\begin{tabular}{@{\!}c@{\quad}c}
-				$\vlinf{\rn{id}}{}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{A} }{}$
+				$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A} }{}$
 				&
@@
 
-\emph{Labelled deduction} has been proposed by Gabbay~\cite{gabbay1996} in the 80s as a unifying framework throughout proof theory in order to provide proof
-systems for a wide range of logics. 
+%\emph{Labelled deduction} has been proposed by Gabbay~\cite{gabbay1996} in the 80s as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics. 
 %
-For modal logics it can take
-the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson~\cite{simpson1994}, Vigan\`o~\cite{vigano2000}, and Negri~\cite{negri2005}. 
+%For modal logics it can take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson~\cite{simpson1994}, Vigan\`o~\cite{vigano2000}, and Negri~\cite{negri2005}.
 %
-Simpson's proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
+Simpson's~\cite{simpson1994} proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
 %
@@
 %
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ as proposed by Maffezioli, Naibo and Negri in~\cite{maffezioli2013}.
+The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ (similarly to~\cite{maffezioli2013} for epistemic logic). 
 %
@@
 \begin{definition}
-	A two-sided intuitionistic \emph{labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $\accs xy$ and preorder atoms $\futs xy$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $\lb x$ and $\lb y$ taken from the set of labels and $A$ an intuitionistic modal formula).
+	A two-sided intuitionistic \emph{fully labelled sequent} is of the form $\B, \Left \SEQ \Right$ where $\B$ denotes a set of relational atoms $\accs xy$ and preorder atoms $\futs xy$, and $\Left$ and $\Right$ are multi-sets of labelled formulas $\labels{x}{A}$ (for $\lb x$ and $\lb y$ taken from a countable set of labels and $A$ an intuitionistic modal formula).
 \end{definition}
@@
 %
-In particular, the rules introducing the $\BOX$-operator correspond to the definition $(\ast)$.
+In particular, the rules introducing the $\BOX$-operator correspond to the definition~\eqref{eq:box}.
 %
@@
 		%		
-		%		\todo{}
 		\smash{%\fbox{
@@
 
-%We show that each rule from our system is sound.
-%
-%We also present a syntactic completeness proof with respect the Hilbert system: we prove all Hilbert axioms using the rules from our system (i.e.
-proof of all propositional intuitionistic axioms, the five variants of k axiom from the intuitionistic syntax, simulate the necessitation rule and simulate modus ponens).
-%
-%We present a completeness proof for our system $\labIKp$ using the Simpson system. 
-%
-%The idea comes from knowing that the Simpson system is a Cut-free system, so this proof lets us know that our system is complete without the cut rule. 
-%
-%We show the proof by case analysis. 
-%
-%Most of the rules from Simpson system are the same as the rules in the system $\labIKp$, then we prove for the rules that are different.
-
-%The proof is a careful adaptation of standard techniques.
+The proof is a careful adaptation of standard techniques (see~\cite{marin:morales:strassburger:hal}).
 %%
@@
 
-\section{Bicolor NS: nested sequents capturing $\rel$ and $\le$}
-\marianela{small introduction of nested sequents}
-Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
+\section{Fully nested sequent calculus}\label{sec:nested}
+
+%Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
 %
@@
 \[
-\vlinf{\rrn{mon}}{}{\Cx[1]{\bBR{\rt A, \Cx[2]}}}{\Cx[1]{\rt A, \bBR{\Cx[2]}}}
+\vlinf{\rrn{mon}}{}{\Cx[1]{\bBR{\rt A, \Cx[2]}}}{\Cx[1]{\rt A, \bBR{\rt A, \Cx[2]}}}
 \quad
@@
 
-In~\cite{Simpson}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
+In~\cite{simpson1994}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
 %

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
complete draft

@@
 
-%\usepackage[matrix,arrow]{xy}
+\usepackage[matrix,arrow]{xy}
 \usepackage[noxy]{../../virginialake}
@@
 In an attempt to make this system amenable for proof-search and decision procedures, we have started investigated a fully nested framework, presented in Section~\ref{sec:nested}.
+%
+We would be particularly interested in a suitable system for logic $\mathsf{IS4}$ whose decidability is not known.
 
@@
 %
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted $\fm a$, modal formulas are constructed from the grammar:
+Starting with a set $\mathcal{A}$ of atomic propositions, denoted $\fm a$, modal formulas are constructed from the grammar:\vspace*{-.1cm}
 %
@@
 	\item the \emph{necessitation rule}: $\fm{\BOX A}$ is a theorem if $\fm{A}$ is a theorem; and
-	\item the following five variants of the \emph{distributivity axiom}:
+	\item the following five variants of the \emph{distributivity axiom}:\vspace*{-.1cm}
 	\begin{equation*}
@@
 
-The relational semantics for $\IK$~\cite{fischer1984} combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic.
+%The relational semantics for intuitionistic modal logic combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic.
 % using two distinct relations on the set of worlds.
@@
 \begin{definition}
-	A \emph{bi-relational frame} $\F$ consists %is a triple $\langle W, R, \le \rangle$ 
+	A \emph{bi-relational frame} consists %is a triple $\langle W, R, \le \rangle$ 
 	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
@@
 \begin{definition}
-	A \emph{bi-relational model} $\M$ is %a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ 
-	a bi-relational frame and a monotone valuation function $V\colon W \to 2^\mathcal{A}$.%, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to: if $\futs{w}{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
+	A \emph{bi-relational model} is %a quadruple $\langle W, R,\le,V \rangle$ with $\langle W, R, \le \rangle$ 
+	a bi-relational frame with a monotone valuation function $V\colon W \to 2^\mathcal{A}$.%, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to: if $\futs{w}{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
 \end{definition}
@@
 %
-The relation $\Vdash$ is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:
+The relation $\Vdash$ is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:\vspace*{-.1cm}
 \begin{align}
@@
 
-Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
+%Similarly to the classical case, in the case of $\IK$, the correspondence between syntax and semantics is recovered.
 
@@
 				\\
-				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
+				$\vlinf{\rn{refl_\le}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
 				&
-				$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
+				$\vlinf{\rn{trans_\le}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
 				\\\\
@@
 %
-Simpson's~\cite{simpson1994} proposed labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
+%Simpson's~\cite{simpson1994} labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
 %
-Echoing the definition of bi-relational structures, we consider another extension of labelled deduction to the intuitionistic setting. 
+Echoing the definition of bi-relational structures, we consider an extension of labelled deduction to the intuitionistic setting
 %
-The idea is to use two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ (similarly to~\cite{maffezioli2013} for epistemic logic). 
+that uses two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ (similarly to~\cite{maffezioli2013} for epistemic logic). 
 %
@@
 %
-Most rules are similar to the ones of Simpson~\cite{simpson1994}, but some rules are even more explicitly in correspondence with the semantics by using the preorder atoms. 
+Most rules are similar to the ones of Simpson~\cite{simpson1994}, but some are more explicitly in correspondence with the semantics by using the preorder atoms. 
 %
-In particular, the rules introducing the $\BOX$-operator correspond to the definition~\eqref{eq:box}.
+For instance, the rules introducing the $\BOX$-connective correspond to the definition~\eqref{eq:box}.
 %
@@
 
-The proof is a careful adaptation of standard techniques (see~\cite{marin:morales:strassburger:hal}).
+The proof is a careful adaptation of standard techniques (see~\cite{marin:morales:strassburger:hal} for details).
 %%
@@
 
-%Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
-%
-Nested sequents are a generalisation of sequents from a multiset
-of formulas to a tree of multisets of formulas.
-In nested sequent notation, brackets are used to indicate the parent-child relation in the tree, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$).
-for intuitionistic logic we need two-sided sequents, which are formally generated by:
-\begin{center}
-	$\Cx \coloncolonequals \lf{A_{1}}, ..., \lf{A_{n}}, \rt{B_{1}},..., \rt{B_{k}}, \BR{\Cx[1]},..., \BR{\Cx[m]}$
-\end{center}
-
-where $\fm{A_{1}}, .
-.
-.
-, \fm{A_{n}}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $\fm{B_{1}}, .
-.
-.
-, \fm{B_{k}}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], .
-.
-.
-, \Cx[m]$ are nested sequents.
-We use the $\bullet$ and $\circ$ as polarities indication for formulas.
-
-In order to capture intuitionistic modal logics, we build a nested sequent system with the two relations explicitly: one of for the accessibility relation $\rel$ associated with the Kripke semantics for normal modal logics (represented with one bracket in the sequent) and one for the preorder relation $\le$ associated with the Kripje semantics for intuitionistic logic (represented with two brackets in the system).
-
-In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
-$\force{\lb x}{\fm{\BOX A}}$ iff for all $\lb y$ and $\lb z$ s.t.
-$\futs xy$ and $\accs yz$, $\force{\lb z}{\fm{A}}$.
-Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
-
-\begin{center}
-	$\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
-	\quad
-	\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}$
-\end{center}
-
-\marianela{add F1 rule?}
-
 \begin{figure}%[h]
@@
 
-\marianela{explain some specific rules: $\rrn\BOX$, $\rrn\IMP$. maybe $\rn F_1$?}
+%Nested sequents were introduced by Kashima \cite{kashima1994cut} and then independently rediscovered by Br\"{u}nnler \cite{brunnler2009deep} and Poggiolesi \cite{poggiolesi2009method}.
+%
+%Nested sequents are a generalisation of sequents from a multiset of formulas to a tree of multisets of formulas.
+%
+In standard nested sequent notation, brackets are used to indicate the parent-child relation in the modal accessibility tree. 
+%, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$). 
+%
+Here again, we enhance the structure with a second type of bracketting to encode the preorder relation.
+%For intuitionistic logic we need two-sided sequents, which are formally generated by:
+%$\Cx \coloncolonequals \lf{A_{1}}, ..., \lf{A_{n}}, \rt{B_{1}},..., \rt{B_{k}}, \BR{\Cx[1]},..., \BR{\Cx[m]}$
+%where $\fm{A_{1}}, .
+.
+.
+, \fm{A_{n}}$ are the formulas that would occur on the left of the turnstile if there was a turnstile, $\fm{B_{1}}, .
+.
+.
+, \fm{B_{k}}$ are the formulas that would occur on the right of the turnstile if there was a turnstile, and $\Cx[1], .
+.
+.
+, \Cx[m]$ are nested sequents.
+We use the $\bullet$ and $\circ$ as polarities indication for formulas.
 
-\sonia{Say that teh meta theoretic result ie cut-elimination is much harder}
+\begin{definition}
+	A two-sided intuitionistic \emph{fully nested sequent} is constructed from the grammar:
+	$$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$$
+	where the $\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow.
+\end{definition}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The obtained nested sequent calculus $\nIKp$ is displayed in Figure~\ref{fig:nIK}.
+%
+The idea is similar to the fully labelled calculus but the shift of paradigm forced us to make different design choices.
+%
+In particular, the underlying tree-structure prevents us to express the rule $\rn{F_2}$, but its absence is compensated by the \emph{monotonicity rules} $\lrn{mon}$ and $\rrn{mon}$ which were admissible in $\labIKp$.
+%
+Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need equivalent here.
 
-\section{Extensions}
-
-\marianela{say something like the idea comes from proving termination for is4...}
-
-\paragraph{Labelled}
-
-In~\cite{simpson1994}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
+A great interest of a nested system is that the rules for axiomatic extensions are usually more suitable for proof-search procedures that in the labelled setting.
 %
-For example, you can add the following rule:
-$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
-to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-In~\cite{plotkin1986}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%
-For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%\begin{center}
-($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%\end{center}
-
-Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
-
-Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
-%
-These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
-
-\paragraph{Nested}
-Replace $\lrn\BOX$ and $\rrn\DIA$ above by the following:
-\[
+Previous nested systems for intuitionistic modal logics~\cite{strassburger2013,kuznets:strassburger:maehara} can be extended from $\IK$ to $\mathsf{IS4}$ by simply adding the following rules:
+\[\small
 \vlinf{\lrn[t]\BOX}{}{\Cx{\lf{\BOX A}}}{\Cx{\lf{\BOX A}, \lf A}}
@@
 \]
+
+%In order to capture intuitionistic modal logics, we build a nested sequent system with the two relations explicitly: one of for the accessibility relation $\rel$ associated with the Kripke semantics for normal modal logics (represented with one bracket in the sequent) and one for the preorder relation $\le$ associated with the Kripje semantics for intuitionistic logic (represented with two brackets in the system).
+
+%In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
+%$\force{\lb x}{\fm{\BOX A}}$ iff for all $\lb y$ and $\lb z$ s.t.
+$\futs xy$ and $\accs yz$, $\force{\lb z}{\fm{A}}$.
+Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
+%
+%\begin{center}
+%	$\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
+%	\quad
+%	\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}$
+%\end{center}
+%
+%\marianela{add F1 rule?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\section{Extensions}
+%
+%\paragraph{Labelled}
+%
+%the frame
+%condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
+%inference rule
+%\begin{equation}
+%\label{eq:Rtrans}
+%\vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+%	\B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
+%\end{equation}
+%where $\B$ stands for a set of relational atoms, and $\Gamma$ and
+%$\Delta$ for multi-sets of labelled formulas.
+%
+%The transitivity rule in~\eqref{eq:Rtrans} can be axiomatised by the conjunction of the two
+%versions of the $\ax 4$-axiom
+%\begin{equation}
+%\label{eq:4ax}
+%\fm{\BOX A\IMP \BOX\BOX A}
+%\qquad
+%\fm{\DIA\DIA A\IMP\DIA A}
+%\quad
+%\end{equation}
+%which are equivalent in classical
+%modal logic. However, in intuitionistic modal logic they are not
+%equivalent, and even though the logic $\IK\ax 4$, i.e., the
+%intuitionistic version of the modal logic $\K\ax 4$, contains both
+%axioms, they can also be added independently to the logic $\IK$ (an
+%intuitionistic version of $\K$). The proof theory of these
+%new logics has not been studied before; no existing labelled (or
+%label-free) proof system can handle them, even though the
+%corresponding frame conditions
+%\begin{equation}
+%\label{eq:4frame}
+%\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
+%\quad
+%\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
+%\;,
+%\end{equation}
+%%  \todo{add graphical representation of the conditions}
+%$$
+%\xymatrix{
+%	x' \ar@{.>}[drr]^R \\
+%	x \ar@{.>}[u]^\le \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z
+%}
+%\qquad\qquad
+%\xymatrix{
+%	&& z''  \\
+%	x  \ar@{.>}[urr]^R \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z \ar@{.>}[u]^\le
+%}
+%$$
+%respectively, have already been studied
+%in~\cite{plotkin:stirling:86}.
+%
+%In~\cite{simpson1994}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
+%%
+%For example, you can add the following rule:
+%$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
+%to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
+%$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
+%
+%In~\cite{plotkin1986}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
+%%
+%For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
+%%\begin{center}
+%($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
+%%\end{center}
+%
+%Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
+%$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
+%
+%Consequently, we can easily translate the frame
+%conditions in~\eqref{eq:4frame} into inference rules:
+%\begin{equation}
+%\label{eq:4rules}
+%\vlinf{\rn{4^{\BOX}}}{\text{\footnotesize$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+%	\B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
+%\qquad
+%\vlinf{\rn{4^{\DIA}}}{\text{\footnotesize$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+%	\B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
+%\end{equation}
+%This allows us to define cut-free deductive systems for a wide range
+%of logics that could not be treated before.
+%
+%%Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
+%%%
+%%These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
+%
+%
+%\paragraph{Nested}
+%Replace $\lrn\BOX$ and $\rrn\DIA$ above by the following:
+%\[
+%\vlinf{\lrn[t]\BOX}{}{\Cx{\lf{\BOX A}}}{\Cx{\lf{\BOX A}, \lf A}}
+%\quad
+%%\vlinf{\lrn[2]\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf{\BOX A}, \Cx[2]}}}}
+%\vlinf{\lrn[4]\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf{\BOX A}, \Cx[2]}}}
+%\quad
+%\vlinf{\rrn[t]\DIA}{}{\Cx{\rt{\DIA A}}}{\Cx{\rt{\DIA A}, \rt A}}
+%\quad
+%\vlinf{\rrn[4]\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt{\DIA A}, \Cx[2]}}}
+%\]
 %\[\mbox{\hbox to .9\linewidth{\dotfill}}\]

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
complete draft with Sec 5

@@
 
-This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing both the modal accesibility relation and the intuitionistic pre-order relation. 
+This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing both the modal accesibility relation and the intuitionistic preorder relation. 
 %
@@
 
-%We present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing both the modal accesibility relation and the intuitionistic pre-order relation. 
+%We present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing both the modal accesibility relation and the intuitionistic preorder relation. 
 %
@@
 	\text{for all }\lb y\text{ and }\lb z\text{ with }\futs xy\text{ and }\accs yz, \lb z \Vdash \fm A %\hfill $(\ast)$
-	\tag{$\star$}\label{eq:box}\\
+	\label{eq:box}\\
 	&\lb x \Vdash \fm{\DIA A} && \text{iff}\qquad
@@
 		%
-		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
+%		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
 	\end{enumerate}
@@
 	A two-sided intuitionistic \emph{fully nested sequent} is constructed from the grammar:
-	$$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$$
+	$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$,
+	%
+%	\noindent
 	where the $\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow.
@@
 Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need equivalent here.
-
-A great interest of a nested system is that the rules for axiomatic extensions are usually more suitable for proof-search procedures that in the labelled setting.
-%
-Previous nested systems for intuitionistic modal logics~\cite{strassburger2013,kuznets:strassburger:maehara} can be extended from $\IK$ to $\mathsf{IS4}$ by simply adding the following rules:
-\[\small
-\vlinf{\lrn[t]\BOX}{}{\Cx{\lf{\BOX A}}}{\Cx{\lf{\BOX A}, \lf A}}
-\quad
-%\vlinf{\lrn[2]\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf{\BOX A}, \Cx[2]}}}}
-\vlinf{\lrn[4]\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf{\BOX A}, \Cx[2]}}}
-\quad
-\vlinf{\rrn[t]\DIA}{}{\Cx{\rt{\DIA A}}}{\Cx{\rt{\DIA A}, \rt A}}
-\quad
-\vlinf{\rrn[4]\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt{\DIA A}, \Cx[2]}}}
-\]
 
@@
 
-%\section{Extensions}
+\section{Extensions: example of transitivity}
+
+As mentionned in the introduction, one of our motivation is to investigate decision procedure for axiomatic extensions of $\IK$, for instance for $\mathsf{IS4}$, intuitionistic logic of reflexive transitive frames.
 %
+So, we will illustrate the benefit of our approach on transitivity here.
+
 %\paragraph{Labelled}
 %
-%the frame
-%condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
+%The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
 %inference rule
@@
 %$\Delta$ for multi-sets of labelled formulas.
+
+The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be axiomatised by the conjunction of the two versions of the $\ax 4$-axiom:\vspace*{-.2cm}
+%\begin{equation*}
+%\label{eq:4ax}
+$$
+\ax{4_{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
+\qquad\qquad\qquad
+\ax{4_{\DIA}}\colon\fm{\DIA\DIA A\IMP\DIA A}
+$$%\end{equation*}
 %
-%The transitivity rule in~\eqref{eq:Rtrans} can be axiomatised by the conjunction of the two
-%versions of the $\ax 4$-axiom
-%\begin{equation}
-%\label{eq:4ax}
-%\fm{\BOX A\IMP \BOX\BOX A}
-%\qquad
-%\fm{\DIA\DIA A\IMP\DIA A}
-%\quad
-%\end{equation}
-%which are equivalent in classical
-%modal logic. However, in intuitionistic modal logic they are not
-%equivalent, and even though the logic $\IK\ax 4$, i.e., the
-%intuitionistic version of the modal logic $\K\ax 4$, contains both
-%axioms, they can also be added independently to the logic $\IK$ (an
-%intuitionistic version of $\K$). The proof theory of these
-%new logics has not been studied before; no existing labelled (or
-%label-free) proof system can handle them, even though the
-%corresponding frame conditions
-%\begin{equation}
-%\label{eq:4frame}
-%\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
-%\quad
-%\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-%\;,
-%\end{equation}
-%%  \todo{add graphical representation of the conditions}
+which are equivalent in classical modal logic. 
+%
+However, in intuitionistic modal logic they are not and they can be added independently to the logic $\IK$. %(an intuitionistic version of $\K$). 
+%
+From~\cite{plotkin1986} we know they are in correspondance with the following frame conditions:\vspace*{-.2cm}
+\begin{equation}
+\label{eq:4frame}
+\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs x{u}\AND\accs {u}z)
+\quad
+\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs z{u}\AND\accs {x}{u})
+\end{equation}
+%  \todo{add graphical representation of the conditions}
 %$$
 %\xymatrix{
-%	x' \ar@{.>}[drr]^R \\
+%	u \ar@{.>}[drr]^R \\
 %	x \ar@{.>}[u]^\le \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z
@@
 %\xymatrix{
-%	&& z''  \\
+%	&& u  \\
 %	x  \ar@{.>}[urr]^R \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z \ar@{.>}[u]^\le
@@
 %$$
-%respectively, have already been studied
-%in~\cite{plotkin:stirling:86}.
+%respectively%, have already been studied in~\cite{plotkin:stirling:86}.
+
+Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule:\vspace*{-.2cm}
 %
-%In~\cite{simpson1994}, Simpson extends his basic sequent system for $\IK$ to the geometric axiom family. 
-%%
 %For example, you can add the following rule:
-%$$\scalebox{.9}{$\vlinf{\boxbrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$}$$
+$$\small
+\vlinf{\rn{4}}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
 %to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
 %$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-%
+
 %In~\cite{plotkin1986}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
@@
 %%\end{center}
+
+Incorporating the preorder symbol into the syntax, however,  allowed us to %also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
+%$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
+%Consequently, we can easily 
+translate the conditions in~\eqref{eq:4frame} into independent inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:\vspace*{-.2cm}
+\begin{equation*}\small
+\label{eq:4rules}
+\vlinf{\rn{4_{\BOX}}}{\text{\footnotesize$\lb{u}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+	\B, \accs xy, \accs yz, \accs {u}z, \futs x{u},\Left \SEQ \Right}
+\quad
+\vlinf{\rn{4_{\DIA}}}{\text{\footnotesize$\lb{u}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
+	\B, \accs xy, \accs yz, \accs {x}{u}, \futs z{u},\Left \SEQ \Right}  
+\end{equation*}
+%This allows us to define cut-free deductive systems for a wide range of logics that could not be treated before.
+
+%Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
+%%
+%These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
+
+A great interest of a nested system is that the rules for axiomatic extensions are usually more suitable for proof-search procedures that in the labelled setting.
 %
-%Incorporating the preorder symbol into the syntax of our sequents allows us to also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-%$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
-%
-%Consequently, we can easily translate the frame
-%conditions in~\eqref{eq:4frame} into inference rules:
-%\begin{equation}
-%\label{eq:4rules}
-%\vlinf{\rn{4^{\BOX}}}{\text{\footnotesize$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-%	\B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
-%\qquad
-%\vlinf{\rn{4^{\DIA}}}{\text{\footnotesize$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-%	\B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
-%\end{equation}
-%This allows us to define cut-free deductive systems for a wide range
-%of logics that could not be treated before.
-%
-%%Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
-%%%
-%%These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
-%
-%
-%\paragraph{Nested}
-%Replace $\lrn\BOX$ and $\rrn\DIA$ above by the following:
-%\[
+Previous nested systems for intuitionistic modal logics~\cite{strassburger2013,kuznets:strassburger:maehara} can be extended from $\IK$ to $\mathsf{IK4}$ by simply adding the following rules:\vspace*{-.2cm}
+\[\small
 %\vlinf{\lrn[t]\BOX}{}{\Cx{\lf{\BOX A}}}{\Cx{\lf{\BOX A}, \lf A}}
 %\quad
-%%\vlinf{\lrn[2]\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf{\BOX A}, \Cx[2]}}}}
-%\vlinf{\lrn[4]\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf{\BOX A}, \Cx[2]}}}
+%\vlinf{\lrn[2]\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf{\BOX A}, \Cx[2]}}}}
+\vlinf{\lrn[4]\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf{\BOX A}, \Cx[2]}}}
 %\quad
 %\vlinf{\rrn[t]\DIA}{}{\Cx{\rt{\DIA A}}}{\Cx{\rt{\DIA A}, \rt A}}
-%\quad
-%\vlinf{\rrn[4]\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt{\DIA A}, \Cx[2]}}}
-%\]
-%\[\mbox{\hbox to .9\linewidth{\dotfill}}\]
-%\[
-%\vlinf{\rn{refl_{\BR{\cdot}}}}{}{\Cx[1]{\Cx[2]}}{\Cx[1]{\BR{\Cx[2]}}}
-%\qquad
-%\vlinf{\rn{trans_{\BR{\cdot}}}}{}{\Cx[1]{\BR{\Cx[2], \BR{\Cx[3]}}}}{\Cx[1]{\BR{\Cx[2]}, \BR{\Cx[3]}}}
-%\]
+\quad
+\vlinf{\rrn[4]\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt{\DIA A}, \Cx[2]}}}
+\]
+
+The generalisation of these results to our fully structured framework is subject of ongoing study.
 

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
correction of intro

@@
 %
-We would be particularly interested in a suitable system for logic $\mathsf{IS4}$ whose decidability is not known.
+We would be particularly interested in a suitable system for logic $\mathsf{IS4}$, whose decidability is not known, and discuss this direction in Section~\ref{sec:extensions}.
 
@@
 
-\section{Extensions: example of transitivity}
+\section{Extensions: example of transitivity}\label{sec:extensions}
 
@@
 %
-So, we will illustrate the benefit of our approach on transitivity here.
+We will therefore illustrate the benefit of our approach taking transitivity as a test-case.
 
@@
 
-Incorporating the preorder symbol into the syntax, however,  allowed us to %also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
+Incorporating the preorder symbol into the syntax, however,  allowed us~\cite{marin:morales:strassburger:hal} to %also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
 %$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
 %Consequently, we can easily 
-translate the conditions in~\eqref{eq:4frame} into independent inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:\vspace*{-.2cm}
+translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:\vspace*{-.2cm}
 \begin{equation*}\small

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
correction of spacing

@@
 %
-For instance, the rules introducing the $\BOX$-connective correspond to the definition~\eqref{eq:box}.
+For instance, the rules introducing the $\BOX$-connective correspond to~\eqref{eq:box}.
 %
-Furthermore, our system has to incorporate the two semantic conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and the rules $\rn{refl}$ and $\rn{trans}$ are also necessary to ensure that the preorder atoms do behave as a preorder relation on labels.
+Furthermore, our system must incorporate the conditions ($F_1$) and ($F_2$) into the deductive rules $\rn{F_1}$ and $\rn{F_2}$, and rules $\rn{refl_\le}$ and $\rn{trans_\le}$ are necessary to ensure that the preorder atoms behave as a preorder on labels.
 %
@@
 $$\small
-\vlinf{\rn{4}}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
+\vlinf{\rn{trans}_\rel}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
 %to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom

### 2020-06-02 BicolorNS/aiml20/aiml20.tex
improving Sec 4

@@
 %
-In standard nested sequent notation, brackets are used to indicate the parent-child relation in the modal accessibility tree. 
+In standard nested sequent notation, brackets $\BR{\cdot}$ are used to indicate the parent-child relation in the modal accessibility tree.
 %, and can be interpreted as the modal $\BOX$ (similarly to how the comma is interpreted as $\OR$). 
 %
-Here again, we enhance the structure with a second type of bracketting to encode the preorder relation.
+$\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow.
+
+To make it fully structured again, we enhance the structure with a second type of bracketting $\bBR{\cdot}$ to encode the preorder relation.
 %For intuitionistic logic we need two-sided sequents, which are formally generated by:
@@
 We use the $\bullet$ and $\circ$ as polarities indication for formulas.
+%
 
@@
 	A two-sided intuitionistic \emph{fully nested sequent} is constructed from the grammar:
-	$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$,
-	%
-%	\noindent
-	where the $\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow.
+	$\Cx \coloncolonequals \varnothing \mid \lf A, \Cx \mid \rt A, \Cx \mid \BR{\Cx} \mid \bBR{\Cx}$
 \end{definition}
@@
 %
-Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need equivalent here.
+Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need any equivalent here.
 

### 2020-07-01 BicolorNS/aiml20/aiml20.tex
working on the final version: answering review 1

@@
 \section{Introduction}
+\marianela{I added in the first paragraph the labelled natural deduction with three cites referencing the classical case.
+I did that so then in the third paragraph I added the reference of Galmiche and Sahli.}
+%Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.
 
-Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.
+Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of labelled natural deduction~\cite{fitting1983,prawitz1965,siemens1977} and labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.
 
@@
 
-Similarly, proof systems have been designed for intuitionistic modal logic both as labelled sequent systems~\cite{simpson1994} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara}.
+Similarly, proof systems have been designed for intuitionistic modal logic as labelled sequent systems~\cite{simpson1994}, labelled natural deduction systems~\cite{galmiche2010} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara}.
 %
-Surprisingly, in both settings, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.
+Surprisingly, in nested and labelled sequents, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.
+
+\marianela{If we want to make an specific distinction between our system and Galmiche/Sahli system I would say:
+
+	In \cite{galmiche2010}, Galmiche and Salhi present label-free natural deduction systems
+	for the different intuitionistic modal logics that are not using the \rn d-axiom.
+In this article, we present a labelled sequent calculus and a nested sequent calculus.
+We consider that sequent calculus is much better	suited for automated proof search than natural deduction.}
+%
 

### 2020-07-01 BicolorNS/aiml20/aiml20.tex
working on final version

@@
 %
+
+\marianela{I think if we write something like the thing above, it would be helpful to make the differencec between our system and the others. Let me know what you think}
 
@@
 \end{equation*}
+\marianela{I think we can make clear that this part is already proven for $\labIKp$ by adding just a sentence here like below}
+
+These extesions for $\labIKp$ are already proveṇ̣~\cite{marin:morales:strassburger:hal} but we are studying these cases for $\nIKp$.
 %This allows us to define cut-free deductive systems for a wide range of logics that could not be treated before.
@@
 
+%The generalisation of these results to our fully structured framework is subject of ongoing study.
+
 %% Appendix.

### 2020-07-02 BicolorNS/aiml20/aiml20.tex
final version completed + galmiche bib + macros inside tex

--- 2020-06-02 BicolorNS/aiml20/aiml20.tex
@@
 
-\input{macros}
+%\input{macros}
+\definecolor{notgreen}{rgb}{.1,.6,.1}
+\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+\newcommand{\red}[1]{{\color{red}{#1}}}
+\newcommand{\blue}[1]{{\color{blue}{#1}}}
+\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
+\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
+
+%%% General
+
+\newcommand{\F}{\mathcal{F}}
+\newcommand{\M}{\mathcal{M}}
+%\newcommand{\G}{\mathcal{G}}
+
+\newcommand{\B}{\mathcal{B}}
+\newcommand{\Left}{\mathcal{L}}
+\newcommand{\Right}{\mathcal{R}}
+
+\newcommand*{\rel}{R}
+\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+\newcommand*{\invr}[1]{#1^\mathsf{inv}}
+
+\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
+\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
+\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
+
+\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
+\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
+\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
+\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
+\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Logic
+\newcommand*{\ax}[1]{\mathsf{#1}}
+\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
+\newcommand*{\A}{\mathcal{A}}
+
+\newcommand{\force}[2]{#1\Vdash#2}
+\newcommand{\nforce}[2]{#1\nVdash#2}
+%
+\newcommand{\height}[1]{|#1|}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Systems
+\newcommand*{\K}{\mathsf{K}}
+\newcommand*{\IK}{\mathsf{IK}}
+\newcommand*{\lab}{\mathsf{lab}}
+\newcommand*{\n}{\mathsf{n}}
+
+%%% Connectives
+\newcommand*{\NOT}{\neg}
+\newcommand*{\AND}{\mathbin{\wedge}}
+\newcommand*{\TOP}{\mathord{\top}}
+\newcommand*{\OR}{\mathbin{\vee}}
+\newcommand*{\BOT}{\mathord{\bot}}
+\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
+
+\newcommand*{\BOX}{\mathord{\Box}}
+\newcommand*{\DIA}{\mathord{\Diamond}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Nested sequents
+\newcommand*\mdelim[3]{%
+	\mathopen{}\left#1%
+	#3%
+	\right#2\mathclose{}%
+}
+
+\makeatletter
+%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
+\newcommand*{\BR}{%
+\@ifnextchar\i{\br@two}{%
+\@ifnextchar\bgroup{\br@one}{% 
+}}}
+\newcommand*{\br@one}[1]{%
+\def\br@{#1}%
+\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
+}
+\newcommand*{\br@two}[3]{%
+\def\br@{#3}%
+\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
+}
+%
+\newcommand*{\bBR}{%
+\@ifnextchar\i{\bbr@two}{%
+\@ifnextchar\bgroup{\bbr@one}{% 
+}}}
+\newcommand*{\bbr@one}[1]{%
+\def\br@{#1}%
+\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
+}
+\newcommand*{\bbr@two}[3]{%
+\def\br@{#3}%
+\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
+}
+%
+%\newcommand*{\@makeoperator}[2]{
+%	\newcommand*{#1}{%
+%		\mathrm{#2}\mdelim{\lparen}{\rparen}
+%	}
+%}
+%%
+%\@makeoperator{\fm}{fm^{\n}}
+%\@makeoperator{\ofm}{fm^{\o}}
+%\@makeoperator{\hfm}{fm^{\h}}
+%%
+%\@makeoperator{\depth}{dp}
+%\@makeoperator{\rank}{rk}
+%\@makeoperator{\height}{ht}
+%\@makeoperator{\tree}{tree}
+%\@makeoperator{\graph}{graph}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% contexts
+\makeatletter
+\newcommand*{\cxs}{%
+\@ifnextchar\i{\cxs@two}{%
+\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
+}}}
+\newcommand*{\cxs@one}[1]{%
+\def\cxs@{#1}%
+\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
+\cxs@one@decor%
+}
+\newcommand*{\cxs@two}[3]{%
+\def\cxs@{#3}%
+\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
+\cxs@one@decor%
+}
+\def\cxs@one@decor{%
+\@ifnextchar_{\cxs@one@sub}{%
+\@ifnextchar^{\cxs@one@sup}{%
+	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
+		\@ifnextchar[{\cxs@one@arg}%]
+		\cxs}}}%
+}
+\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
+\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
+\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}
+
+%% Change these as needed, but keep the \cx@continuation at the end
+\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
+\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
+\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}
+
+\def\cx@delete@star#1*{%
+\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
+}
+
+\newcommand*{\@makecontextual}[2]{
+\newcommand*{#1}{%
+\@ifnextchar*{\cx@delete@star{#2}}{%
+	\@ifnextchar\f{\cx@delete@focus{#2}}{%
+		#2\cx@continuation}}%
+}%
+}
+\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
+
+\@makecontextual{\Ex}{}
+
+\@makecontextual{\Cx}{\Gamma}
+\@makecontextual{\Dx}{\Delta}
+\@makecontextual{\Lx}{\Lambda}
+\@makecontextual{\Rx}{\Pi}
+
+\@makecontextual{\LLx}{\Omega}
+\@makecontextual{\RRx}{\Xi}
+\@makecontextual{\CCx}{\Sigma}
+\@makecontextual{\DDx}{\Theta}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% intuitionistic
+\newcommand*{\rt}[1]{#1^\circ}
+\newcommand*{\lf}[1]{#1^\bullet}
+
+%%% Extracting symbols from MnSymbol 
+\DeclareFontFamily{U} {MnSymbolC}{}
+%
+\DeclareFontShape{U}{MnSymbolC}{m}{n}{
+<-6>  MnSymbolC5
+<6-7>  MnSymbolC6
+<7-8>  MnSymbolC7
+<8-9>  MnSymbolC8
+<9-10> MnSymbolC9
+<10-12> MnSymbolC10
+<12->   MnSymbolC12}{}
+\DeclareFontShape{U}{MnSymbolC}{b}{n}{
+<-6>  MnSymbolC-Bold5
+<6-7>  MnSymbolC-Bold6
+<7-8>  MnSymbolC-Bold7
+<8-9>  MnSymbolC-Bold8
+<9-10> MnSymbolC-Bold9
+<10-12> MnSymbolC-Bold10
+<12->   MnSymbolC-Bold12}{}
+%
+\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
+%
+\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
+\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
+
+%%% Labelled sequents
+\newcommand{\SEQ}{\Rightarrow}
+\newcommand*{\DD}{\mathcal{D}}
+%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+%\newcommand*{\invr}[1]{#1^\bullet}
+%\newcommand*{\rel}{R}
+
+%%% Labelled rules
+\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
+\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
+\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
+%
+\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
+\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
+%
+\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
+\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
+
+\newcommand*{\labIKp}{\lab\IK_{\le}}
+\newcommand*{\nIKp}{\n\IK_{\le}}
 
@@
 \section{Introduction}
-
 Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.
@@
 
-Similarly, proof systems have been designed for intuitionistic modal logic both as labelled sequent systems~\cite{simpson1994} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara}.
+Similarly, proof systems have been designed for intuitionistic modal logic both as labelled sequent systems~\cite{simpson1994} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara,galmiche2018}.
 %
-Surprisingly, in both settings, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.
+Surprisingly, in nested and labelled sequents, extending the sequent structure with the same \emph{one} extra element is enough to obtain sound and complete systems.
+%
 
@@
 \end{equation*}
+
 %This allows us to define cut-free deductive systems for a wide range of logics that could not be treated before.
@@
 
-The generalisation of these results to our fully structured framework is subject of ongoing study.
+%The generalisation of these results to our fully structured framework is subject of ongoing study.
+
+These extensions for $\labIKp$ are already proveṇ̣~\cite{marin:morales:strassburger:hal} but these results for our fully nested sequent system are subject of ongoing study.
+
+%The generalisation of these results to our fully structured framework is subject of ongoing study.
 

### 2020-07-02 BicolorNS/aiml20/aiml20.tex
adding the bibliography to the .tex file

@@
 \section{Introduction}
-Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009deep,poggiolesi2009method}.
+Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009,poggiolesi2009}.
 
@@
 %% Make sure to use the bibliographystyle aiml20.
-\bibliographystyle{aiml20}
-\bibliography{aiml20}
+%\bibliographystyle{aiml20}
+%\bibliography{aiml20}
+
+\begin{thebibliography}{}
+	\bibitem{brunnler2009}Br{\"u}nnler, K., \emph{Deep sequent systems for modal logic}, Archive for Mathematical Logic~\textbf{48} (2009), pp. 551--577.
+	\bibitem{fischer1984}Fischer Servi, G., \emph{Axiomatizations for some intuitionistic modal logics}, Rend. Sem. Mat. Univers. Politecn. Torino~\textbf{42} (1984), pp. 179--194.
+	\bibitem{galmiche2018}Galmiche, D.
+and Salhi, Y., \emph{Tree-sequent calculi and decision procedures for intuitionistic modal logics}, Journal of Logic and Computation~\textbf{28} (2018), pp.
+967--989.
+	\bibitem{kuznets:strassburger:maehara} Kuznets, R. and Stra{\ss}burger, L., \emph{Maehara-style modal nested calculi}, Archive for Mathematical Logic~\textbf{58} (2018), pp. 359--385.
+	\bibitem{maffezioli2013} Maffezioli, P.
+and Naibo, A.
+and Negri, S.,\emph{The {C}hurch--{F}itch knowability paradox in the light of structural proof theory}, Synthese~\textbf{190} (2013), pp.
+2677--2716.
+	\bibitem{marin:morales:strassburger:hal} Marin, S., Morales, M. and Stra{\ss}burger, L., \emph{A fully labelled proof system for intuitionistic modal logics} (2019), working paper or preprint.
+	\bibitem{negri2005} Negri, S., \emph{Proof analysis in modal logic}, Journal of Philosophical Logic~\textbf{34} (2005), pp. 107--128.
+	\bibitem{plotkin1986} Plotkin, G.
+and Stirling, C., \emph{A framework for intuitionistic modal logics}, Proceedings of the 1st Conference on Theoretical Aspects of Reasoning about Knowledge (TARK), (1986), pp.
+399--406.
+	\bibitem{poggiolesi2009} Poggiolesi, F., \emph{The method of tree-hypersequents for modal propositional logic}, Towards mathematical philosophy (2009), pp. 31--51.
+	\bibitem{simpson1994} Simpson, A. K., \emph{The proof theory and semantics of intuitionistic modal logic}, Ph.D. thesis, University of Edinburgh. College of Science and Engineering (1994).
+	\bibitem{strassburger2013} Stra{\ss}burger, L., \emph{Cut Elimination in Nested Sequents for Intuitionistic Modal Logics}, FoSSaCS'13,LNCS~\textbf{7794} (2013), pp. 209--224.
+	\bibitem{vigano2000}Vigan\`o, L., \emph{Labelled non-classical logics}, Kluwer Academic Publisher (2000).
+\end{thebibliography}
 

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
transforming fig 2 into includegraphics

@@
 % definitions specific to your article
-\newcommand{\ob}{[}
-\newcommand{\cb}{]}
+%\newcommand{\ob}{[}
+%\newcommand{\cb}{]}
 
@@
 
-\begin{figure}%[h]
+\begin{figure}
 	\centering
-	\small
 	\fbox{
-\begin{minipage}{.95\textwidth}
-\[
-%\vlinf{\rn{id}}{}{\Cx[1]{\lf A, \bBR{\rt A, \Cx[2]}}}{}
-\vlinf{\rn{id}}{}{\Cx{\lf A, \rt A}}{}
-\quad
-\vlinf{\lrn{\BOT}}{}{\Cx{\lf \BOT}}{}
-\]
-\[
-\vlinf{\lrn\AND}{}{\Cx{\lf{A \AND B}}}{\Cx{\lf A, \lf B}}
-\quad
-\vliinf{\rrn\AND}{}{\Cx{\rt{A \AND B}}}{\Cx{\rt A}}{\Cx{\rt B}}
-\quad
-\vliinf{\lrn\OR}{}{\Cx{\lf{A \OR B}}}{\Cx{\lf A}}{\Cx{\lf B}}
-\quad
-\vlinf{\rrn\OR}{}{\Cx{\rt{A \OR B}}}{\Cx{\rt A, \rt B}}
-\]
-\[
-%\vliinf{\lrn\IMP}{}{\Cx[1]{\lf{A \IMP B}, \bBR{\Cx[2]}}}{\Cx[1]{\lf{A \IMP B}, \bBR{\rt A, \Cx[2]}}}{\Cx[1]{\bBR{\lf B, \Cx[2]}}}
-%
-\vliinf{\lrn\IMP}{}{\Cx[1]{\lf{A \IMP B}}}{\Cx[1]{\lf{A \IMP B}, \rt A}}{\Cx[1]{\lf B}}
-\quad
-%\vlinf{\lrn[2]\IMP}{}{\Cx[1]{\lf{A \IMP B}, \bBR{\Cx[2]}}}{\Cx[1]{\bBR{\lf{A \IMP B}, \Cx[2]}}}
-\quad
-\vlinf{\rrn\IMP}{}{\Cx{\rt{A \IMP B}}}{\Cx{\bBR{\lf A, \rt B}}}
-\]
-\[
-%\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf A, \Cx[2]}}}}
-\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
-\quad
-\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}
-\quad
-\vlinf{\lrn\DIA}{}{\Cx{\lf{\DIA A}}}{\Cx{\BR{\lf A}}}
-\quad
-\vlinf{\rrn\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt A, \Cx[2]}}}
-\]
-\[
-\vlinf{\rrn{mon}}{}{\Cx[1]{\bBR{\rt A, \Cx[2]}}}{\Cx[1]{\rt A, \bBR{\rt A, \Cx[2]}}}
-\quad
-%\vlinf{\lrn{mon}}{}{\Cx[1]{\lf A, \bBR{\Cx[2]}}}{\Cx[1]{\bBR{\lf A, \Cx[2]}}}
-\vlinf{\lrn{mon}}{}{\Cx[1]{\lf A, \bBR{\Cx[2]}}}{\Cx[1]{\lf A, \bBR{\lf A, \Cx[2]}}}
-\quad
-%\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\bBR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\Cx[2]}}}}
-%\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\bBR{\Cx[2]}}}}{\Cx[1]{\BR{\bBR{\Cx[2]}}, \bBR{\BR{\Cx[2]}}}}
-\vlinf{\rn{F_1}}{}{\Cx[1]{\BR{\Cx[2], \bBR{\Cx[3]}}}}{\Cx[1]{\BR{\Cx[2]}, \bBR{{\BR{\Cx[3]}}}}}
-\]
-%\[\mbox{\hbox to .9\linewidth{\dotfill}}\]
-%\[
-%\vlinf{\rrn{mon}}{}{\Cx[1]{\bBR{\rt A, \Cx[2]}}}{\Cx[1]{\rt A, \bBR{\Cx[2]}}}
-%\quad
-%\vlinf{\rn{refl}_\le}{}{\Cx[1]{\Cx[2]}}{\Cx[1]{\bBR{\Cx[2]}}}
-%\quad
-%\vlinf{\rn{trans}_\le}{}{\Cx[1]{\bBR{\Cx[2], \bBR{\Cx[3]}}}}{\Cx[1]{\bBR{\Cx[2]}, \bBR{\Cx[3]}}}
-%\]
-\end{minipage}
+		\includegraphics[scale=.8]{fig-nIK}
 	}		
@@
 
-These extensions for $\labIKp$ are already proveṇ̣~\cite{marin:morales:strassburger:hal} but these results for our fully nested sequent system are subject of ongoing study.
+These extensions for $\labIKp$ are already proven~\cite{marin:morales:strassburger:hal} but these results for our fully nested sequent system are subject of ongoing study.
 

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
fixing some other figures

@@
 
-% definitions specific to your article
-%\newcommand{\ob}{[}
-%\newcommand{\cb}{]}
+\input{macros}
 
-%\input{macros}
-\definecolor{notgreen}{rgb}{.1,.6,.1}
-\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
-\newcommand{\red}[1]{{\color{red}{#1}}}
-\newcommand{\blue}[1]{{\color{blue}{#1}}}
-\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-
-%%% General
-
-\newcommand{\F}{\mathcal{F}}
-\newcommand{\M}{\mathcal{M}}
-%\newcommand{\G}{\mathcal{G}}
-
-\newcommand{\B}{\mathcal{B}}
-\newcommand{\Left}{\mathcal{L}}
-\newcommand{\Right}{\mathcal{R}}
-
-\newcommand*{\rel}{R}
-\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-\newcommand*{\invr}[1]{#1^\mathsf{inv}}
-
-\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-
-\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
-\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
-\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Logic
-\newcommand*{\ax}[1]{\mathsf{#1}}
-\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
-\newcommand*{\A}{\mathcal{A}}
-
-\newcommand{\force}[2]{#1\Vdash#2}
-\newcommand{\nforce}[2]{#1\nVdash#2}
+%\definecolor{notgreen}{rgb}{.1,.6,.1}
+%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
+%\newcommand{\red}[1]{{\color{red}{#1}}}
+%\newcommand{\blue}[1]{{\color{blue}{#1}}}
+%\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
+%\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
 %
-\newcommand{\height}[1]{|#1|}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Systems
-\newcommand*{\K}{\mathsf{K}}
-\newcommand*{\IK}{\mathsf{IK}}
-\newcommand*{\lab}{\mathsf{lab}}
-\newcommand*{\n}{\mathsf{n}}
-
-%%% Connectives
-\newcommand*{\NOT}{\neg}
-\newcommand*{\AND}{\mathbin{\wedge}}
-\newcommand*{\TOP}{\mathord{\top}}
-\newcommand*{\OR}{\mathbin{\vee}}
-\newcommand*{\BOT}{\mathord{\bot}}
-\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
-
-\newcommand*{\BOX}{\mathord{\Box}}
-\newcommand*{\DIA}{\mathord{\Diamond}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% Nested sequents
-\newcommand*\mdelim[3]{%
-	\mathopen{}\left#1%
-	#3%
-	\right#2\mathclose{}%
-}
-
-\makeatletter
-%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
-\newcommand*{\BR}{%
-\@ifnextchar\i{\br@two}{%
-\@ifnextchar\bgroup{\br@one}{% 
-}}}
-\newcommand*{\br@one}[1]{%
-\def\br@{#1}%
-\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
-}
-\newcommand*{\br@two}[3]{%
-\def\br@{#3}%
-\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
-}
+%%%% General
 %
-\newcommand*{\bBR}{%
-\@ifnextchar\i{\bbr@two}{%
-\@ifnextchar\bgroup{\bbr@one}{% 
-}}}
-\newcommand*{\bbr@one}[1]{%
-\def\br@{#1}%
-\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
-}
-\newcommand*{\bbr@two}[3]{%
-\def\br@{#3}%
-\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
-}
+%\newcommand{\F}{\mathcal{F}}
+%\newcommand{\M}{\mathcal{M}}
+%%\newcommand{\G}{\mathcal{G}}
 %
-%\newcommand*{\@makeoperator}[2]{
-%	\newcommand*{#1}{%
-%		\mathrm{#2}\mdelim{\lparen}{\rparen}
-%	}
+%\newcommand{\B}{\mathcal{B}}
+%\newcommand{\Left}{\mathcal{L}}
+%\newcommand{\Right}{\mathcal{R}}
+%
+%\newcommand*{\rel}{R}
+%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+%\newcommand*{\invr}[1]{#1^\mathsf{inv}}
+%
+%\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
+%\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
+%\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
+%
+%\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
+%\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
+%\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
+%\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
+%\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Logic
+%\newcommand*{\ax}[1]{\mathsf{#1}}
+%\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
+%\newcommand*{\A}{\mathcal{A}}
+%
+%\newcommand{\force}[2]{#1\Vdash#2}
+%\newcommand{\nforce}[2]{#1\nVdash#2}
+%%
+%\newcommand{\height}[1]{|#1|}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Systems
+%\newcommand*{\K}{\mathsf{K}}
+%\newcommand*{\IK}{\mathsf{IK}}
+%\newcommand*{\lab}{\mathsf{lab}}
+%\newcommand*{\n}{\mathsf{n}}
+%
+%%%% Connectives
+%\newcommand*{\NOT}{\neg}
+%\newcommand*{\AND}{\mathbin{\wedge}}
+%\newcommand*{\TOP}{\mathord{\top}}
+%\newcommand*{\OR}{\mathbin{\vee}}
+%\newcommand*{\BOT}{\mathord{\bot}}
+%\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
+%
+%\newcommand*{\BOX}{\mathord{\Box}}
+%\newcommand*{\DIA}{\mathord{\Diamond}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Nested sequents
+%\newcommand*\mdelim[3]{%
+%	\mathopen{}\left#1%
+%	#3%
+%	\right#2\mathclose{}%
+%}
+%
+%\makeatletter
+%%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
+%\newcommand*{\BR}{%
+%\@ifnextchar\i{\br@two}{%
+%\@ifnextchar\bgroup{\br@one}{% 
+%}}}
+%\newcommand*{\br@one}[1]{%
+%\def\br@{#1}%
+%\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
+%}
+%\newcommand*{\br@two}[3]{%
+%\def\br@{#3}%
+%\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
 %}
 %%
-%\@makeoperator{\fm}{fm^{\n}}
-%\@makeoperator{\ofm}{fm^{\o}}
-%\@makeoperator{\hfm}{fm^{\h}}
+%\newcommand*{\bBR}{%
+%\@ifnextchar\i{\bbr@two}{%
+%\@ifnextchar\bgroup{\bbr@one}{% 
+%}}}
+%\newcommand*{\bbr@one}[1]{%
+%\def\br@{#1}%
+%\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
+%}
+%\newcommand*{\bbr@two}[3]{%
+%\def\br@{#3}%
+%\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
+%}
 %%
-%\@makeoperator{\depth}{dp}
-%\@makeoperator{\rank}{rk}
-%\@makeoperator{\height}{ht}
-%\@makeoperator{\tree}{tree}
-%\@makeoperator{\graph}{graph}
-\makeatother
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% contexts
-\makeatletter
-\newcommand*{\cxs}{%
-\@ifnextchar\i{\cxs@two}{%
-\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
-}}}
-\newcommand*{\cxs@one}[1]{%
-\def\cxs@{#1}%
-\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
-\cxs@one@decor%
-}
-\newcommand*{\cxs@two}[3]{%
-\def\cxs@{#3}%
-\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
-\cxs@one@decor%
-}
-\def\cxs@one@decor{%
-\@ifnextchar_{\cxs@one@sub}{%
-\@ifnextchar^{\cxs@one@sup}{%
-	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
-		\@ifnextchar[{\cxs@one@arg}%]
-		\cxs}}}%
-}
-\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
-\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
-\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}
-
-%% Change these as needed, but keep the \cx@continuation at the end
-\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
-\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
-\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}
-
-\def\cx@delete@star#1*{%
-\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
-}
-
-\newcommand*{\@makecontextual}[2]{
-\newcommand*{#1}{%
-\@ifnextchar*{\cx@delete@star{#2}}{%
-	\@ifnextchar\f{\cx@delete@focus{#2}}{%
-		#2\cx@continuation}}%
-}%
-}
-\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
-
-\@makecontextual{\Ex}{}
-
-\@makecontextual{\Cx}{\Gamma}
-\@makecontextual{\Dx}{\Delta}
-\@makecontextual{\Lx}{\Lambda}
-\@makecontextual{\Rx}{\Pi}
-
-\@makecontextual{\LLx}{\Omega}
-\@makecontextual{\RRx}{\Xi}
-\@makecontextual{\CCx}{\Sigma}
-\@makecontextual{\DDx}{\Theta}
-\makeatother
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% intuitionistic
-\newcommand*{\rt}[1]{#1^\circ}
-\newcommand*{\lf}[1]{#1^\bullet}
-
-%%% Extracting symbols from MnSymbol 
-\DeclareFontFamily{U} {MnSymbolC}{}
+%%\newcommand*{\@makeoperator}[2]{
+%%	\newcommand*{#1}{%
+%%		\mathrm{#2}\mdelim{\lparen}{\rparen}
+%%	}
+%%}
+%%%
+%%\@makeoperator{\fm}{fm^{\n}}
+%%\@makeoperator{\ofm}{fm^{\o}}
+%%\@makeoperator{\hfm}{fm^{\h}}
+%%%
+%%\@makeoperator{\depth}{dp}
+%%\@makeoperator{\rank}{rk}
+%%\@makeoperator{\height}{ht}
+%%\@makeoperator{\tree}{tree}
+%%\@makeoperator{\graph}{graph}
+%\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% contexts
+%\makeatletter
+%\newcommand*{\cxs}{%
+%\@ifnextchar\i{\cxs@two}{%
+%\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
+%}}}
+%\newcommand*{\cxs@one}[1]{%
+%\def\cxs@{#1}%
+%\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
+%\cxs@one@decor%
+%}
+%\newcommand*{\cxs@two}[3]{%
+%\def\cxs@{#3}%
+%\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
+%\cxs@one@decor%
+%}
+%\def\cxs@one@decor{%
+%\@ifnextchar_{\cxs@one@sub}{%
+%\@ifnextchar^{\cxs@one@sup}{%
+%	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
+%		\@ifnextchar[{\cxs@one@arg}%]
+%		\cxs}}}%
+%}
+%\def\cxs@one@sub_#1{_{#1}\cxs@one@decor}
+%\def\cxs@one@sup^#1{^{#1}\cxs@one@decor}
+%\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}
 %
-\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-<-6>  MnSymbolC5
-<6-7>  MnSymbolC6
-<7-8>  MnSymbolC7
-<8-9>  MnSymbolC8
-<9-10> MnSymbolC9
-<10-12> MnSymbolC10
-<12->   MnSymbolC12}{}
-\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-<-6>  MnSymbolC-Bold5
-<6-7>  MnSymbolC-Bold6
-<7-8>  MnSymbolC-Bold7
-<8-9>  MnSymbolC-Bold8
-<9-10> MnSymbolC-Bold9
-<10-12> MnSymbolC-Bold10
-<12->   MnSymbolC-Bold12}{}
+%%% Change these as needed, but keep the \cx@continuation at the end
+%\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
+%\def\cx@delete@right#1*{{#1}^{\star}\cx@continuation}
+%\def\cx@delete@focus#1\f{{#1}^{\scriptscriptstyle\not{\langle}{\rangle}}\cx@continuation}
 %
-\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
+%\def\cx@delete@star#1*{%
+%\@ifnextchar*{\cx@delete@right{#1}}{\cx@delete@always{#1}}%
+%}
 %
-\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-
-%%% Labelled sequents
-\newcommand{\SEQ}{\Rightarrow}
-\newcommand*{\DD}{\mathcal{D}}
-%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-%\newcommand*{\invr}[1]{#1^\bullet}
-%\newcommand*{\rel}{R}
-
-%%% Labelled rules
-\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
+%\newcommand*{\@makecontextual}[2]{
+%\newcommand*{#1}{%
+%\@ifnextchar*{\cx@delete@star{#2}}{%
+%	\@ifnextchar\f{\cx@delete@focus{#2}}{%
+%		#2\cx@continuation}}%
+%}%
+%}
+%\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
 %
-\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
+%\@makecontextual{\Ex}{}
 %
-\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-
-\newcommand*{\labIKp}{\lab\IK_{\le}}
-\newcommand*{\nIKp}{\n\IK_{\le}}
+%\@makecontextual{\Cx}{\Gamma}
+%\@makecontextual{\Dx}{\Delta}
+%\@makecontextual{\Lx}{\Lambda}
+%\@makecontextual{\Rx}{\Pi}
+%
+%\@makecontextual{\LLx}{\Omega}
+%\@makecontextual{\RRx}{\Xi}
+%\@makecontextual{\CCx}{\Sigma}
+%\@makecontextual{\DDx}{\Theta}
+%\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% intuitionistic
+%\newcommand*{\rt}[1]{#1^\circ}
+%\newcommand*{\lf}[1]{#1^\bullet}
+%
+%
+%%%% Extracting symbols from MnSymbol 
+%\DeclareFontFamily{U} {MnSymbolC}{}
+%%
+%\DeclareFontShape{U}{MnSymbolC}{m}{n}{
+%<-6>  MnSymbolC5
+%<6-7>  MnSymbolC6
+%<7-8>  MnSymbolC7
+%<8-9>  MnSymbolC8
+%<9-10> MnSymbolC9
+%<10-12> MnSymbolC10
+%<12->   MnSymbolC12}{}
+%\DeclareFontShape{U}{MnSymbolC}{b}{n}{
+%<-6>  MnSymbolC-Bold5
+%<6-7>  MnSymbolC-Bold6
+%<7-8>  MnSymbolC-Bold7
+%<8-9>  MnSymbolC-Bold8
+%<9-10> MnSymbolC-Bold9
+%<10-12> MnSymbolC-Bold10
+%<12->   MnSymbolC-Bold12}{}
+%%
+%\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
+%%
+%\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
+%\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
+%
+%
+%%%% Labelled sequents
+%\newcommand{\SEQ}{\Rightarrow}
+%\newcommand*{\DD}{\mathcal{D}}
+%%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+%%\newcommand*{\invr}[1]{#1^\bullet}
+%%\newcommand*{\rel}{R}
+%
+%%%% Labelled rules
+%\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
+%\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
+%\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
+%%
+%\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
+%\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
+%%
+%\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
+%\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
+%
+%\newcommand*{\labIKp}{\lab\IK_{\le}}
+%\newcommand*{\nIKp}{\n\IK_{\le}}
 
@@
 
-\begin{figure}%[h]
+\begin{figure}
 	\centering
-	\small
 	\fbox{
-		\begin{minipage}{.95\textwidth}
-			\begin{tabular}{@{\!}c@{\quad}c}
-				$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A} }{}$
-				&
-				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
-%				\quad
-%				$\vlinf{\rlabrn\top}{}{\B, \Left \SEQ \Right, \labels{x}{\TOP}}{}$
-				\\\\
-				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
-				&
-				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
-				\\\\
-				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
-				&
-				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
-				\\\\
-				\multicolumn{2}{c}{
-					$\vlinf{\llabrn\IMP}{\text{\scriptsize $\lb y$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \Left, \futs xy, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					$\vliinf{\rlabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ B \SEQ \Right}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$ 
-					% 		&$\vliinf{\rlabrn\IMP}{\text{\scriptsize $x \le y \in \B$}}{\B, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \Left \SEQ \Right, \labels{y}{A}}{\B, \Left, \labels{y}{B} \SEQ \Right}$
-				}
-				\\\\
-				$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
-				&
-				$\vlinf{\rlabrn\BOX}{\text{\scriptsize $\lb y, \lb z$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
-				\\\\
-				$\vlinf{\llabrn\DIA}{\text{\scriptsize $\lb y$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
-				&
-				$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
-				\\
-				\multicolumn{2}{c}{
-					$\mbox{\hbox to .9\linewidth{\dotfill}}$
-				}
-				\\
-				$\vlinf{\rn{refl_\le}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
-				&
-				$\vlinf{\rn{trans_\le}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
-				\\\\
-				\multicolumn{2}{c}{
-					$\vlinf{\rn{F_1}}{\text{\scriptsize $\lb u$ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
-				}
-				\\\\
-				\multicolumn{2}{c}{
-					$\vlinf{\rn{F_2}}{\text{\scriptsize $\lb u$ fresh}}{\B, \accs xy,\futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
-				}
-			\end{tabular}		
-		\end{minipage}
+		\includegraphics[scale=.8]{fig-labIK}
 	}		
 	\caption{System $\labIKp$}
-	\label{fig:labIKp}
+	\label{fig:labIK}
 \end{figure}
@@
 		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with %\quad
+		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$ with \quad
 		%		
-		\smash{%\fbox{
-			\scalebox{.9}{$\vliinf{\labrn{cut}}{}{\B_1, \B_2, \Left \SEQ \Right}{\B_1, \Left \SEQ \Right, \labels{z}{C}}{\B_2, \Left, \labels{z}{C} \SEQ \Right}$}
-		}%}
+		\smash{\parbox[c]{5cm}{\includegraphics[scale=0.8]{cut}}}
 		%
@@
 		%
-%		\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
+		%\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
 	\end{enumerate}
@@
 The proof is a careful adaptation of standard techniques (see~\cite{marin:morales:strassburger:hal} for details).
-%%
-%In particular, in the course of the proof of (i) $\rightarrow$ (ii), we have to derive the five $\kax$ axioms. 
-%%
-%As an example, we display the derivation of $\kax[4]$ which also illustrates the need of having the rule corresponding to $F_1$ in the system.
-%
-%\vspace*{-.9cm}
-%$$
-%\hspace*{-.5cm}
-%\scalebox{.9}{
-%	$
-%	\vlderivation{
-%		\vlin{\rlabrn\IMP}{\text{\scriptsize $y$ fresh}} {\SEQ \labels{x}{(\DIA A \IMP \BOX B) \SEQ \BOX (A \IMP B)}}{
-%			\vlin{\rlabrn\BOX}{\text{\scriptsize $z, w$ fresh}}{x \le y, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{y}{\BOX (A \IMP B)}}{
-%				\vlin {\rlabrn\IMP}{\text{\scriptsize $u$ fresh}}{x \le y, y\le z, z \rel w, \labels{y}{\DIA A \IMP \BOX B} \SEQ \labels{w}{A \IMP B}}{
-%					\vlin {\color{red}{\rn{F_1}}}{}{x \le y, y \le z, w \le u, z \rel w, \labels{y}{\DIA A \SEQ \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-%						\vlin {\rn{trans}}{}{x \le y, y \le z, w \le u, z \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-%							\vliin {\llabrn\IMP}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A} \SEQ \labels{u}{B}}{
-%								\vlin {\rlabrn\DIA}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}}{
-%									\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-%										\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, u \le u, z \rel w, t \rel u, \labels{u}{A} \SEQ \labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}{
-%											\vlhy {}
-%										}
-%									}
-%								}
-%							}{
-%								%						\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								%							\vlin {\llabrn\BOX}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B} \SEQ \labels{u}{B}}{
-%								%								\vlin {\rn{refl}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%								%									\vlin {\labrn{id_g}}{}{x \le y, y \le z, w \le u, z \le t, y \le t, t \le t, u \le u, z \rel w, t \rel u, \labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B} \SEQ \labels{u}{B}}{
-%								\vlhy {\qquad\vdots\qquad}
-%								%										}
-%								%									}
-%								%								}
-%								%							}
-%							}
-%						}
-%					}
-%				}
-%			}
-%		}
-%	}$
-%}$$
-%%\end{example}
-%
-%%\vspace*{-.5cm}
-%
-%Note that our system offers only an atomic version of the identity rule, though the above derivation uses a general version of the identity rule $\rn{id_g}$ that applies to generic formulas. 
-%%
-%We therefore have to show that such a rule is admissible in our system.
-%%
-%As an example, we display one step of this admissibility proof that also illustrates the need for the rule $F_2$.% (the other cases are standard).
-%
-%\vspace*{-.5cm}
-%%\begin{example}
-%$$
-%\scalebox{.9}{
-%	$
-%	\vlderivation{
-%		\vlin{\llabrn\DIA}{}{\B, x \le y, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
-%			\vlin{\color{red}{\rn{F_2}}}{}{\B, x \le y, x \rel z, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-%				\vlin{\rlabrn\DIA}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
-%					\vlin{\labrn{id_g}}{}{\B, x \le y, x \rel z, z \le u, y \rel u, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
-%						\vlhy{}
-%					}
-%				}
-%			}
-%		}
-%	}
-%	$
-%}
-%$$
-%%\end{example}
 
@@
 
-Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule:\vspace*{-.2cm}
-%
+Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule%\vspace*{-.2cm}
+
+\begin{center}
+\includegraphics[scale=.8]{fig-trans}
+\end{center}
+
 %For example, you can add the following rule:
-$$\small
-\vlinf{\rn{trans}_\rel}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
+%$$\small
+%\vlinf{\rn{trans}_\rel}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
 %to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
@@
 %Consequently, we can easily 
-translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:\vspace*{-.2cm}
-\begin{equation*}\small
-\label{eq:4rules}
-\vlinf{\rn{4_{\BOX}}}{\text{\footnotesize$\lb{u}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-	\B, \accs xy, \accs yz, \accs {u}z, \futs x{u},\Left \SEQ \Right}
-\quad
-\vlinf{\rn{4_{\DIA}}}{\text{\footnotesize$\lb{u}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-	\B, \accs xy, \accs yz, \accs {x}{u}, \futs z{u},\Left \SEQ \Right}  
-\end{equation*}
+translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:%\vspace*{-.1cm}
+
+\begin{center}
+	\includegraphics[scale=.8]{fig-trans2}
+\end{center}
 
@@
 %
-Previous nested systems for intuitionistic modal logics~\cite{strassburger2013,kuznets:strassburger:maehara} can be extended from $\IK$ to $\mathsf{IK4}$ by simply adding the following rules:\vspace*{-.2cm}
-\[\small
-%\vlinf{\lrn[t]\BOX}{}{\Cx{\lf{\BOX A}}}{\Cx{\lf{\BOX A}, \lf A}}
-%\quad
-%\vlinf{\lrn[2]\BOX}{}{\Cx[1]{\lf{\BOX A}, \bBR{\BR{\Cx[2]}}}}{\Cx[1]{\bBR{\BR{\lf{\BOX A}, \Cx[2]}}}}
-\vlinf{\lrn[4]\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf{\BOX A}, \Cx[2]}}}
-%\quad
-%\vlinf{\rrn[t]\DIA}{}{\Cx{\rt{\DIA A}}}{\Cx{\rt{\DIA A}, \rt A}}
-\quad
-\vlinf{\rrn[4]\DIA}{}{\Cx[1]{\rt{\DIA A}, \BR{\Cx[2]}}}{\Cx[1]{\rt{\DIA A}, \BR{\rt{\DIA A}, \Cx[2]}}}
-\]
+Previous nested systems for intuitionistic modal logics~\cite{strassburger2013,kuznets:strassburger:maehara} can be extended from $\IK$ to $\mathsf{IK4}$ by simply adding the following rules:%\vspace*{-.2cm}
+
+\begin{center}
+	\includegraphics[scale = 0.8]{fig-trans3}
+\end{center}
 
 %The generalisation of these results to our fully structured framework is subject of ongoing study.
-
+%
 These extensions for $\labIKp$ are already proven~\cite{marin:morales:strassburger:hal} but these results for our fully nested sequent system are subject of ongoing study.

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
fixed all the virginialake commands

@@
 % your paper.
+
 \usepackage{graphicx}
 \usepackage{amsmath}
-\usepackage{amssymb}
-
+\usepackage{amssymb,latexsym}
+\usepackage{stmaryrd}
 \usepackage{colonequals}
-
-\usepackage[matrix,arrow]{xy}
-\usepackage[noxy]{../../virginialake}
-%\vlnosmallleftlabels
-\vlnostructuressyntax
 
@@
 
-\input{macros}
-
-%\definecolor{notgreen}{rgb}{.1,.6,.1}
-%\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
-%\newcommand{\red}[1]{{\color{red}{#1}}}
-%\newcommand{\blue}[1]{{\color{blue}{#1}}}
-%\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
-%\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
-%
-%%%% General
-%
-%\newcommand{\F}{\mathcal{F}}
-%\newcommand{\M}{\mathcal{M}}
-%%\newcommand{\G}{\mathcal{G}}
-%
-%\newcommand{\B}{\mathcal{B}}
-%\newcommand{\Left}{\mathcal{L}}
-%\newcommand{\Right}{\mathcal{R}}
-%
-%\newcommand*{\rel}{R}
-%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-%\newcommand*{\invr}[1]{#1^\mathsf{inv}}
-%
-%\newcommand*{\orn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-%\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-%\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%
-%\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
-%\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
-%\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
-%\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
-%\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%% Logic
-%\newcommand*{\ax}[1]{\mathsf{#1}}
-%\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
+\newcommand*{\ax}[1]{\mathsf{#1}}
+\newcommand*{\kax}[1][]		{\ax{k_{#1}}}
 %\newcommand*{\A}{\mathcal{A}}
@@
 %\newcommand{\height}[1]{|#1|}
+\newcommand*{\rel}{R}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Connectives
+\newcommand*{\NOT}{\neg}
+\newcommand*{\AND}{\mathbin{\wedge}}
+\newcommand*{\TOP}{\mathord{\top}}
+\newcommand*{\OR}{\mathbin{\vee}}
+\newcommand*{\BOT}{\mathord{\bot}}
+\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
+
+\newcommand*{\BOX}{\mathord{\Box}}
+\newcommand*{\DIA}{\mathord{\Diamond}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %\newcommand*{\K}{\mathsf{K}}
-%\newcommand*{\IK}{\mathsf{IK}}
-%\newcommand*{\lab}{\mathsf{lab}}
-%\newcommand*{\n}{\mathsf{n}}
+\newcommand*{\IK}{\mathsf{IK}}
 %
-%%%% Connectives
-%\newcommand*{\NOT}{\neg}
-%\newcommand*{\AND}{\mathbin{\wedge}}
-%\newcommand*{\TOP}{\mathord{\top}}
-%\newcommand*{\OR}{\mathbin{\vee}}
-%\newcommand*{\BOT}{\mathord{\bot}}
-%\newcommand*{\IMP}{\mathbin{\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
+\newcommand*{\lab}{\mathsf{lab}}
+\newcommand*{\n}{\mathsf{n}}
 %
-%\newcommand*{\BOX}{\mathord{\Box}}
-%\newcommand*{\DIA}{\mathord{\Diamond}}
+\newcommand*{\labIKp}{\lab\IK_{\le}}
+\newcommand*{\nIKp}{\n\IK_{\le}}
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%% Nested sequents
-%\newcommand*\mdelim[3]{%
-%	\mathopen{}\left#1%
-%	#3%
-%	\right#2\mathclose{}%
-%}
+%%%%%%%%%%%%%%%%%
+%% intuitionistic annotations
+\newcommand*{\rt}[1]{#1^\circ}
+\newcommand*{\lf}[1]{#1^\bullet}
 %
-%\makeatletter
-%%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
-%\newcommand*{\BR}{%
-%\@ifnextchar\i{\br@two}{%
-%\@ifnextchar\bgroup{\br@one}{% 
-%}}}
-%\newcommand*{\br@one}[1]{%
-%\def\br@{#1}%
-%\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
-%}
-%\newcommand*{\br@two}[3]{%
-%\def\br@{#3}%
-%\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
-%}
-%%
-%\newcommand*{\bBR}{%
-%\@ifnextchar\i{\bbr@two}{%
-%\@ifnextchar\bgroup{\bbr@one}{% 
-%}}}
-%\newcommand*{\bbr@one}[1]{%
-%\def\br@{#1}%
-%\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
-%}
-%\newcommand*{\bbr@two}[3]{%
-%\def\br@{#3}%
-%\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
-%}
-%%
-%%\newcommand*{\@makeoperator}[2]{
-%%	\newcommand*{#1}{%
-%%		\mathrm{#2}\mdelim{\lparen}{\rparen}
-%%	}
-%%}
-%%%
-%%\@makeoperator{\fm}{fm^{\n}}
-%%\@makeoperator{\ofm}{fm^{\o}}
-%%\@makeoperator{\hfm}{fm^{\h}}
-%%%
-%%\@makeoperator{\depth}{dp}
-%%\@makeoperator{\rank}{rk}
-%%\@makeoperator{\height}{ht}
-%%\@makeoperator{\tree}{tree}
-%%\@makeoperator{\graph}{graph}
-%\makeatother
+\newcommand*\mdelim[3]{%
+	\mathopen{}\left#1%
+	#3%
+	\right#2\mathclose{}%
+}
+%
+\makeatletter
+%\newcommand*\BR[2][]{\mdelim{\lbrack\strut^{#1}}{\rbrack}{#2}}
+\newcommand*{\BR}{%
+	\@ifnextchar\i{\br@two}{%
+		\@ifnextchar\bgroup{\br@one}{% 
+}}}
+\newcommand*{\br@one}[1]{%
+	\def\br@{#1}%
+	\mdelim{\lbrack}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
+}
+\newcommand*{\br@two}[3]{%
+	\def\br@{#3}%
+	\mdelim{\lbrack\strut^{#2}}{\rbrack}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
+}
+%
+\newcommand*{\bBR}{%
+	\@ifnextchar\i{\bbr@two}{%
+		\@ifnextchar\bgroup{\bbr@one}{% 
+}}}
+\newcommand*{\bbr@one}[1]{%
+	\def\br@{#1}%
+	\mdelim{\llbracket}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #1\fi}%
+}
+\newcommand*{\bbr@two}[3]{%
+	\def\br@{#3}%
+	\mdelim{\llbracket\strut^{#2}}{\rrbracket}{\ifx\br@\empty\mkern 3mu\else #3\fi}%
+}
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% contexts
-%\makeatletter
-%\newcommand*{\cxs}{%
-%\@ifnextchar\i{\cxs@two}{%
-%\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
-%}}}
-%\newcommand*{\cxs@one}[1]{%
-%\def\cxs@{#1}%
-%\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
+\makeatletter
+\newcommand*{\cxs}{%
+	\@ifnextchar\i{\cxs@two}{%
+		\@ifnextchar\bgroup{\cxs@one}{% % \bgroup is the same as {
+}}}
+\newcommand*{\cxs@one}[1]{%
+	\def\cxs@{#1}%
+	\mdelim{\lbrace}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #1\fi}%
 	%\cxs@one@decor%
-%}
-%\newcommand*{\cxs@two}[3]{%
-%\def\cxs@{#3}%
-%\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
+}
+\newcommand*{\cxs@two}[3]{%
+	\def\cxs@{#3}%
+	\mdelim{\lbrace\strut^{#2}}{\rbrace}{\ifx\cxs@\empty\mkern 3mu\else #3\fi}%
 	%\cxs@one@decor%
-%}
+}
 %\def\cxs@one@decor{%
@@
 %\@ifnextchar^{\cxs@one@sup}{%
-%	\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
+%\@ifnextchar\dots{\@firstoftwo{\dotsm\cxs@one@decor}}{%
 %	\@ifnextchar[{\cxs@one@arg}%]
@@
 %\def\cxs@one@arg[#1]{{#1}\cxs@one@decor}
-%
-%%% Change these as needed, but keep the \cx@continuation at the end
+
+%% Change these as needed, but keep the \cx@continuation at the end
 %\def\cx@delete@always#1{{#1}^{\ast}\cx@continuation}
@@
 %}
+
+\newcommand*{\@makecontextual}[2]{
+	\newcommand*{#1}{%
+		\@ifnextchar*{\cx@delete@star{#2}}{%
+			\@ifnextchar\f{\cx@delete@focus{#2}}{%
+				#2\cx@continuation}}%
+	}%
+}
+\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
+
+\@makecontextual{\Cx}{\Gamma}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%Rules
+\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+%\newcommand*{\invr}[1]{#1^\mathsf{inv}}
 %
-%\newcommand*{\@makecontextual}[2]{
-%\newcommand*{#1}{%
-%\@ifnextchar*{\cx@delete@star{#2}}{%
-%	\@ifnextchar\f{\cx@delete@focus{#2}}{%
-%		#2\cx@continuation}}%
-%}%
-%}
-%\newcommand*{\cx@continuation}[1][]{_{#1}\cxs}
+\newcommand*{\rrn}[2][]  {\rn{#2}_\rn{R#1}}
+\newcommand*{\lrn}[2][]  {\rn{#2}_\rn{L#1}}
 %
-%\@makecontextual{\Ex}{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Labelled sequents
+
+\newcommand*{\lb}[1]{#1}%{{\color{blue}{#1}}}
+\newcommand*{\fm}[1]{#1}%{{\color{notgreen}{#1}}}
 %
-%\@makecontextual{\Cx}{\Gamma}
-%\@makecontextual{\Dx}{\Delta}
-%\@makecontextual{\Lx}{\Lambda}
-%\@makecontextual{\Rx}{\Pi}
+\newcommand{\SEQ}{\Rightarrow}
+\newcommand{\B}{\mathcal{B}}
+\newcommand{\Left}{\mathcal{L}}
+\newcommand{\Right}{\mathcal{R}}
 %
-%\@makecontextual{\LLx}{\Omega}
-%\@makecontextual{\RRx}{\Xi}
-%\@makecontextual{\CCx}{\Sigma}
-%\@makecontextual{\DDx}{\Theta}
-%\makeatother
+\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
+\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
+\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
+%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% intuitionistic
-%\newcommand*{\rt}[1]{#1^\circ}
-%\newcommand*{\lf}[1]{#1^\bullet}
-%
-%
-%%%% Extracting symbols from MnSymbol 
-%\DeclareFontFamily{U} {MnSymbolC}{}
+%%%% Labelled rules
+\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
+\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
+\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
 %%
-%\DeclareFontShape{U}{MnSymbolC}{m}{n}{
-%<-6>  MnSymbolC5
-%<6-7>  MnSymbolC6
-%<7-8>  MnSymbolC7
-%<8-9>  MnSymbolC8
-%<9-10> MnSymbolC9
-%<10-12> MnSymbolC10
-%<12->   MnSymbolC12}{}
-%\DeclareFontShape{U}{MnSymbolC}{b}{n}{
-%<-6>  MnSymbolC-Bold5
-%<6-7>  MnSymbolC-Bold6
-%<7-8>  MnSymbolC-Bold7
-%<8-9>  MnSymbolC-Bold8
-%<9-10> MnSymbolC-Bold9
-%<10-12> MnSymbolC-Bold10
-%<12->   MnSymbolC-Bold12}{}
-%%
-%\DeclareSymbolFont{MnSyC}         {U}  {MnSymbolC}{m}{n}
-%%
-%\DeclareMathSymbol{\diamondplus}{\mathbin}{MnSyC}{124}
-%\DeclareMathSymbol{\boxtimes}{\mathbin}{MnSyC}{117}
-%
-%
-%%%% Labelled sequents
-%\newcommand{\SEQ}{\Rightarrow}
-%\newcommand*{\DD}{\mathcal{D}}
-%%\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
-%%\newcommand*{\invr}[1]{#1^\bullet}
-%%\newcommand*{\rel}{R}
-%
-%%%% Labelled rules
-%\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
-%\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
-%\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
-%%
-%\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
-%\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
-%%
-%\newcommand*{\boxbrn}[1]{\brsym_\rn{#1}}%^{\lab}}}
-%\newcommand*{\diabrn}[1]{\diasym_\rn{#1}}
-%
-%\newcommand*{\labIKp}{\lab\IK_{\le}}
-%\newcommand*{\nIKp}{\n\IK_{\le}}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   %
-  We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accesibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic.
-Both systems are in close correspondence with birelational Kripke semantics for intuitionistic modal logic.
+  We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accessibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic.
+Both systems are in close correspondence with the birelational Kripke semantics for intuitionistic modal logic.
   \end{abstract}
@@
 	\fbox{
-		\includegraphics[scale=.8]{fig-labIK}
+		\includegraphics[scale=.9]{fig-labIK}
 	}		
@@
 	\fbox{
-		\includegraphics[scale=.8]{fig-nIK}
+		\includegraphics[scale=.9]{fig-nIK}
 	}		
@@
 
-%In order to capture intuitionistic modal logics, we build a nested sequent system with the two relations explicitly: one of for the accessibility relation $\rel$ associated with the Kripke semantics for normal modal logics (represented with one bracket in the sequent) and one for the preorder relation $\le$ associated with the Kripje semantics for intuitionistic logic (represented with two brackets in the system).
-
-%In the intuitionistic setting, the validity of a modal formula has to be defined using both the $\rel$ and the $\le$ relation as:
-%$\force{\lb x}{\fm{\BOX A}}$ iff for all $\lb y$ and $\lb z$ s.t.
-$\futs xy$ and $\accs yz$, $\force{\lb z}{\fm{A}}$.
-Our system reflects exactly this definition in the rules introducing the $\BOX$-operator:
-%
-%\begin{center}
-%	$\vlinf{\lrn\BOX}{}{\Cx[1]{\lf{\BOX A}, \BR{\Cx[2]}}}{\Cx[1]{\lf{\BOX A}, \BR{\lf A, \Cx[2]}}}
-%	\quad
-%	\vlinf{\rrn\BOX}{}{\Cx{\rt{\BOX A}}}{\Cx{\bBR{\BR{\rt A}}}}$
-%\end{center}
-%
-%\marianela{add F1 rule?}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\paragraph{Labelled}
-%
-%The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
-%inference rule
-%\begin{equation}
-%\label{eq:Rtrans}
-%\vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
-%	\B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
-%\end{equation}
-%where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-%$\Delta$ for multi-sets of labelled formulas.
-
 The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be axiomatised by the conjunction of the two versions of the $\ax 4$-axiom:\vspace*{-.2cm}
-%\begin{equation*}
-%\label{eq:4ax}
-$$
+$$\small
 \ax{4_{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
@@
 \ax{4_{\DIA}}\colon\fm{\DIA\DIA A\IMP\DIA A}
-$$%\end{equation*}
+$$
 %
@@
 From~\cite{plotkin1986} we know they are in correspondance with the following frame conditions:\vspace*{-.2cm}
+{\small
 \begin{equation}
@@
 \end{equation}
-%  \todo{add graphical representation of the conditions}
-%$$
-%\xymatrix{
-%	u \ar@{.>}[drr]^R \\
-%	x \ar@{.>}[u]^\le \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z
-%}
-%\qquad\qquad
-%\xymatrix{
-%	&& u  \\
-%	x  \ar@{.>}[urr]^R \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z \ar@{.>}[u]^\le
-%}
-%$$
-%respectively%, have already been studied in~\cite{plotkin:stirling:86}.
+}
 
@@
 \begin{center}
-\includegraphics[scale=.8]{fig-trans}
+\includegraphics[scale=.9]{fig-trans}
 \end{center}
 
-%For example, you can add the following rule:
-%$$\small
-%\vlinf{\rn{trans}_\rel}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs wu, \Left \SEQ \Right}$$
-%to it and obtain a sound and complete system wrt.~$\IK$ plus the axiom
-%$\ax{4}\colon \fm{(\DIA\DIA A \IMP \DIA A) \AND (\BOX A \IMP \BOX\BOX A)}$, that is, wrt.~to all frames in which $\rel$ is transitive.
-
-%In~\cite{plotkin1986}, Plotkin and Stirling give a more general correspondence result than Theorem~\ref{thm:plotkin}, that is, for intuitionistic modal logic extended with a family of axioms wrt.~some classes of bi-relational frames.
-%%
-%For example, the frames that validate the axiom $\rn{4}_\rn\DIA \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the condition:
-%%\begin{center}
-%($\diabrn{4}$) if $\accs wv$ and $\accs vu$, there exists a $\lb{u'}\in W$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
-%%\end{center}
-
-Incorporating the preorder symbol into the syntax, however,  allowed us~\cite{marin:morales:strassburger:hal} to %also obtain a sound and complete proof system for the intuitionistic modal logic extended with axiom $\rn{4}_\rn\DIA$, by designing the following rule:
-%$$\scalebox{.9}{$\vlinf{\diabrn{4}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'}, \Left \SEQ \Right}$}$$
-%Consequently, we can easily 
+Incorporating the preorder symbol into the syntax, however,  allowed us~\cite{marin:morales:strassburger:hal} to 
 translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:%\vspace*{-.1cm}
@@
 \begin{center}
-	\includegraphics[scale=.8]{fig-trans2}
+	\includegraphics[scale=.9]{fig-trans2}
 \end{center}
-
-%This allows us to define cut-free deductive systems for a wide range of logics that could not be treated before.
-
-%Therefore, we decompose further the formalism of labelled sequents and extend the reach of labelled deduction to the logics studied in~\cite{plotkin1986}.
-%%
-%These systems enjoy cut-elimination via usual arguments, the generality of the result is subject of ongoing study.
 
@@
 These extensions for $\labIKp$ are already proven~\cite{marin:morales:strassburger:hal} but these results for our fully nested sequent system are subject of ongoing study.
-
-%The generalisation of these results to our fully structured framework is subject of ongoing study.
 

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
adding cut.tex

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%Rules
+%%%% Rules
 \newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
@@
   \begin{abstract}
-  %We present a nested sequent system for intuitionistic modal logic in which we capture explicitly two relations: one for the accessibility relation associated with the Kripke semantics for normal modal logics (represented with one bracket in a formula or context) and one for the preorder relation associated with the Kripke semantics for intuitionistic logic (represented with two brackets in a formula or context).
-  %
   We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accessibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic.
@@
 %  \item Please prepare your paper by editing this file (\verb|aiml20.tex|) as well as the bibliography file, \verb|aiml20.bib|.
+%
 %  \item Please do not use includegraphics on any PDF files not having all fonts embedded. If in doubt, please convert to JPG before including.
+%
 %  \item It is strictly prohibited to tamper with the text dimensions, including adding to the text height or width.
@@
 Also, please refrain from using any kind of negative white space.
+%
 %  \item Please make sure too split lines that are too wide in the final output (avoid overfull \verb|\hbox|es).
@@
 \section{Introduction}
-Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction} in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction} in the form of e.g.~nested sequent systems~\cite{brunnler2009,poggiolesi2009}.
+Structural proof theoretic accounts of modal logic can adopt the paradigm of \emph{labelled deduction}, in the form of e.g.~labelled sequent systems~\cite{vigano2000,negri2005}, or the one of \emph{unlabelled deduction}, in the form of e.g.~nested sequent systems~\cite{brunnler2009,poggiolesi2009}.
 

### 2020-07-03 BicolorNS/aiml20/aiml20.tex
changing name of cut

@@
 
-Similarly, proof systems have been designed for intuitionistic modal logic both as labelled sequent systems~\cite{simpson1994} and as nested sequent systems~\cite{strassburger2013,kuznets:strassburger:maehara,galmiche2018}.
+Similarly, proof systems have been designed for \emph{intuitionistic} modal logic both as labelled~\cite{simpson1994} and as nested~\cite{strassburger2013,kuznets:strassburger:maehara,galmiche2018} sequent systems.
 %
@@
 %
-More importantly, it leads to deductive systems that are not entirely satisfactory; they cannot as modularly capture axiomatic extensions (or equivalently restricted semantical conditions) and, in particular, can only provide decision procedures for a handful of them~\cite{simpson1994}.
+More importantly, it leads to deductive systems that are not entirely satisfactory; they cannot as modularly capture axiomatic extensions (or equivalently, restricted semantical conditions) and, in particular, can only provide decision procedures for a handful of them~\cite{simpson1994}.
 
-This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing both the modal accesibility relation and the intuitionistic preorder relation. 
+This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing \emph{both} the modal accesibility relation and the intuitionistic preorder relation. 
 %
@@
 %
-We would be particularly interested in a suitable system for logic $\mathsf{IS4}$, whose decidability is not known, and discuss this direction in Section~\ref{sec:extensions}.
+We would be particularly interested in a suitable system for logic $\mathsf{IS4}$, whose decidability is not known; we discuss this direction in Section~\ref{sec:extensions}.
 
@@
 	\caption{System $\labIKp$}
-	\label{fig:labIK}
+	\label{fig:labIKp}
 \end{figure}

### 2020-08-17 FullyLabelled/JLC/reviews/notes.tex
working on reviews

\documentclass[11pt]{article}

\input{new-macros}

\begin{document}
\textbf{Review 2: TODO list}

\begin{itemize}
	\item \emph{Broken references “??” in pages 13 and 14}: Fixed. Done.
	\item \emph{The section of "Extensions" has to be more detailed}
	\item \emph{Remark 4.2. Show the “need" you would likely have to show that no other proofs of the axioms are possible. That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.}:

	There are two options: 
	1. Do not use the word ``need'';
	2. Show that no other proofs of the axioms are possible.

	\item \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
\end{itemize}

\textbf{Review 1}

\begin{itemize}
	\item \emph{Also the proofs of the structural properties closely follow the methodology of the paper by Maffezioli, Naibo \& Negri. All this has to be said expressis verbis, and appropriate citations have to be added.
	Perhaps even more importantly, the authors of the paper under review neglect an important caveat in the design of rules of contraction-free labelled sequent calculi: to guarantee that contraction be admissible one needs to ensure that a certain closure condition be satisfied, see:}

		\emph{• Negri, S. Proof analysis in modal logic. Journal of Philosophical Logic, 34, 507–544, 2005.}
		\begin{center}
			\includegraphics[scale=.18]{closure-condition-Negri}
		\end{center}

\end{itemize}

\begin{proposition}

	The rules $\llabrn{cont}$ and $\rlabrn{cont}$ are admissible for $\labIKp$.
	\begin{center}
		$\vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}$\quad\quad$\vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}$
	\end{center}
\end{proposition}
\begin{proof}
	The rule $\llabrn{cont}$ can be derived using $\rn{refl}$ and $\llabrn{mon}$ which is admissible by Proposition 3.1.

	\begin{center}
			$\vlderivation{
				\vlin{\rn{refl}}{}
				{\B, \Left, \labels{x}{A} \SEQ \Right}
				{\vlin{\llabrn{mon}}{}
					{\B, \futs{x}{x}, \Left, \labels{x}{A} \SEQ \Right}
					{\vlhy{\B, \futs{x}{x}, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}}}
			}$
	\end{center}

The case for $\rlabrn{cont}$ is similar.
\end{proof}
\end{document}

### 2020-08-17 FullyLabelled/JLC/reviews/notes.tex
notes about reviews

@@
 \begin{document}
-\textbf{Review 2: TODO list}
-
-\begin{itemize}
-	\item \emph{Broken references “??” in pages 13 and 14}: Fixed. Done.
-	\item \emph{The section of "Extensions" has to be more detailed}
-	\item \emph{Remark 4.2.
-Show the “need" you would likely have to show that no other proofs of the axioms are possible.
-That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.}:
-
-	There are two options: 
-	1. Do not use the word ``need'';
-	2. Show that no other proofs of the axioms are possible.
-
-	\item \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
-\end{itemize}
 
@@
 \end{proof}
+
+\begin{itemize}
+	\item \emph{In Section 7, if the rules G klmn are added without their contracted instances, the calculus will not be complete.
+For example, in the classical case, Euclidean transitivity $\forall a,b,c (\accs{a}{b} \& \accs{a}{c} \IMP \accs{b}{c})$ has the contracted instance $\forall a,b (\accs{a}{b} \IMP \accs{b}{b})$ that allows for the derivation of $ \BOX(\BOX A \IMP A)$.
+This, however, can hardly be derived without the rule’s contracted instance.}
+\end{itemize}
+
+\begin{center}
+	$\vlderivation{
+		\vlin{\rlabrn\BOX}
+		{}
+		{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}
+		{\vlin{\rlabrn\IMP}{\lb w\mbox{ fresh}}
+			{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}
+			{\vlin{\rn F_1}{\lb u\mbox{ fresh}}
+				{\futs xy, \futs zw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
+				{\vlin{\rn g_{1100}}{\exists \lb{w'}, \lb{w''}}
+					{\futs xy, \futs zw, \futs yu, \accs uw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
+					{\vlin{\llabrn\BOX}{}
+						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
+						{\vlin{}{}
+							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A}, \labels{w''}{A} \SEQ \labels{w}{A}}
+							{}}}}}}
+	}$
+\end{center}
+
+\textbf{Review 2: TODO list}
+
+\begin{itemize}
+	\item \emph{Broken references “??” in pages 13 and 14}: {\color{green}Fixed.}
+	\item \emph{The section of ``Extensions" has to be more detailed:
+		\begin{itemize}
+			\item it does not help at all that the
+			applications of the rule g1111 are merged with $\llabrn\BOX$ and $\rlabrn\DIA$ in the example
+			derivation. {\color{green}Fixed.}
+			\item Most importantly, I am not convinced by the gklmn rule.
+The side condition stipulates that $\lb y'$ and $\lb u$ are fresh, whereas the frame property contains existential quantifications.
+I was thus expecting either a Skolemization in the style of Vigano in the ``Labelled Non-Classical Logics" book, or a geometric rule with existential quantification in the style of Simpson [Sim94] or, perhaps even better, a “mixed” rule where the labels are	assumed more or less in the style of an $\exists$ elimination to derive a labeled formula.
+		\end{itemize}}
+	\item \emph{Remark 4.2.
+Show the ``need" you would likely have to show that no other proofs of the axioms are possible.
+That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.}:
+
+	There are two options: 
+	1. Do not use the word ``need'';
+	2. Show that no other proofs of the axioms are possible.
+
+	\item \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
+\end{itemize}
+
 \end{document}

### 2020-08-18 FullyLabelled/JLC/reviews/notes.tex
small modif

@@
 				{\futs xy, \futs zw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-				{\vlin{\rn g_{1100}}{\exists \lb{w'}, \lb{w''}}
+				{\vlin{\rn g_{1011}}{ \lb{w'}\mbox{ fresh}}
 					{\futs xy, \futs zw, \futs yu, \accs uw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-					{\vlin{\llabrn\BOX}{}
-						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
+					{\vlin{\llabrn\BOX+\rn{refl}}{}
+						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w}{w'}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
 						{\vlin{}{}
-							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A}, \labels{w''}{A} \SEQ \labels{w}{A}}
+							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w}{w'}, \accs yz, \labels{w}{\BOX A}, \labels{w'}{A} \SEQ \labels{w}{A}}
 							{}}}}}}

### 2020-08-24 BicolorNS/aiml20/aiml20.tex
proving reviewer 1's formula

@@
   We present a labelled sequent system and a nested sequent system for intuitionistic modal logics equipped with two relation symbols, one for the accessibility relation associated with the Kripke semantics for modal logics and one for the preorder relation associated with the Kripke semantics for intuitionistic logic.
-Both systems are in close correspondence with the birelational Kripke semantics for intuitionistic modal logic.
+Both systems are in close correspondence with the bi-relational Kripke semantics for intuitionistic modal logic.
   \end{abstract}
@@
 
-This no longer matches the relational semantics of these logics, which requires to combine the relation for intuitionistic propositional logic and the one for modal logic. 
+This no longer matches the relational semantics of these logics, which requires to combine \emph{both} the relation for intuitionistic propositional logic and the one for modal logic. 
 %
@@
 
-This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing \emph{both} the modal accesibility relation and the intuitionistic preorder relation. 
+This lead us to develop a \emph{fully structured} approach to intuitionistic modal proof theory capturing \emph{both} the modal accessibility relation and the intuitionistic preorder relation. 
 %
-A fully labelled framework, described succintly in Section~\ref{sec:labelled}, has already allowed us to obtain modular systems for all intuitionistic Scott-Lemmon logics~\cite{marin:morales:strassburger:hal}.
+A \emph{fully labelled} framework, described succintly in Section~\ref{sec:labelled}, has already allowed us to obtain modular systems for all intuitionistic Scott-Lemmon logics~\cite{marin:morales:strassburger:hal}.
 %
-In an attempt to make this system amenable for proof-search and decision procedures, we have started investigated a fully nested framework, presented in Section~\ref{sec:nested}.
+In an attempt to make this system amenable for proof-search and decision procedures, we have started investigated a \emph{fully nested} framework, presented in Section~\ref{sec:nested}.
 %
@@
 
-%We present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing both the modal accesibility relation and the intuitionistic preorder relation. 
+%We present a labelled sequent system and a nested sequent system for intuitionistic modal logics capturing both the modal accessibility relation and the intuitionistic preorder relation. 
 %
@@
 %
-%In the nested sequent system, we represent this relations with one bracket in a sequent (for the accesibility relation) and a with two brackets in a sequent (preorder relation).  
+%In the nested sequent system, we represent this relations with one bracket in a sequent (for the accessibility relation) and a with two brackets in a sequent (preorder relation).  
 %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted $\fm a$, modal formulas are constructed from the grammar:\vspace*{-.1cm}
+Starting with a set $\mathcal{A}$ of atomic propositions, denoted $\fm a$, modal formulas are constructed from the grammar:%\vspace*{-.2cm}
 %
@@
 	\item the \emph{necessitation rule}: $\fm{\BOX A}$ is a theorem if $\fm{A}$ is a theorem; and
-	\item the following five variants of the \emph{distributivity axiom}:\vspace*{-.1cm}
+	\item the following five variants of the \emph{distributivity axiom}:%\vspace*{-.2cm}
 	\begin{equation*}
@@
 %
-The relation $\Vdash$ is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:\vspace*{-.1cm}
+The relation $\Vdash$ is extended to all formulas by induction, following the rules for both intuitionistic and modal Kripke models:%\vspace*{-.1cm}
 \begin{align}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Fully labelled sequent calculus}\label{sec:labelled}
@@
 	\fbox{
-		\includegraphics[scale=.9]{fig-labIK}
+		\includegraphics[scale=.85]{fig-labIK}
 	}		
@@
 
-%Simpson~\cite{Simpson} followed the lines of Gentzen in a labelled context, namely, he developed a labelled natural deduction framework for modal logics and then converted it into sequent systems with the consequent restriction to one formula on the right-hand side of each sequent.
-%%
-%This worked as well in the labelled setting as in the ordinary sequent case: we followed Simpson's sequent system where intuitionistic labelled sequents are written $\B, \Left \SEQ \labels{z}{C}$ for some multiset of labelled formulas $\Left$, some formula $C$, some label $z$ and a set of relational atoms $\B$.
-
-%\emph{Labelled deduction} has been proposed by Gabbay~\cite{gabbay1996} in the 80s as a unifying framework throughout proof theory in order to provide proof systems for a wide range of logics. 
-%
-%For modal logics it can take the form of labelled natural deduction and labelled sequent systems as used, for example, by Simpson~\cite{simpson1994}, Vigan\`o~\cite{vigano2000}, and Negri~\cite{negri2005}.
-%
-%Simpson's~\cite{simpson1994} labelled sequent system for intuitionistic modal logic is representing explicitly only the accessibility relation $\rel$ in the syntax.
-%
 Echoing the definition of bi-relational structures, we consider an extension of labelled deduction to the intuitionistic setting
 %
-that uses two sorts of relational atoms, one for the modal relation $\rel$ and another one for the intuitionistic relation $\leq$ (similarly to~\cite{maffezioli2013} for epistemic logic). 
+that uses two sorts of relational atoms, one for the modal accessibility relation $\rel$ and another one for the intuitionistic preorder relation $\leq$ (similarly to~\cite{maffezioli2013} for epistemic logic).
 %
-
 \begin{definition}
@@
 \end{definition}
-
-%Labelled sequents are formed from by labelled formulas of the form $\labels{x}{A}$ and relational or equality atoms of the form $x \rel y$ or $x = y $ respectively, where $x$,$y$ range over  a set of variables (called labels) and $A$ is a modal formula.
-A (onde-sided) \emph{labelled sequent} is then of the form $\B \SEQ \Right$ where $\B$ denotes a set of relational or equality atoms, and $\Right$ a multiset of labelled formulas.
-
 %
@@
 %
-%As we mentioned, we obtain a proof system $\labIKp$ which allows us to give an extension of labelled deduction to the intuitionistic world and then we prove the next theorem:
-
-%\begin{theorem}
-%	\label{thm:sound-compl}
-%	A formula $A$ is provable in the calculus $\labIKp$ if and only if $A$ is valid in every bi-relational frame.
-%\end{theorem}
-%
-%On the one hand, we prove directly that each rule from our system is sound wrt.~bi-relational structures.
-%
-%On the other hand, we show that $\labIKp$ is complete wrt.~Simpson's $\lab\IK$, and the theorem then follows from Theorem~\ref{thm:simpson-sound-compl}.
-
-%Finally we can prove the following theorem ensuring soundness and (cut-free) completeness of $\labIKp$.
-
 \begin{theorem}\label{thm:cutfree-compl}
@@
 		%		
-		\smash{\parbox[c]{5cm}{\includegraphics[scale=0.8]{cut}}}
+		\smash{\parbox[c]{5cm}{\includegraphics[scale=0.8]{fig-cut}}}
 		%
@@
 		%
-		%\item\label{iv} $A$ is valid in every birelational frames %satisfying the properties in $\CC$.
+		%\item\label{iv} $A$ is valid in every bi-relational frames %satisfying the properties in $\CC$.
 	\end{enumerate}
@@
 	\fbox{
-		\includegraphics[scale=.9]{fig-nIK}
+		\includegraphics[scale=.85]{fig-nIK}
 	}		
@@
 %
-$\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent respectively in the absence of the sequent arrow.
+$\lf{(\cdot)}$ and $\rt{(\cdot)}$ annotations are used to indicate that the formulas would occur on the left-hand-side or right-hand-side of a sequent, respectively, in the absence of the sequent arrow.
 
@@
 %
-The idea is similar to the fully labelled calculus but the shift of paradigm forced us to make different design choices.
+The idea is similar to the fully labelled calculus but the shift of paradigm allowed us to make different design choices.
 %
-In particular, the underlying tree-structure prevents us to express the rule $\rn{F_2}$, but its absence is compensated by the \emph{monotonicity rules} $\lrn{mon}$ and $\rrn{mon}$ which were admissible in $\labIKp$.
+In particular, the underlying tree-structure prevents us to express the rule $\rn{F_2}$, but its absence is offset by the \emph{monotonicity rules} $\lrn{mon}$ and $\rrn{mon}$, which were admissible in $\labIKp$.
 %
-Another beneficial result of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need any equivalent here.
+Another benefit of this addition is that rules $\rn{refl_\le}$ and $\rn{trans_\le}$ do not need any equivalent here.
 
@@
 
-As mentionned in the introduction, one of our motivation is to investigate decision procedure for axiomatic extensions of $\IK$, for instance for $\mathsf{IS4}$, intuitionistic logic of reflexive transitive frames.
+As mentioned in the introduction, one of our motivation is to investigate decision procedure for axiomatic extensions of $\IK$, for instance $\mathsf{IS4}$, intuitionistic logic of reflexive transitive frames.
 %
-We will therefore illustrate the benefit of our approach taking transitivity as a test-case.
+We will therefore illustrate our approach taking transitivity as a test-case.
 
-The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be axiomatised by the conjunction of the two versions of the $\ax 4$-axiom:\vspace*{-.2cm}
-$$\small
+The frame condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be axiomatised by adding to $\IK$ the conjunction of the two versions of the $\ax 4$-axiom:%\vspace*{-.2cm}
+$$
 \ax{4_{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
@@
 %
+%\vspace*{-.2cm}\noindent
 which are equivalent in classical modal logic. 
 %
-However, in intuitionistic modal logic they are not and they can be added independently to the logic $\IK$. %(an intuitionistic version of $\K$). 
+However, in intuitionistic modal logic they are not and they can be added to $\IK$ independently.
 %
-From~\cite{plotkin1986} we know they are in correspondance with the following frame conditions:\vspace*{-.2cm}
+From~\cite{plotkin1986} we know they are in correspondence respectively with the following frame conditions:%\vspace*{-.2cm}
+%
 {\small
@@
 \label{eq:4frame}
-\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs x{u}\AND\accs {u}z)
+\forall\lb{xyz}.\:((\accs xy\AND \accs yz)\IMP\exists\lb{u}.\:(\futs x{u}\AND\accs {u}z))
 \quad
-\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{u}.\:\futs z{u}\AND\accs {x}{u})
-\end{equation}
-}
-
-Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule%\vspace*{-.2cm}
-
+\forall\lb{xyz}.\:((\accs xy\AND \accs yz)\IMP\exists\lb{u}.\:(\futs z{u}\AND\accs {x}{u}))
+\end{equation}}
+%
+%\vspace*{-.6cm}
+Following Simpson~\cite{simpson1994} we could extend our basic sequent system for $\IK$ to $\mathsf{IK4} = \IK+(\ax{4_{\BOX}}\AND\ax{4_{\DIA}})$ with the rule%\vspace*{-.1cm}
+%
 \begin{center}
@@
 
-Incorporating the preorder symbol into the syntax, however,  allowed us~\cite{marin:morales:strassburger:hal} to 
+%\vspace*{-.2cm}
+Incorporating the preorder symbol into the syntax too, allowed us however to 
 translate the conditions in~\eqref{eq:4frame} into separate inference rules for $\ax{4_{\BOX}}$ and $\ax{4_{\DIA}}$:%\vspace*{-.1cm}
-
+%
 \begin{center}
@@
 \end{center}
+%
+%\vspace*{-.2cm}\noindent
+These extensions for $\labIKp$ are sound and complete;
+more generally, Theorem~\ref{thm:cutfree-compl} can be extended to the class of intuitionisitc Scott-Lemmon logics~\cite{marin:morales:strassburger:hal}.
 
-A great interest of a nested system is that the rules for axiomatic extensions are usually more suitable for proof-search procedures that in the labelled setting.
+Similar results for the fully nested sequent system are subject of ongoing study. 
 %
 Previous nested systems for intuitionistic modal logics~\cite{strassburger2013,kuznets:strassburger:maehara} can be extended from $\IK$ to $\mathsf{IK4}$ by simply adding the following rules:%\vspace*{-.2cm}
-
+%
 \begin{center}
-	\includegraphics[scale = 0.8]{fig-trans3}
+	\includegraphics[scale = .9]{fig-trans3}
 \end{center}
-
-%The generalisation of these results to our fully structured framework is subject of ongoing study.
 %
-These extensions for $\labIKp$ are already proven~\cite{marin:morales:strassburger:hal} but these results for our fully nested sequent system are subject of ongoing study.
+%\vspace*{-.2cm}\noindent
+A great interest of such rules is their logical rather than structural nature, making them usually more suitable for proof-search procedures than their labelled counterpart.
 
@@
 2677--2716.
-	\bibitem{marin:morales:strassburger:hal} Marin, S., Morales, M. and Stra{\ss}burger, L., \emph{A fully labelled proof system for intuitionistic modal logics} (2019), working paper or preprint.
-	\bibitem{negri2005} Negri, S., \emph{Proof analysis in modal logic}, Journal of Philosophical Logic~\textbf{34} (2005), pp. 107--128.
+	\bibitem{marin:morales:strassburger:hal} Marin, S., Morales, M. and Stra{\ss}burger, L., \emph{A fully labelled proof system for intuitionistic modal logics} (2019), ArXiv preprint.
+	\bibitem{negri2005} Negri, S., \emph{Proof analysis in modal logic}, J.~of Philosophical Logic~\textbf{34} (2005), pp. 107--128.
 	\bibitem{plotkin1986} Plotkin, G.
-and Stirling, C., \emph{A framework for intuitionistic modal logics}, Proceedings of the 1st Conference on Theoretical Aspects of Reasoning about Knowledge (TARK), (1986), pp.
+and Stirling, C., \emph{A framework for intuitionistic modal logics}, Proceedings of the 1st Conf.~on Theoretical Aspects of Reasoning about Knowledge (1986), pp.
 399--406.

### 2020-08-24 FullyLabelled/JLC/reviews/notes.tex
proving reviewer 1's formula

--- 2020-08-17 FullyLabelled/JLC/reviews/notes.tex
@@
 
-\begin{center}
-	$\vlderivation{
-		\vlin{\rlabrn\BOX}
-		{}
-		{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}
-		{\vlin{\rlabrn\IMP}{\lb w\mbox{ fresh}}
-			{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}
-			{\vlin{\rn F_1}{\lb u\mbox{ fresh}}
-				{\futs xy, \futs zw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-				{\vlin{\rn g_{1100}}{\exists \lb{w'}, \lb{w''}}
-					{\futs xy, \futs zw, \futs yu, \accs uw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-					{\vlin{\llabrn\BOX}{}
-						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-						{\vlin{}{}
-							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A}, \labels{w''}{A} \SEQ \labels{w}{A}}
-							{}}}}}}
-	}$
-\end{center}
+$$
+	\vlderivation{
+		\vlin{\rlabrn\BOX}{}{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}{
+			\vlin{\rlabrn\IMP}{\lb w\mbox{ fresh}}{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}{
+				\vlin{\rn F_1}{\lb u\mbox{ fresh}}{\futs xy, \accs yz, \futs zw, \labels{w}{\BOX A} \SEQ \labels{w}{A}}{
+					\vlin{\rn g_{1110}}{ \lb{w'}\mbox{ fresh}}{\futs xy, \accs yz, \futs zw, \futs yu, \accs uw, \labels{w}{\BOX A} \SEQ \labels{w}{A}}{
+						\vlin{\llabrn{mon}}{}{\futs xy, \accs yz, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w}, \labels{w}{\BOX A} \SEQ \labels{w}{A}}{
+							\vlin{\llabrn\BOX}{}{\futs xy, \accs yz, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w}, \labels{w}{\BOX A}, \labels{w'}{\BOX A} \SEQ \labels{w}{A}}{
+								\vlin{\rn{id}}{}{\futs xy, \accs yz, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w}, \labels{w}{\BOX A}, \labels{w'}{\BOX A}, \labels{w}{A} \SEQ \labels{w}{A}}{
+									\vlhy{}
+								}
+							}
+						}
+					}
+				}
+			}
+		}
+	}
+$$
 

### 2020-08-24 FullyLabelled/JLC/reviews/notes.tex
rewriting the proof without mon

--- 2020-08-17 FullyLabelled/JLC/reviews/notes.tex
@@
 
-\begin{center}
-	$\vlderivation{
-		\vlin{\rlabrn\BOX}
-		{}
-		{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}
-		{\vlin{\rlabrn\IMP}{\lb w\mbox{ fresh}}
-			{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}
-			{\vlin{\rn F_1}{\lb u\mbox{ fresh}}
-				{\futs xy, \futs zw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-				{\vlin{\rn g_{1100}}{\exists \lb{w'}, \lb{w''}}
-					{\futs xy, \futs zw, \futs yu, \accs uw, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-					{\vlin{\llabrn\BOX}{}
-						{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A} \SEQ \labels{w}{A}}
-						{\vlin{}{}
-							{\futs xy, \futs zw, \futs yu, \accs uw, \futs{w}{w'}, \accs{w'}{w''}, \accs yz, \labels{w}{\BOX A}, \labels{w''}{A} \SEQ \labels{w}{A}}
-							{}}}}}}
-	}$
-\end{center}
+$$
+	\vlderivation{
+		\vlin{\rlabrn\BOX}{}{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}{
+			\vlin{\rlabrn\IMP}{\lb v\mbox{ fresh}}{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}{
+				\vlin{\rn F_1}{\lb u\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
+					\vlin{\rn g_{1110}}{ \lb{w}\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
+							\vlin{\llabrn\BOX}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
+								\vlin{\rn{id}}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A}, \labels{v}{A} \SEQ \labels{v}{A}}{
+									\vlhy{}
+							}
+						}
+					}
+				}
+			}
+		}
+	}
+$$
 

### 2020-08-25 FullyLabelled/JLC/reviews/notes.tex
adding TODO

@@
 \documentclass[11pt]{article}
+\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
 
@@
 \end{itemize}
-
-\begin{proposition}
+\todo{Add next remark to the paper with a small explanation:}
+\begin{remark}
 
@@
 	\end{center}
-\end{proposition}
+\end{remark}
 \begin{proof}
@@
 
+\todo{Add next proof as an example and a paragraph explaning.}
 $$
@@
 
+\begin{itemize}
+	\item \emph{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in
+	detail, as otherwise the authors’ work would rather look a routine exercise.}: \todo{add a paragraph about constructive modal logics.}
+	\item \todo{Add a paragraph with all the references we are missing.}
+\end{itemize}
+
 \textbf{Review 2: TODO list}
@@
 I was thus expecting either a Skolemization in the style of Vigano in the ``Labelled Non-Classical Logics" book, or a geometric rule with existential quantification in the style of Simpson [Sim94] or, perhaps even better, a “mixed” rule where the labels are	assumed more or less in the style of an $\exists$ elimination to derive a labeled formula.
+\todo{}
 		\end{itemize}}
@@
 	There are two options: 
-	1. Do not use the word ``need'';
-	2. Show that no other proofs of the axioms are possible.
+	\todo{Do not use the word ``need''.}
 
-	\item \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
+	\item \todo{LUTZ: \emph{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}}
 \end{itemize}

### 2020-08-31 FullyLabelled/JLC/introduction.tex
adding more TODO
working on reviews

@@
 %
+
+\review{The rules of their calculus are identical (except for the ones that relate the two accessibility relations) to the rules for the intuitionistic-alethic fragment	of the calculus for intuitionistic bimodal logic in this publication:
+	• Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
 Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.
 %
+\marianela{
 Our system uses the same principle, both labelled and multi-conclusion sequents, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics.
@@
 This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.
+Furthermore, we present in this contribution an internal cut elimination proof.}
 
@@
 
+\todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
 %\todo{maybe paragraph on related work?}

### 2020-08-31 FullyLabelled/JLC/system.tex
continue with reviews

--- 2019-10-08 caleidoscope/system.tex
@@
 %
+\review{Also the proofs of the structural properties closely follow the methodology of the paper by Maffezioli, Naibo \& Negri.
+All this has to be said expressis verbis, and appropriate citations have to be added.}
+\marianela{we are not saying that in the next paragraph?}
 In the Kripke-semantics in~\eqref{eq:kripke} the two
@@
 
+\review{the authors of the paper under review neglect an important caveat in the design of rules of contraction-free labelled sequent calculi: to guarantee that contraction be admissible one needs to ensure that a certain closure condition be satisfied, see:
+
+\emph{• Negri, S. Proof analysis in modal logic. Journal of Philosophical Logic, 34, 507–544, 2005.}}
+
+\marianela{Should we mention Negri's paper here? }
+
+\marianela{In the same way as we did with monotonicity, trying to avoid the problems that contraction has in a cut elimination proof, it is preferable to have a system in which this rule is admissible.
+	\begin{remark}
+
+		The rules $\llabrn{cont}$ and $\rlabrn{cont}$ are admissible for $\labIKp$.
+		\begin{center}
+			$\vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}$\quad\quad$\vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}$
+		\end{center}
+	\end{remark}
+	\begin{proof}
+		The rule $\llabrn{cont}$ can be derived using $\rn{refl}$ and $\llabrn{mon}$ which is admissible by Proposition 3.1.
+
+		\begin{center}
+			$\vlderivation{
+				\vlin{\rn{refl}}{}
+				{\B, \Left, \labels{x}{A} \SEQ \Right}
+				{\vlin{\llabrn{mon}}{}
+					{\B, \futs{x}{x}, \Left, \labels{x}{A} \SEQ \Right}
+					{\vlhy{\B, \futs{x}{x}, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}}}
+			}$
+		\end{center}
+
+		The case for $\rlabrn{cont}$ is similar.
+	\end{proof}
+	}
 In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:

### 2020-08-31 FullyLabelled/JLC/reviews/notes.tex
adding more TODO
adding comments to notes file

@@
 \end{itemize}
-\todo{Add next remark to the paper with a small explanation:}
+\todo{Add next remark to the paper}
+
 \begin{remark}
@@
 
-\todo{Add next proof as an example and a paragraph explaning.}
+\todo{Add next proof as an example} \marianela{How should I introduce this in the extensions section?}
 $$
@@
 	\item \emph{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in
-	detail, as otherwise the authors’ work would rather look a routine exercise.}: \todo{add a paragraph about constructive modal logics.}
+	detail, as otherwise the authors’ work would rather look a routine exercise.}: \todo{add a paragraph about constructive modal logics.} \marianela{using the Skolemization thing (Review 2)?} 
 	\item \todo{Add a paragraph with all the references we are missing.} 
+	\item \emph{They then claim that their calculus is inspired by a ”multiple-conlusion nested sequent
+		system a la Maehara”.
+Such a calculus in fact has appeared in a work which the authors	cite as unpublished, but which seems to have been published in the meantime [Archive for Mathematical Logic (2019) 58:359–385], which reference needs to be updated accordingly.} \marianela{What did she mean?}
+	\item \emph{The rules of their calculus are identical (except for the ones that relate the two accessibility relations) to the rules for the intuitionistic-alethic fragment of the calculus for intuitionistic bimodal logic in this publication:
+		• Maffezioli, P., Naibo, A.
+\& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory.
+Synthese, vol.
+190, 2677–2716, 2013.} {\color{green}Fixed: adding that we have internal cut.}
 \end{itemize}
@@
 I was thus expecting either a Skolemization in the style of Vigano in the ``Labelled Non-Classical Logics" book, or a geometric rule with existential quantification in the style of Simpson [Sim94] or, perhaps even better, a “mixed” rule where the labels are	assumed more or less in the style of an $\exists$ elimination to derive a labeled formula.
-\todo{}
+\todo{SONIA}
 		\end{itemize}}
@@
 Show the ``need" you would likely have to show that no other proofs of the axioms are possible.
-That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.}:
-
-	There are two options: 
-	\todo{Do not use the word ``need''.}
+That is of course the case, but unless you prove it formally, it is not fully correct to claim that the ``need'' is shown.} {\color{green}Fixed.}
 
@@
 
+We do not need contraction. We have an internal cut elimination. That's why it is a novelty.
 \end{document}

### 2020-09-01 FullyLabelled/JLC/main.tex
adding todo to the main file

--- 2019-10-03 caleidoscope/main.tex
@@
 \documentclass[a4paper]{article}
-
+\usepackage{authblk}
 \input{new-macros}
 
-%\begin{frontmatter}
 \title{A fully labelled proof system for intuitionistic modal logics}
-\author{Sonia Marin \and %}
-	%  \address{University College London \\ United Kingdom }
-	%    \author{
-	Marianela Morales %}
-	\and
-	% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-	%      \author{
-	Lutz Stra{\ss}burger }
-% \address{Inria Saclay \& LIX, \'Ecole Polytechnique \\ France}
-%% \begin{keyword}
-%% Intuitionistic modal logic, labelled sequents, cut elimination, proof theory.
-%% \end{keyword}
-% \end{frontmatter}
+\author[1]{Sonia Marin} 
+\author[2,3]{Marianela Morales}
+\author[3,2]{Lutz Stra{\ss}burger}
+\affil[1]{University College London}
+\affil[2]{Laboratoire d'informatique d'\'Ecole polytechnique}
+\affil[3]{Inria Saclay}
+
+\date{}
 
@@
  \begin{abstract}
+ 	\review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}\todo{Lutz}
    In this paper we present a labelled sequent system for
@@
 \input{extensions}
+\input{conclusion}
 

### 2020-09-01 FullyLabelled/JLC/introduction.tex
adding todo to the main file
sec 1 and 2

@@
 \section{Introduction}\label{sec:intro}
+\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
+\todo{add a paragraph about constructive modal logics.} \lutz{I forgot what we agreed on here...}
 
@@
 intuitionistic logic.
-%
+
+A system similar to ours is presented
+in~\cite{maffezioli:etal:synthese13}, for intuitionistic bimodal
+epistemic logic. That system is also a multi-conclusion labelled system with
+more than one relation. In fact, the logical rules are essentially the
+same as ours. But we use a more general setting and provide deductive proof
+systems for a larger class of intuitionistic modal logics, together
+with an internal cut elimination procedure.
 
@@
   • Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
+\lutz{done in previous paragraph? can this be removed: 
+\old{
 Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.
@@
 	This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.
-Furthermore, we present in this contribution an internal cut elimination proof.}
+Furthermore, we present in this contribution an internal cut elimination proof.}}?}
 
@@
 \todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
+\lutz{I've added a refence to \cite{bovzic1984models} in sec.2. But \cite{maffezioli2014} is totally unrelated, and I don't see the point in citing that}
 %\todo{maybe paragraph on related work?}

### 2020-09-01 FullyLabelled/JLC/main.tex
sec 1 and 2

@@
  \begin{abstract}
- 	\review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}\todo{Lutz}
+ 	\review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}\lutz{Not yet done. I am waiting for Sect.7}
    In this paper we present a labelled sequent system for

### 2020-09-01 FullyLabelled/JLC/preliminaries.tex
sec 1 and 2

@@
 %
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.
+It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.\footnote{This semantics and some variants have also been studied in~\cite{bovzic1984models}.
+For an excellent survey on possible variants see~\cite{simpson:phd}.}
 

### 2020-09-01 FullyLabelled/JLC/system.tex
sec. 3-5

--- 2019-10-08 caleidoscope/system.tex
@@
 order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.
+$\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{DN12}.\todo{Dyckhoff,Negri:Proof Analysis in Intermediate Logics}}
+
 %
-These can be obtained by applying the axioms-as-rules methodology as in~\cite{maffezioli:etal:synthese13}.
+%%These can be obtained by applying the axioms-as-rules methodology as in~\cite{maffezioli:etal:synthese13}.
 
@@
 \end{proof}
+
+\begin{remark}
+  As mentioned above, the monotonicity rules $\llabrn{mon}$ and $\rlabrn{mon}$ are a form of contraction. So, it is not a surprise that the contraction rules
+  \begin{equation*}
+    \vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}
+    \hskip8em
+    \vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}
+  \end{equation*}
+  are admissible in our system, as they are derivable as follows:
+  \begin{equation*}
+    \vlderivation{
+      \vlin{\rn{refl}}{}
+	   {\B, \Left, \labels{x}{A} \SEQ \Right}
+	   {\vlin{\llabrn{mon}}{}
+	     {\B, \futs{x}{x}, \Left, \labels{x}{A} \SEQ \Right}
+	     {\vlhy{\B, \futs{x}{x}, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}}}
+    }
+    \hskip6em
+      \vlderivation{
+      \vlin{\rn{refl}}{}
+	   {\B, \Left \SEQ \Right, \labels{x}{A}}
+	   {\vlin{\rlabrn{mon}}{}
+	     {\B, \futs{x}{x}, \Left \SEQ \Right, \labels{x}{A}}
+	     {\vlhy{\B, \futs{x}{x}, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}}}
+    }
+
+  \end{equation*}
+
+\review{the authors of the paper under review neglect an important caveat in the design of rules of contraction-free labelled sequent calculi: to guarantee that contraction be admissible one needs to ensure that a certain closure condition be satisfied, see:
+
+\emph{• Negri, S. Proof analysis in modal logic. Journal of Philosophical Logic, 34, 507–544, 2005.}}\lutz{I think the remark above takes care of that.}
+
+%\marianela{Should we mention Negri's paper here? }
+
+%\marianela{In the same way as we did with monotonicity, trying to avoid the problems that contraction has in a cut elimination proof, it is preferable to have a system in which this rule is admissible.
+%	}
+
+\review{Also the proofs of the structural properties closely follow the methodology of the paper by Maffezioli, Naibo \& Negri.
+All this has to be said expressis verbis, and appropriate citations have to be added.}
+%\marianela{we are not saying that in the next paragraph?}
+\lutz{I just checkt again, and I refuse to do that.
+I see two ways to proceed: Either we just ignore the comment, or we write in the answer to the reviewer that the whole procedure is standard (and we can even cite in the paper the Troelstra-Schwichtenberg Textbook).
+We do cite that paper somewher, but they should not get more credit than they deserve.}

### 2020-09-07 FullyLabelled/JLC/system.tex
minor fix
todo of references done

@@
 order to capture that in the proof system, we need to add the rules
-$\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{DN12}.\todo{Dyckhoff,Negri:Proof Analysis in Intermediate Logics}}
+$\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{dyckhoff2012}.}
 
@@
     }
-
  \end{equation*}
+\end{remark}
 

### 2020-09-08 FullyLabelled/JLC/introduction.tex
discussion

@@
 \section{Introduction}\label{sec:intro}
-\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
-\todo{add a paragraph about constructive modal logics.} \lutz{I forgot what we agreed on here...}
 
@@
 \todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
-\lutz{I've added a refence to \cite{bovzic1984models} in sec.2. But \cite{maffezioli2014} is totally unrelated, and I don't see the point in citing that}
+\lutz{I've added a refence to \cite{bovzic1984models} in sec.2.
+But \cite{maffezioli2014} is totally unrelated, and I don't see the point in citing that}\todo{cite them when we indroduce F1 and F2, because they have something similar}
 %\todo{maybe paragraph on related work?}

### 2020-09-08 FullyLabelled/JLC/preliminaries.tex
discussion

@@
 \section{Intuitionistic modal logics}\label{sec:intmod}
+
+\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
+\todo{add a paragraph about constructive modal logics.}
+
 The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.

### 2020-09-15 FullyLabelled/JLC/system.tex
reformating extensions

@@
 We do cite that paper somewher, but they should not get more credit than they deserve.}
+
+\todo{}
+\sonia{
+	The rule corresponding to the $F_1$ was obtained through the standard axioms-to-rule procedure that is well known for geometric axioms. 
+%
+A similar rule can already be found in~\cite{maffezioli2014}.
+%
+It corresponds to attributing a positive polarity to both relational and pre-order atoms.
+
+$$\vlinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
+
+On the other hand, a different rule for $F_1$ could be obtained in the style of Vigano, that is, by polarising both relational and pre-order atoms negatively, as follows:
+
+$$\vliiinf{}{\lb u \mbox{ fresh}}{\B, \Gamma \SEQ \Delta}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \futs yz, \Gamma \SEQ \Delta}{\futs xu, \accs uz, \Gamma \SEQ \Delta}$$
+
+\lutz{we should say that this is pretty pointless wrt proof search.}
+It is also possible to design a "mixed" rule, by considering relational atoms positively and pre-order atoms negatively:
+
+$$\vliinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
+
+Or vice-versa:
+
+$$\vliinf{}{\lb u \mbox{ fresh}}{\B, \futs yz, \Gamma \SEQ \Delta}{\B, \futs yz, \accs xy, \Gamma \SEQ \Delta}{\futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
+}

### 2020-09-15 FullyLabelled/JLC/introduction.tex
footnote

@@
 \todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
-\lutz{I've added a refence to \cite{bovzic1984models} in sec.2.
-But \cite{maffezioli2014} is totally unrelated, and I don't see the point in citing that}\todo{cite them when we indroduce F1 and F2, because they have something similar}
+\lutz{I've added a refence to \cite{bovzic1984models} in sec.2, and \cite{maffezioli2014} in a footnote in sec.3}
 %\todo{maybe paragraph on related work?}

### 2020-09-15 FullyLabelled/JLC/system.tex
footnote

@@
 Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
+strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$.
+These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.\footnote{The logic studied in~\cite{maffezioli2014} has similar semantic conditions (two binary relations in a Kripke frame) that lead to similar rules as ours in the proof system.}
 %

### 2020-09-17 FullyLabelled/JLC/review-answer.txt
draft of response

Dear Didier,

thank you very much for the reviews. We are very grateful to the
reviewers for their helpful comments, which enabled us to considerably
improve our paper.

We took all comments and remarks into account, and below we address
the reviewers comments in detail.

One of the main concerns of Reviewer 1 is that we have not cited all
the relevant literature. We thank the reviewer for pointing out the
missing references and added them accordingly.

We anow address the other comments:

>  Perhaps even more importantly, the authors of the paper under
>  review neglect an important caveat in the design of rules of
>  contraction-free labelled sequent calculi: to guarantee that
>  contraction be admissible one needs to ensure that a certain
>  closure condition be satisfied

We already said in the submitted version that in our system
contraction is derivable from the monotonicity rules, which in turn
are admissible. We made this even more clear in the new version in
Remark XXXXX.

>  In Section 7, if the rules G_klmn are added without their
>  contracted instances, the calculus will not be complete. For
>  example, in the classical case, Euclidean transitivity ∀a, b,
>  c(aRb&aRc → bRc) has the contracted instance ∀a, b(aRb → bRb) that
>  allows for the derivation of BOX(BOX A → A). This, however, can
>  hardly be derived without the rule’s contracted instance.

In fact, the contracted instances are added. In the same way as for
other rules, occurring labels can be equal. We failed to make this
explicit in the first submitted version and corrected that mistake in
Remark XXXXXXXXXX

>  On top of this, the authors’ claim that labelled calculi ”work best
>  for logics with standard Kripke semantics” is utterly wrong:
>  labelled calculi have been developed for several variants of Kripke
>  semantics, such as Lewis’s semantics for counterfactuals,
>  neighbourhood semantics, Kripke semantics of impossible worlds, and
>  so on.

If something works best for A, it does not mean that it won't work for
B. All we tried to say was that for logics with the standard Kripke
semantics there is this close relationship between the semantics and
the labels in the proof system.

>  In conclusion, the paper does not look highly original. The
>  birelational semantics is not a novelty, nor a calculus
>  internalising that semantics appears an original idea.

We never claim the birelational semantics to be a novelty (it goes
back to the 1980s). Our paper is not about semantics but about about
proof systems. And our system allows for extenstions that could not be
studied before. We made this more clear in the new version (see
Section 7).

>  Also the reason for preferring one semantics for intuitionistic
>  modal logic over another should be discussed in detail, as
>  otherwise the authors’ work would rather look a routine exercise

We are puzzled by this comment, as we just picked the standard
semantics for intuitionistic modal logic, and semantics is not a
concern of our paper. However, we added in the conclusion some
comments on constructive modal logics, which are another variant of
adding BOX and DIAMOND to intuitionistic propositional logic.

The main concern of reviewer 2 is the lacking detail in the section on extensions. We tried to fix this

TODO

"need"

abstract

### 2020-09-17 FullyLabelled/JLC/conclusion.tex
draft of response

--- 2019-12-03 caleidoscope/conclusion.tex
@@
 \section{Conclusion}
+
+\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
+\todo{add a paragraph in conclusion: saying that it is an interesting idea to applly method to CK, but extension is tricky \cite{ADS:lmcs}}
 

### 2020-09-17 FullyLabelled/JLC/introduction.tex
draft of response

@@
 frame conditions corresponding to the desired logic can be directly
-encoded as inference rules. Prominent examples are classical modal
+encoded as inference rules.
+\todo{Reviewer 1 complained about the ``best''}
+Prominent examples are classical modal
 logics and intuitionistic propositional logic, where, e.g., the frame

### 2020-09-21 FullyLabelled/JLC/introduction.tex
I was wrong

@@
   • Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
-\lutz{done in previous paragraph? can this be removed: 
-\old{
-Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.
-%
-\marianela{
-	Our system uses the same principle, both labelled and multi-conclusion sequents, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics.
-	%
-	This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.
-Furthermore, we present in this contribution an internal cut elimination proof.}}?}
+\lutz{done in previous paragraph? can this be removed: }
+%\old{
+%Maffezioli, Naibo and Negri have considered in~\cite{maffezioli:etal:synthese13} a labelled system for intuitionistic bimodal epistemic logic which is multi-conclusion.}
+%%
+%\marianela{
+%	Our system uses the same principle, both labelled and multi-conclusion sequents, but we use in a more general setting and extend it to a framework for many intuitionistic modal logics.
+%	%
+%	This eliminates the undesired discrepancy as, consequently, every rule in our system is invertible, i.e.~we never delete information in a bottom-up proof search.
+Furthermore, we present in this contribution an internal cut elimination proof.}
 

### 2020-09-21 FullyLabelled/JLC/system.tex
I was wrong

--- 2020-09-07 FullyLabelled/JLC/system.tex
@@
 $\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{dyckhoff2012}.}
-
 %
 %%These can be obtained by applying the axioms-as-rules methodology as in~\cite{maffezioli:etal:synthese13}.
+%
+Finally, in the semantics, the two relations $\rel$ and $\le$ are
+strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$.
+These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.\footnote{The logic studied in~\cite{maffezioli2014} has similar semantic conditions (two binary relations in a Kripke frame) that lead to similar rules as ours in the proof system.}
 
-Finally, in the semantics, the two relations $\rel$ and $\le$ are
-strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.
+\sonia{
+The rules corresponding to reflexivity, transitivity, $F_1$ and $F_2$ are obtained through the standard axioms-to-rule procedure that is well known for geometric axioms, and applies more generally to bipolar axioms.
 %
-However, these two rules create new labels, and in order to be
+It corresponds to attributing a positive bias to both relational and pre-order atoms in the procedure established in~\cite{marin:etal:submitted}.
+%
+On the other hand, by polarising both relational and pre-order atoms negatively, a different shape of rules can be obtained in the style of Vigan\`o~\cite{vigano:00}. 
+%
+For example $F_1$ could be incorporated to the system as a pair of rules of the following form:
+$$\vliinf{}{}{\B, \Gamma \SEQ \Delta, \futs x{f(x,y,z)}}{\B, \Gamma \SEQ \Delta, \accs xy}{\B, \Gamma \SEQ \Delta, \futs yz}
+\qquad
+\vliinf{}{}{\B, \Gamma \SEQ \Delta, \accs {g(x,y,z)}z}{\B, \Gamma \SEQ \Delta, \accs xy}{\B, \Gamma \SEQ \Delta, \futs yz}$$
+%
+These rules are equiderivable to the one on Fig.~\ref{fig:labIKp}; note however that it is read top-down and not appropriate for proof search.	
+\lutz{we should say that this is pretty pointless wrt proof search.}
+%
+It is also possible to design a ``mixed" rule, by considering relational atoms positively and pre-order atoms negatively, or vice-versa.
+%$$
+%\vliinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs xu, \accs uz, \Gamma \SEQ \Delta}
+%\qquad	
+%\vliinf{}{\lb u \mbox{ fresh}}{\B, \futs yz, \Gamma \SEQ \Delta}{\B, \futs yz, \accs xy, \Gamma \SEQ \Delta}{\futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
+}
+
+Rules for $F_1$ and $F_2$ require to create new labels, and in order to be
 complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 

### 2020-09-22 FullyLabelled/JLC/system.tex
moving remark to Sec 7

--- 2020-09-15 FullyLabelled/JLC/system.tex
@@
 $\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{dyckhoff2012}.}
-
 %
@@
 %
-However, these two rules create new labels, and in order to be
+These rules require to create new labels, and in order to be
 complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
@@
 We do cite that paper somewher, but they should not get more credit than they deserve.}
-
-\todo{}
-\sonia{
-	The rule corresponding to the $F_1$ was obtained through the standard axioms-to-rule procedure that is well known for geometric axioms. 
-%
-A similar rule can already be found in~\cite{maffezioli2014}.
-%
-It corresponds to attributing a positive polarity to both relational and pre-order atoms.
-
-$$\vlinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
-
-On the other hand, a different rule for $F_1$ could be obtained in the style of Vigano, that is, by polarising both relational and pre-order atoms negatively, as follows:
-
-$$\vliiinf{}{\lb u \mbox{ fresh}}{\B, \Gamma \SEQ \Delta}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \futs yz, \Gamma \SEQ \Delta}{\futs xu, \accs uz, \Gamma \SEQ \Delta}$$
-
-\lutz{we should say that this is pretty pointless wrt proof search.}
-It is also possible to design a "mixed" rule, by considering relational atoms positively and pre-order atoms negatively:
-
-$$\vliinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
-
-Or vice-versa:
-
-$$\vliinf{}{\lb u \mbox{ fresh}}{\B, \futs yz, \Gamma \SEQ \Delta}{\B, \futs yz, \accs xy, \Gamma \SEQ \Delta}{\futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$
-}

### 2020-09-22 FullyLabelled/JLC/main.tex
abstract

--- 2020-09-01 FullyLabelled/JLC/main.tex
@@
  \begin{abstract}
- 	\review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}\todo{Lutz}
+   \review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
+   \lutz{Done?}
    In this paper we present a labelled sequent system for
@@
    %%
-   We also show an internal cut elimination proof for our system.
+   We show soundness and completeness of our system, together with an internal cut elimination proof.
+   %%
+   Finally, we show how the system can be extended with arbitrary intuitionistic Scott-Lemmon axioms.
  \end{abstract}

### 2020-09-22 FullyLabelled/JLC/review-answer.txt
I was wrong
letter

@@
 
-We anow address the other comments:
+We now address the other comments:
 
@@
 
-The main concern of reviewer 2 is the lacking detail in the section on extensions. We tried to fix this
+Reviewer 2 finds this paper well written, but has some technical
+concerns. We address them below.
+
+>  The main issue is indeed with the "wide range of logics”. While the
+>  base logic is discussed in detail, the range of logics is treated
+>  in an “Extensions” section that I believe could actually be more
+>  detailed.
 
@@
 
-"need"
+>  Most importantly, I am not convinced by the gklmn rule. The side
+>  condition stipulates that y’ and u are fresh, whereas the frame
+>  property contains existential quantifications. I was thus expecting
+>  either a Skolemization in the style of Vigano in the “Labelled
+>  Non-Classical Logics” book, or a geometric rule with existential
+>  quantification in the style of Simpson [Sim94] or, perhaps even
+>  better, a “mixed” rule where the labels are assumed more or less in
+>  the style of an \exists elimination to derive a labeled formula.  I
+>  think that a thorough discussion of the alternatives, along with a
+>  more thorough proof of the correctness of the chosen solution, is
+>  needed.
 
-abstract
+We added Remark 7.5 to discuss this. Our rules are in fact in the
+style of Simpson, but we added a comparison to Vigano's method.
+
+>  By the way, it does not help at all that the applications of the
+>  rule g1111 are merged with \Box_L and \Diamond_R in the example
+>  derivation.
+
+We fixed that.
+
+>  Also Remark 4.2 could benefit from some additional explanation. You
+>  write that the proof of Theorem 4.1 shows the “need” of the rules
+>  F_1, refl and trans. However, strictly speaking, the proof only
+>  shows how the rules are used and that they are helpful to prove the
+>  axioms. To show the “need" you would likely have to show that no
+>  other proofs of the axioms are possible. That is of course the
+>  case, but unless you prove it formally, it is not fully correct to
+>  claim that the “need” is shown. This is pedantic, I know.
+
+We just removed the "need".

### 2020-09-28 FullyLabelled/JLC/review-answer.txt
letter
one comment

@@
 thank you very much for the reviews. We are very grateful to the
-reviewers for their helpful comments, which enabled us to considerably
-improve our paper.
+reviewers for their comments, which helped us improve our paper.
 
@@
 
-TODO
+We extended this section with more explanation and also added a few
+more comments and remarks.
 

### 2020-09-28 FullyLabelled/JLC/review-answer.txt
woring on the letter

@@
 the relevant literature. We thank the reviewer for pointing out the
-missing references and added them accordingly.
+missing references and we added them accordingly.
 
@@
 are admissible. We made this even more clear in the new version in
-Remark XXXXX.
+Remark 3.4.
 
@@
 other rules, occurring labels can be equal. We failed to make this
-explicit in the first submitted version and corrected that mistake in
-Remark XXXXXXXXXX
+explicit in the first submitted version and corrected that mistake in Remark 7.2.
 
@@
 
-If something works best for A, it does not mean that it won't work for
-B. All we tried to say was that for logics with the standard Kripke
-semantics there is this close relationship between the semantics and
-the labels in the proof system.
+If something works best for A, it does not mean that it won't work for B. 
+All we tried to say was that for logics with the standard Kripke semantics 
+there is this close relationship between the semantics and the labels in 
+the proof system.
 
@@
 We never claim the birelational semantics to be a novelty (it goes
-back to the 1980s). Our paper is not about semantics but about about
+back to the 1980s). Our paper is not about semantics but about
 proof systems. And our system allows for extenstions that could not be 
@@
 
-Reviewer 2 finds this paper well written, but has some technical
-concerns. We address them below.
+On the other side, Reviewer 2 finds this paper well written, but has some 
+technical concerns. We address them below.
 
@@
 
-We extended this section with more explanation and also added a few
-more comments and remarks.
+We put more emphasis on the section 7 in order to make clearer how to generate "stronger
+logics" adding new axioms to our system. We extended this section with more explanation and 
+we also added a few more comments and remarks. For example, as a better way to understand the extensions, 
+we also illustrated the specific case of adding to IK the 4-axiom.
 
@@
 
-We added Remark 7.5 to discuss this. Our rules are in fact in the
-style of Simpson, but we added a comparison to Vigano's method.
+\marianela{not sure what to put here} We added Remark 7.5 to discuss this. 
+Our rules are in fact in the style of Simpson, but we added a comparison to Vigano's method.
 
@@
 
-We fixed that.
+Following this comment, we fixed the derivation on the paper in order to 
+show better the use of the rule g1111.
 
@@
 
-We just removed the "need".
+In this case, we chose to change the word "need" with the word "use".
+Our intention on this, was to try to show how to apply those rules and how useful there are
+in our proofs.

### 2020-09-28 FullyLabelled/JLC/review-answer.txt
letter
adding more items to the letter
more comments to the letter

@@
 other rules, occurring labels can be equal. We failed to make this
-explicit in the first submitted version and corrected that mistake in Remark 7.2.
+explicit in the first submitted version and corrected that mistake in 
+Remark 7.2.
 
@@
 
-We put more emphasis on the section 7 in order to make clearer how to generate "stronger
-logics" adding new axioms to our system. We extended this section with more explanation and 
-we also added a few more comments and remarks. For example, as a better way to understand the extensions, 
+We put more emphasis on the section 7 in order to make more clear how to 
+generate "stronger logics" adding new axioms to our system. We extended 
+this section with more explanation and we also added a few more comments 
+and remarks. For example, as a better way to understand the extensions, 
 we also illustrated the specific case of adding to IK the 4-axiom.
@@
 In this case, we chose to change the word "need" with the word "use".
-Our intention on this, was to try to show how to apply those rules and how useful there are
-in our proofs.
+Our intention on this, was to try to show how to apply those rules and how 
+useful there are in our proofs.
+
+>Reconsider de abstract. It reads very operational and does not clearly state the
+>contributions of the paper.
+
+We also consider this comment of the Reviewer with the aim of better reflecting 
+our contribution in the paper.
+
+Finally, as the Reviwer 2 pointed out, we fixed some broken references.
+
+We want to thank the reviewers again for their time and for helping us improve our paper. 
+We hope to be able to show our interest in answering each of the points marked by each reviewer.

### 2020-09-29 FullyLabelled/JLC/conclusion.tex
progress on section 7

@@
 \section{Conclusion}
-
-\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
-\todo{add a paragraph in conclusion: saying that it is an interesting idea to applly method to CK, but extension is tricky \cite{ADS:lmcs}}
 
@@
 It would be interesting to know how and where the class of logics we considered can be included in their framework.
+
+\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
+\todo{add a paragraph in conclusion: saying that it is an interesting idea to applly method to CK, but extension is tricky \cite{ADS:lmcs}}
+
+\review{Most importantly, I am not convinced by the gklmn rule.
+The side condition stipulates that $\lb y'$ and $\lb u$ are fresh, whereas the frame property contains existential quantifications.
+I was thus expecting either a Skolemization in the style of Vigano in the ``Labelled Non-Classical Logics" book, or a geometric rule with existential quantification in the style of Simpson [Sim94] or, perhaps even better, a “mixed” rule where the labels are	assumed more or less in the style of an $\exists$ elimination to derive a labeled formula.}
+\todo{add coment on this}
+
+The rules $gklmn$ (similarly to those corresponding to reflexivity, transitivity, $F_1$ and $F_2$) are obtained through the standard axioms-to-rule procedure that is well known for geometric axioms, and applies more generally to bipolar axioms~\cite{marin:etal:submitted} (by assuming a positive bias on atoms).
+%
+On the other hand, a different shape of rules can be obtained in the style of Vigan\`o~\cite{vigano:00 } (by assuming atoms are negative polarised). 
+%
+For reflexivity and transitivity of the preorder relation, this would give:
+%
+$$
+\vlinf{}{}{\Gamma \SEQ \Delta, \futs xx}{}
+\qquad
+\vliinf{}{}{\Gamma \SEQ \Delta, \futs xz}{\Gamma \SEQ \Delta, \futs xy}{\Gamma \SEQ \Delta, \futs yz}
+$$
+%
+We conjecture that $\ax{F_1}$ could be incorporated to the system as a pair of rules of the following form:
+$$\vliinf{}{}{\B, \Gamma \SEQ \Delta, \futs x{f(x,y,z)}}{\B, \Gamma \SEQ \Delta, \accs xy}{\B, \Gamma \SEQ \Delta, \futs yz}
+\qquad
+\vliinf{}{}{\B, \Gamma \SEQ \Delta, \accs {g(x,y,z)}z}{\B, \Gamma \SEQ \Delta, \accs xy}{\B, \Gamma \SEQ \Delta, \futs yz}$$
+%
+where $f$ and $g$ are (Skolem) function constants.
+%
+Note however that these require (relational and preorder) atoms to appear on the right-hand-side of the sequent and are to be read top-down, and therefore are not appropriate for proof search.	
+%	\lutz{we should say that this is pretty pointless wrt proof search.}
+%
+It should also possible to design a ``mixed" rule, by considering relational atoms positively and pre-order atoms negatively, or vice-versa, and we leave this investigation for future work.
+%$$
+%\vliinf{}{\lb u \mbox{ fresh}}{\B, \accs xy, \Gamma \SEQ \Delta}{\B, \accs xy, \futs yz, \Gamma \SEQ \Delta}{\accs xy, \futs xu, \accs uz, \Gamma \SEQ \Delta}
+%\qquad	
+%\vliinf{}{\lb u \mbox{ fresh}}{\B, \futs yz, \Gamma \SEQ \Delta}{\B, \futs yz, \accs xy, \Gamma \SEQ \Delta}{\futs yz, \futs xu, \accs uz, \Gamma \SEQ \Delta}$$

### 2020-09-29 FullyLabelled/JLC/introduction.tex
progress on section 7

@@
 
-Standard labelled sequent calculi attach to every formla $\fm A$ a label
+Standard labelled sequent calculi for logics with
+standard Kripke semantics attach to every formla $\fm A$ a label
 $\lb x$, witten as $\labels xA$, and additionally use
-\emph{relational atoms} of the form $\accs xy$ where $\rel$ is a
-binary relation symbol. These calculi work best for logics with
-standard Kripke semantics, as in this case the relation $\rel$ is used
-to encode the accessibility relation in the Kripke models, and the
+\emph{relational atoms} of the form $\accs xy$ where 
+the binary relation symbol $\rel$
+%These calculi work best for logics with
+%standard Kripke semantics, as in this case the relation $\rel$ 
+is used to encode the accessibility relation in the Kripke models, such that
 frame conditions corresponding to the desired logic can be directly
 encoded as inference rules.
-\todo{Reviewer 1 complained about the ``best''}
+%\todo{Reviewer 1 complained about the ``best''}
 Prominent examples are classical modal
-logics and intuitionistic propositional logic, where, e.g., the frame
-condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$), can be straightforwardly translated into the
+logics and intuitionistic propositional logic, e.g., the frame
+condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be translated into the
 inference rule
@@
 where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas.
+$\Delta$ for multi-sets of labelled formulas~\cite{negri:vonplato:01}.
 
@@
 in this paper we are concerned with \emph{intuitionistic modal
-	logics}, whose Kripke semantics is based on \emph{birelational}
+logics} whose Kripke semantics is based on \emph{birelational}
 frames, i.e., they have two binary relations instead of one: one
@@
 	\label{eq:4ax}
-	\fm{\BOX A\IMP \BOX\BOX A}
+	\ax{4^{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
 	\qquand
-	\fm{\DIA\DIA A\IMP\DIA A}
-	\quadcm
+	\rn{4^{\DIA}}\colon\fm{\DIA\DIA A\IMP\DIA A}
+%	\quadcm
 	\end{equation}
@@
 	modal logic. However, in intuitionistic modal logic they are not
-	equivalent, and even though the logic $\IKfour$, i.e., the
-	intuitionistic version of the modal logic $\Kfour$, contains both
-	axioms, they can also be added independently to the logic $\IK$ (an
-	intuitionistic version of $\K$). The proof theory of these
-	new logics has not been studied before; no existing labelled (or
-	label-free) proof system can handle them, even though the
+	equivalent, and even though the logic $\IKfour$ 
+	(intuitionistic version of modal logic $\Kfour$) contains both
+	axioms, they can also be added independently to the logic $\IK$ 
+	(intuitionistic version of $\K$). The proof theory of these
+	distinct logics has not been discussed before, but their
 	corresponding frame conditions
@@
 	\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
-	\;,
+	\;
 	\end{equation}
@@
 	$$
-	respectively, have already been studied
-	in~\cite{plotkin:stirling:86}.
+	respectively, have been studied in~\cite{plotkin:stirling:86}.
 	%  \sonia{the general condition is correct but not the application to 4}
@@
 	as clean as one would expect. As only the $R$-relation (and not the
-	$\le$-relation) of the frame is visible in an ordinary labelled
-	sequent, we only have that a sequent $\Gamma$ is provable if and
-	only if is satisfied in all \emph{graph-consistent}\footnote{This
+	$\le$-relation) is visible in an ordinary labelled
+	sequent, we only have that a formula is provable in an extension of $\IK$ beyond paths axioms 
+	if and only if is satisfied in all \emph{graph-consistent}\footnote{This
 		means that every layer in the model can be lifted to any future of
 		any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.}   
-	models, 
+	models satisfying the corresponding conditions, 
 	%  \sonia{this is only true for logics outside of the path axioms.}
@@
 	%  \sonia{yes, they are sound and complete for the general models, but they do not \emph{characterize} the frames, they are not \emph{frame conditions}, as opposed to the \emph{correspondence result} of Plotkin and Sterling.}
-	as already observed in by Simpson in his PhD thesis~\cite{simpson:phd}
-	and considered as an inelegant solution (see also \cite{mar:str:tableaux17}).
+	as observed by Simpson
+	and considered as an inelegant solution~\cite{simpson:phd}. % (see also \cite{mar:str:tableaux17}).
 \end{enumerate}
@@
 labelled sequent by allowing both, relational atoms of the
-form $\futs xy$ and of the form $\accs xy$. Consequently, we can easily translate the frame
+form $\futs xy$ and of the form $\accs xy$. 
+%%
+Consequently, following the same ``axiom-to-rule'' method as Simpson, we can translate the frame
 conditions in~\eqref{eq:4frame} into inference rules:
@@
 This allows us to define cut-free deductive systems for a wide range
-of logics that could not be treated before.  Furthermore, the relation
-between syntax and semantics is as one would expect: A sequent is
-provable in our system if and only if it is valid in all models.
+of logics that had been treated proof-theoretically before.  
+%%
+Furthermore, the relation
+between syntax and semantics can be recovered as one would expect: A formula is
+provable in this system if and only if it is valid in all models satisfying the corresponding frame condition.
 
@@
   • Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
-\lutz{done in previous paragraph? can this be removed: }
+\lutz{done in previous paragraph?}
 %\old{
@@
 Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:soundness} and~\ref{sec:completeness}, we show soundness and completeness of the system with cut.
+In Sections~\ref{sec:completeness} and~\ref{sec:soundness}, we show soundness and completeness of the system with cut.
 The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture other intuitionistic modal logics.
+Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture intuitionistic Scott-Lemmon modal logics.
 

### 2020-09-29 FullyLabelled/JLC/main.tex
progress on section 7

@@
 \affil[1]{University College London}
-\affil[2]{Laboratoire d'informatique d'\'Ecole polytechnique}
+\affil[2]{Laboratoire d'Informatique de l'\'Ecole Polytechnique}
 \affil[3]{Inria Saclay}
@@
  \begin{abstract}
-   \review{Reconsider de abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
+   \review{Reconsider abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
    \lutz{Done?}
-   In this paper we present a labelled sequent system for
+   \sonia{Added two setences at the beginning and modified it a bit.}
+   Labelled proof theory has been famously successful for modal logics by mimicking their relational semantics within deductive systems.
+Simpson in particular designed a framework to study a variety of intuitionistic modal logics integrating a binary relation symbol in the syntax.
+   %%
+   In this paper, we present a labelled sequent system for
    intuitionistic modal logics such that there is not only one, but
@@
    This puts our system in close correspondence with the standard
-   birelational Kripke semantics for intuitionistic modal logics. As a
-   consequence it can encompass a wider range of intuitionistic modal
-   logics than existing labelled systems.
+   birelational Kripke semantics for intuitionistic modal logics. 
    %%
-   We show soundness and completeness of our system, together with an internal cut elimination proof.
+   As a consequence it can be extended with arbitrary intuitionistic Scott-Lemmon axioms. 
    %%
-   Finally, we show how the system can be extended with arbitrary intuitionistic Scott-Lemmon axioms.
+   We show soundness and completeness, together with an internal cut elimination proof, encompassing a wider array of intuitionistic modal logics than any existing labelled systems.
  \end{abstract}

### 2020-09-29 FullyLabelled/JLC/conclusion.tex
final pass through paper for now

--- 2020-09-17 FullyLabelled/JLC/conclusion.tex
@@
 
-\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
-\todo{add a paragraph in conclusion: saying that it is an interesting idea to applly method to CK, but extension is tricky \cite{ADS:lmcs}}
-
-In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and generalise it to the class of logics defined by (one-sided intuitionistic) Scott-Lemmon axioms.
+In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and generalise it to the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
 %
@@
 
-For a restricted class of logics defined by so-called \emph{path axioms}: $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
+For a restricted class of these logics defined by so-called \emph{path axioms}: $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
 %
@@
 
-However, we have not showed that our system satisfies Simpson's 6th requirement, that is, "there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [our system] is sound and complete".
+However, we have not showed that our system satisfies Simpson's 6th requirement, that is, ``there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [the system] is sound and complete".
 %
@@
 %
-We instead took the way of a direct correspondence of our system with the class of frames defined by Scott-Lemmon axioms as uncovered by~\cite{plotkin:stirling:86}, but as this class of logics seems to be rather well-behaved, we believe it shoud be possible to prove the satisfaction of Simpson's 6th requirement too.
+We instead took the way of a direct correspondence of our system with the class of frames defined by Scott-Lemmon axioms as uncovered by~\cite{plotkin:stirling:86}, but as this class of logics seems to be rather well-behaved, we believe it should be possible to prove the satisfaction of Simpson's 6th requirement too.
+
+\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
+\todo{add a paragraph in conclusion: saying that it is an interesting idea to apply method to CK, but extension is tricky \cite{ADS:lmcs}} \sonia{done?}
+We have considered in this work the logic known as $\IK$ (and its extensions) with respect to the birelational semantics that is its most well-studied semantics.
+%
+As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the one called \emph{constructive modal logic} $\mathsf{CK}$ and any in between.
+%
+These can also be studied within the birelational framework with some additional conditions, and we are convinces the fully labelled framework, once extended with these conditions, will be suitable to treat constructive fragments equally.
+%
+However, treating extensions of those with axioms such as we did here for Scott-Lemmon logics is known to be complex~\cite{ADS:lmcs}.
 

### 2020-09-29 FullyLabelled/JLC/main.tex
final pass through paper for now

@@
    \lutz{Done?}
-   \sonia{Added two setences at the beginning and modified it a bit.}
+   \sonia{Added two sentences at the beginning and modified it a bit.}
    Labelled proof theory has been famously successful for modal logics by mimicking their relational semantics within deductive systems.

### 2020-09-29 FullyLabelled/JLC/review-answer.txt
letter
letter rewritten

--- 2020-09-28 FullyLabelled/JLC/review-answer.txt
@@
 
-We already said in the submitted version that in our system
-contraction is derivable from the monotonicity rules, which in turn
-are admissible. We made this even more clear in the new version in
+We mentioned in the submitted version that contraction is derivable 
+in our system from the monotonicity rules, which in turn
+are admissible. We made this clearer in the new version in
 Remark 3.4.
@@
 In fact, the contracted instances are added. In the same way as for
-other rules, occurring labels can be equal. We failed to make this
-explicit in the first submitted version and corrected that mistake in Remark 7.2.
+other rules, occurring labels can be equal and substituted as needed. 
+We failed to make this explicit in the first submitted version and 
+corrected that mistake in Remark 7.2.
 
@@
 
-If something works best for A, it does not mean that it won't work for B. 
-All we tried to say was that for logics with the standard Kripke semantics 
+We meant to say that for logics with standard Kripke semantics 
 there is this close relationship between the semantics and the labels in 
-the proof system.
+the proof system which makes this method both efficient and elegant.
 
@@
 
-We never claim the birelational semantics to be a novelty (it goes
-back to the 1980s). Our paper is not about semantics but about
-proof systems. And our system allows for extenstions that could not be 
-studied before. We made this more clear in the new version (see
-Section 7).
+We do not claim the birelational semantics to be a novelty of this work
+(We acknowledge that it dates back to the 1980s). Our paper is using the 
+semantical results of Plotkin and Sterling and others to design proof 
+systems for extensions of intuitionistic modal logic that had not been 
+studied before. We try to make this clearer in the new version (see Section 7).
 
@@
 
-We are puzzled by this comment, as we just picked the standard
-semantics for intuitionistic modal logic, and semantics is not a
-concern of our paper. However, we added in the conclusion some
-comments on constructive modal logics, which are another variant of
-adding BOX and DIAMOND to intuitionistic propositional logic.
+We chose to work the standard birelational semantics for intuitionistic modal 
+logic IK. There are indeed other possible semantics that have been studied 
+for other constructive interpretations of modal logics such as birelational 
+semantics with impossible words or neighbourhood semantics. These could 
+potentially be studied in a similar framework to ours and we commented on 
+this topic in the conclusion.
 
@@
 
-We put more emphasis on the section 7 in order to make clearer how to generate "stronger
-logics" adding new axioms to our system. We extended this section with more explanation and 
-we also added a few more comments and remarks. For example, as a better way to understand the extensions, 
-we also illustrated the specific case of adding to IK the 4-axiom.
+We put more emphasis on Section 7 in this new version. We hope we made 
+it clearer how to generate "stronger logics" adding new axioms to our system. 
+We extended this section with more explanation and also added a few comments 
+and remarks. For example, as a better way to understand the rules and the 
+completeness proof, we present the specific case of the 4-axiom.
 
@@
 
-\marianela{not sure what to put here} We added Remark 7.5 to discuss this. 
-Our rules are in fact in the style of Simpson, but we added a comparison to Vigano's method.
+We hope the additional Remark 7.4 answers these concerns. 
+We are indeed using the same method that Simpson (or Negri) applied to 
+geometric formulas, but in our case also allowing the preorder atoms to occur. 
+This method enforces that both relational and preorder atoms only appear on 
+the left-hand-side of a sequent, never on the right-hand-side. 
+As suggested, it should also be possible to treat the Scott-Lemmon axioms in 
+the style of Viganò and atoms would then appear on the right of sequents 
+only and indeed Skolemisation of some of the quantifiers would be required.
 
@@
 
-Following this comment, we fixed the derivation on the paper in order to 
-show better the use of the rule g1111.
+Following this comment, we fixed the derivation which should now 
+show better the use of rule g1111.
 
@@
 
-In this case, we chose to change the word "need" with the word "use".
-Our intention on this, was to try to show how to apply those rules and how useful there are
-in our proofs.
+In this case, our intention was indeed to only show how to use those rules and how 
+critical there are in these specific cases.
+
+>Reconsider the abstract. It reads very operational and does not clearly state the
+>contributions of the paper.
+
+We rewrote the abstract added some more context and with the aim of better reflecting 
+our contribution in the paper.
+
+We want to thank the reviewers again for their time and for helping us improve our paper. 
+We hope to have addressed all their insightful comments both in this letter and in the new version of this paper.
+
+Best regards,
+Sonia Marin, Marianela Morales and Lutz Strassburger

### 2020-09-29 FullyLabelled/JLC/review-answer.txt
minor change remark 7.2

@@
 >  case, but unless you prove it formally, it is not fully correct to
->  claim that the “need” is shown. This is pedantic, I know.
+>  claim that the “need” is shown.
 
@@
 
->Reconsider the abstract. It reads very operational and does not clearly state the
->contributions of the paper.
+> Finally, I suggest that the authors reconsider the abstract, which, 
+> in my opinion, does not do their paper justice. It reads very “operational” 
+> and does not clearly state the contributions of the paper.
 
-We rewrote the abstract added some more context and with the aim of better reflecting 
-our contribution in the paper.
+We rewrote the abstract adding some more context and with the aim of better reflecting 
+our contributions
 

### 2020-09-29 FullyLabelled/JLC/conclusion.tex
concl

@@
 %
-As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the one called \emph{constructive modal logic} $\mathsf{CK}$ and any in between.
+As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the one called \emph{constructive modal logic} $\mathsf{CK}$~\cite{xxx} and any in between.
 %
-These can also be studied within the birelational framework with some additional conditions, and we are convinces the fully labelled framework, once extended with these conditions, will be suitable to treat constructive fragments equally.
+These can also be studied within the birelational framework with some additional conditions, and we are convinced that the fully labelled framework, once extended with these conditions, will be suitable to treat constructive fragments equally.
 %
-However, treating extensions of those with axioms such as we did here for Scott-Lemmon logics is known to be complex~\cite{ADS:lmcs}.
+However, treating extensions of $\mathsf{CK}$ with axioms such as we did here for Scott-Lemmon logics is known to be complex~\cite{arisaka:etal:lmcs15}.
 

### 2020-09-29 FullyLabelled/JLC/main.tex
abstract

--- 2020-09-29 FullyLabelled/JLC/main.tex
@@
  \begin{abstract}
-   \review{Reconsider abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
-   \lutz{Done?}
-   \sonia{Added two setences at the beginning and modified it a bit.}
+   %% \review{Reconsider abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
+   %% \lutz{Done?}
+   %% \sonia{Added two sentences at the beginning and modified it a bit.}
    Labelled proof theory has been famously successful for modal logics by mimicking their relational semantics within deductive systems.

### 2020-09-29 FullyLabelled/JLC/conclusion.tex
remove comments

@@
 
-\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
-\todo{add a paragraph in conclusion: saying that it is an interesting idea to apply method to CK, but extension is tricky \cite{ADS:lmcs}} \sonia{done?}
+%% \review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
+%% \todo{add a paragraph in conclusion: saying that it is an interesting idea to apply method to CK, but extension is tricky \cite{ADS:lmcs}} \sonia{done?}
 We have considered in this work the logic known as $\IK$ (and its extensions) with respect to the birelational semantics that is its most well-studied semantics.
 %
-As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the one called \emph{constructive modal logic} $\mathsf{CK}$~\cite{xxx} and any in between.
+As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the one called \emph{constructive modal logic} $\mathsf{CK}$~\cite{bierman:depaiva:sl00,mendler:scheele:ic11} and any in between.
 %

### 2020-09-29 FullyLabelled/JLC/preliminaries.tex
footnote
draft of response
remove comments

@@
 \section{Intuitionistic modal logics}\label{sec:intmod}
-
-\review{Also the reason for preferring one semantics for intuitionistic modal logic over another should be discussed in detail, as otherwise the authors’ work would rather look a routine exercise.}
-\todo{add a paragraph about constructive modal logics.}
 
@@
 However this would give strictly no information on the behaviour of the $\DIA$ modality.
-It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}.
+It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}~\cite{bierman:depaiva:sl00,mendler:scheele:ic11}.
 Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.

### 2020-09-29 FullyLabelled/JLC/system.tex
remove comments

@@
 
-\review{the authors of the paper under review neglect an important caveat in the design of rules of contraction-free labelled sequent calculi: to guarantee that contraction be admissible one needs to ensure that a certain closure condition be satisfied, see:
+%% \review{the authors of the paper under review neglect an important caveat in the design of rules of contraction-free labelled sequent calculi: to guarantee that contraction be admissible one needs to ensure that a certain closure condition be satisfied, see:
 
-\emph{• Negri, S. Proof analysis in modal logic. Journal of Philosophical Logic, 34, 507–544, 2005.}}\lutz{I think the remark above takes care of that.}
+%% \emph{• Negri, S. Proof analysis in modal logic. Journal of Philosophical Logic, 34, 507–544, 2005.}}\lutz{I think the remark above takes care of that.}
 
-%\marianela{Should we mention Negri's paper here? }
+%% %\marianela{Should we mention Negri's paper here? }
 
-%\marianela{In the same way as we did with monotonicity, trying to avoid the problems that contraction has in a cut elimination proof, it is preferable to have a system in which this rule is admissible.
-%	}
+%% %\marianela{In the same way as we did with monotonicity, trying to avoid the problems that contraction has in a cut elimination proof, it is preferable to have a system in which this rule is admissible.
+%% %	}
 
-\review{Also the proofs of the structural properties closely follow the methodology of the paper by Maffezioli, Naibo \& Negri.
+%% \review{Also the proofs of the structural properties closely follow the methodology of the paper by Maffezioli, Naibo \& Negri.
 All this has to be said expressis verbis, and appropriate citations have to be added.}
-%\marianela{we are not saying that in the next paragraph?}
-\lutz{I just checkt again, and I refuse to do that.
+%% %\marianela{we are not saying that in the next paragraph?}
+%% \lutz{I just checkt again, and I refuse to do that.
 I see two ways to proceed: Either we just ignore the comment, or we write in the answer to the reviewer that the whole procedure is standard (and we can even cite in the paper the Troelstra-Schwichtenberg Textbook).

### 2020-09-29 FullyLabelled/JLC/introduction.tex
remove comments

@@
 
-\review{The rules of their calculus are identical (except for the ones that relate the two accessibility relations) to the rules for the intuitionistic-alethic fragment	of the calculus for intuitionistic bimodal logic in this publication:
-  • Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
-\lutz{done in previous paragraph?}
+%% \review{The rules of their calculus are identical (except for the ones that relate the two accessibility relations) to the rules for the intuitionistic-alethic fragment	of the calculus for intuitionistic bimodal logic in this publication:
+%%   • Maffezioli, P., Naibo, A. \& Negri, S., The Church-Fitch knowability paradox in the light of structural proof theory. Synthese, vol. 190, 2677–2716, 2013.}
+%% \lutz{done in previous paragraph?}
 %\old{
@@
 
-\todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
-\lutz{I've added a refence to \cite{bovzic1984models} in sec.2, and \cite{maffezioli2014} in a footnote in sec.3}
+%% \todo{Add Bozin and Dozen reference: \cite{bovzic1984models} and Maffezioli and Naibo \cite{maffezioli2014}}
+%% \lutz{I've added a refence to \cite{bovzic1984models} in sec.2, and \cite{maffezioli2014} in a footnote in sec.3}
 %\todo{maybe paragraph on related work?}

### 2020-09-30 FullyLabelled/JLC/introduction.tex
bugfixes in 1 and 2

@@
 where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas~\cite{negri:vonplato:01}.
+$\Delta$ for multi-sets of labelled formulas~\cite{negri:vonplato:01}.\lutz{right ref?}
 
@@
 	}
-	\qquad\qquad
+	\hskip10em
 	\xymatrix{
@@
 	$\le$-relation) is visible in an ordinary labelled
-	sequent, we only have that a formula is provable in an extension of $\IK$ beyond paths axioms 
+	sequent, we only have the result that a formula is provable in an extension of $\IK$ beyond paths axioms 
 	if and only if is satisfied in all \emph{graph-consistent}\footnote{This
@@
 In order to address these two concerns we propose here to enrich usual 
-labelled sequent by allowing both, relational atoms of the
+labelled sequents by allowing both, relational atoms of the
 form $\futs xy$ and of the form $\accs xy$. 
@@
 This allows us to define cut-free deductive systems for a wide range
-of logics that had been treated proof-theoretically before.  
+of logics that had not been treated proof-theoretically before.  
 %%
@@
 Besides that, there is another pleasant observation to make about our
-system. Ordinary labelled sequent systems for intuitionistic modal
+system. It is naturally a multi-conclusion system. Ordinary labelled sequent systems for intuitionistic modal
 logic are single-conclusion~\cite{simpson:phd}. 
@@
 systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
-Maehara style multiple-conclusion systems in nested
+Maehara style multi-conclusion systems in nested
 sequents~\cite{str:2017maehara}, and therefore also in ordinary
@@
 premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83} for
+systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83}\lutz{wrong ref} for
 intuitionistic logic.

### 2020-09-30 FullyLabelled/JLC/main.tex
bugfixes in 1 and 2

@@
    %%
-   We show soundness and completeness, together with an internal cut elimination proof, encompassing a wider array of intuitionistic modal logics than any existing labelled systems.
+   We show soundness and completeness, together with an internal cut elimination proof, encompassing a wider array of intuitionistic modal logics than any existing labelled system.
  \end{abstract}

### 2020-09-30 FullyLabelled/JLC/preliminaries.tex
bugfixes in 1 and 2

@@
 %
-Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$,\ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
+Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$, \ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
 %
@@
 
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
+		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs u{u'}$ and $\accs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
 
@@
 	\label{model}
-	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms true at $\lb w$, additionally subject to:
+	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms that are true at $\lb w$, additionally subject to:
 	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
@@
 
-		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u, \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
+		\M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u \mbox{, we have } \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$
 
@@
 
-From the monotonicity of the valuation function $V$, we get a monotonicity property for the relation:
+From the monotonicity of the valuation function $V$, we get a monotonicity property for the $\Vdash$ relation:
 \begin{proposition}(Monotonicity) 
-	For any formula $\fm A$ and for $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
+	For any formula $\fm A$ and for any $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
 \end{proposition}

### 2020-09-30 FullyLabelled/JLC/soundness.tex
not much in 3-5

@@
 
-We are now ready to state the main theorem of this section, of which
+We are now ready to state and prove the main theorem of this section, of which
 the implication \ref{iii}$\implies$\ref{iv} in

### 2020-09-30 FullyLabelled/JLC/introduction.tex

@@
 premise, even though this is not the case in labelled
-systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:83}\lutz{wrong ref} for
+systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:2014} for
 intuitionistic logic.

### 2020-09-30 FullyLabelled/JLC/introduction.tex
fixed reference

@@
 where $\B$ stands for a set of relational atoms, and $\Gamma$ and
-$\Delta$ for multi-sets of labelled formulas~\cite{negri:vonplato:01}.\lutz{right ref?}
+$\Delta$ for multi-sets of labelled formulas~\cite{negri:jpl2005}.
 

### 2020-09-30 FullyLabelled/JLC/conclusion.tex
done 6 and 7

@@
 
-For a restricted class of these logics defined by so-called \emph{path axioms}: $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
+For a restricted class of these logics defined by so-called \emph{path axioms} $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
 %
@@
 
-However, we have not showed that our system satisfies Simpson's 6th requirement, that is, ``there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [the system] is sound and complete".
+However, we have not shown that our system satisfies Simpson's 6th requirement, that is, ``there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [the system] is sound and complete".
 %
@@
 %
-As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the one called \emph{constructive modal logic} $\mathsf{CK}$~\cite{bierman:depaiva:sl00,mendler:scheele:ic11} and any in between.
+As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the \emph{constructive modal logic} $\mathsf{CK}$~\cite{bierman:depaiva:sl00,mendler:scheele:ic11} and any in between.
 %

### 2020-10-01 FullyLabelled/JLC/introduction.tex
up to section 6

@@
 Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
-\emph{labelled proof calculi} have been widely used by proof theorist
-to give sound, complete and cut-free deductive systems to a broad range
+\emph{labelled proof calculi} have been widely used by proof theorists
+to give sound, complete, and cut-free deductive systems to a broad range
 of logics. Unlike so-called \emph{internal calculi}, like
 hypersequents~\cite{avron:elc96}, nested
-sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann:tableaux15},
+sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 
+2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann:tableaux15},
 labelled calculi have the advantage of being more uniform and being able to 
@@
 
-Standard labelled sequent calculi for logics with
+Labelled sequent calculi for logics with
 standard Kripke semantics attach to every formla $\fm A$ a label
@@
 	as observed by Simpson
-	and considered as an inelegant solution~\cite{simpson:phd}. % (see also \cite{mar:str:tableaux17}).
+	and considered an inelegant solution~\cite{simpson:phd}. % (see also \cite{mar:str:tableaux17}).
 \end{enumerate}
@@
 sequents~\cite{str:2017maehara}, and therefore also in ordinary
-labelled sequents. However, also in these systems there are rules
+labelled sequents. However, even in these systems there are rules
 ($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
@@
 more than one relation. In fact, the logical rules are essentially the
-same as ours. But we use a more general setting and provide deductive proof
+same as ours, but we use a more general setting and provide deductive proof
 systems for a larger class of intuitionistic modal logics, together

### 2020-10-01 FullyLabelled/JLC/preliminaries.tex
up to section 6

@@
 Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$.
-In these systems, however, the addition of the \emph{Excluded Middle} principle to it does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
+In these systems, however, the addition of the \emph{Excluded Middle} does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.
 
@@
 %
-It combines the Kripke semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.\footnote{This semantics and some variants have also been studied in~\cite{bovzic1984models}.
+It combines the semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.\footnote{This semantics and some variants have also been studied in~\cite{bovzic1984models}.
 For an excellent survey on possible variants see~\cite{simpson:phd}.}
@@
 	\begin{enumerate}
-		\item[($\rn{F_1}$)] For all $\lb u, \lb v, \lb{v'} \in W$, if $\accs uv$ and $\futs v{v'}$, there exists $\lb{u'}$ s.t.~$\futs u{u'}$ and $\accs{u'}{v'}$.
+		\item[($\rn{F_1}$)] For all $\lb x, \lb y, \lb z \in W$, if $\accs xy$ and $\futs yz$, there exists $\lb u$ s.t.~$\futs xu$ and $\accs uz$.
 
@@
 		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R  & \lb{v'} \\
-			\lb u \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb v \ar@{->}[u]_{\le}
+			\lb u \ar@{.>}[r]^R  & \lb z \\
+			\lb x \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb y \ar@{->}[u]_{\le}
 		}
@@
 
-		\item[($\rn{F_2}$)] For all $\lb {u'}, \lb u, \lb v \in W$, if $\futs u{u'}$ and $\accs uv$, there exists $\lb {v'}$ s.t.~$\accs{u'}{v'}$ and $\futs v{v'}$.
+		\item[($\rn{F_2}$)] For all $\lb x, \lb y, \lb z \in W$, if $\futs xz$ and $\accs xy$, there exists $\lb u$ s.t.~$\accs zu$ and $\futs yu$.
 
@@
 		\xymatrix{
-			\lb{u'} \ar@{.>}[r]^R & \lb{v'} \\
-			\lb u \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb v \ar@{.>}[u]_{\le}
+			\lb z\ar@{.>}[r]^R & \lb u \\
+			\lb x \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb y \ar@{.>}[u]_{\le}
 		}

### 2020-10-01 FullyLabelled/JLC/soundness.tex
up to section 6

@@
 	$$ for $n\in\{0,1,2\}$, that whenever $\SGi1,\ldots,\SGi n$ are
-	valid in all birelational frame, then so is $\SG$. It follows a case analysis on $\rn r$:
+	valid in all birelational frame, then so is $\SG$. It follows from a case analysis on $\rn r$:
 	\begin{itemize}
@@
 		that $\M,\inter\cdot\not\Vdash\B, \futs xy, \accs yz, \Left,	\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
-		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ and
+		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ but
 		$\cnforce \M wB$ for all $\labels wB\in\Right$. However, by the

### 2020-10-01 FullyLabelled/JLC/conclusion.tex
finished reading

@@
 %
-We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut-elimination argument.
+We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut elimination argument.
 
@@
 %
-To make sure that his system satisfies this requirement, Simpson chose to depart from the direct correspondence with modal axioms and their corresponding class of Kripke frames, and to study intuitionistic purely as a fragment of intuitionistic first-order logic.
+To make sure that his system satisfies this requirement, Simpson chose to depart from the direct correspondence with modal axioms and their corresponding class of Kripke frames, and to study intuitionistic modal logics purely as a fragment of intuitionistic first-order logic.
 %
-We instead took the way of a direct correspondence of our system with the class of frames defined by Scott-Lemmon axioms as uncovered by~\cite{plotkin:stirling:86}, but as this class of logics seems to be rather well-behaved, we believe it should be possible to prove the satisfaction of Simpson's 6th requirement too.
+We instead took the way of a direct correspondence of our system with the class of frames defined by one-sided Scott-Lemmon axioms as uncovered by~\cite{plotkin:stirling:86}, but as this class of logics seems to be rather well-behaved, we believe it should be possible to prove the satisfaction of Simpson's 6th requirement too.
 

### 2020-10-01 FullyLabelled/JLC/letter.tex
final version and latex letter

%\documentclass[preprint,authoryear,times,10pt]{elsart}  
\documentclass[10pt]{article}

\input{new-macros}

%\textbf{Comment:}\\ #1\\}
\newcommand{\R}[1]{\textbf{R#1}:\,}
\newcommand{\reponse}[1]{\textbf{#1}}

\begin{document}

\hfill \today
\bigskip

\noindent\textbf{Letter to the editors of the EICNCL Special Issue of JLC.}
\bigskip

\noindent{Dear Agata, Didier, Nicola, and Revantha,}
\medskip

Please find enclosed the revision of our paper entitled {\it A fully labelled 
proof system for intuitionistic modal logics}, taking into accounts the reviews
that we received concerning our first submission.
%
We detail below the main changes compared to the previous version that we operated 
on the paper in order to address remarks and questions by the reviewers.
\smallskip

One of the main concerns of Reviewer 1 is that we had not cited all
the relevant literature. We thank the reviewer for pointing out the
missing references and we added them accordingly.

We now address their other comments.

\begin{quote}\it
	Perhaps even more importantly, the authors of the paper under 
	review neglect an important caveat in the design of rules of 
	contraction-free labelled sequent calculi: to guarantee that 
	contraction be admissible one needs to ensure that a certain 
	closure condition be satisfied
\end{quote}

We mentioned in the submitted version that contraction is derivable 
in our system from the monotonicity rules, which in turn
are admissible. We made this clearer in the new version in
Remark 3.4.

\begin{quote}\it
	In Section 7, if the rules $\gklmn$ are added without their 
	contracted instances, the calculus will not be complete. For 
	example, in the classical case, Euclidean transitivity $\forall a, b, 
	c(aRb \AND aRc \IMP bRc)$ has the contracted instance $?a, b(aRb \IMP bRb)$ that 
	allows for the derivation of $\BOX(\BOX A \IMP A)$. This, however, can 
	hardly be derived without the rule?s contracted instance.
\end{quote}

In fact, the contracted instances are added. In the same way as for
other rules, occurring labels can be equal and substituted as needed. 
We failed to make this explicit in the first submitted version and 
corrected that mistake in Remark 7.2.

\begin{quote}\it
	On top of this, the authors' claim that labelled calculi ``work best 
	for logics with standard Kripke semantic'' is utterly wrong: 
	labelled calculi have been developed for several variants of Kripke 
	semantics, such as Lewis's semantics for counterfactuals, 
	neighbourhood semantics, Kripke semantics of impossible worlds, and 
	so on.
\end{quote}

We meant to say that for logics with standard Kripke semantics 
there is this close relationship between the semantics and the labels in 
the proof system which makes this method both efficient and elegant.

\begin{quote}\it
In conclusion, the paper does not look highly original. The 
birelational semantics is not a novelty, nor a calculus 
internalising that semantics appears an original idea.
\end{quote}

We do not claim the birelational semantics to be a novelty of this work.
(We acknowledge that it dates back to the 1980s.) Our paper is using the 
semantical results of Plotkin and Sterling, and others, to design proof 
systems for extensions of intuitionistic modal logic that had not been 
studied proof-theoretically before. We try to make this clearer in the new 
version (see Section 7).

\begin{quote}\it
Also the reason for preferring one semantics for intuitionistic 
modal logic over another should be discussed in detail, as 
otherwise the authors? work would rather look a routine exercise
\end{quote}

We chose to work the standard birelational semantics for intuitionistic modal 
logic IK. There are indeed other possible semantics that have been studied 
for other constructive interpretations of modal logics such as birelational 
semantics with impossible words or neighbourhood semantics. These could 
potentially be studied in a similar framework to ours and we commented on 
this topic in the conclusion.

\medskip
Reviewer 2 finds this paper well written, but has some 
technical concerns. We address them below.

\begin{quote}\it
The main issue is indeed with the ``wide range of logics''. While the
base logic is discussed in detail, the range of logics is treated
in an ``Extensions'' section that I believe could actually be more
detailed.
\end{quote}

We put more emphasis on Section 7 in this new version. We hope we made 
it clearer how to generate ``stronger logics" adding new axioms to our system. 
We extended this section with more explanation and also added a few comments 
and remarks. For example, as a better way to understand the rules and the 
completeness proof, we present the specific case of the 4-axioms.

\begin{quote}\it
Most importantly, I am not convinced by the $\gklmn$ rule. The side
condition stipulates that $y?$ and $u$ are fresh, whereas the frame
property contains existential quantifications. I was thus expecting
either a Skolemization in the style of Vigan\`o in the ``Labelled
Non-Classical Logics'' book, or a geometric rule with existential
quantification in the style of Simpson [Sim94] or, perhaps even
better, a ``mixed'' rule where the labels are assumed more or less in
the style of an $\exists$ elimination to derive a labeled formula.  I
think that a thorough discussion of the alternatives, along with a
more thorough proof of the correctness of the chosen solution, is
needed.
\end{quote}

We hope the additional Remark 7.4 answers these concerns. 
We are indeed using the same method that Simpson (or Negri) applied to 
geometric formulas, but in our case also allowing the preorder atoms to occur. 
This method enforces that both relational and preorder atoms only appear on 
the left-hand-side of a sequent, never on the right-hand-side. 
As suggested by Reviewer 2, it should also be possible to treat the Scott-Lemmon axioms in 
the style of Vigan\`o where atoms would then appear on the right of sequents 
only and indeed Skolemisation of some of the quantifiers would be required.

\begin{quote}\it
By the way, it does not help at all that the applications of the
rule $\rn{g_{1111}}$ are merged with $\llabrn\BOX$ and $\rlabrn\DIA$ in the example
derivation.
\end{quote}

Following this comment, we fixed the derivation which should now 
show better the use of rule $\rn{g_{1111}}$.

\begin {quote}\it
Also Remark 4.2 could benefit from some additional explanation. You
write that the proof of Theorem 4.1 shows the ``need'' of the rules
$\rn{F_1}$, $\rn{refl}$ and $\rn{trans}$. However, strictly speaking, the proof only
shows how the rules are used and that they are helpful to prove the
axioms. To show the ``need'' you would likely have to show that no
other proofs of the axioms are possible. That is of course the
case, but unless you prove it formally, it is not fully correct to
claim that the ``need'' is shown. 
\end{quote}

In this case, our intention was indeed only to show how to use those rules and how 
they play an interesting role in these specific cases.

\begin{quote}\it
Finally, I suggest that the authors reconsider the abstract, which, 
in my opinion, does not do their paper justice. It reads very ?operational? 
and does not clearly state the contributions of the paper.
\end{quote}

We rewrote the abstract adding some more context and with the aim of better reflecting 
our contributions
\medskip

We finally want to thank the reviewers for their time and for helping us improve our paper. 
We hope to have addressed all their insightful comments both in this letter and in the new version of this paper. 
\bigskip

Kind regards,
\medskip

Sonia Marin, Marianela Morales and Lutz Stra\ss burger

\end{document}

### 2021-01-02 FullyLabelled/JLC/introduction.tex
working on review

@@
 form $\futs xy$ and of the form $\accs xy$.
+
+\marianela{The reviewer suggested to change the above sentence for the next one:
+	\emph{"As done earlier in the literature  on intuitionistic modal logic (cf....) we consider here
+	to enrich"} since Maffezioli, Naibo and Negri have already done this before and the next one:
+
+	D. Garg, V. Genovese, and S. Negri, Countermodels from sequent calculi in multi-modal	logics. LICS 2012, IEEE Computer Society, pp. 315–324, 2012. (ALREADY ADDED. SHOULD I REMOVE IT?)
+	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times.
+	}
+
 %%

### 2021-01-02 FullyLabelled/JLC/introduction.tex
adding references

@@
 
-	D. Garg, V. Genovese, and S. Negri, Countermodels from sequent calculi in multi-modal	logics. LICS 2012, IEEE Computer Society, pp. 315–324, 2012. (ALREADY ADDED. SHOULD I REMOVE IT?)
-	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times.
+	D.
+Garg, V.
+Genovese, and S.
+Negri, Countermodels from sequent calculi in multi-modal	logics.
+LICS 2012, IEEE Computer Society, pp.
+315–324, 2012.
+(ALREADY ADDED ON REFERENCES FILE TO USE IT IF WE CHANGE THE SENTENCE: \cite{garg2012})
+	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times...
 	}
@@
 
+\review{More specifically, it is not clear what the authors mean by  "internal cut elimination procedure" on the next paragraph.
+	At the beginning of the paper "internal calculi" are identified as those calculi, such as hypersequent
+	or nested calculi, that do not have explicit accessibility relations. But then in which sense it the
+	cut elimination "internal"? Is it because there are no cuts on relational atoms? This is the case
+	also for the mentioned MNN paper.  Please clarify.}
 A system similar to ours is presented
@@
 same as ours, but we use a more general setting and provide deductive proof
-systems for a larger class of intuitionistic modal logics, together
-with an internal cut elimination procedure.
+systems for a larger class of intuitionistic modal logics, \marianela{together
+with a syntactic cut elimination procedure.}
 

### 2021-01-02 FullyLabelled/JLC/conclusion.tex
working on review

@@
 
-In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and generalise it to the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
+\review{One of the main contributions of the mentioned paper by Maffezioli, Naibo and Negri seems to be
+	the proof-theoretical analysis for an extension with a frame property that does not fall under the
+	class of geometric implications and that requires an extension of the usual methodology. In fact,
+	their paper presents the first example of the method of "system of rules", later systematized in :
+
+	S. Negri. Proof analysis beyond geometric theories: from rule systems to systems of rules. Journal of Logic and Computation,
+	vol. 27, pp. 513-537, 2016.
+
+	The frame properties and rules considered in the paper under review are all of the geometric form,
+	so it would be more correct to say that it is an in-depth study of intuitionistic modal logic for a larger
+	class of geometric frame properties rather than a generalization of the results in the paper by
+	Maffezioli,  Naibo and Negri .}
+
+In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and \marianela{we investigate it inside the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.}
 %
@@
 It would be interesting to know how and where the class of logics we considered can be included in their framework.
+
+\review{In references, book and theses titles should be capitalized (this is not done consistently).} \marianela{book title or the chapter as well?}

### 2021-01-02 FullyLabelled/JLC/system.tex
up to section 6
working on review

@@
   \quad
-  \vlinf{\llabrn\BOX}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
+  \vlinf{\llabrn\BOX'}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
 \end{equation}
@@
 
+\review{Theorem 3.3 refers to formulas but a sequent calculus derives, in fact, sequents. In a Gentzen
+	sequent calculus a sequent can be translated into a formula, and conversely, but this is no
+	longer the case in a labelled calculus because of the labelling and the relational atoms.
+	1,4 and 2,3 refer, respectively, to formulas and to labelled formulas, so they cannot be equivalent.
+	Observe also that the paper by  Maffezioli, Naibo and Negri prove completeness wrt sequents,
+	not just wrt formulas, so it presents a more general approach.}
+
+\todo{footnote: completeness can be proved by proof search??}
+
 \begin{theorem}\label{thm:cutfree-compl}

### 2021-01-13 FullyLabelled/JLC/conclusion.tex
adding comments
finished all the todos

--- 2020-10-01 FullyLabelled/JLC/conclusion.tex
@@
 
-In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and generalise it to the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
+In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and we study it in-depth for the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
+\todo{The frame properties and rules considered in the paper under review are all of the geometric form,
+	so it would be more correct to say that it is an in-depth study of intuitionistic modal logic for a larger
+	class of geometric frame properties rather than a generalization of the results in the paper by
+	Maffezioli,  Naibo and Negri .}\sonia{OK}
 %
@@
 %
-The work of~\cite{dalmonte:grellois:olivetti:arxiv19} is a great first step in understanding them in the context of non-normal modalities and neighbourhood semantics.
+The work of~\cite{dalmonte:grellois:olivetti:JPL2020} is a great first step in understanding them in the context of non-normal modalities and neighbourhood semantics.
 %
 It would be interesting to know how and where the class of logics we considered can be included in their framework.
+
+\todo{In references, book and theses titles should be capitalized (this is not done consistently).} \marianela{book title or the chapter as well?} \sonia{OK}
+
+\todo{DG019 change to published reference}\sonia{OK}

### 2021-01-13 FullyLabelled/JLC/introduction.tex
adding comments
finished all the todos

--- 2020-10-01 FullyLabelled/JLC/introduction.tex
@@
 \end{enumerate}
-In order to address these two concerns we propose here to enrich usual 
-labelled sequents by allowing both, relational atoms of the
-form $\futs xy$ and of the form $\accs xy$. 
+In order to address these two concerns we follow here the approach~\cite{garg2012,maffezioli:etal:synthese13} that enriches usual  labelled sequents by allowing both, relational atoms of the form $\futs xy$ and of the form $\accs xy$ and develop it into a uniform general framework.
+%\marianela{The reviewer suggested to change the above sentence for the next one:
+%	\emph{"As done earlier in the literature  on intuitionistic modal logic (cf....) we consider here
+%	to enrich"} since Maffezioli, Naibo and Negri have already done this before and the next one:
+%
+%	D.
+Garg, V.
+Genovese, and S.
+Negri, Countermodels from sequent calculi in multi-modal	logics.
+LICS 2012, IEEE Computer Society, pp.
+315–324, 2012.
+(ALREADY ADDED ON REFERENCES FILE TO USE IT IF WE CHANGE THE SENTENCE: \cite{garg2012})
+%	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times...
+%	}
+\todo{add footnote}\sonia{added the reference in the text directly}
 %%
@@
 systems for a larger class of intuitionistic modal logics, together
-with an internal cut elimination procedure.
+with a syntactic cut elimination procedure.
+%\review{More specifically, it is not clear what the authors mean by  "internal cut elimination procedure" on the next paragraph.
+%	At the beginning of the paper "internal calculi" are identified as those calculi, such as hypersequent
+%	or nested calculi, that do not have explicit accessibility relations. But then in which sense it the
+%	cut elimination "internal"? Is it because there are no cuts on relational atoms? This is the case
+%	also for the mentioned MNN paper.  Please clarify.}
+\sonia{OK}
 

### 2021-01-13 FullyLabelled/JLC/system.tex
more comments
adding comments
finished all the todos

--- 2020-09-29 FullyLabelled/JLC/system.tex
@@
 
-In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination. The cut rule has the following shape:
+In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination.
+%
+The cut rule has the following shape:
 \begin{equation}
@@
 \end{equation}
-Then we can summarize soundness, completeness, and cut
-admissibility of $\labIKp$ in the following Theorem:
+
+We say that a formula is \emph{provable} in $\labIKp$ (or $\labIKp+\labrn{cut}$, resp.) if for any label $\lb x$, the sequent $\SEQ \labels{x}{A}$ is derivable from only axioms using the rules in Figure~\ref{fig:labIKp} (with possible instances of $\labrn{cut}$, resp.).
+%
+We can summarize soundness, completeness, and cut
+admissibility of $\labIKp$ in the following result.
+
+%\review{Theorem 3.3 refers to formulas but a sequent calculus derives, in fact, sequents. In a Gentzen
+%	sequent calculus a sequent can be translated into a formula, and conversely, but this is no
+%	longer the case in a labelled calculus because of the labelling and the relational atoms.
+%	1,4 and 2,3 refer, respectively, to formulas and to labelled formulas, so they cannot be equivalent.
+%	Observe also that the paper by  Maffezioli, Naibo and Negri prove completeness wrt sequents,
+%	not just wrt formulas, so it presents a more general approach.}
+
+\todo{footnote: completeness can be proved by proof search?}\sonia{moved to end of section~\ref{sec:completeness}}
+
+\todo{define what provable means?}\sonia{OK}
 

### 2021-01-14 FullyLabelled/JLC/conclusion.tex
margins fixed

@@
 In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and we study it in-depth for the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
-\todo{The frame properties and rules considered in the paper under review are all of the geometric form,
-	so it would be more correct to say that it is an in-depth study of intuitionistic modal logic for a larger
-	class of geometric frame properties rather than a generalization of the results in the paper by
-	Maffezioli,  Naibo and Negri .}\sonia{OK}
 %
@@
 It would be interesting to know how and where the class of logics we considered can be included in their framework.
-
-\todo{In references, book and theses titles should be capitalized (this is not done consistently).} \marianela{book title or the chapter as well?} \sonia{OK}
-
-\todo{DG019 change to published reference}\sonia{OK}

### 2021-01-14 FullyLabelled/JLC/introduction.tex
margins fixed
typo

@@
 standard Kripke semantics attach to every formla $\fm A$ a label
-$\lb x$, witten as $\labels xA$, and additionally use
+$\lb x$, written as $\labels xA$, and additionally use
 \emph{relational atoms} of the form $\accs xy$ where 
@@
 In order to address these two concerns we follow here the approach~\cite{garg2012,maffezioli:etal:synthese13} that enriches usual  labelled sequents by allowing both, relational atoms of the form $\futs xy$ and of the form $\accs xy$ and develop it into a uniform general framework.
-%\marianela{The reviewer suggested to change the above sentence for the next one:
-%	\emph{"As done earlier in the literature  on intuitionistic modal logic (cf....) we consider here
-%	to enrich"} since Maffezioli, Naibo and Negri have already done this before and the next one:
-%
-%	D.
-Garg, V.
-Genovese, and S.
-Negri, Countermodels from sequent calculi in multi-modal	logics.
-LICS 2012, IEEE Computer Society, pp.
-315–324, 2012.
-(ALREADY ADDED ON REFERENCES FILE TO USE IT IF WE CHANGE THE SENTENCE: \cite{garg2012})
-%	What do you think about changing the sentence? We have already mentioned Maffezioli, Naibo and Negri's paper a few times...
-%	}
-\todo{add footnote}\sonia{added the reference in the text directly}
 %%
@@
 %	also for the mentioned MNN paper.  Please clarify.}
-\sonia{OK}
 
@@
 
-This paper is organized as follows, In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
+This paper is organized as follows.
+In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics.
 Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.

### 2021-01-14 FullyLabelled/JLC/document.tex
tex file with all the sections

\documentclass[a4paper]{article}
\usepackage{authblk}
\input{new-macros}

\title{A fully labelled proof system for intuitionistic modal logics}
\author[1]{Sonia Marin} 
\author[2,3]{Marianela Morales}
\author[3,2]{Lutz Stra{\ss}burger}
\affil[1]{University College London}
\affil[2]{Laboratoire d'Informatique de l'\'Ecole Polytechnique}
\affil[3]{Inria Saclay}

\date{}

\begin{document}

  \maketitle

 \begin{abstract}
   %% \review{Reconsider abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
   %% \lutz{Done?}
   %% \sonia{Added two sentences at the beginning and modified it a bit.}
   Labelled proof theory has been famously successful for modal logics by mimicking their relational semantics within deductive systems. Simpson in particular designed a framework to study a variety of intuitionistic modal logics integrating a binary relation symbol in the syntax.
   %%
   In this paper, we present a labelled sequent system for
   intuitionistic modal logics such that there is not only one, but
   two relation symbols appearing in sequents: one for the accessibility
   relation associated with the Kripke semantics for normal modal logics and
   one for the preorder relation associated with the Kripke semantics
   for intuitionistic logic.
   %%
   This puts our system in close correspondence with the standard
   birelational Kripke semantics for intuitionistic modal logics. 
   %%
   As a consequence it can be extended with arbitrary intuitionistic Scott-Lemmon axioms. 
   %%
   We show soundness and completeness, together with an internal cut elimination proof, encompassing a wider array of intuitionistic modal logics than any existing labelled system.
 \end{abstract}

 \section{Introduction}\label{sec:intro}

 Since their introduction in the 1980s by Gabbay~\cite{gabbay:96},
 \emph{labelled proof calculi} have been widely used by proof theorists
 to give sound, complete, and cut-free deductive systems to a broad range
 of logics. Unlike so-called \emph{internal calculi}, like
 hypersequents~\cite{avron:elc96}, nested
 sequents~\cite{kashima:sl94,brunnler:aml09,poggiolesi:tmp09}, 
 2-sequents~\cite{masini:apal92}, or linear nested sequents~\cite{lellmann:tableaux15},
 labelled calculi have the advantage of being more uniform and being able to 
 accommode a larger class of logics.

 Labelled sequent calculi for logics with
 standard Kripke semantics attach to every formla $\fm A$ a label
 $\lb x$, written as $\labels xA$, and additionally use
 \emph{relational atoms} of the form $\accs xy$ where 
 the binary relation symbol $\rel$
 %These calculi work best for logics with
 %standard Kripke semantics, as in this case the relation $\rel$ 
 is used to encode the accessibility relation in the Kripke models, such that
 frame conditions corresponding to the desired logic can be directly
 encoded as inference rules.
 %\todo{Reviewer 1 complained about the ``best''}
 Prominent examples are classical modal
 logics and intuitionistic propositional logic, e.g., the frame
 condition of transitivity ($\forall \lb {xyz}.\:\accs xy\AND \accs yz\IMP\accs xz$) can be translated into the
 inference rule
 \begin{equation}
 \label{eq:Rtrans}
 \vlinf{\rn{trans}}{}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
 	\B, \accs xy, \accs yz, \accs xz, \Left \SEQ \Right}
 \end{equation}
 where $\B$ stands for a set of relational atoms, and $\Gamma$ and
 $\Delta$ for multi-sets of labelled formulas~\cite{negri:jpl2005}.

 However,
 in this paper we are concerned with \emph{intuitionistic modal
 	logics} whose Kripke semantics is based on \emph{birelational}
 frames, i.e., they have two binary relations instead of one: one
 relation $R$ that corresponds to the accessibility relation in 
 Kripke frames for modal logics, and a relation $\le$ that
 corresponds to the preorder relation in Kripke frames for
 intuitionistic logic. Consequently, standard labelled systems for
 these logics have certain shortcomings:
 \begin{enumerate}
 	\item The transitivity rule in~\eqref{eq:Rtrans} can be axiomatised by the conjunction of the two
 	versions of the $\fourax$-axiom
 	\begin{equation}
 	\label{eq:4ax}
 	\ax{4^{\BOX}}\colon\fm{\BOX A\IMP \BOX\BOX A}
 	\qquand
 	\rn{4^{\DIA}}\colon\fm{\DIA\DIA A\IMP\DIA A}
 	%	\quadcm
 	\end{equation}
 	which are equivalent in classical
 	modal logic. However, in intuitionistic modal logic they are not
 	equivalent, and even though the logic $\IKfour$ 
 	(intuitionistic version of modal logic $\Kfour$) contains both
 	axioms, they can also be added independently to the logic $\IK$ 
 	(intuitionistic version of $\K$). The proof theory of these
 	distinct logics has not been discussed before, but their
 	corresponding frame conditions
 	\begin{equation}
 	\label{eq:4frame}
 	\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{x'}.\:\futs x{x'}\AND\accs {x'}z)
 	\quand
 	\forall\lb{xyz}.\:\accs xy\AND \accs yz\IMP(\exists\lb{z'}.\:\futs z{z'}\AND\accs {x}{z'})
 	\;
 	\end{equation}
 	%  \todo{add graphical representation of the conditions}
 	$$
 	\xymatrix{
 		x' \ar@{.>}[drr]^R \\
 		x \ar@{.>}[u]^\le \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z
 	}
 	\hskip10em
 	\xymatrix{
 		&& z''  \\
 		x  \ar@{.>}[urr]^R \ar@{->}[r]_{R} & y \ar@{->}[r]_{R} & z \ar@{.>}[u]^\le
 	}
 	$$
 	respectively, have been studied in~\cite{plotkin:stirling:86}.
 	%  \sonia{the general condition is correct but not the application to 4}
 	\item The correspondence between the syntax and the semantics is not
 	as clean as one would expect. As only the $R$-relation (and not the
 	$\le$-relation) is visible in an ordinary labelled
 	sequent, we only have the result that a formula is provable in an extension of $\IK$ beyond paths axioms 
 	if and only if is satisfied in all \emph{graph-consistent}\footnote{This
 		means that every layer in the model can be lifted to any future of
 		any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.}   
 	models satisfying the corresponding conditions, as observed by Simpson	and considered an inelegant solution~\cite{simpson:phd}.
 \end{enumerate}
 In order to address these two concerns we follow here the approach~\cite{garg2012,maffezioli:etal:synthese13} that enriches usual  labelled sequents by allowing both, relational atoms of the form $\futs xy$ and of the form $\accs xy$ and develop it into a uniform general framework. 
 %%
 Consequently, following the same ``axiom-to-rule'' method as Simpson, we can translate the frame
 conditions in~\eqref{eq:4frame} into inference rules:
 \begin{equation}
 \label{eq:4rules}
 \vlinf{\rn{4^{\BOX}}}{\proviso{$\lb{x'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
 	\B, \accs xy, \accs yz, \accs {x'}z, \futs x{x'},\Left \SEQ \Right}
 \qquand
 \vlinf{\rn{4^{\DIA}}}{\proviso{$\lb{z'}$ fresh}}{\B, \accs xy, \accs yz, \Left \SEQ \Right}{
 	\B, \accs xy, \accs yz, \accs {x}{z'}, \futs z{z'},\Left \SEQ \Right}  
 \end{equation}
 This allows us to define cut-free deductive systems for a wide range
 of logics that had not been treated proof-theoretically before.  
 %%
 Furthermore, the relation
 between syntax and semantics can be recovered as one would expect: A formula is
 provable in this system if and only if it is valid in all models satisfying the corresponding frame condition.

 Besides that, there is another pleasant observation to make about our
 system. It is naturally a multi-conclusion system. Ordinary labelled sequent systems for intuitionistic modal
 logic are single-conclusion~\cite{simpson:phd}. 
 %
 The same is true for the corresponding nested sequent
 systems~\cite{str:fossacs13,marin:str:aiml}. It is possible to express
 Maehara style multi-conclusion systems in nested
 sequents~\cite{str:2017maehara}, and therefore also in ordinary
 labelled sequents. However, even in these systems there are rules
 ($\rlabrn\IMP$ and $\rlabrn\BOX$) that force a single-conclusion
 premise, even though this is not the case in labelled
 systems~\cite{negri:jpl2005} or nested sequents~\cite{fitting:2014} for
 intuitionistic logic.

 A system similar to ours is presented
 in~\cite{maffezioli:etal:synthese13}, for intuitionistic bimodal
 epistemic logic. That system is also a multi-conclusion labelled system with
 more than one relation. In fact, the logical rules are essentially the
 same as ours, but we use a more general setting and provide deductive proof
 systems for a larger class of intuitionistic modal logics, together
 with a syntactic cut elimination procedure.

 This paper is organized as follows. In the next section (Section~\ref{sec:intmod}) we recall the standard syntax and semantics of intuitionistic modal logics. Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$. In Sections~\ref{sec:completeness} and~\ref{sec:soundness}, we show soundness and completeness of the system with cut. The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system. Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture intuitionistic Scott-Lemmon modal logics.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
 %
 \section{Intuitionistic modal logics}\label{sec:intmod}

 The language of {intuitionisitic modal logic} is the one of intuitionistic propositional logic with the modal operators $\BOX$ and $\DIA$, standing most generally for \emph{necessity} and \emph{possibility}.
 %
 Starting with a set $\mathcal{A}$ of atomic propositions, denoted by lower case letters $\fm a$, $\fm b$, $\fm c$, \ldots, modal formulas, denoted by capital letters $\fm A$, $\fm B$, $\fm C$, \ldots, are constructed from the grammar:
 %
 $$
 \fm A \coloncolonequals
 \fm a \mid \fm{A \AND A} \mid \fm{A \OR A} \mid \fm \BOT \mid \fm{A \IMP A} \mid \fm{\BOX A} \mid \fm{\DIA A}
 $$
 %

 Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
 %%
 Lacking De Morgan duality, there are many variants of the \emph{distributivity axiom} $\mathsf{k}$ that are classically but not intuitionistically equivalent. Five axioms have been considered as primitives in the literature. An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
 %

 %The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}. It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
 \begin{itemize}
 	\item the \emph{necessitation rule}: if $\fm A$ is a theorem then $\fm{\BOX A}$ is also a theorem; and
 	\item the following five variants of $\rn{k}$:
 	\begin{equation*}
 		\label{eq:ik}%\hskip-2em
 		\begin{array}[t]{r@{\;}l@{\qquad}r@{\;}l@{\qquad}r@{\;}l}
 			\kax[1]\colon&\fm{\BOX(A\IMP B)\IMP(\BOX A\IMP\BOX B)}
 			&
 			\kax[3]\colon&\fm{\DIA(A\OR B)\IMP(\DIA A\OR\DIA B)}
 			&
 			\kax[5]\colon&\fm{\DIA\BOT\IMP\BOT}
 			\\
 			\kax[2]\colon&\fm{\BOX(A\IMP B)\IMP(\DIA A\IMP\DIA B)}
 			&
 			\kax[4]\colon&\fm{(\DIA A\IMP \BOX B)\IMP\BOX(A\IMP B)}\\%x[1ex]
 		\end{array}
 	\end{equation*}
 \end{itemize}

 The idea is that intuitionistic propositional logic does not allow the principle of \emph{Excluded Middle}, so the modalities $\BOX$ and $\DIA$ are not de Morgan duals any more, but one can choose to design the axiomatisation in order to relate them in different ways. The most basic intuitionistic modal system one can think of would be to consider only the $\BOX$ modality as regulated by the $\kax$ axiom (or as called here $\kax[1]$), which gives the system \hbox{$\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$}. However this would give strictly no information on the behaviour of the $\DIA$ modality.
 It seems that Fitch \cite{fitch:pm48} was the first one to propose a way to treat $\DIA$ in an intuitionistic system by considering the system  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$, which is now sometimes called $\rn{CK}$ for \emph{constructive modal logic}~\cite{bierman:depaiva:sl00,mendler:scheele:ic11}. Wijekesera \cite{wijesekera:apal90} also considered the axiom $\kax[5]$, which states that $\DIA$ distributes over 0-ary disjunctions, but did not assume that it would always distribute over binary disjunctions; the system he proposed was therefore  $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$  $\rn{+}$ $\kax[5]$. In these systems, however, the addition of the \emph{Excluded Middle} does not yield classical modal logic $\K$, that is, it is not possible to retrieve the De Morgan duality of $\BOX$ and $\DIA$ in this case.

 The axiomatisation that is now generally accepted as \emph{intuitionistic modal logic} denoted by $\IK$ was given by Plotkin and Stirling \cite{plotkin:stirling:86} and is equivalent to the one proposed by Fischer-Servi \cite{fischer-servi:84} and by Ewald \cite{ewald:jsl86} in the case of intuitionistic tense logic. It is taken to be    $\rn{IPL}$ $\rn{+}$ $\rn{nec}$ $\rn{+}$ $\kax[1]$ $\rn{+}$ $\kax[2]$ $\rn{+}$ $\kax[3]$ $\rn{+}$ $\kax[4]$  $\rn{+}$ $\kax[5]$.

 The Kripke semantics for $\IK$ was first defined by Fischer-Servi~\cite{fischer-servi:84}.
 %
 It combines the semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.\footnote{This semantics and some variants have also been studied in~\cite{bovzic1984models}. For an excellent survey on possible variants see~\cite{simpson:phd}.}

 \begin{definition}
 	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
 	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
 	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
 	\begin{enumerate}
 		\item[($\rn{F_1}$)] For all $\lb x, \lb y, \lb z \in W$, if $\accs xy$ and $\futs yz$, there exists $\lb u$ s.t.~$\futs xu$ and $\accs uz$.

 		\begin{equation*}
 			\xymatrix{
 				\lb u \ar@{.>}[r]^R  & \lb z \\
 				\lb x \ar@{.>}[u]^{\le} \ar@{->}[r]^R  & \lb y \ar@{->}[u]_{\le}
 			}
 		\end{equation*}

 		\item[($\rn{F_2}$)] For all $\lb x, \lb y, \lb z \in W$, if $\futs xz$ and $\accs xy$, there exists $\lb u$ s.t.~$\accs zu$ and $\futs yu$.

 		\begin{equation*}
 			\xymatrix{
 				\lb z\ar@{.>}[r]^R & \lb u \\
 				\lb x \ar@{->}[u]^{\le} \ar@{->}[r]^R & \lb y \ar@{.>}[u]_{\le}
 			}
 		\end{equation*}
 	\end{enumerate}
 	%	
 \end{definition}

 \begin{definition}
 	\label{model}
 	A \emph{bi-relational model} $\M$ is a quadruple $\langle W, \rel,\le,V \rangle$ with $\langle W, \rel, \le \rangle$ a bi-relational frame and $V\colon W \to 2^\mathcal{A}$ a monotone valuation function, that is, a function mapping each world $\lb w$ to the subset of propositional atoms that are true at $\lb w$, additionally subject to:
 	if $\lb w \le \lb{w'}$ then $V(\lb w)\subseteq V(\lb{w'})$.
 \end{definition}

 We write $\M, \lb w \Vdash \fm a$ if $\fm a \in V(\lb w)$, and inductively extend the $\Vdash$ relation to all formulas, following the rules for both intuitionistic and modal Kripke models:

 \begin{equation}\label{eq:kripke}
 \begin{array}{rcl}
 %\parbox{30em}{%
 \M, \lb w \Vdash \fm{A \AND B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ and } \M, \lb w \Vdash \fm B\\

 \M, \lb w \Vdash \fm{A \OR B} & \mbox{iff} & \M, \lb w \Vdash \fm A \mbox{ or } \M, \lb w \Vdash \fm B\\

 \M, \lb w \Vdash \fm{A \IMP B} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ with } \futs w{w'}, \mbox{ if } \M, \lb{w'} \Vdash \fm A \mbox{ then } \M, \lb{w'} \Vdash \fm B\\

 \M, \lb w \Vdash \fm{\BOX A} & \mbox{iff} & \mbox{for all } \lb{w'} \mbox{ and } \lb u \mbox{ with } \futs w{w'} \mbox{ and } \accs {w'}u \mbox{, we have } \M, \lb u \Vdash \fm A \hfill \\ %$(\ast)$

 \M, \lb w \Vdash \fm{\DIA A} & \mbox{iff} & \mbox{there exists a } \lb u \mbox{ such that } \accs wu \mbox{ and } \M, \lb u \Vdash \fm A.

 \end{array}
 \end{equation}
 Observe that we never have that $\M, \lb w \Vdash \fm\bot$. 
 %
 We write $\M, \lb w \not\Vdash \fm A$ if it is not the case that $\M, \lb w \Vdash \fm A$, but contrarily to the classical case, we do not have $\M, \lb w \Vdash \fm{\neg A}$ iff $\M, \lb w \not\Vdash \fm A$ (since $\fm{\neg A}$ is defined as $\fm{A \IMP \bot}$).

 From the monotonicity of the valuation function $V$, we get a monotonicity property for the $\Vdash$ relation:
 \begin{proposition}(Monotonicity) 
 	For any formula $\fm A$ and for any $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
 \end{proposition}

 \begin{definition}
 	A formula $\fm A$ is \emph{satisfied} in a model $\M = \langle W, \rel, \le, V \rangle$, if for all $\lb w \in W$ we have $\M, \lb w \Vdash \fm A$.
 	%
 	A formula $\fm A$ is \emph{valid} in a frame $\F = \langle W, \rel, \le \rangle$, if for all valuations $V$, the formula $\fm A$ is satisfied in $\langle W, R, \le, V \rangle$.
 \end{definition}

 Similarly to the classical case, the correspondence between syntax and semantics for $\IK$ can be stated as follows.

 \begin{theorem}[\cite{fischer-servi:84,plotkin:stirling:86}]\label{thm:plotkin}
 	A formula $\fm A$ is a theorem of $\IK$ if and only if $\fm A$ is valid in every bi-relational frame.
 \end{theorem}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
 %
 \section{The system}\label{sec:system}

 In this section we present our fully labelled sequent proof system
 for intuitionistic modal logics. The starting point is the notion of a
 \emph{labelled formula} which is a pair $\labels xA$ of a label $\lb
 x$ and a formula $\fm A$. 
 A \emph{relation atom} is either an expression
 $\accs xy$ or $\futs xy$ where $\lb x$ and $\lb y$ are labels. 
 %
 A \emph{(labelled) sequent} is a triple $\lseq\B\Left\Right$,
 where $\B$ is a set of relational atoms and $\Left$ and $\Right$ are multi-sets of labelled formulas, all written as lists, separated by commas.

 \begin{figure}[!t]
 	\begin{center}
 		\fbox{
 			%
 			\begin{tabular}{c@{\quad}c}
 				$\vlinf{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a} }{}$
 				&
 				$\vlinf{\llabrn\bot}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{}$
 				\\\\
 				$\vlinf{\llabrn\AND}{}{\B,\Left, \labels{x}{A \AND B} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}$
 				&
 				$\vliinf{\rlabrn\AND}{}{\B,\Left \SEQ \Right, \labels{x}{A \AND B}}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{B}}$
 				\\\\
 				$\vliinf{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{B} \SEQ \Right}$
 				&
 				$\vlinf{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}$
 				\\\\
 				\multicolumn{2}{c}{
 					$\vlinf{\rlabrn\IMP}{\lb y \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$
 				}
 				\\\\
 				\multicolumn{2}{c}{
 					$\vliinf{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{\B, \futs xy, \labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{y}{A}}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}$ 
 				}
 				\\\\
 				$\vlinf{\llabrn\BOX}{}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}$
 				&
 				$\vlinf{\rlabrn\BOX}{\lb y, \lb z \mbox{ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{\B, \futs xy, \accs yz, \Left \SEQ \Right, \labels{z}{A}}$
 				\\\\
 				$\vlinf{\llabrn\DIA}{\lb y \mbox{ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$
 				&
 				$\vlinf{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}$
 				\\
 				\multicolumn{2}{c}{
 					$\mbox{\hbox to .9\linewidth{\dotfill}}$
 				}
 				\\
 				$\vlinf{\rn{refl}}{}{\B, \Left \SEQ \Right}{\B, \futs xx, \Left \SEQ \Right}$
 				&
 				$\vlinf{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left \SEQ \Right}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}$
 				\\\\
 				\multicolumn{2}{c}{
 					$\vlinf{\rn{F_1}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs yz, \Left \SEQ \Right}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right}$
 				}
 				\\\\
 				\multicolumn{2}{c}{
 					$\vlinf{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right }$		
 				}
 			\end{tabular}		
 			%\end{minipage}
 		}		
 	\end{center}
 	\caption{System $\labIKp$}
 	\label{fig:labIKp}
 \end{figure}

 Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
 We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
 Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}. However, this naive translation would also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
 \begin{equation}
 \label{eq:nomon}
 \vlinf{\rn{id}'}{}{\B, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a} }{}
 \quad
 \vliinf{\llabrn\IMP'}{}{\B,\Left, \labels{x}{A \IMP B} \SEQ \Right}{\B,\labels{x}{A \IMP B}, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left, \labels{x}{B} \SEQ \Right}
 \quad
 \vlinf{\llabrn\BOX'}{}{\B, \accs xz, \Left, \labels{x}{\BOX A} \SEQ \Right}{\B, \accs xz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right}
 \end{equation}
 that are not sufficient for a complete system, and we will see below
 why. Before, let us first look at the rules $\rlabrn\IMP$ and
 $\rlabrn\BOX$. In the multiple-conlusion nested sequent system
 of~\cite{str:2017maehara}, these are the two rules that force
 single-conclusion.  
 %
 In our system, this phenomenon is replaced by a re-positioning of the considered formulas to a fresh label.
 %
 In the Kripke-semantics in~\eqref{eq:kripke} the two
 connectives $\IMP$ and $\BOX$ are the ones that make use of the
 pre-order relation $\le$. This relation is reflexive and transitive. In
 order to capture that in the proof system, we need to add the rules
 $\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{dyckhoff2012}.}
 %

 Finally, in the semantics, the two relations $\rel$ and $\le$ are
 strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$. These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.\footnote{The logic studied in~\cite{maffezioli2014} has similar semantic conditions (two binary relations in a Kripke frame) that lead to similar rules as ours in the proof system.}
 %
 These rules require to create new labels, and in order to be
 complete, the system needs the \emph{monotonicity} rule $\llabrn{mon}$, shown on the left below. 
 \begin{equation}
 \label{eq:mono}
 \vlinf{\llabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}\Right}{
 	\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}, \labels{y}{A}}\Right}
 \hskip6em
 \vlinf{\rlabrn{mon}}{}{\lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{y}{A}}}{
 	\lseq{\B, \futs{x}{y}}{\Left}{\Right, \labels{x}{A}, \labels{y}{A}}}
 \end{equation}
 Since this rule is a form of contraction, it would cause the same
 problems as contraction in a cut elimination proof. Hence, it is
 preferable to have a system in which this rule is admissible. This is
 the reason why we have monotonicity incorporated in the rules
 $\rn{id}$, $\llabrn\IMP$ and $\llabrn\BOX$ in Figure~\ref{fig:labIKp},
 instead of using the rules in~\eqref{eq:nomon}. Then, not only
 $\llabrn{mon}$ but also its right-hand side version $\rlabrn{mon}$,
 shown on the right in~\eqref{eq:mono} above become admissible.

 \begin{proposition}
 	\label{prop:mon-adm}
 	The rules $\llabrn{mon}$ and $\rlabrn{mon}$ are admissible for $\labIKp$. 
 \end{proposition}

 One can prove this proposition in the same way as one usually proves
 admissibity of contraction in a sequent calculus, by induction on the
 height of the derivation, which in fact would yield a stronger result,
 namely that $\llabrn{mon}$ and $\rlabrn{mon}$ are \emph{height
 	preserving} admissible for $\labIKp$. However, we do not need this
 result in this paper, and therefore we leave it to the interested
 reader. Nonetheless, we will give a short proof of
 Proposition~\ref{prop:mon-adm} at the end of this section.

 Before, let us give another indication of the fact that $\labIKp$ is well-designed, namely that the general identity axiom is admissible.

 \begin{proposition}
 	\label{prop:id}
 	The following general identity axiom~
 	{$\vlinf{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{}$}
 	~is admissible for $\labIKp$. 
 \end{proposition}

 \begin{proof}
 	As standard, we proceed by structural induction on $\fm A$. The two base cases $\fm A=\fm a$ and $\fm A=\fm\bot$ are trivial. The inductive cases are shown below.
 	\begin{itemize}
		\item $\fm{A \AND B}$
 		\begin{smallequation*}
 			\vlderivation{
 				\vlin{\llabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A \AND B} \SEQ \Right, \labels{y}{A \AND B}}{
 					\vliin{\rlabrn\AND}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A \AND B}}{
 						\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{A}}{
 							\vlhy{}
 						}
 					}{
 					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
 						\vlhy{}
 					}
 				}
 			}
 		}
 	\end{smallequation*}
 	\item $\fm{A \OR B}$
 	%\begin{smallequation*}
 	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
 	%	\reducesto
 	%\end{smallequation*}
 	\begin{smallequation*}
 		\vlderivation{
 			\vliin{\llabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{
 				\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A \OR B}}{
 					\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{A} \SEQ \Right, \labels{y}{A}}{
 						\vlhy{}
 					}
 				}
 			}{
 			\vlin{\rlabrn\OR}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{A \OR B}}{
 				\vlin{\labrn{id_g}}{}{\B, \futs xy, \Left, \labels{x}{B} \SEQ \Right, \labels{y}{B}}{
 					\vlhy{}
 				}
 			}
 		}
 	}
 \end{smallequation*}

 \item $\fm{A \IMP B}$
 %	\begin{smallequation*}
 %		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
 %		\reducesto
 %	\end{smallequation*}
 \begin{smallequation*}
 	\vlderivation{
 		\vlin{\rlabrn\IMP}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{
 			\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 				\vliin{\llabrn\IMP}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
 						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{x}{A \IMP B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}, \labels{z}{A}}{
 							\vlhy{}
 						}
 					}
 				}{
 				\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 					\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \futs zz, \Left, \labels{z}{B}, \labels{z}{A} \SEQ \Right, \labels{z}{B}}{
 						\vlhy{}
 					}
 				}
 			}
 		}
 	}
 }
\end{smallequation*}

\item $\fm{\BOX A}$
\begin{smallequation*}
	\vlderivation{
		\vlin{\rlabrn\BOX}{\lb z, \lb w \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{y}{\BOX A}}{
			\vlin{\rn{trans}}{}{\B, \futs xy, \futs yz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
				\vlin{\llabrn\BOX}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{w}{A}}{
					\vlin{\rn{refl}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw; \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
						\vlin{\labrn{id_g}}{}{\B, \futs xy, \futs yz, \futs xz, \accs zw, \futs ww, \Left, \labels{z}{\BOX A}, \labels{w}{A} \SEQ \Right, \labels{w}{A}}{
							\vlhy{}
						}
					}
				}
			}
		}
	}
\end{smallequation*}

\item $\fm{\DIA A}$
%	\begin{smallequation*}
%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
%		\reducesto
%	\end{smallequation*}
\begin{smallequation*}
	\vlderivation{
		\vlin{\llabrn\DIA}{\lb z \mbox{ fresh}}{\B, \futs xy, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{
			\vlin{\color{red}\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \futs xy, \accs xz, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
				\vlin{\rlabrn\DIA}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}}{
					\vlin{\labrn{id_g}}{}{\B, \futs xy, \accs xz, \futs zu, \accs yu, \Left, \labels{z}{A} \SEQ \Right, \labels{y}{\DIA A}, \labels{u}{A}}{
						\vlhy{}
					}
				}
			}
		}
	}
\end{smallequation*}
\qedhere
\end{itemize}
\end{proof}

In the following sections, we will show that the system $\labIKp$ is sound and complete. For the completeness proof we proceed via cut elimination.
%
The cut rule has the following shape:
\begin{equation}
\label{eq:cut}
\vliiinf{\labrn{cut}}{}{
	\lseq\B\Left\Right}{
	\lseq\B\Left{\Right,\labels{z}{C}}}{}{
	\lseq\B{\Left,\labels{z}{C}}{\Right}}
\end{equation}

We say that a formula is \emph{provable} in $\labIKp$ (or $\labIKp+\labrn{cut}$, resp.) if for any label $\lb x$, the sequent $\SEQ \labels{x}{A}$ is derivable from only axioms using the rules in Figure~\ref{fig:labIKp} (with possible instances of $\labrn{cut}$, resp.).
%
We can summarize soundness, completeness, and cut
admissibility of $\labIKp$ in the following result.

\begin{theorem}\label{thm:cutfree-compl}
	For any formula $A$, the following are equivalent.
	%
	\begin{enumerate}
		\item\label{i} $A$ is a theorem of $\IK$. 
		%
		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
		\item\label{iii} $A$ is provable in $\labIKp$.
		%
		\item\label{iv} $A$ is valid in every birelational frame. 
	\end{enumerate}
\end{theorem}

The proof of this theorem is the topic of the following sections. The
equivalence of \ref{i} and \ref{iv} has already been stated in
Theorem~\ref{thm:plotkin}~\cite{fischer-servi:84, plotkin:stirling:86}. The implication
\ref{i}$\implies$\ref{ii} is shown in Section~\ref{sec:completeness},
the implication~\ref{ii}$\implies$\ref{iii} is shown in
Section~\ref{sec:cut-elim}, and finally, the implication \ref{iii}$\implies$\ref{iv} is shown in Section~\ref{sec:soundness}.

Once we have shown cut elimination (the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}), the proof of Proposition~\ref{prop:mon-adm} becomes trivial.

\begin{proof}[Proof of Proposition~\ref{prop:mon-adm}]
	The rule $\llabrn{mon}$ can be derived using the general identity and cut:
	\begin{smallequation*}
		\vlderivation{
			\vliiin{\labrn{cut}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}\Right}{
				\vlin{\labrn{id_g}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}}{\Right, \labels{y}{A}}}{
					\vlhy{}}}{
				\vlhy{\quad}}{
				\vlhy{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{A}, \labels{y}{A}}\Right}}
		}
	\end{smallequation*}
	and both these rules are admissible by Proposition~\ref{prop:id} and
	Theorem~\ref{thm:cutfree-compl}. The case for $\rlabrn{mon}$ is
	similar.
\end{proof}

\begin{remark}
	As mentioned above, the monotonicity rules $\llabrn{mon}$ and $\rlabrn{mon}$ are a form of contraction. So, it is not a surprise that the contraction rules
	\begin{equation*}
		\vlinf{\llabrn{cont}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{\B, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}
		\hskip8em
		\vlinf{\rlabrn{cont}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}
	\end{equation*}
	are admissible in our system, as they are derivable as follows:
	\begin{equation*}
		\vlderivation{
			\vlin{\rn{refl}}{}
			{\B, \Left, \labels{x}{A} \SEQ \Right}
			{\vlin{\llabrn{mon}}{}
				{\B, \futs{x}{x}, \Left, \labels{x}{A} \SEQ \Right}
				{\vlhy{\B, \futs{x}{x}, \Left, \labels{x}{A}, \labels{x}{A} \SEQ \Right}}}
		}
		\hskip6em
		\vlderivation{
			\vlin{\rn{refl}}{}
			{\B, \Left \SEQ \Right, \labels{x}{A}}
			{\vlin{\rlabrn{mon}}{}
				{\B, \futs{x}{x}, \Left \SEQ \Right, \labels{x}{A}}
				{\vlhy{\B, \futs{x}{x}, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{A}}}}
		}
	\end{equation*}
\end{remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Completeness}\label{sec:completeness}

In this section we show our system at work, as most of the section
consists of derivations of axioms of $\IK$ in $\labIKp$. More precisely, we prove completeness of $\labIKp+\rn{cut}$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:

\begin{theorem}\label{thm:completeness}
	For any formula $\fm A$. If $\fm A$ is a theorem of $\IK$ then $\fm A$ is provable in $\labIKp +\labrn{cut}$.
\end{theorem}

\begin{remark}
	We have seen already in the proof of Proposition~\ref{prop:id} the
	use of the rule $\rn{F_2}$. In the following proof of
	Theorem~\ref{thm:completeness} we also see the use of the rules
	$\rn{F_1}$, $\rn{refl}$, and $\rn{trans}$.
\end{remark}

\begin{proof}[Proof of Theorem~\ref{thm:completeness}]
	We begin by showing how the axioms $\kax[1]$--$\kax[5]$ are proved in system $\labIKp$.
	\begin{itemize}
		\item $\kax[1]$:
		\begin{smallequation*}
			\vlderivation{
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{\SEQ \labels{x}{\BOX (A \IMP B) \IMP (\BOX A \IMP \BOX B)}}
				{\vlin {\rlabrn{\IMP}}
					{\lb z \mbox{ fresh}}
					{\lseq{\futs xy}{\labels{y}{\BOX(A \IMP B)}}{\labels{y}{\BOX A \IMP \BOX B}}}
					{\vlin {\rlabrn{\BOX}}
						{\lb w, \lb u \mbox{ fresh}}
						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{z}{\BOX B}}}
						{\vlin {\llabrn{\BOX}}
							{}
							{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}}{\labels{u}{B}}}
							{\vlin {\color{red}\rn{trans}}
								{}
								{\lseq{\futs xy, \futs yz, \futs zw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
								{\vlin {\llabrn{\BOX}}
									{}
									{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}}{\labels{u}{B}}}
									{\vlin {\color{red}\rn{refl}}
										{}
										{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
										{\vliin{\llabrn{\IMP}}
											{}
											{\lseq{\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}}}
											{\vlin {\rn{id_g}}
												{}
												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{u}{B}, \labels{u}{A}}}
												{\vlhy {}}}
											{\vlin {\rn{id_g}}
												{}
												{\lseq{\B}{\labels{y}{\BOX(A \IMP B)}, \labels{z}{\BOX A}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{u}{B}}}
												{\vlhy {}}}}}}}}}}
			}
		\end{smallequation*}
		where $\B$ is equal to: $\futs xy, \futs yz, \futs zw, \futs yw, \futs uu, \accs wu$.
		\item $\kax[2]$:
		\begin{smallequation*}
			\vlderivation {
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{ \SEQ \labels{x}{\BOX (A \IMP B) \IMP (\DIA A \IMP \DIA B)}}
				{\vlin {\rlabrn{\IMP}}
					{\lb z \mbox{ fresh}}
					{\lseq{\futs xy}{\labels{y}{\BOX (A \IMP B)}}{\labels{y}{(\DIA A \IMP \DIA B)}}}
					{\vlin {\llabrn{\DIA}}
						{\lb u \mbox{ fresh}}
						{\lseq{\futs xy, \futs yz}{\labels{y}{\BOX (A \IMP B)}, \labels{z}{\DIA A}}{\labels{z}{\DIA B}}}
						{\vlin{\rlabrn{\DIA}}
							{}
							{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}}}
							{\vlin {\llabrn{\BOX}}
								{}
								{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}}{\labels{z}{\DIA B}, \labels{u}{B}}}
								{\vlin {\color{red}\rn{refl}}
									{}
									{\lseq{\futs xy, \futs yz, \accs zu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
									{\vliin{\llabrn{\IMP}}
										{}
										{\lseq{\futs xy, \futs yz, \accs zu, \futs uu}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
										{\vlin {\rn{id_g}}
											{}
											{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}}{\labels{z}{\DIA B}, \labels{u}{B}, \labels{u}{A}}}
											{\vlhy {}}}
										{\vlin {\rn{id_g}}
											{}
											{\lseq{\B}{\labels{y}{\BOX (A \IMP B)}, \labels{u}{A}, \labels{u}{A \IMP B}, \labels{u}{B}}{\labels{z}{\DIA B}, \labels{u}{B}}}
											{\vlhy {}}}								}}}}}}
			}
		\end{smallequation*}

		where $\B$ is equal to $\futs xy, \futs yz, \accs zu, \futs uu$.
		\item $\kax[3]$:
		\begin{smallequation*}
			\vlderivation {
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{\SEQ \labels{x}{\DIA (A \OR B) \IMP (\DIA A \OR \DIA B)}}
				{\vlin {\llabrn{\DIA}}
					{\lb z \mbox{ fresh}}
					{\lseq{\futs xy}{\labels{y}{\DIA (A \OR B)}}{\labels{y}{\DIA A \OR \DIA B}}}
					{\vliin{\llabrn{\OR}}{}{\lseq{\futs xy, \accs yz}{\labels{z}{A \OR B}}{\labels{y}{\DIA A \OR \DIA B}}}{\vlin {\rlabrn{\OR}}
							{}
							{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A \OR \DIA B}}}
							{\vlin {\rlabrn{\DIA}}
								{}
								{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
								{\vlin {\color{red}\rn{refl}}
									{}
									{\lseq{\futs xy, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
									{\vlin {\rn{id_g}}
										{}
										{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{A}}{\labels{y}{\DIA A}, \labels{z}{A}, \labels{y}{\DIA B}}}
										{\vlhy {}}}}}}{\vlin {\rlabrn{\OR}}
							{}
							{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A \OR \DIA B}}}
							{\vlin {\rlabrn{\DIA}}
								{}
								{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}}}
								{\vlin {\color{red}\rn{refl}}
									{}
									{\lseq{\futs xy, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
									{\vlin {\rn{id_g}}
										{}
										{\lseq{\futs xy, \futs zz, \accs yz}{\labels{z}{B}}{\labels{y}{\DIA A}, \labels{y}{\DIA B}, \labels{z}{B}}}
										{\vlhy {}}}}}}}}
			}
		\end{smallequation*}
		\item $\kax[4]$:
		\begin{smallequation*}
			\vlderivation {
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{\SEQ \labels{x}{(\DIA A \IMP \BOX B) \IMP \BOX (A \IMP B)}}
				{\vlin {\rlabrn{\BOX}}
					{\lb z, \lb w \mbox{ fresh}}
					{\lseq{\futs xy}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{y}{\BOX (A \IMP B)}}}
					{\vlin {\rlabrn{\IMP}}
						{\lb u \mbox{ fresh}}
						{\lseq{\futs xy, \futs yz, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}}{\labels{w}{A \IMP B}}}
						{\vlin {\color{red}{\rn{F_1}}}
							{\lb t \mbox{ fresh}}
							{\lseq{\futs xy, \futs yz, \futs wu, \accs zw}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
							{\vlin {\color{red}\rn{trans}}
								{}
								{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
								{\vliin {\llabrn{\IMP}}
									{}
									{\lseq{\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}}}
									{\vlin {\rlabrn{\DIA}}
										{}
										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}}}
										{\vlin {\color{red}\rn{refl}}
											{}
											{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
											{\vlin {\rn{id_g}}
												{}
												{\lseq{\B, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}}{\labels{u}{B}, \labels{t}{\DIA A}, \labels{u}{A}}}
												{\vlhy {}}}}}
									{\vlin {\color{red}\rn{refl}}
										{}
										{\lseq{\B}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
										{\vlin {\llabrn{\BOX}}
											{}
											{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}}{\labels{u}{B}}}
											{\vlin {\color{red}\rn{refl}}
												{}
												{\lseq{\B, \futs tt}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
												{\vlin {\rn{id_g}}
													{}
													{\lseq{\B, \futs tt, \futs uu}{\labels{y}{\DIA A \IMP \BOX B}, \labels{u}{A}, \labels{t}{\BOX B}, \labels{u}{B}}{\labels{u}{B}}}
													{\vlhy {}}}}}}}}}}}}
		\end{smallequation*}

		where $\B$ is equal to $\futs xy, \futs yz, \futs wu, \futs zt, \futs yt, \accs zw, \accs tu$.
		\item $\kax[5]$:
		\begin{smallequation*}
			\vlderivation {
				\vlin{\rlabrn{\IMP}}
				{\lb y \mbox{ fresh}}
				{\SEQ \labels{x}{\DIA \BOT \IMP \BOT}}
				{\vlin {\llabrn{\DIA}}
					{\lb z \mbox{ fresh}}
					{\lseq{\futs xy}{\labels{y}{\DIA \BOT}}{\labels{y}{\BOT}}}
					{\vlin {\llabrn{\BOT}}
						{}
						{\lseq{\futs xy, \accs yz}{\labels{z}{\BOT}}{\labels{y}{\BOT}}}
						{\vlhy {}}}}
			}
		\end{smallequation*}

	\end{itemize}
	Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
	\begin{smallequation*}
		\vlderivation {
			\vlin{\rlabrn{\IMP}}
			{\lb y \mbox{ fresh}}
			{\SEQ \labels{x}{A \AND B \IMP B}}
			{\vlin {\llabrn{\AND}}
				{}
				{\lseq{\futs xy}{\labels{y}{A \AND B}}{\labels{y}{B}}}
				{\vlin {\color{red}\rn{refl}}
					{}
					{\lseq{\futs xy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
					{\vlin {\rn{id_g}}
						{}
						{\lseq{\futs xy, \futs yy}{\labels{y}{A}, \labels{y}{B}}{\labels{y}{B}}}
						{\vlhy {}}}}}
		}
	\end{smallequation*}

	Finally, we have to show how the rules of modus ponens and
	necessitation can be simulated in our system. For modus ponens, this
	is standard using the cut rule and for necessitation, we can
	transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
	follows.
	A proof of $\fm A$ is in fact a proof $\DD$ of the sequent
	$\SEQ{\labels{z}{A}}$ for some label $\lb z$. If $\lb x$ and $\lb y$
	are fresh labels, we can transform $\DD$ into a proof $\DD'$ of the
	sequent $\futs xy, \accs yz \SEQ \labels{z}{A}$ by adding $\futs xy,
	\accs yz$ to every line. We can now apply the $\rlabrn\BOX$-rule to
	obtain a proof of $\SEQ \labels{x}{\BOX A}$.

	This completes the proof of Theorem~\ref{thm:completeness}.
\end{proof}

Note that we could also have proved completeness via proof search and a countermodel construction argument, as rules are terminationg in $\labIKp$. 
%
This works well for $\IK$ (and a small number of its extensions) and have been used for example by~\cite{maffezioli:etal:synthese13}. 
%
Moreover, it would allow us to show completeness directly for any labelled sequents, not only specifically for formulas.

However, this technique would not be easily adaptable to the general extensions with consider here. 
%
We therefore compromised the generality of the result to the expressivitly of the logic themselves, and restricted the completeness to formulas expressible in $\IK$ and all the Scott-Lemmon logics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Soundness}\label{sec:soundness}

In order to prove the implication \ref{iii}$\implies$\ref{iv} from
Theorem~\ref{thm:cutfree-compl} we need to show that each sequent rule
of our system $\labIKp$ is sound. To make precise what that actually
means, we have to extend the relation $\Vdash$, defined in
Section~\ref{sec:intmod} from formulas to sequents. This is the
purpose of the following definitions.

\begin{definition}\label{def:force-seq}
	Let $\M = \langle W, \rel_\M, \le_\M, V \rangle$ be a model, and let
	$\SG$ be the sequent $\lseq\B\Left\Right$. 
	%
	A \emph{$\SG$-interpretation
		in $\M$} is a mapping $\inter{\cdot}$ from the labels in $\SG$ to the set $W$ of worlds in $\M$, such that whenever $\accs xy$ in $\B$, then $\inter x\rel_\M\inter y$, and whenever $\futs xy$ in $\B$, then $\inter x\le_\M\inter y$. Now we can define 
	\begin{equation}
	\M,\inter\cdot\Vdash\SG\qquad\mbox{iff}\qquad
	\parbox{20em}{if for all $\labels{x}{A} \in \Gamma$, we have $\M, \inter x \Vdash \fm A$, then there exists $\labels{z}{B} \in \Delta$ such that $\M, \inter z \Vdash \fm B$.}
	\end{equation}
\end{definition}

\begin{definition}\label{def:valid-seq}
	A sequent $\SG$ is \emph{satisfied} in $\M = \langle W, \rel, \le, V
	\rangle$ iff for all $\SG$-interpretations $\inter\cdot$ we have
	$\M,\inter\cdot\Vdash\SG$.
	%%
	A sequent $\SG$ is \emph{valid} in a frame $\F = \langle W, \rel,
	\le \rangle$, if for all valuations $V$, the sequent $\SG$ is
	satisfied in $\langle W, R, \le, V \rangle$.
\end{definition}

We are now ready to state and prove the main theorem of this section, of which
the implication \ref{iii}$\implies$\ref{iv} in
Theorem~\ref{thm:cutfree-compl} is an immediate consequence.

\begin{theorem}\label{thm:soundness}
	If a sequent $\SG$ is provable in $\labIKp$, then it is valid in every birelational frame.
\end{theorem}

\begin{proof}
	We proceed by induction on the height of the derivation of $\SG$, and we show for all rules in $\labIKp$
	$$
	\vliiinf{\labrn{r}}{}{\SG}{\SGi1}{\cdots}{\SGi n}
	$$ for $n\in\{0,1,2\}$, that whenever $\SGi1,\ldots,\SGi n$ are
	valid in all birelational frame, then so is $\SG$. It follows from a case analysis on $\rn r$:
	\begin{itemize}
		\item $\rlabrn\bot$: This is trivial because $\bot$ is never forced.
		\item $\rn{id}$: This follows immediately from Proposition~\ref{prop:mon-adm}.
		\item $\llabrn\BOX$: By way of contradiction, assume that $\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ \Right$
		is valid in all birelational frames, but $\B, \futs xy,	\accs yz,\Left, \labels{x}{\BOX A} \SEQ \Right$ is not. This means that
		we have a model $\M$ and an interpretation $\inter\cdot$, such
		that $\M,\inter\cdot\not\Vdash\B, \futs xy, \accs yz, \Left,	\labels{x}{\BOX A} \SEQ \Right$, i.e., $\inter x\le_\M\inter y$
		and $\inter y\rel_\M\inter z$ and $\cforce \M x{\BOX A}$ but
		$\cnforce \M wB$ for all $\labels wB\in\Right$. However, by the
		definition of forcing in~\eqref{eq:kripke} we also have $\cforce
		\M zA$, and consequently $\nforce \M{\inter\cdot}{\B, \futs xy, \accs yz, \Left, \labels{x}{\BOX A}, \labels{z}{A} \SEQ
			\Right}$. Contradiction.
		%
		\item $\rlabrn\BOX$: By way of contradiction, assume that $\B, \futs xy,
		\accs yz, \Left \SEQ \Right, \labels{z}{A}$ is valid in all
		birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{\BOX
			A}$ is not, where $\lb y$ and $\lb z$ do not occur in $\B$ or
		$\Left$ or $\Right$.
		This means that we have a model $\M$ and an
		interpretation $\inter\cdot$, such that
		$\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}$. 
		%
		So in particular, there are worlds $\lb{y'}$ and $\lb{z'}$
		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
		$\lb{y'}\rel_\M\lb{z'}$ and $\nforce\M{\lb{z'}}{\fm A}$. 
		%
		Now we let
		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
		y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
		on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \futs xy,
			\accs yz, \Left \SEQ \Right, \labels{z}{A}}$. Contradiction.

		\item $\rlabrn\IMP$: By way of contradiction, assume that $\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}$ is valid in all birelational frames, but $\B, \Left \SEQ \Right, \labels{x}{A \IMP B}$ is not, where $\lb y$ does not occur in $\B$ or $\Left$ or $\Right$. This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}$. So there exists a world $\lb{y'}$ in $\M$ such that $\inter x\le_\M \lb{y'}$ and $\cforce\M{y'}{A}$ but $\nforce\M{\lb{y'}}{\fm B}$. Now we let 	$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot'=\inter\cdot$ on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$. Contradiction.

		\item $\llabrn\DIA$: By way of contradiction, assume that $\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right$ is valid in all birelational frames, but $\B, \Left, \labels{x}{\DIA A} \SEQ \Right$ is not, where $\lb y$ does not occur in $\B$ or $\Left$ or $\Right$. This means that we have a model $\M$ and an interpretation $\inter\cdot$, such that $\nforce\M{\inter\cdot}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}$, i.e. $\cforce \M x{\DIA A}$. This means that there exists world $\lb{y'}$ in $\M$ such that $\inter x\rel_\M \lb{y'}$ and $\cforce \M {\lb{y'}}{A}$. Now we let $\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot' = \inter\cdot$ on all other labels. Then $\nforce\M{\inter\cdot'}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}$. Contradiction.

	\end{itemize}
	The other cases are similar (and simpler), and we leave them to the
	reader. In particular, note that the cases for the rules $\rn{refl}$,
	$\rn{trans}$, $\rn{F_1}$ and $\rn{F_2}$ are trivial, as all
	birelations frames have to obey the corresponding conditions.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Cut Admissibility}\label{sec:cut-elim}
In this section we are going to prove the admissibility of cut for
$\labIKp$. The presentations follows the standard textbook
exposition (see, e.g., \cite{troelstra:schwichtenberg:00,negri:vonplato:01})
adapted to the system at hand.\footnote{As pointed out
	in~\cite{girard:87:a}, any minor change in a proof system demands
	to do the whole cut elimination argument from scratch.}
%%

\begin{theorem}
	\label{thm:cut-adm}
	The $\labrn{cut}$ rule is admissible for $\labIKp$.
\end{theorem}

This theorem directly entails the implication \ref{ii}$\implies$\ref{iii} of Theorem~\ref{thm:cutfree-compl}. But before we can prove it, we need a series of auxiliary  lemmas.

The \emph{height} of a derivation $\DD$, denoted by $\height\DD$, is the height of $\DD$ when seen as a tree, i.e., the length of
the longest path in the tree from its root to one of its leaves.

We say that a rule is \emph{height-preserving admissible} if for every derivation $\DD$ of its premise(s) there is a derivation $\DD'$ of its conclusion such that $\height{\DD'}\le\height\DD$. A rule is \emph{height-preserving invertible} if for every
derivation of the conclusion of the rule there are derivations for each of its premises with at most the same height.

The first lemma is the height-preserving admissibility of weakening on both relational atoms and labelled formulas.

\begin{lemma}
	\label{lem:weak-adm}
	The weakening rule
	~$\vlinf{\rn{weak}}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}{\lseq{\B}{\Left}{\Right}}$~
	is height-preserving admissible for $\labIKp$.
\end{lemma}

\begin{proof}
	By a straightforward induction on the height of the derivation, we can transform any derivation
	\begin{equation*}
		\vlderivation {\vlpd {\D}{}{\lseq{\B}{\Left}{\Right}}}
		\qquad
		\mbox{into}
		\qquad
		\vlderivation {\vlpd{\Dw}{}{\lseq{\B,\B'}{\Left,\Left'}{\Right,\Right'}}}
	\end{equation*}
	of the same (or smaller) height.
\end{proof}

The next lemma looks like a special case of
Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
preserve the height, and second, we cannot prove it using $\rn{cut}$ rule as we
are trying to eliminate it from derivations.

\begin{lemma}\label{lem:adm-mon-at}
	The atomic version of $\llabrn{mon}$ and $\rlabrn{mon}$
	$$
	\vlinf{\llabrn{mon_a}}{}{\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{a}}\Right}{
		\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{a}, \labels{y}{a}}\Right}
	\qquad
	\vlinf{\rlabrn{mon_a}}{}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{a}}{\B, \futs xy, \Left \SEQ \Right, \labels{x}{a}, \labels{y}{a}}
	$$
	are height-preserving admissible for $\labIKp$.
	%
\end{lemma}

\begin{proof}
	We show the details for $\llabrn{mon_a}$, the argument is the same for $\rlabrn{mon_a}$.
	By induction on the height of $\D$, we prove that for any proof of $\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{a}, \labels{y}{a}}{\Right}$, there exists a proof of $\lseq{\B, \futs{x}{y}}{\Left, \labels{x}{a}}{\Right}$
	of the same (or smaller) height.
	The inductive step is straightforward by permutation of rules.
	The base cases are obtained as follows:
	\begin{smallequation*}
		\vlderivation{
			\vlin{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{
				\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{z}{a}}{
					\vlhy{}
				}
			}
		}
		\reducesto
		\vlderivation{
			\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{y}{z}, \futs{x}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{
					\vlhy{}
				}}
			}
		\end{smallequation*}

		\begin{smallequation*}
			\vlderivation{
				\vlin{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{
					\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{x}{a}}{
						\vlhy{}
					}
				}
			}
			\reducesto
			\vlderivation{
				\vlin{\color{red}\labrn{refl}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{x}{x}, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{
						\vlhy{}
					}}}
				\end{smallequation*}

				\begin{smallequation*}
					\vlderivation{
						\vlin{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
							\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{y}{a}}{
								\vlhy{}
							}
						}
					}
					\reducesto
					\vlinf{\labrn{id}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{}
					\qedhere
				\end{smallequation*}

			\end{proof}

			The next lemma shows that all the rules in our system are invertible, as already mentioned in the introduction.

			\begin{lemma}
				\label{lem:inv}
				All single-premise rules of $\labIKp$ are height-preserving
				invertible. Furthermore, the rules $\llabrn{\OR}$ and
				$\rlabrn{\AND}$ are height-preserving invertible on both premises, and the
				rule $\llabrn{\IMP}$ is height-preserving invertible on the right premise.
				%
			\end{lemma}

			\begin{proof}
				For each rule $\rn{r}$, we need to show that if there exists a proof $\DD$ of the conclusion, there exists a proof $\DD^{\rn r_i}$ of the $i$-th premise, of the same (or smaller) height.
				For $\rlabrn\AND$, $\llabrn\AND$, $\rlabrn\OR$, $\llabrn\OR$, and the right premise of $\llabrn\IMP$, we use a standard induction on the height of $\DD$.
				%
				For $\rlabrn\IMP$, $\rlabrn\BOX$, $\llabrn\DIA$ as well, but
				we need to make sure that the obtained derivation uses a fresh label by using substitution inside $\DD^{\rn r}$ when necessary.
				%
				The other rules can be shown invertible using Lemma~\ref{lem:weak-adm}. 
			\end{proof}

			The next lemma is the central ingredient of our cut elimination proof.

			\begin{lemma}
				\label{lem:reduction}
				Given a derivation of shape
				$$
				\vlderivation{
					\vliiin{\labrn{cut}}{}{\lseq\B\Left\Right}{
						\vlhtr{\DD_1}{\lseq\B\Left{\Right,\labels{z}{C}}}}{
						\vlhy{}}{
						\vlhtr{\DD_2}{\lseq\B{\Left,\labels{z}{C}}{\Right}}}}
				$$
				where $\DD_1$ and $\DD_2$ are both cut-free, there is a cut-free
				derivation of ${\lseq\B\Left\Right}$
			\end{lemma}

			\begin{proof}
				%
				The proof is by a lexicographic induction on the complexity of the cut-formula $C$ and the sum of the heights $\height{\DD_1}+\height{\DD_2}$.
				%
				We perform a case analysis on the last rule used in $\DD_1$ above the $\rn{cut}$ and whether it applies to the cut-formula or not.
				%
				In case it does not, we are in a \emph{commutative} case; in case it does, we have to perform a similar analysis on $\DD_2$ to end up in a \emph{key} case.

				\begin{description}
					\item[Base cases:]\label{base-cases}
					When the last rule in $\DD_1$ is an axiom, 
					%
					we can produce directly a cut-free derivation of the conclusion.
					%
					In the first case, we appeal to Lemma~\ref{lem:adm-mon-at}, to use the atomic monotonicity rule freely.
					\begin{itemize}
						\item 
						\begin{smallequation*}
							\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right}{
								\vlin{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
									\vlhy{}	
								}
							}{
							\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}		
						}
						\reducesto
						\vlderibase{\llabrn{mon_a}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right}{
							\vlhtr{\DD_2^{\rn w}}{\B, \futs xy, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right}
						}
					\end{smallequation*}

					\item
					\begin{smallequation*}
						\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
							\vlin{\labrn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}, \labels{z}{C}}{
								\vlhy{}	
							}
						}{
						\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{x}{a}, \labels{z}{C} \SEQ \Right, \labels{y}{a}}		
					}
					\reducesto
					\vlderibase{\rn{id}}{}{\B, \futs xy, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
						\vlhy{}
					}
				\end{smallequation*}

				\item
				\begin{smallequation*}
					\vlderiibase{\labrn{cut}}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{
						\vlin{\llabrn{\BOT}}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right, \labels{z}{C}}{
							\vlhy{}	
						}
					}{
					\vlhtr{\DD_2}{\B, \Left, \labels{x}{\BOT}, \labels{z}{C} \SEQ \Right}		
				}
				\reducesto
				\vlderibase{\llabrn{\BOT}}{}{\B, \Left, \labels{x}{\BOT} \SEQ \Right}{
					\vlhy{}
				}
			\end{smallequation*}
		\end{itemize}
		\item[Commutative cases:]\label{commutative-cases}
		In such a case, the complexity of the cut-formula stays constant, but the height of the derivation above the $\rn{cut}$ decreases.
		\begin{itemize}
			\item $\llabrn\IMP$:
			\begin{smallequation*}
				\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
					\vliin{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}}{
						\vlhtr{\DD_1}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
					}{
					\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
				}
			}{
			\vlhtr{\DD_3}{\B, \futs xy, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right}
		}
	\end{smallequation*}

	\begin{smallequation*}
		\reducesto\qquad\vlderiibase{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
			\vlhtr{\DD_1'}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
		}{
		\vlhtr{\DD_2'}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}
	}
\end{smallequation*}

\begin{small}
	{with}$\quad\DD_1' = \quad
	\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
		\vlhtr{\DD_1}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{z}{C}, \labels{y}{A}}
	}{
	\vlhtr{\DD_3^{\rn w}}{\B, \futs xy, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
}	$

{and}$\quad\DD_2'= \quad
\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}{
	\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
}{
\vlhtr{\DD_3^{\invr{\llabrn\IMP}}}{\B, \futs xy, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
}$
\end{small}

where $\DD_3^{\rn w}$ is obtained using Lemma~\ref{lem:weak-adm} and $\DD_3^{\llabrn\IMP}$ is obtained using Lemma~\ref{lem:inv}. We use the same naming scheme in the following cases.
\item $\rlabrn\IMP$:
\begin{smallequation*}\hskip-8em
	\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
		\vlin{\rlabrn\IMP}{\text{\footnotesize $\lb{x'}$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B, \futs{x}{x'}, \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{A \IMP B}}
}
\end{smallequation*}

\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\rlabrn\IMP}{\text{\footnotesize $\lb{x''}$ fresh (also in $\DD_2$)}}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
		\vliin{\labrn{cut}}{}{\B, \futs{x}{x''}, \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}{
			\vlhtr{\DD_1[x''/x']}{\B, \futs{x}{x''}, \Left, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\invr{\rlabrn\IMP}}}{\B, \futs{x}{x''}, \Left, \labels{z}{C}, \labels{x''}{A} \SEQ \Right, \labels{x''}{B}}
	}
}
\end{smallequation*}
\item $\llabrn\BOX$:
\begin{smallequation*}\hskip-8em
	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A} \SEQ \Right}{
		\vlin{\llabrn\BOX}{}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A} \SEQ \Right, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{z}{C} \SEQ \Right}
}
\end{smallequation*}

\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\llabrn\BOX}{}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A} \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}{
			\vlhtr{\DD_1}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\rn w}}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{v}{A}, \labels{z}{C} \SEQ \Right}
	}
}
\end{smallequation*}

\item $\rlabrn\BOX$:
\begin{smallequation*}\hskip-8em
	\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{
		\vlin{\rlabrn\BOX}{\text{\footnotesize $\lb{x'},\lb{y'}$ fresh}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B, \futs{x}{x'}, \accs{x'}{y'}, \Left \SEQ \Right, \labels{y'}{A}, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\BOX A}}
}
\end{smallequation*}

\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\rlabrn\BOX}{\text{\footnotesize $\lb u,\lb v$ fresh (also in $\DD_2$)}}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{
		\vliin{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left \SEQ \Right, \labels{v}{A}}{
			\vlhtr{\DD_1}{\B, \futs xu, \accs uv, \Left \SEQ \Right, \labels{v}{A}, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\invr{\rlabrn\BOX}}}{\B, \futs xu, \accs uv, \Left, \labels{z}{C} \SEQ \Right, \labels{v}{A}}
	}
}
\end{smallequation*}
\item $\llabrn\DIA$:

\begin{smallequation*}\hspace*{-5.5em}
	\vlderiibase{\labrn{cut}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
		\vlin{\llabrn\DIA}{\text{\footnotesize $\lb{y'}$ fresh}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B, \accs{x}{y'}, \Left, \labels{y'}{A} \SEQ \Right, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B, \Left, \labels{x}{\DIA A}, \labels{z}{C} \SEQ \Right}
}
\end{smallequation*}

\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\llabrn\DIA}{\text{\footnotesize $\lb{y''}$ fresh (also in $\DD_2$)}}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B, \accs{x}{y''}, \Left, \labels{y''}{A} \SEQ \Right}{
			\vlhtr{\DD_1[y''/y']}{\B, \accs{x}{y''}, \Left, \labels{y''}{A} \SEQ \Right, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\invr{\llabrn\DIA}}}{\B, \accs{x}{y''}, \Left, \labels{y''}{A}, \labels{z}{C} \SEQ \Right}
	}
}
\end{smallequation*}

\item $\rlabrn\DIA$:

\begin{smallequation*}\hspace*{-5.5em}
	\vlderiibase{\labrn{cut}}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{
		\vlin{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{z}{C}}{
			\vlhtr{\DD_1}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
		}
	}{
	\vlhtr{\DD_2}{\B, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}}
}
\end{smallequation*}

\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{
		\vliin{\labrn{cut}}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}{
			\vlhtr{\DD_1}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}, \labels{z}{C}}
		}{
		\vlhtr{\DD_2^{\rn w}}{\B, \Left, \labels{z}{C} \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
	}
}
\end{smallequation*}

\bigskip
\item$\rn{refl}$:
\begin{smallequation*}
	\vlderiibase{\rn{cut}}{}
	{\B, \Left \SEQ \Right}
	{\vlin{\rn{refl}}{}{\B, \Left \SEQ \Right, \labels{z}{C}}{\vlhtr{\DD_1}{\B, \futs xx, \Left \SEQ \Right, \labels{z}{C}}}}
	{\vlhtr{\DD_2}{\B, \Left, \labels{z}{C} \SEQ \Right}}
	\reducesto
	\vlderibase{\rn{refl}}{}{\B, \Left \SEQ \Right}{\vliin{\rn{cut}}{}
		{\B, \futs xx, \Left \SEQ \Right}
		{\vlhtr{\DD_1}{\B, \futs xx, \Left \SEQ \Right, \labels{z}{C}}}
		{\vlhtr{\DD_2^{\rn w}}{\B, \futs xx, \Left, \labels{z}{C} \SEQ \Right}}}
\end{smallequation*}

\bigskip
\item$\rn{trans}$:
\begin{smallequation*}
	\vlderiibase{\rn{cut}}{}
	{\B, \futs xy, \futs yz, \Left \SEQ \Right}
	{\vlin{\rn{trans}}{}
		{\B, \futs xy, \futs yz, \Left \SEQ \Right, \labels{z}{C}}
		{\vlhtr{\DD_1}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right, \labels{z}{C}}}}
	{\vlhtr{\DD_2}{\B, \futs xy, \futs yz, \Left, \labels{z}{C} \SEQ \Right}}
\end{smallequation*}
\begin{smallequation*}
	\reducesto
	\vlderibase{\rn{trans}}{}
	{\B, \futs xy, \futs yz, \Left \SEQ \Right}
	{\vliin{\rn{cut}}{}
		{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right}
		{\vlhtr{\DD_1}{\B, \futs xy, \futs yz, \futs xz, \Left \SEQ \Right, \labels{z}{C}}}
		{\vlhtr{\DD_2^{\rn w}}{\B, \futs xy, \futs yz, \futs xz, \Left, \labels{z}{C} \SEQ \Right}}}
\end{smallequation*}

\item$\rn{F_1}$:
\begin{smallequation*}
	\vlderiibase{\rn{cut}}{}
	{\B, \accs xy, \futs yz, \Left \SEQ \Right}
	{\vlin{\rn{F_1}}{\lb u \mbox{ fresh}}
		{\B, \accs xy, \futs yz, \Left \SEQ \Right, \labels{z}{C}}
		{\vlhtr{\DD_1}{\B, \accs xy, \futs yz, \futs xu, \accs uz, \Left \SEQ \Right, \labels{z}{C}}}}
	{\vlhtr{\DD_2}{\B, \accs xy, \futs yz, \Left, \labels{z}{C} \SEQ \Right}}
\end{smallequation*}
\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\rn{F_1}}{\lb v \mbox{ fresh (also in $\DD_2$)}}
	{\B, \accs xy, \futs yz, \Left \SEQ \Right}
	{\vliin{\rn{cut}}{}
		{\B, \accs xy, \futs yz, \futs xv, \accs vz, \Left \SEQ \Right}
		{\vlhtr{\DD_1[v/u]}{\B, \accs xy, \futs yz, \futs xv, \accs vz, \Left \SEQ \Right, \labels{z}{C}}}
		{\vlhtr{\DD_2^{\rn w}}{\B, \accs xy, \futs yz, \futs xv, \accs vz, \Left, \labels{z}{C} \SEQ \Right}}}
\end{smallequation*}

\item$\rn{F_2}$:
\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B, \accs xy, \futs xz, \Left \SEQ \Right}
	{\vlin{\rn{F_2}}{\lb u \mbox{ fresh}}{\B, \accs xy, \futs xz, \Left \SEQ \Right, \labels{z}{C}}{\vlhtr{\DD_1}{\B, \accs xy, \futs xz, \futs yu, \accs zu, \Left \SEQ \Right, \labels{z}{C}}}}
	{\vlhtr{\DD_2}{\B, \accs xy, \futs xz, \Left, \labels{z}{C} \SEQ \Right}}
\end{smallequation*}
\begin{smallequation*}\hskip8em
	\reducesto
	\vlderibase{\rn{F_2}}{\lb v \mbox{ fresh (also in $\DD_2$)}}{\B, \accs xy, \futs xz, \Left \SEQ \Right}{\vliin{\labrn{cut}}{}
		{\B, \accs xy, \futs xz, \futs yv, \accs zv, \Left \SEQ \Right}
		{\vlhtr{\DD_1[v/u]}{\B, \accs xy, \futs xz, \futs yv, \accs zv, \Left \SEQ \Right, \labels{z}{C}}}
		{\vlhtr{\DD_2^{\rn w}}{\B, \accs xy, \futs xz, \futs yv, \accs zv, \Left, \labels{z}{C} \SEQ \Right}}}
\end{smallequation*}

\end{itemize}
\item[Key cases:]\label{key-cases}
If the last rule in $\DD_1$ and the last rule in $\DD_2$ both apply to the cut-formulas, then it is the complexity of the cut-formula that is the decreasing inductive measure, save for the modal cases, where it is important to note the combination of induction on both height and formula size . 
\begin{itemize}
	\item $C=A \AND B$:

	\begin{smallequation*}\hspace*{-7.5em}
		\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right}{
			\vliin{\rlabrn\AND}{}{\B, \Left \SEQ \Right, \labels{x}{A \AND B}}{
				\vlhtr{\DD_1}{\B, \Left \SEQ \Right, \labels{x}{A}}}{
				\vlhtr{\DD_2}{\B, \Left \SEQ \Right, \labels{x}{B}}}}		
		{
			\vlin{\llabrn\AND}{}{\B, \Left, \labels{x}{A \AND B} \SEQ \Right}{
				\vlhtr{\DD_3}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}}
		}
	\end{smallequation*}

	\begin{smallequation*}\hskip8em
		\reducesto
		\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right}{
			\vlhtr{\DD_1}{\B, \Left \SEQ \Right, \labels{x}{A}}
			%	
		}		
		{
			\vliin{\labrn{cut}}{}{\B, \Left, \labels{x}{A} \SEQ \Right}{
				\vlhtr{\DD_2^{\rn w}}{\B, \Left, \labels{x}{A} \SEQ \Right, \labels{x}{B}}
			}{
			\vlhtr{\DD_3}{\B, \Left, \labels{x}{A}, \labels{x}{B} \SEQ \Right}
		}
	}
\end{smallequation*}

\item $C=A \OR B$:

\begin{smallequation*}\hspace*{-7.5em}
	\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right}{
		\vlin{\rlabrn\OR}{}{\B, \Left \SEQ \Right, \labels{x}{A \OR B}}{
			\vlhtr{\DD_1}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}}}		
	{
		\vliin{\llabrn\OR}{}{\B, \Left, \labels{x}{A \OR B} \SEQ \Right}{
			\vlhtr{\DD_2}{\B, \Left, \labels{x}{A} \SEQ \Right}}{
			\vlhtr{\DD_3}{\B, \Left, \labels{x}{B} \SEQ \Right}}
	}
\end{smallequation*}

\begin{smallequation*}\hskip8em
	\reducesto
	\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B, \Left \SEQ \Right, \labels{x}{A}}{
			\vlhtr{\DD_1}{\B, \Left \SEQ \Right, \labels{x}{A}, \labels{x}{B}}}{
			\vlhtr{\DD_3^{\rn w}}{\B, \Left, \labels{x}{B} \SEQ \Right, \labels{x}{A}}}}		
	{
		\vlhtr{\DD_2}{\B, \Left, \labels{x}{A} \SEQ \Right}
		%		
	}
\end{smallequation*}

\item $C=A\IMP B$:

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left \SEQ \Right}{
		\vlin{\rlabrn\IMP}{}{\B, \futs xy, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
			\vlhtr{\DD_1}{\B, \futs xy, \futs{x}{x'}, \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}}
		}
	}{
	\vliin{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
		\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
	}{
	\vlhtr{\DD_3}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}
}
}
\reducesto
\end{smallequation*}

\begin{smallequation*}
	\hspace*{-7em}
	\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left \SEQ \Right}{\vlhtr{\DD_1'}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{A}}}{\vliin{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right}{
			\vlhtr{\DD_1[y/x']}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}
		}{
		\vlhtr{\DD_3}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}
	}
}
\end{smallequation*}

\begin{small}
	{with}$\quad\DD_1' = \quad
	\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{A}}{
		\vlin{\rlabrn\IMP}{}{\B, \futs xy, \Left \SEQ \Right, \labels{x}{A \IMP B}, \labels{y}{A}}{
			\vlhtr{\DD_1^{\rn w}}{\B, \futs xy, \futs{x}{x'}, \Left, \labels{x'}{A} \SEQ \Right, \labels{x'}{B}, \labels{y}{A}}
		}
		%	
	}{
	\vlhtr{\DD_{2}}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
}
$
\end{small}

\item $C=\BOX A$:

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left \SEQ \Right}{
		\vlin{\rlabrn\BOX}{}{\B, \futs xu, \accs uv, \Left \SEQ \Right, \labels{x}{\BOX A}}{
			\vlhtr{\DD_1}{\B, \futs xu, \accs{u}{v}, \futs{x}{x'}, \accs{x'}{y'}, \Left \SEQ \Right, \labels{y'}{A}}	
		}
	}{
	\vlin{\llabrn\BOX}{}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A} \SEQ \Right}{
		\vlhtr{\DD_2}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}
	}
}
\reducesto
\end{smallequation*}

\begin{smallequation*}\hspace*{-7em}
	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left \SEQ \Right}{
		%	
		\vlhtr{\DD_1[u/x',v/y']}{\B, \futs xu, \accs uv, \Left \SEQ \Right, \labels{v}{A}}	
	}{
	\vlhtr{\DD_1'}{\B, \futs xu, \accs uv, \Left, \labels{v}{A} \SEQ \Right}
}
\end{smallequation*}

\begin{small}
	{with}$\quad\DD_1' = \quad
	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left, \labels{v}{A} \SEQ \Right}{
		\vlin{\rlabrn\BOX}{}{\B, \futs xu, \accs uv, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}}{
			\vlhtr{\DD_1^{\rn w}}{\B, \futs xu, \accs uv, \futs{x}{x'}, \accs{x'}{y'}, \Left, \labels{v}{A} \SEQ \Right, \labels{x}{\BOX A}, \labels{y'}{A}}	
		}
	}{
	\vlhtr{\DD_2}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A}, \labels{v}{A} \SEQ \Right}}$
\end{small}
\bigskip

The top $\rn{cut}$ is admissible by induction on the height, as the size of the cut-formula is constant. This however may increase the height above the right premiss of the bottom $\rn{cut}$ arbitrarily. The bottom $\rn{cut}$ is still admissible as the size of the cut-formula decreases.

\item $C=\DIA A$:

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B, \accs xy, \Left \SEQ \Right}{
		\vlin{\rlabrn\DIA}{}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}}{
			\vlhtr{\DD_1}{\B, \accs xy, \Left \SEQ \Right, \labels{x}{\DIA A}, \labels{y}{A}}
		}
	}{
	\vlin{\llabrn\DIA}{\text{\footnotesize $\lb{y'}$ is fresh}}{\B, \accs xy, \Left, \labels{x}{\DIA A} \SEQ \Right}{
		\vlhtr{\DD_2}{\B, \accs xy, \accs{x}{y'},\Left, \labels{y'}{A} \SEQ \Right}
	}	
}
\end{smallequation*}

\begin{smallequation*}
	\vlderiibase{\labrn{cut}}{}{\B, \accs xy, \Left \SEQ \Right}{
		\vliin{\labrn{cut}}{}{\B, \accs xy, \Left \SEQ \Right, \labels{y}{A}}{
			\vlhtr{\DD_1}{\B, \accs xy, \Left \SEQ \Right, \labels{y}{A}, \labels{x}{\DIA A}}
		}{
		\vlin{\llabrn\DIA}{\text{\footnotesize $\lb{y'}$ is fresh}}{\B, \accs xy, \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{A}}{
			\vlhtr{\DD_2^{\rn w}}{\B, \accs xy, \accs{x}{y'},\Left, \labels{y'}{A} \SEQ \Right, \labels{y}{A}}
		}
	}
}{
\vlhtr{\DD_2[y/y']}{\B, \accs xy, \Left, \labels{y}{A} \SEQ \Right}
}
\end{smallequation*}
%\lutz{Same. we need to explain why we can apply the IH}
The induction hypothesis is applied here again twice as above, on the height for the top $\rn{cut}$ and on formula size for the bottom one.
\end{itemize}
\end{description}
\end{proof}

We can now complete the proof of Theorem~\ref{thm:cut-adm}.
\begin{proof}[Proof of Theorem~\ref{thm:cut-adm}]
	By induction on number of $\rn{cut}$ rules, always applying Lemma~\ref{lem:reduction} to the leftmost topmost cut.
\end{proof}
\newcommand{\set}[1]{\{#1\}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extensions}\label{sec:ext}

The main goal of this section is to generate stronger logics adding new axioms to our system. We say \emph{stronger logic} to refer to the fact that we are restricting the class of frames we want to consider, imposing some restrictions on the accessibility relation.

In the \emph{fully labelled} framework, we are able for the first time to consider the logics defined by \emph{one-sided intuitionistic Scott-Lemmon axioms}:
\begin{equation}
%\gklmn\colon
\fm{\DIA^{k} \BOX^{l} A \IMP \BOX^{m}\DIA^{n} A}
\end{equation}
for any natural numbers $k,l,m,n$.

\begin{figure}
	$$
	\xymatrix{
		& y' \ar@{.>}[ddr]^{R^l} \\
		& y \ar@{.>}[u]^{\le} \\
		x \ar@{->}[ur]^{R^k}\ar@{->}[dr]_{R^m} && u \\
		& z \ar@{.>}[ur]_{R^n}
	}
	$$
	\caption{The intuitionistic klmn-incestuality condition}
	\label{fig:gklmn}
\end{figure}

Indeed, they are known to obey a strong correspondence with the class of frames satisfying the condition illustrated on Figure~\ref{fig:gklmn}, which we call by analogy to the classical case, \emph{intuitionistic klmn-incestuality condition}.

\begin{theorem}[\cite{plotkin:stirling:86}]\label{thm:gklmn-correspondence}
	An intuitionistic modal frame $\langle W, \rel, \le \rangle$ validates $\fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$ if and only if the frame satisfies:

	if $\lb x R^{k} \lb y$ and $\lb x R^{m} \lb z$ then there exists $\lb{y'}$ such that $\futs{y}{y'}$ and there exists $\lb u$ such that $\lb{y'}R^{l}\lb u$ and $\lb z R^{n} \lb u$.\footnote{The relation $R^h$ for $h\ge1$ is defined in the usual way: $R^1=R$ and $R^{h+1}=R\circ R^h=\set{(\lb v,\lb w)|\exists \lb u\in W.\; \lb vR\lb u \wedge \lb uR^h\lb w}$.}
\end{theorem}

Following again the axiom-as-rule idea, to have a sound and complete system for $\IK$ extended by any such axiom, we introduce to the system $\labIKp$ the $\gklmn$ rule, for any natural numbers $k,l,m,n$.

\begin{equation}
\label{eq:gklmn}
\vlinf{\gklmn}{\lb{y'}, \lb {u} \mbox{ fresh}}{\B, \lb x \rel^{k} \lb y, \lb x \rel^{m} \lb z, \Left \SEQ \Right}{\B, \lb x \rel^{k} \lb y, \lb x \rel^{m} \lb z, \futs{y}{y'}, \lb{y'}\rel^{l} \lb u, \lb z \rel^{n} \lb u, \Left\SEQ\Right}
\end{equation}

\begin{remark}
	Observe, that in the rule $\gklmn$ above, $\lb xR^k\lb y$ is an abbrevation for $\lb xR\lb{x_1},\lb{x_1}R\lb{x_2},\ldots,\lb{x_{k-1}}R\lb y$, and the labels $\lb x,\lb{x_1},\ldots,\lb{x_{k-1}},\lb y$ do \emph{not} have to be distinct, and if $k=0$ then $\lb x=\lb y$; and similarly for $\lb x R^{m} \lb z$.
	(In case some of them coincide, they are not repeated since $\B$ is a \emph{set} of relational atoms.)
	However, in the premise, the  expression $\lb{y'}R^{l} \lb u$ stands for  $\lb{y'}R\lb{u_1},\ldots,\lb{u_{l-1}}R \lb u$ where all $\lb{u_1},\ldots,\lb{u_{l-1}},\lb u$ are fresh, and therefore pairwise distinct, except if $l=0$, in which case $\lb u=\lb{y'}$; similarly for $\lb z R^{n} \lb u$, but note that if $n = 0$ then $\lb u=\lb z$.

	For example, the derivation in~\eqref{eq:g-example} below requires the (valid) application of~$\rn{g_{1110}}$: 
	$$\vlinf{\rn g_{1110}}{\lb{y'} \mbox{ fresh}}{\B, \lb x \rel \lb y, \lb x \rel \lb z, \Left \SEQ \Right}{\B, \lb x \rel \lb y, \lb x \rel \lb z, \futs{y}{y'}, \lb{y'}\rel \lb z, \Left\SEQ\Right}
	\qquad\mbox{as}\qquad
	\vlinf{\rn g_{1110}}{\lb{y'} \mbox{ fresh}}{\B, \accs xz, \Left \SEQ \Right}{\B, \lb x \rel \lb z, \futs{z}{y'}, \lb{y'}\rel \lb z, \Left\SEQ\Right}
	$$
	i.e., the case where $\lb y=\lb z$, in order to derive $ \fm{\BOX(\BOX A \IMP A)}$.

	\begin{equation}
	\label{eq:g-example}
	\vlderivation{
		\vlin{\rlabrn\BOX}{}{\SEQ \labels{x}{\BOX(\BOX A \IMP A)}}{
			\vlin{\rlabrn\IMP}{\lb v\mbox{ fresh}}{\futs xy, \accs yz \SEQ \labels{z}{\BOX A \IMP A}}{
				\vlin{\rn F_1}{\lb u\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
					\vlin{\rn g_{1110}}{ \lb{w}\mbox{ fresh}}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
						\vlin{\llabrn\BOX}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A} \SEQ \labels{v}{A}}{
							\vlin{\rn{id}}{}{\futs xy, \accs yz, \futs zv, \futs yu, \accs uv, \futs{v}{w}, \accs{w}{v}, \labels{v}{\BOX A}, \labels{v}{A} \SEQ \labels{v}{A}}{
								\vlhy{}
							}
						}
					}
				}
			}
		}
	}
	\end{equation}
\end{remark}

%

We can then show that Theorem~\ref{thm:cutfree-compl} generalises nicely to $\labIKp$ with any $\gklmn$ rule to provide a sound and cut-free complete system for this family of logics.

\begin{theorem}\label{thm:cutfree-compl-gklmn}
	For any formula $A$, the following are equivalent.
	%
	\begin{enumerate}
		\item\label{1} $A$ is a theorem of $\IK + \fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$. 
		%
		\item\label{2} $A$ is provable in $\labIKp + \gklmn +\labrn{cut}$.
		\item\label{3} $A$ is provable in $\labIKp + \gklmn $.
		%
		\item\label{4} $A$ is valid in every birelational frame satisfying the klmn-incestuality property.
	\end{enumerate}
\end{theorem}

\begin{proof} 
	The proof is similar to the one of Theorem~\ref{thm:cutfree-compl}.
	\begin{itemize}
		\item $1 \implies 2$:
		%
		Same as Thm.~\ref{thm:completeness} with the additional derivation of $\fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$:
		\begin{smallequation*}
			\vlderivation{
				\vlin{\rlabrn\IMP}{}{\SEQ \labels{x}{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}}{
					\vliq{\rlabrn\BOX}{}{\futs{x}{x_0}, \labels{x_0}{\DIA^k\BOX^lA} \SEQ \labels{x_0}{\BOX^m\DIA^n A}}{
						\vliq{\rn{F_1}}{}{\{\futs{x_i}{x_i'}, \accs{x_i'}{x_{i+1}}\}_{0\le i \le m-1}, \labels{x_0}{\DIA^k\BOX^l A} \SEQ \labels{x_m}{\DIA^n A}}{
							\vliq{\llabrn\DIA}{}{\futs{x_{m-2}'}{x_{m-2}''}, \accs{x_{m-2}''}{x_{m-1}'},\{\futs{x_i'}{x_i''},\accs{x_i''}{x_{i+1}''}\}_{0\le i \le m-2}, \labels{x_0}{\DIA^k\BOX^l A} \SEQ \labels{x_m}{\DIA^n A}}{
								\vliq{\rn{F_2}}{}{\accs{x_0}{y_1}, \{\accs{y_j}{y_{j+1}}\}_{1\le j \le k-1}, \labels{y_k}{\BOX^l A}\SEQ\labels{x_m}{\DIA^n A}}{
									\vlin {\gklmn}{}{\accs{x_0''}{y_1'},\{\accs{y_{j}'}{y_{j+1}'}\}_{1\le j \le k-1}, \labels{y_k}{\BOX^l A}\SEQ\labels{x_m}{\DIA^n A}}{
										\vliq {\rlabrn{\DIA}}{}{\futs{y_k'}{y_k''},\lb{y_k''}R^l\lb{w}, \lb{x_m}R^n\lb{w}, \labels{y_k}{\BOX^l A}\SEQ\labels{x_m}{\DIA^n A}}{
											\vlin {\rn{trans}+\rn{refl}}{}{\labels{y_k}{\BOX^l A}\SEQ\labels{x_m}{\DIA^n A},\labels{w}{A}}{
												\vliq {\llabrn{\BOX}}{}{\futs{y_k}{y_k''}, \ldots, \futs{w}{w}, \labels{y_k}{\BOX^l A}\SEQ\labels{x_m}{\DIA^n A},\labels{w}{A}}{
													\vlin {\rn{id}}{}{\labels{y_k}{\BOX^l A},\labels{w}{A}\SEQ\labels{x_m}{\DIA^n A},\labels{w}{A}}{
														\vlhy{}
													}
												}
											}
										}
									}
								}
							}
						}
					}
				}
			}
		\end{smallequation*}
		where we omit the accumulated relational context for space reason.

		\item $2 \implies 3$:
		To prove that the rule $\rn{cut}$ is admissible for $\labIKp + \gklmn$, it is enough to insert a case for the rule $\gklmn$ in the proof of Theorem~\ref{thm:cutfree-compl}, which
		is straightforward as the $\gklmn$ rule only manipulates the relational context.

		\item $3 \implies 4$:
		As we already proved the rules of $\labIKp$ sound in Theorem~\ref{thm:soundness}, we only need to prove that $\gklmn$ is sound.
		%
		By way of contradiction, assume that $\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\SEQ\Right$ is valid in any klmn-incestuous frame,
		but that there is such a model $\M$ and an interpretation $\inter\cdot$, such
		that $\M,\inter\cdot\not\Vdash\B, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \Left \SEQ \Right$.
		%
		That means, $\inter x \rel_\M^k \inter y$, $\inter x \rel_\M^m\inter z$, for all $\labels{x}{A} \in \Left$, $\cforce \M xA$ and for all $\labels wB\in\Right$,
		$\cnforce \M wB$. 
		%
		Since $\M$ is klmn-incestuous, there exists $v,w\in W_\M$, such that $\inter y \le_\M \lb{v}$, $\lb{v} R_\M^l \lb{w}$, and $\inter z R_\M^n \lb{w}$.
		%
		Now let $\inter\cdot^*$ be the extension of $\inter\cdot$ such that $\inter{y'}^* = v$, $\inter{u}^* = w$, and $\inter\cdot^* = \inter\cdot$ otherwise.
		%
		Then, $ \nforce \M {\inter\cdot^*} {\B, \futs{y}{y'}, \lb x R^{k} \lb y, \lb x R^{m} \lb z, \lb{y'}R^{l} \lb u, \lb z R^{n} \lb u, \Left\SEQ\Right}$. Contradiction.
	\end{itemize}

	The proof is completed by appealing to Theorem~\ref{thm:gklmn-correspondence} used as $4 \implies 1$ to close the equivalence.
\end{proof}

%

As we realise this theorem might look rather abstract, we come back to the example of the transitivity frame condition evoked in the introduction.
%%
The frames that validate the axiom $\ax{4^{\DIA}} \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the $2001$- condition: if $\accs wv$ and $\accs vu$, there exists $\lb{u'}$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
%%
The frames that validate the axiom $\ax{4^{\BOX}} \colon \fm{\BOX A \IMP \BOX \BOX A}$ are exactly the ones satisfying the $0120$-condition: if $\accs wv$ and $\accs vu$, there exists $\lb{w'}$ s.t.~$\futs{w}{w'}$ and $\accs{w'}{u}$.

We can therefore obtain a sound and complete proof system for the intuitionistic modal logic $\IK$ extended with axiom $\ax{4^{\DIA}}$ or $\ax{4^{\BOX}}$, respectively, by specialising the rule scheme above as:
$$
\vlinf{\rn{g_{2001}}}{\text{\footnotesize $\lb{u'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'} , \Left \SEQ \Right}
\qquad\mbox{or}\qquad
\vlinf{\rn{g_{0120}}}{\text{\footnotesize $\lb{w'}$ fresh}}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \futs{w}{w'}, \accs{w'}{u} , \Left \SEQ \Right}
$$
respectively.
Indeed, they allow us to derive the corresponding axioms $\ax{4^{\DIA}}$ and $\ax{4^{\BOX}}$ as required above in the completeness proof:
$$\vlderivation{
	\vlin{\rlabrn\IMP}{}{\labels{x}{\DIA\DIA A \IMP \DIA A}}{
		\vliq{\llabrn\DIA}{}{\futs xw, \labels{w}{\DIA\DIA A} \SEQ \labels{w}{\DIA A}}{
			\vlin{\rn{g_{2001}}}{}{\futs xw, \accs wv, \accs vu, \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
				\vlin{\rlabrn\DIA}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'},  \labels{u}{A} \SEQ \labels{w}{\DIA A}}{
					\vlin{\labrn{id}}{}{\futs xw, \accs wv, \accs vu, \futs{u}{u'}, \accs{w}{u'},  \labels{u}{A} \SEQ \labels{w}{\DIA A}, \labels{u'}{A}}{
						\vlhy{}
					}
				}
			}
		}
	}
}
$$
as well as,
$$\vlderivation{
	\vlin{\rlabrn\IMP}{}{\labels{x}{\BOX A \IMP \BOX\BOX A}}{	
		\vliq{\rlabrn\BOX}{}{\futs xw, \labels{w}{\BOX A} \SEQ \labels{w}{\BOX\BOX A}}{
			\vlin{\rn{F_1}}{}{\futs xw, \futs{w}{w'}, {\accs{w'}{v}}, {\futs{v}{v'}}, \accs{v'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
				\vlin{\rn{g_{0120}}}{}{\futs xw, \futs{w}{w'}, {\accs{w'}{v}}, {\accs{v}{v'}}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
					\vlin{\rn{trans_\le}}{}{\futs xw, \futs{w}{w'}, {\accs{w'}{v}}, {\futs{v}{v'}}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{t}{t'}, \accs{t'}{u}, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
						\vlin{\llabrn\BOX}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{t}{t'}, \accs{t'}{u}, \futs wt, \labels{w}{\BOX A} \SEQ \labels{u}{A}}{
							\vlin{\labrn{id}}{}{\futs xw, \futs{w}{w'}, \accs{w'}{v}, \futs{v}{v'}, \accs{v'}{u}, \futs{w'}{t}, \accs{t}{v'}, \futs{w}{t}, \accs tu, \labels{w}{\BOX A}, \labels{u}{\A} \SEQ \labels{u}{A}}{
								\vlhy{}
							}
						}
					}
				}
			}
		}
	}
}
$$

As another illustration of our system, we reconsider an example that was problematic in previous approaches to the logic $\IK + \fm{\DIA\BOX A \IMP \BOX\DIA A}$, corresponding to the $1111$-condition. (See details in Sec.6.3 of~\cite{simpson:phd}.)
%
Indeed, the formula $$\fm{\DIA(\BOX(a \OR b) \AND \DIA a) \AND \DIA(\BOX(a \OR b) \AND \DIA b)) \IMP \DIA(\DIA a \AND \DIA b)}$$ is not a theorem of this logic, but would become provable if we were to directly add to our system the rule 
$$\vlinf{}{}{\B, \accs wv, \accs vu, \Left \SEQ \Right}{\B, \accs wv, \accs vu, \accs{v}{x}, \accs{u}{x}, \Left \SEQ \Right}$$
%
corresponding to the directedness condition $\forall \lb{xyz}. ((\accs xy \AND \accs xz) \IMP\exists \lb{u}. (\accs yu \AND \accs zu))$. 
%
By representing birelational semantics precisely with both $R$ and $\le$ relations and by adding the  rule $\rn{g_{1111}}$ defined above, we can no longer derive this formula, as illustrated by the representation of the failed proof search below:	
\begin{smallequation*}
	\vlderivation{
		\vlin{\rlabrn\IMP,\llabrn\AND}{}{\SEQ\labels{x}{(\DIA(\BOX(a \OR b) \AND \DIA a) \AND \DIA(\BOX(a \OR b) \AND \DIA b)) \IMP \DIA(\DIA a \AND \DIA b)}}{
			\vlin{\llabrn\DIA, \llabrn\AND, \rlabrn\DIA}{\lb y' \mbox{ fresh}}{\futs{x}{x'}, \labels{x'}{\DIA(\BOX(a \OR b) \AND \DIA a)}, \labels{x'}{\DIA(\BOX(a \OR b) \AND \DIA b)} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}}{
				\vlin{\rlabrn\AND, \rn{id}}{}{\futs{x}{x'}, \accs{x'}{y'}, \labels{y'}{\BOX(a \OR b)}, \labels{y'}{\DIA a}, \labels{x'}{\DIA(\BOX(a \OR b) \AND \DIA b)} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA a \AND \DIA b}}{
					\vlin{\llabrn\DIA, \llabrn\AND, \rlabrn\DIA}{\lb z' \mbox{ fresh}}{\futs{x}{x'}, \accs{x'}{y'}, \labels{y'}{\BOX(a \OR b)}, \labels{y'}{\DIA a}, \labels{x'}{\DIA(\BOX(a \OR b) \AND \DIA b)} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}}{
						\vlin{\rlabrn\AND, \rn{id}}{}{\futs{x}{x'}, \accs{x'}{y'}, \accs{x'}{z'}, \labels{y'}{\BOX(a \OR b)}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{z'}{\DIA a \AND \DIA b}}{
							\vlin{\rn{g_{1111}}}{\lb{y''}, \lb{u''} \mbox{ fresh}}{\futs{x}{x'}, \accs{x'}{y'}, \accs{x'}{z'}, \labels{y'}{\BOX(a \OR b)}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{z'}{\DIA a}}{
								\vlin{\llabrn\BOX, \rlabrn\DIA}{}{\B_1, \labels{y'}{\BOX(a \OR b)}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{z'}{\DIA a}}{
									\vlin{\llabrn\OR, \rn{id}}{}{\B_1, \labels{y'}{\BOX(a \OR b)}, \labels{u''}{a \OR b}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{z'}{\DIA a}, \labels{u''}{a}}{
										\vlin{\rn{g_{1111}}}{\lb{z''}, \lb{v''} \mbox{ fresh}}{\B_1, \labels{y'}{\BOX(a \OR b)}, \labels{u''}{b}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{z'}{\DIA a}, \labels{u''}{a}}{
											\vlin{\llabrn\BOX, \rlabrn\DIA}{}{\B_1, \B_2,\labels{y'}{\BOX(a \OR b)}, \labels{u''}{b}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{z'}{\DIA a}, \labels{u''}{a}}{
												\vlin{\llabrn\OR, \rn{id}}{}
												{\B_1, \B_2,\labels{y'}{\BOX(a \OR b)}, \labels{u''}{b}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{v''}{a \OR b}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{v''}{b}, \labels{z'}{\DIA a}, \labels{u''}{a}}
												{\vlid{}{}
													{\B_1, \B_2,\labels{y'}{\BOX(a \OR b)}, \labels{u''}{b}, \labels{y'}{\DIA a}, \labels{z'}{\BOX(a \OR b)}, \labels{v''}{a}, \labels{z'}{\DIA b} \SEQ \labels{x'}{\DIA(\DIA a \AND \DIA b)}, \labels{y'}{\DIA b}, \labels{v''}{b}, \labels{z'}{\DIA a}, \labels{u''}{a}}
													{}}
											}
										}
									}
								}
							}
						}
					}
				}
			}
		}
	}
\end{smallequation*}
where $\B_1 = \futs{x}{x'}, \futs{y'}{y''}, \accs{x'}{y'}, \accs{x'}{z'}, \accs{y''}{u''}, \accs{z'}{u''}$
and $\B_2 = \futs{z'}{z''}, \accs{z''}{v''}, \accs{y'}{v''}$.

%
\begin{remark}
	The rules $\gklmn$ (similarly to those corresponding to reflexivity, transitivity, $\rn{F_1}$ and $\rn{F_2}$ in Section~ \ref{sec:system}) are obtained through the standard axioms-to-rule procedure that is well known for geometric axioms, and applies more generally to bipolar axioms~\cite{marin:etal:submitted} (and amounts to considering a positive bias on atoms).
	%
	On the other hand, a different shape of rules can be obtained in the style of Vigan\`o~\cite{vigano:00} (by assuming atoms are negatively polarised). 
	%
	For reflexivity and transitivity of the preorder relation, this gives
	%
	$$
	\vlinf{}{}{\Gamma \SEQ \Delta, \futs xx}{}
	\qquand
	\vliinf{}{}{\Gamma \SEQ \Delta, \futs xz}{\Gamma \SEQ \Delta, \futs xy}{\Gamma \SEQ \Delta, \futs yz}
	$$
	respectively.
	%
	Note however that these require (relational and preorder) atoms to appear on the right-hand-side of the sequent and the derivations to be read top-down, and therefore are not appropriate for proof search.	
	%

	Vigan\`o's method also assumes that the frame conditions are in a particular shape by prenexing and then skolemizing quantifiers. Following this process, we conjecture that for instance $\ax{F_1}$ could be incorporated to such a system as a pair of rules of the following form
	$$\vliinf{}{}{\B, \Gamma \SEQ \Delta, \futs x{f(x,y,z)}}{\B, \Gamma \SEQ \Delta, \accs xy}{\B, \Gamma \SEQ \Delta, \futs yz}
	\qquand
	\vliinf{}{}{\B, \Gamma \SEQ \Delta, \accs {g(x,y,z)}z}{\B, \Gamma \SEQ \Delta, \accs xy}{\B, \Gamma \SEQ \Delta, \futs yz}$$
	%
	where $f$ and $g$ are (Skolem) function constants, and that similar rules could be designed for Scott-Lemmon axioms too. 
	%
	It should even possible to design ``mixed" rules, by considering relational atoms positively and pre-order atoms negatively, or vice-versa. We leave the investigation of all these different shapes of rules for future work.
\end{remark}

\section{Conclusion}

In this paper we embrace the fully labelled approach to intuitionistic modal logic as pioneered by~\cite{maffezioli:etal:synthese13} and we study it in-depth for the class of logics defined by (one-sided) intuitionistic Scott-Lemmon axioms.
%
We establish that it is a valid approach to intuitionistic modal logic by proving soundness and completeness of our system, via a reductive cut elimination argument.

For a restricted class of these logics defined by so-called \emph{path axioms} $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
%
%
We believe that the framework presented here might be the more appropriate way to treat logics outside of the path axioms definable fragment.

However, we have not shown that our system satisfies Simpson's 6th requirement, that is, ``there is an intuitionistically comprehensible explanation of the meaning of the modalities relative to which [the system] is sound and complete".
%
To make sure that his system satisfies this requirement, Simpson chose to depart from the direct correspondence with modal axioms and their corresponding class of Kripke frames, and to study intuitionistic modal logics purely as a fragment of intuitionistic first-order logic.
%
We instead took the way of a direct correspondence of our system with the class of frames defined by one-sided Scott-Lemmon axioms as uncovered by~\cite{plotkin:stirling:86}, but as this class of logics seems to be rather well-behaved, we believe it should be possible to prove the satisfaction of Simpson's 6th requirement too.

We have considered in this work the logic known as $\IK$ (and its extensions) with respect to the birelational semantics that is its most well-studied semantics.
%
As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the \emph{constructive modal logic} $\mathsf{CK}$~\cite{bierman:depaiva:sl00,mendler:scheele:ic11} and any in between.
%
These can also be studied within the birelational framework with some additional conditions, and we are convinced that the fully labelled framework, once extended with these conditions, will be suitable to treat constructive fragments equally.
%
However, treating extensions of $\mathsf{CK}$ with axioms such as we did here for Scott-Lemmon logics is known to be complex~\cite{arisaka:etal:lmcs15}.

As for more general future work, there is a real necessity of a global view on intutionistic modal logics.
%
The work of~\cite{dalmonte:grellois:olivetti:JPL2020} is a great first step in understanding them in the context of non-normal modalities and neighbourhood semantics.
%
It would be interesting to know how and where the class of logics we considered can be included in their framework.

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %% Bibliography
 %\nocite{*}
 \bibliographystyle{alpha}
 \bibliography{references}

\end{document}

### 2021-01-15 FullyLabelled/JLC/document.tex
removing some comments
proof read up to end of section 3, will resume later today

@@
 \documentclass[a4paper]{article}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% PACKAGES
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{authblk}
-\input{new-macros}
-
+\usepackage[margin=2cm]{geometry}
+
+\usepackage{amsmath} 
+%\usepackage{amssymb} 
+\usepackage{amsthm}
+
+\usepackage{latexsym} % For \Box and \Diamond
+\usepackage{colonequals} % for ::=
+%\usepackage{bm} % nice boldface for maths
+
+\usepackage[matrix,arrow]{xy}
+%\usepackage{xcolor}
+\usepackage[noxy]{virginialake}
+
+%\usepackage{array}
+\usepackage{graphicx} % For command \includegraphics and \scalebox                        
+%\usepackage{tikz}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Small equation environments
+\newdimen\mydisplayskip
+\mydisplayskip=.4\abovedisplayskip
+%\newenvironment{smallequation}
+%{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation\endcsname}{\csname endequation\endcsname\egroup}
+%%
+\newenvironment{smallequation*}
+{\par\nobreak\vskip\mydisplayskip\noindent\bgroup\small\csname equation*\endcsname}{\csname endequation*\endcsname\egroup}
+%%
+%\newenvironment{smallalign}
+%{\par\nobreak\noindent\bgroup\small\csname align\endcsname}{\csname endalign\endcsname\egroup}
+%%
+%\newenvironment{smallalign*}
+%{\par\nobreak\noindent\bgroup\small\csname align*\endcsname}{\csname endalign*\endcsname\egroup}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Theorem counter
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+%\newtheorem{conjecture}[theorem]{Conjecture}
+%\newtheorem{fact}[theorem]{Fact}
+%\newtheorem{claim}[theorem]{Claim}
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+%\newtheorem{corollary}[theorem]{Corollary}
+%%
+\theoremstyle{definition}
+%\newtheorem{observation}[theorem]{Observation}
+\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{problem}[theorem]{Problem}
+%\newtheorem{construction}[theorem]{Construction}
+\newtheorem{remark}[theorem]{Remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Virginialake add-ons
+\newcommand{\vlderivationauxnc}[1]{#1{\box\derboxone}\vlderivationterm}
+\newcommand{\vlderivationnc}{\vlderivationinit\vlderivationauxnc}
+%
+%
+\makeatletter
+\newbox\@conclbox
+\newdimen\@conclheight
+%
+%
+\newcommand{\vlhtr}[2]{\vlpd{#1}{}{#2}}
+\newcommand\vlderiibase[5]{{%
+		\setbox\@conclbox=\hbox{$#3$}\relax%
+		\@conclheight=\ht\@conclbox%
+		\setbox\@conclbox=\hbox{$%
+			\vlderivationnc{%
+				\vliin{#1}{#2}{\box\@conclbox}{#4}{#5}%
+			}$}%
+		\lower\@conclheight\box\@conclbox%
+}}
+%
+\newcommand\vlderibase[4]{{%
+		\setbox\@conclbox=\hbox{$#3$}\relax%
+		\@conclheight=\ht\@conclbox%
+		\setbox\@conclbox=\hbox{$%
+			\vlderivationnc{%
+				\vlin{#1}{#2}{\box\@conclbox}{#4}%
+			}$}%
+		\lower\@conclheight\box\@conclbox%
+}}
+%
+\newcommand\vlderidbase[4]{{%
+		\setbox\@conclbox=\hbox{$#3$}\relax%
+		\@conclheight=\ht\@conclbox%
+		\setbox\@conclbox=\hbox{$%
+			\vlderivationnc{%
+				\vlid{#1}{#2}{\box\@conclbox}{#4}%
+			}$}%
+		\lower\@conclheight\box\@conclbox%
+}}
+%
+\makeatother
+%\left(
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% MACROS
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%% Comments  
+%\definecolor{notgray}{rgb}{.8,.8,.8}
+%\newcommand{\marianela}[1]{{\color{purple}[Marianela: #1]}}
+%\newcommand{\review}[1]{{\color{gray}[Reviewer: #1]}}
+%\newcommand{\sonia}[1]{{\color{blue}[Sonia: #1]}}
+%\newcommand{\lutz}[1]{{\color{notgreen}[Lutz: #1]}}
+%\newcommand{\todo}[1]{{\color{red}[TODO: #1]}}
+%
+%\newcommand{\old}[1]{{\color{notgray}[OLD: #1]}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% General
+\newcommand*{\A}{\mathcal{A}}
+%\newcommand{\G}{\mathcal{G}}
+\newcommand*{\SG}{\fm{\mathcal{G}}}
+\newcommand{\SGi}[1]{\fm{\mathcal{G}_{#1}}}
+%
+\newcommand{\quand}{\quad\mbox{and}\quad}
+\newcommand{\qquand}{\qquad\mbox{and}\qquad}
+\newcommand{\quadcm}{\rlap{\quad,}}
+%
+\newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Systems
+\newcommand*{\ax}[1]{\mathsf{#1}}
+\newcommand*{\kax}[1][]{\ax{k_{#1}}}
+\newcommand{\fourax}{\ax{4}}
+\newcommand{\agklmn}{{g_{klmn}}}
+%
+\newcommand*{\IK}{\mathsf{IK}}
+\newcommand*{\K}{\mathsf{K}}
+%
+\newcommand*{\IKfour}{\mathsf{IK4}}
+\newcommand*{\Kfour}{\mathsf{K4}}
+%
+%\newcommand*{\ISfour}{\mathsf{IS4}}
+%\newcommand*{\Sfour}{\mathsf{S4}}
+%
+\newcommand*{\labIKp}{\lab\IK_{\le}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Connectives
+\newcommand*{\NOT}{\neg}
+\newcommand*{\AND}{\mathbin{\wedge}}
+\newcommand*{\TOP}{\mathord{\top}}
+\newcommand*{\OR}{\mathbin{\vee}}
+\newcommand*{\BOT}{\mathord{\bot}}
+\newcommand*{\IMP}{\mathbin{\supset}}%%\scalebox{.9}{\raise.2ex\hbox{$\supset$}}}}
+
+\newcommand*{\BOX}{\mathord{\Box}}
+\newcommand*{\DIA}{\mathord{\Diamond}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Labelled sequents
+\definecolor{notgreen}{rgb}{.1,.6,.1}
+
+\newcommand{\lseq}[3]{#1 , #2 \SEQ #3}
+%
+\newcommand{\B}{\mathcal{R}}
+\newcommand{\Left}{\Gamma} %{\mathcal{L}}
+\newcommand{\Right}{\Delta} %{\mathcal{R}}
+%
+\newcommand*{\fm}[1]{{\color{notgreen}{#1}}}
+\newcommand*{\lb}[1]{{\color{blue}{#1}}}
+%
+\newcommand*{\rel}{R}
+\newcommand*{\labels}[2]{\lb{#1}\mathord{:}\fm{#2}}
+\newcommand*{\accs}[2]{\lb{#1}R\lb{#2}}
+\newcommand*{\futs}[2]{\lb{#1}\le{\lb{#2}}}
+%
+\newcommand{\SEQ}{\Longrightarrow}
+%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Labelled rules
+\newcommand*{\rn}[1]  {\ensuremath{\mathsf{#1}}}
+\newcommand*{\lab}{\mathsf{lab}}
+%
+\newcommand*{\labrn}[2][]  {\rn{#2}_{#1}}%^{\lab}}}
+\newcommand*{\rlabrn}[2][]  {\rn{#2}_\rn{R#1}}%^\lab}}
+\newcommand*{\llabrn}[2][]  {\rn{#2}_\rn{L#1}}%^\lab}}
+%%
+%\newcommand*{\brsym}{\boxtimes}%\mathord{\scalebox{.8}{$\blacksquare$}}}
+\newcommand*{\diasym}{\diamondplus}%\mathord{\blacklozenge}}
+%%
+\newcommand*{\boxbrn}[1]{\boxtimes_\rn{#1}}%^{\lab}}}
+\newcommand*{\diabrn}[1]{\diamondplus_\rn{#1}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% System labIK+gklmn
+\newcommand{\gklmn}{{\mathsf{g_{klmn}}}}%%\boxtimes
+\newcommand{\boxk}{\square_{R}^{k}}
+\newcommand{\boxlk}{\square_{L}^{k}}
+\newcommand{\diamk}{\lozenge_{L}^{k}}
+\newcommand{\diamrk}{\lozenge_{R}^{k}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Semantics
+\newcommand{\f}{f^{\mathcal{M}}}
+\newcommand{\M}{\mathcal{M}}
+\newcommand{\F}{\mathcal{F}}
+%
+\newcommand{\inter}[1]{\lb{\llbracket #1\rrbracket}}
+%\newcommand{\force}[3]{#1,#2\Vdash#3}
+\newcommand{\nforce}[3]{#1,#2\not\Vdash#3}
+\newcommand{\cforce}[3]{#1,\lb{#2}\Vdash\fm{#3}}
+\newcommand{\cnforce}[3]{#1,\lb{#2}\not\Vdash\fm{#3}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%% Derivations
+\newcommand{\Dw}{\mathcal{D}^{\rn w}}
+\newcommand{\Dwone}{\mathcal{D}_{1}^{\rn w}}
+\newcommand{\Dwtwo}{\mathcal{D}_{2}^{\rn w}}
+%
+\newcommand{\D}{\mathcal{D}}
+\newcommand*{\DD}{\mathcal{D}}
+\newcommand{\Done}{\mathcal{D}_{1}}
+\newcommand{\Dtwo}{\mathcal{D}_{2}}
+%
+\newcommand{\height}[1]{|#1|}
+%
+\newcommand*{\reducesto}{\quad{\leadsto}\quad}
+\newcommand*{\invr}[1]{#1}%^\bullet}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \title{A fully labelled proof system for intuitionistic modal logics}
@@
 \affil[3]{Inria Saclay}
-
 \date{}
@@
  \begin{abstract}
-   %% \review{Reconsider abstract. It reads very “operational” and does not clearly state the contributions of the paper.}
-   %% \lutz{Done?}
-   %% \sonia{Added two sentences at the beginning and modified it a bit.}
    Labelled proof theory has been famously successful for modal logics by mimicking their relational semantics within deductive systems.
@@
  the binary relation symbol $\rel$
- %These calculi work best for logics with
- %standard Kripke semantics, as in this case the relation $\rel$ 
+ %
  is used to encode the accessibility relation in the Kripke models, such that
@@
  encoded as inference rules.
- %\todo{Reviewer 1 complained about the ``best''}
+ %
  Prominent examples are classical modal
@@
  	\end{equation}
- 	%  \todo{add graphical representation of the conditions}
+ 	%  
  	$$
@@
  	respectively, have been studied in~\cite{plotkin:stirling:86}.
- 	%  \sonia{the general condition is correct but not the application to 4}
+ 	%  
  	\item The correspondence between the syntax and the semantics is not
@@
  	$\le$-relation) is visible in an ordinary labelled
- 	sequent, we only have the result that a formula is provable in an extension of $\IK$ beyond paths axioms 
- 	if and only if is satisfied in all \emph{graph-consistent}\footnote{This
+ 	sequent, we only have the result that a formula is provable in an extension of $\IK$ \emph{beyond paths axioms }
+ 	if and only if it is satisfied in all \emph{graph-consistent}\footnote{This
  		means that every layer in the model can be lifted to any future of
  		any world in that layer. See~\cite{simpson:phd} and~\cite{mar:str:tableaux17} for a formal definition and discussion.}   
- 	models satisfying the corresponding conditions, as observed by Simpson	and considered an inelegant solution~\cite{simpson:phd}.
+ 	models satisfying the corresponding standard (\emph{classical}) conditions, as observed by Simpson	and considered an inelegant solution~\cite{simpson:phd}.
  \end{enumerate}
@@
  %%
- Consequently, following the same ``axiom-to-rule'' method as Simpson, we can translate the frame
+ Consequently, following the ``axiom-to-rule'' method, we can translate the frame
  conditions in~\eqref{eq:4frame} into inference rules:
@@
  Besides that, there is another pleasant observation to make about our
- system. It is naturally a multi-conclusion system. Ordinary labelled sequent systems for intuitionistic modal
+ system: It is naturally a multi-conclusion system. 
+ Ordinary labelled sequent systems for intuitionistic modal
  logic are single-conclusion~\cite{simpson:phd}. 
@@
 Then, in Section~\ref{sec:system} we present our system for the intuitionistic modal logic $\IK$.
-In Sections~\ref{sec:completeness} and~\ref{sec:soundness}, we show soundness and completeness of the system with cut.
+In Sections~\ref{sec:completeness} and~\ref{sec:soundness}, we show its soundness and completeness with cut.
 The cut elimination theorem, proved in Section~\ref{sec:cut-elim}, then entails soundness and completeness for the cut-free system.
-Finally, in Section~\ref{sec:ext} we discuss the possible extension to the system to capture intuitionistic Scott-Lemmon modal logics.
+Finally, in Section~\ref{sec:ext} we discuss the extension of the system to capture intuitionistic Scott-Lemmon modal logics.
+
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- %
- %
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \section{Intuitionistic modal logics}\label{sec:intmod}
@@
 
- Obtaining the intuitionistic variant of $\mathsf{K}$ is more involved than the classical variant. 
+ Obtaining the intuitionistic version of $\mathsf{K}$ is more involved than the classical one. 
  %%
- Lacking De Morgan duality, there are many variants of the \emph{distributivity axiom} $\mathsf{k}$ that are classically but not intuitionistically equivalent.
+ Lacking De Morgan duality, there are many variants of the \emph{distributivity axiom} $\mathsf{k}$ that are classical but not intuitionistic consequences of one another.
 Five axioms have been considered as primitives in the literature.
-An intuitionistic variant of the modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
- %
-
- %The axiomatisation that is now generally accepted as intuitionistic modal logic $\IK$ was given by Plotkin and Stirling~\cite{Plotkin} and is equivalent to the one proposed by Fischer-Servi~\cite{Fischer}.
-It is obtained from intuitionistic propositional logic $\mathsf{IPL}$ by adding:
+An intuitionistic version of modal logic $\K$ can then be obtained from ordinary intuitionistic propositional logic $\rn{IPL}$ by adding:
+ %
+
  \begin{itemize}
@@
  It combines the semantics for intuitionistic propositional logic and the one for classical modal logic, using two distinct relations on the set of worlds.\footnote{This semantics and some variants have also been studied in~\cite{bovzic1984models}.
-For an excellent survey on possible variants see~\cite{simpson:phd}.}
+For an excellent survey on possible alternatives see~\cite{simpson:phd}.}
 
@@
  	A \emph{bi-relational frame} $\F$ is a triple $\langle W, \rel, \le \rangle$ 
- 	%	of a non-empty set of worlds $W$ equipped with two binary relations $R$ and $\le$, where $R$ being the modal \emph{accessibility relation} and $\le$ a preorder (\emph{i.e.} a reflexive and transitive relation), satisfying the following conditions:
- 	of a set of worlds $W$ equipped with an {accessibility relation} $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
+ 	%
+ 	of a set of worlds $W$ equipped with an \emph{accessibility} relation $\rel$ and a preorder $\le$ (\emph{i.e.}\ a reflexive and transitive relation) satisfying:
  	\begin{enumerate}
@@
 
- From the monotonicity of the valuation function $V$, we get a monotonicity property for the $\Vdash$ relation:
- \begin{proposition}(Monotonicity) 
- 	For any formula $\fm A$ and for any $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
+ From the monotonicity of the valuation function $V$, a monotonicity property for the $\Vdash$ relation is obtained.
+ \begin{proposition}%(Monotonicity) 
+ 	For any formula $\fm A$ and any $\lb w, \lb{w'} \in W$, if $\futs w{w'}$ and $\M, \lb w \Vdash \fm A$, then $\M, \lb{w'} \Vdash \fm A$.
  \end{proposition}
@@
  			\end{tabular}		
- 			%\end{minipage}
  		}		
@@
 
- Now we can present the inference rules for \emph{system $\labIKp$} for the logic $\IK$.
+ Now we can present the inference rules of \emph{system $\labIKp$} for the logic $\IK$.
  We obtained this system, shown in Figure~\ref{fig:labIKp}, as follows.
- Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can straightforwardly translated into the labelled setting, and which yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as we show them in Figure~\ref{fig:labIKp}.
+ Our starting point was the multiple-conlusion nested sequent system \emph{\`a la} Maehara (as presented in~\cite{str:2017maehara}), which can be straightforwardly translated into the labelled setting, and yields the rules $\llabrn\bot$, $\llabrn\AND$, $\rlabrn\AND$, $\llabrn\OR$, $\rlabrn\OR$, $\llabrn\DIA$, and $\rlabrn\DIA$ as shown in Figure~\ref{fig:labIKp}.
 However, this naive translation would also yield the rules $\rn{id'}$, $\llabrn\IMP'$, and~$\llabrn\BOX'$:
@@
  \end{equation}
- that are not sufficient for a complete system, and we will see below
- why. Before, let us first look at the rules $\rlabrn\IMP$ and
- $\rlabrn\BOX$. In the multiple-conlusion nested sequent system
- of~\cite{str:2017maehara}, these are the two rules that force
+ that are not sufficient for a complete system. Notice also that the rules $\rlabrn\IMP$ and
+ $\rlabrn\BOX$, in the multiple-conlusion nested sequent system
+ of~\cite{str:2017maehara}, are the two rules that force
  single-conclusion.  
@@
  In our system, this phenomenon is replaced by a re-positioning of the considered formulas to a fresh label.
- %
- In the Kripke-semantics in~\eqref{eq:kripke} the two
+
+ In the Kripke semantics in~\eqref{eq:kripke} the two
  connectives $\IMP$ and $\BOX$ are the ones that make use of the
@@
  order to capture that in the proof system, we need to add the rules
- $\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I} as presented in~\cite{dyckhoff2012}.}
+ $\rn{refl}$ and $\rn{trans}$.\footnote{These are the same as for {\bf G3I}, presented in~\cite{dyckhoff2012}.}
  %
@@
  Finally, in the semantics, the two relations $\rel$ and $\le$ are
- strongly connected through the two conditions $\rn{F_1}$ and $\rn{F_2}$.
+ strongly connected through the two conditions ($\rn{F_1}$) and ($\rn{F_2}$).
 These need to be reflected at the level of the proof system, which is done by the two rules $\rn{F_1}$ and $\rn{F_2}$.\footnote{The logic studied in~\cite{maffezioli2014} has similar semantic conditions (two binary relations in a Kripke frame) that lead to similar rules as ours in the proof system.}
@@
  	\item $\fm{A \OR B}$
- 	%\begin{smallequation*}
- 	%	\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \OR B} \SEQ \Right, \labels{y}{A \OR B}}{}
- 	%	\reducesto
- 	%\end{smallequation*}
+ 	%
  	\begin{smallequation*}
@@
  \item $\fm{A \IMP B}$
- %	\begin{smallequation*}
- %		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A \IMP B}}{}
- %		\reducesto
- %	\end{smallequation*}
+ %	
  \begin{smallequation*}
@@
 \item $\fm{\DIA A}$
-%	\begin{smallequation*}
-%		\vlinf{\labrn{id_g}}{}{\B, x \le y; \Left, \labels{x}{\DIA A} \SEQ \Right, \labels{y}{\DIA A}}{}
-%		\reducesto
-%	\end{smallequation*}
+%
 \begin{smallequation*}
@@
 
-We say that a formula is \emph{provable} in $\labIKp$ (or $\labIKp+\labrn{cut}$, resp.) if for any label $\lb x$, the sequent $\SEQ \labels{x}{A}$ is derivable from only axioms using the rules in Figure~\ref{fig:labIKp} (with possible instances of $\labrn{cut}$, resp.).
+We say that a formula $\fm A$ is \emph{provable} in $\labIKp$ (or $\labIKp+\labrn{cut}$, resp.) if for any label $\lb x$, the sequent $\SEQ \labels{x}{A}$ is derivable from only axioms using the rules in Figure~\ref{fig:labIKp} (with possible instances of $\labrn{cut}$, resp.).
 %
@@
 \begin{theorem}\label{thm:cutfree-compl}
-	For any formula $A$, the following are equivalent.
+	For any formula $\fm A$, the following are equivalent.
 	%
 	\begin{enumerate}
-		\item\label{i} $A$ is a theorem of $\IK$. 
-		%
-		\item\label{ii} $A$ is provable in $\labIKp +\labrn{cut}$.
-		\item\label{iii} $A$ is provable in $\labIKp$.
-		%
-		\item\label{iv} $A$ is valid in every birelational frame. 
+		\item\label{i} $\fm A$ is a theorem of $\IK$. 
+		%
+		\item\label{ii} $\fm A$ is provable in $\labIKp +\labrn{cut}$.
+		\item\label{iii} $\fm A$ is provable in $\labIKp$.
+		%
+		\item\label{iv} $\fm A$ is valid in every birelational frame. 
 	\end{enumerate}
@@
 \end{smallequation*}
-%\lutz{Same. we need to explain why we can apply the IH}
+%
 The induction hypothesis is applied here again twice as above, on the height for the top $\rn{cut}$ and on formula size for the bottom one.

### 2021-01-15 FullyLabelled/JLC/document.tex
proof read up to end of section 3, will resume later today
final read through

@@
 \newcommand{\proviso}[1]{\mbox{\scriptsize #1}}
+
+\newcommand{\set}[1]{\{#1\}}
 
@@
 		\item\label{ii} $\fm A$ is provable in $\labIKp +\labrn{cut}$.
+		%
 		\item\label{iii} $\fm A$ is provable in $\labIKp$.
@@
 consists of derivations of axioms of $\IK$ in $\labIKp$.
-More precisely, we prove completeness of $\labIKp+\rn{cut}$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below:
+More precisely, we prove completeness of $\labIKp+\rn{cut}$, i.e., the implication \ref{i}$\implies$\ref{ii} of Theorem~\ref{thm:cutfree-compl}, which is stated again below.
 
@@
 	\end{itemize}
-	Next, we have to prove all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader:
+	Next, we have to prove that all axioms of intuitionistic propositional logic can be shown in $\labIKp$. We do this only for $\fm{A \AND B \IMP B}$ and leave the rest to the reader.
 	\begin{smallequation*}
@@
 	Finally, we have to show how the rules of modus ponens and
-	necessitation can be simulated in our system. For modus ponens, this
-	is standard using the cut rule and for necessitation, we can
+	necessitation can be simulated in our system. For modus ponens, it
+	is standardly done using the cut rule, and for necessitation, we can
 	transform a proof of $\fm A$ into a proof of $\fm{\BOX A}$ as
@@
 	obtain a proof of $\SEQ \labels{x}{\BOX A}$.
-
-	This completes the proof of Theorem~\ref{thm:completeness}.
+%	
+%	This completes the proof of Theorem~\ref{thm:completeness}.
 \end{proof}
@@
 %
-This works well for $\IK$ (and a small number of its extensions) and have been used for example by~\cite{maffezioli:etal:synthese13}. 
+This works well for $\IK$ (and a small number of its extensions) and has been used for example by~\cite{maffezioli:etal:synthese13}. 
 %
@@
 means, we have to extend the relation $\Vdash$, defined in
-Section~\ref{sec:intmod} from formulas to sequents. This is the
+Section~\ref{sec:intmod}, from formulas to sequents. This is the
 purpose of the following definitions.
@@
 	\M,\inter\cdot\Vdash\SG\qquad\mbox{iff}\qquad
-	\parbox{20em}{if for all $\labels{x}{A} \in \Gamma$, we have $\M, \inter x \Vdash \fm A$, then there exists $\labels{z}{B} \in \Delta$ such that $\M, \inter z \Vdash \fm B$.}
+	\parbox{20em}{if for all $\labels{x}{A} \in \Gamma$, we have $\M, \inter x \Vdash \fm A$, then there exists $\labels{z}{B} \in \Delta$, such that $\M, \inter z \Vdash \fm B$.}
 	\end{equation}
@@
 	A sequent $\SG$ is \emph{satisfied} in $\M = \langle W, \rel, \le, V
-	\rangle$ iff for all $\SG$-interpretations $\inter\cdot$ we have
+	\rangle$ if for all $\SG$-interpretations $\inter\cdot$ we have
 	$\M,\inter\cdot\Vdash\SG$.
@@
 	A sequent $\SG$ is \emph{valid} in a frame $\F = \langle W, \rel,
-	\le \rangle$, if for all valuations $V$, the sequent $\SG$ is
+	\le \rangle$ if, for all valuations $V$, the sequent $\SG$ is
 	satisfied in $\langle W, R, \le, V \rangle$.
@@
 		%
-		So in particular, there are worlds $\lb{y'}$ and $\lb{z'}$
+		In particular, there are worlds $\lb{y'}$ and $\lb{z'}$
 		in $\M$ such that $\inter x\le_\M \lb{y'}$ and
@@
 		%
-		Now we let
-		$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter
+		Now we define
+		the extension $\inter\cdot'$ of $\inter\cdot$ as $\inter
 		y'=\lb{y'}$ and $\inter z'=\lb{z'}$ and $\inter\cdot'=\inter\cdot$
@@
 So there exists a world $\lb{y'}$ in $\M$ such that $\inter x\le_\M \lb{y'}$ and $\cforce\M{y'}{A}$ but $\nforce\M{\lb{y'}}{\fm B}$.
-Now we let 	$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot'=\inter\cdot$ on all other labels.
+Now let 	$\inter\cdot'$ be the extension of $\inter\cdot$ such that $\inter y'=\lb{y'}$ and $\inter\cdot'=\inter\cdot$ on all other labels.
 Then $\nforce\M{\inter\cdot'}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right, \labels{y}{B}}$.
@@
 	$\rn{trans}$, $\rn{F_1}$ and $\rn{F_2}$ are trivial, as all
-	birelations frames have to obey the corresponding conditions.
+	birelational frames have to obey the corresponding conditions.
 \end{proof}
@@
 	\label{thm:cut-adm}
-	The $\labrn{cut}$ rule is admissible for $\labIKp$.
+	All the occurences of the $\labrn{cut}$ rule in a proof $\DD$ in $\labIKp$ can be eliminated.
 \end{theorem}
@@
 Proposition~\ref{prop:mon-adm}, but it is not. First, we need to
-preserve the height, and second, we cannot prove it using $\rn{cut}$ rule as we
+preserve the height, and second, we cannot prove it using the $\rn{cut}$ rule as we
 are trying to eliminate it from derivations.
@@
 	\begin{smallequation*}
-		\vlderivation{
-			\vlin{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{
+		\vlderibase{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{
 				\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{z}{a}}{
@@
 			}
-		}
 		\reducesto
-		\vlderivation{
-			\vlin{\color{red}\labrn{trans}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{y}{z}, \futs{x}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{
+		\vlderibase{\color{red}\labrn{trans}}{}{\B, \futs{x}{y}, \futs{y}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{y}{z}, \futs{x}{z}, \Left, \labels{x}{a} \SEQ \Right, \labels{z}{a}}{
+					\vlhy{}
+				}
+			}
+		\end{smallequation*}
+
+		\begin{smallequation*} 
+ 			\vlderibase{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{
+					\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{x}{a}}{
+						\vlhy{}
+					}
+				}
+			\reducesto
+			\vlderibase{\color{red}\labrn{refl}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{x}{x}, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{
 						\vlhy{}
 					}}
-			}
-		\end{smallequation*}
-
-		\begin{smallequation*}
-			\vlderivation{
-				\vlin{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{
-					\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{x}{a}}{
-						\vlhy{}
-					}
-				}
-			}
-			\reducesto
-			\vlderivation{
-				\vlin{\color{red}\labrn{refl}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \futs{x}{x}, \labels{x}{a} \SEQ \Right, \labels{x}{a}}{
-						\vlhy{}
-					}}}
-				\end{smallequation*}
-
-				\begin{smallequation*}
-					\vlderivation{
-						\vlin{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
+				\end{smallequation*}
+
+				\begin{smallequation*}
+					\vlderibase{\llabrn{mon_a}}{}{\B, \futs{x}{y}, \Left, \labels{x}{a} \SEQ \Right, \labels{y}{a}}{
 							\vlin{\labrn{id}}{}{\B, \futs{x}{y}, \labels{x}{a}, \labels{y}{a} \SEQ \Right, \labels{y}{a}}{
 								\vlhy{}
-							}
 							}
@@
 
-			The next lemma shows that all the rules in our system are invertible, as already mentioned in the introduction.
+			The next lemma shows that the rules in our system are invertible, as already mentioned in the introduction.
 
@@
 				$\rlabrn{\AND}$ are height-preserving invertible on both premises, and the
-				rule $\llabrn{\IMP}$ is height-preserving invertible on the right premise.
+				rule $\llabrn{\IMP}$ is height-preserving invertible on the right premise only.
 				%
@@
 				For $\rlabrn\IMP$, $\rlabrn\BOX$, $\llabrn\DIA$ as well, but
-				we need to make sure that the obtained derivation uses a fresh label by using substitution inside $\DD^{\rn r}$ when necessary.
+				we need to make sure that the obtained derivation uses a fresh label by using substitution inside $\DD^{\rn r_i}$ when necessary.
 				%
@@
 					%
-					In the first case, we appeal to Lemma~\ref{lem:adm-mon-at}, to use the atomic monotonicity rule freely.
+					In the first case, we appeal to Lemma~\ref{lem:adm-mon-at}, to use the atomic monotonicity rule freely and to Lemma~\ref{lem:weak-adm} to obtain $\DD_2^{\rn w}$ through weakening admissibility.
 					\begin{itemize}
@@
 	\begin{smallequation*}
-		\reducesto\qquad\vlderiibase{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
+		\reducesto\vlderiibase{\llabrn\IMP}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right}{
 			\vlhtr{\DD_1'}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}
 		}{
-		\vlhtr{\DD_2'}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}
-	}
-\end{smallequation*}
-
+%		\vlhtr{\DD_2'}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}
+			\vliin{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}{
+				\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
+			}{
+				\vlhtr{\DD_3^{\invr{\llabrn\IMP}}}{\B, \futs xy, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
+			}
+	}
+\end{smallequation*}
+
+with
 \begin{small}
-	{with}$\quad\DD_1' = \quad
+	$\quad\DD_1' = \quad
 	\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{x}{A \IMP B} \SEQ \Right, \labels{y}{A}}{
@@
 	\vlhtr{\DD_3^{\rn w}}{\B, \futs xy, \Left, \labels{x}{A \IMP B}, \labels{z}{C} \SEQ \Right, \labels{y}{A}}
-}	$
-
-{and}$\quad\DD_2'= \quad
-\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}{
-	\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
-}{
-\vlhtr{\DD_3^{\invr{\llabrn\IMP}}}{\B, \futs xy, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
-}$
+	}	
+	$
 \end{small}
 
+%and
+%\begin{small}
+%$\quad\DD_2'= \quad
+%\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right}{
+%	\vlhtr{\DD_2}{\B, \futs xy, \Left, \labels{y}{B} \SEQ \Right, \labels{z}{C}}
+%}{
+%\vlhtr{\DD_3^{\invr{\llabrn\IMP}}}{\B, \futs xy, \Left, \labels{y}{B}, \labels{z}{C} \SEQ \Right}
+%}$
+%\end{small}
+
  where $\DD_3^{\rn w}$ is obtained using Lemma~\ref{lem:weak-adm} and $\DD_3^{\llabrn\IMP}$ is obtained using Lemma~\ref{lem:inv}. We use the same naming scheme in the following cases.
+
 \item $\rlabrn\IMP$:
-\begin{smallequation*}\hskip-8em
+\begin{smallequation*}
 	\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right, \labels{x}{A \IMP B}}{
@@
 
-\begin{smallequation*}\hskip8em
+\begin{smallequation*}
 	\reducesto
@@
 \item $\llabrn\BOX$:
-\begin{smallequation*}\hskip-8em
+\begin{smallequation*}
 	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left, \labels{x}{\BOX A} \SEQ \Right}{
@@
 \item $\rlabrn\BOX$:
-\begin{smallequation*}\hskip-8em
+\begin{smallequation*}
 	\vlderiibase{\labrn{cut}}{}{\B, \Left \SEQ \Right, \labels{x}{\BOX A}}{
@@
 
-\begin{smallequation*}\hspace*{-5.5em}
+\begin{smallequation*}
 	\vlderiibase{\labrn{cut}}{}{\B, \Left, \labels{x}{\DIA A} \SEQ \Right}{
@@
 \end{smallequation*}
-\begin{smallequation*}\hskip8em
+\begin{smallequation*}
 	\reducesto
@@
 
-	\begin{smallequation*}\hskip8em
+	\begin{smallequation*}
 		\reducesto
@@
 }
+\end{smallequation*}
+
+\begin{smallequation*}
 	\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}
-	\hspace*{-7em}
 	\vlderiibase{\labrn{cut}}{}{\B, \futs xy, \Left \SEQ \Right}{\vlhtr{\DD_1'}{\B, \futs xy, \Left \SEQ \Right, \labels{y}{A}}}{\vliin{\labrn{cut}}{}{\B, \futs xy, \Left, \labels{y}{A} \SEQ \Right}{
@@
 }
+\end{smallequation*}
+
+\begin{smallequation*}
 	\reducesto
-\end{smallequation*}
-
-\begin{smallequation*}\hspace*{-7em}
 	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left \SEQ \Right}{
@@
 	}{
-	\vlhtr{\DD_1'}{\B, \futs xu, \accs uv, \Left, \labels{v}{A} \SEQ \Right}
+	\vlhtr{\DD_2'}{\B, \futs xu, \accs uv, \Left, \labels{v}{A} \SEQ \Right}
 }
@@
 \begin{small}
-	{with}$\quad\DD_1' = \quad
+	{with}$\quad\DD_2' = 
 	\vlderiibase{\labrn{cut}}{}{\B, \futs xu, \accs uv, \Left, \labels{v}{A} \SEQ \Right}{
@@
 \begin{proof}[Proof of Theorem~\ref{thm:cut-adm}]
-	By induction on number of $\rn{cut}$ rules, always applying Lemma~\ref{lem:reduction} to the leftmost topmost cut.
+	By induction on number of $\rn{cut}$ rules in $\DD$, always applying Lemma~\ref{lem:reduction} to the leftmost topmost cut.
 \end{proof}
-\newcommand{\set}[1]{\{#1\}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-	For example, the derivation in~\eqref{eq:g-example} below requires the (valid) application of~$\rn{g_{1110}}$: 
+	For example, the derivation in~\eqref{eq:g-example} below requires the (valid) application of the rule
 	$$\vlinf{\rn g_{1110}}{\lb{y'} \mbox{ fresh}}{\B, \lb x \rel \lb y, \lb x \rel \lb z, \Left \SEQ \Right}{\B, \lb x \rel \lb y, \lb x \rel \lb z, \futs{y}{y'}, \lb{y'}\rel \lb z, \Left\SEQ\Right}
@@
 \begin{theorem}\label{thm:cutfree-compl-gklmn}
-	For any formula $A$, the following are equivalent.
+	For any formula $\fm A$, the following are equivalent.
 	%
 	\begin{enumerate}
-		\item\label{1} $A$ is a theorem of $\IK + \fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$. 
-		%
-		\item\label{2} $A$ is provable in $\labIKp + \gklmn +\labrn{cut}$.
-		\item\label{3} $A$ is provable in $\labIKp + \gklmn $.
-		%
-		\item\label{4} $A$ is valid in every birelational frame satisfying the klmn-incestuality property.
+		\item\label{1} $\fm A$ is a theorem of $\IK + \fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$. 
+		%
+		\item\label{2} $\fm A$ is provable in $\labIKp + \gklmn +\labrn{cut}$.
+		\item\label{3} $\fm A$ is provable in $\labIKp + \gklmn $.
+		%
+		\item\label{4} $\fm A$ is valid in every birelational frame satisfying the klmn-incestuality property.
 	\end{enumerate}
@@
 		%
-		Same as Thm.~\ref{thm:completeness} with the additional derivation of $\fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$:
+		Same as Thm.~\ref{thm:completeness} with the additional derivation of $\fm{\DIA^k\BOX^l A \IMP \BOX^m\DIA^n A}$
 		\begin{smallequation*}
@@
 		%
-		That means, $\inter x \rel_\M^k \inter y$, $\inter x \rel_\M^m\inter z$, for all $\labels{x}{A} \in \Left$, $\cforce \M xA$ and for all $\labels wB\in\Right$,
+		That means, $\inter x \rel_\M^k \inter y$, $\inter x \rel_\M^m\inter z$, for all $\labels{x}{A} \in \Left$, $\cforce \M xA$, and for all $\labels wB\in\Right$,
 		$\cnforce \M wB$. 
@@
 		%
-		Now let $\inter\cdot^*$ be the extension of $\inter\cdot$ such that $\inter{y'}^* = v$, $\inter{u}^* = w$, and $\inter\cdot^* = \inter\cdot$ otherwise.
+		Now let $\inter\cdot^*$ be the extension of $\inter\cdot$ such that $\inter{y'}^* = \lb v$, $\inter{u}^* = \lb w$, and $\inter\cdot^* = \inter\cdot$ otherwise.
 		%
@@
 %%
-The frames that validate the axiom $\ax{4^{\DIA}} \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the $2001$- condition: if $\accs wv$ and $\accs vu$, there exists $\lb{u'}$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
+The frames that validate the axiom $\ax{4^{\DIA}} \colon \fm{\DIA\DIA A \IMP \DIA A}$ are exactly the ones satisfying the $2001$-condition: if $\accs wv$ and $\accs vu$, there exists $\lb{u'}$ s.t.~$\futs{u}{u'}$ and $\accs{w}{u'}$.
 %%
@@
 
-We can therefore obtain a sound and complete proof system for the intuitionistic modal logic $\IK$ extended with axiom $\ax{4^{\DIA}}$ or $\ax{4^{\BOX}}$, respectively, by specialising the rule scheme above as:
+We can therefore obtain a sound and complete proof system for the intuitionistic modal logic $\IK$ extended with axiom $\ax{4^{\DIA}}$ or $\ax{4^{\BOX}}$, respectively, by specialising the rule scheme above as
 $$
@@
 respectively.
-Indeed, they allow us to derive the corresponding axioms $\ax{4^{\DIA}}$ and $\ax{4^{\BOX}}$ as required above in the completeness proof:
+Indeed, they allow us to derive the corresponding axioms $\ax{4^{\DIA}}$ and $\ax{4^{\BOX}}$ as required above in the completeness proof
 $$\vlderivation{
@@
 	%
-	Note however that these require (relational and preorder) atoms to appear on the right-hand-side of the sequent and the derivations to be read top-down, and therefore are not appropriate for proof search.
+	Note however that these require (relational and preorder) atoms to appear on the right-hand-side of the sequent and the derivations to be read top-down, and therefore would not be appropriate for proof search.
 	%
@@
 	%
-	where $f$ and $g$ are (Skolem) function constants, and that similar rules could be designed for Scott-Lemmon axioms too. 
-	%
-	It should even possible to design ``mixed" rules, by considering relational atoms positively and pre-order atoms negatively, or vice-versa.
+	where $\lb f$ and $\lb g$ are (Skolem) function constants, and that similar rules could be designed for Scott-Lemmon axioms too. 
+	%
+	It should even be possible to design ``mixed" rules, by considering relational atoms positively and pre-order atoms negatively, or vice-versa.
 We leave the investigation of all these different shapes of rules for future work.
@@
 
-For a restricted class of these logics defined by so-called \emph{path axioms} $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation and the birelational semantics~\cite{simpson:phd}.
+For a restricted class of these logics defined by so-called \emph{path axioms} $\fm{(\DIA^k\BOX A \IMP\BOX^m A) \AND (\DIA^k A \IMP \BOX^m\DIA A)}$ the standard labelled framework with one relation $R$ was enough for Simpson to get a strong connection between the sequent system, the axiomatisation, and the birelational semantics~\cite{simpson:phd}.
 %
@@
 %
-As we have mentioned, however, different basis can be considered for intuitionistic modal logic, for example the \emph{constructive modal logic} $\mathsf{CK}$~\cite{bierman:depaiva:sl00,mendler:scheele:ic11} and any in between.
-%
-These can also be studied within the birelational framework with some additional conditions, and we are convinced that the fully labelled framework, once extended with these conditions, will be suitable to treat constructive fragments equally.
+As we have mentioned, however, different basis can be considered for non-classical modal logic, for example the \emph{constructive modal logic} $\mathsf{CK}$~\cite{bierman:depaiva:sl00,mendler:scheele:ic11} and any in between.
+%
+These can also be studied within the birelational semantics with some additional conditions, and we are convinced that the fully labelled framework, once extended with these conditions, will be suitable to treat constructive fragments equally.
 %
@@
 
-As for more general future work, there is a real necessity of a global view on intutionistic modal logics.
+As for more general future work, there is a real necessity of a global view on intuitionistic modal logics.
 %
